### 2016-06-08 ident_manu.Rnw
filling manuscript template

\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
% \usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

% page margins and section title formatting
\linespread{1.5}
\setlength{\footskip}{0.5in}
\titleformat*{\section}{\Large\bf\em}
\titleformat*{\subsection}{\singlespace\large\bf}
\titleformat*{\subsubsection}{\singlespace\normalsize\bf\em}
\titlespacing{\section}{0in}{0in}{0in}
\titlespacing{\subsection}{0in}{0in}{0in}
\titlespacing{\subsubsection}{0in}{0in}{0in}

% cleveref options
\crefname{table}{Table}{Tables}
\crefname{figure}{Fig.}{Figs.}
\renewcommand{\figurename}{Fig.}

% aliased citations
% \defcitealias{FLDEP12}{FLDEP 2012}

%acronyms
% \acrodef{sfe}[SFE]{San Francisco Estuary}

%for supplemental figures/tables
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

%knitr options
<<setup,include=F,cache=F>>=
library(knitr)
# set global chunk options
opts_chunk$set(fig.path = 'figs/', fig.align = 'center', fig.show = 'hold', message = F, echo = F, results = 'asis', dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F)
options(replace.assign = TRUE, width = 90, digits = 1)

source('R/funcs.r')
library(WRTDStidal)
@

% get the version based on commit date
<<echo = FALSE, cache = FALSE>>=
raw <- system('git log -1', intern = TRUE)
raw <- raw[grep('^Date', raw)]
raw <- paste('Version', raw)
@

% get online bib file
<<echo = FALSE, cache = FALSE>>=
refs <- httr::GET('https://raw.githubusercontent.com/fawda123/refs/master/refs.bib')
refs <- rawToChar(refs$content)
writeLines(refs, con = file('refs.bib'))
@

\begin{document}

\raggedbottom
\linenumbers
\raggedright
\urlstyle{same}
\setlength{\parindent}{0.5in}
\renewcommand\refname{References \vspace{12pt}}

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ \Sexpr{raw}
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

\begin{abstract}
\noindent 
\end{abstract}
\acresetall

\section{Introduction}

Overall objective: Bio-geo-chemical models of water quality in coastal environments are useful tools for management and policy-making. Significant time and resources are spent developing these models in system-specific contexts. The transferability or relative ease of downscaling these models to different systems could facilitate their use as tools for environmental management. This study will evaluate a simple bio-geo-chemical model that is the core unit of a larger spatio-temporal model of hypoxia on the Louisiana Shelf of Gulf of Mexico. The analysis will focus on use of the model to describe dissolved oxygen dynamics over time having implications for understanding factors that contribute to hypoxic conditions that are detrimental to aquatic resources.

Questions:

* Can the FishTank model that is currently parameterized for GOM conditions be downscaled and parameterized to smaller systems (using Weeks Bay as a test example)?
* What parameters have the greatest influence on dissolved oxygen as identified by local and global sensitivity analyses?
* What is the 'parameter space' (from sensitivity analysis) and 'identifiability' of the model parameters?
* What is the uncertainty in identifiable parameters (MCMC eval)?
* Does the analysis identify information that is consistent with current understanding of ecological factors that influenc system condition?  That is, does the model give the right results for the right reasons?
* Additional questions may include the following:
    * What initial conditions have the greatest effect on dissolved oxygen?
    * How does the model structure influence predictions of dissolved oxygen?  Does changing complexity influence results, e.g., one to many phytoplankton groups?
    * How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?

Methods:

1. Develop a programmatic infrastructure for FishTank that facilitates sensitivity analysis, parameterization, and additional evaluation.
2. Conduct local and global sensitivity analyses of dissolved oxygen to identify parameters that influence predictions using existing values for the Gulf of Mexico
3. Parameterize FishTank to Weeks Bay conditions using NERRS dissolved oxygen time series and values for initial conditions that approximate observed.  This will include a characterization of parameter identifiability.  Appropriate calibration and validation datasets must also be identified.
4. Use Markov chain Monte Carlo analyses to estimate parameter uncertainties.
5. Evaluate model results in the context of ecological properties that influence hypoxia, with implications for additional data needs or further development of bio-geo-chemical models.

\section{Methods}

Sensitivity of the model to parameter changes is evaluated using the difference in model results before and after perturbing each parameter value.  Each parameter is perturbed by the same value as a percentage of the whole.  The default value (as 1 + 1e-8 proportion, default value for `tiny` argument in `sensFun`).  A sensitivity value $S$ is estimated for each time step $i$ given a set value for parameter $j$ as:

\begin{equation}
S_{ij} = \frac{\partial y_i}{\partial \Theta_j}\cdot\frac{w_{\Theta_j}}{w_{y_i}}
\end{equation}

where the estimate depends on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.  The estimates are unitless such that their relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.  The FME package summarizes sensitivity as $L1$ and $L2$ across the time series:

\begin{equation}
L1 = \sum|S_{ij}|/n
\end{equation}
\begin{equation}
L2 = \sqrt{\sum\left(S_{ij}^2\right)|/n}
\end{equation}

The mean, minimum, and maximum $S_{ij}$ values for each parameter are also reported.  In general, positive mean sensitivity estimates generally indicate that a parameter has a positive effect on the model results for a given increase in the parameter.  However, the effect can change over time so a plot of the 'sensitivity function' should be viewed which shows the difference from the values of the response variable before and after changing a parameter value.  Note that the perturbation factor in `sensFun` depends on the default value of each parameter such perturbations are not consistent for parameter values less than or greater than the perturbation factor.  This can produce results that are inconsistent for different levels of perturbation.  A custom function was keeps the perturbation factors constant regardless of the magnitude of the default values.  Sensitiviy for each parameter using the custom function are estimated using the above equations from the FME package. All parameters that are considered 'sensitive' should be further evaluated by plotting the predictions before and after perturbation and across the total range of the parameter.

Each parameter was perturbed by 50\% using `sensfun` to identify model sensitivity.  Parameters that produced different model results from the default values are shown below, by category.

The parameters that have the greatest effect on the model by category (optics, organics, phytoplankton, zooplankton) are as follows.

Plotting the raw values from the sensitivity analysis provides a visual assessment of changes.

Identifiability describes the ability to estimate a parameter in relation to variation among the remaining parameters.  A parameter is identifiable if all parameters within the set can be uniquely estimated based on the observed data.  Parameters that are unidentifiable typically produce similar model outputs for a given relative perturbation, i.e., the effect of altering one parameter can be undone by altering one or more other parameters.  Model calibration will not converge for parameters sets that are unidentifiable.  Identifiability is estimated from the minimum eigenvector of the cross-product of a model's sensitivity matrix:

\begin{equation}
\gamma = \frac{1} {\sqrt{ \min \left(\rm{EV}[\hat{S}^\intercal \hat{S}]\right)}}
\end{equation}

where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for a set of parameters in the sensitivity matrix $S$.  Identifiability can be estimated for any combination of parameters for a model.  Values less than 10-15 indicate parameters are generally identifiable.  The FME package provides the `collin` function to estimate identifiability of output from the `sensFun`.  For reasons described above, a custom function was created to determine identifiability from model residuals, where the residauls were based on a relative perturbation of the model parameters.  A comparison of results of identifiability using the custom functions and those from the FME package were generally in agreement.  Standard output from the identifiability function is shown below, where identifiability is displayed as a matrix with increasing combinations of subsets of the parameters.

The identifiability functions evaluate the ability to identify all subsets from pairwise to all parameters in the subset.  As an example, the identifiability of pairwise combinations for each of the categories are shown below.

Pairwise identifiability of the top two most sensitive parameters in each category is shown, first as a table showing all unique combinations from two to all parameters and second as a figure showing pairwise combinations.

Model calibration must consider the competing objectives of parameter inclusion and identifability.  Estimating parameters for novel datasets increases model complexity and the ability to identify parameters decreases with the inclusion of parameters to estimate.  The above analyses indicated that estimating all of the parameters was impossible because of redundancies in the the model output.  Calibration to novel datasets should balance the competing objectives of identifiability while including parameters for which model output is most sensitive.  The plots below show different scenarios of parameter inclusion for model calibration.  Reading each plot from left to right can be interpreted as including additional parameters, where each parameter is ranked by relative sensitivity.  The inset in each plot shows the identifiability of including parameters, up to a maximum where additional inclusion exceeds the identifability threshold of fifteen.  The scenarios for including parameters all begin with the parameters that have the greatest effect on the model output.  The inclusion of additional parameters depends on the scenario.  The first scenario selected parameters by decreasing sensitivity within each category (i.e., four separate models calibrated for optics, organics, phytoplankton, or zooplankton), the second scenario selected parameters by sensitivity regardless of category, and the third scenario selects parameters by sensitivity with equal representation between categories.  Boxes in each plot represent a unique parameter and the numbers in each box represent the relative rank of a parameter's sensitivity to the model output within each category.

The following plots show identifiability with the addition of parameters.

\section{Results}

\section{Discussion}

\end{document}

### 2016-06-08 ident_manu.tex
filling manuscript template

--- 2016-06-08 ident_manu.Rnw
@@
-\documentclass[letterpaper,12pt,oneside]{article}
+\documentclass[letterpaper,12pt,oneside]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
@@
 %knitr options
-<<setup,include=F,cache=F>>=
-library(knitr)
-# set global chunk options
-opts_chunk$set(fig.path = 'figs/', fig.align = 'center', fig.show = 'hold', message = F, echo = F, results = 'asis', dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F)
-options(replace.assign = TRUE, width = 90, digits = 1)
-
-source('R/funcs.r')
-library(WRTDStidal)
-@
 
 % get the version based on commit date
-<<echo = FALSE, cache = FALSE>>=
-raw <- system('git log -1', intern = TRUE)
-raw <- raw[grep('^Date', raw)]
-raw <- paste('Version', raw)
-@
 
 % get online bib file
-<<echo = FALSE, cache = FALSE>>=
-refs <- httr::GET('https://raw.githubusercontent.com/fawda123/refs/master/refs.bib')
-refs <- rawToChar(refs$content)
-writeLines(refs, con = file('refs.bib'))
-@
 
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
   \vspace{1in} 
-  \\ \Sexpr{raw}
+  \\ Version Date:   Wed Jun 8 08:37:59 2016 -0500
 	}

### 2016-06-08 ident_manu.Rnw
some general ideas about questions

@@
 \begin{abstract}
-\noindent 
+\noindent Bio-geo-chemical models are useful tools in environmental sciences that can guide management and policy-making.
+Significant time and resources are spent developing these models in system-specific contexts.
+The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools.
+This study describes quantitative limitations of model complexity by contrasting numeric and ecological certainty.
+We evaluate a simple bio-geo-chemical model that is the 1-dimensional unit of a larger spatio-temporal model of hypoxia on the Louisiana Shelf of Gulf of Mexico as an example.
+Results from analysis of the 1D model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
+In particular, we focus on issues of parameter identifiability using global sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
+We argue that quantitative and ecological certainty in model calibration are often at odds and the practitioner must explicitly choose model components to optimize given tradeoffs between the two.
+We conclude that numerically optimal parameter sets are often small subsets of the complete parameter set for a model because of redundancies in the unique effects of paramater perturbations on model output.
+As a result, use of a model for inference into ecological mechanisms of observed or predicted changes in response to management actions can be potentially misguided.
+Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.
+In addition to immediate implications for regional models, we provide a framework for describing the effects of parameter uncertainty and identifiability that can be applied to similar models to better inform environmental management.
 \end{abstract}
@@
 
-Overall objective: Bio-geo-chemical models of water quality in coastal environments are useful tools for management and policy-making.
-Significant time and resources are spent developing these models in system-specific contexts.
-The transferability or relative ease of downscaling these models to different systems could facilitate their use as tools for environmental management.
-This study will evaluate a simple bio-geo-chemical model that is the core unit of a larger spatio-temporal model of hypoxia on the Louisiana Shelf of Gulf of Mexico.
-The analysis will focus on use of the model to describe dissolved oxygen dynamics over time having implications for understanding factors that contribute to hypoxic conditions that are detrimental to aquatic resources.
-
-Questions:
-
-* Can the FishTank model that is currently parameterized for GOM conditions be downscaled and parameterized to smaller systems (using Weeks Bay as a test example)?
-* What parameters have the greatest influence on dissolved oxygen as identified by local and global sensitivity analyses?
-* What is the 'parameter space' (from sensitivity analysis) and 'identifiability' of the model parameters?
-* What is the uncertainty in identifiable parameters (MCMC eval)?
-* Does the analysis identify information that is consistent with current understanding of ecological factors that influenc system condition?
-That is, does the model give the right results for the right reasons?
-* Additional questions may include the following:
-    * What initial conditions have the greatest effect on dissolved oxygen?
-    * How does the model structure influence predictions of dissolved oxygen?  Does changing complexity influence results, e.g., one to many phytoplankton groups?
-    * How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
-
-Methods:
-
-1. Develop a programmatic infrastructure for FishTank that facilitates sensitivity analysis, parameterization, and additional evaluation.
-2. Conduct local and global sensitivity analyses of dissolved oxygen to identify parameters that influence predictions using existing values for the Gulf of Mexico
-3.
-Parameterize FishTank to Weeks Bay conditions using NERRS dissolved oxygen time series and values for initial conditions that approximate observed.
-This will include a characterization of parameter identifiability.
-Appropriate calibration and validation datasets must also be identified.
-4. Use Markov chain Monte Carlo analyses to estimate parameter uncertainties.
-5. Evaluate model results in the context of ecological properties that influence hypoxia, with implications for additional data needs or further development of bio-geo-chemical models.
+\begin{enumerate}
+\item Simulation/biogeochemical/process-based models overview, contrast with statistical models
+\item What models seek to provide - generality, precision, realism \cite{Levins66}, there is a tradeoff so models are 1) developed in partial independence and dependence on the world and theory, 2) function autonomously from both, or 3) represent both at the same time, from \cite{Morrison99}, cited in \cite{Ganju16}.
+This is similar to the bias-variance tradeoff for statistical models, e.g., overparameterization of a model makes it very biased as it fits the data (the world) exactly
+\item How is model performance/uncertainty evaluated regarding what they should provide - structural, observational, parameter \cite{Beck87}?
+\item Parameter uncertainy as low-hanging fruit - can do post-hoc and from inner to outer level of complexity
+\item Challenges related to uncertainty - similar to degrees of freedom, identifiability definition from \cite{Brun01} and need to evaluate identifiability \cite{Fasham06}
+\item objectives of study, definition of `optimum'
+\begin{enumerate}
+\item What parameters have the greatest influence on dissolved oxygen as identified by local and global sensitivity analyses?
+\item What is the 'parameter space' (from sensitivity analysis) and 'identifiability' of the model parameters?
+\item Can we get a better estimate of identifiability other than 10-15 according to \cite{Brun01,Soetaert10}?
+\item Can we reconcile differences in numeric uncertainty and ecological uncertainty, e.g., given a finite parameter space, what is an appropriate way to choose parameters given question of interest?
+\end{enumerate}
+\end{enumerate}
 
 \section{Methods}
+
+\subsection{Model description}
+
+GGEM, FishTank, parameters and parameter categories, how they compare to other models
+
+\subsection{Local sensitivity analysis}
+
+Methods from \cite{Soetaert10}
 
@@
 
+\subsection{Global sensitivity and identifiability}
+
 Identifiability describes the ability to estimate a parameter in relation to variation among the remaining parameters.
@@
 
+\subsection{Identifying subsets and testing calibration}
+
 Model calibration must consider the competing objectives of parameter inclusion and identifability.
@@
 
+Questions specific to GOM - what initial conditions are important? How many phytoplankton groups do we need (e.g., related to structural uncertainty)?
+
+How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
+
+How does uncertainty translate to what a model should provide (generality v precision)?  The first step - find out what can be optimized but then do not overfit....
+
+Need to talk about \cite{Flynn05}
+
+\clearpage
+\begin{singlespace}
+\bibliographystyle{apalike_mine}
+\bibliography{refs}
+\end{singlespace}
+\clearpage
+
 \end{document}

### 2016-06-08 ident_manu.tex
some general ideas about questions

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Jun 8 08:37:59 2016 -0500
+  \\ Version Date:   Wed Jun 8 09:02:46 2016 -0500
 	}

### 2016-06-09 ident_manu.Rnw
minor edits to abs, added combn figure

@@
 library(WRTDStidal)
+library(tidyr)
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
 @
@@
 The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools.
-This study describes quantitative limitations of model complexity by contrasting numeric and ecological certainty.
+This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter uncertainty.
 We evaluate a simple bio-geo-chemical model that is the 1-dimensional unit of a larger spatio-temporal model of hypoxia on the Louisiana Shelf of Gulf of Mexico as an example.
@@
 We argue that quantitative and ecological certainty in model calibration are often at odds and the practitioner must explicitly choose model components to optimize given tradeoffs between the two.
-We conclude that numerically optimal parameter sets are often small subsets of the complete parameter set for a model because of redundancies in the unique effects of paramater perturbations on model output.
-As a result, use of a model for inference into ecological mechanisms of observed or predicted changes in response to management actions can be potentially misguided.
+We further conclude that numerically optimal parameter sets are often small subsets of the complete parameter set for a model because of redundancies in the unique effects of paramater perturbations on model output.
+As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in environmental condition can be potentially misguided in the absence of quantitative descriptions of identifiability.
 Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.
@@
 
+%%%%%%
+% figures
+<<echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
+The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 100 parameter sets are shown each with one through 100 total parameters.
+For example, there are six unique parameter combinations that result from choosing two parameters from a set.
+Note that the number of unique combinations is shown as the natural-log.
+The same information is viewed differently in each plot.', fig.height = 5, fig.width = 10, out.width = '\\textwidth'>>=
+
+numparms <- 1:100
+sels <- 1:100
+toplo <- sapply(numparms, choose, k = sels)
+dimnames(toplo) <- list(sels, numparms)
+toplo <- data.frame(sels = sels, toplo)
+toplo <- gather(toplo, 'numparms', 'combs', -sels) %>% 
+  mutate(numparms = as.numeric(gsub('^X', '', numparms))) %>% 
+  filter(combs > 0) %>% 
+  mutate(combs = log(combs))
+
+pal <- 'RdYlGn'
+
+p1 <- ggplot(toplo, aes(x = sels, y = combs, group = numparms, colour = numparms)) + 
+  geom_line() +
+  # geom_point() + 
+  theme_minimal() + 
+  scale_colour_distiller(palette = pal, 
+    guide = guide_legend(title = 'Total number of\nparameters in set')) +
+  scale_x_continuous('Number of parameters selected from total', expand = c(0, 0)) + 
+  scale_y_continuous('Number of unique parameter combinations, log-scale', expand = c(0, 0)) + 
+  theme(legend.position = 'top')
+
+p2 <- ggplot(toplo, aes(x = numparms, y = sels, fill = combs)) +
+  geom_tile() + 
+  scale_fill_distiller(palette = pal, 
+    guide = guide_legend(title = 'Number of unique parameter\ncombinations, log-scale')) + 
+  scale_x_continuous('Total number of parameters in set', expand = c(0, 0)) + 
+  scale_y_continuous('Number of parameters selected from total', expand = c(0, 0)) +
+  theme_minimal() + 
+  theme(legend.position = 'top')
+
+grid.arrange(p1, p2, ncol = 2)
+@
+
 \end{document}

### 2016-06-09 ident_manu.tex
minor edits to abs, added combn figure

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Jun 8 09:02:46 2016 -0500
+  \\ Version Date:   Wed Jun 8 16:40:27 2016 -0500
 	}
@@
 
+%%%%%%
+% figures
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/unnamed-chunk-3-1}
+
+}
+
+\caption[Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets]{Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
+The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 100 parameter sets are shown each with one through 100 total parameters.
+For example, there are six unique parameter combinations that result from choosing two parameters from a set.
+Note that the number of unique combinations is shown as the natural-log.
+The same information is viewed differently in each plot.}\label{fig:unnamed-chunk-3}
+\end{figure}
+
 \end{document}

### 2016-06-13 ident_manu.Rnw
more content to outline

@@
 \item What models seek to provide - generality, precision, realism \cite{Levins66}, there is a tradeoff so models are 1) developed in partial independence and dependence on the world and theory, 2) function autonomously from both, or 3) represent both at the same time, from \cite{Morrison99}, cited in \cite{Ganju16}.
-This is similar to the bias-variance tradeoff for statistical models, e.g., overparameterization of a model makes it very biased as it fits the data (the world) exactly
+This is similar to the bias-variance tradeoff for statistical models, e.g., overparameterization of a model makes it very biased as it fits the data (the world) exactly, tradeoff between sensitity and error with changes in model complexity (more complexity is less error but increasing sensitivity) described in \cite{Snowling01}
 \item How is model performance/uncertainty evaluated regarding what they should provide - structural, observational, parameter \cite{Beck87}?
-\item Parameter uncertainy as low-hanging fruit - can do post-hoc and from inner to outer level of complexity
-\item Challenges related to uncertainty - similar to degrees of freedom, identifiability definition from \cite{Brun01} and need to evaluate identifiability \cite{Fasham06}
+\item Parameter uncertainy as low-hanging fruit - can do post-hoc and from inner to outer level of complexity, parameter uncertainty is the most common, e.g., marine ecological model \cite{Mateus15}, but stopped short, global sensitivity analysis of eutrophication model \cite{Estrada10}
+\item Challenges related to uncertainty - similar to degrees of freedom, identifiability definition from \cite{Brun01} and need to evaluate identifiability \cite{Fasham06}, \cite{Omlin01} did a similar analysis with freshwater biogeochem model
 \item objectives of study, definition of `optimum'
@@
 
-Methods from \cite{Soetaert10}
+Methods from \cite{Reichert01,Soetaert10}
 
@@
 where the estimate depends on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
-The estimates are unitless such that their relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.
+The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y$, are set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
+The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.
 The FME package summarizes sensitivity as $L1$ and $L2$ across the time series:
@@
 Model calibration will not converge for parameters sets that are unidentifiable.
-Identifiability is estimated from the minimum eigenvector of the cross-product of a model's sensitivity matrix:
+Identifiability is estimated from the minimum eigenvector of the cross-product of a model's sensitivity matrix \citep{Brun01,Omlin01}:
 
@@
 
-Need to talk about \cite{Flynn05}
+What about structural uncertainty - does sensitivity of a model to variation in a parameter imply parameter uncertainty and/or structural uncertainty?
+
+A final point about optimization with identifiable parameter sets - optimization to fit the data still does not ensure a correct model.
+Failing in one way can be over-compensated by another feature, e.g., the parameter set that is optimized (see \cite{Flynn05}, p.
+1207, third paragraph)
+
+\cite{Omlin01} state that the sensitivity, identifiability, estimation process is iterative (p. 113), need to rinse and repeat for proper calibration.
+
+How to improve identifiability - get more/better observed data, include obs from other state variables in RSS minimization (eqn q in \cite{Omlin01})
 
@@
 
-numparms <- 1:100
-sels <- 1:100
+numparms <- 1:50
+sels <- numparms
 toplo <- sapply(numparms, choose, k = sels)

### 2016-06-13 ident_manu.tex
more content to outline

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Jun 8 16:40:27 2016 -0500
+  \\ Version Date:   Thu Jun 9 13:52:04 2016 -0500
 	}

### 2016-06-24 ident_manu.Rnw
last paragraph of intro added

@@
 % aliased citations
-% \defcitealias{FLDEP12}{FLDEP 2012}
+\defcitealias{LehrterIR}{Lehrter et al. in review}
 
 %acronyms
-% \acrodef{sfe}[SFE]{San Francisco Estuary}
+\acrodef{cgem}[CGEM]{Coastal Gulf Ecology Model}
+\acrodef{gom}[GOM]{Gulf of Mexico}
 
@@
 \noindent Bio-geo-chemical models are useful tools in environmental sciences that can guide management and policy-making.
-Significant time and resources are spent developing these models in system-specific contexts.
+Consequently, significant time and resources are spent developing these models in system-specific contexts.
 The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools.
-This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter uncertainty.
+This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter sensitivity and identifability.
 We evaluate a simple bio-geo-chemical model that is the 1-dimensional unit of a larger spatio-temporal model of hypoxia on the Louisiana Shelf of Gulf of Mexico as an example.
 Results from analysis of the 1D model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
-In particular, we focus on issues of parameter identifiability using global sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
+In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
 We argue that quantitative and ecological certainty in model calibration are often at odds and the practitioner must explicitly choose model components to optimize given tradeoffs between the two.
-We further conclude that numerically optimal parameter sets are often small subsets of the complete parameter set for a model because of redundancies in the unique effects of paramater perturbations on model output.
-As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in environmental condition can be potentially misguided in the absence of quantitative descriptions of identifiability.
+We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of paramater perturbations on model output.
+As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in hypoxic condition can be potentially misguided in the absence of quantitative descriptions of identifiability.
 Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.
@@
 \item Challenges related to uncertainty - similar to degrees of freedom, identifiability definition from \cite{Brun01} and need to evaluate identifiability \cite{Fasham06}, \cite{Omlin01} did a similar analysis with freshwater biogeochem model
-\item objectives of study, definition of `optimum'
-\begin{enumerate}
-\item What parameters have the greatest influence on dissolved oxygen as identified by local and global sensitivity analyses?
-\item What is the 'parameter space' (from sensitivity analysis) and 'identifiability' of the model parameters?
-\item Can we get a better estimate of identifiability other than 10-15 according to \cite{Brun01,Soetaert10}?
-\item Can we reconcile differences in numeric uncertainty and ecological uncertainty, e.g., given a finite parameter space, what is an appropriate way to choose parameters given question of interest?
 \end{enumerate}
-\end{enumerate}
+
+This study describes a parameter sensitivity analysis to evaluate identifiability for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
+We evaluate a simple 1-dimensional unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the Lousiana coastal shelf.
+The study also provides a general framework for sensitivity analysis and parameter identifiability that can be used on similar mechanistic models.
+Specifically, an assumption is that models are generally over-parameterized and only a finite and smaller subset of the larger parameter set can be optimized for a given research question or dataset.
+We provide explicit guidance for choosing such subsets of the parameter space given constraints on identifiability as directly related to sensitivity analyses.
+The specific objectives are to \begin{inparaenum}[1\upshape)]
+\item identify the parameters that have the greatest influence on dissolved oxygen using local sensitivity analysis,
+\item quantify the identifiability of subsets of the total parameter space based on sensitivity,
+\item provide a set of heuristics for choosing parameters based on sensitivity and parameter categories with the larger mechanistic model, including extension to other state variables, and 
+\item discuss implications for hypoxia formation in coastal regions, including management strategies for nutrient reduction and use of mechanistic models to inform decision-making.
+\end{inparaenum}
+The `optimum' parameter space is defined as the chosen subset that represents the maximum number of identifiable parameters.
+Here, `optimum' is both a qualitative description based on a research question or management goal and a quantitative objective based on numerical optimization criteria for fitting model output to a calibration dataset.
+These results can be used to refine existing models or guide application of models to novel contexts, such as downscaling or application to new environments.
 
@@
 
-GGEM, FishTank, parameters and parameter categories, how they compare to other models
+Three-dimensional numerical models have recently been developed for the northern \ac{gom} to explore dynamics in bottom-water hypoxia and primary production (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
+The Louisiana coastal shelf  covers an area of
+
+ FishTank, parameters and parameter categories, how they compare to other models
 
@@
 
-\subsection{Global sensitivity and identifiability}
+\subsection{Identifiability}
 
@@
 
+Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}
+
 \clearpage

### 2016-06-24 ident_manu.tex
last paragraph of intro added

@@
   \vspace{1in} 
-  \\ Version Date:   Thu Jun 9 13:52:04 2016 -0500
+  \\ Version Date:   Mon Jun 13 10:12:26 2016 -0500
 	}
@@
 
-GGEM, FishTank, parameters and parameter categories, how they compare to other models
+Three-dimensional numerical models have recently been developed for the northern \ac{gom} to explore dynamics in bottom-water hypoxia and primary production (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
+The Louisiana coastal shelf  covers an area of
+
+CGEM \citepalias{LehrterIR}, FishTank, parameters and parameter categories, how they compare to other models
 

### 2016-06-26 ident_manu.Rnw
working on beginning of methods

@@
 %acronyms
-\acrodef{cgem}[CGEM]{Coastal Gulf Ecology Model}
+\acrodef{cgem}[CGEM]{Coastal General Ecosystem Model}
 \acrodef{gom}[GOM]{Gulf of Mexico}
+\acrodef{lcs}[LCS]{Louisiana continental shelf}
+\acrodef{marb}[MARB]{Mississippi-Atchafalaya River Basin}
 
@@
 This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter sensitivity and identifability.
-We evaluate a simple bio-geo-chemical model that is the 1-dimensional unit of a larger spatio-temporal model of hypoxia on the Louisiana Shelf of Gulf of Mexico as an example.
+We evaluate a simple bio-geo-chemical model that is the 1-dimensional unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example.
 Results from analysis of the 1D model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
@@
 This study describes a parameter sensitivity analysis to evaluate identifiability for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
-We evaluate a simple 1-dimensional unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the Lousiana coastal shelf.
+We evaluate a simple 1-dimensional unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
 The study also provides a general framework for sensitivity analysis and parameter identifiability that can be used on similar mechanistic models.
@@
 
-Three-dimensional numerical models have recently been developed for the northern \ac{gom} to explore dynamics in bottom-water hypoxia and primary production (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
-The Louisiana coastal shelf  covers an area of
+Low concentrations of dissolved oxygen occur seasonally on the \ac{lcs} in the northern \ac{gom}.
+These hypoxic events, defined as $<$2 mg L$^{-1}$ ($<$ 64 mmol m$^-3$ of O$_2$), occur in bottom waters and are caused by nutrient inputs from the \ac{marb} that drains a significant portion of the continental United States.
+Nutrient-stimulated primary production in surface waters increases biological oxygen demand in bottom waters as sinking organic matter is decomposed.
+The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.
+Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas factors related to hydrologic variation and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97}.
+
+Three-dimensional numerical simulation models have been developed to better understand factors contributing to hypoxia and to predict the effects of management actions or climate scenarios on future patterns (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
+This study evaluates a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia.
+The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} to describe hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
+The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia dynamics using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
+The biogehmical component includes equations for 33 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.
+The model is run for a set period of time at a given time step using atmospheric and hydrological boundary conditions described in cites....
 

### 2016-06-26 ident_manu.tex
working on beginning of methods

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Jun 13 10:12:26 2016 -0500
+  \\ Version Date:   Fri Jun 24 16:57:50 2016 -0500
 	}
@@
 
-Three-dimensional numerical models have recently been developed for the northern \ac{gom} to explore dynamics in bottom-water hypoxia and primary production (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
-The Louisiana coastal shelf  covers an area of
+Low concentrations of dissolved oxygen occur seasonally on the \ac{lcs} in the northern \ac{gom}.
+These hypoxic events, defined as $<$2 mg L$^{-1}$ ($<$ 64 mmol m$^-3$ of O$_2$), occur in bottom waters and are caused by nutrient inputs from the \ac{marb} that drains a significant portion of the continental United States.
+Nutrient-stimulated primary production in surface waters increases biological oxygen demand in bottom waters as sinking organic matter is decomposed.
+The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.
+Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas factors related to hydrologic variation and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97}.
 
-CGEM \citepalias{LehrterIR}, FishTank, parameters and parameter categories, how they compare to other models
+Three-dimensional numerical simulation models have been developed to better understand factors contributing to hypoxia and to predict the effects of management actions or climate scenarios on future patterns (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
+This study evaluates a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia.
+The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} to describe hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
+The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia dynamics using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
+The biogehmical component includes equations for 33 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.
+The model is run for a set period of time at a given time step using atmospheric and hydrological boundary conditions described in cites....
+
+FishTank, parameters and parameter categories, how they compare to other models
 

### 2016-06-27 ident_manu.Rnw
model descrip done in methods

@@
 %acronyms
+\acrodef{oned}[1-D]{one-dimensional}
 \acrodef{cgem}[CGEM]{Coastal General Ecosystem Model}
+\acrodef{do}[O$_2$]{dissolved oxygen}
 \acrodef{gom}[GOM]{Gulf of Mexico}
@@
 This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter sensitivity and identifability.
-We evaluate a simple bio-geo-chemical model that is the 1-dimensional unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example.
-Results from analysis of the 1D model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
+We evaluate a simple bio-geo-chemical model that is the \ac{oned} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example.
+Results from analysis of the \ac{oned} model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
 In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
@@
 \item Parameter uncertainy as low-hanging fruit - can do post-hoc and from inner to outer level of complexity, parameter uncertainty is the most common, e.g., marine ecological model \cite{Mateus15}, but stopped short, global sensitivity analysis of eutrophication model \cite{Estrada10}
-\item Challenges related to uncertainty - similar to degrees of freedom, identifiability definition from \cite{Brun01} and need to evaluate identifiability \cite{Fasham06}, \cite{Omlin01} did a similar analysis with freshwater biogeochem model
+\item Challenges related to uncertainty - similar to degrees of freedom, identifiability definition from \cite{Brun01} and need to evaluate identifiability \cite{Fasham06}, \cite{Omlin01} did a similar analysis with freshwater biogeochem model.
+Identifiability describes the ability to estimate a parameter in relation to variation among the remaining parameters.
+A parameter is identifiable if all parameters within the set can be uniquely estimated based on the observed data.
+Parameters that are unidentifiable typically produce similar model outputs for a given relative perturbation, i.e., the effect of altering one parameter can be undone by altering one or more other parameters.
+Model calibration will not converge for parameters sets that are unidentifiable.
 \end{enumerate}
@@
 This study describes a parameter sensitivity analysis to evaluate identifiability for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
-We evaluate a simple 1-dimensional unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
+We evaluate a simple \ac{oned} unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
 The study also provides a general framework for sensitivity analysis and parameter identifiability that can be used on similar mechanistic models.
@@
 The specific objectives are to \begin{inparaenum}[1\upshape)]
-\item identify the parameters that have the greatest influence on dissolved oxygen using local sensitivity analysis,
+\item identify the parameters that have the greatest influence on \ac{do} using local sensitivity analysis,
 \item quantify the identifiability of subsets of the total parameter space based on sensitivity,
@@
 
-Low concentrations of dissolved oxygen occur seasonally on the \ac{lcs} in the northern \ac{gom}.
+Low concentrations of \acl{do} occur seasonally on the \ac{lcs} in the northern \ac{gom}.
 These hypoxic events, defined as $<$2 mg L$^{-1}$ ($<$ 64 mmol m$^-3$ of O$_2$), occur in bottom waters and are caused by nutrient inputs from the \ac{marb} that drains a significant portion of the continental United States.
@@
 
-Three-dimensional numerical simulation models have been developed to better understand factors contributing to hypoxia and to predict the effects of management actions or climate scenarios on future patterns (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
+Three-dimensional numerical simulation models have been developed to describe factors contributing to hypoxia and to predict the effects of management actions or climate scenarios on future patterns (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
 This study evaluates a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia.
@@
 The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia dynamics using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
-The biogehmical component includes equations for 33 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.
-The model is run for a set period of time at a given time step using atmospheric and hydrological boundary conditions described in cites....
+The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.
+The model can be run for a set period of time at a given time step using atmospheric and hydrological boundary conditions described in \citet{Hodur97} and \citet{Lehrter13}.
 
-FishTank, parameters and parameter categories, how they compare to other models
+The core unit of \ac{cgem} is a \ac{oned} model called FishTank that implements the biogeochemical equations in \citet{Eldridge10}.
+This model acts as a standalone operational unit from the 3-D model that does not include any form of transport (i.e., advection, mixing, or surface flux) such that it can easily be applied to other hydrodynamic grids.
+Accordingly, the sensitivity and identifiability analysis described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
+The FishTank model provides estimates for the 36 state variables described above using a \ac{oned} parcel that is uniformly mixed.
+A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 (Table 1, \citet{Murrell14}).
+The FishTank model was executed from January 1\textsuperscript{st} to December \textsuperscript{st}, 2006 at a timestep of five minutes.
+
+Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton (up to six groups) and zooplankton (two groups) as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
+A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
+In addition to the initial conditions, a set of parameter values for each of the equations is also supplied at model execution.
+These parameters define relationships among fixed effects in the equations and represent ecological properties described by the model that influence hypoxia formation.
+Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert-based knowledge in absence of the former.
+The sensitivity of \ac{do} was estimated at each timestep from FishTank was evaluated in relation to 249 parameters that are included in the 108 equations.
+For simplicity in the discussion below, the parameters were grouped into one of six categories in relation to applicable equation: optics, phytoplankton, zooplankton, temperature, and organic matter.
+A full description of the equations and parameters is available as an appendix in \citepalias{LehrterIR}.
 
@@
 
-Methods from \cite{Reichert01,Soetaert10}
-
-Sensitivity of the model to parameter changes is evaluated using the difference in model results before and after perturbing each parameter value.
-Each parameter is perturbed by the same value as a percentage of the whole.
-The default value (as 1 + 1e-8 proportion, default value for `tiny` argument in `sensFun`).
-A sensitivity value $S$ is estimated for each time step $i$ given a set value for parameter $j$ as:
+The analysis focused on sensitivity of \ac{do} in the \ac{oned} model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
+A local sensitivity analysis was performed for each of the 249 parameters using a simple perturbation approach to evaluate the change in dissolved oyxgten from the original parameter values.
+The analyses relied exlusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10}.
+Each parameter was perturbed by 50\% of its original value and the model was executed to obtain an estimate of the effect on \ac{do}.
+For each perturbation, a sensitivity value $S$ was estimated for each time step $i$ given a set value for parameter $j$ as:
 
@@
 
-where the estimate depends on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
-The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y$, are set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
+\noindent where the estimate depended on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
+The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y$, were set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
 The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.
-The FME package summarizes sensitivity as $L1$ and $L2$ across the time series:
+Individual estimates for $S_{ij}$ were as $L1$ and $L2$ across the time series to obtained a single sensitivity value of \ac{do} in response to a change in parameter $j$:
 
@@
 
-The mean, minimum, and maximum $S_{ij}$ values for each parameter are also reported.
-In general, positive mean sensitivity estimates generally indicate that a parameter has a positive effect on the model results for a given increase in the parameter.
-However, the effect can change over time so a plot of the 'sensitivity function' should be viewed which shows the difference from the values of the response variable before and after changing a parameter value.
-Note that the perturbation factor in `sensFun` depends on the default value of each parameter such perturbations are not consistent for parameter values less than or greater than the perturbation factor.
-This can produce results that are inconsistent for different levels of perturbation.
-A custom function was keeps the perturbation factors constant regardless of the magnitude of the default values.
-Sensitiviy for each parameter using the custom function are estimated using the above equations from the FME package.
+The mean, minimum, and maximum $S_{ij}$ for each parameter were also evaluated.
+In general, positive mean sensitivity estimates suggested a parameter had a positive effect on \ac{do} for a given increase in the parameter, whereas the converse was true for negative sensitivity estimates.
+However, the effect of a parameter change may not be uniform over time such that $S_{ij}$ can change in magnitude and sign depending on the time step $i$.
+Time series of \ac{do} estimates before and after perturbation  were also evaluated to identify patterns not captured the summary statistics.
 All parameters that are considered 'sensitive' should be further evaluated by plotting the predictions before and after perturbation and across the total range of the parameter.
-
-Each parameter was perturbed by 50\% using `sensfun` to identify model sensitivity.  Parameters that produced different model results from the default values are shown below, by category.
-
-The parameters that have the greatest effect on the model by category (optics, organics, phytoplankton, zooplankton) are as follows.
-
-Plotting the raw values from the sensitivity analysis provides a visual assessment of changes.
+All parameters for each of the six equation categories (optics, phytoplankton, zooplankton, temperature, and organic matter) that had non-zero $L1$ or $L2$ were retained for identifiability analysis.
 
@@
 
-Identifiability describes the ability to estimate a parameter in relation to variation among the remaining parameters.
-A parameter is identifiable if all parameters within the set can be uniquely estimated based on the observed data.
-Parameters that are unidentifiable typically produce similar model outputs for a given relative perturbation, i.e., the effect of altering one parameter can be undone by altering one or more other parameters.
-Model calibration will not converge for parameters sets that are unidentifiable.
-Identifiability is estimated from the minimum eigenvector of the cross-product of a model's sensitivity matrix \citep{Brun01,Omlin01}:
+Identifiability of parameter subsets was estimated from the minimum eigenvector of the cross-product of a selected sensitivity matrix \citep{Brun01,Omlin01}:
 
@@
 \section{Results}
+
+\subsection{Local sensitivity analysis}
+
+The parameters that have the greatest effect on the model by category (optics, organics, phytoplankton, zooplankton) are as follows.
+
+Plotting the raw values from the sensitivity analysis provides a visual assessment of changes.
 

### 2016-06-27 ident_manu.tex
model descrip done in methods

@@
   \vspace{1in} 
-  \\ Version Date:   Fri Jun 24 16:57:50 2016 -0500
+  \\ Version Date:   Sun Jun 26 16:40:23 2016 -0500
 	}

### 2016-06-28 ident_manu.Rnw
methods draft done

@@
 %acronyms
-\acrodef{oned}[1-D]{one-dimensional}
+\acrodef{chla}[chl-\textit{a}]{chlorophyll \textit{a}}
 \acrodef{cgem}[CGEM]{Coastal General Ecosystem Model}
@@
 \acrodef{marb}[MARB]{Mississippi-Atchafalaya River Basin}
+\acrodef{oned}[1-D]{one-dimensional}
+\acrodef{par}[PAR]{photosynthetically active radiation}
 
@@
 
-The analysis focused on sensitivity of \ac{do} in the \ac{oned} model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
-A local sensitivity analysis was performed for each of the 249 parameters using a simple perturbation approach to evaluate the change in dissolved oyxgten from the original parameter values.
+The analysis focused on sensitivity of \ac{do} in the \ac{oned} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
+A local sensitivity analysis was performed for each of the 249 parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
 The analyses relied exlusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10}.
@@
 
-\begin{equation}
+\begin{equation} \label{sij}
 S_{ij} = \frac{\partial y_i}{\partial \Theta_j}\cdot\frac{w_{\Theta_j}}{w_{y_i}}
@@
 \noindent where the estimate depended on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
-The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y$, were set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
+The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y_i$, were set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
 The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.
-Individual estimates for $S_{ij}$ were as $L1$ and $L2$ across the time series to obtained a single sensitivity value of \ac{do} in response to a change in parameter $j$:
+Individual estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain a single sensitivity value of \ac{do} in response to a change in parameter $j$:
 
@@
 In general, positive mean sensitivity estimates suggested a parameter had a positive effect on \ac{do} for a given increase in the parameter, whereas the converse was true for negative sensitivity estimates.
-However, the effect of a parameter change may not be uniform over time such that $S_{ij}$ can change in magnitude and sign depending on the time step $i$.
-Time series of \ac{do} estimates before and after perturbation  were also evaluated to identify patterns not captured the summary statistics.
-All parameters that are considered 'sensitive' should be further evaluated by plotting the predictions before and after perturbation and across the total range of the parameter.
+However, the effect of a parameter change may not be uniform over time such that $S_{ij}$ can change in magnitude and sign depending on the location.
+Time series of \ac{do} estimates before and after perturbation were also evaluated to identify patterns not captured by the summary statistics.
 All parameters for each of the six equation categories (optics, phytoplankton, zooplankton, temperature, and organic matter) that had non-zero $L1$ or $L2$ were retained for identifiability analysis.
 
-\subsection{Identifiability}
+\subsection{Identifiability and selecting parameter subsets}
 
@@
 
-where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for a set of parameters in the sensitivity matrix $S$.
-Identifiability can be estimated for any combination of parameters for a model.
-Values less than 10-15 indicate parameters are generally identifiable.
-The FME package provides the `collin` function to estimate identifiability of output from the `sensFun`.
-For reasons described above, a custom function was created to determine identifiability from model residuals, where the residauls were based on a relative perturbation of the model parameters.
-A comparison of results of identifiability using the custom functions and those from the FME package were generally in agreement.
-Standard output from the identifiability function is shown below, where identifiability is displayed as a matrix with increasing combinations of subsets of the parameters.
+\noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for a set of parameters in a chosen sensitivity matrix $S$.
+The sensitivity functions are supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sij}) that describe deviations of predicted \ac{do} from the default parameter values.
+The sensitivity matrix $\hat{S}$ is first normalized by dividing by the square root of the summed residuals.
 
-The identifiability functions evaluate the ability to identify all subsets from pairwise to all parameters in the subset.
-As an example, the identifiability of pairwise combinations for each of the categories are shown below.
+The collinearity index $\gamma$ provides a measure of the linear dependence between sensitivity functions described above for subsets of parameters.
+Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning optimal values are inestimable given similar effects of the selected parameters on \ac{do}.
+Greater sensitivity of a state variable to a parameter subset parameters does not imply identifiability if the individual effects are similar.
+An intuitive interpretation of $\gamma$ is provided by \citet{Brun01} such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
+That is, $\gamma = 10$ suggests the relative change in \ac{do} for a selected parameter can be compensated for by 90\% with changes in the other parameters.
 
-Pairwise identifiability of the top two most sensitive parameters in each category is shown, first as a table showing all unique combinations from two to all parameters and second as a figure showing pairwise combinations.
+Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 249 included in the FishTank model.
+Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and identifability as it relates to optimization.
+An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given differences in parameter sensitivity and desired ecological categories of each parameter as they relate to the biogeochemical equations.
+For example, \cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., based on $n$ choose $k$ combinations equal to $n!/\left(k!\left(n-k\right)!\right)$).
+The number of unique combinations increases with the total parameters in the set and is also maximized for moderate selections (e.g., selecting half the total).
+For example, over 1e14 combinations are possible by selecting 25 parameters from a set of 50.
+Accordingly, parameter selection is complicated by differing sensitivity, identifiability, and the difficulty of choosing from many combinations.
 
-\subsection{Identifying subsets and testing calibration}
+A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above.
+These rulesets were developed with the assumption that parameters will be selected given preference for those with high sensitivity and identifability of subsets less than 15 was an acceptable threshold (e.g., 93\% accountability between parameters).
+Selection heurestics also recognized that parameter categories (i.e., optics, phytoplankton, zooplankton, temperature, organic matter) may have unequal preferences given questions of interest.
+In all selection scenarios, parameters were selected by decreasing sensitivity until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
+\item independent of parameter category,
+\item blocked within parameter category,
+\item or considering all categories equally
+\end{inparaenum}.  The selection rules produced seven subsets of parameters that could further be used to optimized model calibration for \ac{do}.
 
-Model calibration must consider the competing objectives of parameter inclusion and identifability.
-Estimating parameters for novel datasets increases model complexity and the ability to identify parameters decreases with the inclusion of parameters to estimate.
-The above analyses indicated that estimating all of the parameters was impossible because of redundancies in the the model output.
-Calibration to novel datasets should balance the competing objectives of identifiability while including parameters for which model output is most sensitive.
-The plots below show different scenarios of parameter inclusion for model calibration.
-Reading each plot from left to right can be interpreted as including additional parameters, where each parameter is ranked by relative sensitivity.
-The inset in each plot shows the identifiability of including parameters, up to a maximum where additional inclusion exceeds the identifability threshold of fifteen.
-The scenarios for including parameters all begin with the parameters that have the greatest effect on the model output.
-The inclusion of additional parameters depends on the scenario.
-The first scenario selected parameters by decreasing sensitivity within each category (i.e., four separate models calibrated for optics, organics, phytoplankton, or zooplankton), the second scenario selected parameters by sensitivity regardless of category, and the third scenario selects parameters by sensitivity with equal representation between categories.
-Boxes in each plot represent a unique parameter and the numbers in each box represent the relative rank of a parameter's sensitivity to the model output within each category.
-
-The following plots show identifiability with the addition of parameters.
+Finally, the above analyses were repeated for additional state variables estimated by FishTank to provide additional perspective on ecological dynamics that are relevant for hypoxia.
+In addition to \ac{do}, other state variables included \ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
+Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon ($OM1_A$, $OM2_A$), fecal pellets ($OM1_{fp}$, $OM2_{fp}$), river sources ($OM1_{rp}$, $OM2_{rp}$), and boundary conditions ($OM1_{bc}$, $OM2_{bc}$, see \citetalias{LehrterIR}).
 
@@
 Plotting the raw values from the sensitivity analysis provides a visual assessment of changes.
+
+The identifiability functions evaluate the ability to identify all subsets from pairwise to all parameters in the subset.
+As an example, the identifiability of pairwise combinations for each of the categories are shown below.
+
+Pairwise identifiability of the top two most sensitive parameters in each category is shown, first as a table showing all unique combinations from two to all parameters and second as a figure showing pairwise combinations.
+
+Reading each plot from left to right can be interpreted as including additional parameters, where each parameter is ranked by relative sensitivity.
+The inset in each plot shows the identifiability of including parameters, up to a maximum where additional inclusion exceeds the identifability threshold of fifteen.
+The scenarios for including parameters all begin with the parameters that have the greatest effect on the model output.
+The inclusion of additional parameters depends on the scenario.
+The first scenario selected parameters by decreasing sensitivity within each category (i.e., four separate models calibrated for optics, organics, phytoplankton, or zooplankton), the second scenario selected parameters by sensitivity regardless of category, and the third scenario selects parameters by sensitivity with equal representation between categories.
 
@@
 % figures
-<<echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
+<<combnex, echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
 The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 100 parameter sets are shown each with one through 100 total parameters.

### 2016-06-28 ident_manu.tex
methods draft done

@@
   \vspace{1in} 
-  \\ Version Date:   Sun Jun 26 16:40:23 2016 -0500
+  \\ Version Date:   Mon Jun 27 17:32:38 2016 -0500
 	}
@@
 
-{\centering \includegraphics[width=\textwidth]{figs/unnamed-chunk-3-1}
+{\centering \includegraphics[width=\textwidth]{figs/combnex-1}
 
@@
 Note that the number of unique combinations is shown as the natural-log.
-The same information is viewed differently in each plot.}\label{fig:unnamed-chunk-3}
+The same information is viewed differently in each plot.}\label{fig:combnex}
 \end{figure}

### 2016-06-28 ident_manu.Rnw
working on tables

@@
 \usepackage{bm}
-\usepackage{amsmath,amsfonts,amssymb,amsthm}
+% \usepackage{amsmath,amsfonts,amssymb,amsthm}
 % \usepackage{showlabels}
@@
 library(gridExtra)
+library(Hmisc)
 @
@@
 Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert-based knowledge in absence of the former.
-The sensitivity of \ac{do} was estimated at each timestep from FishTank was evaluated in relation to 249 parameters that are included in the 108 equations.
-For simplicity in the discussion below, the parameters were grouped into one of six categories in relation to applicable equation: optics, phytoplankton, zooplankton, temperature, and organic matter.
+The sensitivity of \ac{do} was estimated at each timestep from FishTank in relation to 249 parameters that are included in the 108 equations.
+For simplicity in the discussion below, the parameters were grouped into one of six categories in relation to applicable equations: optics, phytoplankton, zooplankton, temperature, and organic matter.
 A full description of the equations and parameters is available as an appendix in \citepalias{LehrterIR}.
-
 \subsection{Local sensitivity analysis}
@@
 
-\begin{equation} \label{sij}
+\begin{equation} \label{sijeqn}
 S_{ij} = \frac{\partial y_i}{\partial \Theta_j}\cdot\frac{w_{\Theta_j}}{w_{y_i}}
@@
 The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.
-Individual estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain a single sensitivity value of \ac{do} in response to a change in parameter $j$:
+Estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain individual sensitivity values of \ac{do} in response to a change in parameter $j$:
 
@@
 
-The mean, minimum, and maximum $S_{ij}$ for each parameter were also evaluated.
-In general, positive mean sensitivity estimates suggested a parameter had a positive effect on \ac{do} for a given increase in the parameter, whereas the converse was true for negative sensitivity estimates.
+In general, positive sensitivity estimates suggested a parameter had a positive effect on \ac{do} for a given increase in the parameter, whereas the converse was true for negative sensitivity estimates.
 However, the effect of a parameter change may not be uniform over time such that $S_{ij}$ can change in magnitude and sign depending on the location.
@@
 \begin{equation}
-\gamma = \frac{1} {\sqrt{ \min \left(\rm{EV}[\hat{S}^\intercal \hat{S}]\right)}}
+\gamma = \frac{1} {\sqrt{ \min \left(\rm{EV}[\mathit{\hat{S}}^\top \mathit{\hat{S}}]\right)}}
 \end{equation}
@@
 \noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for a set of parameters in a chosen sensitivity matrix $S$.
-The sensitivity functions are supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sij}) that describe deviations of predicted \ac{do} from the default parameter values.
-The sensitivity matrix $\hat{S}$ is first normalized by dividing by the square root of the summed residuals.
+The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that describes deviations of predicted \ac{do} from the default parameter values.
+The matrix $\hat{S}$ was first normalized by dividing by the square root of the summed residuals\citep{Omlin01,Soetaert10}.
 
@@
 Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning optimal values are inestimable given similar effects of the selected parameters on \ac{do}.
-Greater sensitivity of a state variable to a parameter subset parameters does not imply identifiability if the individual effects are similar.
+Greater sensitivity of a state variable to parameters within a subset does not imply identifiability if the individual effects are similar.
 An intuitive interpretation of $\gamma$ is provided by \citet{Brun01} such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
@@
 The number of unique combinations increases with the total parameters in the set and is also maximized for moderate selections (e.g., selecting half the total).
-For example, over 1e14 combinations are possible by selecting 25 parameters from a set of 50.
+For example, over 10$^14$ combinations are possible by selecting 25 parameters from a set of 50.
 Accordingly, parameter selection is complicated by differing sensitivity, identifiability, and the difficulty of choosing from many combinations.
@@
 A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above.
-These rulesets were developed with the assumption that parameters will be selected given preference for those with high sensitivity and identifability of subsets less than 15 was an acceptable threshold (e.g., 93\% accountability between parameters).
+These rulesets were developed with the assumption that parameters will be selected given preference for those with high sensitivity and identifability based on $\gamma < 15$ was an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
 Selection heurestics also recognized that parameter categories (i.e., optics, phytoplankton, zooplankton, temperature, organic matter) may have unequal preferences given questions of interest.
-In all selection scenarios, parameters were selected by decreasing sensitivity until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
+In all selection scenarios, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
 \item independent of parameter category,
@@
 \item or considering all categories equally
-\end{inparaenum}.  The selection rules produced seven subsets of parameters that could further be used to optimized model calibration for \ac{do}.
+\end{inparaenum}.  The selection rules produced seven subsets of parameters that could further be used to optimize model calibration for \ac{do}.
 
-Finally, the above analyses were repeated for additional state variables estimated by FishTank to provide additional perspective on ecological dynamics that are relevant for hypoxia.
+Finally, the above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
 In addition to \ac{do}, other state variables included \ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
-Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon ($OM1_A$, $OM2_A$), fecal pellets ($OM1_{fp}$, $OM2_{fp}$), river sources ($OM1_{rp}$, $OM2_{rp}$), and boundary conditions ($OM1_{bc}$, $OM2_{bc}$, see \citetalias{LehrterIR}).
+Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
 
@@
 % figures
+
 <<combnex, echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
@@
 
+\clearpage
+%%%%%%
+% tables
+
+<<optsens, eval = T>>=
+
+data(sens_ests)
+data(sens_ests_cat)
+
+categ <- 'Optics'
+
+labs <- parcats2()[[categ]] %>% 
+  data.frame %>% 
+  rename(Parameter = shrt)
+
+totab <- filter(sens_ests_cat, Category %in% categ) %>% 
+  select(Parameter) %>% 
+  left_join(., sens_ests$sens, by = 'Parameter') %>% 
+  left_join(., labs, by = 'Parameter') %>% 
+  select(Parameter, lngs, vals, L1, L2) %>% 
+  arrange(-L1) %>% 
+  mutate(
+    Parameter = paste0('\\textit{', gsub('_[0-9]$', '', Parameter), '}'),
+    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
+    lngs = gsub('_', '\\\\_', lngs), 
+    L1 = sapply(L1, scinot), 
+    L2 = sapply(L2, scinot)
+  ) %>% 
+  rename(
+    Description = lngs, 
+    Value = vals
+  )
+
+# final table formatting
+Parameter <- totab$Parameter
+totab <- totab[,-1]
+cap.val<-'Test'
+
+latex( 
+  totab,
+  file = '',
+  rowlabel = 'Parameter',
+  caption = cap.val,
+  caption.loc = 'top',
+  # rgroup = segs,
+  # n.rgroup = c(1, rep(4, 2)),
+#   cgroup = vars,
+#   n.cgroup = c(2, 2),
+  rowname = Parameter,
+  label = 'tab:optsens'
+  )
+
+@
+
 \end{document}

### 2016-06-28 ident_manu.tex
working on tables

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Jun 27 17:32:38 2016 -0500
+  \\ Version Date:   Tue Jun 28 11:58:04 2016 -0500
 	}
@@
 % figures
+
 \begin{figure}[!ht]
@@
 
+\clearpage
+%%%%%%
+% tables
+
+%latex.default(totab, file = "", rowlabel = "Parameter", caption = cap.val,     caption.loc = "top", rowname = Parameter, label = "tab:optsens")%
+\begin{table}[!tbp]
+\caption{Test\label{tab:optsens}} 
+\begin{center}
+\begin{tabular}{llrll}
+\hline\hline
+\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Description}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+\textit{astar490}&Chla specific absorption at 490 nm&$0.0375$&$1.64$&$8.64$\tabularnewline
+\textit{astarOMA}&OM\_A specific absorption at 490 nm&$0.1000$&$2.29\times 10^{-2}$&$9.52\times 10^{-2}$\tabularnewline
+\textit{astarOMZ}&OM\_Z specific absorption at 490 nm&$0.1000$&$5.65\times 10^{-3}$&$1.42\times 10^{-2}$\tabularnewline
+\textit{Kcdom}&AOP, light attenuation due to CDOM&$0.0010$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
+\hline
+\end{tabular}\end{center}
+
+\end{table}
+
 \end{document}

### 2016-06-28 R/funcs.R

@@ -1,0 +1,825 @@
+# alternative list structure for parameter categories
+parcats2 <- function(){
+  
+  Optics = list(
+    shrt = c('Kw_1', 
+      'Kcdom_1', 
+      'Kspm_1', 
+      'Kchla_1',
+      'astar490_1',
+      'aw490_1',
+      'astarOMA_1',
+      'astarOMZ_1',
+      'astarOMR_1',
+      'astarOMbC_1',
+      'sink CDOM_1'
+      ),
+    lngs = c(
+      'Kw: AOP, light attenuation due to water',
+      'Kcdom: AOP, light attenuation due to CDOM',
+      'Kspm: AOP, light attenuation due to SPM', 
+      'Kchla: AOP, light attenuation due to chla ',
+      'astar490: Chla specific absorption at 490 nm',
+      'aw490: seawater absorption at 490 nm',
+      'astarOMA: OM_A specific absorption at 490 nm',
+      'astarOMZ: OM_Z specific absorption at 490 nm',
+      'astarOMR: OM_R specific absorption at 490 nm',
+      'astarOMBC: OM_BC specific absorption at 490 nm',
+      'sink CDOM: sinking rate'
+      ),
+    vals = c(
+      0.146,
+      0.001,
+      0.029,
+      0.024,
+      0.0375,
+      0.015,
+      0.1,
+      0.1,
+      0.1,
+      0.1,
+      0
+    )
+  )
+  
+  Temperature = list(
+    shrt = c(
+      'Tref(nospA+nospZ)_1',
+      'Tref(nospA+nospZ)_2',
+      'Tref(nospA+nospZ)_3',
+      'Tref(nospA+nospZ)_4',
+      'Tref(nospA+nospZ)_5',
+      'Tref(nospA+nospZ)_6',
+      'Tref(nospA+nospZ)_7',
+      'Tref(nospA+nospZ)_8',
+      'KTg1(nospA+nospZ)_1',
+      'KTg1(nospA+nospZ)_2',
+      'KTg1(nospA+nospZ)_3',
+      'KTg1(nospA+nospZ)_4',
+      'KTg1(nospA+nospZ)_5',
+      'KTg1(nospA+nospZ)_6',
+      'KTg1(nospA+nospZ)_7',
+      'KTg1(nospA+nospZ)_8',
+      'KTg2(nospA+nospZ)_1',
[…]

### 2016-06-29 R/funcs.R
parcats2 as df

@@ -1,7 +1,8 @@
 # alternative list structure for parameter categories
-parcats2 <- function(){
+parcats2 <- function(as_df = FALSE){
   
   Optics = list(
+    cats = 'Optics',
     shrt = c('Kw_1', 
       'Kcdom_1', 
       'Kspm_1', 
@@ -43,6 +44,7 @@ parcats2 <- function(){
   )
   
   Temperature = list(
+    cats = 'Temperature',
     shrt = c(
       'Tref(nospA+nospZ)_1',
       'Tref(nospA+nospZ)_2',
@@ -148,6 +150,7 @@ parcats2 <- function(){
   )
   
   Phytoplankton = list(
+    cats = 'Phytoplankton',
     shrt = c(
       'ediblevector(Z1)_1',
       'ediblevector(Z1)_2',
@@ -625,6 +628,7 @@ parcats2 <- function(){
   )
   
   Zooplankton = list(
+    cats = 'Zooplankton',
     shrt = c(
       'Zeffic_1',
       'Zeffic_2',
@@ -700,6 +704,7 @@ parcats2 <- function(){
   )
   
   `Organic Matter` = list(
+    cats = 'Organic Matter',
     shrt = c(
       'KG1_1',
       'KG2_1',
@@ -795,15 +800,26 @@ parcats2 <- function(){
       )
   )
   
+  # list
   out <- list(Optics = Optics, Temperature = Temperature, Phytoplankton = Phytoplankton, Zooplankton = Zooplankton, `Organic Matter` = `Organic Matter`)
+  
+  # return as data frame if T
+  if(as_df){
+    
+    out <- lapply(out, data.frame)
+    out <- do.call('rbind', out)
+    row.names(out) <- 1:nrow(out)
+    
+    return(out)
+  }
   
   return(out)
   
 }
 
-
 ##
 # scientific notation from R to LaTeX
+# from https://dankelley.github.io/r/2015/03/22/scinot.html
 scinot <- function(x, digits=2, showDollar=TRUE)
 {
     sign <- ""

### 2016-06-29 ident_manu.Rnw
sensitivity tables done

@@
 
-\begin{equation}
+\begin{equation} \label{l1}
 L1 = \sum|S_{ij}|/n
 \end{equation}
-\begin{equation}
+\begin{equation} \label{l2}
 L2 = \sqrt{\sum\left(S_{ij}^2\right)|/n}
@@
 \section{Results}
+
+\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}
 
@@
 
-<<optsens, eval = T>>=
+<<optsens, eval = T, cache = F>>=
+senstab1('Optics', 'optsens')
+@
 
-data(sens_ests)
-data(sens_ests_cat)
+<<tempsens, eval = T, cache = F >>=
+senstab2('Temperature', 'tempsens')
+@
 
-categ <- 'Optics'
+<<phytosens, eval = T, cache = F>>=
+# data(sens_ests_cat)
+# tmp <- filter(sens_ests_cat, Category == 'Phytoplankton')
+# quantile(tmp$error)
+senstab2('Phytoplankton', 'phytosens', sub = 0.59, sub.txt = 'Parameters less than the 75\\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.')
+@
 
-labs <- parcats2()[[categ]] %>% 
-  data.frame %>% 
-  rename(Parameter = shrt)
+<<zoopsens, eval = T, cache = F>>=
+senstab2('Zooplankton', 'zoopsens')
+@
 
-totab <- filter(sens_ests_cat, Category %in% categ) %>% 
-  select(Parameter) %>% 
-  left_join(., sens_ests$sens, by = 'Parameter') %>% 
-  left_join(., labs, by = 'Parameter') %>% 
-  select(Parameter, lngs, vals, L1, L2) %>% 
-  arrange(-L1) %>% 
-  mutate(
-    Parameter = paste0('\\textit{', gsub('_[0-9]$', '', Parameter), '}'),
-    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
-    lngs = gsub('_', '\\\\_', lngs), 
-    L1 = sapply(L1, scinot), 
-    L2 = sapply(L2, scinot)
-  ) %>% 
-  rename(
-    Description = lngs, 
-    Value = vals
-  )
-
-# final table formatting
-Parameter <- totab$Parameter
-totab <- totab[,-1]
-cap.val<-'Test'
-
-latex( 
-  totab,
-  file = '',
-  rowlabel = 'Parameter',
-  caption = cap.val,
-  caption.loc = 'top',
-  # rgroup = segs,
-  # n.rgroup = c(1, rep(4, 2)),
-#   cgroup = vars,
-#   n.cgroup = c(2, 2),
-  rowname = Parameter,
-  label = 'tab:optsens'
-  )
-
+<<omsens, eval = T, cache = F>>=
+senstab1('Organic Matter', 'omsens')
 @

### 2016-06-29 ident_manu.tex
sensitivity tables done

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Jun 28 11:58:04 2016 -0500
+  \\ Version Date:   Wed Jun 29 09:01:37 2016 -0500
 	}
@@
 
-%latex.default(totab, file = "", rowlabel = "Parameter", caption = cap.val,     caption.loc = "top", rowname = Parameter, label = "tab:optsens")%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
 \begin{table}[!tbp]
-\caption{Test\label{tab:optsens}} 
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of optics parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.\label{tab:optsens}}
 \begin{center}
-\begin{tabular}{llrll}
+\begin{tabular}{lllll}
 \hline\hline
-\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Description}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
 \hline
-\textit{astar490}&Chla specific absorption at 490 nm&$0.0375$&$1.64$&$8.64$\tabularnewline
-\textit{astarOMA}&OM\_A specific absorption at 490 nm&$0.1000$&$2.29\times 10^{-2}$&$9.52\times 10^{-2}$\tabularnewline
-\textit{astarOMZ}&OM\_Z specific absorption at 490 nm&$0.1000$&$5.65\times 10^{-3}$&$1.42\times 10^{-2}$\tabularnewline
-\textit{Kcdom}&AOP, light attenuation due to CDOM&$0.0010$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
+Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$1.64$&$8.64$\tabularnewline
+OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$&$0.1$\tabularnewline
+OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$0.01$&$0.01$\tabularnewline
+AOP, light attenuation due to CDOM&\textit{Kcdom}&$0$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
 \hline
-\end{tabular}\end{center}
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.
+Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+{Optimum temperature for growth(C)}&&&\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{P4}$}&$17$&$2.9$&$22.95$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{Z2}$}&$26$&$0.18$&$2.59$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{P5}$}&$26$&$0.17$&$0.72$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{P2}$}&$22$&$0.16$&$0.82$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{Z1}$}&$22$&$0.16$&$0.33$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{P3}$}&$17$&$0.14$&$0.78$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{P1}$}&$22$&$0.12$&$0.29$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of phytoplankton parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.
+Subscripts show the phytoplankton or zooplankton group that applies for the parameter.
+Parameters less than the 75\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.\label{tab:phytosens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+{coefficient for non-limiting nutrient}&&&\tabularnewline
+~~\textit{aN$_{P1}$}&$1$&$2.7$&$47.26$\tabularnewline
+~~\textit{aN$_{P3}$}&$1$&$0.66$&$3.16$\tabularnewline
+\hline
+{half-saturation constant for N}&&&\tabularnewline
+~~\textit{Kn$_{P3}$}&$5.93$&$1.15$&$9.22$\tabularnewline
+~~\textit{Kn$_{P4}$}&$1.13$&$0.62$&$2.5$\tabularnewline
+\hline
+{initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
+~~\textit{alpha$_{P4}$}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
+~~\textit{alpha$_{P3}$}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
+~~\textit{alpha$_{P5}$}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
+\hline
+{minimum N cell-quota}&&&\tabularnewline
+~~\textit{QminN$_{P3}$}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
+~~\textit{QminN$_{P4}$}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
+~~\textit{QminN$_{P1}$}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
+\hline
+{mortality coefficient}&&&\tabularnewline
+~~\textit{mA$_{P3}$}&$0.03$&$2.98$&$14.34$\tabularnewline
+~~\textit{mA$_{P4}$}&$0.11$&$1.35$&$7.04$\tabularnewline
+\hline
+{N-uptake rate measured at umax}&&&\tabularnewline
+~~\textit{vmaxN$_{P5}$}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
+~~\textit{vmaxN$_{P4}$}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
+~~\textit{vmaxN$_{P3}$}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
+~~\textit{vmaxN$_{P1}$}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
+\hline
+{P-uptake rate measured at umax}&&&\tabularnewline
+~~\textit{vmaxP$_{P3}$}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
+~~\textit{vmaxP$_{P1}$}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
+\hline
+{phytoplankton basal respiration coefficient}&&&\tabularnewline
+~~\textit{respb$_{P4}$}&$0.02$&$3.1$&$26.48$\tabularnewline
+~~\textit{respb$_{P3}$}&$0.02$&$2.15$&$6.35$\tabularnewline
+~~\textit{respb$_{P5}$}&$0.02$&$0.81$&$8.61$\tabularnewline
+\hline
+{phytoplankton carbon/cell}&&&\tabularnewline
+~~\textit{Qc$_{P1}$}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
+~~\textit{Qc$_{P3}$}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
+~~\textit{Qc$_{P2}$}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
+~~\textit{Qc$_{P4}$}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
+\hline
+{phytoplankton growth respiration coefficient}&&&\tabularnewline
+~~\textit{respg$_{P4}$}&$0.1$&$0.98$&$7.37$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.
+Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:zoopsens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+{assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
+~~\textit{Zeffic$_{P1}$}&$0.4$&$0.23$&$0.55$\tabularnewline
+~~\textit{Zeffic$_{P2}$}&$0.4$&$0.21$&$0.75$\tabularnewline
+\hline
+{half saturation coefficient for grazing}&&&\tabularnewline
+~~\textit{ZKa$_{P1}$}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
+~~\textit{ZKa$_{P2}$}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
+\hline
+{maximum growth rate of zooplankton}&&&\tabularnewline
+~~\textit{Zumax$_{P2}$}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
+~~\textit{Zumax$_{P1}$}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
+\hline
+{proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
+~~\textit{Zslop$_{P1}$}&$0.25$&$0.12$&$0.33$\tabularnewline
+\hline
+{Zooplankton biomass-dependent respiration factor}&&&\tabularnewline
+~~\textit{Zrespb$_{P1}$}&$0.1$&$0.45$&$3.02$\tabularnewline
+~~\textit{Zrespb$_{P2}$}&$0.42$&$0.09$&$1.05$\tabularnewline
+\hline
+{zooplankton carbon/individual}&&&\tabularnewline
+~~\textit{ZQc$_{P2}$}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
+~~\textit{ZQc$_{P1}$}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
+\hline
+{Zooplankton growth-dependent respiration factor}&&&\tabularnewline
+~~\textit{Zrespg$_{P1}$}&$0.2$&$0.24$&$3.19$\tabularnewline
+~~\textit{Zrespg$_{P2}$}&$0.3$&$0.12$&$0.31$\tabularnewline
+\hline
+{Zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
+~~\textit{Zm$_{P2}$}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
+~~\textit{Zm$_{P1}$}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
+\hline
+{zooplankton nitrogen/individual}&&&\tabularnewline
+~~\textit{ZQn$_{P1}$}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
+~~\textit{ZQn$_{P2}$}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
+\hline
+{zooplankton phosphorus/individual}&&&\tabularnewline
+~~\textit{ZQp$_{P2}$}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
+~~\textit{ZQp$_{P1}$}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of organic matter parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.\label{tab:omsens}}
+\begin{center}
+\begin{tabular}{lllll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+rate constant for nitrification&\textit{k11}&$5$&$2.11$&$16.1$\tabularnewline
+O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.91$&$11.76$\tabularnewline
+turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.49$&$6.83$\tabularnewline
+turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.37$&$3.46$\tabularnewline
+half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.24$&$7.98$\tabularnewline
+half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.56$&$1.92$\tabularnewline
+decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.01$&$0.03$\tabularnewline
+\hline
+\end{tabular}\end{center}}
 

### 2016-06-29 R/funcs.R

@@ -817,18 +817,23 @@ parcats2 <- function(as_df = FALSE){
   
 }
 
-##
+######
 # scientific notation from R to LaTeX
+# x is numeric to convert
+# pow is minimum exponent (positive or negative) to use for notation
+# digits numeric for rounding
+# showdollar logical if output is enclosed in dollar for latex
 # from https://dankelley.github.io/r/2015/03/22/scinot.html
-scinot <- function(x, digits=2, showDollar=TRUE)
+scinot <- function(x, pow = 3, digits=2, showDollar=TRUE)
 {
+  
     sign <- ""
     if (x < 0) {
         sign <- "-"
         x <- -x
     }
     exponent <- floor(log10(x))
-    if (exponent) {
+    if (exponent & abs(exponent) > pow) {
         xx <- round(x / 10^exponent, digits=digits)
         e <- paste("\\times 10^{", as.integer(exponent), "}", sep="")
     } else {
@@ -839,3 +844,126 @@ scinot <- function(x, digits=2, showDollar=TRUE)
     else paste(sign, xx, e, sep="")
 }
 
+######
+# function for sensitivity tables, no phyto, zoop groupings
+senstab1 <- function(categ, tablab, tabsize = 'normalsize'){
+  
+  library(Hmisc)
+  library(dplyr)
+  library(tidyr)
+  
+  load(file = 'data/sens_ests_cat.RData')
+  load(file = 'data/sens_ests.RData')
+  
+  labs <- parcats2()[[categ]] %>% 
+    data.frame %>% 
+    rename(Parameter = shrt)
+  
+  totab <- filter(sens_ests_cat, Category %in% categ) %>% 
+    select(Parameter) %>% 
+    left_join(., sens_ests$sens, by = 'Parameter') %>% 
+    left_join(., labs, by = 'Parameter') %>% 
+    select(lngs, Parameter, vals, L1, L2) %>% 
+    arrange(-L1) %>% 
+    mutate(
+      Parameter = paste0('\\textit{', gsub('_[0-9]$', '', Parameter), '}'),
+      lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
+      lngs = gsub('_', '', lngs), 
+      vals = sapply(vals, scinot),
+      L1 = sapply(L1, scinot), 
+      L2 = sapply(L2, scinot)
+    ) %>% 
+    rename(
+      Description = lngs, 
+      Value = vals
+    )
+
+  # final table formatting
[…]

### 2016-06-29 ident_manu.Rnw
fig 2 added

@@
 \usepackage{bm}
-% \usepackage{amsmath,amsfonts,amssymb,amsthm}
+\usepackage{fixltx2e}
 % \usepackage{showlabels}
@@
 library(Hmisc)
+library(ncdf4)
 @
@@
 
+% combination example
 <<combnex, echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
@@
 Note that the number of unique combinations is shown as the natural-log.
-The same information is viewed differently in each plot.', fig.height = 5, fig.width = 10, out.width = '\\textwidth'>>=
+The same information is viewed differently in each plot.', fig.height = 5, fig.width = 5, out.width = '0.6\\textwidth'>>=
 
@@
 pal <- 'RdYlGn'
-
-p1 <- ggplot(toplo, aes(x = sels, y = combs, group = numparms, colour = numparms)) + 
-  geom_line() +
-  # geom_point() + 
-  theme_minimal() + 
-  scale_colour_distiller(palette = pal, 
-    guide = guide_legend(title = 'Total number of\nparameters in set')) +
-  scale_x_continuous('Number of parameters selected from total', expand = c(0, 0)) + 
-  scale_y_continuous('Number of unique parameter combinations, log-scale', expand = c(0, 0)) + 
-  theme(legend.position = 'top')
+# 
+# p1 <- ggplot(toplo, aes(x = sels, y = combs, group = numparms, colour = numparms)) + 
+#   geom_line() +
+#   # geom_point() + 
+#   theme_minimal() + 
+#   scale_colour_distiller(palette = pal, 
+#     guide = guide_legend(title = 'Total number of\nparameters in set')) +
+#   scale_x_continuous('Number of parameters selected from total', expand = c(0, 0)) + 
+#   scale_y_continuous('Number of unique parameter combinations, log-scale', expand = c(0, 0)) + 
+#   theme(legend.position = 'top')
 
@@
 
-grid.arrange(p1, p2, ncol = 2)
+# grid.arrange(p1, p2, ncol = 2)
+p2
+@
+
+% sensitivity example of top
+<<sensplo, fig.cap = 'Sensitivity of \\ac{do} to parameter changes.
+Each solid line shows the parameter within each category that had the largest effect on \\ac{do} with a 50\\% change from the default value.
+The dashed line shows \\ac{do} holding all parameters at their default values.
+The bottom plot shows the estimated \\ac{do} as a difference from the default.', fig.height = 5.5, fig.width = 8, echo = F, cache = TRUE>>=
+load(file = 'data/sens_ests.RData')
+load(file = 'data/sens_ests_cat.RData')
+
+toeval <- group_by(sens_ests_cat, Category) %>% 
+  filter(error == max(error)) %>% 
+  arrange(error) %>% 
+  data.frame
+
+toeval <- toeval$Parameter %>% 
+  as.character
+
+toplo <- filter(sens_ests$raw, Parameter %in% toeval) %>% 
+  mutate(
+    diffest = Estimate - default,
+    time = as.POSIXct(time, origin = as.POSIXct('2002-01-01 0:0', tz = "GMT"), tz = 'GMT'),
+    time = as.Date(time)
+  )
+
+ylab <- expression(paste(O[2], ' (mmol ', m^-3, ')'))
+colset <- 'Set2'
+lnsz <- 1
+alph <- 0.8
+
+leglabs <- list(
+  expression(atop('Optics', italic(astar490))),
+  expression(atop('Organic Matter', italic('k11'))),
+  expression(atop('Phytoplankton', italic(Qc[italic('p1')]))),
+  expression(atop('Temperature', italic(Tref(nospA+nospZ)[italic('p4')]))),
+  expression(atop('Zooplankton', italic(Zka[italic('p1')])))
+  )
+
+p1 <- ggplot(toplo, aes(x = time, y = Estimate, group = Parameter, colour = Parameter)) + 
+  geom_line(aes(y = default), colour = 'black', linetype = 'dashed') + 
+  geom_line(size = lnsz, alpha = alph) + 
+  theme_minimal() +
+  scale_colour_brewer(palette = colset, 
+    labels = leglabs
+    ) + 
+  scale_y_continuous(ylab) + 
+  theme(
+    legend.position = 'top',
+    axis.text.x = element_blank(), 
+    axis.title.x = element_blank(),
+    axis.line.x = element_line(), 
+    axis.line.y = element_line()
+    )
+
+p2 <- ggplot(toplo, aes(x = time, y = diffest, group = Parameter, colour = Parameter)) + 
+  geom_hline(yintercept = 0, linetype = 'dashed') +
+  geom_line(size = lnsz, alpha = alph) + 
+  theme_minimal() +
+  scale_colour_brewer(palette = colset) + 
+  scale_y_continuous('Difference') + 
+  theme(
+    legend.position = 'none',
+    axis.title.x = element_blank(),
+    axis.line.x = element_line(), 
+    axis.line.y = element_line()
+    )
+
+# align widths of plots in first column, first two
+pA <- ggplot_gtable(ggplot_build(p1))
+pB <- ggplot_gtable(ggplot_build(p2))
+maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3])
+
+# Set the widths
+pA$widths[2:3] <- maxWidth
+pB$widths[2:3] <- maxWidth
+
+grid.arrange(pA, pB, ncol = 1, heights = c(1, 0.85))
 @

### 2016-06-29 ident_manu.tex
fig 2 added

--- 2016-06-28 ident_manu.tex
@@
   \vspace{1in} 
-  \\ Version Date:   Tue Jun 28 11:58:04 2016 -0500
+  \\ Version Date:   Wed Jun 29 14:50:46 2016 -0500
 	}
@@
 
+\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}
+
 \subsection{Local sensitivity analysis}
@@
 
+% combination example
 \begin{figure}[!ht]
 
-{\centering \includegraphics[width=\textwidth]{figs/combnex-1}
+{\centering \includegraphics[width=0.6\textwidth]{figs/combnex-1}
 
@@
 
+% sensitivity example of top
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\maxwidth]{figs/sensplo-1}
+
+}
+
+\caption{Sensitivity of \ac{do} to parameter changes.
+Each solid line shows the parameter within each category that had the largest effect on \ac{do} with a 50\% change from the default value.
+The dashed line shows \ac{do} holding all parameters at their default values.
+The bottom plot shows the estimated \ac{do} as a difference from the default.}\label{fig:sensplo}
+\end{figure}
+
 \clearpage
@@
 
-%latex.default(totab, file = "", rowlabel = "Parameter", caption = cap.val,     caption.loc = "top", rowname = Parameter, label = "tab:optsens")%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
 \begin{table}[!tbp]
-\caption{Test\label{tab:optsens}} 
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of optics parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.\label{tab:optsens}}
 \begin{center}
-\begin{tabular}{llrll}
+\begin{tabular}{lllll}
 \hline\hline
-\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Description}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
 \hline
-\textit{astar490}&Chla specific absorption at 490 nm&$0.0375$&$1.64$&$8.64$\tabularnewline
-\textit{astarOMA}&OM\_A specific absorption at 490 nm&$0.1000$&$2.29\times 10^{-2}$&$9.52\times 10^{-2}$\tabularnewline
-\textit{astarOMZ}&OM\_Z specific absorption at 490 nm&$0.1000$&$5.65\times 10^{-3}$&$1.42\times 10^{-2}$\tabularnewline
-\textit{Kcdom}&AOP, light attenuation due to CDOM&$0.0010$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
+Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$1.64$&$8.64$\tabularnewline
+OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$&$0.1$\tabularnewline
+OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$0.01$&$0.01$\tabularnewline
+AOP, light attenuation due to CDOM&\textit{Kcdom}&$0$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
 \hline
-\end{tabular}\end{center}
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.
+Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+{Optimum temperature for growth(C)}&&&\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P4}}&$17$&$2.9$&$22.95$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{Z2}}&$26$&$0.18$&$2.59$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P5}}&$26$&$0.17$&$0.72$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P2}}&$22$&$0.16$&$0.82$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{Z1}}&$22$&$0.16$&$0.33$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P3}}&$17$&$0.14$&$0.78$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P1}}&$22$&$0.12$&$0.29$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of phytoplankton parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.
+Subscripts show the phytoplankton or zooplankton group that applies for the parameter.
+Parameters less than the 75\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.\label{tab:phytosens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+{coefficient for non-limiting nutrient}&&&\tabularnewline
+~~\textit{aN\textsubscript{P1}}&$1$&$2.7$&$47.26$\tabularnewline
+~~\textit{aN\textsubscript{P3}}&$1$&$0.66$&$3.16$\tabularnewline
+\hline
+{half-saturation constant for N}&&&\tabularnewline
+~~\textit{Kn\textsubscript{P3}}&$5.93$&$1.15$&$9.22$\tabularnewline
+~~\textit{Kn\textsubscript{P4}}&$1.13$&$0.62$&$2.5$\tabularnewline
+\hline
+{initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
+~~\textit{alpha\textsubscript{P4}}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
+~~\textit{alpha\textsubscript{P3}}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
+~~\textit{alpha\textsubscript{P5}}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
+\hline
+{minimum N cell-quota}&&&\tabularnewline
+~~\textit{QminN\textsubscript{P3}}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
+~~\textit{QminN\textsubscript{P4}}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
+~~\textit{QminN\textsubscript{P1}}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
+\hline
+{mortality coefficient}&&&\tabularnewline
+~~\textit{mA\textsubscript{P3}}&$0.03$&$2.98$&$14.34$\tabularnewline
+~~\textit{mA\textsubscript{P4}}&$0.11$&$1.35$&$7.04$\tabularnewline
+\hline
+{N-uptake rate measured at umax}&&&\tabularnewline
+~~\textit{vmaxN\textsubscript{P5}}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
+~~\textit{vmaxN\textsubscript{P4}}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
+~~\textit{vmaxN\textsubscript{P3}}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
+~~\textit{vmaxN\textsubscript{P1}}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
+\hline
+{P-uptake rate measured at umax}&&&\tabularnewline
+~~\textit{vmaxP\textsubscript{P3}}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
+~~\textit{vmaxP\textsubscript{P1}}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
+\hline
+{phytoplankton basal respiration coefficient}&&&\tabularnewline
+~~\textit{respb\textsubscript{P4}}&$0.02$&$3.1$&$26.48$\tabularnewline
+~~\textit{respb\textsubscript{P3}}&$0.02$&$2.15$&$6.35$\tabularnewline
+~~\textit{respb\textsubscript{P5}}&$0.02$&$0.81$&$8.61$\tabularnewline
+\hline
+{phytoplankton carbon/cell}&&&\tabularnewline
+~~\textit{Qc\textsubscript{P1}}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
+~~\textit{Qc\textsubscript{P3}}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
+~~\textit{Qc\textsubscript{P2}}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
+~~\textit{Qc\textsubscript{P4}}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
+\hline
+{phytoplankton growth respiration coefficient}&&&\tabularnewline
+~~\textit{respg\textsubscript{P4}}&$0.1$&$0.98$&$7.37$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.
+Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:zoopsens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+{assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
+~~\textit{Zeffic\textsubscript{P1}}&$0.4$&$0.23$&$0.55$\tabularnewline
+~~\textit{Zeffic\textsubscript{P2}}&$0.4$&$0.21$&$0.75$\tabularnewline
+\hline
+{half saturation coefficient for grazing}&&&\tabularnewline
+~~\textit{ZKa\textsubscript{P1}}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
+~~\textit{ZKa\textsubscript{P2}}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
+\hline
+{maximum growth rate of zooplankton}&&&\tabularnewline
+~~\textit{Zumax\textsubscript{P2}}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
+~~\textit{Zumax\textsubscript{P1}}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
+\hline
+{proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
+~~\textit{Zslop\textsubscript{P1}}&$0.25$&$0.12$&$0.33$\tabularnewline
+\hline
+{Zooplankton biomass-dependent respiration factor}&&&\tabularnewline
+~~\textit{Zrespb\textsubscript{P1}}&$0.1$&$0.45$&$3.02$\tabularnewline
+~~\textit{Zrespb\textsubscript{P2}}&$0.42$&$0.09$&$1.05$\tabularnewline
+\hline
+{zooplankton carbon/individual}&&&\tabularnewline
+~~\textit{ZQc\textsubscript{P2}}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
+~~\textit{ZQc\textsubscript{P1}}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
+\hline
+{Zooplankton growth-dependent respiration factor}&&&\tabularnewline
+~~\textit{Zrespg\textsubscript{P1}}&$0.2$&$0.24$&$3.19$\tabularnewline
+~~\textit{Zrespg\textsubscript{P2}}&$0.3$&$0.12$&$0.31$\tabularnewline
+\hline
+{Zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
+~~\textit{Zm\textsubscript{P2}}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
+~~\textit{Zm\textsubscript{P1}}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
+\hline
+{zooplankton nitrogen/individual}&&&\tabularnewline
+~~\textit{ZQn\textsubscript{P1}}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
+~~\textit{ZQn\textsubscript{P2}}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
+\hline
+{zooplankton phosphorus/individual}&&&\tabularnewline
+~~\textit{ZQp\textsubscript{P2}}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
+~~\textit{ZQp\textsubscript{P1}}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
+\begin{table}[!tbp]
+{\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of organic matter parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.\label{tab:omsens}}
+\begin{center}
+\begin{tabular}{lllll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+rate constant for nitrification&\textit{k11}&$5$&$2.11$&$16.1$\tabularnewline
+O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.91$&$11.76$\tabularnewline
+turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.49$&$6.83$\tabularnewline
+turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.37$&$3.46$\tabularnewline
+half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.24$&$7.98$\tabularnewline
+half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.56$&$1.92$\tabularnewline
+decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.01$&$0.03$\tabularnewline
+\hline
+\end{tabular}\end{center}}
 

### 2016-06-29 R/funcs.R

@@ -924,7 +924,7 @@ senstab2 <- function(categ, tablab, tabsize = 'normalsize', sub = NULL, sub.txt 
     mutate(
       Group = factor(Group, 
         levels = c(1:8), 
-        labels = c(paste0('$_{P', 1:6, '}$'), paste0('$_{Z', 1:2, '}$'))
+        labels = c(paste0('\\textsubscript{P', 1:6, '}'), paste0('\\textsubscript{Z', 1:2, '}'))
       ),
       lngs = gsub('^.*:\\s', '', lngs), 
       lngs = gsub('_', '', lngs)

### 2016-07-01 ident_manu.Rnw
identifiability by category plot

@@
 opts_chunk$set(fig.path = 'figs/', fig.align = 'center', fig.show = 'hold', message = F, echo = F, results = 'asis', dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F)
-options(replace.assign = TRUE, width = 90, digits = 1)
+options(replace.assign = TRUE, width = 90)
 
@@
 library(Hmisc)
-library(ncdf4)
+library(ggrepel)
 @
@@
 The sensitivity of \ac{do} was estimated at each timestep from FishTank in relation to 249 parameters that are included in the 108 equations.
-For simplicity in the discussion below, the parameters were grouped into one of six categories in relation to applicable equations: optics, phytoplankton, zooplankton, temperature, and organic matter.
+For simplicity in the discussion below, the parameters were grouped into one of six categories based on respective equations: optics, organic matter, phytoplankton, temperature, and zooplankton.
 A full description of the equations and parameters is available as an appendix in \citepalias{LehrterIR}.
@@
 Time series of \ac{do} estimates before and after perturbation were also evaluated to identify patterns not captured by the summary statistics.
-All parameters for each of the six equation categories (optics, phytoplankton, zooplankton, temperature, and organic matter) that had non-zero $L1$ or $L2$ were retained for identifiability analysis.
+All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ or $L2$ were retained for identifiability analysis.
 
@@
 
-\begin{equation}
+\begin{equation} \label{gameq}
 \gamma = \frac{1} {\sqrt{ \min \left(\rm{EV}[\mathit{\hat{S}}^\top \mathit{\hat{S}}]\right)}}
@@
 These rulesets were developed with the assumption that parameters will be selected given preference for those with high sensitivity and identifability based on $\gamma < 15$ was an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
-Selection heurestics also recognized that parameter categories (i.e., optics, phytoplankton, zooplankton, temperature, organic matter) may have unequal preferences given questions of interest.
+Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences given questions of interest.
 In all selection scenarios, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
@@
 
-\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}
-
 \subsection{Local sensitivity analysis}
 
-The parameters that have the greatest effect on the model by category (optics, organics, phytoplankton, zooplankton) are as follows.
+\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}, how many parameters in each category, how many induced a response in \ac{do}, what parameters in each category had the greatest sensitivity (\cref{fig:sensplo}), what were sensitivity magnitudes between categories, did these vary by phyto or zoop groups?
 
-Plotting the raw values from the sensitivity analysis provides a visual assessment of changes.
+Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplot}).
 
@@
 % combination example
-<<combnex, echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
-The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 100 parameter sets are shown each with one through 100 total parameters.
-For example, there are six unique parameter combinations that result from choosing two parameters from a set.
-Note that the number of unique combinations is shown as the natural-log.
-The same information is viewed differently in each plot.', fig.height = 5, fig.width = 5, out.width = '0.6\\textwidth'>>=
+<<combnex, echo = F, fig.cap = 'Examples of unique parameter combinations from different parameter sets and number of selected parameters.
+The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
+Note that the number of unique combinations is shown as the natural-log.', fig.height = 5, fig.width = 5, out.width = '0.6\\textwidth'>>=
 
@@
 <<sensplo, fig.cap = 'Sensitivity of \\ac{do} to parameter changes.
-Each solid line shows the parameter within each category that had the largest effect on \\ac{do} with a 50\\% change from the default value.
-The dashed line shows \\ac{do} holding all parameters at their default values.
-The bottom plot shows the estimated \\ac{do} as a difference from the default.', fig.height = 5.5, fig.width = 8, echo = F, cache = TRUE>>=
+The solid lines show the change in \\ac{do} based on a 50\\% change from the default parameter values (dashed line) for each parameter.
+Individual parameters with the largest effect are shown for each category.
+The top plot shows the model output and the middle plot shows the estimated \\ac{do} as a difference from the default.
+The bottom plot shows the distribution of error values (as $log\\left(L1\\right)$) for all parmaters in each category.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE>>=
 load(file = 'data/sens_ests.RData')
@@
 
+# for top sens plots
 toplo <- filter(sens_ests$raw, Parameter %in% toeval) %>% 
@@
     time = as.POSIXct(time, origin = as.POSIXct('2002-01-01 0:0', tz = "GMT"), tz = 'GMT'),
-    time = as.Date(time)
+    time = as.Date(time), 
+    Parameter = factor(Parameter, levels = c('astar490_1', 'k11_1', 'Qc_1', 'Tref(nospA+nospZ)_4', 'ZKa_1'))
+  )
+
+# for all L1 boxplots
+toplo2 <- mutate(sens_ests_cat,
+  Category = factor(Category, 
+    levels = c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+    ), 
+  Parameter = as.character(Parameter)
+  ) %>% 
+  group_by(Category) %>% 
+  mutate(
+    tops = ifelse(error == max(error), Parameter, NA)
   )
@@
 
+p3 <- ggplot(toplo2, aes(x = Category, y = log(error), fill = Category)) + 
+  geom_boxplot() +
+  theme_minimal() +
+  scale_fill_brewer(palette = colset) + 
+  scale_y_continuous(expression(paste('log(', italic('L1'), ')'))) + 
+  theme(
+    legend.position = 'none',
+    axis.title.x = element_blank(),
+    axis.line.x = element_line(), 
+    axis.line.y = element_line()
+    )
+
 # align widths of plots in first column, first two
@@
 pB <- ggplot_gtable(ggplot_build(p2))
-maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3])
+pC <- ggplot_gtable(ggplot_build(p3))
+maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3], pC$widths[2:3])
 
@@
 pB$widths[2:3] <- maxWidth
+pC$widths[2:3] <- maxWidth
 
-grid.arrange(pA, pB, ncol = 1, heights = c(1, 0.85))
+grid.arrange(pA, pB, pC, ncol = 1, heights = c(1, 0.85, 0.85))
+@
+
+% identifiability boxplots
+<<identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
+Plots in (a) show identifiability by parameter caterogires (b) shows identifiability by seleting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for each the number of parameters in the set.
+The phytoplankton category is limited to 25 total parameters.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE>>=
+# identifiability by category (all parameters with >0 L1) 
+data(cat_ident)
+data(top_ident)
+
+colset <- 'Set2'
+
+toplo <- cat_ident %>% 
+  lapply(., function(x) dplyr::select(x, N, coll)) %>% 
+  reshape2::melt(., id.var = c('N', 'coll')) %>% 
+  rename(Category = L1) %>% 
+  mutate(Category = factor(Category, 
+    levels = c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton'),
+    labels = c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+    )) %>% 
+  filter(N <= 25) %>% # reduced for plot space
+  group_by(N, Category) %>% 
+  summarise(
+    ave = mean(coll), 
+    med = median(coll),
+    min = min(coll), 
+    max = max(coll)
+  )
+
+p1 <- ggplot(toplo, aes(x = N, colour = Category, group = N)) + 
+  geom_point(aes(y = ave)) + 
+  geom_point(aes(y = med)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0) + 
+  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
+  theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank()
+  ) + 
+  scale_colour_brewer(palette = colset) + 
+  theme(legend.position = 'none') + 
+  ggtitle('(a) By parameter category')
+
+# identifiability top 1, 2, 3, 4, 5 all categories combined
+toplo2 <-  reshape2::melt(top_ident, id.var = c('N', 'coll')) %>% 
+  select(N, coll, L1) %>% 
+  mutate(L1 = factor(L1, levels = paste0('top', 1:5), labels = paste0('Top ', 1:5))) %>% 
+  rename(npercat = L1) %>% 
+  group_by(N, npercat) %>% 
+  summarise(
+    ave = mean(coll), 
+    med = median(coll),
+    min = min(coll), 
+    max = max(coll)
+  )
+
+p2 <- ggplot(toplo2, aes(x = N, colour = npercat, group = N)) + 
+  geom_point(aes(y = ave, shape = 'Ave')) + 
+  geom_point(aes(y = med, shape = 'Med')) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0) + 
+  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
+  theme_minimal() + 
+  scale_colour_brewer(palette = colset, guide = F) + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank(), 
+    legend.title = element_blank()
+  ) + 
+  ggtitle('(b) By top parameters, all categories')
+
+pleg <- g_legend(p2)
+p2 <- p2 + theme(legend.position = 'none')
+
+grid.arrange(
+  arrangeGrob(p1, p2, ncol = 2),
+  left = 'Identifiability', 
+  bottom = 'Parameters in set',
+  pleg, ncol = 2, widths = c(1, 0.1)
+)
 @
@@
 
-<<tempsens, eval = T, cache = F >>=
-senstab2('Temperature', 'tempsens')
+<<omsens, eval = T, cache = F>>=
+senstab1('Organic Matter', 'omsens')
 @
@@
 
+<<tempsens, eval = T, cache = F >>=
+senstab2('Temperature', 'tempsens')
+@
+
 <<zoopsens, eval = T, cache = F>>=
@@
 
-<<omsens, eval = T, cache = F>>=
-senstab1('Organic Matter', 'omsens')
-@
-
 \end{document}

### 2016-07-01 ident_manu.tex
identifiability by category plot

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Jun 29 14:50:46 2016 -0500
+  \\ Version Date:   Wed Jun 29 16:36:46 2016 -0500
 	}
@@
 
-\caption[Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets]{Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.
-The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 100 parameter sets are shown each with one through 100 total parameters.
-For example, there are six unique parameter combinations that result from choosing two parameters from a set.
-Note that the number of unique combinations is shown as the natural-log.
-The same information is viewed differently in each plot.}\label{fig:combnex}
+\caption[Examples of unique parameter combinations from different parameter sets and number of selected parameters]{Examples of unique parameter combinations from different parameter sets and number of selected parameters.
+The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
+Note that the number of unique combinations is shown as the natural-log.}\label{fig:combnex}
 \end{figure}
@@
 \caption{Sensitivity of \ac{do} to parameter changes.
-Each solid line shows the parameter within each category that had the largest effect on \ac{do} with a 50\% change from the default value.
-The dashed line shows \ac{do} holding all parameters at their default values.
-The bottom plot shows the estimated \ac{do} as a difference from the default.}\label{fig:sensplo}
+The solid lines show the change in \ac{do} based on a 50\% change from the default parameter values (dashed line) for each parameter.
+Individual parameters with the largest effect are shown for each category.
+The top plot shows the model output and the middle plot shows the estimated \ac{do} as a difference from the default.
+The bottom plot shows the distribution of error values (as $log\left(L1\right)$) for all parmaters in each category.}\label{fig:sensplo}
+\end{figure}
+
+% identifiability boxplots
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\maxwidth]{figs/identbox-1}
+
+}
+
+\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.
+Plots in (a) show identifiability by parameter caterogires (b) shows identifiability by seleting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for each the number of parameters in the set.
+The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
 \end{figure}
@@
 
-%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
 \begin{table}[!tbp]
 {\normalsize
-\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.
+\caption{Sensitivities of \ac{do} to perturbation of organic matter parameters.
 Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
-Parameters that did not affect \ac{do} are not shown.
-Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}}
+Parameters that did not affect \ac{do} are not shown.\label{tab:omsens}}
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \hline\hline
-\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
 \hline
-{Optimum temperature for growth(C)}&&&\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P4}}&$17$&$2.9$&$22.95$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{Z2}}&$26$&$0.18$&$2.59$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P5}}&$26$&$0.17$&$0.72$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P2}}&$22$&$0.16$&$0.82$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{Z1}}&$22$&$0.16$&$0.33$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P3}}&$17$&$0.14$&$0.78$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P1}}&$22$&$0.12$&$0.29$\tabularnewline
+rate constant for nitrification&\textit{k11}&$5$&$2.11$&$16.1$\tabularnewline
+O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.91$&$11.76$\tabularnewline
+turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.49$&$6.83$\tabularnewline
+turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.37$&$3.46$\tabularnewline
+half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.24$&$7.98$\tabularnewline
+half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.56$&$1.92$\tabularnewline
+decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.01$&$0.03$\tabularnewline
 \hline
@@
 {\normalsize
+\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.
+Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
+Parameters that did not affect \ac{do} are not shown.
+Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
+\hline
+{Optimum temperature for growth(C)}&&&\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P4}}&$17$&$2.9$&$22.95$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{Z2}}&$26$&$0.18$&$2.59$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P5}}&$26$&$0.17$&$0.72$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P2}}&$22$&$0.16$&$0.82$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{Z1}}&$22$&$0.16$&$0.33$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P3}}&$17$&$0.14$&$0.78$\tabularnewline
+~~\textit{Tref(nospA+nospZ)\textsubscript{P1}}&$22$&$0.12$&$0.29$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\normalsize
 \caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.
@@
 
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
-\begin{table}[!tbp]
-{\normalsize
-\caption{Sensitivities of \ac{do} to perturbation of organic matter parameters.
-Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
-Parameters that did not affect \ac{do} are not shown.\label{tab:omsens}}
-\begin{center}
-\begin{tabular}{lllll}
-\hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
-\hline
-rate constant for nitrification&\textit{k11}&$5$&$2.11$&$16.1$\tabularnewline
-O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.91$&$11.76$\tabularnewline
-turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.49$&$6.83$\tabularnewline
-turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.37$&$3.46$\tabularnewline
-half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.24$&$7.98$\tabularnewline
-half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.56$&$1.92$\tabularnewline
-decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.01$&$0.03$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
-
 \end{document}

### 2016-07-01 R/funcs.R

@@ -1,3 +1,10 @@
+# get legend from an existing ggplot object
+g_legend <- function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
 # alternative list structure for parameter categories
 parcats2 <- function(as_df = FALSE){
   

### 2016-07-01 ident_manu.Rnw
catident figure

@@
 
-The identifiability functions evaluate the ability to identify all subsets from pairwise to all parameters in the subset.
-As an example, the identifiability of pairwise combinations for each of the categories are shown below.
+\cref{fig:identbox} shows identifiability ranges, describe by caegory, also emphasize that selection indepedent of category may be more appropriate (better identifiability).
+Jumps in median suggest inclusion of a specific parameter has disproportionate affect on identifiability.
 
-Pairwise identifiability of the top two most sensitive parameters in each category is shown, first as a table showing all unique combinations from two to all parameters and second as a figure showing pairwise combinations.
+Note that identifiability for one phytoplankton group and one zooplankton group needs to be evaluated, lots of redundancy between groups.
 
@@
 <<identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
-Plots in (a) show identifiability by parameter caterogires (b) shows identifiability by seleting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for each the number of parameters in the set.
+Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
 The phytoplankton category is limited to 25 total parameters.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE>>=
@@
 
-p1 <- ggplot(toplo, aes(x = N, colour = Category, group = N)) + 
-  geom_point(aes(y = ave)) + 
-  geom_point(aes(y = med)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0) + 
+p1 <- ggplot(toplo, aes(x = N, group = N)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
+  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
+  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
   facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
@@
   ) + 
-  scale_colour_brewer(palette = colset) + 
   theme(legend.position = 'none') + 
@@
 
-p2 <- ggplot(toplo2, aes(x = N, colour = npercat, group = N)) + 
-  geom_point(aes(y = ave, shape = 'Ave')) + 
-  geom_point(aes(y = med, shape = 'Med')) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0) + 
+p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
+  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
+  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
   facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
   theme_minimal() + 
-  scale_colour_brewer(palette = colset, guide = F) + 
   theme(
@@
 )
+@
+
+<<catident, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).
+Parameters are selected in each category by decreasing sensitivity (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
+Grey lines indicate thresholds for maximum acceptable identifiability.
+Selection stops after $\\gamma > 15$ or if the maximum number of parameters in a category is selected.', fig.height = 8.5, fig.width = 4.5, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
+
+# plot of sequential identifiability by category
+
+data(tocal)
+data(sens_ests_cat)
+
+# ggplot theme
+pthm <- theme_minimal() + 
+  theme(
+    axis.text.x = element_text(size = 6), 
+    axis.line.x = element_line(),
+    axis.line.y = element_line(), 
+    panel.grid.minor = element_blank(), 
+    panel.grid.major = element_blank()
+    )
+
+# data prep, select all with coll < 15 plus one, as list
+toplo <- filter(tocal$cat) %>% 
+  split(., .$Category) %>% 
+  lapply(function(x){
+
+    sel <- which(x$coll < 15)
+    x <- x[c(sel, max(sel) + 1), ] %>% 
+      na.omit
+    x
+
+  }) %>% 
+  do.call('rbind', .)
+
+ggplot(toplo, aes(x = Selected, y = coll)) + 
+  geom_line() + 
+  geom_point(size = 3, shape = 21, fill = 'grey') +
+  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
+  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
+  facet_wrap(~Category, ncol = 1, scales = 'free') + 
+  scale_x_continuous(breaks = c(1:25)) + 
+  scale_y_continuous('Identifiability') +
+  pthm
+
 @

### 2016-07-01 ident_manu.tex
catident figure

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Jun 29 16:36:46 2016 -0500
+  \\ Version Date:   Thu Jun 30 19:09:01 2016 -0500
 	}
@@
 \caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.
-Plots in (a) show identifiability by parameter caterogires (b) shows identifiability by seleting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for each the number of parameters in the set.
+Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
 The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
+\end{figure}
+
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=0.6\textwidth]{figs/catident-1}
+
+}
+
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).
+Parameters are selected in each category by decreasing sensitivity (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
+Grey lines indicate thresholds for maximum acceptable identifiability.
+Selection stops after $\gamma > 15$ or if the maximum number of parameters in a category is selected.}\label{fig:catident}
 \end{figure}

### 2016-07-06 ident_manu.Rnw
all heuristics to fig heurist

@@
 In all selection scenarios, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
+\item blocked within parameter category,
 \item independent of parameter category,
-\item blocked within parameter category,
 \item or considering all categories equally
@@
 
-Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplot}).
+Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplo}).
 
-\cref{fig:identbox} shows identifiability ranges, describe by caegory, also emphasize that selection indepedent of category may be more appropriate (better identifiability).
+\cref{fig:identbox} shows identifiability ranges, describe by category, also emphasize that selection independent of category may be more appropriate (better identifiability).
 Jumps in median suggest inclusion of a specific parameter has disproportionate affect on identifiability.
@@
 
-<<catident, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).
-Parameters are selected in each category by decreasing sensitivity (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
-Grey lines indicate thresholds for maximum acceptable identifiability.
-Selection stops after $\\gamma > 15$ or if the maximum number of parameters in a category is selected.', fig.height = 8.5, fig.width = 4.5, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
+<<heurist, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics.
+Parameters are selected by decreasing sensitivity for all examples (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
+The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c).
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\\gamma > 15$ or if the maximum number of possible parameters is selected.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
 
@@
 data(sens_ests_cat)
+
+cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+
+# custom col scale
+mycols <- RColorBrewer::brewer.pal(5, 'Set2')
+names(mycols) <- cats
+cols <- scale_fill_manual(name = 'Category', values = mycols)
 
@@
     panel.grid.minor = element_blank(), 
-    panel.grid.major = element_blank()
+    panel.grid.major = element_blank(), 
+    axis.title.y = element_blank(), 
+    axis.title.x = element_blank()
     )
 
-# data prep, select all with coll < 15 plus one, as list
+# top sensitive within categories
 toplo <- filter(tocal$cat) %>% 
@@
   do.call('rbind', .)
-
-ggplot(toplo, aes(x = Selected, y = coll)) + 
+toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
+pcat <- ggplot(toplo, aes(x = Selected, y = coll)) + 
   geom_line() + 
-  geom_point(size = 3, shape = 21, fill = 'grey') +
+  geom_point(size = 3, shape = 21, aes(fill = Category)) +
   geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
@@
   scale_y_continuous('Identifiability') +
-  pthm
+  cols +
+  pthm +
+  theme(legend.position = 'none') +
+  ggtitle('(a) Blocked by category')
 
+# top sensitive
+toplo <- tocal$top
+sel <- which(toplo$coll < 15)
+toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
+toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
+ptop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
+  geom_line() + 
+  geom_point(size = 4, shape = 21, aes(fill = Category)) +
+  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
+  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
+  scale_x_continuous(breaks = 1:nrow(toplo)) + 
+  scale_y_continuous('Identifiability') + 
+  cols +
+  pthm +
+  theme(legend.position = 'none') +
+  ggtitle('(b) Independent of category')
+
+# top sensitive and category
+toplo <- tocal$cattop
+sel <- which(toplo$coll < 15)
+toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
+toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
+pcattop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
+  geom_line() + 
+  geom_point(size = 4, shape = 21, aes(fill = Category)) +
+  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
+  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
+  scale_x_continuous(breaks = 1:nrow(toplo)) + 
+  scale_y_continuous('Identifiability') +
+  cols +
+  pthm +
+  theme(legend.position = 'top') + 
+  ggtitle('(c) All categories equally')
+
+pleg <- g_legend(pcattop)
+pcattop <- pcattop +
+  theme(legend.position = 'none')
+
+grid.arrange(
+  pleg, 
+  arrangeGrob(
+    pcat,
+    arrangeGrob(ptop, pcattop, ncol = 1), 
+    widths = c(1, 1),
+    ncol = 2
+    ), 
+  ncol = 1, 
+  heights = c(0.05, 1),
+  bottom = 'Selected', 
+  left = 'Identifiability'
+)
+
+@
+
+<<st>>=
+load(file = 'rdata/tocal_all.Rdata')
+
+toplo <- tocal_all$top_all %>% 
+  reshape2::melt(., id.var = names(.[[1]]))
+
+ggplot(toplo, aes(x = Selected, y = coll)) + 
+  geom_line(size = 1) + 
+  geom_hline(yintercept = 15) +
+  geom_label_repel(
+    aes(label = Parameter), 
+    label.padding = unit(0.1, "lines"),
+    box.padding = unit(2, "lines"), 
+    force = 2
+    ) + 
+  geom_point(aes(colour = Category), size = 5) +
+  coord_cartesian(ylim = c(0, 25), xlim = c(0, 16)) + 
+  theme_classic() + 
+  facet_wrap(~L1, scales= 'free_x', ncol = 4) + 
+  scale_colour_brewer(palette = 'Set1') + 
+  scale_y_continuous('Identifiability') + 
+  scale_x_continuous(
+    'No. selected by increasing sensitivity',
+    breaks=toplo$Selected
+    ) + 
+  theme(
+    legend.position = 'top', 
+    strip.text = element_text(size = 12),
+    axis.line.x = element_line(size = 0.5),
+    axis.line.y = element_line(size = 0.5)
+    )
 @

### 2016-07-06 ident_manu.tex
all heuristics to fig heurist

@@
   \vspace{1in} 
-  \\ Version Date:   Thu Jun 30 19:09:01 2016 -0500
+  \\ Version Date:   Fri Jul 1 16:59:17 2016 -0500
 	}
@@
 
-{\centering \includegraphics[width=0.6\textwidth]{figs/catident-1}
+{\centering \includegraphics[width=\textwidth]{figs/heurist-1}
 
@@
 
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters by category (optics, organic matter, phytoplankton, temperature, zooplankton).
-Parameters are selected in each category by decreasing sensitivity (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
-Grey lines indicate thresholds for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$ or if the maximum number of parameters in a category is selected.}\label{fig:catident}
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters with three different heuristics.
+Parameters are selected by decreasing sensitivity for all examples (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
+The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c).
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.}\label{fig:heurist}
 \end{figure}

### 2016-07-06 ident_manu.Rnw
ident of all state variables fig added

@@
   theme(legend.position = 'top') + 
+  guides(fill = guide_legend(nrow = 3)) +
   ggtitle('(c) All categories equally')
@@
 grid.arrange(
-  pleg, 
-  arrangeGrob(
   pcat,
-    arrangeGrob(ptop, pcattop, ncol = 1), 
+  arrangeGrob(ptop, pcattop, pleg, ncol = 1, heights = c(1, 1, 0.6)), 
   widths = c(1, 1),
-    ncol = 2
-    ), 
-  ncol = 1, 
-  heights = c(0.05, 1),
-  bottom = 'Selected', 
+  ncol = 2, 
+  bottom = 'Parameters selected by sensitivity', 
   left = 'Identifiability'
@@
 
-<<st>>=
-load(file = 'rdata/tocal_all.Rdata')
+<<heurist_stts, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables.
+Parameters are selected by decreasing sensitivity indepent of parameter categories.
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\\gamma > 15$.', fig.height = 5, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
+data(tocal_all)
 
+# factor levels
+cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'OM1', 'OM2', 'PO4')
+stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
+
+# custom col scale
+mycols <- RColorBrewer::brewer.pal(5, 'Set2')
+names(mycols) <- cats
+cols <- scale_fill_manual(name = 'Category', values = mycols)
+
+# ggplot theme
+pthm <- theme_minimal() + 
+  theme(
+    axis.text.x = element_text(size = 6), 
+    axis.line.x = element_line(),
+    axis.line.y = element_line(), 
+    panel.grid.minor = element_blank(), 
+    panel.grid.major = element_blank()
+    )
+
+# get all parameters for each state variable where coll < 15 plus one
 toplo <- tocal_all$top_all %>% 
-  reshape2::melt(., id.var = names(.[[1]]))
+  reshape2::melt(., id.var = names(.[[1]])) %>% 
+  filter(!L1 %in% 'O2') %>% 
+  mutate(
+    L1 = factor(L1, levels = stts_lev, labels = stts_lab),
+    Category = factor(Category, levels = cats, labels = cats)
+  ) %>% 
+  split(., .$L1) %>% 
+  lapply(function(x){
+    # browser()
+    sel <- which(x$coll < 15)
+    x <- x[c(sel, max(sel) + 1), ] %>% 
+      na.omit
+    x
+
+  }) %>% 
+  do.call('rbind', .)
 
 ggplot(toplo, aes(x = Selected, y = coll)) + 
-  geom_line(size = 1) + 
-  geom_hline(yintercept = 15) +
-  geom_label_repel(
-    aes(label = Parameter), 
-    label.padding = unit(0.1, "lines"),
-    box.padding = unit(2, "lines"), 
-    force = 2
-    ) + 
-  geom_point(aes(colour = Category), size = 5) +
-  coord_cartesian(ylim = c(0, 25), xlim = c(0, 16)) + 
-  theme_classic() + 
-  facet_wrap(~L1, scales= 'free_x', ncol = 4) + 
-  scale_colour_brewer(palette = 'Set1') + 
+  geom_line() + 
+  geom_point(aes(fill = Category), shape = 21, size = 4) +
+  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
+  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
+  facet_wrap(~L1, scales= 'free', ncol = 4) + 
   scale_y_continuous('Identifiability') + 
   scale_x_continuous(
-    'No. selected by increasing sensitivity',
-    breaks=toplo$Selected
+    'Parameters selected by sensitivity',
+    breaks = toplo$Selected
     ) + 
-  theme(
-    legend.position = 'top', 
-    strip.text = element_text(size = 12),
-    axis.line.x = element_line(size = 0.5),
-    axis.line.y = element_line(size = 0.5)
-    )
+  cols +
+  pthm +
+  theme(legend.position = c(0.9, 0.2))
 @

### 2016-07-07 ident_manu.Rnw
starting results

@@
 library(ggrepel)
+library(english)
 @
@@
 \item How is model performance/uncertainty evaluated regarding what they should provide - structural, observational, parameter \cite{Beck87}?
+\cite{Refsgaard07} provides comprehensive overview of factors that contribute to uncertainty in environmental modelling.
 \item Parameter uncertainy as low-hanging fruit - can do post-hoc and from inner to outer level of complexity, parameter uncertainty is the most common, e.g., marine ecological model \cite{Mateus15}, but stopped short, global sensitivity analysis of eutrophication model \cite{Estrada10}
@@
 \item quantify the identifiability of subsets of the total parameter space based on sensitivity,
-\item provide a set of heuristics for choosing parameters based on sensitivity and parameter categories with the larger mechanistic model, including extension to other state variables, and 
+\item provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories, including extension to other state variables provided by the model, and 
 \item discuss implications for hypoxia formation in coastal regions, including management strategies for nutrient reduction and use of mechanistic models to inform decision-making.
@@
 
-Low concentrations of \acl{do} occur seasonally on the \ac{lcs} in the northern \ac{gom}.
-These hypoxic events, defined as $<$2 mg L$^{-1}$ ($<$ 64 mmol m$^-3$ of O$_2$), occur in bottom waters and are caused by nutrient inputs from the \ac{marb} that drains a significant portion of the continental United States.
-Nutrient-stimulated primary production in surface waters increases biological oxygen demand in bottom waters as sinking organic matter is decomposed.
+Hypoxic events, defined  as $<$2 mg L$^{-1}$ of \ac{do} ($<$ 64 mmol m$^-3$), occur seasonally in bottom waters in the northern \ac{gom}.
+The \ac{lcs} receives high nutrient loads from the \ac{marb} that drains a significant portion of the continental United States.
+Nutrient-stimulated primary production in surface waters increases biological oxygen demand in bottom waters as sinking organic matter is decomposed \citep{Bierman94,Murrell13}.
 The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.
-Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas factors related to hydrologic variation and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97}.
+Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97,Obenour15}.
 
@@
 This study evaluates a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia.
-The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} to describe hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
-The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia dynamics using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
+The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describe hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
+The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
 The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.
-The model can be run for a set period of time at a given time step using atmospheric and hydrological boundary conditions described in \citet{Hodur97} and \citet{Lehrter13}.
+Atmospheric and hydrological boundary conditions described in \citet{Hodur97} and \citet{Lehrter13} are also included in \ac{cgem}.
 
-The core unit of \ac{cgem} is a \ac{oned} model called FishTank that implements the biogeochemical equations in \citet{Eldridge10}.
-This model acts as a standalone operational unit from the 3-D model that does not include any form of transport (i.e., advection, mixing, or surface flux) such that it can easily be applied to other hydrodynamic grids.
+The core unit of \ac{cgem} is FishTank, a \ac{oned} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux).
+Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
 Accordingly, the sensitivity and identifiability analysis described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
@@
 A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 (Table 1, \citet{Murrell14}).
-The FishTank model was executed from January 1\textsuperscript{st} to December \textsuperscript{st}, 2006 at a timestep of five minutes.
+
+<<echo = FALSE>>=
+# numer of parameters in each category
+nparms <- table(parcats2(as_df = TRUE)$cat) %>% 
+  as.list
+@
 
@@
 A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
-In addition to the initial conditions, a set of parameter values for each of the equations is also supplied at model execution.
+In addition to the initial conditions, 250 parameter values for each of the equations is also supplied at model execution.
 These parameters define relationships among fixed effects in the equations and represent ecological properties described by the model that influence hypoxia formation.
-Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert-based knowledge in absence of the former.
-The sensitivity of \ac{do} was estimated at each timestep from FishTank in relation to 249 parameters that are included in the 108 equations.
-For simplicity in the discussion below, the parameters were grouped into one of six categories based on respective equations: optics, organic matter, phytoplankton, temperature, and zooplankton.
-A full description of the equations and parameters is available as an appendix in \citepalias{LehrterIR}.
+Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.
+As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.
+The sensitivity of \ac{do} to perturbations of all parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
+For simplicity, the parameters were grouped into one of six categories based on their respective equations: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
+A full description is available as an appendix in \citepalias{LehrterIR}.
+
 \subsection{Local sensitivity analysis}
@@
 The analysis focused on sensitivity of \ac{do} in the \ac{oned} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
-A local sensitivity analysis was performed for each of the 249 parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
+A local sensitivity analysis was performed for each of the 250 parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
 The analyses relied exlusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10}.
@@
 In general, positive sensitivity estimates suggested a parameter had a positive effect on \ac{do} for a given increase in the parameter, whereas the converse was true for negative sensitivity estimates.
-However, the effect of a parameter change may not be uniform over time such that $S_{ij}$ can change in magnitude and sign depending on the location.
+However, the effect of a parameter change may not be uniform over time such that $S_{ij}$ can change in magnitude and sign depending on the temporal location.
 Time series of \ac{do} estimates before and after perturbation were also evaluated to identify patterns not captured by the summary statistics.
@@
 
-\noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for a set of parameters in a chosen sensitivity matrix $S$.
-The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that describes deviations of predicted \ac{do} from the default parameter values.
-The matrix $\hat{S}$ was first normalized by dividing by the square root of the summed residuals\citep{Omlin01,Soetaert10}.
+\noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for parameters in a sensitivity matrix $S$.
+The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that described deviations of predicted \ac{do} from the default parameter values.
+The matrix $\hat{S}$ was first normalized by dividing by the square root of the summed residuals \citep{Omlin01,Soetaert10}.
 
@@
 Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning optimal values are inestimable given similar effects of the selected parameters on \ac{do}.
-Greater sensitivity of a state variable to parameters within a subset does not imply identifiability if the individual effects are similar.
+Greater sensitivity of a state variable to a subset of parameters does not always imply better identifiability if the individual effects are similar.
 An intuitive interpretation of $\gamma$ is provided by \citet{Brun01} such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
@@
 
-Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 249 included in the FishTank model.
-Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and identifability as it relates to optimization.
-An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given differences in parameter sensitivity and desired ecological categories of each parameter as they relate to the biogeochemical equations.
+Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 250 in the FishTank model.
+Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
+An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter.
 For example, \cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., based on $n$ choose $k$ combinations equal to $n!/\left(k!\left(n-k\right)!\right)$).
 The number of unique combinations increases with the total parameters in the set and is also maximized for moderate selections (e.g., selecting half the total).
-For example, over 10$^14$ combinations are possible by selecting 25 parameters from a set of 50.
+For example, over 10$^{14}$ combinations are possible by selecting 25 parameters from a set of 50.
 Accordingly, parameter selection is complicated by differing sensitivity, identifiability, and the difficulty of choosing from many combinations.
@@
 A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above.
-These rulesets were developed with the assumption that parameters will be selected given preference for those with high sensitivity and identifability based on $\gamma < 15$ was an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
+These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability).
 Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences given questions of interest.
@@
 
+% for inline
+<<echo = FALSE>>=
+data(sens_ests)
+data(sens_ests_cat)
+
+# number of parameters in each category
+bycat <- table(sens_ests_cat$Category)
+nms <- names(bycat)
+bycat <- as.numeric(bycat)
+names(bycat) <- nms
+bycat <- toeng(bycat)
+
+# percent of parameters in each category
+lncats <- table(sens_ests_cat$Category) %>% 
+  `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>% 
+  `*` (100) %>% 
+  form_fun(nsm_val = 0) %>% 
+  as.list %>% 
+  lapply(., paste0, '\\%')
+
+# L1, summaries
+sensrng <- with(sens_ests_cat, which(L2 %in% range(L2))) %>% 
+  sens_ests_cat[., ] %>% 
+  mutate(error = sapply(error, scinot))
+
+@
+
 \subsection{Local sensitivity analysis}
 
-\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}, how many parameters in each category, how many induced a response in \ac{do}, what parameters in each category had the greatest sensitivity (\cref{fig:sensplo}), what were sensitivity magnitudes between categories, did these vary by phyto or zoop groups?
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank.
+Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temparature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}).
+Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
+Among all parameters, sensitivity values ranged from \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).
+
+what parameters in each category had the greatest sensitivity (\cref{fig:sensplo}), what were sensitivity magnitudes between categories, did these vary by phyto or zoop groups?
 
 Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplo}).
+
+\subsection{Subset identifiability}
 
@@
 Failing in one way can be over-compensated by another feature, e.g., the parameter set that is optimized (see \cite{Flynn05}, p.
-1207, third paragraph)
+1207, third paragraph), also \citep{Arhonditsis08}
 
@@
 
-Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}
+Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}, \citep{Arhonditsis08}
 

### 2016-07-07 ident_manu.tex
ident of all state variables fig added
starting results

@@
   \vspace{1in} 
-  \\ Version Date:   Fri Jul 1 16:59:17 2016 -0500
+  \\ Version Date:   Wed Jul 6 16:28:29 2016 -0500
 	}
@@
 A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 (Table 1, \citet{Murrell14}).
-The FishTank model was executed from January 1\textsuperscript{st} to December \textsuperscript{st}, 2006 at a timestep of five minutes.
 
@@
 A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
-In addition to the initial conditions, a set of parameter values for each of the equations is also supplied at model execution.
+In addition to the initial conditions, 250 parameter values for each of the equations is also supplied at model execution.
 These parameters define relationships among fixed effects in the equations and represent ecological properties described by the model that influence hypoxia formation.
-Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert-based knowledge in absence of the former.
-The sensitivity of \ac{do} was estimated at each timestep from FishTank in relation to 249 parameters that are included in the 108 equations.
-For simplicity in the discussion below, the parameters were grouped into one of six categories based on respective equations: optics, organic matter, phytoplankton, temperature, and zooplankton.
-A full description of the equations and parameters is available as an appendix in \citepalias{LehrterIR}.
+Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.
+As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.
+The sensitivity of \ac{do} to perturbations of all parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
+For simplicity, the parameters were grouped into one of six categories based on their respective equations: optics ($n = $ 11 parameters), organic matter (29), phytoplankton (156), temperature (32), and zooplankton (22).
+A full description is available as an appendix in \citepalias{LehrterIR}.
+
 \subsection{Local sensitivity analysis}
@@
 
+% for inline
+
 \subsection{Local sensitivity analysis}
 
-\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}, how many parameters in each category, how many induced a response in \ac{do}, what parameters in each category had the greatest sensitivity (\cref{fig:sensplo}), what were sensitivity magnitudes between categories, did these vary by phyto or zoop groups?
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank.
+Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temparature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}).
+Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
+Among all parameters, sensitivity values ranged from $3.18\times 10^{-6}$ for Kcdom_1 (optics) to $328.35$ for Qc_1 (phytoplankton).
+
+what parameters in each category had the greatest sensitivity (\cref{fig:sensplo}), what were sensitivity magnitudes between categories, did these vary by phyto or zoop groups?
 
 Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplo}).
+
+\subsection{Subset identifiability}
 
@@
 Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.}\label{fig:heurist}
+\end{figure}
+
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/heurist_stts-1}
+
+}
+
+\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables.
+Parameters are selected by decreasing sensitivity indepent of parameter categories.
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
 \end{figure}

### 2016-07-07 R/funcs.R

@@ -5,6 +5,61 @@ g_legend <- function(a.gplot){
   legend <- tmp$grobs[[leg]]
   return(legend)}
 
+# numeric to english for inline text
+# uses english package
+#
+# x numeric vector
+# maxint maximum integer below which english is used
+toeng <- function(x, maxint = 10){
+
+  library(english)
+  
+  if(!is.numeric(x)) stop('x must be numeric')
+
+  nms <- names(x)  
+  xchr <- which(x < maxint) 
+  xeng <- as.character(english(x[xchr]))
+  x <- as.character(x)
+  x[xchr] <- xeng
+  x <- as.list(x)
+  names(x) <- nms
+  
+  return(x)
+  
+}
+
+# formatting of values in S expressions
+form_fun <- function(x, rnd_val = 2, dig_val = 2, nsm_val = 2, ...) {
+  format(round(x, rnd_val), digits = dig_val, nsmall = nsm_val, ...)
+}
+
+######
+# scientific notation from R to LaTeX
+# x is numeric to convert
+# pow is minimum exponent (positive or negative) to use for notation
+# digits numeric for rounding
+# showdollar logical if output is enclosed in dollar for latex
+# from https://dankelley.github.io/r/2015/03/22/scinot.html
+scinot <- function(x, pow = 3, digits=2, showDollar=TRUE)
+{
+  
+    sign <- ""
+    if (x < 0) {
+        sign <- "-"
+        x <- -x
+    }
+    exponent <- floor(log10(x))
+    if (exponent & abs(exponent) > pow) {
+        xx <- round(x / 10^exponent, digits=digits)
+        e <- paste("\\times 10^{", as.integer(exponent), "}", sep="")
+    } else {
+        xx <- round(x, digits=digits)
+        e <- ""
+    }
+    if (showDollar) paste("$", sign, xx, e, "$", sep="")
+    else paste(sign, xx, e, sep="")
+}
+
 # alternative list structure for parameter categories
 parcats2 <- function(as_df = FALSE){
   
@@ -813,7 +868,7 @@ parcats2 <- function(as_df = FALSE){
   # return as data frame if T
   if(as_df){
     
-    out <- lapply(out, data.frame)
+    out <- lapply(out, data.frame, stringsAsFactors = FALSE)
     out <- do.call('rbind', out)
     row.names(out) <- 1:nrow(out)
     
@@ -822,33 +877,6 @@ parcats2 <- function(as_df = FALSE){
   
   return(out)
   
[…]

### 2016-07-08 ident_manu.Rnw
par_txt function to convert parameter chr strings to latex or R expression output

@@
 
-# L1, summaries
-sensrng <- with(sens_ests_cat, which(L2 %in% range(L2))) %>% 
+# L1 range
+sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
   sens_ests_cat[., ] %>% 
-  mutate(error = sapply(error, scinot))
+  mutate(
+    error = sapply(error, scinot),
+    Parameter = par_txt(Parameter)
+    )
+
+# L1 range within categories
+# sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
+#   sens_ests_cat[., ] %>% 
+#   mutate(
+#     error = sapply(error, scinot),
+#     Parameter = par_txt(Parameter)
+#     )
 
@@
 Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank.
-Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temparature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}).
+Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).
+Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).
+Within categories, sensitivity ranged from
 

### 2016-07-08 ident_manu.tex
par_txt function to convert parameter chr strings to latex or R expression output

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Jul 6 16:28:29 2016 -0500
+  \\ Version Date:   Thu Jul 7 15:16:18 2016 -0500
 	}
@@
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $3.18\times 10^{-6}$ for Kcdom_1 (optics) to $328.35$ for Qc_1 (phytoplankton).
+Among all parameters, sensitivity values ranged from $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton).
 
@@
 {coefficient for non-limiting nutrient}&&&\tabularnewline
-~~\textit{aN\textsubscript{P1}}&$1$&$2.7$&$47.26$\tabularnewline
-~~\textit{aN\textsubscript{P3}}&$1$&$0.66$&$3.16$\tabularnewline
+~~\textit{aN$_{p1}$}&$1$&$2.7$&$47.26$\tabularnewline
+~~\textit{aN$_{p3}$}&$1$&$0.66$&$3.16$\tabularnewline
 \hline
-{half-saturation constant for N}&&&\tabularnewline
-~~\textit{Kn\textsubscript{P3}}&$5.93$&$1.15$&$9.22$\tabularnewline
-~~\textit{Kn\textsubscript{P4}}&$1.13$&$0.62$&$2.5$\tabularnewline
+{half-saturation constant for n}&&&\tabularnewline
+~~\textit{Kn$_{p3}$}&$5.93$&$1.15$&$9.22$\tabularnewline
+~~\textit{Kn$_{p4}$}&$1.13$&$0.62$&$2.5$\tabularnewline
 \hline
 {initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
-~~\textit{alpha\textsubscript{P4}}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
-~~\textit{alpha\textsubscript{P3}}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
-~~\textit{alpha\textsubscript{P5}}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
+~~\textit{alpha$_{p4}$}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
+~~\textit{alpha$_{p3}$}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
+~~\textit{alpha$_{p5}$}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
 \hline
-{minimum N cell-quota}&&&\tabularnewline
-~~\textit{QminN\textsubscript{P3}}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
-~~\textit{QminN\textsubscript{P4}}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
-~~\textit{QminN\textsubscript{P1}}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
+{minimum n cell-quota}&&&\tabularnewline
+~~\textit{QminN$_{p3}$}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
+~~\textit{QminN$_{p4}$}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
+~~\textit{QminN$_{p1}$}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
 \hline
 {mortality coefficient}&&&\tabularnewline
-~~\textit{mA\textsubscript{P3}}&$0.03$&$2.98$&$14.34$\tabularnewline
-~~\textit{mA\textsubscript{P4}}&$0.11$&$1.35$&$7.04$\tabularnewline
+~~\textit{mA$_{p3}$}&$0.03$&$2.98$&$14.34$\tabularnewline
+~~\textit{mA$_{p4}$}&$0.11$&$1.35$&$7.04$\tabularnewline
 \hline
-{N-uptake rate measured at umax}&&&\tabularnewline
-~~\textit{vmaxN\textsubscript{P5}}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
-~~\textit{vmaxN\textsubscript{P4}}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
-~~\textit{vmaxN\textsubscript{P3}}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
-~~\textit{vmaxN\textsubscript{P1}}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
+{n-uptake rate measured at umax}&&&\tabularnewline
+~~\textit{vmaxN$_{p5}$}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
+~~\textit{vmaxN$_{p4}$}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
+~~\textit{vmaxN$_{p3}$}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
+~~\textit{vmaxN$_{p1}$}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
 \hline
-{P-uptake rate measured at umax}&&&\tabularnewline
-~~\textit{vmaxP\textsubscript{P3}}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
-~~\textit{vmaxP\textsubscript{P1}}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
+{p-uptake rate measured at umax}&&&\tabularnewline
+~~\textit{vmaxP$_{p3}$}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
+~~\textit{vmaxP$_{p1}$}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
 \hline
 {phytoplankton basal respiration coefficient}&&&\tabularnewline
-~~\textit{respb\textsubscript{P4}}&$0.02$&$3.1$&$26.48$\tabularnewline
-~~\textit{respb\textsubscript{P3}}&$0.02$&$2.15$&$6.35$\tabularnewline
-~~\textit{respb\textsubscript{P5}}&$0.02$&$0.81$&$8.61$\tabularnewline
+~~\textit{respb$_{p4}$}&$0.02$&$3.1$&$26.48$\tabularnewline
+~~\textit{respb$_{p3}$}&$0.02$&$2.15$&$6.35$\tabularnewline
+~~\textit{respb$_{p5}$}&$0.02$&$0.81$&$8.61$\tabularnewline
 \hline
 {phytoplankton carbon/cell}&&&\tabularnewline
-~~\textit{Qc\textsubscript{P1}}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
-~~\textit{Qc\textsubscript{P3}}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
-~~\textit{Qc\textsubscript{P2}}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
-~~\textit{Qc\textsubscript{P4}}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
+~~\textit{Qc$_{p1}$}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
+~~\textit{Qc$_{p3}$}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
+~~\textit{Qc$_{p2}$}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
+~~\textit{Qc$_{p4}$}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
 \hline
 {phytoplankton growth respiration coefficient}&&&\tabularnewline
-~~\textit{respg\textsubscript{P4}}&$0.1$&$0.98$&$7.37$\tabularnewline
+~~\textit{respg$_{p4}$}&$0.1$&$0.98$&$7.37$\tabularnewline
 \hline
@@
 \hline
-{Optimum temperature for growth(C)}&&&\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P4}}&$17$&$2.9$&$22.95$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{Z2}}&$26$&$0.18$&$2.59$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P5}}&$26$&$0.17$&$0.72$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P2}}&$22$&$0.16$&$0.82$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{Z1}}&$22$&$0.16$&$0.33$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P3}}&$17$&$0.14$&$0.78$\tabularnewline
-~~\textit{Tref(nospA+nospZ)\textsubscript{P1}}&$22$&$0.12$&$0.29$\tabularnewline
+{optimum temperature for growth(c)}&&&\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p4}$}&$17$&$2.9$&$22.95$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{z2}$}&$26$&$0.18$&$2.59$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p5}$}&$26$&$0.17$&$0.72$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p2}$}&$22$&$0.16$&$0.82$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{z1}$}&$22$&$0.16$&$0.33$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p3}$}&$17$&$0.14$&$0.78$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.12$&$0.29$\tabularnewline
 \hline
@@
 {assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
-~~\textit{Zeffic\textsubscript{P1}}&$0.4$&$0.23$&$0.55$\tabularnewline
-~~\textit{Zeffic\textsubscript{P2}}&$0.4$&$0.21$&$0.75$\tabularnewline
+~~\textit{Zeffic$_{z1}$}&$0.4$&$0.23$&$0.55$\tabularnewline
+~~\textit{Zeffic$_{z2}$}&$0.4$&$0.21$&$0.75$\tabularnewline
 \hline
 {half saturation coefficient for grazing}&&&\tabularnewline
-~~\textit{ZKa\textsubscript{P1}}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
-~~\textit{ZKa\textsubscript{P2}}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
+~~\textit{ZKa$_{z1}$}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
+~~\textit{ZKa$_{z2}$}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
 \hline
 {maximum growth rate of zooplankton}&&&\tabularnewline
-~~\textit{Zumax\textsubscript{P2}}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
-~~\textit{Zumax\textsubscript{P1}}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
+~~\textit{Zumax$_{z2}$}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
+~~\textit{Zumax$_{z1}$}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
 \hline
 {proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
-~~\textit{Zslop\textsubscript{P1}}&$0.25$&$0.12$&$0.33$\tabularnewline
+~~\textit{Zslop$_{z1}$}&$0.25$&$0.12$&$0.33$\tabularnewline
 \hline
-{Zooplankton biomass-dependent respiration factor}&&&\tabularnewline
-~~\textit{Zrespb\textsubscript{P1}}&$0.1$&$0.45$&$3.02$\tabularnewline
-~~\textit{Zrespb\textsubscript{P2}}&$0.42$&$0.09$&$1.05$\tabularnewline
+{zooplankton biomass-dependent respiration factor}&&&\tabularnewline
+~~\textit{Zrespb$_{z1}$}&$0.1$&$0.45$&$3.02$\tabularnewline
+~~\textit{Zrespb$_{z2}$}&$0.42$&$0.09$&$1.05$\tabularnewline
 \hline
 {zooplankton carbon/individual}&&&\tabularnewline
-~~\textit{ZQc\textsubscript{P2}}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
-~~\textit{ZQc\textsubscript{P1}}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
+~~\textit{ZQc$_{z2}$}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
+~~\textit{ZQc$_{z1}$}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
 \hline
-{Zooplankton growth-dependent respiration factor}&&&\tabularnewline
-~~\textit{Zrespg\textsubscript{P1}}&$0.2$&$0.24$&$3.19$\tabularnewline
-~~\textit{Zrespg\textsubscript{P2}}&$0.3$&$0.12$&$0.31$\tabularnewline
+{zooplankton growth-dependent respiration factor}&&&\tabularnewline
+~~\textit{Zrespg$_{z1}$}&$0.2$&$0.24$&$3.19$\tabularnewline
+~~\textit{Zrespg$_{z2}$}&$0.3$&$0.12$&$0.31$\tabularnewline
 \hline
-{Zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
-~~\textit{Zm\textsubscript{P2}}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
-~~\textit{Zm\textsubscript{P1}}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
+{zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
+~~\textit{Zm$_{z2}$}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
+~~\textit{Zm$_{z1}$}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
 \hline
 {zooplankton nitrogen/individual}&&&\tabularnewline
-~~\textit{ZQn\textsubscript{P1}}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
-~~\textit{ZQn\textsubscript{P2}}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
+~~\textit{ZQn$_{z1}$}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
+~~\textit{ZQn$_{z2}$}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
 \hline
 {zooplankton phosphorus/individual}&&&\tabularnewline
-~~\textit{ZQp\textsubscript{P2}}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
-~~\textit{ZQp\textsubscript{P1}}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
+~~\textit{ZQp$_{z2}$}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
+~~\textit{ZQp$_{z1}$}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
 \hline

### 2016-07-08 R/funcs.R

@@ -880,6 +880,92 @@ parcats2 <- function(as_df = FALSE){
 }
 
 ######
+# convert  parameter names to latex format
+#
+# parin chr vector of short names to convert
+# frm chr string indicating format of output
+par_txt <- function(parin, frm = 'tex'){
+
+  library(dplyr)
+  
+  # sanity check
+  if(!frm %in% c('tex', 'exp'))
+    stop('frm argument must be "tex" or "exp"')
+  
+  # all parameters and names
+  cats <- parcats2(as_df = TRUE)[, c('cats', 'shrt')]
+  
+  # get which row the parameter is in
+  sels <- which(cats$shrt %in% parin)
+  if(length(sels) != length(parin)) stop('parin not completely matched in shrt')
+  
+  # split the names by category
+  splits <- cats[sels, ] %>% 
+    .[match(parin, .$shrt), ] %>% # this is important to make sure the output order matches with input
+    split(., .$cats)
+  
+  # gsub the shrt names differnet by category
+  subs <- lapply(splits, function(x){
+    
+    # 1-6 are phytos, 7-8 are zoops (changed to 1-2)
+    if('Temperature' %in% x$cats){
+
+      x$shrt <- gsub('_([1-6])$', '_p\\1', x$shrt)
+      x$shrt <- gsub('_[7]$', '_z1', x$shrt) 
+      x$shrt <- gsub('_[8]$', '_z2', x$shrt)  
+      
+    }
+      
+    # add p to subscript
+    if('Phytoplankton' %in% x$cats){
+      
+      x$shrt <- gsub('_([1-9])$', '_p\\1', x$shrt) 
+      
+    }
+
+    # add z to subscript
+    if('Zooplankton' %in% x$cats){
+     
+      x$shrt <- gsub('_([1-9])$', '_z\\1', x$shrt) 
+      
+    }
+    
+    # remove subscript
+    if(any(c('Optics', 'Organic Matter') %in% x$cats)){
+     
+      x$shrt <- gsub('_[1-9]$', '', x$shrt)
+       
+    }
+        
+    return(x)
+    
+  }) %>% 
+  do.call('rbind', .) %>% 
+  .$shrt
+  
+  # convert output format for tex
+  if(frm == 'tex'){
+    
+    out <- gsub('_([pz][1-9])$', '$_{\\1}$', subs)
+    out <- paste0('\\textit{', out, '}')
+      
+  }
+  
[…]

### 2016-07-08 ident_manu.Rnw
category error ranges added to text

@@
 # L1 range within categories
-# sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
-#   sens_ests_cat[., ] %>% 
-#   mutate(
-#     error = sapply(error, scinot),
-#     Parameter = par_txt(Parameter)
-#     )
+sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
+  lapply(., function(x){
+
+    with(x, which(error %in% range(error))) %>% 
+      x[., ] %>% 
+      mutate(
+        Parameter = par_txt(Parameter), 
+        error = sapply(error, scinot)
+      )
+
+    }
+  )
+
+# # average L1 within each category
+# sensave <- group_by(sens_ests_cat, Category) %>% 
+#   summarize(error = mean(error))
 
@@
 Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).
-Within categories, sensitivity ranged from
+Within categories, sensitivity ranged from \Sexpr{sensrngcat$Optics$error[1]} (\Sexpr{sensrngcat$Optics$Parameter[1]}) to \Sexpr{sensrngcat$Optics$error[2]} (\Sexpr{sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{sensrngcat$`Organic Matter`$error[1]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{sensrngcat$`Organic Matter`$error[2]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{sensrngcat$Phytoplankton$error[1]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{sensrngcat$Phytoplankton$error[2]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) for phytopankton, \Sexpr{sensrngcat$Temperature$error[1]} (\Sexpr{sensrngcat$Temperature$Parameter[1]}) to \Sexpr{sensrngcat$Temperature$error[2]} (\Sexpr{sensrngcat$Temperature$Parameter[2]}) for temperature, and \Sexpr{sensrngcat$Zooplankton$error[1]} (\Sexpr{sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{sensrngcat$Zooplankton$error[2]} (\Sexpr{sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{fig:sensplo}, bottom).
+Average sensitivity values in each category were
 

### 2016-07-08 ident_manu.tex
category error ranges added to text

@@
   \vspace{1in} 
-  \\ Version Date:   Thu Jul 7 15:16:18 2016 -0500
+  \\ Version Date:   Fri Jul 8 16:33:07 2016 -0500
 	}
@@
 Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank.
-Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temparature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}).
+Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temperature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton).
+Among all parameters, sensitivity values ranged from $L1 = $ $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton).
+Within categories, sensitivity ranged from $3.18\times 10^{-6}$ (\textit{Kcdom}) to $1.64$ (\textit{astar490}) for optics, $0.01$ (\textit{KGcdom}) to $2.11$ (\textit{k11}) for organic matter, $1\times 10^{-5}$ (\textit{Ksi$_{p1}$}) to $328.35$ (\textit{Qc$_{p1}$}) for phytopankton, $0.12$ (\textit{Tref(nospA+nospZ)$_{p1}$}) to $2.9$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $0$ (\textit{ZQp$_{z1}$}) to $0.82$ (\textit{ZKa$_{z1}$}) for zooplankton (\cref{fig:sensplo}, bottom).
 

### 2016-07-09 ident_manu.Rnw
local sensitivty results done

@@
 % for inline
-<<echo = FALSE>>=
+<<echo = FALSE, cache = F>>=
 data(sens_ests)
@@
 
-# # average L1 within each category
-# sensave <- group_by(sens_ests_cat, Category) %>% 
-#   summarize(error = mean(error))
+# average L1, all and by category
+sensave <- scinot(mean(sens_ests_cat$error))
+sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
+  lapply(., function(x) scinot(mean(x$error)))
 
+# phyto errors
+phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>% 
+  separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
+  group_by(grp) %>%
+  summarise(grpave = mean(error)) %>% 
+  arrange(-grpave) %>% 
+  mutate(grpave = sapply(grpave, scinot))
+
+# zoop errors 
+zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>% 
+  separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
+  group_by(grp) %>%
+  summarise(grpave = mean(error)) %>% 
+  arrange(-grpave) %>% 
+  mutate(grpave = sapply(grpave, scinot))
 @
@@
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}).
+Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{sensave}.
 Within categories, sensitivity ranged from \Sexpr{sensrngcat$Optics$error[1]} (\Sexpr{sensrngcat$Optics$Parameter[1]}) to \Sexpr{sensrngcat$Optics$error[2]} (\Sexpr{sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{sensrngcat$`Organic Matter`$error[1]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{sensrngcat$`Organic Matter`$error[2]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{sensrngcat$Phytoplankton$error[1]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{sensrngcat$Phytoplankton$error[2]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) for phytopankton, \Sexpr{sensrngcat$Temperature$error[1]} (\Sexpr{sensrngcat$Temperature$Parameter[1]}) to \Sexpr{sensrngcat$Temperature$error[2]} (\Sexpr{sensrngcat$Temperature$Parameter[2]}) for temperature, and \Sexpr{sensrngcat$Zooplankton$error[1]} (\Sexpr{sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{sensrngcat$Zooplankton$error[2]} (\Sexpr{sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{fig:sensplo}, bottom).
-Average sensitivity values in each category were
+Average sensitivity values in each category were $L1 = $ \Sexpr{sensave_cat$Optics} for optics, \Sexpr{sensave_cat$`Organic Matter`} for organic matter, \Sexpr{sensave_cat$Phytoplankton} for phytoplankton, \Sexpr{sensave_cat$Temperature} for temperature, and \Sexpr{sensave_cat$Zooplankton} for zooplankton.
+Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitues varied.
+Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ \Sexpr{phytogrps[1, 2]}, \Sexpr{phytogrps[2, 2]}), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
+Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two)
 
-what parameters in each category had the greatest sensitivity (\cref{fig:sensplo}), what were sensitivity magnitudes between categories, did these vary by phyto or zoop groups?
-
-Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplo}).
+Response of \ac{do} to parameter perturbations was not uniform acros the time series.
+\Cref{fig:sensplo} shows variation for the top parameters within each category.
+Because FishTank does not include a spatial component, the estimated \ac{do} trend describes a closed, heterotrophic system where respiration processes eventually remove all \ac{do} from the model space.
+The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January), the spring/summer increase represents production associated with expected seasonal maxima, and the remaining time series from August to the end of year shows complete removal of \ac{do} from the system as respiration processes dominate metabolic activity.
+Although this time series is not a realistic depiction of an actual system, the model behaves as expected in the absence of the hydrodynamic model.
+Accordingly, the interpretation of sensitivity results from the simple model has relevance in an ecological context.
+As expected, parameter perturbations had the largest effect during the summer months, although the effects varied.
+An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, \Sexpr{sensrngcat$Zooplankton$Parameter[2]}, which caused an increase in \ac{do}.
+The phytoplankton parameter, \Sexpr{sensrngcat$Phytoplankton$Parameter[2]}, had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.
+The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (\Sexpr{sensrngcat$Optics$Parameter[2]}) and phytoplankton (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) parameters.
 
@@
   expression(atop('Temperature', italic(Tref(nospA+nospZ)[italic('p4')]))),
-  expression(atop('Zooplankton', italic(Zka[italic('p1')])))
+  expression(atop('Zooplankton', italic(Zka[italic('z1')])))
   )
@@
 
+% heuristic plots o2
 <<heurist, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics.
@@
 
+% heuristic plots, all state
 <<heurist_stts, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables.
@@
 
+% optics sensitivity
 <<optsens, eval = T, cache = F>>=
@@
 
+% organic matter sensitivity
 <<omsens, eval = T, cache = F>>=
@@
 
+% phytoplankton sensitivity
 <<phytosens, eval = T, cache = F>>=
@@
 
+% temperature sensitivity
 <<tempsens, eval = T, cache = F >>=
@@
 
+% zooplankton sensitivity
 <<zoopsens, eval = T, cache = F>>=

### 2016-07-09 ident_manu.tex
local sensitivty results done

@@
   \vspace{1in} 
-  \\ Version Date:   Fri Jul 8 16:33:07 2016 -0500
+  \\ Version Date:   Fri Jul 8 16:56:17 2016 -0500
 	}
@@
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton).
+Among all parameters, sensitivity values ranged from $L1 = $ $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $4.52$.
 Within categories, sensitivity ranged from $3.18\times 10^{-6}$ (\textit{Kcdom}) to $1.64$ (\textit{astar490}) for optics, $0.01$ (\textit{KGcdom}) to $2.11$ (\textit{k11}) for organic matter, $1\times 10^{-5}$ (\textit{Ksi$_{p1}$}) to $328.35$ (\textit{Qc$_{p1}$}) for phytopankton, $0.12$ (\textit{Tref(nospA+nospZ)$_{p1}$}) to $2.9$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $0$ (\textit{ZQp$_{z1}$}) to $0.82$ (\textit{ZKa$_{z1}$}) for zooplankton (\cref{fig:sensplo}, bottom).
+Average sensitivity values in each category were $L1 = $ $0.42$ for optics, $1.24$ for organic matter, $5.96$ for phytoplankton, $0.55$ for temperature, and $0.27$ for zooplankton.
+Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitues varied.
+Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ $19.71$, $14.56$), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
+Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0.31$, $0.23$ for groups one and two)
 
-what parameters in each category had the greatest sensitivity (\cref{fig:sensplo}), what were sensitivity magnitudes between categories, did these vary by phyto or zoop groups?
-
-Plotting the raw values from the sensitivity analysis provides a visual assessment of changes (\cref{fig:sensplo}).
+Response of \ac{do} to parameter perturbations was not uniform acros the time series.
+\Cref{fig:sensplo} shows variation for the top parameters within each category.
+Because FishTank does not include a spatial component, the estimated \ac{do} trend describes a closed, heterotrophic system where respiration processes eventually remove all \ac{do} from the model space.
+The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January), the spring/summer increase represents production associated with expected seasonal maxima, and the remaining time series from August to the end of year shows complete removal of \ac{do} from the system as respiration processes dominate metabolic activity.
+Although this time series is not a realistic depiction of an actual system, the model behaves as expected in the absence of the hydrodynamic model.
+Accordingly, the interpretation of sensitivity results from the simple model has relevance in an ecological context.
+As expected, parameter perturbations had the largest effect during the summer months, although the effects varied.
+An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, \textit{ZKa$_{z1}$}, which caused an increase in \ac{do}.
+The phytoplankton parameter, \textit{Qc$_{p1}$}, had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.
+The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (\textit{astar490}) and phytoplankton (\textit{Qc$_{p1}$}) parameters.
 
@@
 
+% heuristic plots o2
 \begin{figure}[!ht]
@@
 
+% heuristic plots, all state
 \begin{figure}[!ht]
@@
 
+% optics sensitivity
 %latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
@@
 
+% organic matter sensitivity
 %latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
@@
 
+% phytoplankton sensitivity
 %latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
@@
 
+% temperature sensitivity
 %latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
@@
 
+% zooplankton sensitivity
 %latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%

### 2016-07-09 ident_manu.Rnw
started identifiability results section

@@
 
+<<>>=
+data(cat_ident)
+data(top_ident)
+
+# percent combos less than gamma 15, 10 by category
+collcatpers <- lapply(cat_ident, function(x){
+
+  colls <- x$coll
+  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+  c(l15, l10)
+
+  })
+
+# percent combos less than gamma 15, 10 by top in each category
+colltoppers <- lapply(top_ident, function(x){
+
+  colls <- x$coll
+  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+  c(l15, l10)
+
+  })
+
+@
+
+The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
+By category, identifiability was lowest for parameter subsets in the phytoplankton (\Sexpr{collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$)  and zooplankton categories (\Sexpr{collcatpers$Zooplankton[1]}\%, \Sexpr{collcatpers$Zooplankton[2]}\%), whereas a majority of combinations for temperature were identifiable (\Sexpr{collcatpers$Temperature[1]}\%, \Sexpr{collcatpers$Temperature[2]}\%).
+All subset combinations for optics and organic matter parmeters had $\gamma < 15$.
+All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\% less than $\gamma = 10$) and top five (\Sexpr{colltoppers$top4[1]}\%, \Sexpr{colltoppers$top4[2]}\%) parameters.
+A comparison of average and median identifiability by parameter category or top parameters in each category...
+something about jump
+
 \cref{fig:identbox} shows identifiability ranges, describe by category, also emphasize that selection independent of category may be more appropriate (better identifiability).
@@
 \section{Discussion}
+
+Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).
 

### 2016-07-09 ident_manu.tex
started identifiability results section

@@
   \vspace{1in} 
-  \\ Version Date:   Fri Jul 8 16:56:17 2016 -0500
+  \\ Version Date:   Sat Jul 9 14:44:18 2016 -0500
 	}
@@
 
+The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
+By category, identifiability was lowest for parameter subsets in the phytoplankton ($7$\% less than $\gamma = 15$, $5.9$\% less than $\gamma = 10$)  and zooplankton categories ($28.9$\%, $24.2$\%), whereas a majority of combinations for temperature were identifiable ($83.3$\%, $73.3$\%).
+All subset combinations for optics and organic matter parmeters had $\gamma < 15$.
+All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four ($77$\% less than $\gamma = 15$, $70.8$\% less than $\gamma = 10$) and top five ($77$\%, $70.8$\%) parameters.
+A comparison of average and median identifiability by parameter category or top parameters in each category...
+something about jump
+
 \cref{fig:identbox} shows identifiability ranges, describe by category, also emphasize that selection independent of category may be more appropriate (better identifiability).

### 2016-07-10 ident_manu.Rnw
more identifiability results

--- 2016-07-09 ident_manu.Rnw
@@
 
-\cref{fig:identbox} shows identifiability ranges, describe by category, also emphasize that selection independent of category may be more appropriate (better identifiability).
-Jumps in median suggest inclusion of a specific parameter has disproportionate affect on identifiability.
+<<identres>>=
+data(cat_ident)
+data(top_ident)
 
-Note that identifiability for one phytoplankton group and one zooplankton group needs to be evaluated, lots of redundancy between groups.
+# percent combos less than gamma 15, 10 by category
+collcatpers <- lapply(cat_ident, function(x){
+
+  colls <- x$coll
+  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+  c(l15, l10)
+
+  })
+
+# percent combos less than gamma 15, 10 by top in each category
+colltoppers <- lapply(top_ident, function(x){
+
+  colls <- x$coll
+  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+  c(l15, l10)
+
+  })
+
+maxtempcoll <- scinot(max(cat_ident$Temperature$coll))
+@
+
+The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
+By category, identifiability was lowest for parameter subsets in the phytoplankton (\Sexpr{collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$)  and zooplankton categories (\Sexpr{collcatpers$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{collcatpers$Zooplankton[2]}\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable (\Sexpr{collcatpers$Temperature[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Temperature[2]}\%, less than $\gamma = 10$).
+All subset combinations for optics and organic matter parmeters had $\gamma < 10$.
+All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\% less than $\gamma = 10$) and top five (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\%, less than $\gamma = 10$) parameters.
+
+<<echo = F>>=
+temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
+
+@
+
+A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
+For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.
+Further evaluation showed that identifiability was greatly affected by the inclusion of two parameters in a subset combination.
+\Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.
+Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.
+Exclusion of the parameters \Sexpr{temp_coll[2]} and \Sexpr{temp_coll[5]} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.
+Morever, inclusion of \Sexpr{temp_coll[1]}, \Sexpr{temp_coll[4]}, \Sexpr{temp_coll[7]}, and \Sexpr{temp_coll[8]} generally reduced collinearity relative to when the parameters were excluded.
+Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).
+
+Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
+As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.
+However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differenceses between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs.
+fast-growing plankton.
+To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group.
 
@@
 \section{Discussion}
+
+Emphasize that parameters that have the greatest effect on collinearity are not those that have the highest sensitivity (contrast the identifiability by category vs identifiability by top parameters)  , also note that groups of parameters together can have large effects on collinearity, maybe some kind of bootstrap analysis could be done looking at doubletons, etc.
+The example in teh results highlights how redundant variables can be identified as a necessary part of the model calibration process.
+
+Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).
 
@@
 
+% parameter exclusion temp
+<<excltemp, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of temperature parameters for subset combinations in \\cref{fig:identbox}.
+Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
+Identifiability of including all seven parameters is in \\cref{fig:identbox}.
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 8, fig.width = 5, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
+data(cat_ident)
+
+toplo <- cat_ident$`Temperature` %>% 
+  gather('parm', 'inc', -N, -coll) %>% 
+  ungroup %>% 
+  filter(N < max(N)) %>% 
+  mutate(
+    parm = as.character(par_txt(parm, frm = 'exp')),
+    N = factor(N), 
+    inc = factor(inc, levels = c(0, 1), labels = c('excluded', 'included'))
+    )
+
+ggplot(toplo, aes(x = N, y = coll, fill = inc)) + 
+  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
+  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
+  geom_boxplot(outlier.size = 0.5, size = 0.5) + 
+  facet_wrap(~parm, label = label_parsed, ncol = 2) + 
+  theme_minimal() + 
+  scale_fill_brewer(palette = 'Greys') + 
+  scale_y_continuous('Identifiability') +
+  scale_x_discrete('Parameters in set') + 
+  theme(
+    legend.title = element_blank(),
+    axis.line.x = element_line(),
+    axis.line.y = element_line(),
+    panel.grid.minor = element_blank(), 
+    panel.grid.major = element_blank(), 
+    legend.position = c(0.8, 0.1)
+  )
+
+@
+
 % heuristic plots o2

### 2016-07-10 ident_manu.tex
more identifiability results

--- 2016-07-09 ident_manu.tex
@@
   \vspace{1in} 
-  \\ Version Date:   Fri Jul 8 16:56:17 2016 -0500
+  \\ Version Date:   Sat Jul 9 15:31:45 2016 -0500
 	}
@@
 
-\cref{fig:identbox} shows identifiability ranges, describe by category, also emphasize that selection independent of category may be more appropriate (better identifiability).
-Jumps in median suggest inclusion of a specific parameter has disproportionate affect on identifiability.
+The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
+By category, identifiability was lowest for parameter subsets in the phytoplankton ($7$\% less than $\gamma = 15$, $5.9$\% less than $\gamma = 10$)  and zooplankton categories ($28.9$\%, less than $\gamma = 15$, $24.2$\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable ($83.3$\% less than $\gamma = 15$, $73.3$\%, less than $\gamma = 10$).
+All subset combinations for optics and organic matter parmeters had $\gamma < 10$.
+All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four ($77$\% less than $\gamma = 15$, $70.8$\% less than $\gamma = 10$) and top five ($77$\% less than $\gamma = 15$, $70.8$\%, less than $\gamma = 10$) parameters.
 
-Note that identifiability for one phytoplankton group and one zooplankton group needs to be evaluated, lots of redundancy between groups.
+A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
+For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.
+Further evaluation showed that identifiability was greatly affected by the inclusion of two parameters in a subset combination.
+\Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.
+Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.
+Exclusion of the parameters \textit{Tref(nospA+nospZ)$_{p2}$} and \textit{Tref(nospA+nospZ)$_{p5}$} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.
+Morever, inclusion of \textit{Tref(nospA+nospZ)$_{p1}$}, \textit{Tref(nospA+nospZ)$_{p4}$}, \textit{Tref(nospA+nospZ)$_{z1}$}, and \textit{Tref(nospA+nospZ)$_{z2}$} generally reduced collinearity relative to when the parameters were excluded.
+Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).
+
+Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
+As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.
+However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differenceses between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs.
+fast-growing plankton.
+To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group.
 
@@
 The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
+\end{figure}
+
+% parameter exclusion temp
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=0.6\textwidth]{figs/excltemp-1}
+
+}
+
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of temperature parameters for subset combinations in \cref{fig:identbox}.
+Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
+Identifiability of including all seven parameters is in \cref{fig:identbox}.
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:excltemp}
 \end{figure}

### 2016-07-10 R/funcs.R

@@ -894,10 +894,10 @@ par_txt <- function(parin, frm = 'tex'){
   
   # all parameters and names
   cats <- parcats2(as_df = TRUE)[, c('cats', 'shrt')]
-  
+
   # get which row the parameter is in
   sels <- which(cats$shrt %in% parin)
-  if(length(sels) != length(parin)) stop('parin not completely matched in shrt')
+  if(length(sels) != length(unique(parin))) stop('parin not completely matched in shrt')
   
   # split the names by category
   splits <- cats[sels, ] %>% 

### 2016-07-10 ident_manu.Rnw
working on p1 z1 eval

@@
 temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
-
 @
@@
 For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.
-Further evaluation showed that identifiability was greatly affected by the inclusion of two parameters in a subset combination.
+Further evaluation showed that identifiability was greatly affected by the inclusion of one or two specific parameters in a subset combination.
 \Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.
@@
 
+% identifiability boxplot, p1, z1 only
+<<p1z1identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
+Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.', fig.height = 10, fig.width = 4, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
+data(p1z1cat_ident)
+data(p1z1top_ident)
+
+toplo1 <- p1z1cat_ident %>% 
+  lapply(., function(x) dplyr::select(x, N, coll)) %>% 
+  reshape2::melt(., id.var = c('N', 'coll')) %>% 
+  rename(Category = L1) %>% 
+  mutate(Category = factor(Category, 
+    levels = c('Phytoplankton', 'Zooplankton'),
+    labels = c('Phytoplankton', 'Zooplankton')
+    )) %>% 
+  filter(N <= 25) %>% # reduced for plot space
+  group_by(N, Category) %>% 
+  summarise(
+    ave = mean(coll), 
+    med = median(coll),
+    min = min(coll), 
+    max = max(coll)
+  )
+
+# identifiability top 1, 2, 3, 4, 5 all categories combined
+toplo2 <-  reshape2::melt(p1z1top_ident, id.var = c('N', 'coll')) %>% 
+  select(N, coll, L1) %>% 
+  mutate(L1 = factor(L1, levels = paste0('top', 1:5), labels = paste0('Top ', 1:5))) %>% 
+  rename(npercat = L1) %>% 
+  group_by(N, npercat) %>% 
+  summarise(
+    ave = mean(coll), 
+    med = median(coll),
+    min = min(coll), 
+    max = max(coll)
+  )
+
+p1 <- ggplot(toplo1, aes(x = N, group = N)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
+  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
+  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
+  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
+  theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank()
+  ) + 
+  theme(legend.position = 'none') +
+  ggtitle('(a) By parameter category')
+
+p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
+  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
+  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
+  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
+  theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank(), 
+    legend.title = element_blank()
+  ) + 
+  ggtitle('(b) By top parameters, all categories')
+
+pleg <- g_legend(p2)
+p2 <- p2 + theme(legend.position = 'none')
+
+grid.arrange(
+  arrangeGrob(p1, p2, ncol = 1, heights = c(0.5, 1)),
+  left = 'Identifiability', 
+  bottom = 'Parameters in set',
+  pleg, ncol = 2, widths = c(1, 0.1)
+)
+
+@
+
 % heuristic plots o2

### 2016-07-10 ident_manu.tex
working on p1 z1 eval

@@
   \vspace{1in} 
-  \\ Version Date:   Sat Jul 9 15:31:45 2016 -0500
+  \\ Version Date:   Sun Jul 10 14:28:00 2016 -0500
 	}
@@
 Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:excltemp}
+\end{figure}
+
+% identifiability boxplot, p1, z1 only
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=0.6\textwidth]{figs/p1z1identbox-1}
+
+}
+
+\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
+Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.}\label{fig:p1z1identbox}
 \end{figure}

### 2016-07-11 ident_manu.Rnw
p1z1 ident fig done

@@
 As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.
-However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differenceses between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs.
+However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs.
 fast-growing plankton.
-To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group.
+To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
 
@@
 Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.', fig.height = 10, fig.width = 4, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.', fig.height = 8, fig.width = 4.5, echo = F, cache = TRUE, out.width = '0.5\\textwidth'>>=
 data(p1z1cat_ident)
@@
 
+p1 <- ggplot(toplo1, aes(x = N, group = N)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
+  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
+  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
+  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
+  scale_x_continuous(limits = c(1, 20)) +
+  theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank()
+  ) + 
+  theme(legend.position = 'none') +
+  ggtitle('(a) By parameter category')
+
 # identifiability top 1, 2, 3, 4, 5 all categories combined
@@
 
-p1 <- ggplot(toplo1, aes(x = N, group = N)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
-  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
-  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
-  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
-  theme_minimal() + 
-  theme(
-    axis.line.x = element_line(), 
-    axis.line.y = element_line(), 
-    axis.title.x = element_blank(), 
-    axis.title.y = element_blank()
-  ) + 
-  theme(legend.position = 'none') +
-  ggtitle('(a) By parameter category')
-
 p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
@@
   facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
+  scale_x_continuous(limits = c(1, 20)) +
   theme_minimal() + 
@@
 
+# align widths of plots in first column, first two
+pA <- ggplot_gtable(ggplot_build(p1))
+pB <- ggplot_gtable(ggplot_build(p2))
+maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3])
+
+# Set the widths
+pA$widths[2:3] <- maxWidth
+pB$widths[2:3] <- maxWidth
+
 grid.arrange(
-  arrangeGrob(p1, p2, ncol = 1, heights = c(0.5, 1)),
+  arrangeGrob(pA, pB, ncol = 1, heights = c(0.45, 1)),
   left = 'Identifiability', 
   bottom = 'Parameters in set',
-  pleg, ncol = 2, widths = c(1, 0.1)
+  pleg, ncol = 2, widths = c(1, 0.15)
 )

### 2016-07-11 ident_manu.tex
p1z1 ident fig done

@@
   \vspace{1in} 
-  \\ Version Date:   Sun Jul 10 14:28:00 2016 -0500
+  \\ Version Date:   Sun Jul 10 15:30:23 2016 -0500
 	}
@@
 
-{\centering \includegraphics[width=0.6\textwidth]{figs/p1z1identbox-1}
+{\centering \includegraphics[width=0.5\textwidth]{figs/p1z1identbox-1}
 

### 2016-07-11 ident_manu.Rnw
results text done

@@
 The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January), the spring/summer increase represents production associated with expected seasonal maxima, and the remaining time series from August to the end of year shows complete removal of \ac{do} from the system as respiration processes dominate metabolic activity.
-Although this time series is not a realistic depiction of an actual system, the model behaves as expected in the absence of the hydrodynamic model.
+Although this time series is not a realistic depiction of an actual system, the biogeochemical model behaves as expected in the absence of the hydrodynamic model.
 Accordingly, the interpretation of sensitivity results from the simple model has relevance in an ecological context.
@@
 
-<<identres>>=
+<<>>=
 data(cat_ident)
@@
 
-<<echo = F>>=
+<<>>=
 temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
@@
 
+<<>>=
+data(p1z1cat_ident)
+data(p1z1top_ident)
+
+# percent combos less than gamma 15, 10 by category
+p1z1collcatpers <- lapply(p1z1cat_ident, function(x){
+
+  colls <- x$coll
+  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+  c(l15, l10)
+
+  })
+
+# percent combos less than gamma 15, 10 by top in each category
+p1z1colltoppers <- lapply(p1z1top_ident, function(x){
+
+  colls <- x$coll
+  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+  c(l15, l10)
+
+  })
+@
+
 Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
@@
 To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
-
-Reading each plot from left to right can be interpreted as including additional parameters, where each parameter is ranked by relative sensitivity.
-The inset in each plot shows the identifiability of including parameters, up to a maximum where additional inclusion exceeds the identifability threshold of fifteen.
-The scenarios for including parameters all begin with the parameters that have the greatest effect on the model output.
-The inclusion of additional parameters depends on the scenario.
-The first scenario selected parameters by decreasing sensitivity within each category (i.e., four separate models calibrated for optics, organics, phytoplankton, or zooplankton), the second scenario selected parameters by sensitivity regardless of category, and the third scenario selects parameters by sensitivity with equal representation between categories.
+Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (\Sexpr{p1z1collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$ for Phytoplankton; \Sexpr{p1z1collcatpers$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Zooplankton[2]}\%, less than $\gamma = 10$ for zooplankton).
+Analysis of identifiability for top parameters in all categories did now show similar improvements in identifiability.
+Although all combinations for the top one, two, and three parameters in each category were well below the threshold, selecting the top four and five parameters showed an increase (\Sexpr{p1z1colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top4[2]}\% less than $\gamma = 10$) and a decrease (\Sexpr{p1z1colltoppers$top5[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top5[2]}\% less than $\gamma = 10$) in identifiability, respectively, compared to results that included all phytoplankton and zooplankton groups.
+
+\subsection{Parameter selection}
+
+<<>>=
+data(tocal)
+
+# n parms and ident for each selection heuristic
+h1_id <- tocal$cat %>% 
+  split(., .$Category) %>% 
+  lapply(function(x){
+    x <- x[x$coll < 15, ]
+    list(nrow(x), scinot(max(x$coll), digits = 1))
+  }) 
+h2_id <- filter(tocal$top, coll < 15) %>%
+  list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
+  .[c(2, 3)]
+h3_id <- filter(tocal$cattop, coll < 15) %>%
+  list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
+  .[c(2, 3)]
+
+# which parameter broke selection for h2, h3
+h2_brk <- tocal$top
+sel <- which(h2_brk$coll < 15)
+h2_brk <- h2_brk[c(sel, rev(sel)[1] + 1), ] %>% 
+  arrange(-coll) %>% 
+  .[1:2, ] %>% 
+  list(c(as.character(.$Parameter[1]), .$coll)) %>% 
+  .[[2]]
+# which parameter broke selection for h2, h3
+h3_brk <- tocal$cattop
+sel <- which(h3_brk$coll < 15)
+h3_brk <- h3_brk[c(sel, rev(sel)[1] + 1), ] %>% 
+  arrange(-coll) %>% 
+  .[1:2, ] %>% 
+  list(c(as.character(.$Parameter[1]), .$coll)) %>% 
+  .[[2]]
+@
+
+Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist}).
+For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).
+For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]} with a majority from the phytoplankton category.
+For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories.
+For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.
+Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.
+Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts}).
+Less than ten parameters were selected for the remaining state variables with most selected from the phytoplankton category.
+Interestingly, no parameters from the temperature category were selected.
 
@@
 The example in teh results highlights how redundant variables can be identified as a necessary part of the model calibration process.
+
+Why did identifiability decrease for top five parameters in each category after removing redundant phyto/zoop groups?
 
@@
 Identifiability of including all seven parameters is in \\cref{fig:identbox}.
-Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 8, fig.width = 5, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 8, fig.width = 5, echo = F, cache = TRUE, out.width = "0.6\\textwidth">>=
 data(cat_ident)

### 2016-07-11 ident_manu.tex
results text done

@@
   \vspace{1in} 
-  \\ Version Date:   Sun Jul 10 15:30:23 2016 -0500
+  \\ Version Date:   Mon Jul 11 09:01:42 2016 -0500
 	}
@@
 To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
+Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold ($56.3$\% less than $\gamma = 15$, $47.1$\% less than $\gamma = 10$ for Phytoplankton; $83.4$\%, less than $\gamma = 15$, $72.6$\%, less than $\gamma = 10$ for zooplankton).
+Analysis of identifiability for top parameters in all categories did now show similar improvements in identifiability.
+Although all combinations for the top one, two, and three parameters in each category were well below the threshold, selecting the top four and five parameters showed an increase ($84.2$\% less than $\gamma = 15$, $78.7$\% less than $\gamma = 10$) and a decrease ($54.4$\% less than $\gamma = 15$, $51$\% less than $\gamma = 10$) in identifiability, respectively, compared to results that included all phytoplankton and zooplankton groups.
 
-Reading each plot from left to right can be interpreted as including additional parameters, where each parameter is ranked by relative sensitivity.
-The inset in each plot shows the identifiability of including parameters, up to a maximum where additional inclusion exceeds the identifability threshold of fifteen.
-The scenarios for including parameters all begin with the parameters that have the greatest effect on the model output.
-The inclusion of additional parameters depends on the scenario.
-The first scenario selected parameters by decreasing sensitivity within each category (i.e., four separate models calibrated for optics, organics, phytoplankton, or zooplankton), the second scenario selected parameters by sensitivity regardless of category, and the third scenario selects parameters by sensitivity with equal representation between categories.
+\subsection{Parameter selection}
+
+Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist}).
+For the first selection heuristic, all sensitive parameters from the optics ($n = $ $4$, $\gamma =$  $3.7$) and organic matter ($n = $ $7$, $\gamma =$  $1.7$) categories were selected, whereas 23 were selected for phytoplankton ($\gamma = $ $13.7$), five for temperature ($\gamma = $ $11.4$), and five for zooplankton ($\gamma = $ $3.1$).
+For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$ with a majority from the phytoplankton category.
+For the third heuristic, 18 parameters were selected ($\gamma = $ $9.2$) with equal representation between categories.
+For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.
+Selection independent of category showed that including \textit{KNO3} caused in increase in $\gamma$ from $4.6$ to $15.6$ and equal selection within cateogies showed that including \textit{Tref(nospA+nospZ)$_{p2}$} caused in increase in $\gamma$ from $9.2$ to $66.2$.
+Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts}).
+Less than ten parameters were selected for the remaining state variables with most selected from the phytoplankton category.
+Interestingly, no parameters from the temperature category were selected.
 

### 2016-07-11 R/funcs.R

@@ -42,22 +42,22 @@ form_fun <- function(x, rnd_val = 2, dig_val = 2, nsm_val = 2, ...) {
 # from https://dankelley.github.io/r/2015/03/22/scinot.html
 scinot <- function(x, pow = 3, digits=2, showDollar=TRUE)
 {
-  
-    sign <- ""
-    if (x < 0) {
-        sign <- "-"
-        x <- -x
-    }
-    exponent <- floor(log10(x))
-    if (exponent & abs(exponent) > pow) {
-        xx <- round(x / 10^exponent, digits=digits)
-        e <- paste("\\times 10^{", as.integer(exponent), "}", sep="")
-    } else {
-        xx <- round(x, digits=digits)
-        e <- ""
-    }
-    if (showDollar) paste("$", sign, xx, e, "$", sep="")
-    else paste(sign, xx, e, sep="")
+  x <- as.numeric(x)
+  sign <- ""
+  if (x < 0) {
+      sign <- "-"
+      x <- -x
+  }
+  exponent <- floor(log10(x))
+  if (exponent & abs(exponent) > pow) {
+      xx <- round(x / 10^exponent, digits=digits)
+      e <- paste("\\times 10^{", as.integer(exponent), "}", sep="")
+  } else {
+      xx <- round(x, digits=digits)
+      e <- ""
+  }
+  if (showDollar) paste("$", sign, xx, e, "$", sep="")
+  else paste(sign, xx, e, sep="")
 }
 
 # alternative list structure for parameter categories

### 2016-07-11 ident_manu.Rnw
minor edits to results

@@
 Average sensitivity values in each category were $L1 = $ \Sexpr{sensave_cat$Optics} for optics, \Sexpr{sensave_cat$`Organic Matter`} for organic matter, \Sexpr{sensave_cat$Phytoplankton} for phytoplankton, \Sexpr{sensave_cat$Temperature} for temperature, and \Sexpr{sensave_cat$Zooplankton} for zooplankton.
-Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitues varied.
+Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied.
 Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ \Sexpr{phytogrps[1, 2]}, \Sexpr{phytogrps[2, 2]}), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
-Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two)
+Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two).
 
@@
 Because FishTank does not include a spatial component, the estimated \ac{do} trend describes a closed, heterotrophic system where respiration processes eventually remove all \ac{do} from the model space.
-The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January), the spring/summer increase represents production associated with expected seasonal maxima, and the remaining time series from August to the end of year shows complete removal of \ac{do} from the system as respiration processes dominate metabolic activity.
+The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January, February), the spring/summer increase represents production associated with expected seasonal growth, and the remaining time series from August to the end of year shows complete removal of \ac{do} as respiration processes dominate metabolic activity.
 Although this time series is not a realistic depiction of an actual system, the biogeochemical model behaves as expected in the absence of the hydrodynamic model.
@@
 
-The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
 Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
 By category, identifiability was lowest for parameter subsets in the phytoplankton (\Sexpr{collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$)  and zooplankton categories (\Sexpr{collcatpers$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{collcatpers$Zooplankton[2]}\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable (\Sexpr{collcatpers$Temperature[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Temperature[2]}\%, less than $\gamma = 10$).
-All subset combinations for optics and organic matter parmeters had $\gamma < 10$.
+All subset combinations for optics and organic matter parameters had $\gamma < 10$.
 All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\% less than $\gamma = 10$) and top five (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\%, less than $\gamma = 10$) parameters.
@@
 Further evaluation showed that identifiability was greatly affected by the inclusion of one or two specific parameters in a subset combination.
-\Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.
+\Cref{fig:excltemp} shows the temperature collinearity ($\gamma$) ranges in detail for the parameter subsets in \cref{fig:identbox} before and after excluding individual parameters.
 Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.
-Exclusion of the parameters \Sexpr{temp_coll[2]} and \Sexpr{temp_coll[5]} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.
+Exclusion of the parameters \Sexpr{temp_coll[2]} and \Sexpr{temp_coll[5]} showed that $\gamma$ remained well below the 10, 15 threshold for all parameter combinations.
 Morever, inclusion of \Sexpr{temp_coll[1]}, \Sexpr{temp_coll[4]}, \Sexpr{temp_coll[7]}, and \Sexpr{temp_coll[8]} generally reduced collinearity relative to when the parameters were excluded.
@@
 Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (\Sexpr{p1z1collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$ for Phytoplankton; \Sexpr{p1z1collcatpers$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Zooplankton[2]}\%, less than $\gamma = 10$ for zooplankton).
-Analysis of identifiability for top parameters in all categories did now show similar improvements in identifiability.
-Although all combinations for the top one, two, and three parameters in each category were well below the threshold, selecting the top four and five parameters showed an increase (\Sexpr{p1z1colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top4[2]}\% less than $\gamma = 10$) and a decrease (\Sexpr{p1z1colltoppers$top5[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top5[2]}\% less than $\gamma = 10$) in identifiability, respectively, compared to results that included all phytoplankton and zooplankton groups.
+Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.
+Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (\Sexpr{p1z1colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top4[2]}\% less than $\gamma = 10$) and a decrease (\Sexpr{p1z1colltoppers$top5[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top5[2]}\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).
 
@@
 For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).
-For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]} with a majority from the phytoplankton category.
+For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category).
 For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories.
@@
 Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts}).
-Less than ten parameters were selected for the remaining state variables with most selected from the phytoplankton category.
+Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
 Interestingly, no parameters from the temperature category were selected.

### 2016-07-11 ident_manu.tex
minor edits to results

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Jul 11 09:01:42 2016 -0500
+  \\ Version Date:   Mon Jul 11 10:46:03 2016 -0500
 	}
@@
 Average sensitivity values in each category were $L1 = $ $0.42$ for optics, $1.24$ for organic matter, $5.96$ for phytoplankton, $0.55$ for temperature, and $0.27$ for zooplankton.
-Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitues varied.
+Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied.
 Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ $19.71$, $14.56$), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
-Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0.31$, $0.23$ for groups one and two)
+Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0.31$, $0.23$ for groups one and two).
 
@@
 
-The identifiability analyses suggested that most parameter subsets exceeded the threshold of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
 Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
 By category, identifiability was lowest for parameter subsets in the phytoplankton ($7$\% less than $\gamma = 15$, $5.9$\% less than $\gamma = 10$)  and zooplankton categories ($28.9$\%, less than $\gamma = 15$, $24.2$\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable ($83.3$\% less than $\gamma = 15$, $73.3$\%, less than $\gamma = 10$).
-All subset combinations for optics and organic matter parmeters had $\gamma < 10$.
+All subset combinations for optics and organic matter parameters had $\gamma < 10$.
 All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four ($77$\% less than $\gamma = 15$, $70.8$\% less than $\gamma = 10$) and top five ($77$\% less than $\gamma = 15$, $70.8$\%, less than $\gamma = 10$) parameters.
@@
 Further evaluation showed that identifiability was greatly affected by the inclusion of one or two specific parameters in a subset combination.
-\Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.
+\Cref{fig:excltemp} shows the temperature collinearity ($\gamma$) ranges in detail for the parameter subsets in \cref{fig:identbox} before and after excluding individual parameters.
 Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.
-Exclusion of the parameters \textit{Tref(nospA+nospZ)$_{p2}$} and \textit{Tref(nospA+nospZ)$_{p5}$} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.
+Exclusion of the parameters \textit{Tref(nospA+nospZ)$_{p2}$} and \textit{Tref(nospA+nospZ)$_{p5}$} showed that $\gamma$ remained well below the 10, 15 threshold for all parameter combinations.
 Morever, inclusion of \textit{Tref(nospA+nospZ)$_{p1}$}, \textit{Tref(nospA+nospZ)$_{p4}$}, \textit{Tref(nospA+nospZ)$_{z1}$}, and \textit{Tref(nospA+nospZ)$_{z2}$} generally reduced collinearity relative to when the parameters were excluded.
@@
 Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold ($56.3$\% less than $\gamma = 15$, $47.1$\% less than $\gamma = 10$ for Phytoplankton; $83.4$\%, less than $\gamma = 15$, $72.6$\%, less than $\gamma = 10$ for zooplankton).
-Analysis of identifiability for top parameters in all categories did now show similar improvements in identifiability.
-Although all combinations for the top one, two, and three parameters in each category were well below the threshold, selecting the top four and five parameters showed an increase ($84.2$\% less than $\gamma = 15$, $78.7$\% less than $\gamma = 10$) and a decrease ($54.4$\% less than $\gamma = 15$, $51$\% less than $\gamma = 10$) in identifiability, respectively, compared to results that included all phytoplankton and zooplankton groups.
+Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.
+Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase ($84.2$\% less than $\gamma = 15$, $78.7$\% less than $\gamma = 10$) and a decrease ($54.4$\% less than $\gamma = 15$, $51$\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).
 
@@
 For the first selection heuristic, all sensitive parameters from the optics ($n = $ $4$, $\gamma =$  $3.7$) and organic matter ($n = $ $7$, $\gamma =$  $1.7$) categories were selected, whereas 23 were selected for phytoplankton ($\gamma = $ $13.7$), five for temperature ($\gamma = $ $11.4$), and five for zooplankton ($\gamma = $ $3.1$).
-For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$ with a majority from the phytoplankton category.
+For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$, with a majority from the phytoplankton category).
 For the third heuristic, 18 parameters were selected ($\gamma = $ $9.2$) with equal representation between categories.

### 2016-07-22 ident_manu.Rnw
Wagener stuff, started structural uncertainty placeholder

@@
 
-A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above.
+A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
 These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability).
@@
 
-Finally, the above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
+The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
 In addition to \ac{do}, other state variables included \ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
 Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
+
+\subsection{Identifiability and structural uncertainty}
+
+The sensitivity and identifiability analyses can be extended to
 
@@
 
-Response of \ac{do} to parameter perturbations was not uniform acros the time series.
+Response of \ac{do} to parameter perturbations was not uniform across the time series.
 \Cref{fig:sensplo} shows variation for the top parameters within each category.
@@
 
+We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
+14 for models that follow traditional calibration schemes (e.g., objective function minimization).
+
 Emphasize that parameters that have the greatest effect on collinearity are not those that have the highest sensitivity (contrast the identifiability by category vs identifiability by top parameters)  , also note that groups of parameters together can have large effects on collinearity, maybe some kind of bootstrap analysis could be done looking at doubletons, etc.
@@
 How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
+\citet{Wagener01} describes this as a potential approach to improving model performance by improving the availability of information for model calibration (p.
+14).
 
@@
 Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}, \citep{Arhonditsis08}
+
+Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by Wagener et al. 1999, 2001 (cited on page 15, in \citealt{Wagener01}).
 

### 2016-07-22 ident_manu.tex
Wagener stuff, started structural uncertainty placeholder

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Jul 11 10:46:03 2016 -0500
+  \\ Version Date:   Mon Jul 11 11:13:58 2016 -0500
 	}
@@
 
-Finally, the above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
+The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
 In addition to \ac{do}, other state variables included \ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
 Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
+
+\subsection{Identifiability to evaluate structural uncertainty}
+
+The sensitivity and identifiability analyses can be extended to
 

### 2016-07-29 ident_manu.Rnw
sens_ests_all and sens_ests_cat_all to data
comparing parameter sensitivity between state variables, fix to par_txt

@@
 
+% back of envelop calcs for number of relevant parms, all state variables
+<<echo = F>>=
+
+data(sens_ests_cat_all)
+
+tmp <- reshape2::melt(sens_ests_cat_all, id.var = c('Parameter', 'error', 'Category'))
+
+lims <- with(tmp, quantile(error, c(0.05, 0.95))) %>% 
+  as.numeric
+
+stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'O2', 'OM1', 'OM2', 'PO4')
+stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'Dissolved Oxygen', 'OM1', 'OM2', 'Phosphate')
+
+toplo <- filter(tmp, error < lims[2] & error > lims[1]) %>% 
+  mutate(
+    L1 = factor(L1, levels = stts_lev, labels = stts_lab)
+  )
+toplo1 <- filter(toplo, !Category %in% c('Phytoplankton', 'Zooplankton')) %>% 
+  mutate(Parameter = as.character(par_txt(Parameter, frm = 'exp')))
+toplo2 <- filter(toplo, Category %in% c('Phytoplankton')) %>% 
+  mutate(
+    grp = gsub('^.*_([1-6])$', 'p\\1', Parameter), 
+    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
+  )
+toplo3 <- filter(toplo, Category %in% c('Zooplankton')) %>% 
+  mutate(
+    grp = gsub('^.*_([1-2])$', 'z\\1', Parameter), 
+    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
+  )
+
+pbase <- theme(
+  panel.grid.major = element_blank(), 
+  panel.grid.minor = element_blank(), 
+  axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 8), 
+  axis.text.y = element_text(size =8),
+  axis.title.y = element_blank(), 
+  axis.title.x = element_blank(),
+  legend.position = 'none'
+  )
+
+p1 <- ggplot(toplo1, aes(x = Parameter, y = L1, fill = error)) + 
+  geom_tile() + 
+  pbase +
+  scale_x_discrete(expand = c(0, 0),
+    breaks = toplo1$Parameter, 
+    labels = parse(text = toplo1$Parameter)
+    ) + 
+  scale_y_discrete(expand = c(0, 0)) +
+  scale_fill_distiller(palette = "Spectral", limits = lims) + 
+  facet_grid(~Category, scales = 'free')
+p2 <- ggplot(toplo2, aes(x = Parameter, y = L1, fill = error)) + 
+  geom_tile() + 
+  pbase +
+  scale_x_discrete(expand = c(0, 0), 
+    breaks = toplo2$Parameter, 
+    labels = parse(text = toplo2$Parameter)
+    ) + 
+  scale_y_discrete(expand = c(0, 0)) +
+  scale_fill_distiller(palette = "Spectral", limits = lims) + 
+  facet_grid(~grp, scales = 'free') + 
+  ggtitle('Phytoplankton')
+p3 <- ggplot(toplo3, aes(x = Parameter, y = L1, fill = error)) + 
+  geom_tile() + 
+  pbase +
+  scale_x_discrete(expand = c(0, 0), 
+    breaks = toplo3$Parameter, 
+    labels = parse(text = toplo3$Parameter)
+    ) + 
+  scale_y_discrete(expand = c(0, 0)) + 
+  scale_fill_distiller(palette = "Spectral", limits = lims) + 
+  facet_grid(~grp, scales = 'free') + 
+  ggtitle('Zooplankton') + 
+  theme(legend.position = 'right')
+pleg <- g_legend(p3)
+p3 <- p3 + theme(legend.position = 'none')
+
+grid.arrange(
+  arrangeGrob(p1, p2, p3, ncol = 1), 
+  pleg, ncol = 2, widths =  c(1, 0.1), 
+  bottom = 'Parameter', 
+  left = 'State variable'
+)
+@
+
 We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.

### 2016-07-29 R/funcs.R

@@ -891,6 +891,8 @@ par_txt <- function(parin, frm = 'tex'){
   # sanity check
   if(!frm %in% c('tex', 'exp'))
     stop('frm argument must be "tex" or "exp"')
+
+  parin <- as.character(parin) 
   
   # all parameters and names
   cats <- parcats2(as_df = TRUE)[, c('cats', 'shrt')]
@@ -901,48 +903,48 @@ par_txt <- function(parin, frm = 'tex'){
   
   # split the names by category
   splits <- cats[sels, ] %>% 
-    .[match(parin, .$shrt), ] %>% # this is important to make sure the output order matches with input
-    split(., .$cats)
+    .[match(parin, .$shrt), ] # this is important to make sure the output order matches with input
   
   # gsub the shrt names differnet by category
-  subs <- lapply(splits, function(x){
-    
-    # 1-6 are phytos, 7-8 are zoops (changed to 1-2)
-    if('Temperature' %in% x$cats){
+  subs <- apply(splits, 1,  function(x){
 
-      x$shrt <- gsub('_([1-6])$', '_p\\1', x$shrt)
-      x$shrt <- gsub('_[7]$', '_z1', x$shrt) 
-      x$shrt <- gsub('_[8]$', '_z2', x$shrt)  
+    # 1-6 are phytos, 7-8 are zoops (changed to 1-2)
+    if('Temperature' %in% x['cats']){
+
+      x['shrt'] <- gsub('_([1-6])$', '_p\\1', x['shrt'])
+      x['shrt'] <- gsub('_[7]$', '_z1', x['shrt']) 
+      x['shrt'] <- gsub('_[8]$', '_z2', x['shrt'])  
       
     }
       
     # add p to subscript
-    if('Phytoplankton' %in% x$cats){
+    if('Phytoplankton' %in% x['cats']){
       
-      x$shrt <- gsub('_([1-9])$', '_p\\1', x$shrt) 
+      x['shrt'] <- gsub('_([1-9])$', '_p\\1', x['shrt']) 
       
     }
 
     # add z to subscript
-    if('Zooplankton' %in% x$cats){
+    if('Zooplankton' %in% x['cats']){
      
-      x$shrt <- gsub('_([1-9])$', '_z\\1', x$shrt) 
+      x['shrt'] <- gsub('_([1-9])$', '_z\\1', x['shrt']) 
       
     }
     
     # remove subscript
[…]

### 2016-07-30 ident_manu.Rnw
sensalltile to supplementary

--- 2016-07-22 ident_manu.Rnw
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank.
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
 Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}).
@@
 
+% back of envelop calcs for number of relevant parms, all state variables
+<<echo = F>>=
+
+@
 We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
@@
 \end{singlespace}
+\clearpage
+
+%%%%%%
+% tables
+
+% optics sensitivity
+<<optsens, eval = T, cache = F>>=
+senstab1('Optics', 'optsens')
+@
+
+% organic matter sensitivity
+<<omsens, eval = T, cache = F>>=
+senstab1('Organic Matter', 'omsens')
+@
+
+% phytoplankton sensitivity
+<<phytosens, eval = T, cache = F>>=
+# data(sens_ests_cat)
+# tmp <- filter(sens_ests_cat, Category == 'Phytoplankton')
+# quantile(tmp$error)
+senstab2('Phytoplankton', 'phytosens', sub = 0.59, sub.txt = 'Parameters less than the 75\\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.')
+@
+
+% temperature sensitivity
+<<tempsens, eval = T, cache = F >>=
+senstab2('Temperature', 'tempsens')
+@
+
+% zooplankton sensitivity
+<<zoopsens, eval = T, cache = F>>=
+senstab2('Zooplankton', 'zoopsens')
+@
 \clearpage
@@
 @
-
 \clearpage
-%%%%%%
-% tables
-
-% optics sensitivity
-<<optsens, eval = T, cache = F>>=
-senstab1('Optics', 'optsens')
-@
-
-% organic matter sensitivity
-<<omsens, eval = T, cache = F>>=
-senstab1('Organic Matter', 'omsens')
-@
-
-% phytoplankton sensitivity
-<<phytosens, eval = T, cache = F>>=
-# data(sens_ests_cat)
-# tmp <- filter(sens_ests_cat, Category == 'Phytoplankton')
-# quantile(tmp$error)
-senstab2('Phytoplankton', 'phytosens', sub = 0.59, sub.txt = 'Parameters less than the 75\\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.')
-@
-
-% temperature sensitivity
-<<tempsens, eval = T, cache = F >>=
-senstab2('Temperature', 'tempsens')
-@
-
-% zooplankton sensitivity
-<<zoopsens, eval = T, cache = F>>=
-senstab2('Zooplankton', 'zoopsens')
+
+% supplementary material
+\beginsupplement
+
+<<sensalltile, echo = F, fig.height = 9, fig.width = 9, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
+Values are truncated by the 5\\textsuperscript{th} and 95\\textsuperscript{th} sensitivity values between all parameters for visual appearance.
+Parameters are grouped by category (plot strips).
+Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.'>>=
+data(sens_ests_cat_all)
+
+tmp <- reshape2::melt(sens_ests_cat_all, id.var = c('Parameter', 'error', 'Category'))
+
+lims <- with(tmp, quantile(error, c(0.05, 0.95))) %>% 
+  as.numeric
+
+stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'O2', 'OM1', 'OM2', 'PO4')
+stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'Dissolved Oxygen', 'OM1', 'OM2', 'Phosphate')
+
+toplo <- filter(tmp, error < lims[2] & error > lims[1]) %>% 
+  mutate(
+    L1 = factor(L1, levels = stts_lev, labels = stts_lab)
+  ) %>% 
+  rename(Sensitivity = error)
+
+toplo1 <- filter(toplo, !Category %in% c('Phytoplankton', 'Zooplankton')) %>% 
+  mutate(Parameter = as.character(par_txt(Parameter, frm = 'exp')))
+toplo2 <- filter(toplo, Category %in% c('Phytoplankton')) %>% 
+  mutate(
+    grp = gsub('^.*_([1-6])$', 'p\\1', Parameter), 
+    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
+  )
+toplo3 <- filter(toplo, Category %in% c('Zooplankton')) %>% 
+  mutate(
+    grp = gsub('^.*_([1-2])$', 'z\\1', Parameter), 
+    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
+  )
+
+pbase <- theme(
+  panel.grid.major = element_blank(), 
+  panel.grid.minor = element_blank(), 
+  axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6), 
+  axis.text.y = element_text(size =8),
+  axis.title.y = element_blank(), 
+  axis.title.x = element_blank(),
+  legend.position = 'none', 
+  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt')
+  )
+
+p1 <- ggplot(toplo1, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
+  geom_tile() + 
+  pbase +
+  scale_x_discrete(expand = c(0, 0),
+    breaks = toplo1$Parameter, 
+    labels = parse(text = toplo1$Parameter)
+    ) + 
+  scale_y_discrete(expand = c(0, 0)) +
+  scale_fill_distiller(palette = "Spectral", limits = lims) + 
+  facet_grid(~Category, scales = 'free')
+p2 <- ggplot(toplo2, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
+  geom_tile() + 
+  pbase +
+  scale_x_discrete(expand = c(0, 0), 
+    breaks = toplo2$Parameter, 
+    labels = parse(text = toplo2$Parameter)
+    ) + 
+  scale_y_discrete(expand = c(0, 0)) +
+  scale_fill_distiller(palette = "Spectral", limits = lims) + 
+  facet_grid(~grp, scales = 'free') + 
+  ggtitle('Phytoplankton')
+p3 <- ggplot(toplo3, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
+  geom_tile() + 
+  pbase +
+  scale_x_discrete(expand = c(0, 0), 
+    breaks = toplo3$Parameter, 
+    labels = parse(text = toplo3$Parameter)
+    ) + 
+  scale_y_discrete(expand = c(0, 0)) + 
+  scale_fill_distiller(palette = "Spectral", limits = lims) + 
+  facet_grid(~grp, scales = 'free') + 
+  ggtitle('Zooplankton') + 
+  theme(legend.position = 'top')
+pleg <- g_legend(p3)
+p3 <- p3 + theme(legend.position = 'none')
+
+grid.arrange(
+  pleg, p1, p2, p3, ncol = 1, 
+  heights = c(0.2, 1, 0.85, 1),
+  bottom = 'Parameter', 
+  left = 'State variable'
+)
 @

### 2016-07-30 ident_manu.tex
sens_ests_all and sens_ests_cat_all to data
sensalltile to supplementary

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Jul 11 11:13:58 2016 -0500
+  \\ Version Date:   Fri Jul 29 17:27:00 2016 -0500
 	}
@@
 
-\subsection{Identifiability to evaluate structural uncertainty}
+\subsection{Identifiability and structural uncertainty}
 
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank.
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
 Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temperature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}).
@@
 
+% back of envelop calcs for number of relevant parms, all state variables
+
 We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
@@
 
-%%%%%%
-% figures
-
-% combination example
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=0.6\textwidth]{figs/combnex-1}
-
-}
-
-\caption[Examples of unique parameter combinations from different parameter sets and number of selected parameters]{Examples of unique parameter combinations from different parameter sets and number of selected parameters.
-The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
-Note that the number of unique combinations is shown as the natural-log.}\label{fig:combnex}
-\end{figure}
-
-% sensitivity example of top
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\maxwidth]{figs/sensplo-1}
-
-}
-
-\caption{Sensitivity of \ac{do} to parameter changes.
-The solid lines show the change in \ac{do} based on a 50\% change from the default parameter values (dashed line) for each parameter.
-Individual parameters with the largest effect are shown for each category.
-The top plot shows the model output and the middle plot shows the estimated \ac{do} as a difference from the default.
-The bottom plot shows the distribution of error values (as $log\left(L1\right)$) for all parmaters in each category.}\label{fig:sensplo}
-\end{figure}
-
-% identifiability boxplots
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\maxwidth]{figs/identbox-1}
-
-}
-
-\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.
-Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
-The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
-\end{figure}
-
-% parameter exclusion temp
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=0.6\textwidth]{figs/excltemp-1}
-
-}
-
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of temperature parameters for subset combinations in \cref{fig:identbox}.
-Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
-Identifiability of including all seven parameters is in \cref{fig:identbox}.
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:excltemp}
-\end{figure}
-
-% identifiability boxplot, p1, z1 only
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=0.5\textwidth]{figs/p1z1identbox-1}
-
-}
-
-\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
-Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.}\label{fig:p1z1identbox}
-\end{figure}
-
-% heuristic plots o2
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/heurist-1}
-
-}
-
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters with three different heuristics.
-Parameters are selected by decreasing sensitivity for all examples (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
-The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c).
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.}\label{fig:heurist}
-\end{figure}
-
-% heuristic plots, all state
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/heurist_stts-1}
-
-}
-
-\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables.
-Parameters are selected by decreasing sensitivity indepent of parameter categories.
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
-\end{figure}
-
-\clearpage
 %%%%%%
@@
 
+\clearpage
+
+%%%%%%
+% figures
+
+% combination example
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=0.6\textwidth]{figs/combnex-1}
+
+}
+
+\caption[Examples of unique parameter combinations from different parameter sets and number of selected parameters]{Examples of unique parameter combinations from different parameter sets and number of selected parameters.
+The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
+Note that the number of unique combinations is shown as the natural-log.}\label{fig:combnex}
+\end{figure}
+
+% sensitivity example of top
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\maxwidth]{figs/sensplo-1}
+
+}
+
+\caption{Sensitivity of \ac{do} to parameter changes.
+The solid lines show the change in \ac{do} based on a 50\% change from the default parameter values (dashed line) for each parameter.
+Individual parameters with the largest effect are shown for each category.
+The top plot shows the model output and the middle plot shows the estimated \ac{do} as a difference from the default.
+The bottom plot shows the distribution of error values (as $log\left(L1\right)$) for all parmaters in each category.}\label{fig:sensplo}
+\end{figure}
+
+% identifiability boxplots
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\maxwidth]{figs/identbox-1}
+
+}
+
+\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.
+Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
+The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
+\end{figure}
+
+% parameter exclusion temp
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=0.6\textwidth]{figs/excltemp-1}
+
+}
+
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of temperature parameters for subset combinations in \cref{fig:identbox}.
+Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
+Identifiability of including all seven parameters is in \cref{fig:identbox}.
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:excltemp}
+\end{figure}
+
+% identifiability boxplot, p1, z1 only
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=0.5\textwidth]{figs/p1z1identbox-1}
+
+}
+
+\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
+Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.}\label{fig:p1z1identbox}
+\end{figure}
+
+% heuristic plots o2
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/heurist-1}
+
+}
+
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters with three different heuristics.
+Parameters are selected by decreasing sensitivity for all examples (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
+The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c).
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.}\label{fig:heurist}
+\end{figure}
+
+% heuristic plots, all state
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/heurist_stts-1}
+
+}
+
+\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables.
+Parameters are selected by decreasing sensitivity indepent of parameter categories.
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
+\end{figure}
+
+\clearpage
+
+% supplementary material
+\beginsupplement
+
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/sensalltile-1}
+
+}
+
+\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
+Values are truncated by the 5\textsuperscript{th} and 95\textsuperscript{th} sensitivity values between all parameters for visual appearance.
+Parameters are grouped by category (plot strips).
+Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.}\label{fig:sensalltile}
+\end{figure}
+
 \end{document}

### 2016-07-30 ident_manu.Rnw
state variable factor order changed

@@
 cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
-stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'OM1', 'OM2', 'PO4')
-stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
+stts_lev <- c('NH4', 'Chla_mg_tot', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4')
+stts_lab <- c('Ammonium', 'Chlorophyll', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
 
@@
 Parameters are grouped by category (plot strips).
-Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.'>>=
+Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1-p6, z1, z2), respectively.'>>=
 data(sens_ests_cat_all)
@@
 
-stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'O2', 'OM1', 'OM2', 'PO4')
-stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'Dissolved Oxygen', 'OM1', 'OM2', 'Phosphate')
+stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
 

### 2016-07-30 ident_manu.tex
state variable factor order changed

@@
   \vspace{1in} 
-  \\ Version Date:   Fri Jul 29 17:27:00 2016 -0500
+  \\ Version Date:   Sat Jul 30 12:31:08 2016 -0500
 	}
@@
 Parameters are grouped by category (plot strips).
-Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.}\label{fig:sensalltile}
+Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1-p6, z1, z2), respectively.}\label{fig:sensalltile}
 \end{figure}

### 2016-07-30 ident_manu.Rnw
ident tables added

@@
 library(english)
+library(purrr)
 @
@@
 
-Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist}).
+Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
 For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).
-For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category).
+For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category, \cref{tab:identall1}).
 For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories.
@@
 Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.
-Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts}).
+Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
 Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
@@
 senstab2('Zooplankton', 'zoopsens')
+@
+
+% ident all states
+<<identdo, eval = T, cache = F>>=
+data(tocal_all)
+
+# factor levels
+cats_lev <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+cats_lab <- c('O', 'OM', 'P', 'T', 'Z')
+stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+
+labs <- parcats2(as_df = T) %>% 
+    rename(Parameter = shrt) %>% 
+    select(Parameter, lngs)
+
+# format tocal_all for identifiability table
+# add long parameter name
+# get parameter combos with coll < 15 + 1
+# format error and coll with scinot
+# format category label so no duplicates
+totab <- tocal_all$top_all %>% 
+  reshape2::melt(., id.var = names(.[[1]])) %>%
+  mutate(Parameter = as.character(Parameter)) %>% 
+  left_join(., labs, by = 'Parameter') %>% 
+  mutate(
+    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
+    lngs = gsub('_', '', lngs), 
+    stts = factor(L1, levels = stts_lev, labels = stts_lab),
+    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
+    Parameter = par_txt(Parameter, frm = 'tex')
+  ) %>% 
+  split(., .$L1) %>% 
+  lapply(function(x){
+
+    sel <- which(x$coll < 15)
+    x <- x[sel, ] %>% 
+    # x <- x[c(sel, max(sel) + 1), ] %>% 
+      na.omit
+    x
+
+  }) %>% 
+  do.call('rbind', .) %>%
+  mutate(
+    error = sapply(error, scinot),
+    coll = sapply(coll, scinot), 
+    Rank = sapply(rnk_incat, scinot), 
+    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
+    ) %>%
+  group_by(stts) %>% 
+  nest %>% 
+  unnest %>% 
+  select(stts, lngs, Parameter, Rank, error, coll) %>% 
+  rename(
+    Description = lngs, 
+    L1 = error
+  ) %>% 
+  mutate(
+    stts = as.character(stts),
+    Description = paste0('\\scriptsize{', Description, '}'),
+    Parameter = paste0('\\scriptsize{', Parameter, '}')
+    ) %>% 
+  arrange(stts)
+
+identall1 <- filter(totab, stts %in% 'Dissolved Oxygen')
+
+# final table formatting
+descrip <- as.character(identall1$Description)
+identall1 <- identall1[,-c(1, 2)]
+cap_val<- 'Parameter identifiability for dissolved oxygen.
+Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.
+Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
+colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')
+
+latex( 
+  identall1,
+  file = '',
+  rowlabel = 'Parameter description',
+  caption = cap_val,
+  caption.loc = 'top',
+  size = 'footnotesize',
+  label = 'tab:identall1',
+  rowname = descrip,
+  colheads = colnms,
+  rgroupTexCmd = NULL
+  )
+@
+
+% ident all states
+<<identall, eval = T, cache = F>>=
+data(tocal_all)
+
+# factor levels
+cats_lev <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+cats_lab <- c('O', 'OM', 'P', 'T', 'Z')
+stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+
+labs <- parcats2(as_df = T) %>% 
+    rename(Parameter = shrt) %>% 
+    select(Parameter, lngs)
+
+# format tocal_all for identifiability table
+# add long parameter name
+# get parameter combos with coll < 15 + 1
+# format error and coll with scinot
+# format category label so no duplicates
+totab <- tocal_all$top_all %>% 
+  reshape2::melt(., id.var = names(.[[1]])) %>%
+  mutate(Parameter = as.character(Parameter)) %>% 
+  left_join(., labs, by = 'Parameter') %>% 
+  mutate(
+    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
+    lngs = gsub('_', '', lngs), 
+    stts = factor(L1, levels = stts_lev, labels = stts_lab),
+    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
+    Parameter = par_txt(Parameter, frm = 'tex')
+  ) %>% 
+  split(., .$L1) %>% 
+  lapply(function(x){
+
+    sel <- which(x$coll < 15)
+    x <- x[sel, ] %>% 
+    # x <- x[c(sel, max(sel) + 1), ] %>% 
+      na.omit
+    x
+
+  }) %>% 
+  do.call('rbind', .) %>%
+  mutate(
+    error = sapply(error, scinot),
+    coll = sapply(coll, scinot), 
+    Rank = sapply(rnk_incat, scinot), 
+    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
+    ) %>%
+  group_by(stts) %>% 
+  nest %>% 
+  unnest %>% 
+  select(stts, lngs, Parameter, Rank, error, coll) %>% 
+  rename(
+    Description = lngs, 
+    L1 = error
+  ) %>% 
+  mutate(
+    stts = as.character(stts),
+    Description = paste0('\\scriptsize{', Description, '}'),
+    Parameter = paste0('\\scriptsize{', Parameter, '}')
+    ) %>% 
+  arrange(stts)
+
+identall2 <- filter(totab, !stts %in% 'Dissolved Oxygen')
+
+# final table formatting
+stts <- identall2$stts
+descrip <- as.character(identall2$Description)
+identall2 <- identall2[,-c(1, 2)]
+cap_val<- 'Parameter identifiability for ammonium, chlorophyll, irradiance, nitrate, OM1, OM2, and phosphate.
+Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.
+Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
+colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')
+
+latex( 
+  identall2,
+  file = '',
+  rowlabel = 'State variable, parameter description',
+  caption = cap_val,
+  caption.loc = 'top',
+  size = 'footnotesize',
+  label = 'tab:identall2',
+  rgroup = unique(as.character(stts)),
+  n.rgroup = as.numeric(table(as.character(stts))),
+  rowname = descrip,
+  colheads = colnms,
+  rgroupTexCmd = NULL
+  )
 @
@@
 Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\\gamma > 15$ or if the maximum number of possible parameters is selected.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
+Selection stops after $\\gamma > 15$ or if the maximum number of possible parameters is selected.
+See \\cref{tab:identall1} for values in (b).', fig.height = 8, fig.width = 8, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
 
@@
 Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\\gamma > 15$.', fig.height = 5, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
+Selection stops after $\\gamma > 15$.
+See \\cref{tab:identall2} for values.', fig.height = 5, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
 data(tocal_all)

### 2016-07-30 ident_manu.tex
ident tables added

@@
   \vspace{1in} 
-  \\ Version Date:   Sat Jul 30 12:31:08 2016 -0500
+  \\ Version Date:   Sat Jul 30 12:41:03 2016 -0500
 	}
@@
 
-Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist}).
+Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
 For the first selection heuristic, all sensitive parameters from the optics ($n = $ $4$, $\gamma =$  $3.7$) and organic matter ($n = $ $7$, $\gamma =$  $1.7$) categories were selected, whereas 23 were selected for phytoplankton ($\gamma = $ $13.7$), five for temperature ($\gamma = $ $11.4$), and five for zooplankton ($\gamma = $ $3.1$).
-For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$, with a majority from the phytoplankton category).
+For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$, with a majority from the phytoplankton category, \cref{tab:identall1}).
 For the third heuristic, 18 parameters were selected ($\gamma = $ $9.2$) with equal representation between categories.
@@
 Selection independent of category showed that including \textit{KNO3} caused in increase in $\gamma$ from $4.6$ to $15.6$ and equal selection within cateogies showed that including \textit{Tref(nospA+nospZ)$_{p2}$} caused in increase in $\gamma$ from $9.2$ to $66.2$.
-Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts}).
+Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
 Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
@@
 
+% ident all states
+%latex.default(identall1, file = "", rowlabel = "Parameter description",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:identall1", rowname = descrip, colheads = colnms,     rgroupTexCmd = NULL)%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Parameter identifiability for dissolved oxygen.
+Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\gamma < 15$.
+Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:identall1}}
+\begin{center}
+\begin{tabular}{lllll}
+\hline\hline
+\multicolumn{1}{l}{Parameter description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
+\hline
+\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$1$\textsuperscript{P}&$328.35$&$1$\tabularnewline
+\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$2$\textsuperscript{P}&$232.8$&$1$\tabularnewline
+\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p5}$}}&$3$\textsuperscript{P}&$7.57$&$1$\tabularnewline
+\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p2}$}}&$4$\textsuperscript{P}&$4.08$&$1$\tabularnewline
+\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p4}$}}&$5$\textsuperscript{P}&$3.1$&$1$\tabularnewline
+\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$6$\textsuperscript{P}&$2.98$&$1.01$\tabularnewline
+\scriptsize{Tref(nospA+nospZ): Optimum temperature for growth(C)}&\scriptsize{\textit{Tref(nospA+nospZ)$_{p4}$}}&$1$\textsuperscript{T}&$2.9$&$1.02$\tabularnewline
+\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p4}$}}&$7$\textsuperscript{P}&$2.88$&$1.04$\tabularnewline
+\scriptsize{coefficient for non-limiting nutrient}&\scriptsize{\textit{aN$_{p1}$}}&$8$\textsuperscript{P}&$2.7$&$1.05$\tabularnewline
+\scriptsize{P-uptake rate measured at umax}&\scriptsize{\textit{vmaxP$_{p3}$}}&$9$\textsuperscript{P}&$2.23$&$1.07$\tabularnewline
+\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p3}$}}&$10$\textsuperscript{P}&$2.15$&$1.73$\tabularnewline
+\scriptsize{rate constant for nitrification}&\scriptsize{\textit{k11}}&$1$\textsuperscript{OM}&$2.11$&$1.73$\tabularnewline
+\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p3}$}}&$11$\textsuperscript{P}&$1.99$&$1.73$\tabularnewline
+\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$1.91$&$1.73$\tabularnewline
+\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$1.64$&$1.77$\tabularnewline
+\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$12$\textsuperscript{P}&$1.61$&$4.1$\tabularnewline
+\scriptsize{minimum N cell-quota}&\scriptsize{\textit{QminN$_{p3}$}}&$13$\textsuperscript{P}&$1.53$&$4.1$\tabularnewline
+\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$3$\textsuperscript{OM}&$1.49$&$4.2$\tabularnewline
+\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$4$\textsuperscript{OM}&$1.37$&$4.62$\tabularnewline
+\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p4}$}}&$14$\textsuperscript{P}&$1.35$&$4.62$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% ident all states
+%latex.default(identall2, file = "", rowlabel = "State variable, parameter description",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:identall2", rgroup = unique(as.character(stts)),     n.rgroup = as.numeric(table(as.character(stts))), rowname = descrip,     colheads = colnms, rgroupTexCmd = NULL)%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Parameter identifiability for ammonium, chlorophyll, irradiance, nitrate, OM1, OM2, and phosphate.
+Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\gamma < 15$.
+Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:identall2}}
+\begin{center}
+\begin{tabular}{lllll}
+\hline\hline
+\multicolumn{1}{l}{State variable, parameter description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
+\hline
+{Ammonium}&&&&\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$2.38$&$1$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$2.23$&$3.1$\tabularnewline
+~~\scriptsize{rate constant for nitrification}&\scriptsize{\textit{k11}}&$1$\textsuperscript{OM}&$0.68$&$3.1$\tabularnewline
+~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$0.46$&$3.12$\tabularnewline
+~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$3$\textsuperscript{OM}&$0.39$&$6.53$\tabularnewline
+~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$3$\textsuperscript{P}&$0.35$&$7.18$\tabularnewline
+~~\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p4}$}}&$4$\textsuperscript{P}&$0.35$&$7.26$\tabularnewline
+~~\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p3}$}}&$5$\textsuperscript{P}&$0.34$&$13.14$\tabularnewline
+\hline
+{Chlorophyll}&&&&\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$104.26$&$1$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$47.86$&$3.65$\tabularnewline
+~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$3$\textsuperscript{P}&$1.71$&$4.07$\tabularnewline
+~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$1.29$&$5.58$\tabularnewline
+\hline
+{Irradiance}&&&&\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$0.32$&$1$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$0.25$&$4.87$\tabularnewline
+~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$3$\textsuperscript{P}&$0.19$&$5.38$\tabularnewline
+~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$4$\textsuperscript{P}&$0.17$&$7.61$\tabularnewline
+~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.15$&$13.34$\tabularnewline
+~~\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p3}$}}&$5$\textsuperscript{P}&$0.11$&$13.5$\tabularnewline
+~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$0.08$&$14.64$\tabularnewline
+\hline
+{Nitrate}&&&&\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$1.07\times 10^{38}$&$1$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$1.44\times 10^{23}$&$1$\tabularnewline
+~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$2\times 10^{5}$&$10.55$\tabularnewline
+\hline
+{OM1}&&&&\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1.5$\textsuperscript{P}&$1.13$&$1$\tabularnewline
+~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p4}$}}&$1.5$\textsuperscript{P}&$0.78$&$1.68$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$3$\textsuperscript{P}&$0.76$&$8.66$\tabularnewline
+~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$0.71$&$8.98$\tabularnewline
+~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$4$\textsuperscript{P}&$0.48$&$9.22$\tabularnewline
+~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.43$&$9.22$\tabularnewline
+\hline
+{OM2}&&&&\tabularnewline
+~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.3$&$1$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$0.94$&$2.01$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$0.74$&$7.65$\tabularnewline
+~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$3$\textsuperscript{P}&$0.35$&$11$\tabularnewline
+~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$0.34$&$11.29$\tabularnewline
+~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$4$\textsuperscript{P}&$0.31$&$11.44$\tabularnewline
+~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.29$&$11.54$\tabularnewline
+~~\scriptsize{maximum growth rate of zooplankton}&\scriptsize{\textit{Zumax$_{z1}$}}&$1$\textsuperscript{Z}&$0.29$&$11.66$\tabularnewline
+\hline
+{Phosphate}&&&&\tabularnewline
+~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$1$\textsuperscript{P}&$2.92$&$1$\tabularnewline
+~~\scriptsize{P-uptake rate measured at umax}&\scriptsize{\textit{vmaxP$_{p3}$}}&$2$\textsuperscript{P}&$1.57$&$2.23$\tabularnewline
+~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$3$\textsuperscript{P}&$0.78$&$2.57$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$4$\textsuperscript{P}&$0.73$&$5.29$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
 \clearpage
@@
 Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.}\label{fig:heurist}
+Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.
+See \cref{tab:identall1} for values in (b).}\label{fig:heurist}
 \end{figure}
@@
 
-\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables.
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables.
 Parameters are selected by decreasing sensitivity indepent of parameter categories.
 Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
+Selection stops after $\gamma > 15$.
+See \cref{tab:identall2} for values.}\label{fig:heurist_stts}
 \end{figure}

### 2016-07-30 R/funcs.R

@@ -883,7 +883,7 @@ parcats2 <- function(as_df = FALSE){
 # convert  parameter names to latex format
 #
 # parin chr vector of short names to convert
-# frm chr string indicating format of output
+# frm chr string indicating format of output, tex or exp for latex or expression
 par_txt <- function(parin, frm = 'tex'){
 
   library(dplyr)

### 2016-08-02 ident_manu.Rnw
added methods for structural uncertainty, need to revisit

@@
 \begin{singlespace}
-\title{{\bf {\Large Title....}}}
+\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
 \author{
-  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
+  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
   \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
@@
 	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
+	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
+	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
+	\\{\textit {\normalsize Phone: 919-541-3985,}}
+	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
   \vspace{1in} 
@@
 
-The sensitivity and identifiability analyses can be extended to
+As a final analysis, the effects of model structure on parameter identifiability were evaluated for \ac{do} predictions.
+The FishTank model includes several processes that can be included or excluded from the equations based on expected conditions or available data.
+These `switches' are conceptually different from model parameters as they define the use of explicit equations or processes that affect the model structure.
+As such, a comparison of sensitivity and identifiability given different equations uses parameter uncertainty as a means to begin addressing componenents of structural uncertainty.
+The analysis is provided as an example of applying basic (i.e., local) sensitivity analyses to address more complex questions in model uncertainty.
+Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).
+Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIR}.
+Parameter identifiability was evaluated using three scenarios of simple, intermediate, and complex combinations of model switches.
 
@@
   caption.loc = 'top',
-  size = 'footnotesize',
+  size = 'normalsize',
   label = 'tab:identall1',

### 2016-08-02 ident_manu.tex
added methods for structural uncertainty, need to revisit

@@
 	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
+	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
+	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
+	\\{\textit {\normalsize Phone: 919-541-3985,}}
+	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
   \vspace{1in} 
-  \\ Version Date:   Sat Jul 30 12:41:03 2016 -0500
+  \\ Version Date:   Sat Jul 30 15:11:50 2016 -0500
 	}
@@
 % ident all states
-%latex.default(identall1, file = "", rowlabel = "Parameter description",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:identall1", rowname = descrip, colheads = colnms,     rgroupTexCmd = NULL)%
+%latex.default(identall1, file = "", rowlabel = "Parameter description",     caption = cap_val, caption.loc = "top", size = "normalsize",     label = "tab:identall1", rowname = descrip, colheads = colnms,     rgroupTexCmd = NULL)%
 \begin{table}[!tbp]
-{\footnotesize
+{\normalsize
 \caption{Parameter identifiability for dissolved oxygen.

### 2016-08-02 ident_manu.Rnw
started intro text

@@
 
+\begin{comment}
 \begin{enumerate}
-\item Simulation/biogeochemical/process-based models overview, contrast with statistical models
+\item Hypoxia formation and use of simulation/biogeochemical/process-based models overview, contrast with statistical models
 \item What models seek to provide - generality, precision, realism \cite{Levins66}, there is a tradeoff so models are 1) developed in partial independence and dependence on the world and theory, 2) function autonomously from both, or 3) represent both at the same time, from \cite{Morrison99}, cited in \cite{Ganju16}.
@@
 \end{enumerate}
+\end{comment}
+
+Formation of hypoxia in bottom waters of coastal oceans occurs primarily as a result of excess nutrient inputs from land-based sources.
+These events are detrimental to aquatic organisms and have significant negative effects on economic resources derived from coastal ecosystems.
+An understanding of the biological, physical, and chemical processes that contribute to the growth of hypoxic areas is a critical concern for mitigating and preventing these negative impacts.
+Numerical ecosystem models have been important tools for describing current knowledge of ecosystem processes that contribute to hypoxia formation and for predicting the effects of proposed management activities or future scenarios.
+Unlike statistical models with more generic structures, simulation and process-based models include explicit descriptions of relevant processes that are constrained by empirical or observational data relevant to the system of interest.
+These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions.
+Coupled hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom}
+
+coupled with hydrodynamic models....
 

### 2016-08-02 ident_manu.tex
started intro text

@@
   \vspace{1in} 
-  \\ Version Date:   Sat Jul 30 15:11:50 2016 -0500
+  \\ Version Date:   Tue Aug 2 11:00:17 2016 -0500
 	}

### 2016-08-02 ident_manu.Rnw
working on intro

--- 2016-08-02 ident_manu.Rnw
@@
 
+Hypoxia formation in bottom waters of coastal oceans occurs primarily from excess nutrient inputs from land-based sources \citep{Justic87,Diaz95,Howarth96}.
+These events are detrimental to aquatic organisms and have significant negative effects on economic resources derived from coastal ecosystems \citep{Lipton03,Diaz11}.
+An understanding of the biological, physical, and chemical processes that contribute to the growth of hypoxic areas is a critical concern for mitigating and preventing these negative impacts.
+Numerical ecosystem models have been important tools for describing current knowledge of ecosystem processes that contribute to hypoxia formation and for predicting the effects of proposed management activities or future scenarios \citep{Scavia04,Hagy07,Pauer16}.
+Unlike statistical models that have more generic structures, simulation and process-based models include explicit descriptions of relevant processes that are constrained by empirical or observational data relevant to the system of interest \citep[e.g.][]{Omlin01b,Eldridge10}.
+These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions \citep{Warner05,Zhao10,Ganju16}.
+Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} (\citealt{Obenour15,Pauer16}, \citetalias{LehrterIR}).
+This area drains a significant portion of the continental United States through the \ac{marb} and is the second largest hypoxic area in the world \citep{Rabalais02}.
+Understanding processes that contribute to the frequency and duration of hypoxic events remains a critical research goal for the region, including the application of process-based models to characterize the current knowledge domain.
+
+The development and application of a model represents a tradeoff between desirable characteristics that are defined by the analysis needs.
+An idealized model should be sufficiently generalizable across systems, provide results that are precise given the inputs, and include structural components that are realistic descriptions of actual processes \citep{Levins66}.
+Given that a model cannot possibly excel in all of these characterics, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99}.
+These challenges are analagous to the well-known `bias-variance' tradeoff in statistical models that balances the competing objectives of over- and under-fitting to an observed dataset.
+Process-based models are typically not well balanced between reality and theory, such that a common tendency during development is to over-parameterize equations in an attempt to descibe reality completely.
+Such over-parameterization, including use of excessive structural equations, can have serious implications for practical applications of a model.
+Over-parameterization can limit application to novel systems outside of the development area and impose uncertainty in model predictions as `realistic' values for every variable may not be known.
+Quantitative limitations of over-parameterization are also analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset.
+The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and more comprehensive approaches are needed to develop models that more carefully balance theory with reality.
+
+Standard approaches for uncertainty analysis can be used
+
+\begin{comment}
 \begin{enumerate}
-\item Simulation/biogeochemical/process-based models overview, contrast with statistical models
 \item What models seek to provide - generality, precision, realism \cite{Levins66}, there is a tradeoff so models are 1) developed in partial independence and dependence on the world and theory, 2) function autonomously from both, or 3) represent both at the same time, from \cite{Morrison99}, cited in \cite{Ganju16}.
@@
 \end{enumerate}
+\end{comment}
 
@@
 The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.
-Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97,Obenour15}.
+Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97,Paerl98,Obenour15}.
 
@@
 Failing in one way can be over-compensated by another feature, e.g., the parameter set that is optimized (see \cite{Flynn05}, p.
-1207, third paragraph), also \citep{Arhonditsis08}
+1207, third paragraph), also \citep{Arhonditsis08}, also note that over-parameterized models are not necessarily bad, see \citep{Omlin01}
 

### 2016-08-02 ident_manu.tex
working on intro

--- 2016-08-02 ident_manu.tex
@@
   \vspace{1in} 
-  \\ Version Date:   Sat Jul 30 15:11:50 2016 -0500
+  \\ Version Date:   Tue Aug 2 11:40:44 2016 -0500
 	}

### 2016-08-03 ident_manu.Rnw
intro draft done

@@
 
-The development and application of a model represents a tradeoff between desirable characteristics that are defined by the analysis needs.
-An idealized model should be sufficiently generalizable across systems, provide results that are precise given the inputs, and include structural components that are realistic descriptions of actual processes \citep{Levins66}.
-Given that a model cannot possibly excel in all of these characterics, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99}.
-These challenges are analagous to the well-known `bias-variance' tradeoff in statistical models that balances the competing objectives of over- and under-fitting to an observed dataset.
-Process-based models are typically not well balanced between reality and theory, such that a common tendency during development is to over-parameterize equations in an attempt to descibe reality completely.
+The development and application of a model represents a tradeoff between different characteristics that are expected from the output or provided by the structural components.
+An idealized model is sufficiently generalizable across systems, provides results that are precise given the inputs, and includes components that are realistic descriptions of actual processes \citep{Levins66}.
+Given that all of these characteristics cannot be achieved, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99,Ganju16}.
+These challenges are analagous to the well-known `bias-variance' tradeoff in statistical models that balances the competing objectives of over- and under-fitting an observed dataset.
+Process-based models are more commonly imbalanced between reality and theory, such that many models are over-parameterized in an attempt to describe reality completely \citep{Denman03,Nossent12,Petrucci14}.
 Such over-parameterization, including use of excessive structural equations, can have serious implications for practical applications of a model.
-Over-parameterization can limit application to novel systems outside of the development area and impose uncertainty in model predictions as `realistic' values for every variable may not be known.
-Quantitative limitations of over-parameterization are also analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset.
-The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and more comprehensive approaches are needed to develop models that more carefully balance theory with reality.
-
-Standard approaches for uncertainty analysis can be used
+Over-parameterization can limit application to novel systems outside of the data domain and impose uncertainty in model predictions as `realistic' values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
+More importantly, quantitative limitations of over-parameterization are analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset \citep{Kirchner06}.
+The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and more comprehensive approaches are needed to develop models that more carefully balance theory with reality \citep[e.g.,][]{Snowling01}.
+
+Standard approaches for uncertainty analysis can be used to begin addressing model complexity issues.
+In the most general sense, uncertainty can be evaluated relative to the effects of input conditions or the observed data used to calibrate a model, changes in parameter values, or variation in the structural components \citep{Beck87}.
+Evaluating parameter uncertainty is by far the most common and simplest means of evaluating model behavior.
+Although uncertainty analyses should be integrated throughout model development and application, parameters are more often evaluated post-hoc as a form of `damage control' for further calibration.
+This approach is related to inverse modelling where results from sensitivity analysis of parameters are used to guide calibration or fit of the developed model to observations (\citealt{Soetaert10}, or confronting models with data, \textit{sensu} \citealt{Hilborn97}).
+Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability', such that only a subset of parameters can be numerically constrained to the data as compared to the entire parameter set.
+Redundancies in the effects of parameters on the output lead to unidentifiable models where optimal solutions may be empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
+The concept of identifiable parameter subsets is not foreign to hypoxia or eutrophication models  \citep{Omlin01,Estrada10,Mateus15}, although there is a clear need for greater integration of these concepts in model development \citep{Fasham06}.
+Moreover, the inclusion of sensitivity and identifiability analyses in model tuning will require the adoption of selection rules that are context-dependent given the subsets that are possible with large parameter sets \citep[e.g.,][]{Wagener01, Wagener01b}.
 
@@
 \begin{enumerate}
-\item What models seek to provide - generality, precision, realism \cite{Levins66}, there is a tradeoff so models are 1) developed in partial independence and dependence on the world and theory, 2) function autonomously from both, or 3) represent both at the same time, from \cite{Morrison99}, cited in \cite{Ganju16}.
-This is similar to the bias-variance tradeoff for statistical models, e.g., overparameterization of a model makes it very biased as it fits the data (the world) exactly, tradeoff between sensitity and error with changes in model complexity (more complexity is less error but increasing sensitivity) described in \cite{Snowling01}
-\item How is model performance/uncertainty evaluated regarding what they should provide - structural, observational, parameter \cite{Beck87}?
-\cite{Refsgaard07} provides comprehensive overview of factors that contribute to uncertainty in environmental modelling.
+\
 \item Parameter uncertainy as low-hanging fruit - can do post-hoc and from inner to outer level of complexity, parameter uncertainty is the most common, e.g., marine ecological model \cite{Mateus15}, but stopped short, global sensitivity analysis of eutrophication model \cite{Estrada10}
@@
 
+\citep{Denman03} describes over-parameterization for multiple phyto groups, use this to emphasize collinearity issues with the phyto groups despite differing sensitivity values between groups
+
 Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).
@@
 Failing in one way can be over-compensated by another feature, e.g., the parameter set that is optimized (see \cite{Flynn05}, p.
-1207, third paragraph), also \citep{Arhonditsis08}, also note that over-parameterized models are not necessarily bad, see \citep{Omlin01}
+1207, third paragraph), also \citep{Durand02,Arhonditsis08}, also note that over-parameterized models are not necessarily bad, see \citep{Omlin01}, models must be validated for the uses which they were intended where a comparison of observed and predicted is the simplest approach and other methods should be used depending on analysis needs \citep{Rykiel96}
 
@@
 
-Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by Wagener et al. 1999, 2001 (cited on page 15, in \citealt{Wagener01}).
+Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by \citep{Wagener01b}2001 (cited on page 15, in \citealt{Wagener01}), although ours is simple in comparison
 
@@
     stts = as.character(stts),
-    Description = paste0('\\scriptsize{', Description, '}'),
-    Parameter = paste0('\\scriptsize{', Parameter, '}')
+    Description = paste0('\\footnotesize{', Description, '}'),
+    Parameter = paste0('\\footnotesize{', Parameter, '}')
     ) %>% 

### 2016-08-03 ident_manu.tex
intro draft done

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Aug 2 11:40:44 2016 -0500
+  \\ Version Date:   Tue Aug 2 17:30:02 2016 -0500
 	}
@@
 
-The development and application of a model represents a tradeoff between desirable characteristics that are defined by the analysis needs.
-An idealized model should be sufficiently generalizable across systems, provide results that are precise given the inputs, and include structural components that are realistic descriptions of actual processes \citep{Levins66}.
-Given that a model cannot possibly excel in all of these characterics, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99}.
-These challenges are analagous to the well-known `bias-variance' tradeoff in statistical models that balances the competing objectives of over- and under-fitting to an observed dataset.
-Process-based models are typically not well balanced between reality and theory, such that a common tendency during development is to over-parameterize equations in an attempt to descibe reality completely.
+The development and application of a model represents a tradeoff between different characteristics that are expected from the output or provided by the structural components.
+An idealized model is sufficiently generalizable across systems, provides results that are precise given the inputs, and includes components that are realistic descriptions of actual processes \citep{Levins66}.
+Given that all of these characteristics cannot be achieved, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99,Ganju16}.
+These challenges are analagous to the well-known `bias-variance' tradeoff in statistical models that balances the competing objectives of over- and under-fitting an observed dataset.
+Process-based models are more commonly imbalanced between reality and theory, such that many models are over-parameterized in an attempt to describe reality completely \citep{Denman03,Nossent12,Petrucci14}.
 Such over-parameterization, including use of excessive structural equations, can have serious implications for practical applications of a model.
-Over-parameterization can limit application to novel systems outside of the development area and impose uncertainty in model predictions as `realistic' values for every variable may not be known.
-Quantitative limitations of over-parameterization are also analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset.
-The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and more comprehensive approaches are needed to develop models that more carefully balance theory with reality.
+Over-parameterization can limit application to novel systems outside of the data domain and impose uncertainty in model predictions as `realistic' values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
+More importantly, quantitative limitations of over-parameterization are analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset \citep{Kirchner06}.
+The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and more comprehensive approaches are needed to develop models that more carefully balance theory with reality \citep[e.g.,][]{Snowling01}.
 
-Standard approaches for uncertainty analysis can be used
+Standard approaches for uncertainty analysis can be used to begin addressing model complexity issues.
+In the most general sense, uncertainty can be evaluated relative to the effects of input conditions or the observed data used to calibrate a model, changes in parameter values, or variation in the structural components \citep{Beck87}.
+Evaluating parameter uncertainty is by far the most common and simplest means of evaluating model behavior.
+Although uncertainty analyses should be integrated throughout model development and application, parameters are more often evaluated post-hoc as a form of `damage control' for further calibration.
+This approach is related to inverse modelling where results from sensitivity analysis of parameters are used to guide calibration or fit of the developed model to observations (\citealt{Soetaert10}, or confronting models with data, \textit{sensu} \citealt{Hilborn97}).
+Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability', such that only a subset of parameters can be numerically constrained to the data as compared to the entire parameter set.
+Redundancies in the effects of parameters on the output lead to unidentifiable models where optimal solutions may be empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
+The concept of identifiable parameter subsets is not foreign to hypoxia or eutrophication models  \citep{Omlin01,Estrada10,Mateus15}, although there is a clear need for greater integration of these concepts in model development \citep{Fasham06}.
+Moreover, the inclusion of sensitivity and identifiability analyses in model tuning will require the adoption of selection rules that are context-dependent given the subsets that are possible with large parameter sets \citep[e.g.,][]{Wagener01, Wagener01b}.
 
@@
 \hline
-\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$1$\textsuperscript{P}&$328.35$&$1$\tabularnewline
-\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$2$\textsuperscript{P}&$232.8$&$1$\tabularnewline
-\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p5}$}}&$3$\textsuperscript{P}&$7.57$&$1$\tabularnewline
-\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p2}$}}&$4$\textsuperscript{P}&$4.08$&$1$\tabularnewline
-\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p4}$}}&$5$\textsuperscript{P}&$3.1$&$1$\tabularnewline
-\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$6$\textsuperscript{P}&$2.98$&$1.01$\tabularnewline
-\scriptsize{Tref(nospA+nospZ): Optimum temperature for growth(C)}&\scriptsize{\textit{Tref(nospA+nospZ)$_{p4}$}}&$1$\textsuperscript{T}&$2.9$&$1.02$\tabularnewline
-\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p4}$}}&$7$\textsuperscript{P}&$2.88$&$1.04$\tabularnewline
-\scriptsize{coefficient for non-limiting nutrient}&\scriptsize{\textit{aN$_{p1}$}}&$8$\textsuperscript{P}&$2.7$&$1.05$\tabularnewline
-\scriptsize{P-uptake rate measured at umax}&\scriptsize{\textit{vmaxP$_{p3}$}}&$9$\textsuperscript{P}&$2.23$&$1.07$\tabularnewline
-\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p3}$}}&$10$\textsuperscript{P}&$2.15$&$1.73$\tabularnewline
-\scriptsize{rate constant for nitrification}&\scriptsize{\textit{k11}}&$1$\textsuperscript{OM}&$2.11$&$1.73$\tabularnewline
-\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p3}$}}&$11$\textsuperscript{P}&$1.99$&$1.73$\tabularnewline
-\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$1.91$&$1.73$\tabularnewline
-\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$1.64$&$1.77$\tabularnewline
-\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$12$\textsuperscript{P}&$1.61$&$4.1$\tabularnewline
-\scriptsize{minimum N cell-quota}&\scriptsize{\textit{QminN$_{p3}$}}&$13$\textsuperscript{P}&$1.53$&$4.1$\tabularnewline
-\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$3$\textsuperscript{OM}&$1.49$&$4.2$\tabularnewline
-\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$4$\textsuperscript{OM}&$1.37$&$4.62$\tabularnewline
-\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p4}$}}&$14$\textsuperscript{P}&$1.35$&$4.62$\tabularnewline
+\footnotesize{phytoplankton carbon/cell}&\footnotesize{\textit{Qc$_{p1}$}}&$1$\textsuperscript{P}&$328.35$&$1$\tabularnewline
+\footnotesize{phytoplankton carbon/cell}&\footnotesize{\textit{Qc$_{p3}$}}&$2$\textsuperscript{P}&$232.8$&$1$\tabularnewline
+\footnotesize{N-uptake rate measured at umax}&\footnotesize{\textit{vmaxN$_{p5}$}}&$3$\textsuperscript{P}&$7.57$&$1$\tabularnewline
+\footnotesize{phytoplankton carbon/cell}&\footnotesize{\textit{Qc$_{p2}$}}&$4$\textsuperscript{P}&$4.08$&$1$\tabularnewline
+\footnotesize{phytoplankton basal respiration coefficient}&\footnotesize{\textit{respb$_{p4}$}}&$5$\textsuperscript{P}&$3.1$&$1$\tabularnewline
+\footnotesize{mortality coefficient}&\footnotesize{\textit{mA$_{p3}$}}&$6$\textsuperscript{P}&$2.98$&$1.01$\tabularnewline
+\footnotesize{Tref(nospA+nospZ): Optimum temperature for growth(C)}&\footnotesize{\textit{Tref(nospA+nospZ)$_{p4}$}}&$1$\textsuperscript{T}&$2.9$&$1.02$\tabularnewline
+\footnotesize{N-uptake rate measured at umax}&\footnotesize{\textit{vmaxN$_{p4}$}}&$7$\textsuperscript{P}&$2.88$&$1.04$\tabularnewline
+\footnotesize{coefficient for non-limiting nutrient}&\footnotesize{\textit{aN$_{p1}$}}&$8$\textsuperscript{P}&$2.7$&$1.05$\tabularnewline
+\footnotesize{P-uptake rate measured at umax}&\footnotesize{\textit{vmaxP$_{p3}$}}&$9$\textsuperscript{P}&$2.23$&$1.07$\tabularnewline
+\footnotesize{phytoplankton basal respiration coefficient}&\footnotesize{\textit{respb$_{p3}$}}&$10$\textsuperscript{P}&$2.15$&$1.73$\tabularnewline
+\footnotesize{rate constant for nitrification}&\footnotesize{\textit{k11}}&$1$\textsuperscript{OM}&$2.11$&$1.73$\tabularnewline
+\footnotesize{N-uptake rate measured at umax}&\footnotesize{\textit{vmaxN$_{p3}$}}&$11$\textsuperscript{P}&$1.99$&$1.73$\tabularnewline
+\footnotesize{O2 concentration that inhibits denitrification}&\footnotesize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$1.91$&$1.73$\tabularnewline
+\footnotesize{Chla specific absorption at 490 nm}&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$1.64$&$1.77$\tabularnewline
+\footnotesize{initial slope of the photosynthesis-irradiance relationship}&\footnotesize{\textit{alpha$_{p4}$}}&$12$\textsuperscript{P}&$1.61$&$4.1$\tabularnewline
+\footnotesize{minimum N cell-quota}&\footnotesize{\textit{QminN$_{p3}$}}&$13$\textsuperscript{P}&$1.53$&$4.1$\tabularnewline
+\footnotesize{turnover rate for OM1A and OM1G}&\footnotesize{\textit{KG1}}&$3$\textsuperscript{OM}&$1.49$&$4.2$\tabularnewline
+\footnotesize{turnover rate for OM2A and OM2G}&\footnotesize{\textit{KG2}}&$4$\textsuperscript{OM}&$1.37$&$4.62$\tabularnewline
+\footnotesize{mortality coefficient}&\footnotesize{\textit{mA$_{p4}$}}&$14$\textsuperscript{P}&$1.35$&$4.62$\tabularnewline
 \hline

### 2016-08-03 ident_manu.Rnw
intro smithing

@@
 An idealized model is sufficiently generalizable across systems, provides results that are precise given the inputs, and includes components that are realistic descriptions of actual processes \citep{Levins66}.
-Given that all of these characteristics cannot be achieved, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99,Ganju16}.
-These challenges are analagous to the well-known `bias-variance' tradeoff in statistical models that balances the competing objectives of over- and under-fitting an observed dataset.
-Process-based models are more commonly imbalanced between reality and theory, such that many models are over-parameterized in an attempt to describe reality completely \citep{Denman03,Nossent12,Petrucci14}.
-Such over-parameterization, including use of excessive structural equations, can have serious implications for practical applications of a model.
-Over-parameterization can limit application to novel systems outside of the data domain and impose uncertainty in model predictions as `realistic' values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
+Given that these characteristics cannot be simultaneously achieved, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99,Ganju16}.
+These challenges are analagous to the well-known bias-variance tradeoff in statistical models that balances the competing objectives of over- and under-fitting to an observed dataset.
+Process-based models are more commonly imbalanced between reality and theory, such that most are over-parameterized in an attempt to completely describe reality \citep{Denman03,Nossent12,Petrucci14}.
+Such over-parameterization, including use of excessive structural equations, can have serious implications for practical applications.
+Over-parameterization can limit use across systems outside of the data domain and impose uncertainty in model predictions as realistic values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
 More importantly, quantitative limitations of over-parameterization are analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset \citep{Kirchner06}.
@@
 Standard approaches for uncertainty analysis can be used to begin addressing model complexity issues.
-In the most general sense, uncertainty can be evaluated relative to the effects of input conditions or the observed data used to calibrate a model, changes in parameter values, or variation in the structural components \citep{Beck87}.
+In the most general sense, uncertainty is evaluated relative to the effects of input conditions or the observed data used to calibrate a model, changes in parameter values, or variation in the structural components \citep{Beck87}.
 Evaluating parameter uncertainty is by far the most common and simplest means of evaluating model behavior.
 Although uncertainty analyses should be integrated throughout model development and application, parameters are more often evaluated post-hoc as a form of `damage control' for further calibration.
-This approach is related to inverse modelling where results from sensitivity analysis of parameters are used to guide calibration or fit of the developed model to observations (\citealt{Soetaert10}, or confronting models with data, \textit{sensu} \citealt{Hilborn97}).
-Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability', such that only a subset of parameters can be numerically constrained to the data as compared to the entire parameter set.
-Redundancies in the effects of parameters on the output lead to unidentifiable models where optimal solutions may be empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
+This approach is sometimes called inverse modelling where results from sensitivity analyses are used to guide calibration or fit of the developed model to observations (\citealt{Soetaert10}, or confronting models with data, \textit{sensu} \citealt{Hilborn97}).
+Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability', where only a subset of parameters can be numerically constrained to the data as compared to the entire parameter set.
+Redundancies in parameter effects lead to unidentifiable models where optimal solutions may be empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
 The concept of identifiable parameter subsets is not foreign to hypoxia or eutrophication models  \citep{Omlin01,Estrada10,Mateus15}, although there is a clear need for greater integration of these concepts in model development \citep{Fasham06}.
@@
 
-\begin{comment}
-\begin{enumerate}
-\
-\item Parameter uncertainy as low-hanging fruit - can do post-hoc and from inner to outer level of complexity, parameter uncertainty is the most common, e.g., marine ecological model \cite{Mateus15}, but stopped short, global sensitivity analysis of eutrophication model \cite{Estrada10}
-\item Challenges related to uncertainty - similar to degrees of freedom, identifiability definition from \cite{Brun01} and need to evaluate identifiability \cite{Fasham06}, \cite{Omlin01} did a similar analysis with freshwater biogeochem model.
-Identifiability describes the ability to estimate a parameter in relation to variation among the remaining parameters.
-A parameter is identifiable if all parameters within the set can be uniquely estimated based on the observed data.
-Parameters that are unidentifiable typically produce similar model outputs for a given relative perturbation, i.e., the effect of altering one parameter can be undone by altering one or more other parameters.
-Model calibration will not converge for parameters sets that are unidentifiable.
-\end{enumerate}
-\end{comment}
-
 This study describes a parameter sensitivity analysis to evaluate identifiability for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
 We evaluate a simple \ac{oned} unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
-The study also provides a general framework for sensitivity analysis and parameter identifiability that can be used on similar mechanistic models.
-Specifically, an assumption is that models are generally over-parameterized and only a finite and smaller subset of the larger parameter set can be optimized for a given research question or dataset.
+Specifically, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the larger parameter set can be optimized for a given research question or dataset.
 We provide explicit guidance for choosing such subsets of the parameter space given constraints on identifiability as directly related to sensitivity analyses.
-The specific objectives are to \begin{inparaenum}[1\upshape)]
+The objectives are to \begin{inparaenum}[1\upshape)]
 \item identify the parameters that have the greatest influence on \ac{do} using local sensitivity analysis,
 \item quantify the identifiability of subsets of the total parameter space based on sensitivity,
-\item provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories, including extension to other state variables provided by the model, and 
-\item discuss implications for hypoxia formation in coastal regions, including management strategies for nutrient reduction and use of mechanistic models to inform decision-making.
+\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories, including extension to other state variables provided by the model.
 \end{inparaenum}
-The `optimum' parameter space is defined as the chosen subset that represents the maximum number of identifiable parameters.
+A final analysis evaluates identifiability relative to structural uncertainty to provide an example of extending these methods to more complex uncertainty assessments.
+The optimum parameter space is defined as the chosen subset that represents the maximum number of identifiable parameters.
 Here, `optimum' is both a qualitative description based on a research question or management goal and a quantitative objective based on numerical optimization criteria for fitting model output to a calibration dataset.
 These results can be used to refine existing models or guide application of models to novel contexts, such as downscaling or application to new environments.
+We conclude with a discussion of the implications for hypoxia formation in coastal regions, including management strategies for nutrient reduction and use of mechanistic models to inform decision-making.
 

### 2016-08-03 ident_manu.tex
intro smithing

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Aug 2 17:30:02 2016 -0500
+  \\ Version Date:   Wed Aug 3 10:50:52 2016 -0500
 	}

### 2016-08-04 ident_manu.Rnw
minor edits to intro, method, 1d to 0d

@@
 \acrodef{marb}[MARB]{Mississippi-Atchafalaya River Basin}
-\acrodef{oned}[1-D]{one-dimensional}
+\acrodef{zerod}[0-D]{zero-dimensional}
 \acrodef{par}[PAR]{photosynthetically active radiation}
@@
 This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter sensitivity and identifability.
-We evaluate a simple bio-geo-chemical model that is the \ac{oned} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example.
-Results from analysis of the \ac{oned} model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
+We evaluate a simple bio-geo-chemical model that is the \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example.
+Results from analysis of the \ac{zerod} model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
 In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
@@
 These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions \citep{Warner05,Zhao10,Ganju16}.
-Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} (\citealt{Obenour15,Pauer16}, \citetalias{LehrterIR}).
+Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} (\citealt{Fennel13,Obenour15,Pauer16}, \citetalias{LehrterIR}).
 This area drains a significant portion of the continental United States through the \ac{marb} and is the second largest hypoxic area in the world \citep{Rabalais02}.
@@
 
-The development and application of a model represents a tradeoff between different characteristics that are expected from the output or provided by the structural components.
+The development and application of a model represents a tradeoff between characteristics expected from the output or provided by the structural components.
 An idealized model is sufficiently generalizable across systems, provides results that are precise given the inputs, and includes components that are realistic descriptions of actual processes \citep{Levins66}.
@@
 Such over-parameterization, including use of excessive structural equations, can have serious implications for practical applications.
-Over-parameterization can limit use across systems outside of the data domain and impose uncertainty in model predictions as realistic values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
-More importantly, quantitative limitations of over-parameterization are analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset \citep{Kirchner06}.
+Quantitative limitations of over-parameterization are analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset \citep{Kirchner06}.
+More importantly, over-parameterization can limit use across systems outside of the data domain and impose uncertainty in model predictions as realistic values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
 The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and more comprehensive approaches are needed to develop models that more carefully balance theory with reality \citep[e.g.,][]{Snowling01}.
@@
 This study describes a parameter sensitivity analysis to evaluate identifiability for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
-We evaluate a simple \ac{oned} unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
+We evaluate a simple \ac{zerod} unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
 Specifically, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the larger parameter set can be optimized for a given research question or dataset.
@@
 
-Three-dimensional numerical simulation models have been developed to describe factors contributing to hypoxia and to predict the effects of management actions or climate scenarios on future patterns (\citealt{Fennel13,Pauer16}, \citetalias{LehrterIR}).
-This study evaluates a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia.
+This study evaluates a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.
 The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describe hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
@@
 
-The core unit of \ac{cgem} is FishTank, a \ac{oned} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux).
+The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux).
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
 Accordingly, the sensitivity and identifiability analysis described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
-The FishTank model provides estimates for the 36 state variables described above using a \ac{oned} parcel that is uniformly mixed.
-A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 (Table 1, \citet{Murrell14}).
+The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
+A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 \citet[Table 1 in][]{Murrell14}.
 
@@
 
-Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton (up to six groups) and zooplankton (two groups) as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
+Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
 A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
@@
 
-The analysis focused on sensitivity of \ac{do} in the \ac{oned} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
+The analysis focused on sensitivity of \ac{do} in the \ac{zerod} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
 A local sensitivity analysis was performed for each of the 250 parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
@@
 As such, a comparison of sensitivity and identifiability given different equations uses parameter uncertainty as a means to begin addressing componenents of structural uncertainty.
-The analysis is provided as an example of applying basic (i.e., local) sensitivity analyses to address more complex questions in model uncertainty.
 Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).

### 2016-08-04 ident_manu.tex
minor edits to intro, method, 1d to 0d

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Aug 3 10:50:52 2016 -0500
+  \\ Version Date:   Wed Aug 3 11:12:36 2016 -0500
 	}
@@
 
-The core unit of \ac{cgem} is FishTank, a \ac{oned} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux).
+The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux).
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
 Accordingly, the sensitivity and identifiability analysis described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
-The FishTank model provides estimates for the 36 state variables described above using a \ac{oned} parcel that is uniformly mixed.
-A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 (Table 1, \citet{Murrell14}).
+The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
+A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 \citet[Table 1 in][]{Murrell14}.
 
-Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton (up to six groups) and zooplankton (two groups) as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
+Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
 A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.

### 2016-08-13 R/funcs.R
parcats2 updated for new fishtank

@@ -178,12 +178,12 @@ parcats2 <- function(as_df = FALSE){
     vals = c(
       22, 
       22, 
-      17, 
-      17, 
-      26, 
-      29, 
+      22, 
+      22, 
+      22, 
+      22, 
       22,
-      26,
+      22,
       0.0035,
       0.0035,
       0.0035,
@@ -531,29 +531,29 @@ parcats2 <- function(as_df = FALSE){
       ),
     vals = c(
       0.25,
-      0.5,
+      0.25,
       0.25, 
-      0.5,
-      0.6,
-      1, 
       0.25,
-      0.5, 
       0.25,
-      0.5, 
-      0.6, 
-      1, 
+      0.25, 
+      0.25,
+      0.25, 
+      0.25,
+      0.25, 
+      0.25, 
+      0.25, 
       0.41,
-      0.76,
-      0.34,
-      1.12,
-      1.1, 
-      1.72,
+      0.41,
+      0.41,
+      0.41,
+      0.41, 
+      0.41,
       8.42e-17, 
-      2.18e-16, 
-      6.19e-17, 
-      3.96e-16, 
-      3.87e-16, 
-      7.63e-17, 
+      8.42e-17, 
+      8.42e-17, 
+      8.42e-17, 
+      8.42e-17, 
+      8.42e-17, 
       1.1e-18, 
       1.1e-18, 
       1.1e-18, 
@@ -573,47 +573,47 @@ parcats2 <- function(as_df = FALSE){
       0.02,
       0.02,
       6.08e-09,
-      6.32e-10,
-      1.27e-08,
-      1.53e-10,
-      1.62e-10,
-      3.21e-11,
+      6.08e-09,
+      6.08e-09,
+      6.08e-09,
+      6.08e-09,
+      6.08e-09,
       6.19e-10,
-      5.1e-11, 
-      1.39e-09,
-      1.07e-11,
-      1.14e-11,
-      1.91e-12,
+      6.19e-10, 
+      6.19e-10,
+      6.19e-10,
+      6.19e-10,
+      6.19e-10,
       2.04e-07,
-      2.53e-08,
-      4.01e-07,
-      6.85e-09,
-      7.22e-09,
-      1.62e-09,
+      2.04e-07,
+      2.04e-07,
+      2.04e-07,
+      2.04e-07,
+      2.04e-07,
       1.28e-08,
-      1.58e-09,
-      2.50e-08,
-      4.28e-10,
[…]

### 2016-08-22 ident_manu.Rnw
explanation of parameter removal

@@
 
-This study evaluates a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.
-The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describe hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
+This study evaluated a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.
+The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describes hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
 The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
@@
 The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
-A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 \citet[Table 1 in][]{Murrell14}.
+A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 \citep[Table 1 in][]{Murrell14}.
 
 <<echo = FALSE>>=
-# numer of parameters in each category
-nparms <- table(parcats2(as_df = TRUE)$cat) %>% 
+# remove irrelevant parameters, from 'ignore/noparams.csv'
+rmpars <- c('Kw_1', 'Kcdom_1', 'Kspm_1', 'Kchla_1', 'aw490_1', 'astarOMR_1', 'astarOMBC_1', 'KTg1(nospA+nospZ)_1', 'KTg1(nospA+nospZ)_2', 'KTg1(nospA+nospZ)_3', 'KTg1(nospA+nospZ)_4', 'KTg1(nospA+nospZ)_5', 'KTg1(nospA+nospZ)_6', 'KTg1(nospA+nospZ)_7', 'KTg1(nospA+nospZ)_8', 'KTg2(nospA+nospZ)_1', 'KTg2(nospA+nospZ)_2', 'KTg2(nospA+nospZ)_3', 'KTg2(nospA+nospZ)_4', 'KTg2(nospA+nospZ)_5', 'KTg2(nospA+nospZ)_6', 'KTg2(nospA+nospZ)_7', 'KTg2(nospA+nospZ)_8', 'Ea_R(nospA+nospZ)_1', 'Ea_R(nospA+nospZ)_2', 'Ea_R(nospA+nospZ)_3', 'Ea_R(nospA+nospZ)_4', 'Ea_R(nospA+nospZ)_5', 'Ea_R(nospA+nospZ)_6', 'Ea_R(nospA+nospZ)_7', 'Ea_R(nospA+nospZ)_8', 'beta_1', 'beta_2', 'beta_3', 'beta_4', 'beta_5', 'beta_6', 'QmaxN_1', 'QmaxN_2', 'QmaxN_3', 'QmaxN_4', 'QmaxN_5', 'QmaxN_6', 'QmaxP_1', 'QmaxP_2', 'QmaxP_3', 'QmaxP_4', 'QmaxP_5', 'QmaxP_6', 'nfQs_1', 'nfQs_2', 'nfQs_3', 'nfQs_4', 'nfQs_5', 'nfQs_6', 'KG1_R_1', 'KG2_R_1', 'KG1_BC_1', 'KG2_BC_1', 'pCO2_1', 'stoich_x1R_1', 'stoich_y1R_1', 'stoich_x2R_1', 'stoich_y2R_1', 'stoich_x1BC_1', 'stoich_y1BC_1', 'stoich_x2BC_1', 'stoich_y2BC_1', 'sink OM1_R_1', 'sink OM2_R_1', 'sink OM1_BC_1', 'sink OM2_BC_1', 'CF_SPM_1')
+
+# number of parameters in each category
+nparms <- parcats2(as_df = TRUE) %>% 
+  filter(!shrt %in% rmpars) %>% 
+  .$cats %>% 
+  table %>% 
   as.list
@@
 A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
-In addition to the initial conditions, 250 parameter values for each of the equations is also supplied at model execution.
+In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution.
 These parameters define relationships among fixed effects in the equations and represent ecological properties described by the model that influence hypoxia formation.
@@
 As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.
-The sensitivity of \ac{do} to perturbations of all parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
-For simplicity, the parameters were grouped into one of six categories based on their respective equations: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
+The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
+Initial screening removed 73 irrelevant parameters that were not relevant such that 178 were retained for the sensitivity analysis.
+Irrelevant parameters were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
+For simplicity, the remaining parameters were grouped into one of six categories based on their respective equations: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
 A full description is available as an appendix in \citepalias{LehrterIR}.
@@
 The analysis focused on sensitivity of \ac{do} in the \ac{zerod} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
-A local sensitivity analysis was performed for each of the 250 parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
+A local sensitivity analysis was performed for each of the 178 parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
 The analyses relied exlusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10}.
@@
 The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.
-Estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain individual sensitivity values of \ac{do} in response to a change in parameter $j$:
+Estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain individual sensitivity values of \ac{do} in response to a change in parame ter $j$:
 
@@
 
-Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 250 in the FishTank model.
+Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 178 evaluated for the FishTank model.
 Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 250 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/250, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 178 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/178, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
 Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}).

### 2016-08-22 ident_manu.tex
parcats2 updated for new fishtank
explanation of parameter removal

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Aug 3 11:12:36 2016 -0500
+  \\ Version Date:   Sat Aug 13 13:27:22 2016 -0500
 	}
@@
 The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
-A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 \citet[Table 1 in][]{Murrell14}.
+A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 \citep[Table 1 in][]{Murrell14}.
 
@@
 As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.
-The sensitivity of \ac{do} to perturbations of all parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
-For simplicity, the parameters were grouped into one of six categories based on their respective equations: optics ($n = $ 11 parameters), organic matter (29), phytoplankton (156), temperature (32), and zooplankton (22).
+The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
+Initial screening removed 73 irrelevant parameters that were not relevant such that 178 were retained for the sensitivity analysis.
+Irrelevant parameters were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
+For simplicity, the remaining parameters were grouped into one of six categories based on their respective equations: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (132), temperature (8), and zooplankton (22).
 A full description is available as an appendix in \citepalias{LehrterIR}.
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 140 of 250 parameters (56\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
-Within each parameter category, \ac{do} was sensitive to four parameters for optics (36\% of all optic parameters, \cref{tab:optsens}), seven for organic matter (24\%, \cref{tab:omsens}), 103 for phytoplankton (66\%, \cref{tab:phytosens}), seven for temperature (22\%, \cref{tab:tempsens}), and 19 for zooplankton (86\%, \cref{tab:zoopsens}).
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 105 of 178 parameters (59\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
+Within each parameter category, \ac{do} was sensitive to three parameters for optics (27\% of all optic parameters, \cref{tab:optsens}), eight for organic matter (25\%, \cref{tab:omsens}), 78 for phytoplankton (50\%, \cref{tab:phytosens}), six for temperature (27\%, \cref{tab:tempsens}), and 10 for zooplankton (33\%, \cref{tab:zoopsens}).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ $3.18\times 10^{-6}$ for \textit{Kcdom} (optics) to $328.35$ for \textit{Qc$_{p1}$} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $4.52$.
-Within categories, sensitivity ranged from $3.18\times 10^{-6}$ (\textit{Kcdom}) to $1.64$ (\textit{astar490}) for optics, $0.01$ (\textit{KGcdom}) to $2.11$ (\textit{k11}) for organic matter, $1\times 10^{-5}$ (\textit{Ksi$_{p1}$}) to $328.35$ (\textit{Qc$_{p1}$}) for phytopankton, $0.12$ (\textit{Tref(nospA+nospZ)$_{p1}$}) to $2.9$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $0$ (\textit{ZQp$_{z1}$}) to $0.82$ (\textit{ZKa$_{z1}$}) for zooplankton (\cref{fig:sensplo}, bottom).
-Average sensitivity values in each category were $L1 = $ $0.42$ for optics, $1.24$ for organic matter, $5.96$ for phytoplankton, $0.55$ for temperature, and $0.27$ for zooplankton.
+Among all parameters, sensitivity values ranged from $L1 = $ $2.29\times 10^{-5}$ for \textit{respg$_{p5}$} (phytoplankton) to $1.24$ for \textit{KG2} (organic matter), whereas average sensitivity among all parameters was $L1 = $ $0.12$.
+Within categories, sensitivity ranged from $6.78\times 10^{-4}$ (\textit{astarOMZ}) to $0.43$ (\textit{astar490}) for optics, $0.01$ (\textit{KNO3}) to $1.24$ (\textit{KG2}) for organic matter, $2.29\times 10^{-5}$ (\textit{respg$_{p5}$}) to $0.65$ (\textit{Qc$_{p1}$}) for phytopankton, $9.75\times 10^{-5}$ (\textit{Tref(nospA+nospZ)$_{p6}$}) to $9.97\times 10^{-5}$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $5.75\times 10^{-5}$ (\textit{ZQp$_{z1}$}) to $5.75\times 10^{-5}$ (\textit{ZQp$_{z2}$}) for zooplankton (\cref{fig:sensplo}, bottom).
+Average sensitivity values in each category were $L1 = $ $0.17$ for optics, $0.34$ for organic matter, $0.12$ for phytoplankton, $9.89\times 10^{-5}$ for temperature, and $0$ for zooplankton.
 Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied.
-Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ $19.71$, $14.56$), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
-Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0.31$, $0.23$ for groups one and two).
+Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ $0.12$, $0.12$), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
+Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0$, $0$ for groups one and two).
 
@@
 As expected, parameter perturbations had the largest effect during the summer months, although the effects varied.
-An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, \textit{ZKa$_{z1}$}, which caused an increase in \ac{do}.
+An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, \textit{ZQp$_{z2}$}, which caused an increase in \ac{do}.
 The phytoplankton parameter, \textit{Qc$_{p1}$}, had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.
@@
 Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
-By category, identifiability was lowest for parameter subsets in the phytoplankton ($7$\% less than $\gamma = 15$, $5.9$\% less than $\gamma = 10$)  and zooplankton categories ($28.9$\%, less than $\gamma = 15$, $24.2$\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable ($83.3$\% less than $\gamma = 15$, $73.3$\%, less than $\gamma = 10$).
+By category, identifiability was lowest for parameter subsets in the phytoplankton ($1.7$\% less than $\gamma = 15$, $1.2$\% less than $\gamma = 10$)  and zooplankton categories ($7.9$\%, less than $\gamma = 15$, $4.3$\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable ($NaN\times 10^{NA}$\% less than $\gamma = 15$, $NaN\times 10^{NA}$\%, less than $\gamma = 10$).
 All subset combinations for optics and organic matter parameters had $\gamma < 10$.
-All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four ($77$\% less than $\gamma = 15$, $70.8$\% less than $\gamma = 10$) and top five ($77$\% less than $\gamma = 15$, $70.8$\%, less than $\gamma = 10$) parameters.
+All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four ($2.7$\% less than $\gamma = 15$, $1.9$\% less than $\gamma = 10$) and top five ($2.7$\% less than $\gamma = 15$, $1.9$\%, less than $\gamma = 10$) parameters.
 
@@
 Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
-For the first selection heuristic, all sensitive parameters from the optics ($n = $ $4$, $\gamma =$  $3.7$) and organic matter ($n = $ $7$, $\gamma =$  $1.7$) categories were selected, whereas 23 were selected for phytoplankton ($\gamma = $ $13.7$), five for temperature ($\gamma = $ $11.4$), and five for zooplankton ($\gamma = $ $3.1$).
-For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$, with a majority from the phytoplankton category, \cref{tab:identall1}).
-For the third heuristic, 18 parameters were selected ($\gamma = $ $9.2$) with equal representation between categories.
+For the first selection heuristic, all sensitive parameters from the optics ($n = $ $2$, $\gamma =$  $3.5$) and organic matter ($n = $ $3$, $\gamma =$  $10.5$) categories were selected, whereas one were selected for phytoplankton ($\gamma = $ $1$), one for temperature ($\gamma = $ $1$), and one for zooplankton ($\gamma = $ $1$).
+For the second selection heuristic, two parameters were selected ($\gamma = $ $8.5$, with a majority from the phytoplankton category, \cref{tab:identall1}).
+For the third heuristic, four parameters were selected ($\gamma = $ $12.6$) with equal representation between categories.
 For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.
-Selection independent of category showed that including \textit{KNO3} caused in increase in $\gamma$ from $4.6$ to $15.6$ and equal selection within cateogies showed that including \textit{Tref(nospA+nospZ)$_{p2}$} caused in increase in $\gamma$ from $9.2$ to $66.2$.
+Selection independent of category showed that including \textit{Qc$_{p1}$} caused in increase in $\gamma$ from $8.5$ to $17.5$ and equal selection within cateogies showed that including \textit{ZQc$_{z1}$} caused in increase in $\gamma$ from $12.6$ to $72.2$.
 Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
@@
 \hline
-Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$1.64$&$8.64$\tabularnewline
-OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$&$0.1$\tabularnewline
-OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$0.01$&$0.01$\tabularnewline
-AOP, light attenuation due to CDOM&\textit{Kcdom}&$0$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
+Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.43$&$1.95$\tabularnewline
+OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.09$&$0.4$\tabularnewline
+OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$6.78\times 10^{-4}$&$0$\tabularnewline
 \hline
@@
 \hline
-rate constant for nitrification&\textit{k11}&$5$&$2.11$&$16.1$\tabularnewline
-O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.91$&$11.76$\tabularnewline
-turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.49$&$6.83$\tabularnewline
-turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.37$&$3.46$\tabularnewline
-half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.24$&$7.98$\tabularnewline
-half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.56$&$1.92$\tabularnewline
-decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.01$&$0.03$\tabularnewline
+turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.24$&$6.02$\tabularnewline
+turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.92$&$4.62$\tabularnewline
+half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.35$&$1.57$\tabularnewline
+O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.06$&$0.34$\tabularnewline
+maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$0.05$&$0.21$\tabularnewline
+NH4 rate constant for nitrification&\textit{KNH4}&$1$&$0.04$&$0.17$\tabularnewline
+decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.03$&$0.12$\tabularnewline
+half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.01$&$0.05$\tabularnewline
 \hline
@@
 \hline
-{coefficient for non-limiting nutrient}&&&\tabularnewline
-~~\textit{aN$_{p1}$}&$1$&$2.7$&$47.26$\tabularnewline
-~~\textit{aN$_{p3}$}&$1$&$0.66$&$3.16$\tabularnewline
-\hline
-{half-saturation constant for n}&&&\tabularnewline
-~~\textit{Kn$_{p3}$}&$5.93$&$1.15$&$9.22$\tabularnewline
-~~\textit{Kn$_{p4}$}&$1.13$&$0.62$&$2.5$\tabularnewline
-\hline
-{initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
-~~\textit{alpha$_{p4}$}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
-~~\textit{alpha$_{p3}$}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
-~~\textit{alpha$_{p5}$}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
-\hline
-{minimum n cell-quota}&&&\tabularnewline
-~~\textit{QminN$_{p3}$}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
-~~\textit{QminN$_{p4}$}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
-~~\textit{QminN$_{p1}$}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
-\hline
-{mortality coefficient}&&&\tabularnewline
-~~\textit{mA$_{p3}$}&$0.03$&$2.98$&$14.34$\tabularnewline
-~~\textit{mA$_{p4}$}&$0.11$&$1.35$&$7.04$\tabularnewline
-\hline
-{n-uptake rate measured at umax}&&&\tabularnewline
-~~\textit{vmaxN$_{p5}$}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
-~~\textit{vmaxN$_{p4}$}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
-~~\textit{vmaxN$_{p3}$}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
-~~\textit{vmaxN$_{p1}$}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
-\hline
-{p-uptake rate measured at umax}&&&\tabularnewline
-~~\textit{vmaxP$_{p3}$}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
-~~\textit{vmaxP$_{p1}$}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
-\hline
-{phytoplankton basal respiration coefficient}&&&\tabularnewline
-~~\textit{respb$_{p4}$}&$0.02$&$3.1$&$26.48$\tabularnewline
-~~\textit{respb$_{p3}$}&$0.02$&$2.15$&$6.35$\tabularnewline
-~~\textit{respb$_{p5}$}&$0.02$&$0.81$&$8.61$\tabularnewline
-\hline
 {phytoplankton carbon/cell}&&&\tabularnewline
-~~\textit{Qc$_{p1}$}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
-~~\textit{Qc$_{p3}$}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
-~~\textit{Qc$_{p2}$}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
-~~\textit{Qc$_{p4}$}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
-\hline
-{phytoplankton growth respiration coefficient}&&&\tabularnewline
-~~\textit{respg$_{p4}$}&$0.1$&$0.98$&$7.37$\tabularnewline
+~~\textit{Qc$_{p1}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
+~~\textit{Qc$_{p2}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
+~~\textit{Qc$_{p3}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
+~~\textit{Qc$_{p4}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
+~~\textit{Qc$_{p5}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
+~~\textit{Qc$_{p6}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
 \hline
@@
 {optimum temperature for growth(c)}&&&\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p4}$}&$17$&$2.9$&$22.95$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{z2}$}&$26$&$0.18$&$2.59$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p5}$}&$26$&$0.17$&$0.72$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p2}$}&$22$&$0.16$&$0.82$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{z1}$}&$22$&$0.16$&$0.33$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p3}$}&$17$&$0.14$&$0.78$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.12$&$0.29$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p4}$}&$22$&$9.97\times 10^{-5}$&$1.46\times 10^{-4}$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p2}$}&$22$&$9.96\times 10^{-5}$&$1.46\times 10^{-4}$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$9.96\times 10^{-5}$&$1.46\times 10^{-4}$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p3}$}&$22$&$9.86\times 10^{-5}$&$1.45\times 10^{-4}$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p5}$}&$22$&$9.86\times 10^{-5}$&$1.45\times 10^{-4}$\tabularnewline
+~~\textit{Tref(nospA+nospZ)$_{p6}$}&$22$&$9.75\times 10^{-5}$&$1.43\times 10^{-4}$\tabularnewline
 \hline
@@
 \hline
-{assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
-~~\textit{Zeffic$_{z1}$}&$0.4$&$0.23$&$0.55$\tabularnewline
-~~\textit{Zeffic$_{z2}$}&$0.4$&$0.21$&$0.75$\tabularnewline
-\hline
-{half saturation coefficient for grazing}&&&\tabularnewline
-~~\textit{ZKa$_{z1}$}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
-~~\textit{ZKa$_{z2}$}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
-\hline
-{maximum growth rate of zooplankton}&&&\tabularnewline
-~~\textit{Zumax$_{z2}$}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
-~~\textit{Zumax$_{z1}$}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
-\hline
-{proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
-~~\textit{Zslop$_{z1}$}&$0.25$&$0.12$&$0.33$\tabularnewline
-\hline
 {zooplankton biomass-dependent respiration factor}&&&\tabularnewline
-~~\textit{Zrespb$_{z1}$}&$0.1$&$0.45$&$3.02$\tabularnewline
-~~\textit{Zrespb$_{z2}$}&$0.42$&$0.09$&$1.05$\tabularnewline
+~~\textit{Zrespb$_{z1}$}&$0.1$&$0$&$0.01$\tabularnewline
+~~\textit{Zrespb$_{z2}$}&$0.1$&$0$&$0.01$\tabularnewline
 \hline
 {zooplankton carbon/individual}&&&\tabularnewline
-~~\textit{ZQc$_{z2}$}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
-~~\textit{ZQc$_{z1}$}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
-\hline
-{zooplankton growth-dependent respiration factor}&&&\tabularnewline
-~~\textit{Zrespg$_{z1}$}&$0.2$&$0.24$&$3.19$\tabularnewline
-~~\textit{Zrespg$_{z2}$}&$0.3$&$0.12$&$0.31$\tabularnewline
+~~\textit{ZQc$_{z1}$}&$3.13\times 10^{-4}$&$0.01$&$0.04$\tabularnewline
+~~\textit{ZQc$_{z2}$}&$3.13\times 10^{-4}$&$0.01$&$0.04$\tabularnewline
 \hline
 {zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
-~~\textit{Zm$_{z2}$}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
-~~\textit{Zm$_{z1}$}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
+~~\textit{Zm$_{z1}$}&$7.2\times 10^{-4}$&$4.95\times 10^{-4}$&$0$\tabularnewline
+~~\textit{Zm$_{z2}$}&$7.2\times 10^{-4}$&$4.95\times 10^{-4}$&$0$\tabularnewline
 \hline
 {zooplankton nitrogen/individual}&&&\tabularnewline
-~~\textit{ZQn$_{z1}$}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
-~~\textit{ZQn$_{z2}$}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
+~~\textit{ZQn$_{z1}$}&$6.95\times 10^{-5}$&$0$&$0.01$\tabularnewline
+~~\textit{ZQn$_{z2}$}&$6.95\times 10^{-5}$&$0$&$0.01$\tabularnewline
 \hline
 {zooplankton phosphorus/individual}&&&\tabularnewline
-~~\textit{ZQp$_{z2}$}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
-~~\textit{ZQp$_{z1}$}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
+~~\textit{ZQp$_{z1}$}&$3.77\times 10^{-6}$&$5.75\times 10^{-5}$&$2.66\times 10^{-4}$\tabularnewline
+~~\textit{ZQp$_{z2}$}&$3.77\times 10^{-6}$&$5.75\times 10^{-5}$&$2.66\times 10^{-4}$\tabularnewline
 \hline
@@
 \hline
-\footnotesize{phytoplankton carbon/cell}&\footnotesize{\textit{Qc$_{p1}$}}&$1$\textsuperscript{P}&$328.35$&$1$\tabularnewline
-\footnotesize{phytoplankton carbon/cell}&\footnotesize{\textit{Qc$_{p3}$}}&$2$\textsuperscript{P}&$232.8$&$1$\tabularnewline
-\footnotesize{N-uptake rate measured at umax}&\footnotesize{\textit{vmaxN$_{p5}$}}&$3$\textsuperscript{P}&$7.57$&$1$\tabularnewline
-\footnotesize{phytoplankton carbon/cell}&\footnotesize{\textit{Qc$_{p2}$}}&$4$\textsuperscript{P}&$4.08$&$1$\tabularnewline
-\footnotesize{phytoplankton basal respiration coefficient}&\footnotesize{\textit{respb$_{p4}$}}&$5$\textsuperscript{P}&$3.1$&$1$\tabularnewline
-\footnotesize{mortality coefficient}&\footnotesize{\textit{mA$_{p3}$}}&$6$\textsuperscript{P}&$2.98$&$1.01$\tabularnewline
-\footnotesize{Tref(nospA+nospZ): Optimum temperature for growth(C)}&\footnotesize{\textit{Tref(nospA+nospZ)$_{p4}$}}&$1$\textsuperscript{T}&$2.9$&$1.02$\tabularnewline
-\footnotesize{N-uptake rate measured at umax}&\footnotesize{\textit{vmaxN$_{p4}$}}&$7$\textsuperscript{P}&$2.88$&$1.04$\tabularnewline
-\footnotesize{coefficient for non-limiting nutrient}&\footnotesize{\textit{aN$_{p1}$}}&$8$\textsuperscript{P}&$2.7$&$1.05$\tabularnewline
-\footnotesize{P-uptake rate measured at umax}&\footnotesize{\textit{vmaxP$_{p3}$}}&$9$\textsuperscript{P}&$2.23$&$1.07$\tabularnewline
-\footnotesize{phytoplankton basal respiration coefficient}&\footnotesize{\textit{respb$_{p3}$}}&$10$\textsuperscript{P}&$2.15$&$1.73$\tabularnewline
-\footnotesize{rate constant for nitrification}&\footnotesize{\textit{k11}}&$1$\textsuperscript{OM}&$2.11$&$1.73$\tabularnewline
-\footnotesize{N-uptake rate measured at umax}&\footnotesize{\textit{vmaxN$_{p3}$}}&$11$\textsuperscript{P}&$1.99$&$1.73$\tabularnewline
-\footnotesize{O2 concentration that inhibits denitrification}&\footnotesize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$1.91$&$1.73$\tabularnewline
-\footnotesize{Chla specific absorption at 490 nm}&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$1.64$&$1.77$\tabularnewline
-\footnotesize{initial slope of the photosynthesis-irradiance relationship}&\footnotesize{\textit{alpha$_{p4}$}}&$12$\textsuperscript{P}&$1.61$&$4.1$\tabularnewline
-\footnotesize{minimum N cell-quota}&\footnotesize{\textit{QminN$_{p3}$}}&$13$\textsuperscript{P}&$1.53$&$4.1$\tabularnewline
-\footnotesize{turnover rate for OM1A and OM1G}&\footnotesize{\textit{KG1}}&$3$\textsuperscript{OM}&$1.49$&$4.2$\tabularnewline
-\footnotesize{turnover rate for OM2A and OM2G}&\footnotesize{\textit{KG2}}&$4$\textsuperscript{OM}&$1.37$&$4.62$\tabularnewline
-\footnotesize{mortality coefficient}&\footnotesize{\textit{mA$_{p4}$}}&$14$\textsuperscript{P}&$1.35$&$4.62$\tabularnewline
+\footnotesize{turnover rate for OM2A and OM2G}&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.24$&$1$\tabularnewline
+\footnotesize{turnover rate for OM1A and OM1G}&\footnotesize{\textit{KG1}}&$2$\textsuperscript{OM}&$0.92$&$8.48$\tabularnewline
 \hline
@@
 {Ammonium}&&&&\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$2.38$&$1$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$2.23$&$3.1$\tabularnewline
-~~\scriptsize{rate constant for nitrification}&\scriptsize{\textit{k11}}&$1$\textsuperscript{OM}&$0.68$&$3.1$\tabularnewline
-~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$0.46$&$3.12$\tabularnewline
-~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$3$\textsuperscript{OM}&$0.39$&$6.53$\tabularnewline
-~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$3$\textsuperscript{P}&$0.35$&$7.18$\tabularnewline
-~~\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p4}$}}&$4$\textsuperscript{P}&$0.35$&$7.26$\tabularnewline
-~~\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p3}$}}&$5$\textsuperscript{P}&$0.34$&$13.14$\tabularnewline
+~~\scriptsize{NH4 rate constant for nitrification}&\scriptsize{\textit{KNH4}}&$1$\textsuperscript{OM}&$0.81$&$1$\tabularnewline
 \hline
 {Chlorophyll}&&&&\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$104.26$&$1$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$47.86$&$3.65$\tabularnewline
-~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$3$\textsuperscript{P}&$1.71$&$4.07$\tabularnewline
-~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$1.29$&$5.58$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p5}$}}&$1$\textsuperscript{P}&$0.08$&$1$\tabularnewline
 \hline
 {Irradiance}&&&&\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$0.32$&$1$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$0.25$&$4.87$\tabularnewline
-~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$3$\textsuperscript{P}&$0.19$&$5.38$\tabularnewline
-~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$4$\textsuperscript{P}&$0.17$&$7.61$\tabularnewline
-~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.15$&$13.34$\tabularnewline
-~~\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p3}$}}&$5$\textsuperscript{P}&$0.11$&$13.5$\tabularnewline
-~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$0.08$&$14.64$\tabularnewline
+~~\scriptsize{OMA specific absorption at 490 nm}&\scriptsize{\textit{astarOMA}}&$1$\textsuperscript{O}&$5.86\times 10^{14}$&$1$\tabularnewline
+~~\scriptsize{decay rate of CDOM, 1/day}&\scriptsize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$2.66\times 10^{14}$&$3.92$\tabularnewline
 \hline
 {Nitrate}&&&&\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$1.07\times 10^{38}$&$1$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$1.44\times 10^{23}$&$1$\tabularnewline
-~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$2\times 10^{5}$&$10.55$\tabularnewline
+~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$1$\textsuperscript{OM}&$0.85$&$1$\tabularnewline
 \hline
 {OM1}&&&&\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1.5$\textsuperscript{P}&$1.13$&$1$\tabularnewline
-~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p4}$}}&$1.5$\textsuperscript{P}&$0.78$&$1.68$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$3$\textsuperscript{P}&$0.76$&$8.66$\tabularnewline
-~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$0.71$&$8.98$\tabularnewline
-~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$4$\textsuperscript{P}&$0.48$&$9.22$\tabularnewline
-~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.43$&$9.22$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$3.5$\textsuperscript{P}&$43.06$&$1$\tabularnewline
 \hline
 {OM2}&&&&\tabularnewline
-~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.3$&$1$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$0.94$&$2.01$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$0.74$&$7.65$\tabularnewline
-~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$3$\textsuperscript{P}&$0.35$&$11$\tabularnewline
-~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$0.34$&$11.29$\tabularnewline
-~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$4$\textsuperscript{P}&$0.31$&$11.44$\tabularnewline
-~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.29$&$11.54$\tabularnewline
-~~\scriptsize{maximum growth rate of zooplankton}&\scriptsize{\textit{Zumax$_{z1}$}}&$1$\textsuperscript{Z}&$0.29$&$11.66$\tabularnewline
+~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$35.62$&$1$\tabularnewline
+~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$3.5$\textsuperscript{P}&$33.53$&$10.36$\tabularnewline
 \hline
 {Phosphate}&&&&\tabularnewline
-~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$1$\textsuperscript{P}&$2.92$&$1$\tabularnewline
-~~\scriptsize{P-uptake rate measured at umax}&\scriptsize{\textit{vmaxP$_{p3}$}}&$2$\textsuperscript{P}&$1.57$&$2.23$\tabularnewline
-~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$3$\textsuperscript{P}&$0.78$&$2.57$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$4$\textsuperscript{P}&$0.73$&$5.29$\tabularnewline
+~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$1$\textsuperscript{OM}&$0.21$&$1$\tabularnewline
 \hline

### 2016-08-22 R/funcs.R

@@ -74,7 +74,7 @@ parcats2 <- function(as_df = FALSE){
       'astarOMA_1',
       'astarOMZ_1',
       'astarOMR_1',
-      'astarOMbC_1',
+      'astarOMBC_1',
       'sink CDOM_1'
       ),
     lngs = c(

### 2016-08-23 ident_manu.Rnw
sensalltile redone for p1z1

@@
 %knitr options
-<<setup,include=F,cache=F>>=
+<<setup, include = F, cache = F>>=
 library(knitr)
@@
 options(replace.assign = TRUE, width = 90)
-
+@
+
+% R dependencies
+<<include = F, cache = F>>=
 source('R/funcs.r')
@@
 
-<<echo = FALSE>>=
-# remove irrelevant parameters, from 'ignore/noparams.csv'
-rmpars <- c('Kw_1', 'Kcdom_1', 'Kspm_1', 'Kchla_1', 'aw490_1', 'astarOMR_1', 'astarOMBC_1', 'KTg1(nospA+nospZ)_1', 'KTg1(nospA+nospZ)_2', 'KTg1(nospA+nospZ)_3', 'KTg1(nospA+nospZ)_4', 'KTg1(nospA+nospZ)_5', 'KTg1(nospA+nospZ)_6', 'KTg1(nospA+nospZ)_7', 'KTg1(nospA+nospZ)_8', 'KTg2(nospA+nospZ)_1', 'KTg2(nospA+nospZ)_2', 'KTg2(nospA+nospZ)_3', 'KTg2(nospA+nospZ)_4', 'KTg2(nospA+nospZ)_5', 'KTg2(nospA+nospZ)_6', 'KTg2(nospA+nospZ)_7', 'KTg2(nospA+nospZ)_8', 'Ea_R(nospA+nospZ)_1', 'Ea_R(nospA+nospZ)_2', 'Ea_R(nospA+nospZ)_3', 'Ea_R(nospA+nospZ)_4', 'Ea_R(nospA+nospZ)_5', 'Ea_R(nospA+nospZ)_6', 'Ea_R(nospA+nospZ)_7', 'Ea_R(nospA+nospZ)_8', 'beta_1', 'beta_2', 'beta_3', 'beta_4', 'beta_5', 'beta_6', 'QmaxN_1', 'QmaxN_2', 'QmaxN_3', 'QmaxN_4', 'QmaxN_5', 'QmaxN_6', 'QmaxP_1', 'QmaxP_2', 'QmaxP_3', 'QmaxP_4', 'QmaxP_5', 'QmaxP_6', 'nfQs_1', 'nfQs_2', 'nfQs_3', 'nfQs_4', 'nfQs_5', 'nfQs_6', 'KG1_R_1', 'KG2_R_1', 'KG1_BC_1', 'KG2_BC_1', 'pCO2_1', 'stoich_x1R_1', 'stoich_y1R_1', 'stoich_x2R_1', 'stoich_y2R_1', 'stoich_x1BC_1', 'stoich_y1BC_1', 'stoich_x2BC_1', 'stoich_y2BC_1', 'sink OM1_R_1', 'sink OM2_R_1', 'sink OM1_BC_1', 'sink OM2_BC_1', 'CF_SPM_1')
-
-# number of parameters in each category
-nparms <- parcats2(as_df = TRUE) %>% 
-  filter(!shrt %in% rmpars) %>% 
-  .$cats %>% 
-  table %>% 
-  as.list
-@
-
 Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
@@
 The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
-Initial screening removed 73 irrelevant parameters that were not relevant such that 178 were retained for the sensitivity analysis.
-Irrelevant parameters were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
-For simplicity, the remaining parameters were grouped into one of six categories based on their respective equations: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
+Initial screening removed 73 irrelevant parameters that were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
+
+<<echo = FALSE>>=
+# remove irrelevant parameters, from 'ignore/noparams.csv'
+rmpars <- c('Kw_1', 'Kcdom_1', 'Kspm_1', 'Kchla_1', 'aw490_1', 'astarOMR_1', 'astarOMBC_1', 'KTg1(nospA+nospZ)_1', 'KTg1(nospA+nospZ)_2', 'KTg1(nospA+nospZ)_3', 'KTg1(nospA+nospZ)_4', 'KTg1(nospA+nospZ)_5', 'KTg1(nospA+nospZ)_6', 'KTg1(nospA+nospZ)_7', 'KTg1(nospA+nospZ)_8', 'KTg2(nospA+nospZ)_1', 'KTg2(nospA+nospZ)_2', 'KTg2(nospA+nospZ)_3', 'KTg2(nospA+nospZ)_4', 'KTg2(nospA+nospZ)_5', 'KTg2(nospA+nospZ)_6', 'KTg2(nospA+nospZ)_7', 'KTg2(nospA+nospZ)_8', 'Ea_R(nospA+nospZ)_1', 'Ea_R(nospA+nospZ)_2', 'Ea_R(nospA+nospZ)_3', 'Ea_R(nospA+nospZ)_4', 'Ea_R(nospA+nospZ)_5', 'Ea_R(nospA+nospZ)_6', 'Ea_R(nospA+nospZ)_7', 'Ea_R(nospA+nospZ)_8', 'beta_1', 'beta_2', 'beta_3', 'beta_4', 'beta_5', 'beta_6', 'QmaxN_1', 'QmaxN_2', 'QmaxN_3', 'QmaxN_4', 'QmaxN_5', 'QmaxN_6', 'QmaxP_1', 'QmaxP_2', 'QmaxP_3', 'QmaxP_4', 'QmaxP_5', 'QmaxP_6', 'nfQs_1', 'nfQs_2', 'nfQs_3', 'nfQs_4', 'nfQs_5', 'nfQs_6', 'KG1_R_1', 'KG2_R_1', 'KG1_BC_1', 'KG2_BC_1', 'pCO2_1', 'stoich_x1R_1', 'stoich_y1R_1', 'stoich_x2R_1', 'stoich_y2R_1', 'stoich_x1BC_1', 'stoich_y1BC_1', 'stoich_x2BC_1', 'stoich_y2BC_1', 'sink OM1_R_1', 'sink OM2_R_1', 'sink OM1_BC_1', 'sink OM2_BC_1', 'CF_SPM_1')
+
+# number of parameters in each category
+nparms <- parcats2(as_df = TRUE) %>% 
+  filter(!shrt %in% rmpars) %>% 
+  .$cats %>% 
+  table %>% 
+  as.list
+@
+
+As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize greater complexity in community structure and foodweb dynamics.
+However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc..
+Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
+To remove obvious redundancies in the model, the sensitivity analyes were conducted using only one phytoplankton and one zooplankton group.
+This further reduced the parameter set....
+For simplicity, the remaining parameters were grouped in  to one of six categories based on their respective equations: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
 A full description is available as an appendix in \citepalias{LehrterIR}.
@@
 \noindent where the estimate depended on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
-The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y_i$, were set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
-The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes that may vary in scale.
+The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y_i$, were set as the default value of the unperturbed parameter and the initial value of $y$ at time $= 0$ \citep{Soetaert10}.
+The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes and state variables that differ in scale.
 Estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain individual sensitivity values of \ac{do} in response to a change in parame ter $j$:
@@
 \section{Results}
-
-% for inline
-<<echo = FALSE, cache = F>>=
-data(sens_ests)
-data(sens_ests_cat)
-
-# number of parameters in each category
-bycat <- table(sens_ests_cat$Category)
-nms <- names(bycat)
-bycat <- as.numeric(bycat)
-names(bycat) <- nms
-bycat <- toeng(bycat)
-
-# percent of parameters in each category
-lncats <- table(sens_ests_cat$Category) %>% 
-  `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>% 
-  `*` (100) %>% 
-  form_fun(nsm_val = 0) %>% 
-  as.list %>% 
-  lapply(., paste0, '\\%')
-
-# L1 range
-sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
-  sens_ests_cat[., ] %>% 
-  mutate(
-    error = sapply(error, scinot),
-    Parameter = par_txt(Parameter)
-    )
-
-# L1 range within categories
-sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
-  lapply(., function(x){
-
-    with(x, which(error %in% range(error))) %>% 
-      x[., ] %>% 
-      mutate(
-        Parameter = par_txt(Parameter), 
-        error = sapply(error, scinot)
-      )
-
-    }
-  )
-
-# average L1, all and by category
-sensave <- scinot(mean(sens_ests_cat$error))
-sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
-  lapply(., function(x) scinot(mean(x$error)))
-
-# phyto errors
-phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>% 
-  separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
-  group_by(grp) %>%
-  summarise(grpave = mean(error)) %>% 
-  arrange(-grpave) %>% 
-  mutate(grpave = sapply(grpave, scinot))
-
-# zoop errors 
-zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>% 
-  separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
-  group_by(grp) %>%
-  summarise(grpave = mean(error)) %>% 
-  arrange(-grpave) %>% 
-  mutate(grpave = sapply(grpave, scinot))
-@
-
-\subsection{Local sensitivity analysis}
-
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 178 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/178, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
+%' 
+%' % for inline
+%' <<echo = FALSE, eavl = F, cache = F>>=
+%' data(sens_ests)
+%' data(sens_ests_cat)
+%' 
+%' # number of parameters in each category
+%' bycat <- table(sens_ests_cat$Category)
+%' nms <- names(bycat)
+%' bycat <- as.numeric(bycat)
+%' names(bycat) <- nms
+%' bycat <- toeng(bycat)
+%' 
+%' # percent of parameters in each category
+%' lncats <- table(sens_ests_cat$Category) %>% 
+%'   `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>% 
+%'   `*` (100) %>% 
+%'   form_fun(nsm_val = 0) %>% 
+%'   as.list %>% 
+%'   lapply(., paste0, '\\%')
+%' 
+%' # L1 range
+%' sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
+%'   sens_ests_cat[., ] %>% 
+%'   mutate(
+%'     error = sapply(error, scinot),
+%'     Parameter = par_txt(Parameter)
+%'     )
+%' 
+%' # L1 range within categories
+%' sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
+%'   lapply(., function(x){
+%'     
+%'     with(x, which(error %in% range(error))) %>% 
+%'       x[., ] %>% 
+%'       mutate(
+%'         Parameter = par_txt(Parameter), 
+%'         error = sapply(error, scinot)
+%'       )
+%'     
+%'     }
+%'   )
+%' 
+%' # average L1, all and by category
+%' sensave <- scinot(mean(sens_ests_cat$error))
+%' sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
+%'   lapply(., function(x) scinot(mean(x$error)))
+%'     
+%' # phyto errors
+%' phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>% 
+%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
+%'   group_by(grp) %>%
+%'   summarise(grpave = mean(error)) %>% 
+%'   arrange(-grpave) %>% 
+%'   mutate(grpave = sapply(grpave, scinot))
+%' 
+%' # zoop errors 
+%' zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>% 
+%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
+%'   group_by(grp) %>%
+%'   summarise(grpave = mean(error)) %>% 
+%'   arrange(-grpave) %>% 
+%'   mutate(grpave = sapply(grpave, scinot))
+%' @
+%' 
+%' \subsection{Local sensitivity analysis}
+%' 
+%' Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 178 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/178, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
 Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}).
@@
 Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two).
-
-Response of \ac{do} to parameter perturbations was not uniform across the time series.
+%' 
+%' Response of \ac{do} to parameter perturbations was not uniform across the time series.
 \Cref{fig:sensplo} shows variation for the top parameters within each category.
@@
 The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (\Sexpr{sensrngcat$Optics$Parameter[2]}) and phytoplankton (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) parameters.
-
-\subsection{Subset identifiability}
-
-<<>>=
-data(cat_ident)
-data(top_ident)
-
-# percent combos less than gamma 15, 10 by category
-collcatpers <- lapply(cat_ident, function(x){
-
-  colls <- x$coll
-  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-  c(l15, l10)
-
-  })
-
-# percent combos less than gamma 15, 10 by top in each category
-colltoppers <- lapply(top_ident, function(x){
-
-  colls <- x$coll
-  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-  c(l15, l10)
-
-  })
-
-maxtempcoll <- scinot(max(cat_ident$Temperature$coll))
-@
-
-The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+%' 
+%' \subsection{Subset identifiability}
+%' 
+%' <<eval = F>>=
+%' data(cat_ident)
+%' data(top_ident)
+%' 
+%' # percent combos less than gamma 15, 10 by category
+%' collcatpers <- lapply(cat_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' 
+%' # percent combos less than gamma 15, 10 by top in each category
+%' colltoppers <- lapply(top_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' 
+%' maxtempcoll <- scinot(max(cat_ident$Temperature$coll))
+%' @
+%' 
+%' The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
 Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
@@
 All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\% less than $\gamma = 10$) and top five (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\%, less than $\gamma = 10$) parameters.
-
-<<>>=
-temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
-@
-
-A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
+%' 
+%' <<eval = F>>=
+%' temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
+%' @
+%' 
+%' A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
 For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.
@@
 Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).
-
-<<>>=
-data(p1z1cat_ident)
-data(p1z1top_ident)
-
-# percent combos less than gamma 15, 10 by category
-p1z1collcatpers <- lapply(p1z1cat_ident, function(x){
-
-  colls <- x$coll
-  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-  c(l15, l10)
-
-  })
-
-# percent combos less than gamma 15, 10 by top in each category
-p1z1colltoppers <- lapply(p1z1top_ident, function(x){
-
-  colls <- x$coll
-  l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-  l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-  c(l15, l10)
-
-  })
-@
-
-Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
+%' 
+%' <<eval = F>>=
+%' data(p1z1cat_ident)
+%' data(p1z1top_ident)
+%' 
+%' # percent combos less than gamma 15, 10 by category
+%' p1z1collcatpers <- lapply(p1z1cat_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' 
+%' # percent combos less than gamma 15, 10 by top in each category
+%' p1z1colltoppers <- lapply(p1z1top_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' @
+%' 
+%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
 As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.
@@
 Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (\Sexpr{p1z1colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top4[2]}\% less than $\gamma = 10$) and a decrease (\Sexpr{p1z1colltoppers$top5[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top5[2]}\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).
-
-\subsection{Parameter selection}
-
-<<>>=
-data(tocal)
-
-# n parms and ident for each selection heuristic
-h1_id <- tocal$cat %>% 
-  split(., .$Category) %>% 
-  lapply(function(x){
-    x <- x[x$coll < 15, ]
-    list(nrow(x), scinot(max(x$coll), digits = 1))
-  }) 
-h2_id <- filter(tocal$top, coll < 15) %>%
-  list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
-  .[c(2, 3)]
-h3_id <- filter(tocal$cattop, coll < 15) %>%
-  list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
-  .[c(2, 3)]
-
-# which parameter broke selection for h2, h3
-h2_brk <- tocal$top
-sel <- which(h2_brk$coll < 15)
-h2_brk <- h2_brk[c(sel, rev(sel)[1] + 1), ] %>% 
-  arrange(-coll) %>% 
-  .[1:2, ] %>% 
-  list(c(as.character(.$Parameter[1]), .$coll)) %>% 
-  .[[2]]
-# which parameter broke selection for h2, h3
-h3_brk <- tocal$cattop
-sel <- which(h3_brk$coll < 15)
-h3_brk <- h3_brk[c(sel, rev(sel)[1] + 1), ] %>% 
-  arrange(-coll) %>% 
-  .[1:2, ] %>% 
-  list(c(as.character(.$Parameter[1]), .$coll)) %>% 
-  .[[2]]
-@
-
-Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
+%' 
+%' \subsection{Parameter selection}
+%' 
+%' <<eval = F>>=
+%' data(tocal)
+%' 
+%' # n parms and ident for each selection heuristic
+%' h1_id <- tocal$cat %>% 
+%'   split(., .$Category) %>% 
+%'   lapply(function(x){
+%'     x <- x[x$coll < 15, ]
+%'     list(nrow(x), scinot(max(x$coll), digits = 1))
+%'   }) 
+%' h2_id <- filter(tocal$top, coll < 15) %>%
+%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
+%'   .[c(2, 3)]
+%' h3_id <- filter(tocal$cattop, coll < 15) %>%
+%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
+%'   .[c(2, 3)]
+%' 
+%' # which parameter broke selection for h2, h3
+%' h2_brk <- tocal$top
+%' sel <- which(h2_brk$coll < 15)
+%' h2_brk <- h2_brk[c(sel, rev(sel)[1] + 1), ] %>% 
+%'   arrange(-coll) %>% 
+%'   .[1:2, ] %>% 
+%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
+%'   .[[2]]
+%' # which parameter broke selection for h2, h3
+%' h3_brk <- tocal$cattop
+%' sel <- which(h3_brk$coll < 15)
+%' h3_brk <- h3_brk[c(sel, rev(sel)[1] + 1), ] %>% 
+%'   arrange(-coll) %>% 
+%'   .[1:2, ] %>% 
+%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
+%'   .[[2]]
+%' @
+%' 
+%' Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
 For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).
@@
 % optics sensitivity
-<<optsens, eval = T, cache = F>>=
+<<optsens, eval = F, cache = F>>=
 senstab1('Optics', 'optsens')
@@
 % organic matter sensitivity
-<<omsens, eval = T, cache = F>>=
+<<omsens, eval = F, cache = F>>=
 senstab1('Organic Matter', 'omsens')
@@
 % phytoplankton sensitivity
-<<phytosens, eval = T, cache = F>>=
+<<phytosens, eval = F, cache = F>>=
 # data(sens_ests_cat)
@@
 % temperature sensitivity
-<<tempsens, eval = T, cache = F >>=
+<<tempsens, eval = F, cache = F >>=
 senstab2('Temperature', 'tempsens')
@@
 % zooplankton sensitivity
-<<zoopsens, eval = T, cache = F>>=
+<<zoopsens, eval = F, cache = F>>=
 senstab2('Zooplankton', 'zoopsens')
@@
 % ident all states
-<<identdo, eval = T, cache = F>>=
+<<identdo, eval = F, cache = F>>=
 data(tocal_all)
@@
 % ident all states
-<<identall, eval = T, cache = F>>=
+<<identall, eval = F, cache = F>>=
 data(tocal_all)
@@
 # format category label so no duplicates
-totab <- tocal_all$top_all %>% 
+totab <- lapply(tocal_all, function(x) x$top) %>% 
   reshape2::melt(., id.var = names(.[[1]])) %>% 
@@
 % combination example
-<<combnex, echo = F, fig.cap = 'Examples of unique parameter combinations from different parameter sets and number of selected parameters.
+<<combnex, eval = T, echo = F, fig.cap = 'Examples of unique parameter combinations from different parameter sets and number of selected parameters.
 The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
@@
 % sensitivity example of top
-<<sensplo, fig.cap = 'Sensitivity of \\ac{do} to parameter changes.
+<<sensplo, eval = F, fig.cap = 'Sensitivity of \\ac{do} to parameter changes.
 The solid lines show the change in \\ac{do} based on a 50\\% change from the default parameter values (dashed line) for each parameter.
@@
 % identifiability boxplots
-<<identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
+<<identbox, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
 Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
@@
 % parameter exclusion temp
-<<excltemp, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of temperature parameters for subset combinations in \\cref{fig:identbox}.
+<<excltemp, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of temperature parameters for subset combinations in \\cref{fig:identbox}.
 Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
@@
 % identifiability boxplot, p1, z1 only
-<<p1z1identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
+<<p1z1identbox, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
 Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
@@
 % heuristic plots o2
-<<heurist, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics.
+<<heurist, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics.
 Parameters are selected by decreasing sensitivity for all examples (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
@@
 % heuristic plots, all state
-<<heurist_stts, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables.
+<<heurist_stts, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables.
 Parameters are selected by decreasing sensitivity indepent of parameter categories.
@@
 
-<<sensalltile, echo = F, fig.height = 9, fig.width = 9, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
-Values are truncated by the 5\\textsuperscript{th} and 95\\textsuperscript{th} sensitivity values between all parameters for visual appearance.
-Parameters are grouped by category (plot strips).
-Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1-p6, z1, z2), respectively.'>>=
+<<sensalltile, eval = T, echo = F, fig.height = 7, fig.width = 6, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
+Values are in log-space for visual comparison.
+Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.'>>=
 data(sens_ests_cat_all)
@@
 
-lims <- with(tmp, quantile(error, c(0.05, 0.95))) %>% 
+lims <- with(tmp, quantile(error)) %>% 
   as.numeric
@@
 
-toplo <- filter(tmp, error < lims[2] & error > lims[1]) %>% 
-  mutate(
-    L1 = factor(L1, levels = stts_lev, labels = stts_lab)
+toplo <- mutate(tmp,
+    L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab))
   ) %>% 
@@
 
-toplo1 <- filter(toplo, !Category %in% c('Phytoplankton', 'Zooplankton')) %>% 
-  mutate(Parameter = as.character(par_txt(Parameter, frm = 'exp')))
-toplo2 <- filter(toplo, Category %in% c('Phytoplankton')) %>% 
-  mutate(
-    grp = gsub('^.*_([1-6])$', 'p\\1', Parameter), 
-    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
-  )
-toplo3 <- filter(toplo, Category %in% c('Zooplankton')) %>% 
-  mutate(
-    grp = gsub('^.*_([1-2])$', 'z\\1', Parameter), 
-    Parameter = as.character(par_txt(Parameter, frm = 'exp'))
-  )
+toplo1 <- mutate(toplo, Parameter = as.character(par_txt(Parameter, frm = 'exp')))
 
@@
   panel.grid.minor = element_blank(), 
-  axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6), 
-  axis.text.y = element_text(size =8),
-  axis.title.y = element_blank(), 
-  axis.title.x = element_blank(),
-  legend.position = 'none', 
-  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt')
-  )
-
-p1 <- ggplot(toplo1, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
-  geom_tile() + 
+  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
+  axis.text.y = element_text(size = 6),
+  legend.position = 'top', 
+  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt'), 
+  strip.background = element_blank(), 
+  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5)
+  )
+
+ggplot(toplo1, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
+  geom_tile(colour = 'black') + 
   pbase +
-  scale_x_discrete(expand = c(0, 0),
+  scale_y_discrete('Parameter', 
+    expand = c(0, 0),
     breaks = toplo1$Parameter, 
@@
     ) + 
-  scale_y_discrete(expand = c(0, 0)) +
-  scale_fill_distiller(palette = "Spectral", limits = lims) + 
-  facet_grid(~Category, scales = 'free')
-p2 <- ggplot(toplo2, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
-  geom_tile() + 
-  pbase +
-  scale_x_discrete(expand = c(0, 0), 
-    breaks = toplo2$Parameter, 
-    labels = parse(text = toplo2$Parameter)
-    ) + 
-  scale_y_discrete(expand = c(0, 0)) +
-  scale_fill_distiller(palette = "Spectral", limits = lims) + 
-  facet_grid(~grp, scales = 'free') + 
-  ggtitle('Phytoplankton')
-p3 <- ggplot(toplo3, aes(x = Parameter, y = L1, fill = Sensitivity)) + 
-  geom_tile() + 
-  pbase +
-  scale_x_discrete(expand = c(0, 0), 
-    breaks = toplo3$Parameter, 
-    labels = parse(text = toplo3$Parameter)
-    ) + 
-  scale_y_discrete(expand = c(0, 0)) + 
-  scale_fill_distiller(palette = "Spectral", limits = lims) + 
-  facet_grid(~grp, scales = 'free') + 
-  ggtitle('Zooplankton') + 
-  theme(legend.position = 'top')
-pleg <- g_legend(p3)
-p3 <- p3 + theme(legend.position = 'none')
-
-grid.arrange(
-  pleg, p1, p2, p3, ncol = 1, 
-  heights = c(0.2, 1, 0.85, 1),
-  bottom = 'Parameter', 
-  left = 'State variable'
-)
+  scale_x_discrete('State variable', expand = c(0, 0)) +
+  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
+  facet_grid(Category~., scales = 'free_y', space = 'free') + 
+  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
+
 @

### 2016-08-23 ident_manu.tex
sensalltile redone for p1z1

@@
 
+% R dependencies
+
 % get the version based on commit date
@@
   \vspace{1in} 
-  \\ Version Date:   Sat Aug 13 13:27:22 2016 -0500
+  \\ Version Date:   Mon Aug 22 16:13:24 2016 -0500
 	}
@@
 The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
-Initial screening removed 73 irrelevant parameters that were not relevant such that 178 were retained for the sensitivity analysis.
-Irrelevant parameters were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
-For simplicity, the remaining parameters were grouped into one of six categories based on their respective equations: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (132), temperature (8), and zooplankton (22).
+Initial screening removed 73 irrelevant parameters that were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
+
+As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize greater complexity in community structure and foodweb dynamics.
+However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc..
+Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
+To remove obvious redundancies in the model, the sensitivity analyes were conducted using only one phytoplankton and one zooplankton group.
+This further reduced the parameter set....
+For simplicity, the remaining parameters were grouped in  to one of six categories based on their respective equations: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (132), temperature (8), and zooplankton (22).
 A full description is available as an appendix in \citepalias{LehrterIR}.
@@
 \section{Results}
-
-% for inline
-
-\subsection{Local sensitivity analysis}
-
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 105 of 178 parameters (59\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
-Within each parameter category, \ac{do} was sensitive to three parameters for optics (27\% of all optic parameters, \cref{tab:optsens}), eight for organic matter (25\%, \cref{tab:omsens}), 78 for phytoplankton (50\%, \cref{tab:phytosens}), six for temperature (27\%, \cref{tab:tempsens}), and 10 for zooplankton (33\%, \cref{tab:zoopsens}).
+%' 
+%' % for inline
+%' <<echo = FALSE, eavl = F, cache = F>>=
+%' data(sens_ests)
+%' data(sens_ests_cat)
+%' 
+%' # number of parameters in each category
+%' bycat <- table(sens_ests_cat$Category)
+%' nms <- names(bycat)
+%' bycat <- as.numeric(bycat)
+%' names(bycat) <- nms
+%' bycat <- toeng(bycat)
+%' 
+%' # percent of parameters in each category
+%' lncats <- table(sens_ests_cat$Category) %>% 
+%'   `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>% 
+%'   `*` (100) %>% 
+%'   form_fun(nsm_val = 0) %>% 
+%'   as.list %>% 
+%'   lapply(., paste0, '\\%')
+%' 
+%' # L1 range
+%' sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
+%'   sens_ests_cat[., ] %>% 
+%'   mutate(
+%'     error = sapply(error, scinot),
+%'     Parameter = par_txt(Parameter)
+%'     )
+%' 
+%' # L1 range within categories
+%' sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
+%'   lapply(., function(x){
+%'     
+%'     with(x, which(error %in% range(error))) %>% 
+%'       x[., ] %>% 
+%'       mutate(
+%'         Parameter = par_txt(Parameter), 
+%'         error = sapply(error, scinot)
+%'       )
+%'     
+%'     }
+%'   )
+%' 
+%' # average L1, all and by category
+%' sensave <- scinot(mean(sens_ests_cat$error))
+%' sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
+%'   lapply(., function(x) scinot(mean(x$error)))
+%'     
+%' # phyto errors
+%' phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>% 
+%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
+%'   group_by(grp) %>%
+%'   summarise(grpave = mean(error)) %>% 
+%'   arrange(-grpave) %>% 
+%'   mutate(grpave = sapply(grpave, scinot))
+%' 
+%' # zoop errors 
+%' zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>% 
+%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
+%'   group_by(grp) %>%
+%'   summarise(grpave = mean(error)) %>% 
+%'   arrange(-grpave) %>% 
+%'   mutate(grpave = sapply(grpave, scinot))
+%' @
+%' 
+%' \subsection{Local sensitivity analysis}
+%' 
+%' Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in nrow(sens_ests_cat) of 178 parameters (round(100 * nrow(sens_ests_cat)/178, 0)\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
+Within each parameter category, \ac{do} was sensitive to bycat$Optics parameters for optics (lncats$Optics of all optic parameters, \cref{tab:optsens}), bycat$`Organic Matter` for organic matter (lncats$`Organic Matter`, \cref{tab:omsens}), bycat$Phytoplankton for phytoplankton (lncats$Phytoplankton, \cref{tab:phytosens}), bycat$Temperature for temperature (lncats$Temperature, \cref{tab:tempsens}), and bycat$Zooplankton for zooplankton (lncats$Zooplankton, \cref{tab:zoopsens}).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ $2.29\times 10^{-5}$ for \textit{respg$_{p5}$} (phytoplankton) to $1.24$ for \textit{KG2} (organic matter), whereas average sensitivity among all parameters was $L1 = $ $0.12$.
-Within categories, sensitivity ranged from $6.78\times 10^{-4}$ (\textit{astarOMZ}) to $0.43$ (\textit{astar490}) for optics, $0.01$ (\textit{KNO3}) to $1.24$ (\textit{KG2}) for organic matter, $2.29\times 10^{-5}$ (\textit{respg$_{p5}$}) to $0.65$ (\textit{Qc$_{p1}$}) for phytopankton, $9.75\times 10^{-5}$ (\textit{Tref(nospA+nospZ)$_{p6}$}) to $9.97\times 10^{-5}$ (\textit{Tref(nospA+nospZ)$_{p4}$}) for temperature, and $5.75\times 10^{-5}$ (\textit{ZQp$_{z1}$}) to $5.75\times 10^{-5}$ (\textit{ZQp$_{z2}$}) for zooplankton (\cref{fig:sensplo}, bottom).
-Average sensitivity values in each category were $L1 = $ $0.17$ for optics, $0.34$ for organic matter, $0.12$ for phytoplankton, $9.89\times 10^{-5}$ for temperature, and $0$ for zooplankton.
+Among all parameters, sensitivity values ranged from $L1 = $ sensrng$error[1] for sensrng$Parameter[1] (tolower(sensrng$Category[1])) to sensrng$error[2] for sensrng$Parameter[2] (tolower(sensrng$Category[2])), whereas average sensitivity among all parameters was $L1 = $ sensave.
+Within categories, sensitivity ranged from sensrngcat$Optics$error[1] (sensrngcat$Optics$Parameter[1]) to sensrngcat$Optics$error[2] (sensrngcat$Optics$Parameter[2]) for optics, sensrngcat$`Organic Matter`$error[1] (sensrngcat$`Organic Matter`$Parameter[1]) to sensrngcat$`Organic Matter`$error[2] (sensrngcat$`Organic Matter`$Parameter[2]) for organic matter, sensrngcat$Phytoplankton$error[1] (sensrngcat$Phytoplankton$Parameter[1]) to sensrngcat$Phytoplankton$error[2] (sensrngcat$Phytoplankton$Parameter[2]) for phytopankton, sensrngcat$Temperature$error[1] (sensrngcat$Temperature$Parameter[1]) to sensrngcat$Temperature$error[2] (sensrngcat$Temperature$Parameter[2]) for temperature, and sensrngcat$Zooplankton$error[1] (sensrngcat$Zooplankton$Parameter[1]) to sensrngcat$Zooplankton$error[2] (sensrngcat$Zooplankton$Parameter[2]) for zooplankton (\cref{fig:sensplo}, bottom).
+Average sensitivity values in each category were $L1 = $ sensave_cat$Optics for optics, sensave_cat$`Organic Matter` for organic matter, sensave_cat$Phytoplankton for phytoplankton, sensave_cat$Temperature for temperature, and sensave_cat$Zooplankton for zooplankton.
 Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied.
-Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ $0.12$, $0.12$), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
-Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ $0$, $0$ for groups one and two).
-
-Response of \ac{do} to parameter perturbations was not uniform across the time series.
+Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ phytogrps[1, 2], phytogrps[2, 2]), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
+Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ zoopgrps[1, 2], zoopgrps[2, 2] for groups one and two).
+%' 
+%' Response of \ac{do} to parameter perturbations was not uniform across the time series.
 \Cref{fig:sensplo} shows variation for the top parameters within each category.
@@
 As expected, parameter perturbations had the largest effect during the summer months, although the effects varied.
-An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, \textit{ZQp$_{z2}$}, which caused an increase in \ac{do}.
-The phytoplankton parameter, \textit{Qc$_{p1}$}, had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.
-The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (\textit{astar490}) and phytoplankton (\textit{Qc$_{p1}$}) parameters.
-
-\subsection{Subset identifiability}
-
-The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, sensrngcat$Zooplankton$Parameter[2], which caused an increase in \ac{do}.
+The phytoplankton parameter, sensrngcat$Phytoplankton$Parameter[2], had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.
+The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (sensrngcat$Optics$Parameter[2]) and phytoplankton (sensrngcat$Phytoplankton$Parameter[2]) parameters.
+%' 
+%' \subsection{Subset identifiability}
+%' 
+%' <<eval = F>>=
+%' data(cat_ident)
+%' data(top_ident)
+%' 
+%' # percent combos less than gamma 15, 10 by category
+%' collcatpers <- lapply(cat_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' 
+%' # percent combos less than gamma 15, 10 by top in each category
+%' colltoppers <- lapply(top_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' 
+%' maxtempcoll <- scinot(max(cat_ident$Temperature$coll))
+%' @
+%' 
+%' The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
 Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
-By category, identifiability was lowest for parameter subsets in the phytoplankton ($1.7$\% less than $\gamma = 15$, $1.2$\% less than $\gamma = 10$)  and zooplankton categories ($7.9$\%, less than $\gamma = 15$, $4.3$\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable ($NaN\times 10^{NA}$\% less than $\gamma = 15$, $NaN\times 10^{NA}$\%, less than $\gamma = 10$).
+By category, identifiability was lowest for parameter subsets in the phytoplankton (collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, collcatpers$Phytoplankton[2]\% less than $\gamma = 10$)  and zooplankton categories (collcatpers$Zooplankton[1]\%, less than $\gamma = 15$, collcatpers$Zooplankton[2]\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable (collcatpers$Temperature[1]\% less than $\gamma = 15$, collcatpers$Temperature[2]\%, less than $\gamma = 10$).
 All subset combinations for optics and organic matter parameters had $\gamma < 10$.
-All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four ($2.7$\% less than $\gamma = 15$, $1.9$\% less than $\gamma = 10$) and top five ($2.7$\% less than $\gamma = 15$, $1.9$\%, less than $\gamma = 10$) parameters.
-
-A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
+All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (colltoppers$top4[1]\% less than $\gamma = 15$, colltoppers$top4[2]\% less than $\gamma = 10$) and top five (colltoppers$top4[1]\% less than $\gamma = 15$, colltoppers$top4[2]\%, less than $\gamma = 10$) parameters.
+%' 
+%' <<eval = F>>=
+%' temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
+%' @
+%' 
+%' A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
 For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.
@@
 Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.
-Exclusion of the parameters \textit{Tref(nospA+nospZ)$_{p2}$} and \textit{Tref(nospA+nospZ)$_{p5}$} showed that $\gamma$ remained well below the 10, 15 threshold for all parameter combinations.
-Morever, inclusion of \textit{Tref(nospA+nospZ)$_{p1}$}, \textit{Tref(nospA+nospZ)$_{p4}$}, \textit{Tref(nospA+nospZ)$_{z1}$}, and \textit{Tref(nospA+nospZ)$_{z2}$} generally reduced collinearity relative to when the parameters were excluded.
+Exclusion of the parameters temp_coll[2] and temp_coll[5] showed that $\gamma$ remained well below the 10, 15 threshold for all parameter combinations.
+Morever, inclusion of temp_coll[1], temp_coll[4], temp_coll[7], and temp_coll[8] generally reduced collinearity relative to when the parameters were excluded.
 Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).
-
-Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
+%' 
+%' <<eval = F>>=
+%' data(p1z1cat_ident)
+%' data(p1z1top_ident)
+%' 
+%' # percent combos less than gamma 15, 10 by category
+%' p1z1collcatpers <- lapply(p1z1cat_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' 
+%' # percent combos less than gamma 15, 10 by top in each category
+%' p1z1colltoppers <- lapply(p1z1top_ident, function(x){
+%'   
+%'   colls <- x$coll
+%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+%'   c(l15, l10)
+%'   
+%'   })
+%' @
+%' 
+%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
 As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.
@@
 To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
-Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold ($56.3$\% less than $\gamma = 15$, $47.1$\% less than $\gamma = 10$ for Phytoplankton; $83.4$\%, less than $\gamma = 15$, $72.6$\%, less than $\gamma = 10$ for zooplankton).
+Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (p1z1collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Phytoplankton[2]\% less than $\gamma = 10$ for Phytoplankton; p1z1collcatpers$Zooplankton[1]\%, less than $\gamma = 15$, p1z1collcatpers$Zooplankton[2]\%, less than $\gamma = 10$ for zooplankton).
 Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.
-Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase ($84.2$\% less than $\gamma = 15$, $78.7$\% less than $\gamma = 10$) and a decrease ($54.4$\% less than $\gamma = 15$, $51$\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).
-
-\subsection{Parameter selection}
-
-Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
-For the first selection heuristic, all sensitive parameters from the optics ($n = $ $2$, $\gamma =$  $3.5$) and organic matter ($n = $ $3$, $\gamma =$  $10.5$) categories were selected, whereas one were selected for phytoplankton ($\gamma = $ $1$), one for temperature ($\gamma = $ $1$), and one for zooplankton ($\gamma = $ $1$).
-For the second selection heuristic, two parameters were selected ($\gamma = $ $8.5$, with a majority from the phytoplankton category, \cref{tab:identall1}).
-For the third heuristic, four parameters were selected ($\gamma = $ $12.6$) with equal representation between categories.
+Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (p1z1colltoppers$top4[1]\% less than $\gamma = 15$, p1z1colltoppers$top4[2]\% less than $\gamma = 10$) and a decrease (p1z1colltoppers$top5[1]\% less than $\gamma = 15$, p1z1colltoppers$top5[2]\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).
+%' 
+%' \subsection{Parameter selection}
+%' 
+%' <<eval = F>>=
+%' data(tocal)
+%' 
+%' # n parms and ident for each selection heuristic
+%' h1_id <- tocal$cat %>% 
+%'   split(., .$Category) %>% 
+%'   lapply(function(x){
+%'     x <- x[x$coll < 15, ]
+%'     list(nrow(x), scinot(max(x$coll), digits = 1))
+%'   }) 
+%' h2_id <- filter(tocal$top, coll < 15) %>%
+%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
+%'   .[c(2, 3)]
+%' h3_id <- filter(tocal$cattop, coll < 15) %>%
+%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
+%'   .[c(2, 3)]
+%' 
+%' # which parameter broke selection for h2, h3
+%' h2_brk <- tocal$top
+%' sel <- which(h2_brk$coll < 15)
+%' h2_brk <- h2_brk[c(sel, rev(sel)[1] + 1), ] %>% 
+%'   arrange(-coll) %>% 
+%'   .[1:2, ] %>% 
+%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
+%'   .[[2]]
+%' # which parameter broke selection for h2, h3
+%' h3_brk <- tocal$cattop
+%' sel <- which(h3_brk$coll < 15)
+%' h3_brk <- h3_brk[c(sel, rev(sel)[1] + 1), ] %>% 
+%'   arrange(-coll) %>% 
+%'   .[1:2, ] %>% 
+%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
+%'   .[[2]]
+%' @
+%' 
+%' Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
+For the first selection heuristic, all sensitive parameters from the optics ($n = $ scinot(h1_id$Optics[[1]], digits = 0), $\gamma =$  h1_id$Optics[[2]]) and organic matter ($n = $ scinot(h1_id$`Organic Matter`[[1]], digits = 0), $\gamma =$  h1_id$`Organic Matter`[[2]]) categories were selected, whereas toeng(h1_id$Phytoplankton[[1]])[[1]] were selected for phytoplankton ($\gamma = $ h1_id$Phytoplankton[[2]]), toeng(h1_id$Temperature[[1]])[[1]] for temperature ($\gamma = $ h1_id$Temperature[[2]]), and toeng(h1_id$Zooplankton[[1]])[[1]] for zooplankton ($\gamma = $ h1_id$Zooplankton[[2]]).
+For the second selection heuristic, toeng(h2_id[[1]])[[1]] parameters were selected ($\gamma = $ h2_id[[2]], with a majority from the phytoplankton category, \cref{tab:identall1}).
+For the third heuristic, toeng(h3_id[[1]])[[1]] parameters were selected ($\gamma = $ h3_id[[2]]) with equal representation between categories.
 For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.
-Selection independent of category showed that including \textit{Qc$_{p1}$} caused in increase in $\gamma$ from $8.5$ to $17.5$ and equal selection within cateogies showed that including \textit{ZQc$_{z1}$} caused in increase in $\gamma$ from $12.6$ to $72.2$.
+Selection independent of category showed that including par_txt(h2_brk[1]) caused in increase in $\gamma$ from scinot(h2_brk[3], digits = 1) to scinot(h2_brk[2], digits = 1) and equal selection within cateogies showed that including par_txt(h3_brk[1]) caused in increase in $\gamma$ from scinot(h3_brk[3], digits = 1) to scinot(h3_brk[2], digits = 1).
 Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
@@
 % optics sensitivity
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
-\begin{table}[!tbp]
-{\normalsize
-\caption{Sensitivities of \ac{do} to perturbation of optics parameters.
-Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
-Parameters that did not affect \ac{do} are not shown.\label{tab:optsens}}
-\begin{center}
-\begin{tabular}{lllll}
-\hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
-\hline
-Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.43$&$1.95$\tabularnewline
-OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.09$&$0.4$\tabularnewline
-OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$6.78\times 10^{-4}$&$0$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
 
 % organic matter sensitivity
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
-\begin{table}[!tbp]
-{\normalsize
-\caption{Sensitivities of \ac{do} to perturbation of organic matter parameters.
-Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
-Parameters that did not affect \ac{do} are not shown.\label{tab:omsens}}
-\begin{center}
-\begin{tabular}{lllll}
-\hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
-\hline
-turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.24$&$6.02$\tabularnewline
-turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.92$&$4.62$\tabularnewline
-half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.35$&$1.57$\tabularnewline
-O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.06$&$0.34$\tabularnewline
-maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$0.05$&$0.21$\tabularnewline
-NH4 rate constant for nitrification&\textit{KNH4}&$1$&$0.04$&$0.17$\tabularnewline
-decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.03$&$0.12$\tabularnewline
-half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.01$&$0.05$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
 
 % phytoplankton sensitivity
-%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
-\begin{table}[!tbp]
-{\normalsize
-\caption{Sensitivities of \ac{do} to perturbation of phytoplankton parameters.
-Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
-Parameters that did not affect \ac{do} are not shown.
-Subscripts show the phytoplankton or zooplankton group that applies for the parameter.
-Parameters less than the 75\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.\label{tab:phytosens}}
-\begin{center}
-\begin{tabular}{llll}
-\hline\hline
-\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
-\hline
-{phytoplankton carbon/cell}&&&\tabularnewline
-~~\textit{Qc$_{p1}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
-~~\textit{Qc$_{p2}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
-~~\textit{Qc$_{p3}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
-~~\textit{Qc$_{p4}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
-~~\textit{Qc$_{p5}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
-~~\textit{Qc$_{p6}$}&$1.35\times 10^{-6}$&$0.65$&$3.16$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
 
 % temperature sensitivity
-%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
-\begin{table}[!tbp]
-{\normalsize
-\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.
-Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
-Parameters that did not affect \ac{do} are not shown.
-Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}}
-\begin{center}
-\begin{tabular}{llll}
-\hline\hline
-\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
-\hline
-{optimum temperature for growth(c)}&&&\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p4}$}&$22$&$9.97\times 10^{-5}$&$1.46\times 10^{-4}$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p2}$}&$22$&$9.96\times 10^{-5}$&$1.46\times 10^{-4}$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$9.96\times 10^{-5}$&$1.46\times 10^{-4}$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p3}$}&$22$&$9.86\times 10^{-5}$&$1.45\times 10^{-4}$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p5}$}&$22$&$9.86\times 10^{-5}$&$1.45\times 10^{-4}$\tabularnewline
-~~\textit{Tref(nospA+nospZ)$_{p6}$}&$22$&$9.75\times 10^{-5}$&$1.43\times 10^{-4}$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
 
 % zooplankton sensitivity
-%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
-\begin{table}[!tbp]
-{\normalsize
-\caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.
-Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).
-Parameters that did not affect \ac{do} are not shown.
-Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:zoopsens}}
-\begin{center}
-\begin{tabular}{llll}
-\hline\hline
-\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
-\hline
-{zooplankton biomass-dependent respiration factor}&&&\tabularnewline
-~~\textit{Zrespb$_{z1}$}&$0.1$&$0$&$0.01$\tabularnewline
-~~\textit{Zrespb$_{z2}$}&$0.1$&$0$&$0.01$\tabularnewline
-\hline
-{zooplankton carbon/individual}&&&\tabularnewline
-~~\textit{ZQc$_{z1}$}&$3.13\times 10^{-4}$&$0.01$&$0.04$\tabularnewline
-~~\textit{ZQc$_{z2}$}&$3.13\times 10^{-4}$&$0.01$&$0.04$\tabularnewline
-\hline
-{zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
-~~\textit{Zm$_{z1}$}&$7.2\times 10^{-4}$&$4.95\times 10^{-4}$&$0$\tabularnewline
-~~\textit{Zm$_{z2}$}&$7.2\times 10^{-4}$&$4.95\times 10^{-4}$&$0$\tabularnewline
-\hline
-{zooplankton nitrogen/individual}&&&\tabularnewline
-~~\textit{ZQn$_{z1}$}&$6.95\times 10^{-5}$&$0$&$0.01$\tabularnewline
-~~\textit{ZQn$_{z2}$}&$6.95\times 10^{-5}$&$0$&$0.01$\tabularnewline
-\hline
-{zooplankton phosphorus/individual}&&&\tabularnewline
-~~\textit{ZQp$_{z1}$}&$3.77\times 10^{-6}$&$5.75\times 10^{-5}$&$2.66\times 10^{-4}$\tabularnewline
-~~\textit{ZQp$_{z2}$}&$3.77\times 10^{-6}$&$5.75\times 10^{-5}$&$2.66\times 10^{-4}$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
 
 % ident all states
-%latex.default(identall1, file = "", rowlabel = "Parameter description",     caption = cap_val, caption.loc = "top", size = "normalsize",     label = "tab:identall1", rowname = descrip, colheads = colnms,     rgroupTexCmd = NULL)%
-\begin{table}[!tbp]
-{\normalsize
-\caption{Parameter identifiability for dissolved oxygen.
-Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\gamma < 15$.
-Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:identall1}}
-\begin{center}
-\begin{tabular}{lllll}
-\hline\hline
-\multicolumn{1}{l}{Parameter description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
-\hline
-\footnotesize{turnover rate for OM2A and OM2G}&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.24$&$1$\tabularnewline
-\footnotesize{turnover rate for OM1A and OM1G}&\footnotesize{\textit{KG1}}&$2$\textsuperscript{OM}&$0.92$&$8.48$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
 
 % ident all states
-%latex.default(identall2, file = "", rowlabel = "State variable, parameter description",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:identall2", rgroup = unique(as.character(stts)),     n.rgroup = as.numeric(table(as.character(stts))), rowname = descrip,     colheads = colnms, rgroupTexCmd = NULL)%
-\begin{table}[!tbp]
-{\footnotesize
-\caption{Parameter identifiability for ammonium, chlorophyll, irradiance, nitrate, OM1, OM2, and phosphate.
-Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\gamma < 15$.
-Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:identall2}}
-\begin{center}
-\begin{tabular}{lllll}
-\hline\hline
-\multicolumn{1}{l}{State variable, parameter description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
-\hline
-{Ammonium}&&&&\tabularnewline
-~~\scriptsize{NH4 rate constant for nitrification}&\scriptsize{\textit{KNH4}}&$1$\textsuperscript{OM}&$0.81$&$1$\tabularnewline
-\hline
-{Chlorophyll}&&&&\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p5}$}}&$1$\textsuperscript{P}&$0.08$&$1$\tabularnewline
-\hline
-{Irradiance}&&&&\tabularnewline
-~~\scriptsize{OMA specific absorption at 490 nm}&\scriptsize{\textit{astarOMA}}&$1$\textsuperscript{O}&$5.86\times 10^{14}$&$1$\tabularnewline
-~~\scriptsize{decay rate of CDOM, 1/day}&\scriptsize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$2.66\times 10^{14}$&$3.92$\tabularnewline
-\hline
-{Nitrate}&&&&\tabularnewline
-~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$1$\textsuperscript{OM}&$0.85$&$1$\tabularnewline
-\hline
-{OM1}&&&&\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$3.5$\textsuperscript{P}&$43.06$&$1$\tabularnewline
-\hline
-{OM2}&&&&\tabularnewline
-~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$35.62$&$1$\tabularnewline
-~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$3.5$\textsuperscript{P}&$33.53$&$10.36$\tabularnewline
-\hline
-{Phosphate}&&&&\tabularnewline
-~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$1$\textsuperscript{OM}&$0.21$&$1$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-
-\end{table}
 
@@
 % sensitivity example of top
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\maxwidth]{figs/sensplo-1}
-
-}
-
-\caption{Sensitivity of \ac{do} to parameter changes.
-The solid lines show the change in \ac{do} based on a 50\% change from the default parameter values (dashed line) for each parameter.
-Individual parameters with the largest effect are shown for each category.
-The top plot shows the model output and the middle plot shows the estimated \ac{do} as a difference from the default.
-The bottom plot shows the distribution of error values (as $log\left(L1\right)$) for all parmaters in each category.}\label{fig:sensplo}
-\end{figure}
 
 % identifiability boxplots
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\maxwidth]{figs/identbox-1}
-
-}
-
-\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.
-Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
-The phytoplankton category is limited to 25 total parameters.}\label{fig:identbox}
-\end{figure}
 
 % parameter exclusion temp
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=0.6\textwidth]{figs/excltemp-1}
-
-}
-
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of temperature parameters for subset combinations in \cref{fig:identbox}.
-Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
-Identifiability of including all seven parameters is in \cref{fig:identbox}.
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:excltemp}
-\end{figure}
 
 % identifiability boxplot, p1, z1 only
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=0.5\textwidth]{figs/p1z1identbox-1}
-
-}
-
-\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
-Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.}\label{fig:p1z1identbox}
-\end{figure}
 
 % heuristic plots o2
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/heurist-1}
-
-}
-
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters with three different heuristics.
-Parameters are selected by decreasing sensitivity for all examples (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
-The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c).
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.
-See \cref{tab:identall1} for values in (b).}\label{fig:heurist}
-\end{figure}
 
 % heuristic plots, all state
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/heurist_stts-1}
-
-}
-
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables.
-Parameters are selected by decreasing sensitivity indepent of parameter categories.
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$.
-See \cref{tab:identall2} for values.}\label{fig:heurist_stts}
-\end{figure}
 
@@
 
-\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
-Values are truncated by the 5\textsuperscript{th} and 95\textsuperscript{th} sensitivity values between all parameters for visual appearance.
-Parameters are grouped by category (plot strips).
-Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1-p6, z1, z2), respectively.}\label{fig:sensalltile}
+\caption[Sensitivity values (L1, \cref{l1}) for local analyses of all state variables]{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
+Values are in log-space for visual comparison.
+Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.}\label{fig:sensalltile}
 \end{figure}

### 2016-08-23 R/funcs.R

@@ -887,7 +887,8 @@ parcats2 <- function(as_df = FALSE){
 #
 # parin chr vector of short names to convert
 # frm chr string indicating format of output, tex or exp for latex or expression
-par_txt <- function(parin, frm = 'tex'){
+# p1z1 logical indicating if subscripts for multiple phyto/zoop groups are removed
+par_txt <- function(parin, frm = 'tex', p1z1 = TRUE){
 
   library(dplyr)
   
@@ -947,6 +948,9 @@ par_txt <- function(parin, frm = 'tex'){
   t %>% 
   data.frame(., stringsAsFactors = FALSE) %>% 
   .$shrt
+
+  # remove subscripts if p1z1
+  if(p1z1) subs <- gsub('_p[1-6]$|_z[1-1]$', '', subs)
 
   # convert output format for tex
   if(frm == 'tex'){

### 2016-08-24 ident_manu.Rnw
methods should reflect p1z1, added obser uncert info

@@
 The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
-Initial screening removed 73 irrelevant parameters that were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
 
 <<echo = FALSE>>=
-# remove irrelevant parameters, from 'ignore/noparams.csv'
+pars <- parcats2(as_df = TRUE)$shrt %>% 
+  as.character
 rmpars <- c('Kw_1', 'Kcdom_1', 'Kspm_1', 'Kchla_1', 'aw490_1', 'astarOMR_1', 'astarOMBC_1', 'KTg1(nospA+nospZ)_1', 'KTg1(nospA+nospZ)_2', 'KTg1(nospA+nospZ)_3', 'KTg1(nospA+nospZ)_4', 'KTg1(nospA+nospZ)_5', 'KTg1(nospA+nospZ)_6', 'KTg1(nospA+nospZ)_7', 'KTg1(nospA+nospZ)_8', 'KTg2(nospA+nospZ)_1', 'KTg2(nospA+nospZ)_2', 'KTg2(nospA+nospZ)_3', 'KTg2(nospA+nospZ)_4', 'KTg2(nospA+nospZ)_5', 'KTg2(nospA+nospZ)_6', 'KTg2(nospA+nospZ)_7', 'KTg2(nospA+nospZ)_8', 'Ea_R(nospA+nospZ)_1', 'Ea_R(nospA+nospZ)_2', 'Ea_R(nospA+nospZ)_3', 'Ea_R(nospA+nospZ)_4', 'Ea_R(nospA+nospZ)_5', 'Ea_R(nospA+nospZ)_6', 'Ea_R(nospA+nospZ)_7', 'Ea_R(nospA+nospZ)_8', 'beta_1', 'beta_2', 'beta_3', 'beta_4', 'beta_5', 'beta_6', 'QmaxN_1', 'QmaxN_2', 'QmaxN_3', 'QmaxN_4', 'QmaxN_5', 'QmaxN_6', 'QmaxP_1', 'QmaxP_2', 'QmaxP_3', 'QmaxP_4', 'QmaxP_5', 'QmaxP_6', 'nfQs_1', 'nfQs_2', 'nfQs_3', 'nfQs_4', 'nfQs_5', 'nfQs_6', 'KG1_R_1', 'KG2_R_1', 'KG1_BC_1', 'KG2_BC_1', 'pCO2_1', 'stoich_x1R_1', 'stoich_y1R_1', 'stoich_x2R_1', 'stoich_y2R_1', 'stoich_x1BC_1', 'stoich_y1BC_1', 'stoich_x2BC_1', 'stoich_y2BC_1', 'sink OM1_R_1', 'sink OM2_R_1', 'sink OM1_BC_1', 'sink OM2_BC_1', 'CF_SPM_1')
+rmpars <- c(rmpars, 'respb_7') # there's an extra of this one
+pars <- pars[!pars %in% rmpars]
+p1z1pars <- grep('_1$|_7$', pars, value = TRUE) # get parameters for one phyto, one zoop (_7 is for temp)
 
@@
   filter(!shrt %in% rmpars) %>% 
+  filter(grepl('_1$|_7$', shrt)) %>% 
   .$cats %>% 
@@
   as.list
-@
-
-As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize greater complexity in community structure and foodweb dynamics.
-However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc..
+
+@
+
+Irrelevant parameters were removed for several reasons from the analysis.
+Parameters that were removed were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
+Additionally, FishTank includes six phytoplankton and two zooplankton groups to describe complexity in community structure and foodweb dynamics.
+However, structural equations for each group do not vary considerably such that variation in parameter values primarily controls differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
 Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
-To remove obvious redundancies in the model, the sensitivity analyes were conducted using only one phytoplankton and one zooplankton group.
-This further reduced the parameter set....
-For simplicity, the remaining parameters were grouped in  to one of six categories based on their respective equations: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
-A full description is available as an appendix in \citepalias{LehrterIR}.
+To remove obvious redundancies in the model, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
+The final parameter set that was evaluated included \Sexpr{length(p1z1pars)} parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
+A full description of the model parameters is available as an appendix in \citetalias{LehrterIR}.
 
@@
 The analysis focused on sensitivity of \ac{do} in the \ac{zerod} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
-A local sensitivity analysis was performed for each of the 178 parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
+A local sensitivity analysis was performed for each of the parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
 The analyses relied exlusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10}.
@@
 \noindent where the estimate depended on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
-The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y_i$, were set as the default value of the unperturbed parameter and the initial value of $y$ at time $= 0$ \citep{Soetaert10}.
-The scaling ensures the estimates are unitless such that the relative magnitudes provide a comparison for model sensitivity to parameter changes and state variables that differ in scale.
+The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y_i$, were set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
+The scaling ensures the estimates are unitless such that the relative magnitudes allows comparisons of model sensitivity to parameter changes and state variables that differ in scale.
 Estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain individual sensitivity values of \ac{do} in response to a change in parame ter $j$:
@@
 
-Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 178 evaluated for the FishTank model.
+Initial analyses suggested that considerably limited subsets of parameters were identifiable of the \Sexpr{length(p1z1pars)} evaluated for the FishTank model.
 Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
@@
 These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability).
-Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences given questions of interest.
+Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences by model users given questions of interest.
 In all selection scenarios, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
@@
 \item independent of parameter category,
-\item or considering all categories equally
-\end{inparaenum}.  The selection rules produced seven subsets of parameters that could further be used to optimize model calibration for \ac{do}.
+\item or considering all categories equally.
+\end{inparaenum} The selection rules produced eight subsets of parameters that could further be used to optimize model calibration for \ac{do}.
 
@@
 
-\subsection{Identifiability and structural uncertainty}
-
-As a final analysis, the effects of model structure on parameter identifiability were evaluated for \ac{do} predictions.
-The FishTank model includes several processes that can be included or excluded from the equations based on expected conditions or available data.
-These `switches' are conceptually different from model parameters as they define the use of explicit equations or processes that affect the model structure.
-As such, a comparison of sensitivity and identifiability given different equations uses parameter uncertainty as a means to begin addressing componenents of structural uncertainty.
+\subsection{Observational and structural uncertainty}
+
+As a final analysis, the effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.
+These analyses used changes in parameter uncertainty and identifiability to infer the effects of observational and structural uncertainty on model output to create a more comprehensive evaluation.
+First, observational uncertainty was evaluated by varying the initial conditions supplied to the model.
+The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
+For example, the sensitivity of \ac{do} to variation in the half-saturation constants (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
+Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting .
+Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.
+
+The effects of model structure on parameter identifiability were evaluated by including or excluding specific components of the model.
+The FishTank model includes several processes that are based on expected conditions or available data.
+These `switches' are conceptually different from model parameters as they define the use of explicit equations or processes included in the model structure.
+As such, a comparison of sensitivity and identifiability given different equations uses parameter uncertainty to begin addressing componenents of structural uncertainty.
 Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).
@@
 <<sensalltile, eval = T, echo = F, fig.height = 7, fig.width = 6, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
-Values are in log-space for visual comparison.
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.'>>=

### 2016-08-24 ident_manu.tex
methods should reflect p1z1, added obser uncert info

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Aug 22 16:13:24 2016 -0500
+  \\ Version Date:   Tue Aug 23 17:18:33 2016 -0500
 	}
@@
 The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
-Initial screening removed 73 irrelevant parameters that were removed for several reasons, e.g., a parameter was only relevant for the hydrodynamic model, was considered a physical constant, or had no effect given initial conditions.
 
-As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize greater complexity in community structure and foodweb dynamics.
-However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc..
+Irrelevant parameters were removed for several reasons from the analysis.
+Parameters that were removed were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
+Additionally, FishTank includes six phytoplankton and two zooplankton groups to describe complexity in community structure and foodweb dynamics.
+However, structural equations for each group do not vary considerably such that variation in parameter values primarily controls differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
 Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
-To remove obvious redundancies in the model, the sensitivity analyes were conducted using only one phytoplankton and one zooplankton group.
-This further reduced the parameter set....
-For simplicity, the remaining parameters were grouped in  to one of six categories based on their respective equations: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (132), temperature (8), and zooplankton (22).
-A full description is available as an appendix in \citepalias{LehrterIR}.
+To remove obvious redundancies in the model, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
+The final parameter set that was evaluated included 51 parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (22), temperature (2), and zooplankton (11).
+A full description of the model parameters is available as an appendix in \citetalias{LehrterIR}.
 
@@
 
-Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 178 evaluated for the FishTank model.
+Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 51 evaluated for the FishTank model.
 Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
@@
 
-\subsection{Identifiability and structural uncertainty}
+\subsection{Observational and structural uncertainty}
 
-As a final analysis, the effects of model structure on parameter identifiability were evaluated for \ac{do} predictions.
-The FishTank model includes several processes that can be included or excluded from the equations based on expected conditions or available data.
-These `switches' are conceptually different from model parameters as they define the use of explicit equations or processes that affect the model structure.
-As such, a comparison of sensitivity and identifiability given different equations uses parameter uncertainty as a means to begin addressing componenents of structural uncertainty.
+As a final analysis, the effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.
+These analyses used changes in parameter uncertainty and identifiability to infer the effects of observational and structural uncertainty on model output to create a more comprehensive evaluation.
+First, observational uncertainty was evaluated by varying the initial conditions supplied to the model.
+The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
+For example, the sensitivity of \ac{do} to variation in the half-saturation constants (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
+Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on the limiting nutrient .
+Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values estimated from the observed data.
+
+The effects of model structure on parameter identifiability were evaluated by including or excluding specific components of the model.
+The FishTank model includes several processes that are based on expected conditions or available data.
+These `switches' are conceptually different from model parameters as they define the use of explicit equations or processes included in the model structure.
+As such, a comparison of sensitivity and identifiability given different equations uses parameter uncertainty to begin addressing componenents of structural uncertainty.
 Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).
@@
 \caption[Sensitivity values (L1, \cref{l1}) for local analyses of all state variables]{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
-Values are in log-space for visual comparison.
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.}\label{fig:sensalltile}

### 2016-08-24 ident_manu.Rnw
table 1 do sens all cats added

@@
 The scaling ensures the estimates are unitless such that the relative magnitudes allows comparisons of model sensitivity to parameter changes and state variables that differ in scale.
-Estimates for $S_{ij}$ were summarized as $L1$ and $L2$ across the time series to obtain individual sensitivity values of \ac{do} in response to a change in parame ter $j$:
+Estimates for $S_{ij}$ were summarized as $L1$ to obtain individual sensitivity values of \ac{do} in response to a change in parame ter $j$:
 
@@
 \end{equation}
-\begin{equation} \label{l2}
-L2 = \sqrt{\sum\left(S_{ij}^2\right)|/n}
-\end{equation}
 
@@
 Time series of \ac{do} estimates before and after perturbation were also evaluated to identify patterns not captured by the summary statistics.
-All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ or $L2$ were retained for identifiability analysis.
+All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ were retained for identifiability analysis.
 
@@
 For example, the sensitivity of \ac{do} to variation in the half-saturation constants (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
-Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting .
+Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.
 Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.
@@
 
-% optics sensitivity
-<<optsens, eval = F, cache = F>>=
-senstab1('Optics', 'optsens')
-@
-
-% organic matter sensitivity
-<<omsens, eval = F, cache = F>>=
-senstab1('Organic Matter', 'omsens')
-@
-
-% phytoplankton sensitivity
-<<phytosens, eval = F, cache = F>>=
-# data(sens_ests_cat)
-# tmp <- filter(sens_ests_cat, Category == 'Phytoplankton')
-# quantile(tmp$error)
-senstab2('Phytoplankton', 'phytosens', sub = 0.59, sub.txt = 'Parameters less than the 75\\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.')
-@
-
-% temperature sensitivity
-<<tempsens, eval = F, cache = F >>=
-senstab2('Temperature', 'tempsens')
-@
-
-% zooplankton sensitivity
-<<zoopsens, eval = F, cache = F>>=
-senstab2('Zooplankton', 'zoopsens')
+<<dosens, eval = T, cache = F>>=
+load(file = 'data/sens_ests_cat_all.RData')
+load(file = 'data/sens_ests_all.RData')
+
+# subset the sensitivy and sensitivity catgory lists
+tmpest <- sens_ests_all[['O2']]
+tmpest_cat <- sens_ests_cat_all[['O2']]
+
+labs <- parcats2(as_df = TRUE) %>% 
+  rename(Parameter = shrt)
+
+totab <- tmpest_cat %>% 
+  select(Parameter) %>% 
+  left_join(., tmpest$sens, by = 'Parameter') %>% 
+  left_join(., labs, by = 'Parameter') %>% 
+  select(cats, lngs, Parameter, vals, L1) %>% 
+  arrange(cats, -L1) %>% 
+  mutate(
+    Parameter = par_txt(Parameter),
+    lngs = gsub('^.*:\\s', '', lngs), 
+    lngs = gsub('_', '', lngs), 
+    vals = sapply(vals, scinot),
+    L1 = sapply(L1, scinot, digits = 2, pow = 2)
+  ) %>% 
+  rename(
+    Description = lngs, 
+    Value = vals
+  )
+
+# final table formatting
+Description <- totab$Description
+cats <- totab$cats
+totab <- totab[,-c(1:2)]
+
+cap.val<- paste('Sensitivities of \\ac{do} to perturbation of indivividual parameters.
+Sensitivities are based on a 50\\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \\cref{l1}).
+Parameters that did not affect \\ac{do} are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.')
+
+latex( 
+  totab,
+  file = '',
+  rowlabel = 'Description',
+  caption = cap.val,
+  caption.loc = 'top',
+  rowname = Description,
+  rgroup = unique(cats),
+  n.rgroup = as.numeric(table(cats)),
+  size = 'footnotesize',
+  label = 'tab:dosens'
+  )
 @
@@
 <<sensalltile, eval = T, echo = F, fig.height = 7, fig.width = 6, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
-Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.'>>=
+Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
+See \\cref{tab:dosens} for L1 values for \\ac{do}.'>>=
 data(sens_ests_cat_all)

### 2016-08-24 ident_manu.tex
table 1 do sens all cats added

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Aug 23 17:18:33 2016 -0500
+  \\ Version Date:   Wed Aug 24 10:41:50 2016 -0500
 	}
@@
 L1 = \sum|S_{ij}|/n
-\end{equation}
-\begin{equation} \label{l2}
-L2 = \sqrt{\sum\left(S_{ij}^2\right)|/n}
 \end{equation}
@@
 For example, the sensitivity of \ac{do} to variation in the half-saturation constants (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
-Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on the limiting nutrient .
-Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values estimated from the observed data.
+Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.
+Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.
 
@@
 
-% optics sensitivity
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = "footnotesize",     label = "tab:dosens")%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivities of \ac{do} to perturbation of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect \ac{do} are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$6.27\times 10^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$3.22\times 10^{-4}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.35\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$1.8\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.71$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.03$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$0.03$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.03$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.01$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.01$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.01$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$7.44\times 10^{-3}$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$5.34\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.56\times 10^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$1.3\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.59\times 10^{-4}$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$7.63\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$4.51\times 10^{-3}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$1.97\times 10^{-3}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.47\times 10^{-4}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$4.61\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$2.89\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.05$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.01$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$7.53\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$6.49\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$6.36\times 10^{-3}$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$8\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.9\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$2.44\times 10^{-4}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
 
-% organic matter sensitivity
-
-% phytoplankton sensitivity
-
-% temperature sensitivity
-
-% zooplankton sensitivity
+\end{table}
 
@@
 
-\caption[Sensitivity values (L1, \cref{l1}) for local analyses of all state variables]{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
-Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.}\label{fig:sensalltile}
+\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
+Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
+See \cref{tab:dosens} for L1 values for \ac{do}.}\label{fig:sensalltile}
 \end{figure}

### 2016-08-24 ident_manu.Rnw
senstab1 senstab2 gone, senstab now all cats by state var

@@
 
+% do sensitivity all categories
 <<dosens, eval = T, cache = F>>=
-load(file = 'data/sens_ests_cat_all.RData')
-load(file = 'data/sens_ests_all.RData')
-
-# subset the sensitivy and sensitivity catgory lists
-tmpest <- sens_ests_all[['O2']]
-tmpest_cat <- sens_ests_cat_all[['O2']]
-
-labs <- parcats2(as_df = TRUE) %>% 
-  rename(Parameter = shrt)
-
-totab <- tmpest_cat %>% 
-  select(Parameter) %>% 
-  left_join(., tmpest$sens, by = 'Parameter') %>% 
-  left_join(., labs, by = 'Parameter') %>% 
-  select(cats, lngs, Parameter, vals, L1) %>% 
-  arrange(cats, -L1) %>% 
-  mutate(
-    Parameter = par_txt(Parameter),
-    lngs = gsub('^.*:\\s', '', lngs), 
-    lngs = gsub('_', '', lngs), 
-    vals = sapply(vals, scinot),
-    L1 = sapply(L1, scinot, digits = 2, pow = 2)
-  ) %>% 
-  rename(
-    Description = lngs, 
-    Value = vals
-  )
-
-# final table formatting
-Description <- totab$Description
-cats <- totab$cats
-totab <- totab[,-c(1:2)]
-
-cap.val<- paste('Sensitivities of \\ac{do} to perturbation of indivividual parameters.
-Sensitivities are based on a 50\\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \\cref{l1}).
-Parameters that did not affect \\ac{do} are not shown.
-Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.')
-
-latex( 
-  totab,
-  file = '',
-  rowlabel = 'Description',
-  caption = cap.val,
-  caption.loc = 'top',
-  rowname = Description,
-  rgroup = unique(cats),
-  n.rgroup = as.numeric(table(cats)),
-  size = 'footnotesize',
-  label = 'tab:dosens'
-  )
+senstab(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', digits = 2, pow = 2, tabsize = 'footnotesize')
 @

### 2016-08-24 ident_manu.tex
senstab1 senstab2 gone, senstab now all cats by state var

--- 2016-08-24 ident_manu.tex
@@
   \vspace{1in} 
-  \\ Version Date:   Tue Aug 23 17:18:33 2016 -0500
+  \\ Version Date:   Wed Aug 24 11:39:30 2016 -0500
 	}
@@
 
-% optics sensitivity
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivities of \ac{do} to perturbation of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect \ac{do} are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.94\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.92$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$102.96$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$18.21$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$1.62$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$1.2$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.95$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.35$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.16$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.1$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.09$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.09$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$8.86\times 10^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$3.49\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.09\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.87\times 10^{-3}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$1.1\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.72\times 10^{-4}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.21\times 10^{-4}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$2.19\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.9$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.53$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.15$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.11$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.02$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$5.27\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$3.67\times 10^{-6}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$1.75\times 10^{-6}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
 
-% organic matter sensitivity
-
-% phytoplankton sensitivity
-
-% temperature sensitivity
-
-% zooplankton sensitivity
+\end{table}
 

### 2016-08-24 R/funcs.R

@@ -40,7 +40,7 @@ form_fun <- function(x, rnd_val = 2, dig_val = 2, nsm_val = 2, ...) {
 # digits numeric for rounding
 # showdollar logical if output is enclosed in dollar for latex
 # from https://dankelley.github.io/r/2015/03/22/scinot.html
-scinot <- function(x, pow = 3, digits=2, showDollar=TRUE)
+scinot <- function(x, pow = 3, digits = 2, showDollar = TRUE)
 {
   x <- as.numeric(x)
   sign <- ""
@@ -976,43 +976,50 @@ par_txt <- function(parin, frm = 'tex', p1z1 = TRUE){
 
 ######
 # function for sensitivity tables, no phyto, zoop groupings
-senstab1 <- function(categ, tablab, tabsize = 'normalsize'){
-  
+senstab <- function(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', tabsize = 'normalsize', pow = 3, digits = 2){
+
   library(Hmisc)
   library(dplyr)
   library(tidyr)
   
-  load(file = 'data/sens_ests_cat.RData')
-  load(file = 'data/sens_ests.RData')
+  load(file = 'data/sens_ests_cat_all.RData')
+  load(file = 'data/sens_ests_all.RData')
   
-  labs <- parcats2()[[categ]] %>% 
-    data.frame %>% 
-    rename(Parameter = shrt)
+  # subset the sensitivy and sensitivity catgory lists
+  tmpest <- sens_ests_all[[out_var]]$sens
+  tmpest$Parameter <- as.character(tmpest$Parameter)
+  tmpest_cat <- sens_ests_cat_all[[out_var]]
   
-  totab <- filter(sens_ests_cat, Category %in% categ) %>% 
+  labs <- parcats2(as_df = TRUE) %>% 
+    rename(Parameter = shrt) %>% 
+    mutate(Parameter = as.character(Parameter))
+
+  totab <- tmpest_cat %>% 
     select(Parameter) %>% 
-    left_join(., sens_ests$sens, by = 'Parameter') %>% 
+    mutate(Parameter = as.character(Parameter)) %>% 
+    left_join(., tmpest, by = 'Parameter') %>% 
     left_join(., labs, by = 'Parameter') %>% 
-    select(lngs, Parameter, vals, L1, L2) %>% 
-    arrange(-L1) %>% 
+    select(cats, lngs, Parameter, vals, L1) %>% 
[…]

### 2016-08-30 ident_manu.Rnw
updating figures tables

@@
 source('R/funcs.r')
-library(WRTDStidal)
 library(tidyr)
@@
 As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.
-The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
 
@@
 
-Irrelevant parameters were removed for several reasons from the analysis.
-Parameters that were removed were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
+The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
+Irrelevant parameters were removed for several reasons; parameters were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
 Additionally, FishTank includes six phytoplankton and two zooplankton groups to describe complexity in community structure and foodweb dynamics.
-However, structural equations for each group do not vary considerably such that variation in parameter values primarily controls differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
+However, structural equations for each group are identical such that chosen parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
 Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
@@
 A local sensitivity analysis was performed for each of the parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
-The analyses relied exlusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10}.
-Each parameter was perturbed by 50\% of its original value and the model was executed to obtain an estimate of the effect on \ac{do}.
+The analyses relied exclusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10,RDCT16}.
+Each parameter was perturbed by 50\% of its original value and the model was executed to obtain an estimate of the change in \ac{do}.
 For each perturbation, a sensitivity value $S$ was estimated for each time step $i$ given a set value for parameter $j$ as:
@@
 The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y_i$, were set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
-The scaling ensures the estimates are unitless such that the relative magnitudes allows comparisons of model sensitivity to parameter changes and state variables that differ in scale.
-Estimates for $S_{ij}$ were summarized as $L1$ to obtain individual sensitivity values of \ac{do} in response to a change in parame ter $j$:
+The scaling ensures the estimates are unitless such that the relative magnitudes allow comparisons of model sensitivity to parameters and state variables that differ in scale.
+Sensitivity values for all $j$ parameters were summarized across the time series from $i = 1$ to $n$ as $L1$:
 
@@
 
-In general, positive sensitivity estimates suggested a parameter had a positive effect on \ac{do} for a given increase in the parameter, whereas the converse was true for negative sensitivity estimates.
-However, the effect of a parameter change may not be uniform over time such that $S_{ij}$ can change in magnitude and sign depending on the temporal location.
-Time series of \ac{do} estimates before and after perturbation were also evaluated to identify patterns not captured by the summary statistics.
 All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ were retained for identifiability analysis.
@@
 \item or considering all categories equally.
-\end{inparaenum} The selection rules produced eight subsets of parameters that could further be used to optimize model calibration for \ac{do}.
-
-The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
-In addition to \ac{do}, other state variables included \ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
-Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
+\end{inparaenum} The selection rules produced seven subsets of parameters that could further be used to optimize model calibration for \ac{do}.
 
@@
 
-As a final analysis, the effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.
+The effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.
 These analyses used changes in parameter uncertainty and identifiability to infer the effects of observational and structural uncertainty on model output to create a more comprehensive evaluation.
@@
 The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
-For example, the sensitivity of \ac{do} to variation in the half-saturation constants (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
+For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplnakton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
 Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.
 Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.
-
-The effects of model structure on parameter identifiability were evaluated by including or excluding specific components of the model.
+Initial conditions were also changed to test the effects of different limiting nutrients by setting nitrogen and phosphorus values above or below concentrations defined by the standard Redfield ratio.
+
+The effects of model structure on parameter sensitivity and identifiability were evaluated by including or excluding specific components of the model.
 The FishTank model includes several processes that are based on expected conditions or available data.
@@
 Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIR}.
-Parameter identifiability was evaluated using three scenarios of simple, intermediate, and complex combinations of model switches.
+For simplicity, parameter identifiability was evaluated using three scenarios of simple, intermediate, and complex combinations of model switches.
+
+The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
+In addition to \ac{do}, other state variables included \ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
+Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
 
@@
 
-% sensitivity example of top
-<<sensplo, eval = F, fig.cap = 'Sensitivity of \\ac{do} to parameter changes.
-The solid lines show the change in \\ac{do} based on a 50\\% change from the default parameter values (dashed line) for each parameter.
-Individual parameters with the largest effect are shown for each category.
-The top plot shows the model output and the middle plot shows the estimated \\ac{do} as a difference from the default.
-The bottom plot shows the distribution of error values (as $log\\left(L1\\right)$) for all parmaters in each category.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE>>=
-load(file = 'data/sens_ests.RData')
-load(file = 'data/sens_ests_cat.RData')
-
-toeval <- group_by(sens_ests_cat, Category) %>% 
-  filter(error == max(error)) %>% 
-  arrange(error) %>% 
-  data.frame
-
-toeval <- toeval$Parameter %>% 
-  as.character
-
-# for top sens plots
-toplo <- filter(sens_ests$raw, Parameter %in% toeval) %>% 
-  mutate(
-    diffest = Estimate - default,
-    time = as.POSIXct(time, origin = as.POSIXct('2002-01-01 0:0', tz = "GMT"), tz = 'GMT'),
-    time = as.Date(time), 
-    Parameter = factor(Parameter, levels = c('astar490_1', 'k11_1', 'Qc_1', 'Tref(nospA+nospZ)_4', 'ZKa_1'))
-  )
-
-# for all L1 boxplots
-toplo2 <- mutate(sens_ests_cat,
-  Category = factor(Category, 
-    levels = c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
-    ), 
-  Parameter = as.character(Parameter)
-  ) %>% 
-  group_by(Category) %>% 
-  mutate(
-    tops = ifelse(error == max(error), Parameter, NA)
-  )
-
-ylab <- expression(paste(O[2], ' (mmol ', m^-3, ')'))
-colset <- 'Set2'
-lnsz <- 1
-alph <- 0.8
-
-leglabs <- list(
-  expression(atop('Optics', italic(astar490))),
-  expression(atop('Organic Matter', italic('k11'))),
-  expression(atop('Phytoplankton', italic(Qc[italic('p1')]))),
-  expression(atop('Temperature', italic(Tref(nospA+nospZ)[italic('p4')]))),
-  expression(atop('Zooplankton', italic(Zka[italic('z1')])))
-  )
-
-p1 <- ggplot(toplo, aes(x = time, y = Estimate, group = Parameter, colour = Parameter)) + 
-  geom_line(aes(y = default), colour = 'black', linetype = 'dashed') + 
-  geom_line(size = lnsz, alpha = alph) + 
-  theme_minimal() +
-  scale_colour_brewer(palette = colset, 
-    labels = leglabs
-    ) + 
-  scale_y_continuous(ylab) + 
-  theme(
-    legend.position = 'top',
-    axis.text.x = element_blank(), 
-    axis.title.x = element_blank(),
-    axis.line.x = element_line(), 
-    axis.line.y = element_line()
-    )
-
-p2 <- ggplot(toplo, aes(x = time, y = diffest, group = Parameter, colour = Parameter)) + 
-  geom_hline(yintercept = 0, linetype = 'dashed') +
-  geom_line(size = lnsz, alpha = alph) + 
-  theme_minimal() +
-  scale_colour_brewer(palette = colset) + 
-  scale_y_continuous('Difference') + 
-  theme(
-    legend.position = 'none',
-    axis.title.x = element_blank(),
-    axis.line.x = element_line(), 
-    axis.line.y = element_line()
-    )
-
-p3 <- ggplot(toplo2, aes(x = Category, y = log(error), fill = Category)) + 
-  geom_boxplot() +
-  theme_minimal() +
-  scale_fill_brewer(palette = colset) + 
-  scale_y_continuous(expression(paste('log(', italic('L1'), ')'))) + 
-  theme(
-    legend.position = 'none',
-    axis.title.x = element_blank(),
-    axis.line.x = element_line(), 
-    axis.line.y = element_line()
-    )
-
-# align widths of plots in first column, first two
-pA <- ggplot_gtable(ggplot_build(p1))
-pB <- ggplot_gtable(ggplot_build(p2))
-pC <- ggplot_gtable(ggplot_build(p3))
-maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3], pC$widths[2:3])
-
-# Set the widths
-pA$widths[2:3] <- maxWidth
-pB$widths[2:3] <- maxWidth
-pC$widths[2:3] <- maxWidth
-
-grid.arrange(pA, pB, pC, ncol = 1, heights = c(1, 0.85, 0.85))
-@
-
-% identifiability boxplots
-<<identbox, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
-Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
-The phytoplankton category is limited to 25 total parameters.', fig.height = 8, fig.width = 8, echo = F, cache = TRUE>>=
-# identifiability by category (all parameters with >0 L1) 
-data(cat_ident)
-data(top_ident)
-
-colset <- 'Set2'
-
-toplo <- cat_ident %>% 
-  lapply(., function(x) dplyr::select(x, N, coll)) %>% 
-  reshape2::melt(., id.var = c('N', 'coll')) %>% 
-  rename(Category = L1) %>% 
-  mutate(Category = factor(Category, 
-    levels = c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton'),
-    labels = c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
-    )) %>% 
-  filter(N <= 25) %>% # reduced for plot space
-  group_by(N, Category) %>% 
-  summarise(
-    ave = mean(coll), 
-    med = median(coll),
-    min = min(coll), 
-    max = max(coll)
-  )
-
-p1 <- ggplot(toplo, aes(x = N, group = N)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
-  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
-  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
-  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
-  theme_minimal() + 
-  theme(
-    axis.line.x = element_line(), 
-    axis.line.y = element_line(), 
-    axis.title.x = element_blank(), 
-    axis.title.y = element_blank()
-  ) + 
-  theme(legend.position = 'none') + 
-  ggtitle('(a) By parameter category')
-
-# identifiability top 1, 2, 3, 4, 5 all categories combined
-toplo2 <-  reshape2::melt(top_ident, id.var = c('N', 'coll')) %>% 
-  select(N, coll, L1) %>% 
-  mutate(L1 = factor(L1, levels = paste0('top', 1:5), labels = paste0('Top ', 1:5))) %>% 
-  rename(npercat = L1) %>% 
-  group_by(N, npercat) %>% 
-  summarise(
-    ave = mean(coll), 
-    med = median(coll),
-    min = min(coll), 
-    max = max(coll)
-  )
-
-p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
-  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
-  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
-  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
-  theme_minimal() + 
-  theme(
-    axis.line.x = element_line(), 
-    axis.line.y = element_line(), 
-    axis.title.x = element_blank(), 
-    axis.title.y = element_blank(), 
-    legend.title = element_blank()
-  ) + 
-  ggtitle('(b) By top parameters, all categories')
-
-pleg <- g_legend(p2)
-p2 <- p2 + theme(legend.position = 'none')
-
-grid.arrange(
-  arrangeGrob(p1, p2, ncol = 2),
-  left = 'Identifiability', 
-  bottom = 'Parameters in set',
-  pleg, ncol = 2, widths = c(1, 0.1)
-)
-@
-
-% parameter exclusion temp
-<<excltemp, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of temperature parameters for subset combinations in \\cref{fig:identbox}.
-Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
-Identifiability of including all seven parameters is in \\cref{fig:identbox}.
-Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 8, fig.width = 5, echo = F, cache = TRUE, out.width = "0.6\\textwidth">>=
-data(cat_ident)
-
-toplo <- cat_ident$`Temperature` %>% 
-  gather('parm', 'inc', -N, -coll) %>% 
-  ungroup %>% 
-  filter(N < max(N)) %>% 
-  mutate(
-    parm = as.character(par_txt(parm, frm = 'exp')),
-    N = factor(N), 
-    inc = factor(inc, levels = c(0, 1), labels = c('excluded', 'included'))
-    )
-
-ggplot(toplo, aes(x = N, y = coll, fill = inc)) + 
-  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
-  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
-  geom_boxplot(outlier.size = 0.5, size = 0.5) + 
-  facet_wrap(~parm, label = label_parsed, ncol = 2) + 
-  theme_minimal() + 
-  scale_fill_brewer(palette = 'Greys') + 
-  scale_y_continuous('Identifiability') +
-  scale_x_discrete('Parameters in set') + 
-  theme(
-    legend.title = element_blank(),
-    axis.line.x = element_line(),
-    axis.line.y = element_line(),
-    panel.grid.minor = element_blank(), 
-    panel.grid.major = element_blank(), 
-    legend.position = c(0.8, 0.1)
-  )
-
-@
-
-% identifiability boxplot, p1, z1 only
-<<p1z1identbox, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do} using only subsets from the first phytoplankon group and first zooplankton group.
-Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.', fig.height = 8, fig.width = 4.5, echo = F, cache = TRUE, out.width = '0.5\\textwidth'>>=
-data(p1z1cat_ident)
-data(p1z1top_ident)
-
-toplo1 <- p1z1cat_ident %>% 
-  lapply(., function(x) dplyr::select(x, N, coll)) %>% 
-  reshape2::melt(., id.var = c('N', 'coll')) %>% 
-  rename(Category = L1) %>% 
-  mutate(Category = factor(Category, 
-    levels = c('Phytoplankton', 'Zooplankton'),
-    labels = c('Phytoplankton', 'Zooplankton')
-    )) %>% 
-  filter(N <= 25) %>% # reduced for plot space
-  group_by(N, Category) %>% 
-  summarise(
-    ave = mean(coll), 
-    med = median(coll),
-    min = min(coll), 
-    max = max(coll)
-  )
-
-p1 <- ggplot(toplo1, aes(x = N, group = N)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
-  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
-  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
-  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
-  scale_x_continuous(limits = c(1, 20)) +
-  theme_minimal() + 
-  theme(
-    axis.line.x = element_line(), 
-    axis.line.y = element_line(), 
-    axis.title.x = element_blank(), 
-    axis.title.y = element_blank()
-  ) + 
-  theme(legend.position = 'none') +
-  ggtitle('(a) By parameter category')
-
-# identifiability top 1, 2, 3, 4, 5 all categories combined
-toplo2 <-  reshape2::melt(p1z1top_ident, id.var = c('N', 'coll')) %>% 
-  select(N, coll, L1) %>% 
-  mutate(L1 = factor(L1, levels = paste0('top', 1:5), labels = paste0('Top ', 1:5))) %>% 
-  rename(npercat = L1) %>% 
-  group_by(N, npercat) %>% 
-  summarise(
-    ave = mean(coll), 
-    med = median(coll),
-    min = min(coll), 
-    max = max(coll)
-  )
-
-p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
-  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
-  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
-  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
-  scale_x_continuous(limits = c(1, 20)) +
-  theme_minimal() + 
-  theme(
-    axis.line.x = element_line(), 
-    axis.line.y = element_line(), 
-    axis.title.x = element_blank(), 
-    axis.title.y = element_blank(), 
-    legend.title = element_blank()
-  ) + 
-  ggtitle('(b) By top parameters, all categories')
-
-pleg <- g_legend(p2)
-p2 <- p2 + theme(legend.position = 'none')
-
-# align widths of plots in first column, first two
-pA <- ggplot_gtable(ggplot_build(p1))
-pB <- ggplot_gtable(ggplot_build(p2))
-maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3])
-
-# Set the widths
-pA$widths[2:3] <- maxWidth
-pB$widths[2:3] <- maxWidth
-
-grid.arrange(
-  arrangeGrob(pA, pB, ncol = 1, heights = c(0.45, 1)),
-  left = 'Identifiability', 
-  bottom = 'Parameters in set',
-  pleg, ncol = 2, widths = c(1, 0.15)
-)
-
-@
-
-% heuristic plots o2
-<<heurist, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters with three different heuristics.
-Parameters are selected by decreasing sensitivity for all examples (\\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}).
-The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c).
-Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\\gamma > 15$ or if the maximum number of possible parameters is selected.
-See \\cref{tab:identall1} for values in (b).', fig.height = 8, fig.width = 8, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
-
-# plot of sequential identifiability by category
-
-data(tocal)
-data(sens_ests_cat)
-
-cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
-
-# custom col scale
-mycols <- RColorBrewer::brewer.pal(5, 'Set2')
-names(mycols) <- cats
-cols <- scale_fill_manual(name = 'Category', values = mycols)
-
-# ggplot theme
-pthm <- theme_minimal() + 
-  theme(
-    axis.text.x = element_text(size = 6), 
-    axis.line.x = element_line(),
-    axis.line.y = element_line(), 
-    panel.grid.minor = element_blank(), 
-    panel.grid.major = element_blank(), 
-    axis.title.y = element_blank(), 
-    axis.title.x = element_blank()
-    )
-
-# top sensitive within categories
-toplo <- filter(tocal$cat) %>% 
-  split(., .$Category) %>% 
-  lapply(function(x){
-
-    sel <- which(x$coll < 15)
-    x <- x[c(sel, max(sel) + 1), ] %>% 
-      na.omit
-    x
-
-  }) %>% 
-  do.call('rbind', .)
-toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
-pcat <- ggplot(toplo, aes(x = Selected, y = coll)) + 
-  geom_line() + 
-  geom_point(size = 3, shape = 21, aes(fill = Category)) +
-  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
-  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
-  facet_wrap(~Category, ncol = 1, scales = 'free') + 
-  scale_x_continuous(breaks = c(1:25)) + 
-  scale_y_continuous('Identifiability') +
-  cols +
-  pthm +
-  theme(legend.position = 'none') +
-  ggtitle('(a) Blocked by category')
-
-# top sensitive
-toplo <- tocal$top
-sel <- which(toplo$coll < 15)
-toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
-toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
-ptop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
-  geom_line() + 
-  geom_point(size = 4, shape = 21, aes(fill = Category)) +
-  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
-  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
-  scale_x_continuous(breaks = 1:nrow(toplo)) + 
-  scale_y_continuous('Identifiability') + 
-  cols +
-  pthm +
-  theme(legend.position = 'none') +
-  ggtitle('(b) Independent of category')
-
-# top sensitive and category
-toplo <- tocal$cattop
-sel <- which(toplo$coll < 15)
-toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
-toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
-pcattop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
-  geom_line() + 
-  geom_point(size = 4, shape = 21, aes(fill = Category)) +
-  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
-  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
-  scale_x_continuous(breaks = 1:nrow(toplo)) + 
-  scale_y_continuous('Identifiability') +
-  cols +
-  pthm +
-  theme(legend.position = 'top') + 
-  guides(fill = guide_legend(nrow = 3)) +
-  ggtitle('(c) All categories equally')
-
-pleg <- g_legend(pcattop)
-pcattop <- pcattop +
-  theme(legend.position = 'none')
-
-grid.arrange(
-  pcat,
-  arrangeGrob(ptop, pcattop, pleg, ncol = 1, heights = c(1, 1, 0.6)), 
-  widths = c(1, 1),
-  ncol = 2, 
-  bottom = 'Parameters selected by sensitivity', 
-  left = 'Identifiability'
-)
-
-@
-
-% heuristic plots, all state
-<<heurist_stts, eval = F, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables.
-Parameters are selected by decreasing sensitivity indepent of parameter categories.
-Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\\gamma > 15$.
-See \\cref{tab:identall2} for values.', fig.height = 5, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
-data(tocal_all)
-
-# factor levels
-cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
-stts_lev <- c('NH4', 'Chla_mg_tot', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4')
-stts_lab <- c('Ammonium', 'Chlorophyll', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
-
-# custom col scale
-mycols <- RColorBrewer::brewer.pal(5, 'Set2')
-names(mycols) <- cats
-cols <- scale_fill_manual(name = 'Category', values = mycols)
-
-# ggplot theme
-pthm <- theme_minimal() + 
-  theme(
-    axis.text.x = element_text(size = 6), 
-    axis.line.x = element_line(),
-    axis.line.y = element_line(), 
-    panel.grid.minor = element_blank(), 
-    panel.grid.major = element_blank()
-    )
-
-# get all parameters for each state variable where coll < 15 plus one
-toplo <- tocal_all$top_all %>% 
-  reshape2::melt(., id.var = names(.[[1]])) %>% 
-  filter(!L1 %in% 'O2') %>% 
-  mutate(
-    L1 = factor(L1, levels = stts_lev, labels = stts_lab),
-    Category = factor(Category, levels = cats, labels = cats)
-  ) %>% 
-  split(., .$L1) %>% 
-  lapply(function(x){
-    # browser()
-    sel <- which(x$coll < 15)
-    x <- x[c(sel, max(sel) + 1), ] %>% 
-      na.omit
-    x
-
-  }) %>% 
-  do.call('rbind', .)
-
-ggplot(toplo, aes(x = Selected, y = coll)) + 
-  geom_line() + 
-  geom_point(aes(fill = Category), shape = 21, size = 4) +
-  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
-  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
-  facet_wrap(~L1, scales= 'free', ncol = 4) + 
-  scale_y_continuous('Identifiability') + 
-  scale_x_continuous(
-    'Parameters selected by sensitivity',
-    breaks = toplo$Selected
-    ) + 
-  cols +
-  pthm +
-  theme(legend.position = c(0.9, 0.2))
-@
-\clearpage
-
-% supplementary material
-\beginsupplement
-
 <<sensalltile, eval = T, echo = F, fig.height = 7, fig.width = 6, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
-See \\cref{tab:dosens} for L1 values for \\ac{do}.'>>=
+See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.'>>=
 data(sens_ests_cat_all)
@@
 
+% identifiability boxplots
+<<identbox, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
+Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
+The temperature category is not shown because only \\ac{do} was senstive to only one parameter.', fig.height = 7, fig.width = 8, echo = F, cache = TRUE>>=
+# identifiability by category (all parameters with >0 L1) 
+data(cat_ident_all)
+data(top_ident_all)
+
+# state variable, categories, and tops to plot (no temp ident because only one parameter)
+catnms <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Zooplankton')
+topnms <- paste0('top', 1:4)
+tmpcat <- cat_ident_all[['O2']] %>% 
+  .[names(.) %in% catnms]
+tmptop <- top_ident_all[['O2']] %>% 
+  .[names(.) %in% topnms]
+
+# default theme
+mytheme <- theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank(),
+    axis.ticks.x = element_line(),
+    axis.ticks.y = element_line(),
+    axis.ticks.length = unit(.1, "cm")
+  )
+
+toplo <- tmpcat %>% 
+  lapply(., function(x) dplyr::select(x, N, coll)) %>% 
+  reshape2::melt(., id.var = c('N', 'coll')) %>% 
+  rename(Category = L1) %>% 
+  mutate(Category = factor(Category, 
+    levels = catnms,
+    labels = catnms
+    )) %>% 
+  filter(N <= 25) %>% # reduced for plot space
+  group_by(N, Category) %>% 
+  summarise(
+    ave = mean(coll), 
+    med = median(coll),
+    min = min(coll), 
+    max = max(coll)
+  )
+
+p1 <- ggplot(toplo, aes(x = N, group = N)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
+  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
+  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
+  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
+  mytheme +
+  theme(legend.position = 'none') + 
+  ggtitle('(a) By parameter category')
+
+# identifiability top 1, 2, 3, 4, 5 all categories combined
+toplo2 <-  reshape2::melt(tmptop, id.var = c('N', 'coll')) %>% 
+  select(N, coll, L1) %>% 
+  mutate(L1 = factor(L1, levels = topnms, labels = topnms)) %>% 
+  rename(npercat = L1) %>% 
+  group_by(N, npercat) %>% 
+  summarise(
+    ave = mean(coll), 
+    med = median(coll),
+    min = min(coll), 
+    max = max(coll)
+  )
+
+p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
+  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
+  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
+  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
+  mytheme + 
+  theme(legend.title = element_blank()) + 
+  ggtitle('(b) By top parameters, all categories')
+
+pleg <- g_legend(p2)
+p2 <- p2 + theme(legend.position = 'none')
+
+grid.arrange(
+  arrangeGrob(p1, p2, ncol = 2),
+  left = 'Identifiability', 
+  bottom = 'Parameters in set',
+  pleg, ncol = 2, widths = c(1, 0.1)
+)
+@
+
+% parameter exclusion temp
+<<exclex, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of organic matter parameters for subset combinations in \\cref{fig:identbox}.
+Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
+Identifiability of including all eight parameters is in \\cref{fig:identbox}.
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "\\textwidth">>=
+data(cat_ident_all)
+
+tmpcat <- cat_ident_all[['O2']]
+
+toplo <-tmpcat$`Organic Matter` %>% 
+  gather('parm', 'inc', -N, -coll) %>% 
+  ungroup %>% 
+  filter(N < max(N)) %>% 
+  mutate(
+    parm = as.character(par_txt(parm, frm = 'exp')),
+    N = factor(N), 
+    inc = factor(inc, levels = c(0, 1), labels = c('excluded', 'included'))
+    )
+
+ggplot(toplo, aes(x = N, y = coll, fill = inc)) + 
+  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
+  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
+  geom_boxplot(outlier.size = 0.5, size = 0.5) + 
+  facet_wrap(~parm, label = label_parsed, ncol = 2) + 
+  theme_minimal() + 
+  scale_fill_brewer(palette = 'Greys') + 
+  scale_y_continuous('Identifiability', trans = 'log', breaks = c(0.1, 1, 10, 100, 1000)) +
+  scale_x_discrete('Parameters in set') + 
+  theme(
+    legend.title = element_blank(),
+    axis.line.x = element_line(),
+    axis.line.y = element_line(),
+    panel.grid.minor = element_blank(), 
+    panel.grid.major = element_blank(), 
+    legend.position = 'top', #c(0.8, 0.1),
+    axis.ticks.x = element_line(),
+    axis.ticks.y = element_line(),
+    axis.ticks.length = unit(.1, "cm")
+  )
+
+@
+
+% heuristic plots, all state
+<<heurist_stts, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for all state variables.
+Parameters are selected by decreasing sensitivity independent of parameter categories.
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\\gamma > 15$.', fig.height = 6, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
+data(tocal_all)
+
+# factor levels
+cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+stts_lev <- c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4')
+stts_lab <- c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
+
+# custom col scale
+mycols <- RColorBrewer::brewer.pal(5, 'Spectral')
+names(mycols) <- cats
+cols <- scale_fill_manual(name = 'Category', values = mycols)
+
+# ggplot theme
+pthm <- theme_minimal() + 
+  theme(
+    axis.text.x = element_text(size = 8), 
+    axis.line.x = element_line(),
+    axis.line.y = element_line(), 
+    panel.grid.minor = element_blank(), 
+    panel.grid.major = element_blank(),
+    axis.ticks.x = element_line(),
+    axis.ticks.y = element_line(),
+    axis.ticks.length = unit(.1, "cm")
+    )
+
+# get all parameters for each state variable where coll < 15 plus one
+toplo <- lapply(tocal_all, function(x) x$top) %>% 
+  reshape2::melt(., id.var = names(.[[1]])) %>% 
+  mutate(
+    L1 = factor(L1, levels = stts_lev, labels = stts_lab),
+    Category = factor(Category, levels = cats, labels = cats)
+  ) %>% 
+  split(., .$L1) %>% 
+  lapply(function(x){
+    # browser()
+    sel <- which(x$coll < 15)
+    x <- x[c(sel, max(sel) + 1), ] %>% 
+      na.omit
+    x
+
+  }) %>% 
+  do.call('rbind', .) %>% 
+  data.frame %>% 
+  mutate(Parameter = as.character(par_txt(Parameter, frm = 'exp')))
+
+ggplot(toplo, aes(x = Selected, y = coll)) + 
+  geom_line() + 
+  geom_text_repel(aes(label = Parameter), size = 3,
+    parse = TRUE,
+    point.padding = unit(0, "lines"),
+    box.padding = unit(1, "lines"), 
+    force = 3
+    ) +
+  geom_point(aes(fill = Category), shape = 21, size = 4) +
+  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
+  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
+  facet_wrap(~L1, scales= 'free', ncol = 4) + 
+  scale_y_continuous('Identifiability') + 
+  scale_x_continuous(
+    'Parameters selected by sensitivity',
+    breaks = toplo$Selected, 
+    expand = c(.1, .1)
+    ) + 
+  cols +
+  pthm +
+  theme(legend.position = 'top')
+@
+\clearpage
+
+% supplementary material
+\beginsupplement
+
+% ammonium sensitivity all categories
+<<nh4sens, eval = T, cache = F>>=
+senstab(out_var = 'NH4', tablab = 'nh4sens', captxt = 'ammonium', digits = 2, pow = 2, tabsize = 'footnotesize')
+@
+
+% chlorophyll sensitivity all categories
+<<chlsens, eval = T, cache = F>>=
+senstab(out_var = 'Chla_mg_tot', tablab = 'chlsens', captxt = '\\ac{chla}', digits = 2, pow = 2, tabsize = 'footnotesize')
+@
+
+% irradiance sensitivity all categories
+<<irrsens, eval = T, cache = F>>=
+senstab(out_var = 'irradiance', tablab = 'irrsens', captxt = 'irradiance', digits = 2, pow = 2, tabsize = 'footnotesize')
+@
+
+% nitrate sensitivity all categories
+<<no3sens, eval = T, cache = F>>=
+senstab(out_var = 'NO3', tablab = 'no3sens', captxt = 'nitrate', digits = 2, pow = 2, tabsize = 'footnotesize')
+@
+
+% om1 sensitivity all categories
+<<om1sens, eval = T, cache = F>>=
+senstab(out_var = 'OM1', tablab = 'om1sens', captxt = 'particulate organic matter', digits = 2, pow = 2, tabsize = 'footnotesize')
+@
+
+% om2 sensitivity all categories
+<<om2sens, eval = T, cache = F>>=
+senstab(out_var = 'OM2', tablab = 'om2sens', captxt = 'dissolved organic matter', digits = 2, pow = 2, tabsize = 'footnotesize')
+@
+
+% phosphatesensitivity all categories
+<<po4sens, eval = T, cache = F>>=
+senstab(out_var = 'PO4', tablab = 'po4sens', captxt = 'phosphate', digits = 2, pow = 2, tabsize = 'footnotesize')
+@
+
 \end{document}

### 2016-08-30 ident_manu.tex
updating figures tables

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Aug 24 11:39:30 2016 -0500
+  \\ Version Date:   Wed Aug 24 11:58:31 2016 -0500
 	}
@@
 As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.
+
 The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
-
-Irrelevant parameters were removed for several reasons from the analysis.
-Parameters that were removed were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
+Irrelevant parameters were removed for several reasons; parameters were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
 Additionally, FishTank includes six phytoplankton and two zooplankton groups to describe complexity in community structure and foodweb dynamics.
-However, structural equations for each group do not vary considerably such that variation in parameter values primarily controls differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
+However, structural equations for each group are identical such that chosen parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
 Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
@@
 The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
-For example, the sensitivity of \ac{do} to variation in the half-saturation constants (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
+For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplnakton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
 Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.
 Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.
+Initial conditions were also changed to test the effects of different limiting nutrients by setting nitrogen and phosphorus values above or below concentrations defined by the standard Redfield ratio.
 
-The effects of model structure on parameter identifiability were evaluated by including or excluding specific components of the model.
+The effects of model structure on parameter sensitivity and identifiability were evaluated by including or excluding specific components of the model.
 The FishTank model includes several processes that are based on expected conditions or available data.
@@
 
+% do sensitivity all categories
 %latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
@@
 {\footnotesize
-\caption{Sensitivities of \ac{do} to perturbation of indivividual parameters.
+\caption{Sensitivity of \ac{do} to perturbations of indivividual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$6.27\times 10^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$3.22\times 10^{-4}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.35\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$1.8\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.71$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.03$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$0.03$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.03$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.01$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.01$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.01$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$7.44\times 10^{-3}$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$5.34\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.56\times 10^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$1.3\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.59\times 10^{-4}$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$7.63\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$4.51\times 10^{-3}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$1.97\times 10^{-3}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.47\times 10^{-4}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$4.61\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$2.89\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.05$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.01$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$7.53\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$6.49\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$6.36\times 10^{-3}$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$8\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.9\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$2.44\times 10^{-4}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% ident all states
+
+% ident all states
+
+\clearpage
+
+%%%%%%
+% figures
+
+% combination example
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=0.6\textwidth]{figs/combnex-1}
+
+}
+
+\caption[Examples of unique parameter combinations from different parameter sets and number of selected parameters]{Examples of unique parameter combinations from different parameter sets and number of selected parameters.
+The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
+Note that the number of unique combinations is shown as the natural-log.}\label{fig:combnex}
+\end{figure}
+
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/sensalltile-1}
+
+}
+
+\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
+Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
+See \cref{tab:dosens} for L1 values for \ac{do} and \cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.}\label{fig:sensalltile}
+\end{figure}
+
+% identifiability boxplots
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\maxwidth]{figs/identbox-1}
+
+}
+
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.
+Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
+Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
+The temperature category is not shown because only \ac{do} was senstive to only one parameter.}\label{fig:identbox}
+\end{figure}
+
+% parameter exclusion temp
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/exclex-1}
+
+}
+
+\caption{Identifiability (as $\gamma$, \cref{gameq}) of organic matter parameters for subset combinations in \cref{fig:identbox}.
+Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
+Identifiability of including all eight parameters is in \cref{fig:identbox}.
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:exclex}
+\end{figure}
+
+% heuristic plots, all state
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/heurist_stts-1}
+
+}
+
+\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for all state variables.
+Parameters are selected by decreasing sensitivity independent of parameter categories.
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
+Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
+\end{figure}
+
+\clearpage
+
+% supplementary material
+\beginsupplement
+
+% ammonium sensitivity all categories
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivity of ammonium to perturbations of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect ammonium are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:nh4sens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.01$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.01$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$4.77\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.61$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$43.95$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$9.63$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$1.32$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.9$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.56$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.31$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.3$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.21$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.05$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.04$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.02$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$9.3\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$6.4\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.18$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.17$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$1.41\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.85\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$1.1$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$0.71$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.36$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.2$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.14$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.07$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$0.05$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.01$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% chlorophyll sensitivity all categories
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivity of \ac{chla} to perturbations of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect \ac{chla} are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:chlsens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$6.77\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.96$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$132.89$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$20.34$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$1.9$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$1.33$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.91$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.37$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$4.69\times 10^{-3}$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$2.25\times 10^{-3}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$2.13\times 10^{-3}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$7.11\times 10^{-4}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$2.05\times 10^{-4}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$1.71\times 10^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$2.32\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$6.79\times 10^{-5}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.46\times 10^{-5}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$1.07\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$6.48\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.58$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.02$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$1.69\times 10^{-3}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.38\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.96\times 10^{-4}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$3.14\times 10^{-5}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% irradiance sensitivity all categories
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivity of irradiance to perturbations of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect irradiance are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:irrsens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$2.71\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$2.41\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$7.15\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$2.29\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$8.09\times 10^{-3}$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$7.65\times 10^{-3}$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$7.42\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$2.13\times 10^{-3}$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$2.09\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$7.39\times 10^{-4}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$5.74\times 10^{-4}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$4.7\times 10^{-4}$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$4.44\times 10^{-4}$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$6.64\times 10^{-5}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$4.7\times 10^{-5}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$3.48\times 10^{-5}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$2.45\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$7.23\times 10^{-6}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.05\times 10^{-6}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$9.27\times 10^{-7}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$4.47\times 10^{-7}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$2.43\times 10^{-8}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.05$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.6\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$1.61\times 10^{-4}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.31\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.82\times 10^{-5}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$2.95\times 10^{-6}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$7.41\times 10^{-9}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$4.81\times 10^{-9}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% nitrate sensitivity all categories
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivity of nitrate to perturbations of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect nitrate are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:no3sens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$5.03\times 10^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$2.58\times 10^{-4}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$8.38\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$1.79\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.1$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.02$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$9.21\times 10^{-3}$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$8.6\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$4.69\times 10^{-3}$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$4.56\times 10^{-3}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$3.7\times 10^{-3}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$1.91\times 10^{-3}$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$1.81\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.54\times 10^{-4}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$8.37\times 10^{-5}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$4.18\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$1.28\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$4.96\times 10^{-4}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$3.02\times 10^{-5}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.53\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$5.55\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.05$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$7.09\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$4.36\times 10^{-3}$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.5\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$8.65\times 10^{-4}$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$7.43\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$3.34\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$3.23\times 10^{-4}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% om1 sensitivity all categories
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivity of particulate organic matter to perturbations of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect particulate organic matter are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om1sens}}
 \begin{center}
@@
 
-% ident all states
+% om2 sensitivity all categories
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivity of dissolved organic matter to perturbations of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect dissolved organic matter are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om2sens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.67\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.96$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$120$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$19.66$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$1.44$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$1.09$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.96$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.84$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.47$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.42$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.41$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.34$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.04$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$9.43\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$6.95\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$8.74\times 10^{-3}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$7.52\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.1\times 10^{-3}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$2.72\times 10^{-4}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$3.18\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$0.98$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.53$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.18$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.13$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.02$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.01$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$1.14\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$6.11\times 10^{-6}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
 
-% ident all states
+\end{table}
 
-\clearpage
+% phosphatesensitivity all categories
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Sensitivity of phosphate to perturbations of indivividual parameters.
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Parameters that did not affect phosphate are not shown.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:po4sens}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$2.08\times 10^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$8.92\times 10^{-5}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$2.09\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$3.19\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$0.02$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$0.01$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$9.03\times 10^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$7.23\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$5.4\times 10^{-3}$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$5.23\times 10^{-3}$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$2.08\times 10^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$3.87\times 10^{-4}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$1.63\times 10^{-4}$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$1.13\times 10^{-4}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$1.04\times 10^{-4}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$8.56\times 10^{-5}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.19\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$2.99\times 10^{-3}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$6.74\times 10^{-5}$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$6.68\times 10^{-6}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.32\times 10^{-6}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$3.59\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$6.07\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$2.38\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$8.4\times 10^{-4}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$7.05\times 10^{-4}$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$3.73\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.01\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.44\times 10^{-7}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$1.29\times 10^{-7}$\tabularnewline
+\hline
+\end{tabular}\end{center}}
 
-%%%%%%
-% figures
-
-% combination example
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=0.6\textwidth]{figs/combnex-1}
-
-}
-
-\caption[Examples of unique parameter combinations from different parameter sets and number of selected parameters]{Examples of unique parameter combinations from different parameter sets and number of selected parameters.
-The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
-Note that the number of unique combinations is shown as the natural-log.}\label{fig:combnex}
-\end{figure}
-
-% sensitivity example of top
-
-% identifiability boxplots
-
-% parameter exclusion temp
-
-% identifiability boxplot, p1, z1 only
-
-% heuristic plots o2
-
-% heuristic plots, all state
-
-\clearpage
-
-% supplementary material
-\beginsupplement
-
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/sensalltile-1}
-
-}
-
-\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
-Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
-See \cref{tab:dosens} for L1 values for \ac{do}.}\label{fig:sensalltile}
-\end{figure}
+\end{table}
 

### 2016-08-30 R/funcs.R

@@ -1018,7 +1018,7 @@ senstab <- function(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', tabs
   cats <- totab$cats
   totab <- totab[,-c(1:2)]
   
-  cap.val<- paste('Sensitivities of', captxt, 'to perturbation of indivividual parameters.  Sensitivities are based on a 50\\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \\cref{l1}).  Parameters that did not affect', captxt, 'are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.')
+  cap.val<- paste('Sensitivity of', captxt, 'to perturbations of indivividual parameters.  Sensitivities are based on a 50\\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \\cref{l1}).  Parameters that did not affect', captxt, 'are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.')
   
   latex( 
     totab,

### 2016-08-30 ident_manu.Rnw
identifiability tables for all state variables are done

@@
 
-% ident all states
-<<identdo, eval = F, cache = F>>=
+% first heuristic, all states
+<<heurist1, eval = T, cache = F>>=
 data(tocal_all)
@@
 cats_lev <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
-cats_lab <- c('O', 'OM', 'P', 'T', 'Z')
+cats_lab <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
 stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
@@
 
-labs <- parcats2(as_df = T) %>% 
-    rename(Parameter = shrt) %>% 
-    select(Parameter, lngs)
-
 # format tocal_all for identifiability table
-# add long parameter name
-# get parameter combos with coll < 15 + 1
-# format error and coll with scinot
-# format category label so no duplicates
-totab <- tocal_all$top_all %>% 
+totab <- lapply(tocal_all, function(x) x$cat) %>% 
   reshape2::melt(., id.var = names(.[[1]])) %>%
   mutate(Parameter = as.character(Parameter)) %>%
-  left_join(., labs, by = 'Parameter') %>% 
   mutate(
-    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
-    lngs = gsub('_', '', lngs), 
     stts = factor(L1, levels = stts_lev, labels = stts_lab),
@@
     x <- x[sel, ] %>%
+
     # x <- x[c(sel, max(sel) + 1), ] %>% 
@@
   mutate(
-    error = sapply(error, scinot),
     coll = sapply(coll, scinot), 
     Rank = sapply(rnk_incat, scinot), 
-    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
+    Rank = paste0(Rank)
     ) %>%
@@
   unnest %>% 
-  select(stts, lngs, Parameter, Rank, error, coll) %>% 
-  rename(
-    Description = lngs, 
-    L1 = error
-  ) %>% 
+  select(stts, Category, Parameter, Rank, coll) %>%
   mutate(
     stts = as.character(stts),
-    Description = paste0('\\footnotesize{', Description, '}'),
     Parameter = paste0('\\footnotesize{', Parameter, '}')
     ) %>% 
-  arrange(stts)
-
-identall1 <- filter(totab, stts %in% 'Dissolved Oxygen')
+  spread(stts, coll, fill = '-') %>% 
+  group_by(Parameter) %>% 
+  arrange(Category, Rank)
 
 # final table formatting
-descrip <- as.character(identall1$Description)
-identall1 <- identall1[,-c(1, 2)]
-cap_val<- 'Parameter identifiability for dissolved oxygen.
-Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.
-Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
-colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')
+parms <- totab$Parameter
+cats <- as.character(totab$Category)
+cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) by category for relevant state variables.
+Selections followed the first heuristic where parameters were selected within categories from most to least sensitive until $\\gamma > 15$.
+Rank describes the relative parameter sensitivity in each category for each state variable.'
+colnms <- c('Rank', 'Ammonium', 'Chl-\\textit{a}', 'O$_2$', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
 
 latex( 
-  identall1,
+  totab[, -c(1, 2)],
   file = '',
-  rowlabel = 'Parameter description',
+  rowlabel = 'Parameter',
   caption = cap_val,
   caption.loc = 'top',
-  size = 'normalsize',
-  label = 'tab:identall1',
-  rowname = descrip,
+  size = 'footnotesize',
+  label = 'tab:heurist1',
+  rowname = parms,
+  rgroup = unique(cats),
+  n.rgroup = as.numeric(table(cats)),
   colheads = colnms,
@@
 
-% ident all states
-<<identall, eval = F, cache = F>>=
+% second heuristic, all states
+<<heurist2, eval = T, cache = F>>=
 data(tocal_all)
@@
 
-labs <- parcats2(as_df = T) %>% 
-    rename(Parameter = shrt) %>% 
-    select(Parameter, lngs)
-
 # format tocal_all for identifiability table
-# add long parameter name
-# get parameter combos with coll < 15 + 1
-# format error and coll with scinot
-# format category label so no duplicates
 totab <- lapply(tocal_all, function(x) x$top) %>% 
@@
   mutate(Parameter = as.character(Parameter)) %>% 
-  left_join(., labs, by = 'Parameter') %>% 
   mutate(
-    lngs = gsub('^[a-z,A-Z,0-9]*:\\s', '', lngs), 
-    lngs = gsub('_', '', lngs), 
     stts = factor(L1, levels = stts_lev, labels = stts_lab),
@@
   ) %>% 
-  split(., .$L1) %>% 
-  lapply(function(x){
-
-    sel <- which(x$coll < 15)
-    x <- x[sel, ] %>% 
-    # x <- x[c(sel, max(sel) + 1), ] %>% 
-      na.omit
-    x
-
-  }) %>% 
-  do.call('rbind', .) %>%
+  filter(coll < 15) %>% 
   mutate(
-    error = sapply(error, scinot),
     coll = sapply(coll, scinot), 
@@
     ) %>%
-  group_by(stts) %>% 
-  nest %>% 
-  unnest %>% 
-  select(stts, lngs, Parameter, Rank, error, coll) %>% 
-  rename(
-    Description = lngs, 
-    L1 = error
-  ) %>% 
+  select(stts, Selected, Parameter, Rank, coll) %>%
   mutate(
     stts = as.character(stts),
-    Description = paste0('\\scriptsize{', Description, '}'),
-    Parameter = paste0('\\scriptsize{', Parameter, '}')
+    Parameter = paste0('\\footnotesize{', Parameter, '}')
     ) %>% 
-  arrange(stts)
-
-identall2 <- filter(totab, !stts %in% 'Dissolved Oxygen')
+  arrange(stts, Selected)
 
 # final table formatting
-stts <- identall2$stts
-descrip <- as.character(identall2$Description)
-identall2 <- identall2[,-c(1, 2)]
-cap_val<- 'Parameter identifiability for ammonium, chlorophyll, irradiance, nitrate, OM1, OM2, and phosphate.
-Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\\gamma < 15$.
-Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
-colnms <- c('Parameter', 'Rank', 'L1', '$\\gamma$')
+stts <- as.character(totab$stts)
+sels <- totab$Selected
+cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) for relevant state variables.
+Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\\gamma > 15$.
+Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).
+See \\cref{fig:heurist_stts} for a graphical illustration.'
+colnms <- c('Parameter', 'Rank', '$\\gamma$')
 
 latex( 
-  identall2,
+  totab[, -c(1, 2)],
   file = '',
-  rowlabel = 'State variable, parameter description',
+  rowlabel = 'Selections by state variable',
   caption = cap_val,
@@
   size = 'footnotesize',
-  label = 'tab:identall2',
-  rgroup = unique(as.character(stts)),
-  n.rgroup = as.numeric(table(as.character(stts))),
-  rowname = descrip,
+  label = 'tab:heurist2',
+  rowname = sels,
+  rgroup = unique(stts),
+  n.rgroup = as.numeric(table(stts)),
   colheads = colnms,
@@
 @
+
+% third heuristic, all states
+<<heurist3, eval = T, cache = F>>=
+data(tocal_all)
+
+# factor levels
+cats_lev <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
+cats_lab <- c('O', 'OM', 'P', 'T', 'Z')
+stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+
+# format tocal_all for identifiability table
+totab <- lapply(tocal_all, function(x) x$cattop) %>% 
+  reshape2::melt(., id.var = names(.[[1]])) %>%
+  mutate(Parameter = as.character(Parameter)) %>% 
+  mutate(
+    stts = factor(L1, levels = stts_lev, labels = stts_lab),
+    Category = factor(Category, levels = cats_lev, labels = cats_lab), 
+    Parameter = par_txt(Parameter, frm = 'tex')
+  ) %>% 
+  filter(coll < 15) %>% 
+  mutate(
+    coll = sapply(coll, scinot), 
+    Rank = sapply(rnk_incat, scinot), 
+    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
+    ) %>%
+  select(stts, Selected, Parameter, Rank, coll) %>%
+  mutate(
+    stts = as.character(stts),
+    Parameter = paste0('\\footnotesize{', Parameter, '}')
+    ) %>% 
+  arrange(stts, Selected)
+
+# final table formatting
+stts <- as.character(totab$stts)
+sels <- totab$Selected
+cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) for relevant state variables.
+Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive until $\\gamma > 15$.
+Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
+colnms <- c('Parameter', 'Rank', '$\\gamma$')
+
+latex( 
+  totab[, -c(1, 2)],
+  file = '',
+  rowlabel = 'Selections by state variable',
+  caption = cap_val,
+  caption.loc = 'top',
+  size = 'footnotesize',
+  label = 'tab:heurist3',
+  rowname = sels,
+  rgroup = unique(stts),
+  n.rgroup = as.numeric(table(stts)),
+  colheads = colnms,
+  rgroupTexCmd = NULL
+  )
+@
+
 \clearpage
@@
 
-% phosphatesensitivity all categories
+% phosphate sensitivity all categories
 <<po4sens, eval = T, cache = F>>=

### 2016-08-30 ident_manu.tex
identifiability tables for all state variables are done

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Aug 24 11:58:31 2016 -0500
+  \\ Version Date:   Tue Aug 30 11:59:58 2016 -0500
 	}
@@
 
-% ident all states
-
-% ident all states
+% first heuristic, all states
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) by category for relevant state variables.
+Selections followed the first heuristic where parameters were selected within categories from most to least sensitive until $\gamma > 15$.
+Rank describes the relative parameter sensitivity in each category for each state variable.\label{tab:heurist1}}
+\begin{center}
+\begin{tabular}{llllllllll}
+\hline\hline
+\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Ammonium}&\multicolumn{1}{c}{Chl-\textit{a}}&\multicolumn{1}{c}{O$_2$}&\multicolumn{1}{c}{Irradiance}&\multicolumn{1}{c}{Nitrate}&\multicolumn{1}{c}{OM1}&\multicolumn{1}{c}{OM2}&\multicolumn{1}{c}{Phosphate}\tabularnewline
+\hline
+{Optics}&&&&&&&&&\tabularnewline
+~~\footnotesize{\textit{astar490}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\footnotesize{\textit{astarOMA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\footnotesize{\textit{astar490}}&$2$&$8.54$&$10.83$&-&-&-&$9.19$&$7.33$&-\tabularnewline
+~~\footnotesize{\textit{astarOMA}}&$2$&-&-&$3.86$&$1.43$&-&-&-&$3.63$\tabularnewline
+~~\footnotesize{\textit{astarOMZ}}&$3$&-&$13.7$&$3.93$&$3.78$&-&$13.31$&$13.12$&$3.73$\tabularnewline
+\hline
+{Organic Matter}&&&&&&&&&\tabularnewline
+~~\footnotesize{\textit{KG1}}&$1$&-&-&-&-&-&$1$&-&$1$\tabularnewline
+~~\footnotesize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
+~~\footnotesize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KNH4}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KstarO2}}&$1$&-&-&$1$&-&$1$&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG1}}&$2$&-&$3.42$&$1.12$&$1.43$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$6.03$\tabularnewline
+~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.9$&$1.73$&-\tabularnewline
+~~\footnotesize{\textit{nitmax}}&$2$&$14.51$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG2}}&$3$&-&-&$5.31$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KGcdom}}&$3$&$14.51$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KO2}}&$3$&-&-&-&$6.37$&-&$6.17$&$4.98$&-\tabularnewline
+\hline
+{Phytoplankton}&&&&&&&&&\tabularnewline
+~~\footnotesize{\textit{alpha}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\footnotesize{\textit{Qc}}&$1$&-&-&$1$&$1$&$1$&-&-&-\tabularnewline
+~~\footnotesize{\textit{QminP}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
+~~\footnotesize{\textit{alpha}}&$2$&-&-&$1.66$&$1.36$&$4.98$&-&-&-\tabularnewline
+~~\footnotesize{\textit{mA}}&$2$&-&-&-&-&-&-&-&$1.24$\tabularnewline
+~~\footnotesize{\textit{umax}}&$2$&$8.51$&$4.64$&-&-&-&$6.1$&$5.36$&-\tabularnewline
+~~\footnotesize{\textit{alpha}}&$3$&-&-&-&-&-&-&-&$4.73$\tabularnewline
+~~\footnotesize{\textit{mA}}&$3$&$9.18$&$5.26$&$7.56$&$2.7$&-&$7.13$&$6.72$&-\tabularnewline
+~~\footnotesize{\textit{respb}}&$4$&$13.74$&$9.62$&-&-&-&$13.32$&$14.3$&-\tabularnewline
+~~\footnotesize{\textit{vmaxP}}&$4$&-&-&-&-&-&-&-&$6.18$\tabularnewline
+~~\footnotesize{\textit{Qc}}&$5$&-&$13.06$&-&-&-&$13.35$&$14.39$&-\tabularnewline
+\hline
+{Zooplankton}&&&&&&&&&\tabularnewline
+~~\footnotesize{\textit{ZQc}}&$1$&-&$1$&$1$&$1$&-&$1$&$1$&-\tabularnewline
+~~\footnotesize{\textit{ZQn}}&$1$&$1$&-&-&-&$1$&-&-&-\tabularnewline
+~~\footnotesize{\textit{ZQp}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
+~~\footnotesize{\textit{Zm}}&$2$&-&-&-&-&-&$2.76$&-&-\tabularnewline
+~~\footnotesize{\textit{Zrespb}}&$2$&-&$5.46$&-&$5.88$&-&-&-&$1.66$\tabularnewline
+~~\footnotesize{\textit{Zm}}&$3$&-&$14.16$&-&-&-&-&-&$4.21$\tabularnewline
+~~\footnotesize{\textit{ZQp}}&$3$&-&-&-&-&-&$2.76$&-&-\tabularnewline
+~~\footnotesize{\textit{ZQc}}&$4$&-&-&-&-&-&-&-&$5.23$\tabularnewline
+~~\footnotesize{\textit{ZQp}}&$4$&-&$14.2$&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{Zrespb}}&$4$&-&-&-&-&-&$12.49$&-&-\tabularnewline
+~~\footnotesize{\textit{ZQn}}&$5$&-&-&-&-&-&$13.59$&-&-\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% second heuristic, all states
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.
+Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.
+Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).
+See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
+\hline
+{Ammonium}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$8.51$\tabularnewline
+~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$9.18$\tabularnewline
+~~4&\footnotesize{\textit{KNH4}}&$1$\textsuperscript{OM}&$11.35$\tabularnewline
+\hline
+{Chlorophyll}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$4.64$\tabularnewline
+~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$5.26$\tabularnewline
+~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$9.62$\tabularnewline
+~~5&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$12.93$\tabularnewline
+\hline
+{Dissolved Oxygen}&&&\tabularnewline
+~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+\hline
+{Irradiance}&&&\tabularnewline
+~~1&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1.15$\tabularnewline
+~~3&\footnotesize{\textit{alpha}}&$2$\textsuperscript{P}&$2.5$\tabularnewline
+~~4&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$2.92$\tabularnewline
+\hline
+{Nitrate}&&&\tabularnewline
+~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+\hline
+{OM1}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$6.1$\tabularnewline
+~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$7.13$\tabularnewline
+~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$13.32$\tabularnewline
+~~5&\footnotesize{\textit{Qc}}&$5$\textsuperscript{P}&$13.35$\tabularnewline
+\hline
+{OM2}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$5.36$\tabularnewline
+~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$6.72$\tabularnewline
+~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$14.3$\tabularnewline
+~~5&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$14.9$\tabularnewline
+\hline
+{Phosphate}&&&\tabularnewline
+~~1&\footnotesize{\textit{QminP}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$1.24$\tabularnewline
+~~3&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.73$\tabularnewline
+~~4&\footnotesize{\textit{vmaxP}}&$4$\textsuperscript{P}&$6.18$\tabularnewline
+~~5&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.17$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% third heuristic, all states
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
+\begin{table}[!tbp]
+{\footnotesize
+\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.
+Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive until $\gamma > 15$.
+Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:heurist3}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
+\hline
+{Ammonium}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{KNH4}}&$1$\textsuperscript{OM}&$1.67$\tabularnewline
+~~3&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.96$\tabularnewline
+~~4&\footnotesize{\textit{ZQn}}&$1$\textsuperscript{Z}&$3.61$\tabularnewline
+~~5&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$4.97$\tabularnewline
+\hline
+{Chlorophyll}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.36$\tabularnewline
+~~3&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$6.39$\tabularnewline
+~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$13.97$\tabularnewline
+\hline
+{Dissolved Oxygen}&&&\tabularnewline
+~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+\hline
+{Irradiance}&&&\tabularnewline
+~~1&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1.15$\tabularnewline
+~~3&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.97$\tabularnewline
+~~4&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$5.14$\tabularnewline
+~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$6.62$\tabularnewline
+~~6&\footnotesize{\textit{alpha}}&$2$\textsuperscript{P}&$12.85$\tabularnewline
+\hline
+{Nitrate}&&&\tabularnewline
+~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+\hline
+{OM1}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.73$\tabularnewline
+~~3&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$2.77$\tabularnewline
+~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$6.91$\tabularnewline
+~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$6.91$\tabularnewline
+~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$13.68$\tabularnewline
+\hline
+{OM2}&&&\tabularnewline
+~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.46$\tabularnewline
+~~3&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.53$\tabularnewline
+~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$7.69$\tabularnewline
+~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$7.87$\tabularnewline
+\hline
+{Phosphate}&&&\tabularnewline
+~~1&\footnotesize{\textit{QminP}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$1.3$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
 
@@
 
-% phosphatesensitivity all categories
+% phosphate sensitivity all categories
 %latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%

### 2016-09-06 ident_manu.Rnw
structural and initial condition effects figures added to supp

@@
 \acrodef{zerod}[0-D]{zero-dimensional}
-\acrodef{par}[PAR]{photosynthetically active radiation}
 
@@
 
+\subsection{Extension to other state variables}
+
 The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
-In addition to \ac{do}, other state variables included \ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
+In addition to \ac{do}, other state variables included \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
 Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
@@
 Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.
-Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
+Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
 Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
@@
 \section{Discussion}
-
-% back of envelop calcs for number of relevant parms, all state variables
-<<echo = F>>=
-
-@
-We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
+%' 
+%' % back of envelop calcs for number of relevant parms, all state variables
+%' <<echo = F>>=
+%' 
+%' @
+%' We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
 14 for models that follow traditional calibration schemes (e.g., objective function minimization).
-
-Emphasize that parameters that have the greatest effect on collinearity are not those that have the highest sensitivity (contrast the identifiability by category vs identifiability by top parameters)  , also note that groups of parameters together can have large effects on collinearity, maybe some kind of bootstrap analysis could be done looking at doubletons, etc.
+%' 
+%' Emphasize that parameters that have the greatest effect on collinearity are not those that have the highest sensitivity (contrast the identifiability by category vs identifiability by top parameters)  , also note that groups of parameters together can have large effects on collinearity, maybe some kind of bootstrap analysis could be done looking at doubletons, etc.
 The example in teh results highlights how redundant variables can be identified as a necessary part of the model calibration process.
-
-Why did identifiability decrease for top five parameters in each category after removing redundant phyto/zoop groups?
-
-\citep{Denman03} describes over-parameterization for multiple phyto groups, use this to emphasize collinearity issues with the phyto groups despite differing sensitivity values between groups
-
-Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).
-
-Questions specific to GOM - what initial conditions are important? How many phytoplankton groups do we need (e.g., related to structural uncertainty)?
-
-How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
+%' 
+%' Why did identifiability decrease for top five parameters in each category after removing redundant phyto/zoop groups?
+%' 
+%' \citep{Denman03} describes over-parameterization for multiple phyto groups, use this to emphasize collinearity issues with the phyto groups despite differing sensitivity values between groups
+%' 
+%' Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).  
+%' 
+%' Questions specific to GOM - what initial conditions are important? How many phytoplankton groups do we need (e.g., related to structural uncertainty)?
+%' 
+%' How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
 \citet{Wagener01} describes this as a potential approach to improving model performance by improving the availability of information for model calibration (p.
 14).
-
-How does uncertainty translate to what a model should provide (generality v precision)?  The first step - find out what can be optimized but then do not overfit....
-
-What about structural uncertainty - does sensitivity of a model to variation in a parameter imply parameter uncertainty and/or structural uncertainty?
-
-A final point about optimization with identifiable parameter sets - optimization to fit the data still does not ensure a correct model.
+%' 
+%' How does uncertainty translate to what a model should provide (generality v precision)?  The first step - find out what can be optimized but then do not overfit....
+%' 
+%' What about structural uncertainty - does sensitivity of a model to variation in a parameter imply parameter uncertainty and/or structural uncertainty?
+%' 
+%' A final point about optimization with identifiable parameter sets - optimization to fit the data still does not ensure a correct model.
 Failing in one way can be over-compensated by another feature, e.g., the parameter set that is optimized (see \cite{Flynn05}, p.
 1207, third paragraph), also \citep{Durand02,Arhonditsis08}, also note that over-parameterized models are not necessarily bad, see \citep{Omlin01}, models must be validated for the uses which they were intended where a comparison of observed and predicted is the simplest approach and other methods should be used depending on analysis needs \citep{Rykiel96}
-
-\cite{Omlin01} state that the sensitivity, identifiability, estimation process is iterative (p. 113), need to rinse and repeat for proper calibration.
-
-How to improve identifiability - get more/better observed data, include obs from other state variables in RSS minimization (eqn q in \cite{Omlin01})
-
-Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}, \citep{Arhonditsis08}
-
-Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by \citep{Wagener01b}2001 (cited on page 15, in \citealt{Wagener01}), although ours is simple in comparison
+%' 
+%' \cite{Omlin01} state that the sensitivity, identifiability, estimation process is iterative (p. 113), need to rinse and repeat for proper calibration. 
+%' 
+%' How to improve identifiability - get more/better observed data, include obs from other state variables in RSS minimization (eqn q in \cite{Omlin01})
+%' 
+%' Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}, \citep{Arhonditsis08}
+%' 
+%' Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by \citep{Wagener01b}2001 (cited on page 15, in \citealt{Wagener01}), although ours is simple in comparison
 
@@
 
-lims <- with(tmp, quantile(error)) %>% 
-  as.numeric
-
 stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
@@
 Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
-The temperature category is not shown because only \\ac{do} was senstive to only one parameter.', fig.height = 7, fig.width = 8, echo = F, cache = TRUE>>=
+The temperature category is not shown because \\ac{do} was sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 7, fig.width = 8, echo = F, cache = TRUE>>=
 # identifiability by category (all parameters with >0 L1) 
@@
 
+%%
+% sup tabs
+
 % ammonium sensitivity all categories
@@
 
+%%
+% sup figs
+
+% effects of structural uncertainty
+<<streval, fig.cap = 'Effects of model structure on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
+# structural
+data(struct_eval)
+
+swtc_levs <- paste0('Which_quota', 1:length(struct_eval))
+swtc_labs <- paste0('Which quota: ', c('Droop', 'Nyholm', 'Flynn'))
+
+toplo_all <- lapply(struct_eval, function(x) {
+
+  tmp <- reshape2::melt(x[[2]], id.var = c('Parameter', 'error', 'Category'))
+  swtc <- paste0(names(x[[1]]), x[[1]])
+
+  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+
+  toplo <- mutate(tmp,
+      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
+      Parameter = as.character(par_txt(Parameter, frm = 'exp')),
+      swtc = as.character(swtc)
+    ) %>% 
+    rename(Sensitivity = error)
+
+  return(toplo)
+
+  })
+toplo_all <- do.call('rbind', toplo_all)
+toplo_all <- mutate(toplo_all, swtc = factor(swtc, levels = swtc_levs, labels = swtc_labs))
+
+pbase <- theme(
+  panel.grid.major = element_blank(), 
+  panel.grid.minor = element_blank(), 
+  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
+  axis.text.y = element_text(size = 6),
+  legend.position = 'top', 
+  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt'), 
+  strip.background = element_blank(), 
+  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5)
+  )
+
+pstr <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
+  geom_tile(colour = 'black') + 
+  pbase +
+  scale_y_discrete('Parameter', 
+    expand = c(0, 0),
+    breaks = toplo_all$Parameter, 
+    labels = parse(text = toplo_all$Parameter)
+    ) + 
+  scale_x_discrete('State variable', expand = c(0, 0)) +
+  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
+  facet_grid(Category~swtc, scales = 'free_y', space = 'free') + 
+  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
+
+print(pstr)
+@
+
+% effects of initial conditions
+<<inieval, fig.cap = 'Effects of initial conditions on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
+# initial conditions
+data(ini_eval)
+
+ini_levs <- paste('Initial:', c('def', 'apr', 'sep'))
+ini_labs <- paste('Initial:', c('Default', 'April', 'September'))
+
+toplo_all <- sapply(1:length(ini_eval), function(x) {
+
+  tmp <- reshape2::melt(ini_eval[[x]][[2]], id.var = c('Parameter', 'error', 'Category'))
+  ini <- names(ini_eval)[x]
+
+  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+
+  toplo <- mutate(tmp,
+      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
+      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
+      ini = paste('Initial:', ini)
+    ) %>% 
+    rename(Sensitivity = error)
+
+  return(toplo)
+
+  }, simplify = F)
+toplo_all <- do.call('rbind', toplo_all)
+toplo_all <- mutate(toplo_all, ini = factor(ini, levels = ini_levs, labels = ini_labs))
+
+pbase <- theme(
+  panel.grid.major = element_blank(), 
+  panel.grid.minor = element_blank(), 
+  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
+  axis.text.y = element_text(size = 6),
+  legend.position = 'top', 
+  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt'), 
+  strip.background = element_blank(), 
+  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5)
+  )
+
+pini <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
+  geom_tile(colour = 'black') + 
+  pbase +
+  scale_y_discrete('Parameter', 
+    expand = c(0, 0),
+    breaks = toplo_all$Parameter, 
+    labels = parse(text = toplo_all$Parameter)
+    ) + 
+  scale_x_discrete('State variable', expand = c(0, 0)) +
+  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
+  facet_grid(Category~ini, scales = 'free_y', space = 'free') + 
+  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
+
+print(pini)
+@
+
 \end{document}

### 2016-09-06 ident_manu.tex
structural and initial condition effects figures added to supp

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Aug 30 11:59:58 2016 -0500
+  \\ Version Date:   Tue Aug 30 15:34:01 2016 -0500
 	}
@@
 Selection independent of category showed that including par_txt(h2_brk[1]) caused in increase in $\gamma$ from scinot(h2_brk[3], digits = 1) to scinot(h2_brk[2], digits = 1) and equal selection within cateogies showed that including par_txt(h3_brk[1]) caused in increase in $\gamma$ from scinot(h3_brk[3], digits = 1) to scinot(h3_brk[2], digits = 1).
-Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
+Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
 Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
@@
 \section{Discussion}
-
-% back of envelop calcs for number of relevant parms, all state variables
-
-We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
+%' 
+%' % back of envelop calcs for number of relevant parms, all state variables
+%' <<echo = F>>=
+%' 
+%' @
+%' We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
 14 for models that follow traditional calibration schemes (e.g., objective function minimization).
-
-Emphasize that parameters that have the greatest effect on collinearity are not those that have the highest sensitivity (contrast the identifiability by category vs identifiability by top parameters)  , also note that groups of parameters together can have large effects on collinearity, maybe some kind of bootstrap analysis could be done looking at doubletons, etc.
+%' 
+%' Emphasize that parameters that have the greatest effect on collinearity are not those that have the highest sensitivity (contrast the identifiability by category vs identifiability by top parameters)  , also note that groups of parameters together can have large effects on collinearity, maybe some kind of bootstrap analysis could be done looking at doubletons, etc.
 The example in teh results highlights how redundant variables can be identified as a necessary part of the model calibration process.
-
-Why did identifiability decrease for top five parameters in each category after removing redundant phyto/zoop groups?
-
-\citep{Denman03} describes over-parameterization for multiple phyto groups, use this to emphasize collinearity issues with the phyto groups despite differing sensitivity values between groups
-
-Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).
-
-Questions specific to GOM - what initial conditions are important? How many phytoplankton groups do we need (e.g., related to structural uncertainty)?
-
-How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
+%' 
+%' Why did identifiability decrease for top five parameters in each category after removing redundant phyto/zoop groups?
+%' 
+%' \citep{Denman03} describes over-parameterization for multiple phyto groups, use this to emphasize collinearity issues with the phyto groups despite differing sensitivity values between groups
+%' 
+%' Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).  
+%' 
+%' Questions specific to GOM - what initial conditions are important? How many phytoplankton groups do we need (e.g., related to structural uncertainty)?
+%' 
+%' How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
 \citet{Wagener01} describes this as a potential approach to improving model performance by improving the availability of information for model calibration (p.
 14).
-
-How does uncertainty translate to what a model should provide (generality v precision)?  The first step - find out what can be optimized but then do not overfit....
-
-What about structural uncertainty - does sensitivity of a model to variation in a parameter imply parameter uncertainty and/or structural uncertainty?
-
-A final point about optimization with identifiable parameter sets - optimization to fit the data still does not ensure a correct model.
+%' 
+%' How does uncertainty translate to what a model should provide (generality v precision)?  The first step - find out what can be optimized but then do not overfit....
+%' 
+%' What about structural uncertainty - does sensitivity of a model to variation in a parameter imply parameter uncertainty and/or structural uncertainty?
+%' 
+%' A final point about optimization with identifiable parameter sets - optimization to fit the data still does not ensure a correct model.
 Failing in one way can be over-compensated by another feature, e.g., the parameter set that is optimized (see \cite{Flynn05}, p.
 1207, third paragraph), also \citep{Durand02,Arhonditsis08}, also note that over-parameterized models are not necessarily bad, see \citep{Omlin01}, models must be validated for the uses which they were intended where a comparison of observed and predicted is the simplest approach and other methods should be used depending on analysis needs \citep{Rykiel96}
-
-\cite{Omlin01} state that the sensitivity, identifiability, estimation process is iterative (p. 113), need to rinse and repeat for proper calibration.
-
-How to improve identifiability - get more/better observed data, include obs from other state variables in RSS minimization (eqn q in \cite{Omlin01})
-
-Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}, \citep{Arhonditsis08}
-
-Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by \citep{Wagener01b}2001 (cited on page 15, in \citealt{Wagener01}), although ours is simple in comparison
+%' 
+%' \cite{Omlin01} state that the sensitivity, identifiability, estimation process is iterative (p. 113), need to rinse and repeat for proper calibration. 
+%' 
+%' How to improve identifiability - get more/better observed data, include obs from other state variables in RSS minimization (eqn q in \cite{Omlin01})
+%' 
+%' Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}, \citep{Arhonditsis08}
+%' 
+%' Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by \citep{Wagener01b}2001 (cited on page 15, in \citealt{Wagener01}), although ours is simple in comparison
 
@@
 Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
-The temperature category is not shown because only \ac{do} was senstive to only one parameter.}\label{fig:identbox}
+The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identbox}
 \end{figure}
@@
 \beginsupplement
+
+%%
+% sup tabs
 
@@
 
+%%
+% sup figs
+
+% effects of structural uncertainty
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/streval-1}
+
+}
+
+\caption[Effects of model structure on parameter sensitivity]{Effects of model structure on parameter sensitivity.}\label{fig:streval}
+\end{figure}
+
+% effects of initial conditions
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/inieval-1}
+
+}
+
+\caption[Effects of initial conditions on parameter sensitivity]{Effects of initial conditions on parameter sensitivity.}\label{fig:inieval}
+\end{figure}
+
 \end{document}

### 2016-09-23 ident_manu.Rnw
updating results with new fishtank mod

@@
 <<echo = FALSE>>=
-pars <- parcats2(as_df = TRUE)$shrt %>% 
-  as.character
-rmpars <- c('Kw_1', 'Kcdom_1', 'Kspm_1', 'Kchla_1', 'aw490_1', 'astarOMR_1', 'astarOMBC_1', 'KTg1(nospA+nospZ)_1', 'KTg1(nospA+nospZ)_2', 'KTg1(nospA+nospZ)_3', 'KTg1(nospA+nospZ)_4', 'KTg1(nospA+nospZ)_5', 'KTg1(nospA+nospZ)_6', 'KTg1(nospA+nospZ)_7', 'KTg1(nospA+nospZ)_8', 'KTg2(nospA+nospZ)_1', 'KTg2(nospA+nospZ)_2', 'KTg2(nospA+nospZ)_3', 'KTg2(nospA+nospZ)_4', 'KTg2(nospA+nospZ)_5', 'KTg2(nospA+nospZ)_6', 'KTg2(nospA+nospZ)_7', 'KTg2(nospA+nospZ)_8', 'Ea_R(nospA+nospZ)_1', 'Ea_R(nospA+nospZ)_2', 'Ea_R(nospA+nospZ)_3', 'Ea_R(nospA+nospZ)_4', 'Ea_R(nospA+nospZ)_5', 'Ea_R(nospA+nospZ)_6', 'Ea_R(nospA+nospZ)_7', 'Ea_R(nospA+nospZ)_8', 'beta_1', 'beta_2', 'beta_3', 'beta_4', 'beta_5', 'beta_6', 'QmaxN_1', 'QmaxN_2', 'QmaxN_3', 'QmaxN_4', 'QmaxN_5', 'QmaxN_6', 'QmaxP_1', 'QmaxP_2', 'QmaxP_3', 'QmaxP_4', 'QmaxP_5', 'QmaxP_6', 'nfQs_1', 'nfQs_2', 'nfQs_3', 'nfQs_4', 'nfQs_5', 'nfQs_6', 'KG1_R_1', 'KG2_R_1', 'KG1_BC_1', 'KG2_BC_1', 'pCO2_1', 'stoich_x1R_1', 'stoich_y1R_1', 'stoich_x2R_1', 'stoich_y2R_1', 'stoich_x1BC_1', 'stoich_y1BC_1', 'stoich_x2BC_1', 'stoich_y2BC_1', 'sink OM1_R_1', 'sink OM2_R_1', 'sink OM1_BC_1', 'sink OM2_BC_1', 'CF_SPM_1')
-rmpars <- c(rmpars, 'respb_7') # there's an extra of this one
-pars <- pars[!pars %in% rmpars]
-p1z1pars <- grep('_1$|_7$', pars, value = TRUE) # get parameters for one phyto, one zoop (_7 is for temp)
+p1z1pars <- par_tst()
 
@@
 nparms <- parcats2(as_df = TRUE) %>% 
-  filter(!shrt %in% rmpars) %>% 
-  filter(grepl('_1$|_7$', shrt)) %>% 
+  filter(shrt %in% p1z1pars) %>% 
   .$cats %>% 
@@
 The effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.
-These analyses used changes in parameter uncertainty and identifiability to infer the effects of observational and structural uncertainty on model output to create a more comprehensive evaluation.
+These analyses used changes in parameter uncertainty and identifiability from results using the model's default configuration to infer the effects of observational and structural uncertainty on model output.
 First, observational uncertainty was evaluated by varying the initial conditions supplied to the model.
 The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
-For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplnakton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
+For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplankton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
 Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.
@@
 % effects of structural uncertainty
-<<streval, fig.cap = 'Effects of model structure on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
+<<streval, fig.cap = 'Effects of model structure on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = F, echo = F, warning = F, message = F>>=
 # structural

### 2016-09-23 ident_manu.tex
updating results with new fishtank mod

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Aug 30 15:34:01 2016 -0500
+  \\ Version Date:   Tue Sep 6 12:52:12 2016 -0500
 	}
@@
 {\footnotesize
-\caption{Sensitivity of \ac{do} to perturbations of indivividual parameters.
+\caption{Sensitivity of \ac{do} to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$6.27\times 10^{-4}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$3.22\times 10^{-4}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.35\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$1.8\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.71$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.03$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$0.03$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.03$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.01$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.01$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.01$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$7.44\times 10^{-3}$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$5.34\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.56\times 10^{-3}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$1.3\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.59\times 10^{-4}$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$7.63\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$4.51\times 10^{-3}$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$1.97\times 10^{-3}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.47\times 10^{-4}$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$4.61\times 10^{-5}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$2.89\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.05$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.01$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$7.53\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$6.49\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$6.36\times 10^{-3}$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$8\times 10^{-4}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.9\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$2.44\times 10^{-4}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$7.41\times 10^{-4}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.91\times 10^{-5}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.34\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.06$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.02$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.02$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.02$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.01$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$8.28\times 10^{-3}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$8.15\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$6.93\times 10^{-3}$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.41\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$4.25\times 10^{-3}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$4.2\times 10^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$4.19\times 10^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$4.05\times 10^{-3}$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.9\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$3.03\times 10^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$1.4\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.05$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.02$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.02$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$0.02$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.01$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.58\times 10^{-3}$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.19\times 10^{-3}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.89\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$9.48\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.63\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.1\times 10^{-3}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.59\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.11\times 10^{-3}$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.95\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.68\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$4.91\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$4.12\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.93\times 10^{-4}$\tabularnewline
 \hline
@@
 {Optics}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{astar490}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
-~~\footnotesize{\textit{astarOMA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\footnotesize{\textit{astar490}}&$2$&$8.54$&$10.83$&-&-&-&$9.19$&$7.33$&-\tabularnewline
-~~\footnotesize{\textit{astarOMA}}&$2$&-&-&$3.86$&$1.43$&-&-&-&$3.63$\tabularnewline
-~~\footnotesize{\textit{astarOMZ}}&$3$&-&$13.7$&$3.93$&$3.78$&-&$13.31$&$13.12$&$3.73$\tabularnewline
+~~\footnotesize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
+~~\footnotesize{\textit{astarOMA}}&$2$&$7.26$&$5.4$&-&$5.35$&-&$7.72$&$7.91$&-\tabularnewline
+~~\footnotesize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.81$\tabularnewline
+~~\footnotesize{\textit{astarOMA}}&$3$&-&-&$3.73$&-&-&-&-&$9.65$\tabularnewline
+~~\footnotesize{\textit{astarOMZ}}&$3$&$7.5$&$5.51$&-&$6.01$&-&$7.88$&$7.91$&-\tabularnewline
 \hline
 {Organic Matter}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{KG1}}&$1$&-&-&-&-&-&$1$&-&$1$\tabularnewline
+~~\footnotesize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
 ~~\footnotesize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
 ~~\footnotesize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KNH4}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KstarO2}}&$1$&-&-&$1$&-&$1$&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG1}}&$2$&-&$3.42$&$1.12$&$1.43$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$6.03$\tabularnewline
-~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.9$&$1.73$&-\tabularnewline
-~~\footnotesize{\textit{nitmax}}&$2$&$14.51$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG2}}&$3$&-&-&$5.31$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KGcdom}}&$3$&$14.51$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KO2}}&$3$&-&-&-&$6.37$&-&$6.17$&$4.98$&-\tabularnewline
+~~\footnotesize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
+~~\footnotesize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$13.44$\tabularnewline
+~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.4$&-\tabularnewline
+~~\footnotesize{\textit{KNH4}}&$2$&$4.04$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KNO3}}&$2$&-&-&-&-&$9.1$&-&-&-\tabularnewline
+~~\footnotesize{\textit{KstarO2}}&$2$&-&-&$1.06$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG1}}&$3$&$4.1$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG2}}&$3$&-&-&$6.01$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.78$\tabularnewline
+~~\footnotesize{\textit{KO2}}&$3$&-&-&-&-&-&$14.25$&$12.35$&-\tabularnewline
+~~\footnotesize{\textit{KstarO2}}&$3$&-&$1.28$&-&$1.99$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KG2}}&$4$&-&-&-&$11.17$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KGcdom}}&$4$&-&-&$6.08$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.5$\tabularnewline
+~~\footnotesize{\textit{KstarO2}}&$4$&$4.29$&-&-&-&-&$14.34$&$13.61$&-\tabularnewline
+~~\footnotesize{\textit{KGcdom}}&$5$&$4.41$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KO2}}&$5$&-&-&$8.44$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{nitmax}}&$6$&-&-&$10.12$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KNH4}}&$7$&-&-&$10.17$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{KNO3}}&$8$&-&-&$13.94$&-&-&-&-&-\tabularnewline
 \hline
 {Phytoplankton}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{alpha}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\footnotesize{\textit{Qc}}&$1$&-&-&$1$&$1$&$1$&-&-&-\tabularnewline
-~~\footnotesize{\textit{QminP}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
-~~\footnotesize{\textit{alpha}}&$2$&-&-&$1.66$&$1.36$&$4.98$&-&-&-\tabularnewline
-~~\footnotesize{\textit{mA}}&$2$&-&-&-&-&-&-&-&$1.24$\tabularnewline
-~~\footnotesize{\textit{umax}}&$2$&$8.51$&$4.64$&-&-&-&$6.1$&$5.36$&-\tabularnewline
-~~\footnotesize{\textit{alpha}}&$3$&-&-&-&-&-&-&-&$4.73$\tabularnewline
-~~\footnotesize{\textit{mA}}&$3$&$9.18$&$5.26$&$7.56$&$2.7$&-&$7.13$&$6.72$&-\tabularnewline
-~~\footnotesize{\textit{respb}}&$4$&$13.74$&$9.62$&-&-&-&$13.32$&$14.3$&-\tabularnewline
-~~\footnotesize{\textit{vmaxP}}&$4$&-&-&-&-&-&-&-&$6.18$\tabularnewline
-~~\footnotesize{\textit{Qc}}&$5$&-&$13.06$&-&-&-&$13.35$&$14.39$&-\tabularnewline
+~~\footnotesize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\footnotesize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\footnotesize{\textit{ediblevector(Z1)}}&$2$&$1.13$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{mA}}&$2$&-&-&$1.16$&$1.28$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{Qc}}&$2$&-&-&-&-&$3.38$&-&-&-\tabularnewline
+~~\footnotesize{\textit{umax}}&$2$&-&$1.09$&-&-&-&$1.18$&$1.18$&-\tabularnewline
+~~\footnotesize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$2.75$\tabularnewline
+~~\footnotesize{\textit{alpha}}&$3$&-&-&$1.43$&$1.98$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{ediblevector(Z1)}}&$3$&-&$2.14$&-&-&-&$3.22$&$2.87$&-\tabularnewline
+~~\footnotesize{\textit{umax}}&$3$&$1.23$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{alpha}}&$4$&$1.64$&$4.3$&-&-&-&-&$7.17$&-\tabularnewline
+~~\footnotesize{\textit{ediblevector(Z1)}}&$4$&-&-&$1.83$&$3.15$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{Qc}}&$4$&-&-&-&-&-&$5.2$&-&-\tabularnewline
+~~\footnotesize{\textit{alpha}}&$5$&-&-&-&-&-&$9.72$&-&-\tabularnewline
+~~\footnotesize{\textit{Qc}}&$5$&-&-&$3.18$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{vmaxN}}&$5$&$8$&$14.42$&-&-&-&-&$14.48$&-\tabularnewline
+~~\footnotesize{\textit{Athresh}}&$6$&$8.32$&-&-&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{respg}}&$6$&-&$14.56$&$3.65$&-&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{vmaxN}}&$7$&-&-&$4$&-&-&-&-&-\tabularnewline
 \hline
 {Zooplankton}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{ZQc}}&$1$&-&$1$&$1$&$1$&-&$1$&$1$&-\tabularnewline
-~~\footnotesize{\textit{ZQn}}&$1$&$1$&-&-&-&$1$&-&-&-\tabularnewline
-~~\footnotesize{\textit{ZQp}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
-~~\footnotesize{\textit{Zm}}&$2$&-&-&-&-&-&$2.76$&-&-\tabularnewline
-~~\footnotesize{\textit{Zrespb}}&$2$&-&$5.46$&-&$5.88$&-&-&-&$1.66$\tabularnewline
-~~\footnotesize{\textit{Zm}}&$3$&-&$14.16$&-&-&-&-&-&$4.21$\tabularnewline
-~~\footnotesize{\textit{ZQp}}&$3$&-&-&-&-&-&$2.76$&-&-\tabularnewline
-~~\footnotesize{\textit{ZQc}}&$4$&-&-&-&-&-&-&-&$5.23$\tabularnewline
-~~\footnotesize{\textit{ZQp}}&$4$&-&$14.2$&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{Zrespb}}&$4$&-&-&-&-&-&$12.49$&-&-\tabularnewline
-~~\footnotesize{\textit{ZQn}}&$5$&-&-&-&-&-&$13.59$&-&-\tabularnewline
+~~\footnotesize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\footnotesize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\footnotesize{\textit{ZKa}}&$2$&-&$3.48$&-&-&-&$5.38$&$4.15$&-\tabularnewline
+~~\footnotesize{\textit{ZQn}}&$2$&-&-&$2.38$&$3.84$&$5.97$&-&-&$4.1$\tabularnewline
+~~\footnotesize{\textit{Zm}}&$3$&-&-&$2.74$&-&-&-&-&$11.52$\tabularnewline
+~~\footnotesize{\textit{Zumax}}&$3$&-&-&-&$5.94$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{Zm}}&$4$&-&-&-&$6.9$&-&-&-&-\tabularnewline
+~~\footnotesize{\textit{Zumax}}&$4$&-&-&$3.59$&-&-&-&-&-\tabularnewline
 \hline
@@
 {Ammonium}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$8.51$\tabularnewline
-~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$9.18$\tabularnewline
-~~4&\footnotesize{\textit{KNH4}}&$1$\textsuperscript{OM}&$11.35$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.17$\tabularnewline
+~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.88$\tabularnewline
 \hline
 {Chlorophyll}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$4.64$\tabularnewline
-~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$5.26$\tabularnewline
-~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$9.62$\tabularnewline
-~~5&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$12.93$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
+~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.1$\tabularnewline
 \hline
 {Dissolved Oxygen}&&&\tabularnewline
-~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.27$\tabularnewline
+~~3&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$2.37$\tabularnewline
+~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.41$\tabularnewline
+~~5&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.54$\tabularnewline
+~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.9$\tabularnewline
+~~7&\footnotesize{\textit{Zm}}&$3$\textsuperscript{Z}&$4.92$\tabularnewline
+~~8&\footnotesize{\textit{Zumax}}&$4$\textsuperscript{Z}&$4.94$\tabularnewline
 \hline
 {Irradiance}&&&\tabularnewline
-~~1&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1.15$\tabularnewline
-~~3&\footnotesize{\textit{alpha}}&$2$\textsuperscript{P}&$2.5$\tabularnewline
-~~4&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$2.92$\tabularnewline
+~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$5.03$\tabularnewline
+~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.98$\tabularnewline
+~~4&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$8.27$\tabularnewline
+~~5&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$10.08$\tabularnewline
+~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$10.09$\tabularnewline
+~~7&\footnotesize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.83$\tabularnewline
 \hline
 {Nitrate}&&&\tabularnewline
-~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$4.79$\tabularnewline
+~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$6.88$\tabularnewline
 \hline
 {OM1}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$6.1$\tabularnewline
-~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$7.13$\tabularnewline
-~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$13.32$\tabularnewline
-~~5&\footnotesize{\textit{Qc}}&$5$\textsuperscript{P}&$13.35$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$1.18$\tabularnewline
+~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$3.18$\tabularnewline
+~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.5$\tabularnewline
 \hline
 {OM2}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$5.36$\tabularnewline
-~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$6.72$\tabularnewline
-~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$14.3$\tabularnewline
-~~5&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$14.9$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
+~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.74$\tabularnewline
+~~4&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.86$\tabularnewline
+~~5&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$5.44$\tabularnewline
 \hline
 {Phosphate}&&&\tabularnewline
-~~1&\footnotesize{\textit{QminP}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$1.24$\tabularnewline
-~~3&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.73$\tabularnewline
-~~4&\footnotesize{\textit{vmaxP}}&$4$\textsuperscript{P}&$6.18$\tabularnewline
-~~5&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.17$\tabularnewline
+~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$4.9$\tabularnewline
+~~3&\footnotesize{\textit{vmaxP}}&$2$\textsuperscript{P}&$6.84$\tabularnewline
+~~4&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$14.13$\tabularnewline
 \hline
@@
 {Ammonium}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{KNH4}}&$1$\textsuperscript{OM}&$1.67$\tabularnewline
-~~3&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.96$\tabularnewline
-~~4&\footnotesize{\textit{ZQn}}&$1$\textsuperscript{Z}&$3.61$\tabularnewline
-~~5&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$4.97$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.17$\tabularnewline
+~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.88$\tabularnewline
+~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$3.45$\tabularnewline
+~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.23$\tabularnewline
 \hline
 {Chlorophyll}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.36$\tabularnewline
-~~3&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$6.39$\tabularnewline
-~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$13.97$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
+~~3&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.62$\tabularnewline
+~~4&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$3.25$\tabularnewline
+~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$5.91$\tabularnewline
+~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$5.92$\tabularnewline
+~~7&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$10.99$\tabularnewline
+~~8&\footnotesize{\textit{KG1}}&$2$\textsuperscript{OM}&$11.01$\tabularnewline
+~~9&\footnotesize{\textit{astarOMA}}&$2$\textsuperscript{O}&$11.32$\tabularnewline
 \hline
 {Dissolved Oxygen}&&&\tabularnewline
-~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.27$\tabularnewline
+~~3&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.36$\tabularnewline
+~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$4.05$\tabularnewline
+~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.1$\tabularnewline
+~~6&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$4.4$\tabularnewline
+~~7&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$5.08$\tabularnewline
+~~8&\footnotesize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$5.87$\tabularnewline
+~~9&\footnotesize{\textit{astarOMZ}}&$2$\textsuperscript{O}&$6.08$\tabularnewline
+~~10&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$6.17$\tabularnewline
+~~11&\footnotesize{\textit{Zm}}&$3$\textsuperscript{Z}&$10.42$\tabularnewline
 \hline
 {Irradiance}&&&\tabularnewline
-~~1&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1.15$\tabularnewline
-~~3&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.97$\tabularnewline
-~~4&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$5.14$\tabularnewline
-~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$6.62$\tabularnewline
-~~6&\footnotesize{\textit{alpha}}&$2$\textsuperscript{P}&$12.85$\tabularnewline
+~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$5.03$\tabularnewline
+~~3&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$5.05$\tabularnewline
+~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$5.12$\tabularnewline
+~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$7.6$\tabularnewline
+~~6&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$10.92$\tabularnewline
+~~7&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$10.94$\tabularnewline
+~~8&\footnotesize{\textit{KG1}}&$2$\textsuperscript{OM}&$10.94$\tabularnewline
+~~9&\footnotesize{\textit{astarOMA}}&$2$\textsuperscript{O}&$11.12$\tabularnewline
+~~10&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$12.29$\tabularnewline
 \hline
 {Nitrate}&&&\tabularnewline
-~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$4.79$\tabularnewline
+~~3&\footnotesize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$6.71$\tabularnewline
+~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$7.63$\tabularnewline
 \hline
 {OM1}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.73$\tabularnewline
-~~3&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$2.77$\tabularnewline
-~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$6.91$\tabularnewline
-~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$6.91$\tabularnewline
-~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$13.68$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.15$\tabularnewline
+~~3&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$3.88$\tabularnewline
+~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$3.93$\tabularnewline
+~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$5.85$\tabularnewline
+~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$9.9$\tabularnewline
+~~7&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$10.05$\tabularnewline
 \hline
 {OM2}&&&\tabularnewline
-~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.46$\tabularnewline
-~~3&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$2.53$\tabularnewline
-~~4&\footnotesize{\textit{astarOMA}}&$1$\textsuperscript{O}&$7.69$\tabularnewline
-~~5&\footnotesize{\textit{ZQc}}&$1$\textsuperscript{Z}&$7.87$\tabularnewline
+~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
+~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.61$\tabularnewline
+~~4&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$3.4$\tabularnewline
+~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.52$\tabularnewline
+~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$7.43$\tabularnewline
+~~7&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$7.62$\tabularnewline
+~~8&\footnotesize{\textit{KGcdom}}&$2$\textsuperscript{OM}&$12.42$\tabularnewline
 \hline
 {Phosphate}&&&\tabularnewline
-~~1&\footnotesize{\textit{QminP}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$1.3$\tabularnewline
+~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
+~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$4.9$\tabularnewline
+~~3&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$5.63$\tabularnewline
+~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.55$\tabularnewline
+~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$9.82$\tabularnewline
+~~6&\footnotesize{\textit{vmaxP}}&$2$\textsuperscript{P}&$11.26$\tabularnewline
 \hline
@@
 {\footnotesize
-\caption{Sensitivity of ammonium to perturbations of indivividual parameters.
+\caption{Sensitivity of ammonium to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.01$\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.01$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$4.77\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.61$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$43.95$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$9.63$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$1.32$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.9$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.56$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.31$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.3$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.21$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.05$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.04$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.02$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$9.3\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$6.4\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.18$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.17$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$1.41\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.85\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$1.1$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$0.71$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.36$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.2$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.14$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.07$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$0.05$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.01$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.61\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.48\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.78$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$8.49$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$1.31$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.75$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.59$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.46$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.28$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.16$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.15$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.14$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.13$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$0.1$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.1$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.05$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$1.97\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$1.41$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.76$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.59$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.56$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.48$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.29$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.22$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.16$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.07\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$1.93\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.53$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$0.66$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.07$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.07$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.06$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.06$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.03$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$5.42\times 10^{-3}$\tabularnewline
 \hline
@@
 {\footnotesize
-\caption{Sensitivity of \ac{chla} to perturbations of indivividual parameters.
+\caption{Sensitivity of \ac{chla} to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$6.77\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.96$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$132.89$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$20.34$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$1.9$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$1.33$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.91$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.37$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$4.69\times 10^{-3}$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$2.25\times 10^{-3}$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$2.13\times 10^{-3}$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$7.11\times 10^{-4}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$2.05\times 10^{-4}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$1.71\times 10^{-4}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$2.32\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$6.79\times 10^{-5}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.46\times 10^{-5}$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$1.07\times 10^{-5}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$6.48\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.58$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.02$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$1.69\times 10^{-3}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.38\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.96\times 10^{-4}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$3.14\times 10^{-5}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.45\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.13\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$13.94$\tabularnewline
+~~maximum growth rate&\textit{umax}&$1$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.95$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.62$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.54$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.26$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.25$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.24$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.14$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.12$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$0.07$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.03$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$0.02$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$1.57\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$1.03$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.95$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.57$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.54$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.24$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.14$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.29\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$1.01\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.08$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.03$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.02$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.51\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$9.86\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$3.23\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$2.86\times 10^{-5}$\tabularnewline
 \hline
@@
 {\footnotesize
-\caption{Sensitivity of irradiance to perturbations of indivividual parameters.
+\caption{Sensitivity of irradiance to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$2.71\times 10^{-3}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$2.41\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$7.15\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$2.29\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$8.09\times 10^{-3}$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$7.65\times 10^{-3}$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$7.42\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$2.13\times 10^{-3}$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$2.09\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$7.39\times 10^{-4}$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$5.74\times 10^{-4}$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$4.7\times 10^{-4}$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$4.44\times 10^{-4}$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$6.64\times 10^{-5}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$4.7\times 10^{-5}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$3.48\times 10^{-5}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$2.45\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$7.23\times 10^{-6}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.05\times 10^{-6}$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$9.27\times 10^{-7}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$4.47\times 10^{-7}$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$2.43\times 10^{-8}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.05$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.6\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$1.61\times 10^{-4}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.31\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.82\times 10^{-5}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$2.95\times 10^{-6}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$7.41\times 10^{-9}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$4.81\times 10^{-9}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.46\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.34\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.13$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.05$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.04$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.04$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.03$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.02$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.01$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.01$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.01$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$9.49\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$9.4\times 10^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$8.15\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$5.78\times 10^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$4.45\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$1.04\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$2.03\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.17$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.06$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$0.04$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.04$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.03$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.02$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.72\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$9.29\times 10^{-5}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$2.11\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$3.95\times 10^{-3}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$1.23\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$9.87\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.61\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$4.94\times 10^{-5}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.59\times 10^{-6}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1.38\times 10^{-6}$\tabularnewline
 \hline
@@
 {\footnotesize
-\caption{Sensitivity of nitrate to perturbations of indivividual parameters.
+\caption{Sensitivity of nitrate to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$5.03\times 10^{-4}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$2.58\times 10^{-4}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$8.38\times 10^{-7}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$1.79\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.1$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.02$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$9.21\times 10^{-3}$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$8.6\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$4.69\times 10^{-3}$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$4.56\times 10^{-3}$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$3.7\times 10^{-3}$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$1.91\times 10^{-3}$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$1.81\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.54\times 10^{-4}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$8.37\times 10^{-5}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$4.18\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$1.28\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$4.96\times 10^{-4}$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$3.02\times 10^{-5}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.53\times 10^{-5}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$5.55\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.05$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$7.09\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$4.36\times 10^{-3}$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.5\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$8.65\times 10^{-4}$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$7.43\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$3.34\times 10^{-4}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$3.23\times 10^{-4}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.54\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.43\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.34$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$49.33$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.54$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$1.1$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.37$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.31$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.26$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.22$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.13$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.13$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.13$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.12$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$0.11$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.08$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$9.1\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$4.01\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$34.61$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$2.21$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$1.1$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$0.38$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.35$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.29$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.21$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$4.7\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.05\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$1.27$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$0.05$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.03$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.03$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$0.01$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.01$\tabularnewline
 \hline
@@
 {\footnotesize
-\caption{Sensitivity of particulate organic matter to perturbations of indivividual parameters.
+\caption{Sensitivity of particulate organic matter to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.94\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.92$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$102.96$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$18.21$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$1.62$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$1.2$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.95$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.35$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.16$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.1$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.09$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.09$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$8.86\times 10^{-3}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$3.49\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.09\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.87\times 10^{-3}$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$1.1\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.72\times 10^{-4}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.21\times 10^{-4}$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$2.19\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.9$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.53$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.15$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.11$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.02$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$5.27\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$3.67\times 10^{-6}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$1.75\times 10^{-6}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.72\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.49\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$7.23$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.99$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.9$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.68$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.67$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.45$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.29$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.24$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.22$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$0.21$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.14$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.12$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.09$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$7.35\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$0.96$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.85$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.54$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.51$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.39$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.27$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.16$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$9.64\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.05\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.92$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$2.47\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$4.74\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$4.25\times 10^{-5}$\tabularnewline
 \hline
@@
 {\footnotesize
-\caption{Sensitivity of dissolved organic matter to perturbations of indivividual parameters.
+\caption{Sensitivity of dissolved organic matter to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.67\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$0.96$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$120$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$19.66$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$1.44$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$1.09$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.96$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.84$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.47$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.42$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.41$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.34$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.04$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$9.43\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$6.95\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$8.74\times 10^{-3}$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$7.52\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.1\times 10^{-3}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$2.72\times 10^{-4}$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$3.18\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$0.98$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.53$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.18$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.13$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.02$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.01$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$1.14\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$6.11\times 10^{-6}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$2.47\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$2.05\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$14.26$\tabularnewline
+~~maximum growth rate&\textit{umax}&$1.24$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.95$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.86$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.86$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.68$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.36$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.29$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.25$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$0.24$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.23$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.21$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.14$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.11$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$0.02$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$4.36\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$1.02$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.98$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.58$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.57$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.42$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.13$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.12$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$0.04$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.68\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.94$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.1$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.04$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.04$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.98\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$6.14\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$5.23\times 10^{-5}$\tabularnewline
 \hline
@@
 {\footnotesize
-\caption{Sensitivity of phosphate to perturbations of indivividual parameters.
+\caption{Sensitivity of phosphate to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$2.08\times 10^{-4}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$8.92\times 10^{-5}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$2.09\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Temperature}&&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$3.19\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$0.02$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.1$&$0.01$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$9.03\times 10^{-3}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$7.23\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$5.4\times 10^{-3}$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.86$&$5.23\times 10^{-3}$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.41$&$2.08\times 10^{-3}$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$3.87\times 10^{-4}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$1.63\times 10^{-4}$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$1.13\times 10^{-4}$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$1.04\times 10^{-4}$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$8.56\times 10^{-5}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.19\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$2.99\times 10^{-3}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$6.74\times 10^{-5}$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$6.68\times 10^{-6}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.32\times 10^{-6}$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$3.59\times 10^{-7}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$6.07\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$2.38\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$8.4\times 10^{-4}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$7.05\times 10^{-4}$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$3.73\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.01\times 10^{-4}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.44\times 10^{-7}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$1.29\times 10^{-7}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$9\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$5.36\times 10^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.79\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$1.06$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.58$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.23$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.2$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.18$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.13$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.11$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.09$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.06$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.06$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$0.04$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.03$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.01$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$7.3\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$9.82\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.8$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.51$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.35$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$0.26$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.19$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.15$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.1$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$6.39\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.93\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.14$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.06$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.02$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.01$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$9.96\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$7.66\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.75\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1.71\times 10^{-5}$\tabularnewline
 \hline
@@
 % effects of structural uncertainty
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/streval-1}
-
-}
-
-\caption[Effects of model structure on parameter sensitivity]{Effects of model structure on parameter sensitivity.}\label{fig:streval}
-\end{figure}
 

### 2016-09-23 R/funcs.R

@@ -909,7 +909,7 @@ par_txt <- function(parin, frm = 'tex', p1z1 = TRUE){
   splits <- cats[sels, ] %>% 
     .[match(parin, .$shrt), ] # this is important to make sure the output order matches with input
   
-  # gsub the shrt names differnet by category
+  # gsub the shrt names different by category
   subs <- apply(splits, 1,  function(x){
 
     # 1-6 are phytos, 7-8 are zoops (changed to 1-2)
@@ -950,14 +950,28 @@ par_txt <- function(parin, frm = 'tex', p1z1 = TRUE){
   .$shrt
 
   # remove subscripts if p1z1
-  if(p1z1) subs <- gsub('_p[1-6]$|_z[1-1]$', '', subs)
+  if(p1z1){
+    
+    # temperature has both phyto and zoop for p1z1, so do not remove subs for those
+    temps <- filter(cats, cats %in% 'Temperature') %>% 
+      .$shrt %>% 
+      as.character %>% 
+      gsub('\\(nospA\\+nospZ\\)_[1-8]$', '', .) %>% 
+      unique
+    sels <- grepl(paste(temps, collapse = '|'), subs)
+    
+    # remove subs for all but temp
+    subs[!sels] <- gsub('_p[1-6]$|_z[1-2]$', '', subs[!sels])
+    
+  }
 
   # convert output format for tex
   if(frm == 'tex'){
     
     out <- gsub('_([pz][1-9])$', '$_{\\1}$', subs)
+    out <- gsub('([1-9,a-z,A-Z])_', '\\1\\\\_', out)
     out <- paste0('\\textit{', out, '}')
-      
+
   }
   
   # convert output format as expressions for R
@@ -999,18 +1013,16 @@ senstab <- function(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', tabs
     mutate(Parameter = as.character(Parameter)) %>% 
     left_join(., tmpest, by = 'Parameter') %>% 
     left_join(., labs, by = 'Parameter') %>% 
-    select(cats, lngs, Parameter, vals, L1) %>% 
+    select(cats, lngs, Parameter, L1) %>% 
     arrange(cats, -L1) %>% 
     mutate(
[…]

### 2016-09-27 ident_manu.Rnw
added better tables and figures for initial and structural analyses

@@
     stts = as.character(stts),
-    Parameter = paste0('\\footnotesize{', Parameter, '}')
+    Parameter = paste0('\\scriptsize{', Parameter, '}')
     ) %>% 
@@
   caption.loc = 'top',
-  size = 'footnotesize',
+  size = 'scriptsize',
   label = 'tab:heurist1',
@@
   caption.loc = 'top',
-  size = 'footnotesize',
+  size = 'scriptsize',
   label = 'tab:heurist2',
@@
     Rank = sapply(rnk_incat, scinot), 
-    Rank = paste0(Rank, '\\textsuperscript{', Category, '}')
+    Rank = paste0(Rank, '\\textsubscript{', Category, '}')
     ) %>%
@@
   caption.loc = 'top',
-  size = 'footnotesize',
+  size = 'scriptsize',
   label = 'tab:heurist3',
@@
   )
+@
+
+% change in sensitivity for different initial, structural conditions
+<<inistrchg, eval = T, cache = F>>=
+# initial conditions
+data(ini_eval)
+data(struct_eval)
+
+to_eval <- lapply(ini_eval, function(x) x[[2]]) %>% 
+  c(., struct = list(struct_eval))
+
+eval_levs <- c('def', 'apr', 'sep', 'struct')
+eval_labs <- c('Default', 'Initial: April', 'Initial: September', 'Structure: complex')
+
+totab_all <- sapply(1:length(to_eval), function(x) {
+
+  tmp <- reshape2::melt(to_eval[[x]], id.var = c('Parameter', 'error', 'Category'))
+  nms <- names(to_eval)[x]
+
+  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+
+  toplo <- mutate(tmp,
+      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
+      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
+      nms = nms
+    ) %>% 
+    rename(Sensitivity = error)
+
+  return(toplo)
+
+  }, simplify = F)
+totab_all <- do.call('rbind', totab_all)
+totab_all <- mutate(totab_all, nms = factor(nms, levels = eval_levs, labels = eval_labs))
+
+# summarize
+totab_all <- spread(totab_all, nms, Sensitivity) %>% 
+  group_by(Category, L1) %>% 
+  summarise(
+    mean_def = mean(Default, na.rm = TRUE),
+    iniapr_dif = mean_def - mean(`Initial: April`, na.rm = TRUE),
+    iniapr_sgn = sign(iniapr_dif),
+    iniapr_dif = sapply(iniapr_dif, scinot),
+    iniapr_dif = ifelse(iniapr_sgn == -1, iniapr_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', iniapr_dif))),
+    inisep_dif = mean_def - mean(`Initial: September`, na.rm = TRUE),
+    inisep_sgn = sign(inisep_dif),
+    inisep_dif = sapply(inisep_dif, scinot),
+    inisep_dif = ifelse(inisep_sgn == -1, inisep_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', inisep_dif))),
+    strcom_dif = mean_def - mean(`Structure: complex`, na.rm = TRUE),
+    strcom_sgn = sign(strcom_dif),
+    strcom_dif = sapply(strcom_dif, scinot),
+    strcom_dif = ifelse(strcom_sgn == -1, strcom_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', strcom_dif))),
+    mean_def = sapply(mean_def, scinot)
+  ) %>% 
+  select(-iniapr_sgn, -inisep_sgn, -strcom_sgn)
+
+# final table formatting
+cats <- as.character(totab_all$Category)
+stts<- totab_all$L1
+cap_val<- 'Changes in mean sensitivity of state variables by parameter categories to different initial conditions and changes in structural components of the model.
+Changes show the difference in average sensitivity from results using the default model setup.
+Sensitivities are based on average $L1$ (see \\cref{l1}) values of the state variables to changes in parameters in each parameter category.
+Increases in average sensitivity are in bold.
+Medians and ranges of sensitivity values for the different conditions are shown in \\cref{fig:inistrsumm}.'
+colnms <- c('Default sensitivity', 'Initial: April', 'Initial: September', 'Structure: complex')
+
+latex( 
+  totab_all[, -c(1, 2)],
+  file = '',
+  rowlabel = 'State variables by parameter category',
+  caption = cap_val,
+  caption.loc = 'top',
+  size = 'scriptsize',
+  label = 'tab:inistrchg',
+  rowname = stts,
+  rgroup = unique(cats),
+  n.rgroup = as.numeric(table(cats)),
+  colheads = colnms,
+  rgroupTexCmd = NULL
+  )
+
 @
@@
 
-<<sensalltile, eval = T, echo = F, fig.height = 7, fig.width = 6, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
+<<sensalltile, eval = T, echo = F, fig.height = 6, fig.width = 3.5, out.width = '0.7\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
@@
 @
+
+% summary of initial/structural changes on parameter sensitivity
+<<inistrsumm, eval = T, fig.cap = 'Summaries of changes in parameter sensitivity values (L1, \\cref{l1}) from the default model conditions.
+Sensitivity was re-evaluated using initial conditions as seasonal means for April and September, and added structural complexity.
+Sensitivity is summarized as the minimum, median, and maximum for each state variable separated by parameter categories.
+Changes in average sensitivity from the default model conditions are in \\cref{tab:inistrchg}.', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
+
+# initial conditions
+data(ini_eval)
+data(struct_eval)
+
+to_eval <- lapply(ini_eval, function(x) x[[2]]) %>% 
+  c(., struct = list(struct_eval))
+
+eval_levs <- c('def', 'apr', 'sep', 'struct')
+eval_labs <- c('Default', 'Initial: April', 'Initial: September', 'Structure: complex')
+
+toplo_all <- sapply(1:length(to_eval), function(x) {
+
+  tmp <- reshape2::melt(to_eval[[x]], id.var = c('Parameter', 'error', 'Category'))
+  nms <- names(to_eval)[x]
+
+  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
+  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+
+  toplo <- mutate(tmp,
+      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
+      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
+      nms = nms
+    ) %>% 
+    rename(Sensitivity = error)
+
+  return(toplo)
+
+  }, simplify = F)
+toplo_all <- do.call('rbind', toplo_all)
+toplo_all <- mutate(toplo_all, nms = factor(nms, levels = eval_levs, labels = eval_labs))
+
+# summarize
+toplo_all <- group_by(toplo_all, Category, L1, nms) %>% 
+  summarise(
+    med_val = median(Sensitivity, na.rm = TRUE),
+    ave_val = mean(Sensitivity, na.rm = TRUE), 
+    min_val = quantile(Sensitivity, 0, na.rm = TRUE), 
+    max_val = quantile(Sensitivity, 1, na.rm = TRUE)
+  )
+
+pbase <- theme_minimal() + 
+  theme(
+    legend.position = 'top',
+    axis.text.x = element_text(size = 8), 
+    axis.line.x = element_line(),
+    axis.line.y = element_line(), 
+    # panel.grid.minor = element_blank(), 
+    # panel.grid.major = element_blank(),
+    axis.ticks.x = element_line(),
+    axis.ticks.y = element_line(),
+    axis.ticks.length = unit(.1, "cm")
+    )
+
+mycols <- RColorBrewer::brewer.pal(5, 'Spectral')
+names(mycols) <- cats
+fils<- scale_fill_manual(name = 'Category', values = mycols)
+cols <- scale_colour_manual(name = 'Category', values = mycols)
+
+ddge_wd <- 0.7
+ggplot(toplo_all, aes(x = L1)) + 
+  geom_errorbar(aes(ymin = min_val, ymax = max_val, group = Category), colour = 'black', width = 0, position = position_dodge(width = ddge_wd)) +
+  geom_point(aes(y = med_val, fill = Category), colour = 'black', pch = 21, position = position_dodge(width = ddge_wd), size = 3) + 
+  scale_y_continuous('Sensitivity', trans = 'log10') + 
+  scale_x_discrete('State variable') + 
+  facet_wrap( ~ nms, ncol = 1) +
+  cols +
+  fils + 
+  pbase
+@
+
 \clearpage
@@
 
+\clearpage
+
 %%
@@
 
-% effects of structural uncertainty
-<<streval, fig.cap = 'Effects of model structure on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = F, echo = F, warning = F, message = F>>=
-# structural
+% effects of changing initial and structural conditions
+<<inistreval, fig.cap = 'Effects of initial and structural conditions on parameter sensitivity.', fig.height = 7, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
+# initial conditions
+data(ini_eval)
 data(struct_eval)
 
-swtc_levs <- paste0('Which_quota', 1:length(struct_eval))
-swtc_labs <- paste0('Which quota: ', c('Droop', 'Nyholm', 'Flynn'))
-
-toplo_all <- lapply(struct_eval, function(x) {
-
-  tmp <- reshape2::melt(x[[2]], id.var = c('Parameter', 'error', 'Category'))
-  swtc <- paste0(names(x[[1]]), x[[1]])
+to_eval <- lapply(ini_eval, function(x) x[[2]]) %>% 
+  c(., struct = list(struct_eval))
+
+eval_levs <- c('def', 'apr', 'sep', 'struct')
+eval_labs <- c('Default', 'Initial: April', 'Initial: September', 'Structure: complex')
+
+toplo_all <- sapply(1:length(to_eval), function(x) {
+
+  tmp <- reshape2::melt(to_eval[[x]], id.var = c('Parameter', 'error', 'Category'))
+  nms <- names(to_eval)[x]
 
@@
       Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
-      swtc = as.character(swtc)
+      nms = nms
     ) %>% 
@@
 
-  })
+  }, simplify = F)
 toplo_all <- do.call('rbind', toplo_all)
-toplo_all <- mutate(toplo_all, swtc = factor(swtc, levels = swtc_levs, labels = swtc_labs))
+toplo_all <- mutate(toplo_all, nms = factor(nms, levels = eval_levs, labels = eval_labs))
 
@@
 
-pstr <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
+p <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
   geom_tile(colour = 'black') + 
@@
   scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
-  facet_grid(Category~swtc, scales = 'free_y', space = 'free') + 
+  facet_grid(Category~nms, scales = 'free_y', space = 'free') + 
   guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
 
-print(pstr)
-@
-
-% effects of initial conditions
-<<inieval, fig.cap = 'Effects of initial conditions on parameter sensitivity.', fig.height = 8, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
-# initial conditions
-data(ini_eval)
-
-ini_levs <- paste('Initial:', c('def', 'apr', 'sep'))
-ini_labs <- paste('Initial:', c('Default', 'April', 'September'))
-
-toplo_all <- sapply(1:length(ini_eval), function(x) {
-
-  tmp <- reshape2::melt(ini_eval[[x]][[2]], id.var = c('Parameter', 'error', 'Category'))
-  ini <- names(ini_eval)[x]
-
-  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
-  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
-
-  toplo <- mutate(tmp,
-      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
-      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
-      ini = paste('Initial:', ini)
-    ) %>% 
-    rename(Sensitivity = error)
-
-  return(toplo)
-
-  }, simplify = F)
-toplo_all <- do.call('rbind', toplo_all)
-toplo_all <- mutate(toplo_all, ini = factor(ini, levels = ini_levs, labels = ini_labs))
-
-pbase <- theme(
-  panel.grid.major = element_blank(), 
-  panel.grid.minor = element_blank(), 
-  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
-  axis.text.y = element_text(size = 6),
-  legend.position = 'top', 
-  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt'), 
-  strip.background = element_blank(), 
-  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5)
-  )
-
-pini <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
-  geom_tile(colour = 'black') + 
-  pbase +
-  scale_y_discrete('Parameter', 
-    expand = c(0, 0),
-    breaks = toplo_all$Parameter, 
-    labels = parse(text = toplo_all$Parameter)
-    ) + 
-  scale_x_discrete('State variable', expand = c(0, 0)) +
-  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
-  facet_grid(Category~ini, scales = 'free_y', space = 'free') + 
-  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
-
-print(pini)
+print(p)
 @

### 2016-09-27 ident_manu.tex
added better tables and figures for initial and structural analyses

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Sep 6 12:52:12 2016 -0500
+  \\ Version Date:   Fri Sep 23 17:24:42 2016 -0500
 	}
@@
 {\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$7.41\times 10^{-4}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.91\times 10^{-5}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.34\times 10^{-5}$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$7.51\times 10^{-4}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.92\times 10^{-5}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.39\times 10^{-5}$\tabularnewline
 \hline
@@
 {\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.06$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.05$\tabularnewline
 ~~mortality coefficient&\textit{mA}&$0.02$\tabularnewline
@@
 ~~phytoplankton carbon/cell&\textit{Qc}&$0.01$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$8.28\times 10^{-3}$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$8.15\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$6.93\times 10^{-3}$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.41\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$4.25\times 10^{-3}$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$4.2\times 10^{-3}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$4.19\times 10^{-3}$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$4.05\times 10^{-3}$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$8.36\times 10^{-3}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$8.12\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$6.94\times 10^{-3}$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$4.32\times 10^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$4.27\times 10^{-3}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$4.23\times 10^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$4.13\times 10^{-3}$\tabularnewline
 ~~half-saturation constant for P&\textit{Kp}&$2.9\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$3.03\times 10^{-4}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$1.4\times 10^{-7}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$2.77\times 10^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$8.34\times 10^{-8}$\tabularnewline
 \hline
@@
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.01$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.58\times 10^{-3}$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.19\times 10^{-3}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.89\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$9.48\times 10^{-5}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.63\times 10^{-5}$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$9.38\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.69\times 10^{-5}$\tabularnewline
 \hline
 {\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.1\times 10^{-3}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.59\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.11\times 10^{-3}$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.95\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.68\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$4.91\times 10^{-4}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$4.12\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.93\times 10^{-4}$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$4.99\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$4.17\times 10^{-4}$\tabularnewline
 \hline
@@
 % first heuristic, all states
-%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%
 \begin{table}[!tbp]
-{\footnotesize
+{\scriptsize
 \caption{Parameter identifiability (as $\gamma$, \cref{gameq}) by category for relevant state variables.
@@
 {Optics}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
-~~\footnotesize{\textit{astarOMA}}&$2$&$7.26$&$5.4$&-&$5.35$&-&$7.72$&$7.91$&-\tabularnewline
-~~\footnotesize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.81$\tabularnewline
-~~\footnotesize{\textit{astarOMA}}&$3$&-&-&$3.73$&-&-&-&-&$9.65$\tabularnewline
-~~\footnotesize{\textit{astarOMZ}}&$3$&$7.5$&$5.51$&-&$6.01$&-&$7.88$&$7.91$&-\tabularnewline
+~~\scriptsize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
+~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$5.36$&-&$7.78$&$7.87$&-\tabularnewline
+~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.73$\tabularnewline
+~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&-&$10.04$\tabularnewline
+~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$6.02$&-&$7.91$&$7.87$&-\tabularnewline
 \hline
 {Organic Matter}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
-~~\footnotesize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
-~~\footnotesize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
-~~\footnotesize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$13.44$\tabularnewline
-~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.4$&-\tabularnewline
-~~\footnotesize{\textit{KNH4}}&$2$&$4.04$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KNO3}}&$2$&-&-&-&-&$9.1$&-&-&-\tabularnewline
-~~\footnotesize{\textit{KstarO2}}&$2$&-&-&$1.06$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG1}}&$3$&$4.1$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG2}}&$3$&-&-&$6.01$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.78$\tabularnewline
-~~\footnotesize{\textit{KO2}}&$3$&-&-&-&-&-&$14.25$&$12.35$&-\tabularnewline
-~~\footnotesize{\textit{KstarO2}}&$3$&-&$1.28$&-&$1.99$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KG2}}&$4$&-&-&-&$11.17$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KGcdom}}&$4$&-&-&$6.08$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.5$\tabularnewline
-~~\footnotesize{\textit{KstarO2}}&$4$&$4.29$&-&-&-&-&$14.34$&$13.61$&-\tabularnewline
-~~\footnotesize{\textit{KGcdom}}&$5$&$4.41$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KO2}}&$5$&-&-&$8.44$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{nitmax}}&$6$&-&-&$10.12$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KNH4}}&$7$&-&-&$10.17$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{KNO3}}&$8$&-&-&$13.94$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
+~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
+~~\scriptsize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
+~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
+~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline
 \hline
 {Phytoplankton}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\footnotesize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
-~~\footnotesize{\textit{ediblevector(Z1)}}&$2$&$1.13$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{mA}}&$2$&-&-&$1.16$&$1.28$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{Qc}}&$2$&-&-&-&-&$3.38$&-&-&-\tabularnewline
-~~\footnotesize{\textit{umax}}&$2$&-&$1.09$&-&-&-&$1.18$&$1.18$&-\tabularnewline
-~~\footnotesize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$2.75$\tabularnewline
-~~\footnotesize{\textit{alpha}}&$3$&-&-&$1.43$&$1.98$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{ediblevector(Z1)}}&$3$&-&$2.14$&-&-&-&$3.22$&$2.87$&-\tabularnewline
-~~\footnotesize{\textit{umax}}&$3$&$1.23$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{alpha}}&$4$&$1.64$&$4.3$&-&-&-&-&$7.17$&-\tabularnewline
-~~\footnotesize{\textit{ediblevector(Z1)}}&$4$&-&-&$1.83$&$3.15$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{Qc}}&$4$&-&-&-&-&-&$5.2$&-&-\tabularnewline
-~~\footnotesize{\textit{alpha}}&$5$&-&-&-&-&-&$9.72$&-&-\tabularnewline
-~~\footnotesize{\textit{Qc}}&$5$&-&-&$3.18$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{vmaxN}}&$5$&$8$&$14.42$&-&-&-&-&$14.48$&-\tabularnewline
-~~\footnotesize{\textit{Athresh}}&$6$&$8.32$&-&-&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{respg}}&$6$&-&$14.56$&$3.65$&-&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{vmaxN}}&$7$&-&-&$4$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
+~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$2$&-&-&-&-&-&-&$1.21$&-\tabularnewline
+~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$7.45$\tabularnewline
+~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$5$&$8.14$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Athresh}}&$6$&$11.27$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{respg}}&$6$&-&-&$3.41$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$7$&-&-&$3.97$&-&-&-&-&-\tabularnewline
 \hline
 {Zooplankton}&&&&&&&&&\tabularnewline
-~~\footnotesize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
-~~\footnotesize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\footnotesize{\textit{ZKa}}&$2$&-&$3.48$&-&-&-&$5.38$&$4.15$&-\tabularnewline
-~~\footnotesize{\textit{ZQn}}&$2$&-&-&$2.38$&$3.84$&$5.97$&-&-&$4.1$\tabularnewline
-~~\footnotesize{\textit{Zm}}&$3$&-&-&$2.74$&-&-&-&-&$11.52$\tabularnewline
-~~\footnotesize{\textit{Zumax}}&$3$&-&-&-&$5.94$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{Zm}}&$4$&-&-&-&$6.9$&-&-&-&-\tabularnewline
-~~\footnotesize{\textit{Zumax}}&$4$&-&-&$3.59$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&-&-&$7.3$&$5.43$&-\tabularnewline
+~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
+~~\scriptsize{\textit{Zm}}&$3$&-&-&$4.57$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&$6.93$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zm}}&$4$&-&-&-&$11.86$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$4$&-&-&$5.2$&-&-&-&-&-\tabularnewline
 \hline
@@
 % second heuristic, all states
-%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
 \begin{table}[!tbp]
-{\footnotesize
+{\scriptsize
 \caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.
@@
 {Ammonium}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.17$\tabularnewline
-~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.88$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.16$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.9$\tabularnewline
 \hline
 {Chlorophyll}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
-~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.1$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
 \hline
 {Dissolved Oxygen}&&&\tabularnewline
-~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.27$\tabularnewline
-~~3&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$2.37$\tabularnewline
-~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.41$\tabularnewline
-~~5&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.54$\tabularnewline
-~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.9$\tabularnewline
-~~7&\footnotesize{\textit{Zm}}&$3$\textsuperscript{Z}&$4.92$\tabularnewline
-~~8&\footnotesize{\textit{Zumax}}&$4$\textsuperscript{Z}&$4.94$\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.17$\tabularnewline
+~~3&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$2.31$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.37$\tabularnewline
+~~5&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.69$\tabularnewline
+~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$4.91$\tabularnewline
+~~7&\scriptsize{\textit{Zm}}&$3$\textsuperscript{Z}&$6.73$\tabularnewline
+~~8&\scriptsize{\textit{Zumax}}&$4$\textsuperscript{Z}&$6.81$\tabularnewline
 \hline
 {Irradiance}&&&\tabularnewline
-~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$5.03$\tabularnewline
-~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.98$\tabularnewline
-~~4&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$8.27$\tabularnewline
-~~5&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$10.08$\tabularnewline
-~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$10.09$\tabularnewline
-~~7&\footnotesize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.83$\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$4.41$\tabularnewline
+~~3&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.54$\tabularnewline
+~~4&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$8.17$\tabularnewline
+~~5&\scriptsize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$9.44$\tabularnewline
+~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$9.66$\tabularnewline
+~~7&\scriptsize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.79$\tabularnewline
 \hline
 {Nitrate}&&&\tabularnewline
-~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$4.79$\tabularnewline
-~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$6.88$\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
 \hline
 {OM1}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$1.18$\tabularnewline
-~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$3.18$\tabularnewline
-~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.5$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.15$\tabularnewline
+~~3&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$3.87$\tabularnewline
 \hline
 {OM2}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
-~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.74$\tabularnewline
-~~4&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.86$\tabularnewline
-~~5&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$5.44$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
+~~3&\scriptsize{\textit{umax}}&$2$\textsuperscript{P}&$2.46$\tabularnewline
+~~4&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.91$\tabularnewline
 \hline
 {Phosphate}&&&\tabularnewline
-~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$4.9$\tabularnewline
-~~3&\footnotesize{\textit{vmaxP}}&$2$\textsuperscript{P}&$6.84$\tabularnewline
-~~4&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$14.13$\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$11.45$\tabularnewline
+~~3&\scriptsize{\textit{vmaxP}}&$2$\textsuperscript{P}&$11.48$\tabularnewline
+~~4&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$13.74$\tabularnewline
 \hline
@@
 % third heuristic, all states
-%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
 \begin{table}[!tbp]
-{\footnotesize
+{\scriptsize
 \caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.
@@
 {Ammonium}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.17$\tabularnewline
-~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.88$\tabularnewline
-~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$3.45$\tabularnewline
-~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.23$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$3.46$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$4.25$\tabularnewline
 \hline
 {Chlorophyll}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
-~~3&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.62$\tabularnewline
-~~4&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$3.25$\tabularnewline
-~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$5.91$\tabularnewline
-~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$5.92$\tabularnewline
-~~7&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$10.99$\tabularnewline
-~~8&\footnotesize{\textit{KG1}}&$2$\textsuperscript{OM}&$11.01$\tabularnewline
-~~9&\footnotesize{\textit{astarOMA}}&$2$\textsuperscript{O}&$11.32$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.18$\tabularnewline
+~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.62$\tabularnewline
+~~4&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$3.24$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$5.98$\tabularnewline
 \hline
 {Dissolved Oxygen}&&&\tabularnewline
-~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.27$\tabularnewline
-~~3&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.36$\tabularnewline
-~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$4.05$\tabularnewline
-~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.1$\tabularnewline
-~~6&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$4.4$\tabularnewline
-~~7&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$5.08$\tabularnewline
-~~8&\footnotesize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$5.87$\tabularnewline
-~~9&\footnotesize{\textit{astarOMZ}}&$2$\textsuperscript{O}&$6.08$\tabularnewline
-~~10&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$6.17$\tabularnewline
-~~11&\footnotesize{\textit{Zm}}&$3$\textsuperscript{Z}&$10.42$\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$2.17$\tabularnewline
+~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.29$\tabularnewline
+~~4&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.85$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$3.89$\tabularnewline
+~~6&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$4.42$\tabularnewline
+~~7&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$5.22$\tabularnewline
 \hline
 {Irradiance}&&&\tabularnewline
-~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$5.03$\tabularnewline
-~~3&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$5.05$\tabularnewline
-~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$5.12$\tabularnewline
-~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$7.6$\tabularnewline
-~~6&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$10.92$\tabularnewline
-~~7&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$10.94$\tabularnewline
-~~8&\footnotesize{\textit{KG1}}&$2$\textsuperscript{OM}&$10.94$\tabularnewline
-~~9&\footnotesize{\textit{astarOMA}}&$2$\textsuperscript{O}&$11.12$\tabularnewline
-~~10&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$12.29$\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$4.41$\tabularnewline
+~~3&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$4.5$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$4.5$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$6.9$\tabularnewline
+~~6&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$10.63$\tabularnewline
+~~7&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$11.21$\tabularnewline
+~~8&\scriptsize{\textit{KG1}}&$2$\textsubscript{OM}&$14.65$\tabularnewline
+~~9&\scriptsize{\textit{astarOMA}}&$2$\textsubscript{O}&$14.72$\tabularnewline
 \hline
 {Nitrate}&&&\tabularnewline
-~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$4.79$\tabularnewline
-~~3&\footnotesize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$6.71$\tabularnewline
-~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$7.63$\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
 \hline
 {OM1}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.15$\tabularnewline
-~~3&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$3.88$\tabularnewline
-~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$3.93$\tabularnewline
-~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$5.85$\tabularnewline
-~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$9.9$\tabularnewline
-~~7&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$10.05$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.15$\tabularnewline
+~~3&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.87$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$3.93$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$5.81$\tabularnewline
 \hline
 {OM2}&&&\tabularnewline
-~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
-~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.61$\tabularnewline
-~~4&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$3.4$\tabularnewline
-~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$4.52$\tabularnewline
-~~6&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$7.43$\tabularnewline
-~~7&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$7.62$\tabularnewline
-~~8&\footnotesize{\textit{KGcdom}}&$2$\textsuperscript{OM}&$12.42$\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$1.05$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.61$\tabularnewline
+~~4&\scriptsize{\textit{KG2}}&$1$\textsubscript{OM}&$3.39$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$4.46$\tabularnewline
+~~6&\scriptsize{\textit{umax}}&$2$\textsubscript{P}&$6.02$\tabularnewline
+~~7&\scriptsize{\textit{ZKa}}&$2$\textsubscript{Z}&$9.21$\tabularnewline
 \hline
 {Phosphate}&&&\tabularnewline
-~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
-~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$4.9$\tabularnewline
-~~3&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$5.63$\tabularnewline
-~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.55$\tabularnewline
-~~5&\footnotesize{\textit{astar490}}&$1$\textsuperscript{O}&$9.82$\tabularnewline
-~~6&\footnotesize{\textit{vmaxP}}&$2$\textsuperscript{P}&$11.26$\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$11.45$\tabularnewline
+~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$13.71$\tabularnewline
+~~4&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$14.64$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+
+\end{table}
+
+% change in sensitivity for different initial, structural conditions
+%latex.default(totab_all[, -c(1, 2)], file = "", rowlabel = "State variables by parameter category",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:inistrchg", rowname = stts, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%
+\begin{table}[!tbp]
+{\scriptsize
+\caption{Changes in mean sensitivity of state variables by parameter categories to different initial conditions and changes in structural components of the model.
+Changes show the difference in average sensitivity from results using the default model setup.
+Sensitivities are based on average $L1$ (see \cref{l1}) values of the state variables to changes in parameters in each parameter category.
+Increases in average sensitivity are in bold.
+Medians and ranges of sensitivity values for the different conditions are shown in \cref{fig:inistrsumm}.\label{tab:inistrchg}}
+\begin{center}
+\begin{tabular}{lllll}
+\hline\hline
+\multicolumn{1}{l}{State variables by parameter category}&\multicolumn{1}{c}{Default sensitivity}&\multicolumn{1}{c}{Initial: April}&\multicolumn{1}{c}{Initial: September}&\multicolumn{1}{c}{Structure: complex}\tabularnewline
+\hline
+{Optics}&&&&\tabularnewline
+~~Ammonium&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Chlorophyll&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Dissolved Oxygen&$2.81\times 10^{-4}$&$\bm{2.11\times 10^{-4}}$&$\bm{1.46\times 10^{-4}}$&$\bm{1.93\times 10^{-4}}$\tabularnewline
+~~Irradiance&$0.01$&$-0$&$-0$&$-0$\tabularnewline
+~~Nitrate&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~OM1&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~OM2&$0.02$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Phosphate&$0$&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline
+\hline
+{Organic Matter}&&&&\tabularnewline
+~~Ammonium&$0.31$&$-0.08$&$-0.04$&$\bm{2.22\times 10^{-4}}$\tabularnewline
+~~Chlorophyll&$0.02$&$-0.12$&$-0.14$&$\bm{0.01}$\tabularnewline
+~~Dissolved Oxygen&$0$&$\bm{6.75\times 10^{-4}}$&$-2.32\times 10^{-4}$&$\bm{0}$\tabularnewline
+~~Irradiance&$0.01$&$-0.01$&$-0.01$&$\bm{2.99\times 10^{-4}}$\tabularnewline
+~~Nitrate&$0.12$&$-0.06$&$-0.09$&$\bm{0.1}$\tabularnewline
+~~OM1&$0.13$&$-0.15$&$-0.12$&$-0.04$\tabularnewline
+~~OM2&$0.14$&$-0.07$&$-0.17$&$-0.05$\tabularnewline
+~~Phosphate&$0.03$&$-0.04$&$-0.06$&$\bm{0.02}$\tabularnewline
+\hline
+{Phytoplankton}&&&&\tabularnewline
+~~Ammonium&$0.8$&$\bm{0.02}$&$-0.3$&$-65.98$\tabularnewline
+~~Chlorophyll&$1.14$&$-1.23$&$-4.38$&$-104.24$\tabularnewline
+~~Dissolved Oxygen&$0.01$&$\bm{4.58\times 10^{-4}}$&$-0$&$-3.44\times 10^{-4}$\tabularnewline
+~~Irradiance&$0.02$&$\bm{0}$&$-0$&$-0.01$\tabularnewline
+~~Nitrate&$0.74$&$\bm{0.43}$&$\bm{0.45}$&$\bm{0.64}$\tabularnewline
+~~OM1&$0.76$&$-0.17$&$-0.46$&$-55.11$\tabularnewline
+~~OM2&$1.28$&$-0.34$&$-1.15$&$-128.93$\tabularnewline
+~~Phosphate&$0.17$&$-0.03$&$-0.05$&$\bm{0.14}$\tabularnewline
+\hline
+{Temperature}&&&&\tabularnewline
+~~Ammonium&$0.79$&$\bm{0.69}$&$\bm{0.69}$&$-272.31$\tabularnewline
+~~Chlorophyll&$0.6$&$\bm{0.47}$&$\bm{0.45}$&$-114.51$\tabularnewline
+~~Dissolved Oxygen&$0.02$&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
+~~Irradiance&$0.03$&$\bm{0.02}$&$\bm{0.02}$&$-0.01$\tabularnewline
+~~Nitrate&$0.3$&$\bm{0.15}$&$\bm{0.16}$&$\bm{0.19}$\tabularnewline
+~~OM1&$0.86$&$\bm{0.68}$&$\bm{0.69}$&$-215.17$\tabularnewline
+~~OM2&$1.48$&$\bm{1.21}$&$\bm{1.2}$&$-900.26$\tabularnewline
+~~Phosphate&$0.16$&$\bm{0.11}$&$\bm{0.09}$&$\bm{0.11}$\tabularnewline
+\hline
+{Zooplankton}&&&&\tabularnewline
+~~Ammonium&$0.47$&$\bm{0.45}$&$\bm{0.44}$&$\bm{0.16}$\tabularnewline
+~~Chlorophyll&$0.39$&$\bm{0.26}$&$\bm{0.23}$&$\bm{0.2}$\tabularnewline
+~~Dissolved Oxygen&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Irradiance&$0.03$&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
+~~Nitrate&$1.06$&$\bm{1.02}$&$\bm{1.02}$&$\bm{0.98}$\tabularnewline
+~~OM1&$0.37$&$\bm{0.27}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
+~~OM2&$0.39$&$\bm{0.3}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
+~~Phosphate&$0.31$&$\bm{0.19}$&$\bm{0.17}$&$\bm{0.27}$\tabularnewline
 \hline
@@
 
-{\centering \includegraphics[width=\textwidth]{figs/sensalltile-1}
+{\centering \includegraphics[width=0.7\textwidth]{figs/sensalltile-1}
 
@@
 Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
+\end{figure}
+
+% summary of initial/structural changes on parameter sensitivity
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/inistrsumm-1}
+
+}
+
+\caption{Summaries of changes in parameter sensitivity values (L1, \cref{l1}) from the default model conditions.
+Sensitivity was re-evaluated using initial conditions as seasonal means for April and September, and added structural complexity.
+Sensitivity is summarized as the minimum, median, and maximum for each state variable separated by parameter categories.
+Changes in average sensitivity from the default model conditions are in \cref{tab:inistrchg}.}\label{fig:inistrsumm}
 \end{figure}
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.61\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.48\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.63\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.5\times 10^{-3}$\tabularnewline
 \hline
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.78$\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline
 \hline
@@
 ~~mortality coefficient&\textit{mA}&$8.49$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$1.31$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.75$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.59$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$1.32$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.65$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.6$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.46$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.28$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.29$\tabularnewline
 ~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
@@
 ~~half-saturation constant for P&\textit{Kp}&$0.14$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.13$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.14$\tabularnewline
 ~~minimum N cell-quota&\textit{QminN}&$0.1$\tabularnewline
 ~~P-uptake rate measured at umax&\textit{vmaxP}&$0.1$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.05$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.03$\tabularnewline
 ~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$1.97\times 10^{-6}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$2.24\times 10^{-6}$\tabularnewline
 \hline
 {\bfseries Zooplankton}&&\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$1.41$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$1.42$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.76$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.59$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.56$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.48$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.29$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.74$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.62$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.5$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.3$\tabularnewline
 ~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.22$\tabularnewline
@@
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$1.07\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$1.93\times 10^{-4}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$1.44\times 10^{-4}$\tabularnewline
 \hline
 {\bfseries Organic Matter}&&\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.53$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.54$\tabularnewline
 ~~NH4 rate constant for nitrification&\textit{KNH4}&$0.66$\tabularnewline
 ~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.07$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.07$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.06$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.06$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.05$\tabularnewline
 ~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.03$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$5.42\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
 \hline
@@
 ~~mortality coefficient&\textit{mA}&$13.94$\tabularnewline
-~~maximum growth rate&\textit{umax}&$1$\tabularnewline
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.95$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.85$\tabularnewline
 ~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.62$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.54$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.53$\tabularnewline
 ~~phytoplankton growth respiration coefficient&\textit{respg}&$0.26$\tabularnewline
@@
 ~~minimum N cell-quota&\textit{QminN}&$0.07$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.03$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$0.02$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$1.57\times 10^{-6}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.02$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$1.38\times 10^{-6}$\tabularnewline
 \hline
 {\bfseries Zooplankton}&&\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$1.03$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.95$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$1.02$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.85$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.57$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.54$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.52$\tabularnewline
 ~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.24$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.23$\tabularnewline
 ~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
@@
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$1.29\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$1.01\times 10^{-4}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$7.55\times 10^{-5}$\tabularnewline
 \hline
 {\bfseries Organic Matter}&&\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.08$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
 ~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.03$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.02$\tabularnewline
 ~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.51\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$9.86\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$3.23\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$2.86\times 10^{-5}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.01$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.35\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$3.4\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$2.97\times 10^{-5}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.46\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.47\times 10^{-3}$\tabularnewline
 ~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.34\times 10^{-3}$\tabularnewline
@@
 {\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.13$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.09$\tabularnewline
 ~~mortality coefficient&\textit{mA}&$0.05$\tabularnewline
@@
 ~~half-saturation constant for P&\textit{Kp}&$0.01$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$9.49\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$9.4\times 10^{-3}$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$8.15\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$5.78\times 10^{-3}$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$4.45\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$1.04\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$2.03\times 10^{-7}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$9.48\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$9.38\times 10^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$8.1\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$5.75\times 10^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$3.78\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$9.81\times 10^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$1.92\times 10^{-7}$\tabularnewline
 \hline
 {\bfseries Zooplankton}&&\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.17$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.13$\tabularnewline
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$0.06$\tabularnewline
@@
 ~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.72\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$9.29\times 10^{-5}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$2.11\times 10^{-5}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$9.34\times 10^{-5}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$1.99\times 10^{-5}$\tabularnewline
 \hline
@@
 ~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$3.95\times 10^{-3}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$1.23\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$9.87\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.61\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$4.94\times 10^{-5}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.59\times 10^{-6}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1.38\times 10^{-6}$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2G&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.2\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.54\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.72\times 10^{-6}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1.48\times 10^{-6}$\tabularnewline
 \hline
@@
 {\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.54\times 10^{-3}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.43\times 10^{-3}$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.27\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.19\times 10^{-3}$\tabularnewline
 \hline
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.34$\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline
 \hline
 {\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$49.33$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$1.54$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$1.1$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.37$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.31$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.26$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.22$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.13$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.13$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.13$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.12$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$0.11$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.08$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$9.1\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$4.01\times 10^{-7}$\tabularnewline
+~~maximum growth rate&\textit{umax}&$8.49$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.89$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.7$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.33$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.27$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.2$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$0.19$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$0.13$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.11$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.1$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.09$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$0.09$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.07$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$7.06\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.67\times 10^{-7}$\tabularnewline
 \hline
 {\bfseries Zooplankton}&&\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$34.61$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$2.21$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$1.1$\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$0.38$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.35$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.29$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.21$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$4.7\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.05\times 10^{-3}$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$7.59$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$1.17$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.7$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$0.34$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.26$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.25$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.8\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$8.59\times 10^{-4}$\tabularnewline
 \hline
 {\bfseries Organic Matter}&&\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$1.27$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$0.05$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.78$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$0.07$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.04$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.03$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.03$\tabularnewline
+~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.02$\tabularnewline
 ~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$0.01$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$0.01$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$9.96\times 10^{-3}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$9.87\times 10^{-3}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.72\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.73\times 10^{-3}$\tabularnewline
 ~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.49\times 10^{-3}$\tabularnewline
@@
 {\bfseries Phytoplankton}&&\tabularnewline
-~~mortality coefficient&\textit{mA}&$7.23$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.99$\tabularnewline
+~~mortality coefficient&\textit{mA}&$7.22$\tabularnewline
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.9$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.68$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.89$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.67$\tabularnewline
 ~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.67$\tabularnewline
@@
 ~~coefficient for non-limiting nutrient&\textit{aN}&$0.14$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.12$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.11$\tabularnewline
 ~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
@@
 ~~maximum growth rate of zooplankton&\textit{Zumax}&$0.96$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.85$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.79$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.54$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.51$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.49$\tabularnewline
 ~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.39$\tabularnewline
@@
 ~~zooplankton carbon/individual&\textit{ZQc}&$9.64\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.05\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.06\times 10^{-3}$\tabularnewline
 \hline
@@
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.02$\tabularnewline
 ~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$2.47\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$4.74\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$4.25\times 10^{-5}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$6.98\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$6.41\times 10^{-5}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$2.47\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$2.05\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$2.48\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$2.04\times 10^{-3}$\tabularnewline
 \hline
@@
 {\bfseries Phytoplankton}&&\tabularnewline
-~~mortality coefficient&\textit{mA}&$14.26$\tabularnewline
-~~maximum growth rate&\textit{umax}&$1.24$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.95$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.86$\tabularnewline
+~~mortality coefficient&\textit{mA}&$14.25$\tabularnewline
+~~maximum growth rate&\textit{umax}&$1.11$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.94$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.86$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.68$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.85$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$0.67$\tabularnewline
 ~~phytoplankton growth respiration coefficient&\textit{respg}&$0.36$\tabularnewline
@@
 ~~minimum N cell-quota&\textit{QminN}&$0.24$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.23$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.21$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.22$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$0.2$\tabularnewline
 ~~P-uptake rate measured at umax&\textit{vmaxP}&$0.14$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.11$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
 ~~half-saturation constant for N&\textit{Kn}&$0.02$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$4.36\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$4.37\times 10^{-3}$\tabularnewline
 \hline
 {\bfseries Zooplankton}&&\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$1.02$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.98$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$1.01$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$0.88$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.58$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.57$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.42$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.54$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
 ~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
@@
 ~~zooplankton carbon/individual&\textit{ZQc}&$0.04$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.68\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.69\times 10^{-3}$\tabularnewline
 \hline
@@
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.04$\tabularnewline
 ~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.04$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.98\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$6.14\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$5.23\times 10^{-5}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$8.44\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$7.41\times 10^{-5}$\tabularnewline
 \hline
@@
 {\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$9\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$5.36\times 10^{-4}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.79\times 10^{-4}$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$9.01\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$5.21\times 10^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$5.13\times 10^{-4}$\tabularnewline
 \hline
@@
 {\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$1.06$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.58$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.78$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$0.59$\tabularnewline
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$\tabularnewline
@@
 ~~half-saturation constant for P&\textit{Kp}&$0.03$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.01$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$7.3\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$9.82\times 10^{-7}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$6.97\times 10^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$6.68\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$8.21\times 10^{-7}$\tabularnewline
 \hline
 {\bfseries Zooplankton}&&\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$1.8$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.51$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.47$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$0.5$\tabularnewline
 ~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.35$\tabularnewline
@@
 ~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$6.39\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.93\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$6.43\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.38\times 10^{-5}$\tabularnewline
 \hline
@@
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.01$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$9.96\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$7.66\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.75\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1.71\times 10^{-5}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.29\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$2.7\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$2.64\times 10^{-5}$\tabularnewline
 \hline
@@
 \end{table}
+
+\clearpage
 
@@
 
-% effects of structural uncertainty
-
-% effects of initial conditions
+% effects of changing initial and structural conditions
 \begin{figure}[!ht]
 
-{\centering \includegraphics[width=\textwidth]{figs/inieval-1}
+{\centering \includegraphics[width=\textwidth]{figs/inistreval-1}
 
@@
 
-\caption[Effects of initial conditions on parameter sensitivity]{Effects of initial conditions on parameter sensitivity.}\label{fig:inieval}
+\caption[Effects of initial and structural conditions on parameter sensitivity]{Effects of initial and structural conditions on parameter sensitivity.}\label{fig:inistreval}
 \end{figure}

### 2016-09-28 ident_manu.Rnw
table/figure revisions, about to look at identbox for all state variables

@@
   n.rgroup = as.numeric(table(cats)),
-  colheads = colnms,
-  rgroupTexCmd = NULL
+  colheads = colnms
   )
@@
   n.rgroup = as.numeric(table(stts)),
-  colheads = colnms,
-  rgroupTexCmd = NULL
+  colheads = colnms
   )
@@
 stts<- totab_all$L1
-cap_val<- 'Changes in mean sensitivity of state variables by parameter categories to different initial conditions and changes in structural components of the model.
+cap_val<- 'Changes in mean sensitivity of state variables by parameter categories to different initial conditions and structural components of the model.
 Changes show the difference in average sensitivity from results using the default model setup.
@@
   colheads = colnms,
-  rgroupTexCmd = NULL
+  cgroup = c('', 'Change'),
+  n.cgroup = c(1, 3)
   )
@@
 The temperature category is not shown because \\ac{do} was sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 7, fig.width = 8, echo = F, cache = TRUE>>=
+
 # identifiability by category (all parameters with >0 L1) 
@@
 catnms <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Zooplankton')
-topnms <- paste0('top', 1:4)
+toplevs <- paste0('top', 1:4)
+toplabs <- paste('Top', 1:4)
 tmpcat <- cat_ident_all[['O2']] %>% 
@@
 tmptop <- top_ident_all[['O2']] %>% 
-  .[names(.) %in% topnms]
+  .[names(.) %in% toplevs]
 
@@
 
+cols <- RColorBrewer::brewer.pal(11, 'Spectral')
+lncol <- 'darkgrey'
+sz <- 2
+
 p1 <- ggplot(toplo, aes(x = N, group = N)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
-  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
-  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
+  geom_point(aes(y = ave, shape = 'Ave'), fill = cols[5], colour = lncol, size = sz) + 
+  geom_point(aes(y = med, shape = 'Med'), fill = cols[3], colour = lncol, size = sz) + 
+  scale_shape_manual(values = c(21, 24)) + 
   facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
@@
   select(N, coll, L1) %>% 
-  mutate(L1 = factor(L1, levels = topnms, labels = topnms)) %>% 
+  mutate(L1 = factor(L1, levels = toplevs, labels = toplabs)) %>% 
   rename(npercat = L1) %>% 
@@
 p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
-  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
-  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
-  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
+  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
+  geom_point(aes(y = ave, shape = 'Ave', fill = 'Ave'), colour = lncol, size = sz) + 
+  geom_point(aes(y = med, shape = 'Med', fill = 'Med'), colour = lncol, size = sz) + 
+  scale_shape_manual(name = '', labels = c('Ave', 'Med'), values = c(21, 24)) + 
+  scale_fill_manual(name = '', labels = c('Ave', 'Med'), values = cols[c(5, 3)]) +
   facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
@@
   theme_minimal() + 
-  scale_fill_brewer(palette = 'Greys') + 
+  scale_fill_brewer(palette = 'Spectral') + 
   scale_y_continuous('Identifiability', trans = 'log', breaks = c(0.1, 1, 10, 100, 1000)) +

### 2016-09-28 ident_manu.tex
table/figure revisions, about to look at identbox for all state variables

@@
   \vspace{1in} 
-  \\ Version Date:   Fri Sep 23 17:24:42 2016 -0500
+  \\ Version Date:   Tue Sep 27 17:40:51 2016 -0500
 	}
@@
 % first heuristic, all states
-%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms)%
 \begin{table}[!tbp]
@@
 \hline
-{Optics}&&&&&&&&&\tabularnewline
+{\bfseries Optics}&&&&&&&&&\tabularnewline
 ~~\scriptsize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
@@
 \hline
-{Organic Matter}&&&&&&&&&\tabularnewline
+{\bfseries Organic Matter}&&&&&&&&&\tabularnewline
 ~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
@@
 \hline
-{Phytoplankton}&&&&&&&&&\tabularnewline
+{\bfseries Phytoplankton}&&&&&&&&&\tabularnewline
 ~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
@@
 \hline
-{Zooplankton}&&&&&&&&&\tabularnewline
+{\bfseries Zooplankton}&&&&&&&&&\tabularnewline
 ~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
@@
 % second heuristic, all states
-%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms)%
 \begin{table}[!tbp]
@@
 \hline
-{Ammonium}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.16$\tabularnewline
-~~3&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.9$\tabularnewline
-\hline
-{Chlorophyll}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
-\hline
-{Dissolved Oxygen}&&&\tabularnewline
-~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.17$\tabularnewline
-~~3&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$2.31$\tabularnewline
-~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.37$\tabularnewline
-~~5&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.69$\tabularnewline
-~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$4.91$\tabularnewline
-~~7&\scriptsize{\textit{Zm}}&$3$\textsuperscript{Z}&$6.73$\tabularnewline
-~~8&\scriptsize{\textit{Zumax}}&$4$\textsuperscript{Z}&$6.81$\tabularnewline
-\hline
-{Irradiance}&&&\tabularnewline
-~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
-~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$4.41$\tabularnewline
-~~3&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.54$\tabularnewline
-~~4&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$8.17$\tabularnewline
-~~5&\scriptsize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$9.44$\tabularnewline
-~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$9.66$\tabularnewline
-~~7&\scriptsize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.79$\tabularnewline
-\hline
-{Nitrate}&&&\tabularnewline
-~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
-\hline
-{OM1}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.15$\tabularnewline
-~~3&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$3.87$\tabularnewline
-\hline
-{OM2}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
-~~3&\scriptsize{\textit{umax}}&$2$\textsuperscript{P}&$2.46$\tabularnewline
-~~4&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.91$\tabularnewline
-\hline
-{Phosphate}&&&\tabularnewline
-~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
-~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$11.45$\tabularnewline
-~~3&\scriptsize{\textit{vmaxP}}&$2$\textsuperscript{P}&$11.48$\tabularnewline
-~~4&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$13.74$\tabularnewline
+{\bfseries Ammonium}&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
+\hline
+{\bfseries Chlorophyll}&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.18$\tabularnewline
+\hline
+{\bfseries Dissolved Oxygen}&&&\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$2.17$\tabularnewline
+~~3&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$2.31$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.37$\tabularnewline
+~~5&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$4.69$\tabularnewline
+~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$4.91$\tabularnewline
+~~7&\scriptsize{\textit{Zm}}&$3$\textsubscript{Z}&$6.73$\tabularnewline
+~~8&\scriptsize{\textit{Zumax}}&$4$\textsubscript{Z}&$6.81$\tabularnewline
+\hline
+{\bfseries Irradiance}&&&\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$4.41$\tabularnewline
+~~3&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$7.54$\tabularnewline
+~~4&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$8.17$\tabularnewline
+~~5&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$9.44$\tabularnewline
+~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$9.66$\tabularnewline
+~~7&\scriptsize{\textit{Zumax}}&$3$\textsubscript{Z}&$10.79$\tabularnewline
+\hline
+{\bfseries Nitrate}&&&\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
+\hline
+{\bfseries OM1}&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.15$\tabularnewline
+~~3&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.87$\tabularnewline
+\hline
+{\bfseries OM2}&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$1.05$\tabularnewline
+~~3&\scriptsize{\textit{umax}}&$2$\textsubscript{P}&$2.46$\tabularnewline
+~~4&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.91$\tabularnewline
+\hline
+{\bfseries Phosphate}&&&\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$11.45$\tabularnewline
+~~3&\scriptsize{\textit{vmaxP}}&$2$\textsubscript{P}&$11.48$\tabularnewline
+~~4&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$13.74$\tabularnewline
 \hline
@@
 % third heuristic, all states
-%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms)%
 \begin{table}[!tbp]
@@
 \hline
-{Ammonium}&&&\tabularnewline
+{\bfseries Ammonium}&&&\tabularnewline
 ~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
@@
 \hline
-{Chlorophyll}&&&\tabularnewline
+{\bfseries Chlorophyll}&&&\tabularnewline
 ~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
@@
 \hline
-{Dissolved Oxygen}&&&\tabularnewline
+{\bfseries Dissolved Oxygen}&&&\tabularnewline
 ~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
@@
 \hline
-{Irradiance}&&&\tabularnewline
+{\bfseries Irradiance}&&&\tabularnewline
 ~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
@@
 \hline
-{Nitrate}&&&\tabularnewline
+{\bfseries Nitrate}&&&\tabularnewline
 ~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
 \hline
-{OM1}&&&\tabularnewline
+{\bfseries OM1}&&&\tabularnewline
 ~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
@@
 \hline
-{OM2}&&&\tabularnewline
+{\bfseries OM2}&&&\tabularnewline
 ~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
@@
 \hline
-{Phosphate}&&&\tabularnewline
+{\bfseries Phosphate}&&&\tabularnewline
 ~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
@@
 % change in sensitivity for different initial, structural conditions
-%latex.default(totab_all[, -c(1, 2)], file = "", rowlabel = "State variables by parameter category",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:inistrchg", rowname = stts, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%
+%latex.default(totab_all[, -c(1, 2)], file = "", rowlabel = "State variables by parameter category",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:inistrchg", rowname = stts, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, cgroup = c("",         "Change"), n.cgroup = c(1, 3))%
 \begin{table}[!tbp]
 {\scriptsize
-\caption{Changes in mean sensitivity of state variables by parameter categories to different initial conditions and changes in structural components of the model.
+\caption{Changes in mean sensitivity of state variables by parameter categories to different initial conditions and structural components of the model.
 Changes show the difference in average sensitivity from results using the default model setup.
@@
 \begin{center}
-\begin{tabular}{lllll}
+\begin{tabular}{llclll}
 \hline\hline
-\multicolumn{1}{l}{State variables by parameter category}&\multicolumn{1}{c}{Default sensitivity}&\multicolumn{1}{c}{Initial: April}&\multicolumn{1}{c}{Initial: September}&\multicolumn{1}{c}{Structure: complex}\tabularnewline
-\hline
-{Optics}&&&&\tabularnewline
-~~Ammonium&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Chlorophyll&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Dissolved Oxygen&$2.81\times 10^{-4}$&$\bm{2.11\times 10^{-4}}$&$\bm{1.46\times 10^{-4}}$&$\bm{1.93\times 10^{-4}}$\tabularnewline
-~~Irradiance&$0.01$&$-0$&$-0$&$-0$\tabularnewline
-~~Nitrate&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~OM1&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~OM2&$0.02$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Phosphate&$0$&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline
-\hline
-{Organic Matter}&&&&\tabularnewline
-~~Ammonium&$0.31$&$-0.08$&$-0.04$&$\bm{2.22\times 10^{-4}}$\tabularnewline
-~~Chlorophyll&$0.02$&$-0.12$&$-0.14$&$\bm{0.01}$\tabularnewline
-~~Dissolved Oxygen&$0$&$\bm{6.75\times 10^{-4}}$&$-2.32\times 10^{-4}$&$\bm{0}$\tabularnewline
-~~Irradiance&$0.01$&$-0.01$&$-0.01$&$\bm{2.99\times 10^{-4}}$\tabularnewline
-~~Nitrate&$0.12$&$-0.06$&$-0.09$&$\bm{0.1}$\tabularnewline
-~~OM1&$0.13$&$-0.15$&$-0.12$&$-0.04$\tabularnewline
-~~OM2&$0.14$&$-0.07$&$-0.17$&$-0.05$\tabularnewline
-~~Phosphate&$0.03$&$-0.04$&$-0.06$&$\bm{0.02}$\tabularnewline
-\hline
-{Phytoplankton}&&&&\tabularnewline
-~~Ammonium&$0.8$&$\bm{0.02}$&$-0.3$&$-65.98$\tabularnewline
-~~Chlorophyll&$1.14$&$-1.23$&$-4.38$&$-104.24$\tabularnewline
-~~Dissolved Oxygen&$0.01$&$\bm{4.58\times 10^{-4}}$&$-0$&$-3.44\times 10^{-4}$\tabularnewline
-~~Irradiance&$0.02$&$\bm{0}$&$-0$&$-0.01$\tabularnewline
-~~Nitrate&$0.74$&$\bm{0.43}$&$\bm{0.45}$&$\bm{0.64}$\tabularnewline
-~~OM1&$0.76$&$-0.17$&$-0.46$&$-55.11$\tabularnewline
-~~OM2&$1.28$&$-0.34$&$-1.15$&$-128.93$\tabularnewline
-~~Phosphate&$0.17$&$-0.03$&$-0.05$&$\bm{0.14}$\tabularnewline
-\hline
-{Temperature}&&&&\tabularnewline
-~~Ammonium&$0.79$&$\bm{0.69}$&$\bm{0.69}$&$-272.31$\tabularnewline
-~~Chlorophyll&$0.6$&$\bm{0.47}$&$\bm{0.45}$&$-114.51$\tabularnewline
-~~Dissolved Oxygen&$0.02$&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
-~~Irradiance&$0.03$&$\bm{0.02}$&$\bm{0.02}$&$-0.01$\tabularnewline
-~~Nitrate&$0.3$&$\bm{0.15}$&$\bm{0.16}$&$\bm{0.19}$\tabularnewline
-~~OM1&$0.86$&$\bm{0.68}$&$\bm{0.69}$&$-215.17$\tabularnewline
-~~OM2&$1.48$&$\bm{1.21}$&$\bm{1.2}$&$-900.26$\tabularnewline
-~~Phosphate&$0.16$&$\bm{0.11}$&$\bm{0.09}$&$\bm{0.11}$\tabularnewline
-\hline
-{Zooplankton}&&&&\tabularnewline
-~~Ammonium&$0.47$&$\bm{0.45}$&$\bm{0.44}$&$\bm{0.16}$\tabularnewline
-~~Chlorophyll&$0.39$&$\bm{0.26}$&$\bm{0.23}$&$\bm{0.2}$\tabularnewline
-~~Dissolved Oxygen&$0.01$&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Irradiance&$0.03$&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
-~~Nitrate&$1.06$&$\bm{1.02}$&$\bm{1.02}$&$\bm{0.98}$\tabularnewline
-~~OM1&$0.37$&$\bm{0.27}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
-~~OM2&$0.39$&$\bm{0.3}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
-~~Phosphate&$0.31$&$\bm{0.19}$&$\bm{0.17}$&$\bm{0.27}$\tabularnewline
+\multicolumn{1}{l}{\bfseries State variables by parameter category}&\multicolumn{1}{c}{\bfseries }&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Change}\tabularnewline
+\cline{4-6}
+\multicolumn{1}{l}{}&\multicolumn{1}{c}{Default sensitivity}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Initial: April}&\multicolumn{1}{c}{Initial: September}&\multicolumn{1}{c}{Structure: complex}\tabularnewline
+\hline
+{\bfseries Optics}&&&&&\tabularnewline
+~~Ammonium&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Chlorophyll&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Dissolved Oxygen&$2.81\times 10^{-4}$&&$\bm{2.11\times 10^{-4}}$&$\bm{1.46\times 10^{-4}}$&$\bm{1.93\times 10^{-4}}$\tabularnewline
+~~Irradiance&$0.01$&&$-0$&$-0$&$-0$\tabularnewline
+~~Nitrate&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~OM1&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~OM2&$0.02$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Phosphate&$0$&&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&&&\tabularnewline
+~~Ammonium&$0.31$&&$-0.08$&$-0.04$&$\bm{2.22\times 10^{-4}}$\tabularnewline
+~~Chlorophyll&$0.02$&&$-0.12$&$-0.14$&$\bm{0.01}$\tabularnewline
+~~Dissolved Oxygen&$0$&&$\bm{6.75\times 10^{-4}}$&$-2.32\times 10^{-4}$&$\bm{0}$\tabularnewline
+~~Irradiance&$0.01$&&$-0.01$&$-0.01$&$\bm{2.99\times 10^{-4}}$\tabularnewline
+~~Nitrate&$0.12$&&$-0.06$&$-0.09$&$\bm{0.1}$\tabularnewline
+~~OM1&$0.13$&&$-0.15$&$-0.12$&$-0.04$\tabularnewline
+~~OM2&$0.14$&&$-0.07$&$-0.17$&$-0.05$\tabularnewline
+~~Phosphate&$0.03$&&$-0.04$&$-0.06$&$\bm{0.02}$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&&&\tabularnewline
+~~Ammonium&$0.8$&&$\bm{0.02}$&$-0.3$&$-65.98$\tabularnewline
+~~Chlorophyll&$1.14$&&$-1.23$&$-4.38$&$-104.24$\tabularnewline
+~~Dissolved Oxygen&$0.01$&&$\bm{4.58\times 10^{-4}}$&$-0$&$-3.44\times 10^{-4}$\tabularnewline
+~~Irradiance&$0.02$&&$\bm{0}$&$-0$&$-0.01$\tabularnewline
+~~Nitrate&$0.74$&&$\bm{0.43}$&$\bm{0.45}$&$\bm{0.64}$\tabularnewline
+~~OM1&$0.76$&&$-0.17$&$-0.46$&$-55.11$\tabularnewline
+~~OM2&$1.28$&&$-0.34$&$-1.15$&$-128.93$\tabularnewline
+~~Phosphate&$0.17$&&$-0.03$&$-0.05$&$\bm{0.14}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&&&\tabularnewline
+~~Ammonium&$0.79$&&$\bm{0.69}$&$\bm{0.69}$&$-272.31$\tabularnewline
+~~Chlorophyll&$0.6$&&$\bm{0.47}$&$\bm{0.45}$&$-114.51$\tabularnewline
+~~Dissolved Oxygen&$0.02$&&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
+~~Irradiance&$0.03$&&$\bm{0.02}$&$\bm{0.02}$&$-0.01$\tabularnewline
+~~Nitrate&$0.3$&&$\bm{0.15}$&$\bm{0.16}$&$\bm{0.19}$\tabularnewline
+~~OM1&$0.86$&&$\bm{0.68}$&$\bm{0.69}$&$-215.17$\tabularnewline
+~~OM2&$1.48$&&$\bm{1.21}$&$\bm{1.2}$&$-900.26$\tabularnewline
+~~Phosphate&$0.16$&&$\bm{0.11}$&$\bm{0.09}$&$\bm{0.11}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&&&\tabularnewline
+~~Ammonium&$0.47$&&$\bm{0.45}$&$\bm{0.44}$&$\bm{0.16}$\tabularnewline
+~~Chlorophyll&$0.39$&&$\bm{0.26}$&$\bm{0.23}$&$\bm{0.2}$\tabularnewline
+~~Dissolved Oxygen&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
+~~Irradiance&$0.03$&&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
+~~Nitrate&$1.06$&&$\bm{1.02}$&$\bm{1.02}$&$\bm{0.98}$\tabularnewline
+~~OM1&$0.37$&&$\bm{0.27}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
+~~OM2&$0.39$&&$\bm{0.3}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
+~~Phosphate&$0.31$&&$\bm{0.19}$&$\bm{0.17}$&$\bm{0.27}$\tabularnewline
 \hline

### 2016-09-28 ident_manu.Rnw
added ident all figure, L1 to heurist tables

@@
     ) %>%
-  select(stts, Selected, Parameter, Rank, coll) %>%
+  select(stts, Selected, Parameter, error, Rank, coll) %>%
   mutate(
@@
     ) %>% 
-  arrange(stts, Selected)
+  arrange(stts, Selected) %>% 
+  rename(L1 = error) %>% 
+  mutate(L1 = sapply(L1, scinot))
 
@@
 cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) for relevant state variables.
-Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\\gamma > 15$.
+Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive (L1, \\cref{l1}), until $\\gamma > 15$.
 Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).
 See \\cref{fig:heurist_stts} for a graphical illustration.'
-colnms <- c('Parameter', 'Rank', '$\\gamma$')
+colnms <- c('Parameter', 'L1', 'Rank', '$\\gamma$')
 
@@
 cap_val<- 'Parameter identifiability (as $\\gamma$, \\cref{gameq}) for relevant state variables.
-Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive until $\\gamma > 15$.
+Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive (L1, \\cref{l1}), until $\\gamma > 15$.
 Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
-colnms <- c('Parameter', 'Rank', '$\\gamma$')
+colnms <- c('Parameter', 'L1', 'Rank', '$\\gamma$')
 
@@
 
-% identifiability boxplots
-<<identbox, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
+% identifiability plot
+<<identplo, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
 Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
@@
   pleg, ncol = 2, widths = c(1, 0.1)
+)
+@
+
+% identifiability plot, all state variables
+<<identploall, eval = T, fig.cap = 'Average identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for all state variables.
+Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
+Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
+The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\\gamma = 1$, see \\cref{fig:inistreval}).', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=
+
+# identifiability by category (all parameters with >0 L1) 
+data(cat_ident_all)
+data(top_ident_all)
+
+# state variable, categories, and tops to plot (no temp ident because only one parameter)
+catnms <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Zooplankton')
+toplevs <- paste0('top', 1:4)
+toplabs <- paste('Top', 1:4)
+
+stts_lev <- c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4')
+stts_lab <- c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
+
+# default theme
+mytheme <- theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank(),
+    axis.ticks.x = element_line(),
+    axis.ticks.y = element_line(),
+    axis.ticks.length = unit(.1, "cm")
+  )
+
+toplo <- sapply(1:length(cat_ident_all), function(x){
+
+  out <- cat_ident_all[[x]] %>% 
+    .[names(.) %in% catnms] %>% 
+    lapply(function(y) dplyr::select(y, N, coll)) %>% 
+    reshape2::melt(., id.var = c('N', 'coll')) %>% 
+    rename(Category = L1) %>% 
+    mutate(Category = factor(Category, 
+      levels = catnms,
+      labels = catnms
+      )) %>% 
+    filter(N <= 25) %>% # reduced for plot space
+    group_by(N, Category) %>% 
+    summarise(
+      ave = mean(coll),   
+      med = median(coll),
+      min = min(coll), 
+      max = max(coll)
+      )
+  data.frame(stvar = names(cat_ident_all)[x], out, stringsAsFactors = F)
+
+  }, simplify = F) %>% 
+  do.call('rbind', .) %>% 
+  mutate(`State variable` = factor(stvar, levels = stts_lev, labels = stts_lab))
+
+stvars <- unique(toplo$`State variable`)
+mycols <- RColorBrewer::brewer.pal(8, 'Spectral')
+names(mycols) <- stvars
+fils <- scale_fill_manual(name = 'State variable', values = mycols)
+
+lncol <- 'darkgrey'
+sz <- 3
+
+p1 <- ggplot(toplo, aes(x = N, group = N)) + 
+  geom_line(aes(y = ave, group = `State variable`), colour = lncol) + 
+  geom_point(aes(y = ave, fill = `State variable`), shape = 21, colour = lncol, 
+    size = sz
+    ) + 
+  fils + 
+  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
+  mytheme +
+  scale_y_continuous(trans = 'log10') + 
+  theme(legend.position = 'none') + 
+  ggtitle('(a) By parameter category')
+
+toplo2 <- sapply(1:length(top_ident_all), function(x){
+
+  out <- top_ident_all[[x]] %>% 
+    .[names(.) %in% toplevs] %>% 
+    reshape2::melt(id.var = c('N', 'coll')) %>% 
+    select(N, coll, L1) %>% 
+    mutate(L1 = factor(L1, levels = toplevs, labels = toplabs)) %>% 
+    rename(npercat = L1) %>% 
+    group_by(N, npercat) %>% 
+    summarise(
+      ave = mean(coll), 
+      med = median(coll),
+      min = min(coll), 
+      max = max(coll)
+    )
+  data.frame(stvar = names(top_ident_all)[x], out, stringsAsFactors = F)
+
+  }, simplify = F) %>% 
+  do.call('rbind', .) %>% 
+  mutate(`State variable` = factor(stvar, levels = stts_lev, labels = stts_lab))
+
+p2 <- ggplot(toplo2, aes(x = N, group = N)) + 
+  geom_line(aes(y = ave, group = `State variable`), colour = lncol) + 
+  geom_point(aes(y = ave, fill = `State variable`), shape = 21, colour = lncol, 
+    size = sz
+    ) + 
+  fils + 
+  facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
+  mytheme +
+  scale_y_continuous(trans = 'log10') + 
+  ggtitle('(b) By top parameters, all categories')
+
+pleg <- g_legend(p2)
+p2 <- p2 + theme(legend.position = 'none')
+
+grid.arrange(
+  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
+  left = 'Identifiability',
+  pleg, ncol = 2, widths = c(1, 0.2)
 )

### 2016-09-28 ident_manu.tex
added ident all figure, L1 to heurist tables

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Sep 27 17:40:51 2016 -0500
+  \\ Version Date:   Wed Sep 28 08:25:08 2016 -0500
 	}
@@
 \caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.
-Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.
+Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive (L1, \cref{l1}), until $\gamma > 15$.
 Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).
@@
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \hline\hline
-\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
-\hline
-{\bfseries Ammonium}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
-~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
-\hline
-{\bfseries Chlorophyll}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.18$\tabularnewline
-\hline
-{\bfseries Dissolved Oxygen}&&&\tabularnewline
-~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$2.17$\tabularnewline
-~~3&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$2.31$\tabularnewline
-~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.37$\tabularnewline
-~~5&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$4.69$\tabularnewline
-~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$4.91$\tabularnewline
-~~7&\scriptsize{\textit{Zm}}&$3$\textsubscript{Z}&$6.73$\tabularnewline
-~~8&\scriptsize{\textit{Zumax}}&$4$\textsubscript{Z}&$6.81$\tabularnewline
-\hline
-{\bfseries Irradiance}&&&\tabularnewline
-~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
-~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$4.41$\tabularnewline
-~~3&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$7.54$\tabularnewline
-~~4&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$8.17$\tabularnewline
-~~5&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$9.44$\tabularnewline
-~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$9.66$\tabularnewline
-~~7&\scriptsize{\textit{Zumax}}&$3$\textsubscript{Z}&$10.79$\tabularnewline
-\hline
-{\bfseries Nitrate}&&&\tabularnewline
-~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
-\hline
-{\bfseries OM1}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.15$\tabularnewline
-~~3&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.87$\tabularnewline
-\hline
-{\bfseries OM2}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$1.05$\tabularnewline
-~~3&\scriptsize{\textit{umax}}&$2$\textsubscript{P}&$2.46$\tabularnewline
-~~4&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.91$\tabularnewline
-\hline
-{\bfseries Phosphate}&&&\tabularnewline
-~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
-~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$11.45$\tabularnewline
-~~3&\scriptsize{\textit{vmaxP}}&$2$\textsubscript{P}&$11.48$\tabularnewline
-~~4&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$13.74$\tabularnewline
+\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
+\hline
+{\bfseries Ammonium}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{nitmax}}&$1.54$&$1$\textsubscript{OM}&$1.16$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1.42$&$1$\textsubscript{Z}&$2.9$\tabularnewline
+\hline
+{\bfseries Chlorophyll}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$13.94$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1.02$&$1$\textsubscript{Z}&$1.18$\tabularnewline
+\hline
+{\bfseries Dissolved Oxygen}&&&&\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$0.05$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{ZKa}}&$0.05$&$1$\textsubscript{Z}&$2.17$\tabularnewline
+~~3&\scriptsize{\textit{mA}}&$0.02$&$2$\textsubscript{P}&$2.31$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.02$&$1$\textsubscript{T}&$2.37$\tabularnewline
+~~5&\scriptsize{\textit{ZQn}}&$0.02$&$2$\textsubscript{Z}&$4.69$\tabularnewline
+~~6&\scriptsize{\textit{alpha}}&$0.02$&$3$\textsubscript{P}&$4.91$\tabularnewline
+~~7&\scriptsize{\textit{Zm}}&$0.02$&$3$\textsubscript{Z}&$6.73$\tabularnewline
+~~8&\scriptsize{\textit{Zumax}}&$0.02$&$4$\textsubscript{Z}&$6.81$\tabularnewline
+\hline
+{\bfseries Irradiance}&&&&\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$0.13$&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$0.09$&$1$\textsubscript{P}&$4.41$\tabularnewline
+~~3&\scriptsize{\textit{ZQn}}&$0.06$&$2$\textsubscript{Z}&$7.54$\tabularnewline
+~~4&\scriptsize{\textit{mA}}&$0.05$&$2$\textsubscript{P}&$8.17$\tabularnewline
+~~5&\scriptsize{\textit{KGcdom}}&$0.05$&$1$\textsubscript{OM}&$9.44$\tabularnewline
+~~6&\scriptsize{\textit{alpha}}&$0.04$&$3$\textsubscript{P}&$9.66$\tabularnewline
+~~7&\scriptsize{\textit{Zumax}}&$0.04$&$3$\textsubscript{Z}&$10.79$\tabularnewline
+\hline
+{\bfseries Nitrate}&&&&\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline
+\hline
+{\bfseries OM1}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$7.22$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$0.96$&$1$\textsubscript{Z}&$1.15$\tabularnewline
+~~3&\scriptsize{\textit{KG1}}&$0.92$&$1$\textsubscript{OM}&$3.87$\tabularnewline
+\hline
+{\bfseries OM2}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
+~~3&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$2.46$\tabularnewline
+~~4&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.91$\tabularnewline
+\hline
+{\bfseries Phosphate}&&&&\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1.47$&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$0.78$&$1$\textsubscript{P}&$11.45$\tabularnewline
+~~3&\scriptsize{\textit{vmaxP}}&$0.59$&$2$\textsubscript{P}&$11.48$\tabularnewline
+~~4&\scriptsize{\textit{ZQn}}&$0.5$&$2$\textsubscript{Z}&$13.74$\tabularnewline
 \hline
@@
 \caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.
-Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive until $\gamma > 15$.
+Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive (L1, \cref{l1}), until $\gamma > 15$.
 Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:heurist3}}
 \begin{center}
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \hline\hline
-\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
-\hline
-{\bfseries Ammonium}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
-~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
-~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$3.46$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$4.25$\tabularnewline
-\hline
-{\bfseries Chlorophyll}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.18$\tabularnewline
-~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.62$\tabularnewline
-~~4&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$3.24$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$5.98$\tabularnewline
-\hline
-{\bfseries Dissolved Oxygen}&&&\tabularnewline
-~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$2.17$\tabularnewline
-~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.29$\tabularnewline
-~~4&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.85$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$3.89$\tabularnewline
-~~6&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$4.42$\tabularnewline
-~~7&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$5.22$\tabularnewline
-\hline
-{\bfseries Irradiance}&&&\tabularnewline
-~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
-~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$4.41$\tabularnewline
-~~3&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$4.5$\tabularnewline
-~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$4.5$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$6.9$\tabularnewline
-~~6&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$10.63$\tabularnewline
-~~7&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$11.21$\tabularnewline
-~~8&\scriptsize{\textit{KG1}}&$2$\textsubscript{OM}&$14.65$\tabularnewline
-~~9&\scriptsize{\textit{astarOMA}}&$2$\textsubscript{O}&$14.72$\tabularnewline
-\hline
-{\bfseries Nitrate}&&&\tabularnewline
-~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
-\hline
-{\bfseries OM1}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.15$\tabularnewline
-~~3&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.87$\tabularnewline
-~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$3.93$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$5.81$\tabularnewline
-\hline
-{\bfseries OM2}&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$1.05$\tabularnewline
-~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.61$\tabularnewline
-~~4&\scriptsize{\textit{KG2}}&$1$\textsubscript{OM}&$3.39$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$4.46$\tabularnewline
-~~6&\scriptsize{\textit{umax}}&$2$\textsubscript{P}&$6.02$\tabularnewline
-~~7&\scriptsize{\textit{ZKa}}&$2$\textsubscript{Z}&$9.21$\tabularnewline
-\hline
-{\bfseries Phosphate}&&&\tabularnewline
-~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
-~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$11.45$\tabularnewline
-~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$13.71$\tabularnewline
-~~4&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$14.64$\tabularnewline
+\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
+\hline
+{\bfseries Ammonium}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{nitmax}}&$1.54$&$1$\textsubscript{OM}&$1.16$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1.42$&$1$\textsubscript{Z}&$2.9$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.79$&$1$\textsubscript{T}&$3.46$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$0.03$&$1$\textsubscript{O}&$4.25$\tabularnewline
+\hline
+{\bfseries Chlorophyll}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$13.94$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$1.02$&$1$\textsubscript{Z}&$1.18$\tabularnewline
+~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.6$&$1$\textsubscript{T}&$2.62$\tabularnewline
+~~4&\scriptsize{\textit{KGcdom}}&$0.07$&$1$\textsubscript{OM}&$3.24$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$0.02$&$1$\textsubscript{O}&$5.98$\tabularnewline
+\hline
+{\bfseries Dissolved Oxygen}&&&&\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$0.05$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{ZKa}}&$0.05$&$1$\textsubscript{Z}&$2.17$\tabularnewline
+~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.02$&$1$\textsubscript{T}&$2.29$\tabularnewline
+~~4&\scriptsize{\textit{KG1}}&$0.01$&$1$\textsubscript{OM}&$3.85$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$7.51\times 10^{-4}$&$1$\textsubscript{O}&$3.89$\tabularnewline
+~~6&\scriptsize{\textit{mA}}&$0.02$&$2$\textsubscript{P}&$4.42$\tabularnewline
+~~7&\scriptsize{\textit{ZQn}}&$0.02$&$2$\textsubscript{Z}&$5.22$\tabularnewline
+\hline
+{\bfseries Irradiance}&&&&\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$0.13$&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$0.09$&$1$\textsubscript{P}&$4.41$\tabularnewline
+~~3&\scriptsize{\textit{KGcdom}}&$0.05$&$1$\textsubscript{OM}&$4.5$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.03$&$1$\textsubscript{T}&$4.5$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$0.02$&$1$\textsubscript{O}&$6.9$\tabularnewline
+~~6&\scriptsize{\textit{ZQn}}&$0.06$&$2$\textsubscript{Z}&$10.63$\tabularnewline
+~~7&\scriptsize{\textit{mA}}&$0.05$&$2$\textsubscript{P}&$11.21$\tabularnewline
+~~8&\scriptsize{\textit{KG1}}&$0$&$2$\textsubscript{OM}&$14.65$\tabularnewline
+~~9&\scriptsize{\textit{astarOMA}}&$0$&$2$\textsubscript{O}&$14.72$\tabularnewline
+\hline
+{\bfseries Nitrate}&&&&\tabularnewline
+~~1&\scriptsize{\textit{umax}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline
+\hline
+{\bfseries OM1}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$7.22$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$0.96$&$1$\textsubscript{Z}&$1.15$\tabularnewline
+~~3&\scriptsize{\textit{KG1}}&$0.92$&$1$\textsubscript{OM}&$3.87$\tabularnewline
+~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.86$&$1$\textsubscript{T}&$3.93$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$0.03$&$1$\textsubscript{O}&$5.81$\tabularnewline
+\hline
+{\bfseries OM2}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.61$\tabularnewline
+~~4&\scriptsize{\textit{KG2}}&$0.94$&$1$\textsubscript{OM}&$3.39$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$0.04$&$1$\textsubscript{O}&$4.46$\tabularnewline
+~~6&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$6.02$\tabularnewline
+~~7&\scriptsize{\textit{ZKa}}&$0.88$&$2$\textsubscript{Z}&$9.21$\tabularnewline
+\hline
+{\bfseries Phosphate}&&&&\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1.47$&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$0.78$&$1$\textsubscript{P}&$11.45$\tabularnewline
+~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.16$&$1$\textsubscript{T}&$13.71$\tabularnewline
+~~4&\scriptsize{\textit{KG1}}&$0.14$&$1$\textsubscript{OM}&$14.64$\tabularnewline
 \hline
@@
 
-% identifiability boxplots
+% identifiability plot
 \begin{figure}[!ht]
 
-{\centering \includegraphics[width=\maxwidth]{figs/identbox-1}
+{\centering \includegraphics[width=\maxwidth]{figs/identplo-1}
 
@@
 Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
-The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identbox}
+The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identplo}
+\end{figure}
+
+% identifiability plot, all state variables
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\maxwidth]{figs/identploall-1}
+
+}
+
+\caption{Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables.
+Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
+Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
+The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\gamma = 1$, see \cref{fig:inistreval}).}\label{fig:identploall}
 \end{figure}

### 2016-09-28 ident_manu.Rnw
inits and strcs supp tables added

@@
 
-A set of heuristics was developed to balance the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
+A set of heuristics was developed that address the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
 These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability).
@@
 \item or considering all categories equally.
-\end{inparaenum} The selection rules produced seven subsets of parameters that could further be used to optimize model calibration for \ac{do}.
+\end{inparaenum} The selection rules produced seven subsets of parameters that could further be used to optimize model calibration.
 
@@
 
-The effects of observational and structural uncertainty on the sensitivity analyses were evaluated for \ac{do}.
-These analyses used changes in parameter uncertainty and identifiability from results using the model's default configuration to infer the effects of observational and structural uncertainty on model output.
-First, observational uncertainty was evaluated by varying the initial conditions supplied to the model.
-The initial conditions were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14} and uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
+The effects of observational and structural uncertainty on the sensitivity analyses were evaluated by changing the initial conditions and structural components, respectively, from the default model setup.
+First, observational uncertainty was evaluated by varying the initial conditions that were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14}.
+Uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
 For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplankton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
-Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on which nutrient is limiting.
-Parameter sensitivity and identifiability was re-evaluated for \ac{do} by varying all initial conditions that were non-zero by 50\% and 200\% of the original values that were estimated from the observed data.
-Initial conditions were also changed to test the effects of different limiting nutrients by setting nitrogen and phosphorus values above or below concentrations defined by the standard Redfield ratio.
-
-The effects of model structure on parameter sensitivity and identifiability were evaluated by including or excluding specific components of the model.
-The FishTank model includes several processes that are based on expected conditions or available data.
-These `switches' are conceptually different from model parameters as they define the use of explicit equations or processes included in the model structure.
-As such, a comparison of sensitivity and identifiability given different equations uses parameter uncertainty to begin addressing componenents of structural uncertainty.
+Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on the limiting nutrient.
+Parameter sensitivity was re-evaluated by varying all initial conditions that were non-zero by different seasonal means based on averages of water quality data across stations and years.
+April and September seasonal averages of the observed data were used to evaluate the effects of conditions that were typical of spring and late summer on the \ac{lcs}.
+
+The effects of model structure on parameter sensitivity were evaluated by changing specific components of the model.
+The FishTank model includes several ecosystem processes or characteristics that can be included based on expected conditions, available data, or desired complexity.
+These `switches' are conceptually different from model parameters as they allow the inclusion of explicit equations or processes.
 Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).
 Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIR}.
-For simplicity, parameter identifiability was evaluated using three scenarios of simple, intermediate, and complex combinations of model switches.
+Parameter sensitivity was evaluated by comparing the results from the default model setup to an alternative, more complex, setup that included additional processes with added switches.
 
@@
 The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
-In addition to \ac{do}, other state variables included \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
+In addition to \ac{do}, other state variables that were evaluated were \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
 Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
@@
 
+% initial conditions evaluated 
+<<inits, eval = T, cache = F>>=
+data(ini_eval)
+
+inits <- lapply(ini_eval, function(x) unlist(x[[1]])) %>% 
+  do.call('rbind', .) %>% 
+  t %>% 
+  data.frame(vars = row.names(.), .) %>% 
+  mutate(
+    Default = sapply(def, scinot),
+    April = sapply(apr, scinot), 
+    September = sapply(sep, scinot)
+  ) %>% 
+  select(-def, -apr, -sep) %>% 
+  mutate(
+    vars = factor(vars, 
+      labels = c('Ammonium', 'Dissolved Inorganic Carbon', 'Dissolved Oygen','Nitrate', 'Phosphate', 'Silica'),
+      levels = c('NH4', 'DIC', 'O2', 'NO3', 'PO4', 'Si')
+    ), 
+    vars = as.character(vars)
+  )
+
+cap_val <- 'Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
+April and September values are based on seasonal averages from water quality samples of the \\ac{lcs}.
+All units are $\\mu$mol L$^{-1}$.'
+
+latex( 
+  inits[, -1],
+  file = '',
+  rowlabel = 'Variables',
+  caption = cap_val,
+  caption.loc = 'top',
+  label = 'tab:inits',
+  rowname = inits[, 1]
+  )  
+@
+
+% structural conditions
+<<strcs, eval = T, cache = F>>=
+swtch <- data.frame(
+  lab = c('Temperature', 'Uptake', 'Quota', 'Chla:C', 'Photosynthesis', 'Growth'),
+  sim = c('sigmoidal', 'Michaelis-Menten', 'Droop', 'regression', 'photoinhibition', 'minimum'),
+  com = c('Arrenhius', 'Geider', 'Flynn', 'Cloern', 'nutrient dependent', '\\textit{umax} is nutrient dependent'), 
+  stringsAsFactors = F
+  ) %>% 
+  rename(
+    `Switch type` = lab, 
+    Default = sim, 
+    Complex = com
+  )
+
+cap_val <- 'Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.'
+
+latex( 
+  swtch[, -1],
+  file = '',
+  rowlabel = 'Switch type',
+  caption = cap_val,
+  caption.loc = 'top',
+  label = 'tab:strcs',
+  rowname = swtch[, 1]
+  )
+
+@
 \clearpage

### 2016-09-28 ident_manu.tex
inits and strcs supp tables added

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Sep 28 08:25:08 2016 -0500
+  \\ Version Date:   Wed Sep 28 10:02:54 2016 -0500
 	}
@@
 
+% initial conditions evaluated 
+%latex.default(inits[, -1], file = "", rowlabel = "Variables",     caption = cap_val, caption.loc = "top", label = "tab:inits",     rowname = inits[, 1])%
+\begin{table}[!tbp]
+\caption{Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
+April and September values are based on seasonal averages from water quality samples of the \ac{lcs}.
+All units are $\mu$mol L$^{-1}$.\label{tab:inits}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Variables}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{April}&\multicolumn{1}{c}{September}\tabularnewline
+\hline
+Dissolved Inorganic Carbon&$2134$&$2096.5$&$2133.37$\tabularnewline
+Ammonium&$1.09$&$1.79$&$0.35$\tabularnewline
+Nitrate&$71.4$&$3.75$&$2.04$\tabularnewline
+Dissolved Oygen&$172$&$194.47$&$152.57$\tabularnewline
+Phosphate&$1.81$&$0.23$&$0.42$\tabularnewline
+Silica&$71.4$&$5.84$&$9.77$\tabularnewline
+\hline
+\end{tabular}\end{center}
+
+\end{table}
+
+% structural conditions
+%latex.default(swtch[, -1], file = "", rowlabel = "Switch type",     caption = cap_val, caption.loc = "top", label = "tab:strcs",     rowname = swtch[, 1])%
+\begin{table}[!tbp]
+\caption{Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.\label{tab:strcs}} 
+\begin{center}
+\begin{tabular}{lll}
+\hline\hline
+\multicolumn{1}{l}{Switch type}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{Complex}\tabularnewline
+\hline
+Temperature&sigmoidal&Arrenhius\tabularnewline
+Uptake&Michaelis-Menten&Geider\tabularnewline
+Quota&Droop&Flynn\tabularnewline
+Chla:C&regression&Cloern\tabularnewline
+Photosynthesis&photoinhibition&nutrient dependent\tabularnewline
+Growth&minimum&\textit{umax} is nutrient dependent\tabularnewline
+\hline
+\end{tabular}\end{center}
+
+\end{table}
+
 \clearpage

### 2016-11-28 ident_manu.Rnw
minor personal edits to intro/methods

@@
 In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
-We argue that quantitative and ecological certainty in model calibration are often at odds and the practitioner must explicitly choose model components to optimize given tradeoffs between the two.
+We argue that quantitative and ecological certainty in model calibration are often at odds and practitioners must choose explicit model components to optimize given tradeoffs between the two.
 We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of paramater perturbations on model output.
@@
 Process-based models are more commonly imbalanced between reality and theory, such that most are over-parameterized in an attempt to completely describe reality \citep{Denman03,Nossent12,Petrucci14}.
-Such over-parameterization, including use of excessive structural equations, can have serious implications for practical applications.
+Such over-parameterization, including use of many  structural equations, can have serious implications for practical applications.
 Quantitative limitations of over-parameterization are analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset \citep{Kirchner06}.
 More importantly, over-parameterization can limit use across systems outside of the data domain and impose uncertainty in model predictions as realistic values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
-The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and more comprehensive approaches are needed to develop models that more carefully balance theory with reality \citep[e.g.,][]{Snowling01}.
+The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and comprehensive approaches are needed to develop models that more carefully balance theory with reality \citep[e.g.,][]{Snowling01}.
 
@@
 
-This study describes a parameter sensitivity analysis to evaluate identifiability for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
+This study describes a parameter sensitivity analysis to evaluate identifiability of parameter subsets for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
 We evaluate a simple \ac{zerod} unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
@@
 
-Hypoxic events, defined  as $<$2 mg L$^{-1}$ of \ac{do} ($<$ 64 mmol m$^-3$), occur seasonally in bottom waters in the northern \ac{gom}.
+Hypoxic events, defined  as $<$2 mg L$^{-1}$ of \ac{do} ($<$ 64 mmol m$^{-3}$), occur seasonally in bottom waters in the northern \ac{gom}.
 The \ac{lcs} receives high nutrient loads from the \ac{marb} that drains a significant portion of the continental United States.
@@
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
-Accordingly, the sensitivity and identifiability analysis described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
+Accordingly, the sensitivity and identifiability analyses described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
 The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
-A set of initial conditions is provided as input to the model that was based on observations of relevant variables obtained from research cruises in April, June, and September 2006 \citep[Table 1 in][]{Murrell14}.
+A set of initial conditions is provided on execution of the model that is based on observations of relevant variables obtained from research cruises in the northern \ac{gom} during April, June, and September of 2006 \citep[Table 1 in][]{Murrell14}.
 
@@
 
-The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006 by running FishTank at a timestep of five minutes.
+The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep of FishTank simulations from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
 Irrelevant parameters were removed for several reasons; parameters were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
@@
 
-The analysis focused on sensitivity of \ac{do} in the \ac{zerod} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
-A local sensitivity analysis was performed for each of the parameters using a simple perturbation approach to evaluate the change in \ac{do} from the original parameter values.
+The analysis focused on sensitivity of \ac{do} and other state variables (noted below) in the \ac{zerod} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
+A local sensitivity analysis was performed by evaluating the change in \ac{do} following perturbation of each parameter from its original value.
 The analyses relied exclusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10,RDCT16}.
-Each parameter was perturbed by 50\% of its original value and the model was executed to obtain an estimate of the change in \ac{do}.
-For each perturbation, a sensitivity value $S$ was estimated for each time step $i$ given a set value for parameter $j$ as:
+Parameters were individually perturbed by 50\% of the original values and the model was executed to obtain an estimate \ac{do} sensitivity.
+For each perturbation, a sensitivity value $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
 
@@
 
-All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ were retained for identifiability analysis.
+All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ (suggesting sensitivity) were retained for identifiability analysis.
 
@@
 The collinearity index $\gamma$ provides a measure of the linear dependence between sensitivity functions described above for subsets of parameters.
-Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning optimal values are inestimable given similar effects of the selected parameters on \ac{do}.
+Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms given similar effects of the selected parameters on \ac{do}.
 Greater sensitivity of a state variable to a subset of parameters does not always imply better identifiability if the individual effects are similar.
 An intuitive interpretation of $\gamma$ is provided by \citet{Brun01} such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
-That is, $\gamma = 10$ suggests the relative change in \ac{do} for a selected parameter can be compensated for by 90\% with changes in the other parameters.
+That is, $\gamma = 10$ suggests the relative change in \ac{do} for an arbitrary parameter in the selected set can be compensated for by 90\% with changes in the other parameters.
 
@@
 Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
-An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter.
+An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practicioners may only be interested in optics parameters).
 For example, \cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., based on $n$ choose $k$ combinations equal to $n!/\left(k!\left(n-k\right)!\right)$).
@@
 For example, over 10$^{14}$ combinations are possible by selecting 25 parameters from a set of 50.
-Accordingly, parameter selection is complicated by differing sensitivity, identifiability, and the difficulty of choosing from many combinations.
+Accordingly, parameter selection is complicated by differing sensitivity, identifiability limits for parameter subsets, and the difficulty of choosing from many combinations.
 
@@
 
-The effects of observational and structural uncertainty on the sensitivity analyses were evaluated by changing the initial conditions and structural components, respectively, from the default model setup.
-First, observational uncertainty was evaluated by varying the initial conditions that were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14}.
+In addition to parameter uncertainty, the effects of observational and structural uncertainty on the sensitivity analyses were evaluated by changing the initial conditions and structural components, respectively, from the default model setup.
+First, observational uncertainty (i.e., effects of observed data on model output) was evaluated by varying the initial conditions that were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14}.
 Uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
@@
 Parameter sensitivity was re-evaluated by varying all initial conditions that were non-zero by different seasonal means based on averages of water quality data across stations and years.
-April and September seasonal averages of the observed data were used to evaluate the effects of conditions that were typical of spring and late summer on the \ac{lcs}.
-
-The effects of model structure on parameter sensitivity were evaluated by changing specific components of the model.
+April and September seasonal averages of the observed data were used to evaluate the effects of conditions that were typical of spring and late summer on the \ac{lcs} (\cref{tab:inits}).
+
+The effects of model structure on parameter sensitivity (i.e., structural uncertainty) were evaluated by changing specific components of the model.
 The FishTank model includes several ecosystem processes or characteristics that can be included based on expected conditions, available data, or desired complexity.
-These `switches' are conceptually different from model parameters as they allow the inclusion of explicit equations or processes.
+These `switches' are conceptually different from model parameters as they allow the inclusion or exclusion of explicit equations or processes.
 Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).
 Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIR}.
-Parameter sensitivity was evaluated by comparing the results from the default model setup to an alternative, more complex, setup that included additional processes with added switches.
+Parameter sensitivity was evaluated by comparing the results from the default model setup to an alternative, more complex, setup that included additional processes with added switches (\cref{tab:strcs}).
 

### 2016-11-28 ident_manu.tex
minor personal edits to intro/methods

@@
 \newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
 
@@
   \vspace{1in} 
-  \\ Version Date:   Wed Sep 28 10:02:54 2016 -0500
+  \\ Version Date:   Wed Sep 28 15:23:05 2016 -0500
 	}

### 2016-11-28 ident_manu.Rnw
changed author contact, added lowe edits

@@
 \author{
-  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
+  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
   \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
@@
 	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
-	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
-	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
+	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
+	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
+  \\{\textit {\normalsize Dauphin Island, AL 36528}}
+	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
+	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
+	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
 	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
@@
 The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools.
-This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter sensitivity and identifability.
-We evaluate a simple bio-geo-chemical model that is the \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example.
-Results from analysis of the \ac{zerod} model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
+This study provides a context for understanding quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.
+The analysis provides a contrast of numeric and ecological certainty in parameter subsets using a systematic framework to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
 In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
@@
 
-This study evaluated a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.
+This study evaluated the core unit of a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.
 The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describes hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
@@
 
-The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux).
+The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux) nor sediment diagenesis.
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
-Accordingly, the sensitivity and identifiability analyses described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
+Accordingly, the sensitivity and identifiability analyses described below focused exclusively on FishTank and are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
 The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
@@
 
-Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
+Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
 A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
@@
 In addition to \ac{do}, other state variables that were evaluated were \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
-Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).
+Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIR}).
 
@@
 <<dosens, eval = T, cache = F>>=
-senstab(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', digits = 2, pow = 2, tabsize = 'footnotesize')
+senstab(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', digits = 2, pow = 2, tabsize = 'footnotesize', foot.val = '\\footnotesize *Temperature parameters apply separately to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts')
 @
@@
 % parameter exclusion temp
-<<exclex, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of organic matter parameters for subset combinations in \\cref{fig:identbox}.
+<<exclex, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) for \\ac{do} of organic matter parameters for subset combinations in \\cref{fig:identplo}.
 Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
-Identifiability of including all eight parameters is in \\cref{fig:identbox}.
+Identifiability of including all eight parameters is in \\cref{fig:identplo}.
 Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "\\textwidth">>=

### 2016-11-28 ident_manu.tex
changed author contact, added lowe edits

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Sep 28 15:23:05 2016 -0500
+  \\ Version Date:   Mon Nov 28 16:09:57 2016 -0600
 	}
@@
 % do sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 {\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
@@
 
-\end{table}
+\footnotesize *Temperaure parameters apply to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts\end{table}
 
@@
 
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of organic matter parameters for subset combinations in \cref{fig:identbox}.
+\caption{Identifiability (as $\gamma$, \cref{gameq}) for \ac{do} of organic matter parameters for subset combinations in \cref{fig:identplo}.
 Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
-Identifiability of including all eight parameters is in \cref{fig:identbox}.
+Identifiability of including all eight parameters is in \cref{fig:identplo}.
 Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:exclex}
@@
 % ammonium sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 ~~NH4 rate constant for nitrification&\textit{KNH4}&$0.66$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.07$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.07$\tabularnewline
 ~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
@@
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.05$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.03$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.03$\tabularnewline
 ~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
@@
 % chlorophyll sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 ~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.03$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.03$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.01$\tabularnewline
@@
 % irradiance sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 ~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.2\times 10^{-4}$\tabularnewline
@@
 % nitrate sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.03$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.02$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.02$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
 ~~maximum rate of nitrification per day&\textit{nitmax}&$9.96\times 10^{-3}$\tabularnewline
@@
 % om1 sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 {\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.92$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.92$\tabularnewline
 ~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
@@
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.02$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
 ~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
@@
 % om2 sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 {\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.94$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.94$\tabularnewline
 ~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.1$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.04$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.04$\tabularnewline
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
@@
 % phosphate sensitivity all categories
-%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
 \begin{table}[!tbp]
@@
 {\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.14$\tabularnewline
-~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.06$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.14$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.06$\tabularnewline
 ~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.02$\tabularnewline

### 2016-11-28 R/funcs.R

@@ -800,8 +800,8 @@ parcats2 <- function(as_df = FALSE){
       'CF_SPM_1'
       ), 
     lngs = c(
-      'KG1: turnover rate for OM1_A and OM1_G',	
-      'KG2: turnover rate for OM2_A and OM2_G',
+      'KG1: turnover rate for OM1_A and OM1_Z',	
+      'KG2: turnover rate for OM2_A and OM2_Z',
       'KG1_R: OM1 turnover rate for riverine',
       'KG2_R: OM2 turnover rate for riverine',
       'KG1_BC: OM1 turnover rate for initial and bc',
@@ -990,7 +990,7 @@ par_txt <- function(parin, frm = 'tex', p1z1 = TRUE){
 
 ######
 # function for sensitivity tables, no phyto, zoop groupings
-senstab <- function(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', tabsize = 'normalsize', pow = 3, digits = 2){
+senstab <- function(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', tabsize = 'normalsize', pow = 3, digits = 2, foot.val = NULL){
 
   library(Hmisc)
   library(dplyr)
@@ -1042,7 +1042,8 @@ senstab <- function(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', tabs
     rgroup = unique(cats),
     n.rgroup = as.numeric(table(cats)),
     size = tabsize,
-    label = paste0('tab:', tablab)
+    label = paste0('tab:', tablab), 
+    insert.bottom = foot.val
     )
     
 }

### 2016-11-29 ident_manu.Rnw
moved supp tabs/figs to main text

@@
 
+% initial conditions evaluated 
+<<inits, eval = T, cache = F>>=
+data(ini_eval)
+
+inits <- lapply(ini_eval, function(x) unlist(x[[1]])) %>% 
+  do.call('rbind', .) %>% 
+  t %>% 
+  data.frame(vars = row.names(.), .) %>% 
+  mutate(
+    Default = sapply(def, scinot),
+    April = sapply(apr, scinot), 
+    September = sapply(sep, scinot)
+  ) %>% 
+  select(-def, -apr, -sep) %>% 
+  mutate(
+    vars = factor(vars, 
+      labels = c('Ammonium', 'Dissolved Inorganic Carbon', 'Dissolved Oygen','Nitrate', 'Phosphate', 'Silica'),
+      levels = c('NH4', 'DIC', 'O2', 'NO3', 'PO4', 'Si')
+    ), 
+    vars = as.character(vars)
+  )
+
+cap_val <- 'Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
+April and September values are based on seasonal averages from water quality samples of the \\ac{lcs}.
+All units are $\\mu$mol L$^{-1}$.'
+
+latex( 
+  inits[, -1],
+  file = '',
+  rowlabel = 'Variables',
+  caption = cap_val,
+  caption.loc = 'top',
+  label = 'tab:inits',
+  rowname = inits[, 1]
+  )  
+@
+
+% structural conditions
+<<strcs, eval = T, cache = F>>=
+swtch <- data.frame(
+  lab = c('Temperature', 'Uptake', 'Quota', 'Chla:C', 'Photosynthesis', 'Growth'),
+  sim = c('sigmoidal', 'Michaelis-Menten', 'Droop', 'regression', 'photoinhibition', 'minimum'),
+  com = c('Arrenhius', 'Geider', 'Flynn', 'Cloern', 'nutrient dependent', '\\textit{umax} is nutrient dependent'), 
+  stringsAsFactors = F
+  ) %>% 
+  rename(
+    `Switch type` = lab, 
+    Default = sim, 
+    Complex = com
+  )
+
+cap_val <- 'Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.'
+
+latex( 
+  swtch[, -1],
+  file = '',
+  rowlabel = 'Switch type',
+  caption = cap_val,
+  caption.loc = 'top',
+  label = 'tab:strcs',
+  rowname = swtch[, 1]
+  )
+
+@
+
 % do sensitivity all categories
@@
 
-<<sensalltile, eval = T, echo = F, fig.height = 6, fig.width = 3.5, out.width = '0.7\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.
+% effects of changing initial and structural conditions
+<<sensalltile, fig.cap = 'Sensitivity values (L1, \\cref{l1}) of all state variables to changes in parameter values using default conditions, changes in initial conditions (April, September seasonal means, \\cref{tab:inits}), and changes in structural complexity (\\cref{tab:strcs}).
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
-See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.'>>=
-data(sens_ests_cat_all)
-
-tmp <- reshape2::melt(sens_ests_cat_all, id.var = c('Parameter', 'error', 'Category'))
+See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 7, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
+# initial conditions
+data(ini_eval)
+data(struct_eval)
+
+to_eval <- lapply(ini_eval, function(x) x[[2]]) %>% 
+  c(., struct = list(struct_eval))
+
+eval_levs <- c('def', 'apr', 'sep', 'struct')
+eval_labs <- c('Default', 'Initial: April', 'Initial: September', 'Structure: complex')
+
+toplo_all <- sapply(1:length(to_eval), function(x) {
+
+  tmp <- reshape2::melt(to_eval[[x]], id.var = c('Parameter', 'error', 'Category'))
+  nms <- names(to_eval)[x]
 
@@
   toplo <- mutate(tmp,
-    L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab))
+      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
+      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
+      nms = nms
     ) %>% 
@@
 
-toplo1 <- mutate(toplo, Parameter = as.character(par_txt(Parameter, frm = 'exp')))
+  return(toplo)
+
+  }, simplify = F)
+toplo_all <- do.call('rbind', toplo_all)
+toplo_all <- mutate(toplo_all, nms = factor(nms, levels = eval_levs, labels = eval_labs))
 
@@
 
-ggplot(toplo1, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
+p <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
   geom_tile(colour = 'black') + 
@@
     expand = c(0, 0),
-    breaks = toplo1$Parameter, 
-    labels = parse(text = toplo1$Parameter)
+    breaks = toplo_all$Parameter, 
+    labels = parse(text = toplo_all$Parameter)
     ) + 
@@
   scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
-  facet_grid(Category~., scales = 'free_y', space = 'free') + 
+  facet_grid(Category~nms, scales = 'free_y', space = 'free') + 
   guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
 
+print(p)
 @
@@
   theme(legend.position = 'top')
+
 @
@@
 
-% initial conditions evaluated 
-<<inits, eval = T, cache = F>>=
-data(ini_eval)
-
-inits <- lapply(ini_eval, function(x) unlist(x[[1]])) %>% 
-  do.call('rbind', .) %>% 
-  t %>% 
-  data.frame(vars = row.names(.), .) %>% 
-  mutate(
-    Default = sapply(def, scinot),
-    April = sapply(apr, scinot), 
-    September = sapply(sep, scinot)
-  ) %>% 
-  select(-def, -apr, -sep) %>% 
-  mutate(
-    vars = factor(vars, 
-      labels = c('Ammonium', 'Dissolved Inorganic Carbon', 'Dissolved Oygen','Nitrate', 'Phosphate', 'Silica'),
-      levels = c('NH4', 'DIC', 'O2', 'NO3', 'PO4', 'Si')
-    ), 
-    vars = as.character(vars)
-  )
-
-cap_val <- 'Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
-April and September values are based on seasonal averages from water quality samples of the \\ac{lcs}.
-All units are $\\mu$mol L$^{-1}$.'
-
-latex( 
-  inits[, -1],
-  file = '',
-  rowlabel = 'Variables',
-  caption = cap_val,
-  caption.loc = 'top',
-  label = 'tab:inits',
-  rowname = inits[, 1]
-  )  
-@
-
-% structural conditions
-<<strcs, eval = T, cache = F>>=
-swtch <- data.frame(
-  lab = c('Temperature', 'Uptake', 'Quota', 'Chla:C', 'Photosynthesis', 'Growth'),
-  sim = c('sigmoidal', 'Michaelis-Menten', 'Droop', 'regression', 'photoinhibition', 'minimum'),
-  com = c('Arrenhius', 'Geider', 'Flynn', 'Cloern', 'nutrient dependent', '\\textit{umax} is nutrient dependent'), 
-  stringsAsFactors = F
-  ) %>% 
-  rename(
-    `Switch type` = lab, 
-    Default = sim, 
-    Complex = com
-  )
-
-cap_val <- 'Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.'
-
-latex( 
-  swtch[, -1],
-  file = '',
-  rowlabel = 'Switch type',
-  caption = cap_val,
-  caption.loc = 'top',
-  label = 'tab:strcs',
-  rowname = swtch[, 1]
-  )
-
-@
 \clearpage
@@
 % sup figs
-
-% effects of changing initial and structural conditions
-<<inistreval, fig.cap = 'Effects of initial and structural conditions on parameter sensitivity.', fig.height = 7, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
-# initial conditions
-data(ini_eval)
-data(struct_eval)
-
-to_eval <- lapply(ini_eval, function(x) x[[2]]) %>% 
-  c(., struct = list(struct_eval))
-
-eval_levs <- c('def', 'apr', 'sep', 'struct')
-eval_labs <- c('Default', 'Initial: April', 'Initial: September', 'Structure: complex')
-
-toplo_all <- sapply(1:length(to_eval), function(x) {
-
-  tmp <- reshape2::melt(to_eval[[x]], id.var = c('Parameter', 'error', 'Category'))
-  nms <- names(to_eval)[x]
-
-  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
-  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
-
-  toplo <- mutate(tmp,
-      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
-      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
-      nms = nms
-    ) %>% 
-    rename(Sensitivity = error)
-
-  return(toplo)
-
-  }, simplify = F)
-toplo_all <- do.call('rbind', toplo_all)
-toplo_all <- mutate(toplo_all, nms = factor(nms, levels = eval_levs, labels = eval_labs))
-
-pbase <- theme(
-  panel.grid.major = element_blank(), 
-  panel.grid.minor = element_blank(), 
-  axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
-  axis.text.y = element_text(size = 6),
-  legend.position = 'top', 
-  plot.margin = grid::unit(c(2, 2, 2, 2), 'pt'), 
-  strip.background = element_blank(), 
-  strip.text.y = element_text(angle = 0, hjust = 0, vjust = 0.5)
-  )
-
-p <- ggplot(toplo_all, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
-  geom_tile(colour = 'black') + 
-  pbase +
-  scale_y_discrete('Parameter', 
-    expand = c(0, 0),
-    breaks = toplo_all$Parameter, 
-    labels = parse(text = toplo_all$Parameter)
-    ) + 
-  scale_x_discrete('State variable', expand = c(0, 0)) +
-  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
-  facet_grid(Category~nms, scales = 'free_y', space = 'free') + 
-  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
-
-print(p)
-@
+% NULL
 

### 2016-11-29 ident_manu.tex
moved supp tabs/figs to main text

@@
 \newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
 
@@
   \vspace{1in} 
-  \\ Version Date:   Mon Nov 28 16:09:57 2016 -0600
+  \\ Version Date:   Mon Nov 28 17:05:13 2016 -0600
 	}
@@
 
+% initial conditions evaluated 
+%latex.default(inits[, -1], file = "", rowlabel = "Variables",     caption = cap_val, caption.loc = "top", label = "tab:inits",     rowname = inits[, 1])%
+\begin{table}[!tbp]
+\caption{Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
+April and September values are based on seasonal averages from water quality samples of the \ac{lcs}.
+All units are $\mu$mol L$^{-1}$.\label{tab:inits}}
+\begin{center}
+\begin{tabular}{llll}
+\hline\hline
+\multicolumn{1}{l}{Variables}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{April}&\multicolumn{1}{c}{September}\tabularnewline
+\hline
+Dissolved Inorganic Carbon&$2134$&$2096.5$&$2133.37$\tabularnewline
+Ammonium&$1.09$&$1.79$&$0.35$\tabularnewline
+Nitrate&$71.4$&$3.75$&$2.04$\tabularnewline
+Dissolved Oygen&$172$&$194.47$&$152.57$\tabularnewline
+Phosphate&$1.81$&$0.23$&$0.42$\tabularnewline
+Silica&$71.4$&$5.84$&$9.77$\tabularnewline
+\hline
+\end{tabular}\end{center}
+
+\end{table}
+
+% structural conditions
+%latex.default(swtch[, -1], file = "", rowlabel = "Switch type",     caption = cap_val, caption.loc = "top", label = "tab:strcs",     rowname = swtch[, 1])%
+\begin{table}[!tbp]
+\caption{Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.\label{tab:strcs}} 
+\begin{center}
+\begin{tabular}{lll}
+\hline\hline
+\multicolumn{1}{l}{Switch type}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{Complex}\tabularnewline
+\hline
+Temperature&sigmoidal&Arrenhius\tabularnewline
+Uptake&Michaelis-Menten&Geider\tabularnewline
+Quota&Droop&Flynn\tabularnewline
+Chla:C&regression&Cloern\tabularnewline
+Photosynthesis&photoinhibition&nutrient dependent\tabularnewline
+Growth&minimum&\textit{umax} is nutrient dependent\tabularnewline
+\hline
+\end{tabular}\end{center}
+
+\end{table}
+
 % do sensitivity all categories
@@
 
-\footnotesize *Temperaure parameters apply to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts\end{table}
+\footnotesize *Temperature parameters apply separately to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts\end{table}
 
@@
 \hline
-{\bfseries Optics}&&&&&&&&&\tabularnewline
+{\bfseries Phytoplankton}&&&&&&&&&\tabularnewline
+~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
 ~~\scriptsize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
 ~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$5.36$&-&$7.78$&$7.87$&-\tabularnewline
+\hline
+{\bfseries Optics}&&&&&&&&&\tabularnewline
+~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&-&$10.04$\tabularnewline
 ~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.73$\tabularnewline
-~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&-&$10.04$\tabularnewline
 ~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$6.02$&-&$7.91$&$7.87$&-\tabularnewline
+~~\scriptsize{\textit{Athresh}}&$6$&$11.27$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
+~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
+~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
 \hline
 {\bfseries Organic Matter}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
-~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
+~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
+~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
-~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
-~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
-~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{respg}}&$6$&-&-&$3.41$&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
-~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
 ~~\scriptsize{\textit{umax}}&$2$&-&-&-&-&-&-&$1.21$&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$5$&$8.14$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$7$&-&-&$3.97$&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$7.45$\tabularnewline
-~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
-~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
-~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
-~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{vmaxN}}&$5$&$8.14$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Athresh}}&$6$&$11.27$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{respg}}&$6$&-&-&$3.41$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{vmaxN}}&$7$&-&-&$3.97$&-&-&-&-&-\tabularnewline
 \hline
@@
 ~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&-&-&$7.3$&$5.43$&-\tabularnewline
+~~\scriptsize{\textit{Zm}}&$3$&-&-&$4.57$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zm}}&$4$&-&-&-&$11.86$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
 ~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&-&-&$7.3$&$5.43$&-\tabularnewline
-~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
-~~\scriptsize{\textit{Zm}}&$3$&-&-&$4.57$&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&$6.93$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Zm}}&$4$&-&-&-&$11.86$&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{Zumax}}&$4$&-&-&$5.2$&-&-&-&-&-\tabularnewline
@@
 
+% effects of changing initial and structural conditions
 \begin{figure}[!ht]
 
-{\centering \includegraphics[width=0.7\textwidth]{figs/sensalltile-1}
+{\centering \includegraphics[width=\textwidth]{figs/sensalltile-1}
 
@@
 
-\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.
+\caption{Sensitivity values (L1, \cref{l1}) of all state variables to changes in parameter values using default conditions, changes in initial conditions (April, September seasonal means, \cref{tab:inits}), and changes in structural complexity (\cref{tab:strcs}).
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
@@
 
-% initial conditions evaluated 
-%latex.default(inits[, -1], file = "", rowlabel = "Variables",     caption = cap_val, caption.loc = "top", label = "tab:inits",     rowname = inits[, 1])%
-\begin{table}[!tbp]
-\caption{Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
-April and September values are based on seasonal averages from water quality samples of the \ac{lcs}.
-All units are $\mu$mol L$^{-1}$.\label{tab:inits}}
-\begin{center}
-\begin{tabular}{llll}
-\hline\hline
-\multicolumn{1}{l}{Variables}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{April}&\multicolumn{1}{c}{September}\tabularnewline
-\hline
-Dissolved Inorganic Carbon&$2134$&$2096.5$&$2133.37$\tabularnewline
-Ammonium&$1.09$&$1.79$&$0.35$\tabularnewline
-Nitrate&$71.4$&$3.75$&$2.04$\tabularnewline
-Dissolved Oygen&$172$&$194.47$&$152.57$\tabularnewline
-Phosphate&$1.81$&$0.23$&$0.42$\tabularnewline
-Silica&$71.4$&$5.84$&$9.77$\tabularnewline
-\hline
-\end{tabular}\end{center}
-
-\end{table}
-
-% structural conditions
-%latex.default(swtch[, -1], file = "", rowlabel = "Switch type",     caption = cap_val, caption.loc = "top", label = "tab:strcs",     rowname = swtch[, 1])%
-\begin{table}[!tbp]
-\caption{Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.\label{tab:strcs}} 
-\begin{center}
-\begin{tabular}{lll}
-\hline\hline
-\multicolumn{1}{l}{Switch type}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{Complex}\tabularnewline
-\hline
-Temperature&sigmoidal&Arrenhius\tabularnewline
-Uptake&Michaelis-Menten&Geider\tabularnewline
-Quota&Droop&Flynn\tabularnewline
-Chla:C&regression&Cloern\tabularnewline
-Photosynthesis&photoinhibition&nutrient dependent\tabularnewline
-Growth&minimum&\textit{umax} is nutrient dependent\tabularnewline
-\hline
-\end{tabular}\end{center}
-
-\end{table}
-
 \clearpage
@@
 % sup figs
-
-% effects of changing initial and structural conditions
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/inistreval-1}
-
-}
-
-\caption[Effects of initial and structural conditions on parameter sensitivity]{Effects of initial and structural conditions on parameter sensitivity.}\label{fig:inistreval}
-\end{figure}
+% NULL
 

### 2016-11-29 ident_manu.Rnw
refs and better description for switches

@@
 Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIR}.
-Parameter sensitivity was evaluated by comparing the results from the default model setup to an alternative, more complex, setup that included additional processes with added switches (\cref{tab:strcs}).
+
+Parameter sensitivity was evaluated by comparing the results from the default model setup to an alternative, more complex setup with alternative switches (\cref{tab:strcs}).
+The scenarios used different equations to represent structural relationships of phytoplankton growth patterns with temperature, nutrient uptake, cell quotas, \ac{chla} to carbon ratios, photosynthesis dynamics, and specific growth limits.
+The default scenario modelled phytoplankton growth with temperature as a sigmoidal function \citep{Eldridge10}, nutrient uptake as Michaelis-Menten kinetics \citep{Dugdale67}, internal cell quotas following \citet{Droop73}, \ac{chla} to carbon ratios as a simple regression \citep{Murrell14}, light-dependence of photosynthesis with photoinhibition \citep{Platt80}, and a specific growth rate following Leibig's law of the minimum.
+Conversely, the complex scenario used switches that modelled relationships between phytoplankton growth with temperature using the Arrhenius model \citep{Geider97}, nutrient uptake as proposed by \citet{Lehman75} and modified in \citet{Geider98}, internal cell quotas following \citet{Flynn03}, \ac{chla} to carbon ratios following \citet{Cloern95}, light-dependence of photosynthesis that is nutrient dependent \citep{Flynn03}, and a specific growth rate that is nutrient dependent.
+Complete details are provided as supplementary material to \citetalias{LehrterIR}.
 
@@
 \section{Results}
-%' 
-%' % for inline
-%' <<echo = FALSE, eavl = F, cache = F>>=
-%' data(sens_ests)
-%' data(sens_ests_cat)
-%' 
-%' # number of parameters in each category
-%' bycat <- table(sens_ests_cat$Category)
-%' nms <- names(bycat)
-%' bycat <- as.numeric(bycat)
-%' names(bycat) <- nms
-%' bycat <- toeng(bycat)
-%' 
-%' # percent of parameters in each category
-%' lncats <- table(sens_ests_cat$Category) %>% 
-%'   `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>% 
-%'   `*` (100) %>% 
-%'   form_fun(nsm_val = 0) %>% 
-%'   as.list %>% 
-%'   lapply(., paste0, '\\%')
-%' 
-%' # L1 range
-%' sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
-%'   sens_ests_cat[., ] %>% 
-%'   mutate(
-%'     error = sapply(error, scinot),
-%'     Parameter = par_txt(Parameter)
-%'     )
-%' 
-%' # L1 range within categories
-%' sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
-%'   lapply(., function(x){
-%'     
-%'     with(x, which(error %in% range(error))) %>% 
-%'       x[., ] %>% 
-%'       mutate(
-%'         Parameter = par_txt(Parameter), 
-%'         error = sapply(error, scinot)
-%'       )
-%'     
-%'     }
-%'   )
-%' 
-%' # average L1, all and by category
-%' sensave <- scinot(mean(sens_ests_cat$error))
-%' sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
-%'   lapply(., function(x) scinot(mean(x$error)))
-%'     
-%' # phyto errors
-%' phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>% 
-%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
-%'   group_by(grp) %>%
-%'   summarise(grpave = mean(error)) %>% 
-%'   arrange(-grpave) %>% 
-%'   mutate(grpave = sapply(grpave, scinot))
-%' 
-%' # zoop errors 
-%' zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>% 
-%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
-%'   group_by(grp) %>%
-%'   summarise(grpave = mean(error)) %>% 
-%'   arrange(-grpave) %>% 
-%'   mutate(grpave = sapply(grpave, scinot))
-%' @
-%' 
+
+% for inline
+<<echo = FALSE, eval = F, cache = F>>=
+data(sens_ests_all)
+data(sens_ests_cat)
+
+# number of parameters in each category
+bycat <- table(sens_ests_cat$Category)
+nms <- names(bycat)
+bycat <- as.numeric(bycat)
+names(bycat) <- nms
+bycat <- toeng(bycat)
+
+# percent of parameters in each category
+lncats <- table(sens_ests_cat$Category) %>%
+  `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>%
+  `*` (100) %>%
+  form_fun(nsm_val = 0) %>%
+  as.list %>%
+  lapply(., paste0, '\\%')
+
+# L1 range
+sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>%
+  sens_ests_cat[., ] %>%
+  mutate(
+   error = sapply(error, scinot),
+   Parameter = par_txt(Parameter)
+   )
+
+# L1 range within categories
+sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>%
+  lapply(., function(x){
+
+  with(x, which(error %in% range(error))) %>%
+    x[., ] %>%
+    mutate(
+      Parameter = par_txt(Parameter),
+      error = sapply(error, scinot)
+    )
+
+  }
+)
+
+# average L1, all and by category
+sensave <- scinot(mean(sens_ests_cat$error))
+sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>%
+  lapply(., function(x) scinot(mean(x$error)))
+
+# phyto errors
+phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>%
+  separate(Parameter, c('parm', 'grp'), sep = '_') %>%
+  group_by(grp) %>%
+  summarise(grpave = mean(error)) %>%
+  arrange(-grpave) %>%
+  mutate(grpave = sapply(grpave, scinot))
+
+# zoop errors
+zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>%
+  separate(Parameter, c('parm', 'grp'), sep = '_') %>%
+  group_by(grp) %>%
+  summarise(grpave = mean(error)) %>%
+  arrange(-grpave) %>%
+  mutate(grpave = sapply(grpave, scinot))
+@
+
 %' \subsection{Local sensitivity analysis}
@@
 swtch <- data.frame(
-  lab = c('Temperature', 'Uptake', 'Quota', 'Chla:C', 'Photosynthesis', 'Growth'),
-  sim = c('sigmoidal', 'Michaelis-Menten', 'Droop', 'regression', 'photoinhibition', 'minimum'),
-  com = c('Arrenhius', 'Geider', 'Flynn', 'Cloern', 'nutrient dependent', '\\textit{umax} is nutrient dependent'), 
+  lab = c('Temperature', 'Uptake', 'Quota', 'Chla:C', 'Photosynthesis', 'Specific growth rate'),
+  sim = c('sigmoidal {\\scriptsize \\citep{Eldridge10}}', 'Michaelis-Menten {\\scriptsize \\citep{Dugdale67}}', 'Droop {\\scriptsize \\citep{Droop73}}', 'regression {\\scriptsize \\citep{Murrell14}}', 'photoinhibition {\\scriptsize \\citep{Platt80}}', "Leibig's minimum"),
+  com = c('Arrenhius {\\scriptsize \\citep{Geider97}}', 'Geider {\\scriptsize \\citep{Lehman75,Geider98}}', 'Flynn {\\scriptsize \\citep{Flynn03}}', 'Cloern {\\scriptsize \\citep{Cloern95}}', 'nutrient dependent', 'nutrient dependent'),
   stringsAsFactors = F
@@
 
-cap_val <- 'Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.'
+cap_val <- 'Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.
+Complete details and equations are provided as supplementary material to \\citetalias{LehrterIR}.'
 

### 2016-11-29 ident_manu.tex
refs and better description for switches

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Nov 28 17:05:13 2016 -0600
+  \\ Version Date:   Tue Nov 29 13:48:43 2016 -0600
 	}
@@
 \section{Results}
-%' 
-%' % for inline
-%' <<echo = FALSE, eavl = F, cache = F>>=
-%' data(sens_ests)
-%' data(sens_ests_cat)
-%' 
-%' # number of parameters in each category
-%' bycat <- table(sens_ests_cat$Category)
-%' nms <- names(bycat)
-%' bycat <- as.numeric(bycat)
-%' names(bycat) <- nms
-%' bycat <- toeng(bycat)
-%' 
-%' # percent of parameters in each category
-%' lncats <- table(sens_ests_cat$Category) %>% 
-%'   `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>% 
-%'   `*` (100) %>% 
-%'   form_fun(nsm_val = 0) %>% 
-%'   as.list %>% 
-%'   lapply(., paste0, '\\%')
-%' 
-%' # L1 range
-%' sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>% 
-%'   sens_ests_cat[., ] %>% 
-%'   mutate(
-%'     error = sapply(error, scinot),
-%'     Parameter = par_txt(Parameter)
-%'     )
-%' 
-%' # L1 range within categories
-%' sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
-%'   lapply(., function(x){
-%'     
-%'     with(x, which(error %in% range(error))) %>% 
-%'       x[., ] %>% 
-%'       mutate(
-%'         Parameter = par_txt(Parameter), 
-%'         error = sapply(error, scinot)
-%'       )
-%'     
-%'     }
-%'   )
-%' 
-%' # average L1, all and by category
-%' sensave <- scinot(mean(sens_ests_cat$error))
-%' sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>% 
-%'   lapply(., function(x) scinot(mean(x$error)))
-%'     
-%' # phyto errors
-%' phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>% 
-%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
-%'   group_by(grp) %>%
-%'   summarise(grpave = mean(error)) %>% 
-%'   arrange(-grpave) %>% 
-%'   mutate(grpave = sapply(grpave, scinot))
-%' 
-%' # zoop errors 
-%' zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>% 
-%'   separate(Parameter, c('parm', 'grp'), sep = '_') %>% 
-%'   group_by(grp) %>%
-%'   summarise(grpave = mean(error)) %>% 
-%'   arrange(-grpave) %>% 
-%'   mutate(grpave = sapply(grpave, scinot))
-%' @
-%' 
+
+% for inline
+
 %' \subsection{Local sensitivity analysis}
@@
 \begin{table}[!tbp]
-\caption{Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.\label{tab:strcs}} 
+\caption{Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.
+Complete details and equations are provided as supplementary material to \citetalias{LehrterIR}.\label{tab:strcs}}
 \begin{center}
@@
 \hline
-Temperature&sigmoidal&Arrenhius\tabularnewline
-Uptake&Michaelis-Menten&Geider\tabularnewline
-Quota&Droop&Flynn\tabularnewline
-Chla:C&regression&Cloern\tabularnewline
-Photosynthesis&photoinhibition&nutrient dependent\tabularnewline
-Growth&minimum&\textit{umax} is nutrient dependent\tabularnewline
+Temperature&sigmoidal {\scriptsize \citep{Eldridge10}}&Arrenhius {\scriptsize \citep{Geider97}}\tabularnewline
+Uptake&Michaelis-Menten {\scriptsize \citep{Dugdale67}}&Geider {\scriptsize \citep{Lehman75,Geider98}}\tabularnewline
+Quota&Droop {\scriptsize \citep{Droop73}}&Flynn {\scriptsize \citep{Flynn03}}\tabularnewline
+Chla:C&regression {\scriptsize \citep{Murrell14}}&Cloern {\scriptsize \citep{Cloern95}}\tabularnewline
+Photosynthesis&photoinhibition {\scriptsize \citep{Platt80}}&nutrient dependent\tabularnewline
+Specific growth rate&Leibig's minimum&nutrient dependent\tabularnewline
 \hline

### 2016-11-30 ident_manu.Rnw
local sensitivity analysis results section done

@@
 \usepackage{fixltx2e}
-% \usepackage{showlabels}
+\usepackage[inline]{showlabels}
 \bibpunct{(}{)}{,}{a}{}{,}
@@
 \acrodef{do}[O$_2$]{dissolved oxygen}
+\acrodef{dom}[DOM]{dissolved organic matter}
 \acrodef{gom}[GOM]{Gulf of Mexico}
@@
 \acrodef{marb}[MARB]{Mississippi-Atchafalaya River Basin}
+\acrodef{pom}[POM]{particulate organic matter}
 \acrodef{zerod}[0-D]{zero-dimensional}
@@
 
+% number of parameters evaluated, total and by category
 <<echo = FALSE>>=
@@
   as.list  
-
 @
@@
 
-Parameter sensitivity was evaluated by comparing the results from the default model setup to an alternative, more complex setup with alternative switches (\cref{tab:strcs}).
-The scenarios used different equations to represent structural relationships of phytoplankton growth patterns with temperature, nutrient uptake, cell quotas, \ac{chla} to carbon ratios, photosynthesis dynamics, and specific growth limits.
+Parameter sensitivity was evaluated by comparing the results from the default model setup to a more complex setup with alternative switches (\cref{tab:strcs}).
+The scenarios used switches for different equations to represent structural relationships of phytoplankton growth patterns with temperature, nutrient uptake, cell quotas, \ac{chla} to carbon ratios, photosynthesis dynamics, and specific growth limits.
 The default scenario modelled phytoplankton growth with temperature as a sigmoidal function \citep{Eldridge10}, nutrient uptake as Michaelis-Menten kinetics \citep{Dugdale67}, internal cell quotas following \citet{Droop73}, \ac{chla} to carbon ratios as a simple regression \citep{Murrell14}, light-dependence of photosynthesis with photoinhibition \citep{Platt80}, and a specific growth rate following Leibig's law of the minimum.
@@
 The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
-In addition to \ac{do}, other state variables that were evaluated were \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.
+In addition to \ac{do}, other state variables that were evaluated were ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.
 Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIR}).
@@
 % for inline
-<<echo = FALSE, eval = F, cache = F>>=
-data(sens_ests_all)
-data(sens_ests_cat)
-
-# number of parameters in each category
-bycat <- table(sens_ests_cat$Category)
-nms <- names(bycat)
-bycat <- as.numeric(bycat)
-names(bycat) <- nms
-bycat <- toeng(bycat)
-
-# percent of parameters in each category
-lncats <- table(sens_ests_cat$Category) %>%
-  `/` (table(sort(parcats2(as_df = TRUE)$cats))) %>%
-  `*` (100) %>%
-  form_fun(nsm_val = 0) %>%
-  as.list %>%
-  lapply(., paste0, '\\%')
-
-# L1 range
-sensrng <- with(sens_ests_cat, which(error %in% range(error))) %>%
-  sens_ests_cat[., ] %>%
-  mutate(
-   error = sapply(error, scinot),
-   Parameter = par_txt(Parameter)
-   )
-
-# L1 range within categories
-sensrngcat <- split(sens_ests_cat, sens_ests_cat$Category) %>%
-  lapply(., function(x){
-
-  with(x, which(error %in% range(error))) %>%
-    x[., ] %>%
-    mutate(
-      Parameter = par_txt(Parameter),
-      error = sapply(error, scinot)
-    )
-
-  }
-)
-
-# average L1, all and by category
-sensave <- scinot(mean(sens_ests_cat$error))
-sensave_cat <- split(sens_ests_cat, sens_ests_cat$Category) %>%
-  lapply(., function(x) scinot(mean(x$error)))
-
-# phyto errors
-phytogrps <- filter(sens_ests_cat, Category == 'Phytoplankton') %>%
-  separate(Parameter, c('parm', 'grp'), sep = '_') %>%
-  group_by(grp) %>%
-  summarise(grpave = mean(error)) %>%
-  arrange(-grpave) %>%
-  mutate(grpave = sapply(grpave, scinot))
-
-# zoop errors
-zoopgrps <- filter(sens_ests_cat, Category == 'Zooplankton') %>%
-  separate(Parameter, c('parm', 'grp'), sep = '_') %>%
-  group_by(grp) %>%
-  summarise(grpave = mean(error)) %>%
-  arrange(-grpave) %>%
-  mutate(grpave = sapply(grpave, scinot))
-@
-
-%' \subsection{Local sensitivity analysis}
-%' 
-%' Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{nrow(sens_ests_cat)} of 178 parameters (\Sexpr{round(100 * nrow(sens_ests_cat)/178, 0)}\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
-Within each parameter category, \ac{do} was sensitive to \Sexpr{bycat$Optics} parameters for optics (\Sexpr{lncats$Optics} of all optic parameters, \cref{tab:optsens}), \Sexpr{bycat$`Organic Matter`} for organic matter (\Sexpr{lncats$`Organic Matter`}, \cref{tab:omsens}), \Sexpr{bycat$Phytoplankton} for phytoplankton (\Sexpr{lncats$Phytoplankton}, \cref{tab:phytosens}), \Sexpr{bycat$Temperature} for temperature (\Sexpr{lncats$Temperature}, \cref{tab:tempsens}), and \Sexpr{bycat$Zooplankton} for zooplankton (\Sexpr{lncats$Zooplankton}, \cref{tab:zoopsens}).
+<<echo = FALSE, eval = T, cache = F>>=
+data(sens_ests_cat_all)
+
+# each state variable has:
+#   txt: chr string for inline text of variable name
+#   tot: total number of sensitive parameters
+#   bycat: list of number of sensitive parameters in each category
+#   lncat: list of percentage of sensitive parameters in each category
+#   sensrng: tibble with min/max sensitivity across categories
+#   sensrngcat: list of tibbles with min/max sensitivity within categories
+#   sensave: numeric of overall sensitivity
+#   sensavecat; list of average sensitivity by categories
+loc <- loc_summ(sens_ests_cat_all)
+locO2 <- loc$O2
+locO2$sensavecat <- lapply(locO2$sensavecat, scinot)
+locO2$sensave <- scinot(locO2$sensave)
+
+@
+
+\subsection{Local sensitivity analysis}
+
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{locO2$tot} of the \Sexpr{length(p1z1pars)} (\Sexpr{round(100 * locO2$tot/length(p1z1pars), 0)}\% of total) evaluated parameters in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
+Within each parameter category, \ac{do} was sensitive to \Sexpr{locO2$bycat$Optics} parameters for optics (\Sexpr{locO2$lncat$Optics} of all optic parameters), \Sexpr{locO2$bycat$`Organic Matter`} for organic matter (\Sexpr{locO2$lncat$`Organic Matter`}), \Sexpr{locO2$bycat$Phytoplankton} for phytoplankton (\Sexpr{locO2$lncat$Phytoplankton}), \Sexpr{locO2$bycat$Temperature} for temperature (\Sexpr{locO2$lncat$Temperature}), and \Sexpr{locO2$bycat$Zooplankton} for zooplankton (\Sexpr{locO2$lncat$Zooplankton}).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{sensrng$error[1]} for \Sexpr{sensrng$Parameter[1]} (\Sexpr{tolower(sensrng$Category[1])}) to \Sexpr{sensrng$error[2]} for \Sexpr{sensrng$Parameter[2]} (\Sexpr{tolower(sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{sensave}.
-Within categories, sensitivity ranged from \Sexpr{sensrngcat$Optics$error[1]} (\Sexpr{sensrngcat$Optics$Parameter[1]}) to \Sexpr{sensrngcat$Optics$error[2]} (\Sexpr{sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{sensrngcat$`Organic Matter`$error[1]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{sensrngcat$`Organic Matter`$error[2]} (\Sexpr{sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{sensrngcat$Phytoplankton$error[1]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{sensrngcat$Phytoplankton$error[2]} (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) for phytopankton, \Sexpr{sensrngcat$Temperature$error[1]} (\Sexpr{sensrngcat$Temperature$Parameter[1]}) to \Sexpr{sensrngcat$Temperature$error[2]} (\Sexpr{sensrngcat$Temperature$Parameter[2]}) for temperature, and \Sexpr{sensrngcat$Zooplankton$error[1]} (\Sexpr{sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{sensrngcat$Zooplankton$error[2]} (\Sexpr{sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{fig:sensplo}, bottom).
-Average sensitivity values in each category were $L1 = $ \Sexpr{sensave_cat$Optics} for optics, \Sexpr{sensave_cat$`Organic Matter`} for organic matter, \Sexpr{sensave_cat$Phytoplankton} for phytoplankton, \Sexpr{sensave_cat$Temperature} for temperature, and \Sexpr{sensave_cat$Zooplankton} for zooplankton.
-Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied.
-Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ \Sexpr{phytogrps[1, 2]}, \Sexpr{phytogrps[2, 2]}), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
-Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ \Sexpr{zoopgrps[1, 2]}, \Sexpr{zoopgrps[2, 2]} for groups one and two).
-%' 
-%' Response of \ac{do} to parameter perturbations was not uniform across the time series.
-\Cref{fig:sensplo} shows variation for the top parameters within each category.
-Because FishTank does not include a spatial component, the estimated \ac{do} trend describes a closed, heterotrophic system where respiration processes eventually remove all \ac{do} from the model space.
-The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January, February), the spring/summer increase represents production associated with expected seasonal growth, and the remaining time series from August to the end of year shows complete removal of \ac{do} as respiration processes dominate metabolic activity.
-Although this time series is not a realistic depiction of an actual system, the biogeochemical model behaves as expected in the absence of the hydrodynamic model.
-Accordingly, the interpretation of sensitivity results from the simple model has relevance in an ecological context.
-As expected, parameter perturbations had the largest effect during the summer months, although the effects varied.
-An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, \Sexpr{sensrngcat$Zooplankton$Parameter[2]}, which caused an increase in \ac{do}.
-The phytoplankton parameter, \Sexpr{sensrngcat$Phytoplankton$Parameter[2]}, had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.
-The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (\Sexpr{sensrngcat$Optics$Parameter[2]}) and phytoplankton (\Sexpr{sensrngcat$Phytoplankton$Parameter[2]}) parameters.
-%' 
-%' \subsection{Subset identifiability}
-%' 
+Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{locO2$sensrng$error[1]} for \Sexpr{locO2$sensrng$Parameter[1]} (\Sexpr{tolower(locO2$sensrng$Category[1])}) to \Sexpr{locO2$sensrng$error[2]} for \Sexpr{locO2$sensrng$Parameter[2]} (\Sexpr{tolower(locO2$sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{locO2$sensave}.
+Within categories (excluding temperature), sensitivity ranged from \Sexpr{locO2$sensrngcat$Optics$error[1]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Optics$error[2]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{locO2$sensrngcat$`Organic Matter`$error[1]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{locO2$sensrngcat$`Organic Matter`$error[2]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{locO2$sensrngcat$Phytoplankton$error[1]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Phytoplankton$error[2]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[2]}) for phytoplankton, and \Sexpr{locO2$sensrngcat$Zooplankton$error[1]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Zooplankton$error[2]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[2]}) for zooplankton.
+Average sensitivity values in each category were $L1 = $ \Sexpr{locO2$sensavecat$Optics} for optics, \Sexpr{locO2$sensavecat$`Organic Matter`} for organic matter, \Sexpr{locO2$sensavecat$Temperature} for temperature, \Sexpr{locO2$sensavecat$Phytoplankton} for phytoplankton, and \Sexpr{locO2$sensavecat$Zooplankton} for zooplankton.
+
+<<echo = F>>=
+locChla_mg_tot <- loc$Chla_mg_tot
+locirradiance <- loc$irradiance
+locNH4 <- loc$NH4
+locNO3 <- loc$NO3
+locOM1 <- loc$OM1
+locOM2 <- loc$OM2
+locPO4 <- loc$PO4
+
+# average sensitivities for all
+aveall <- lapply(loc, function(x){
+  out <- x$sensave
+  names(out) <- x$txt
+  out
+  }) %>% 
+  unlist %>% 
+  sort
+names(aveall) <- gsub('^.*\\.', '', names(aveall))
+
+# parameter category with highest average sensitivity for each st var
+maxcat <- lapply(loc, function(x){
+
+  out <- x$sensavecat %>% 
+    unlist %>% 
+    .[which.max(.)]
+
+  nms <- tolower(names(out))
+  out <- scinot(out)
+  names(out) <- nms
+  out
+
+})
+
+# average parameter sensitivity for categories, independent of state variables
+avecat <- do.call('rbind', sens_ests_cat_all) %>% 
+  split(.$Category) %>% 
+  lapply(function(x) mean(x$error)) %>% 
+  unlist %>% 
+  sort %>% 
+  sapply(scinot)
+names(avecat) <- tolower(names(avecat))
+
+@
+
+Local sensitivity analyses for the additional state variables (ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus) had similar results as \ac{do} with some exceptions (\cref{fig:sensalltile,tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens}).
+All additional variables were sensitive to the same parameters (\Sexpr{locO2$tot} of \Sexpr{length(p1z1pars)} evaluated), although average sensitivity differed between variables.
+Average $L1$ ranged from \Sexpr{scinot(aveall[2])} for \Sexpr{names(aveall)[2]} (\cref{tab:irrsens}) to \Sexpr{scinot(aveall[length(aveall)])} for \Sexpr{names(aveall)[length(aveall)]} (\cref{tab:om2sens}).
+All average sensitivity values for the state variables were higher than the average for \ac{do} ($L1$ = \Sexpr{scinot(aveall[1])}).
+For each variable, $L1$ ranged from \Sexpr{locNH4$sensrng[1, 2]} (\Sexpr{locNH4$sensrng[1, 1]}) to \Sexpr{locNH4$sensrng[2, 2]} (\Sexpr{locNH4$sensrng[2, 1]}) for ammonium (\cref{tab:nh4sens}), \Sexpr{locChla_mg_tot$sensrng[1, 2]} (\Sexpr{locChla_mg_tot$sensrng[1, 1]}) to \Sexpr{locChla_mg_tot$sensrng[2, 2]} (\Sexpr{locChla_mg_tot$sensrng[2, 1]}) for \ac{chla} (\cref{tab:chlsens}), \Sexpr{locirradiance$sensrng[1, 2]} (\Sexpr{locirradiance$sensrng[1, 1]}) to \Sexpr{locirradiance$sensrng[2, 2]} (\Sexpr{locirradiance$sensrng[2, 1]}) for irradiance (\cref{tab:irrsens}), \Sexpr{locNO3$sensrng[1, 2]} (\Sexpr{locNO3$sensrng[1, 1]}) to \Sexpr{locNO3$sensrng[2, 2]} (\Sexpr{locNO3$sensrng[2, 1]}) for nitrate (\cref{tab:no3sens}), \Sexpr{locOM1$sensrng[1, 2]} (\Sexpr{locOM1$sensrng[1, 1]}) to \Sexpr{locOM1$sensrng[2, 2]} (\Sexpr{locOM1$sensrng[2, 1]}) for \ac{pom} (\cref{tab:om1sens}),  \Sexpr{locOM2$sensrng[1, 2]} (\Sexpr{locOM2$sensrng[1, 1]}) to \Sexpr{locOM2$sensrng[2, 2]} (\Sexpr{locOM2$sensrng[2, 1]}) for \ac{dom} (\cref{tab:om2sens}), and \Sexpr{locPO4$sensrng[1, 2]} (\Sexpr{locPO4$sensrng[1, 1]}) to \Sexpr{locPO4$sensrng[2, 2]} (\Sexpr{locPO4$sensrng[2, 1]}) for phosphate (\cref{tab:po4sens}).
+For the parameter categories, ammonium was most sensitive to \Sexpr{names(maxcat$NH4)} parameters (average $L1$ = \Sexpr{maxcat$NH4} across all parameters in the category), \ac{chla} to \Sexpr{names(maxcat$Chla_mg_tot)} ($L1$ = \Sexpr{maxcat$Chla_mg_tat}), irradiance to \Sexpr{names(maxcat$irradiance)} ($L1$ = \Sexpr{maxcat$irradiance}), nitrate to \Sexpr{names(maxcat$NO3)} ($L1$ = \Sexpr{maxcat$NO3}), \ac{pom} to \Sexpr{names(maxcat$OM1)} ($L1$ = \Sexpr{maxcat$OM1}), \ac{dom} to \Sexpr{names(maxcat$OM2)} ($L1$ = \Sexpr{maxcat$OM2}), and phosphate to \Sexpr{names(maxcat$PO4)} ($L1$ = \Sexpr{maxcat$PO4}).
+Finally, average sensititivy between parameter categories independent of the state variables ranged from \Sexpr{avecat[1]} for \Sexpr{names(avecat)[1]} (average $L1$ across all variables) to \Sexpr{avecat[length(avecat)]} for \Sexpr{names(avecat)[length(avecat)]}.
+
+\subsection{Subset identifiability}
+
 %' <<eval = F>>=
@@
 Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.
-Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
+Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, \ac{pom}, \ac{dom}, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
 Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
@@
 )
+
 @
@@
 <<om1sens, eval = T, cache = F>>=
-senstab(out_var = 'OM1', tablab = 'om1sens', captxt = 'particulate organic matter', digits = 2, pow = 2, tabsize = 'footnotesize')
+senstab(out_var = 'OM1', tablab = 'om1sens', captxt = '\\ac{pom}', digits = 2, pow = 2, tabsize = 'footnotesize')
 @
@@
 <<om2sens, eval = T, cache = F>>=
-senstab(out_var = 'OM2', tablab = 'om2sens', captxt = 'dissolved organic matter', digits = 2, pow = 2, tabsize = 'footnotesize')
+senstab(out_var = 'OM2', tablab = 'om2sens', captxt = '\\acl{dom}', digits = 2, pow = 2, tabsize = 'footnotesize')
 @

### 2016-11-30 ident_manu.tex
local sensitivity analysis results section done

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Nov 29 13:48:43 2016 -0600
+  \\ Version Date:   Tue Nov 29 17:13:44 2016 -0600
 	}
@@
 
+% number of parameters evaluated, total and by category
+
 The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep of FishTank simulations from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
@@
 
-%' \subsection{Local sensitivity analysis}
-%' 
-%' Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in nrow(sens_ests_cat) of 178 parameters (round(100 * nrow(sens_ests_cat)/178, 0)\% of total) in FishTank (see \cref{fig:sensalltile} for other state variables).
-Within each parameter category, \ac{do} was sensitive to bycat$Optics parameters for optics (lncats$Optics of all optic parameters, \cref{tab:optsens}), bycat$`Organic Matter` for organic matter (lncats$`Organic Matter`, \cref{tab:omsens}), bycat$Phytoplankton for phytoplankton (lncats$Phytoplankton, \cref{tab:phytosens}), bycat$Temperature for temperature (lncats$Temperature, \cref{tab:tempsens}), and bycat$Zooplankton for zooplankton (lncats$Zooplankton, \cref{tab:zoopsens}).
+\subsection{Local sensitivity analysis}
+
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 38 of the 51 (75\% of total) evaluated parameters in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
+Within each parameter category, \ac{do} was sensitive to three parameters for optics (75\% of all optic parameters), eight for organic matter (67\%), 16 for phytoplankton (73\%), one for temperature (50\%), and 10 for zooplankton (91\%).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ sensrng$error[1] for sensrng$Parameter[1] (tolower(sensrng$Category[1])) to sensrng$error[2] for sensrng$Parameter[2] (tolower(sensrng$Category[2])), whereas average sensitivity among all parameters was $L1 = $ sensave.
-Within categories, sensitivity ranged from sensrngcat$Optics$error[1] (sensrngcat$Optics$Parameter[1]) to sensrngcat$Optics$error[2] (sensrngcat$Optics$Parameter[2]) for optics, sensrngcat$`Organic Matter`$error[1] (sensrngcat$`Organic Matter`$Parameter[1]) to sensrngcat$`Organic Matter`$error[2] (sensrngcat$`Organic Matter`$Parameter[2]) for organic matter, sensrngcat$Phytoplankton$error[1] (sensrngcat$Phytoplankton$Parameter[1]) to sensrngcat$Phytoplankton$error[2] (sensrngcat$Phytoplankton$Parameter[2]) for phytopankton, sensrngcat$Temperature$error[1] (sensrngcat$Temperature$Parameter[1]) to sensrngcat$Temperature$error[2] (sensrngcat$Temperature$Parameter[2]) for temperature, and sensrngcat$Zooplankton$error[1] (sensrngcat$Zooplankton$Parameter[1]) to sensrngcat$Zooplankton$error[2] (sensrngcat$Zooplankton$Parameter[2]) for zooplankton (\cref{fig:sensplo}, bottom).
-Average sensitivity values in each category were $L1 = $ sensave_cat$Optics for optics, sensave_cat$`Organic Matter` for organic matter, sensave_cat$Phytoplankton for phytoplankton, sensave_cat$Temperature for temperature, and sensave_cat$Zooplankton for zooplankton.
-Within the six phytoplankton groups, \ac{do} was sensitive to the same parameters within each group although the sensitivity magnitudes varied.
-Average sensitivity across parameters in each phytoplankton groups showed that \ac{do} was most sensitive to the first and third phytoplankton groups (average $L1 = $ phytogrps[1, 2], phytogrps[2, 2]), whereas sensitivity to parameters in the remaining groups was much lower (all with average $L1 < 1$).
-Sensitivity of \ac{do} did not vary considerably between parameters in the two zooplankton groups (average $L1 = $ zoopgrps[1, 2], zoopgrps[2, 2] for groups one and two).
-%' 
-%' Response of \ac{do} to parameter perturbations was not uniform across the time series.
-\Cref{fig:sensplo} shows variation for the top parameters within each category.
-Because FishTank does not include a spatial component, the estimated \ac{do} trend describes a closed, heterotrophic system where respiration processes eventually remove all \ac{do} from the model space.
-The initial decrease in the time series reflects change from the initial conditions outside of the growing seasons (i.e., January, February), the spring/summer increase represents production associated with expected seasonal growth, and the remaining time series from August to the end of year shows complete removal of \ac{do} as respiration processes dominate metabolic activity.
-Although this time series is not a realistic depiction of an actual system, the biogeochemical model behaves as expected in the absence of the hydrodynamic model.
-Accordingly, the interpretation of sensitivity results from the simple model has relevance in an ecological context.
-As expected, parameter perturbations had the largest effect during the summer months, although the effects varied.
-An inrease in 50\% from the parameter default values generally caused a reduction in \ac{do} during the summer, with the exception of the zooplankton parameter, sensrngcat$Zooplankton$Parameter[2], which caused an increase in \ac{do}.
-The phytoplankton parameter, sensrngcat$Phytoplankton$Parameter[2], had the largest effect such that the \ac{do} time series was similar to the default output in April/May, whereas a dramatic decrease was observed in the remaining months.
-The effects of perturbations early in the time series (January, February) showed similar patterns such that a reduction in \ac{do} was most common, particularly for the optics (sensrngcat$Optics$Parameter[2]) and phytoplankton (sensrngcat$Phytoplankton$Parameter[2]) parameters.
-%' 
-%' \subsection{Subset identifiability}
-%' 
+Among all parameters, sensitivity values ranged from $L1 = $ $8.34\times 10^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $0.01$.
+Within categories (excluding temperature), sensitivity ranged from $4.39\times 10^{-5}$ (\textit{astarOMA}) to $7.51\times 10^{-4}$ (\textit{astar490}) for optics, $4.17\times 10^{-4}$ (\textit{KNH4}) to $0.01$ (\textit{KG1}) for organic matter, $8.34\times 10^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69\times 10^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton.
+Average sensitivity values in each category were $L1 = $ $2.81\times 10^{-4}$ for optics, $0$ for organic matter, $0.02$ for temperature, $0.01$ for phytoplankton, and $0.01$ for zooplankton.
+
+Local sensitivity analyses for the additional state variables (ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus) had similar results as \ac{do} with some exceptions (\cref{fig:sensalltile,tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens}).
+All additional variables were sensitive to the same parameters (38 of 51 evaluated), although average sensitivity differed between variables.
+Average $L1$ ranged from $0.02$ for irradiance (\cref{tab:irrsens}) to $0.71$ for \ac{dom} (\cref{tab:om2sens}).
+All average sensitivity values for the state variables were higher than the average for \ac{do} ($L1$ = $0.01$).
+For each variable, $L1$ ranged from $2.24\times 10^{-6}$ (\textit{QminP}) to $8.49$ (\textit{mA}) for ammonium (\cref{tab:nh4sens}), $1.38\times 10^{-6}$ (\textit{QminP}) to $13.94$ (\textit{mA}) for \ac{chla} (\cref{tab:chlsens}), $1.92\times 10^{-7}$ (\textit{QminP}) to $0.13$ (\textit{ZKa}) for irradiance (\cref{tab:irrsens}), $6.67\times 10^{-7}$ (\textit{QminP}) to $8.49$ (\textit{umax}) for nitrate (\cref{tab:no3sens}), $6.41\times 10^{-5}$ (\textit{KNH4}) to $7.22$ (\textit{mA}) for \ac{pom} (\cref{tab:om1sens}),  $7.41\times 10^{-5}$ (\textit{KNH4}) to $14.25$ (\textit{mA}) for \ac{dom} (\cref{tab:om2sens}), and $8.21\times 10^{-7}$ (\textit{QminP}) to $1.47$ (\textit{ZKa}) for phosphate (\cref{tab:po4sens}).
+For the parameter categories, ammonium was most sensitive to phytoplankton parameters (average $L1$ = $0.8$ across all parameters in the category), \ac{chla} to phytoplankton ($L1$ = ), irradiance to zooplankton ($L1$ = $0.03$), nitrate to zooplankton ($L1$ = $1.06$), \ac{pom} to temperature ($L1$ = $0.86$), \ac{dom} to temperature ($L1$ = $1.48$), and phosphate to zooplankton ($L1$ = $0.31$).
+Finally, average sensititivy between parameter categories independent of the state variables ranged from $0.01$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
+
+\subsection{Subset identifiability}
+
 %' <<eval = F>>=
@@
 Selection independent of category showed that including par_txt(h2_brk[1]) caused in increase in $\gamma$ from scinot(h2_brk[3], digits = 1) to scinot(h2_brk[2], digits = 1) and equal selection within cateogies showed that including par_txt(h3_brk[1]) caused in increase in $\gamma$ from scinot(h3_brk[3], digits = 1) to scinot(h3_brk[2], digits = 1).
-Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
+Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, \ac{pom}, \ac{dom}, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
 Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
@@
 \hline
-{\bfseries Phytoplankton}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
+{\bfseries Optics}&&&&&&&&&\tabularnewline
 ~~\scriptsize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
 ~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$5.36$&-&$7.78$&$7.87$&-\tabularnewline
-\hline
-{\bfseries Optics}&&&&&&&&&\tabularnewline
+~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.73$\tabularnewline
 ~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&-&$10.04$\tabularnewline
-~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.73$\tabularnewline
 ~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$6.02$&-&$7.91$&$7.87$&-\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&&&&&&&\tabularnewline
+~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
+~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
+~~\scriptsize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
+~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
+~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&&&&&&&\tabularnewline
+~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
+~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$2$&-&-&-&-&-&-&$1.21$&-\tabularnewline
+~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$7.45$\tabularnewline
+~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$5$&$8.14$&-&-&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{Athresh}}&$6$&$11.27$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
-~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
-~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
-~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
-~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
-~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{respg}}&$6$&-&-&$3.41$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
-~~\scriptsize{\textit{umax}}&$2$&-&-&-&-&-&-&$1.21$&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
-~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
-~~\scriptsize{\textit{vmaxN}}&$5$&$8.14$&-&-&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{vmaxN}}&$7$&-&-&$3.97$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$7.45$\tabularnewline
 \hline
@@
 ~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
 ~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&-&-&$7.3$&$5.43$&-\tabularnewline
+~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
 ~~\scriptsize{\textit{Zm}}&$3$&-&-&$4.57$&-&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&$6.93$&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{Zm}}&$4$&-&-&-&$11.86$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
-~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&$6.93$&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{Zumax}}&$4$&-&-&$5.2$&-&-&-&-&-\tabularnewline
@@
 {\footnotesize
-\caption{Sensitivity of particulate organic matter to perturbations of individual parameters.
+\caption{Sensitivity of \ac{pom} to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
-Parameters that did not affect particulate organic matter are not shown.
+Parameters that did not affect \ac{pom} are not shown.
 Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om1sens}}
@@
 {\footnotesize
-\caption{Sensitivity of dissolved organic matter to perturbations of individual parameters.
+\caption{Sensitivity of \acl{dom} to perturbations of individual parameters.
 Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
-Parameters that did not affect dissolved organic matter are not shown.
+Parameters that did not affect \acl{dom} are not shown.
 Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om2sens}}

### 2016-11-30 R/funcs.R

@@ -1065,3 +1065,107 @@ par_tst <- function(){
   return(pars)
 
 }
+
+######
+# summarize L1 values for local  by state variable, parameter categories
+# used for inline text in manuscript
+# input files is sens_ests_cat_all for scatall
+#
+# output is list for each state variable
+# each state variable has:
+#   txt: chr string for inline text of variable name
+#   tot: total number of sensitive parameters
+#   bycat: list of number of sensitive parameters in each category
+#   lncat: list of percentage of sensitive parameters in each category
+#   sensrng: tibble with min/max sensitivity across categories
+#   sensrngcat: list of tibbles with min/max sensitivity within categories
+#   sensave: numeric of overall sensitivity
+#   sensavecat; list of average sensitivity by categories
+loc_summ <- function(scatall){
+  
+  # number of parameters in each category that were evaluated
+  p1z1pars <- par_tst()
+  nparms <- parcats2(as_df = TRUE) %>% 
+    filter(shrt %in% p1z1pars) %>% 
+    .$cats %>% 
+    table
+  
+  # names for inline txt of each state variable
+  txts <- list(
+    'NH4' = 'ammonium', 
+    'Chla_mg_tot' = '\\ac{chla}',
+    'O2' = '\\ac{do}', 
+    'irradiance' = 'irradiance',
+    'NO3' = 'nitrate ',
+    'OM1' = '\\ac{pom}',
+    'OM2' = '\\ac{dom}', 
+    'PO4' = 'phosphate'
+    )
+  
+  # output list to fill
+  out_ls <- vector('list', length = length(scatall))
+  names(out_ls) <- names(scatall)
+  
+  # iterate through state variables, elements in list
+  for(nm in names(scatall)){
+    
+    # select the state variable from the list
+    tmp <- scatall[[nm]]
+    
+    # name for inline text
+    txt <- txts[[nm]]
+    
+    # total sensitive
+    tot <- nrow(tmp)
+    
+    # number of parameters in each category
+    bycat <- table(tmp$Category)
+    nms <- names(bycat)
+    bycat <- as.numeric(bycat)
+    names(bycat) <- nms
+    bycat <- toeng(bycat)
+
+    # percent of parameters in each category
+    lncat <- table(tmp$Category) %>%
+      `/` (nparms[names(.)]) %>%
+      `*` (100) %>%
+      form_fun(nsm_val = 0) %>%
+      as.list %>%
[…]

### 2016-11-30 ident_manu.Rnw
first paragraph of ident results done

@@
 Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{locO2$sensrng$error[1]} for \Sexpr{locO2$sensrng$Parameter[1]} (\Sexpr{tolower(locO2$sensrng$Category[1])}) to \Sexpr{locO2$sensrng$error[2]} for \Sexpr{locO2$sensrng$Parameter[2]} (\Sexpr{tolower(locO2$sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{locO2$sensave}.
-Within categories (excluding temperature), sensitivity ranged from \Sexpr{locO2$sensrngcat$Optics$error[1]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Optics$error[2]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{locO2$sensrngcat$`Organic Matter`$error[1]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{locO2$sensrngcat$`Organic Matter`$error[2]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{locO2$sensrngcat$Phytoplankton$error[1]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Phytoplankton$error[2]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[2]}) for phytoplankton, and \Sexpr{locO2$sensrngcat$Zooplankton$error[1]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Zooplankton$error[2]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[2]}) for zooplankton.
+Within categories (excluding temperature), sensitivity ranged from \Sexpr{locO2$sensrngcat$Optics$error[1]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Optics$error[2]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{locO2$sensrngcat$`Organic Matter`$error[1]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{locO2$sensrngcat$`Organic Matter`$error[2]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{locO2$sensrngcat$Phytoplankton$error[1]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Phytoplankton$error[2]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[2]}) for phytoplankton, and \Sexpr{locO2$sensrngcat$Zooplankton$error[1]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Zooplankton$error[2]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{tab:dosens}).
 Average sensitivity values in each category were $L1 = $ \Sexpr{locO2$sensavecat$Optics} for optics, \Sexpr{locO2$sensavecat$`Organic Matter`} for organic matter, \Sexpr{locO2$sensavecat$Temperature} for temperature, \Sexpr{locO2$sensavecat$Phytoplankton} for phytoplankton, and \Sexpr{locO2$sensavecat$Zooplankton} for zooplankton.
@@
 For each variable, $L1$ ranged from \Sexpr{locNH4$sensrng[1, 2]} (\Sexpr{locNH4$sensrng[1, 1]}) to \Sexpr{locNH4$sensrng[2, 2]} (\Sexpr{locNH4$sensrng[2, 1]}) for ammonium (\cref{tab:nh4sens}), \Sexpr{locChla_mg_tot$sensrng[1, 2]} (\Sexpr{locChla_mg_tot$sensrng[1, 1]}) to \Sexpr{locChla_mg_tot$sensrng[2, 2]} (\Sexpr{locChla_mg_tot$sensrng[2, 1]}) for \ac{chla} (\cref{tab:chlsens}), \Sexpr{locirradiance$sensrng[1, 2]} (\Sexpr{locirradiance$sensrng[1, 1]}) to \Sexpr{locirradiance$sensrng[2, 2]} (\Sexpr{locirradiance$sensrng[2, 1]}) for irradiance (\cref{tab:irrsens}), \Sexpr{locNO3$sensrng[1, 2]} (\Sexpr{locNO3$sensrng[1, 1]}) to \Sexpr{locNO3$sensrng[2, 2]} (\Sexpr{locNO3$sensrng[2, 1]}) for nitrate (\cref{tab:no3sens}), \Sexpr{locOM1$sensrng[1, 2]} (\Sexpr{locOM1$sensrng[1, 1]}) to \Sexpr{locOM1$sensrng[2, 2]} (\Sexpr{locOM1$sensrng[2, 1]}) for \ac{pom} (\cref{tab:om1sens}),  \Sexpr{locOM2$sensrng[1, 2]} (\Sexpr{locOM2$sensrng[1, 1]}) to \Sexpr{locOM2$sensrng[2, 2]} (\Sexpr{locOM2$sensrng[2, 1]}) for \ac{dom} (\cref{tab:om2sens}), and \Sexpr{locPO4$sensrng[1, 2]} (\Sexpr{locPO4$sensrng[1, 1]}) to \Sexpr{locPO4$sensrng[2, 2]} (\Sexpr{locPO4$sensrng[2, 1]}) for phosphate (\cref{tab:po4sens}).
-For the parameter categories, ammonium was most sensitive to \Sexpr{names(maxcat$NH4)} parameters (average $L1$ = \Sexpr{maxcat$NH4} across all parameters in the category), \ac{chla} to \Sexpr{names(maxcat$Chla_mg_tot)} ($L1$ = \Sexpr{maxcat$Chla_mg_tat}), irradiance to \Sexpr{names(maxcat$irradiance)} ($L1$ = \Sexpr{maxcat$irradiance}), nitrate to \Sexpr{names(maxcat$NO3)} ($L1$ = \Sexpr{maxcat$NO3}), \ac{pom} to \Sexpr{names(maxcat$OM1)} ($L1$ = \Sexpr{maxcat$OM1}), \ac{dom} to \Sexpr{names(maxcat$OM2)} ($L1$ = \Sexpr{maxcat$OM2}), and phosphate to \Sexpr{names(maxcat$PO4)} ($L1$ = \Sexpr{maxcat$PO4}).
+For the parameter categories, ammonium was most sensitive to \Sexpr{names(maxcat$NH4)} parameters (average $L1$ = \Sexpr{maxcat$NH4} across all parameters in the category), \ac{chla} to \Sexpr{names(maxcat$Chla_mg_tot)} ($L1$ = \Sexpr{maxcat$Chla_mg_tot}), irradiance to \Sexpr{names(maxcat$irradiance)} ($L1$ = \Sexpr{maxcat$irradiance}), nitrate to \Sexpr{names(maxcat$NO3)} ($L1$ = \Sexpr{maxcat$NO3}), \ac{pom} to \Sexpr{names(maxcat$OM1)} ($L1$ = \Sexpr{maxcat$OM1}), \ac{dom} to \Sexpr{names(maxcat$OM2)} ($L1$ = \Sexpr{maxcat$OM2}), and phosphate to \Sexpr{names(maxcat$PO4)} ($L1$ = \Sexpr{maxcat$PO4}).
 Finally, average sensititivy between parameter categories independent of the state variables ranged from \Sexpr{avecat[1]} for \Sexpr{names(avecat)[1]} (average $L1$ across all variables) to \Sexpr{avecat[length(avecat)]} for \Sexpr{names(avecat)[length(avecat)]}.
@@
 
-%' <<eval = F>>=
-%' data(cat_ident)
-%' data(top_ident)
-%' 
-%' # percent combos less than gamma 15, 10 by category
-%' collcatpers <- lapply(cat_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' 
-%' # percent combos less than gamma 15, 10 by top in each category
-%' colltoppers <- lapply(top_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' 
-%' maxtempcoll <- scinot(max(cat_ident$Temperature$coll))
-%' @
-%' 
-%' The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
-Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
-By category, identifiability was lowest for parameter subsets in the phytoplankton (\Sexpr{collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$)  and zooplankton categories (\Sexpr{collcatpers$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{collcatpers$Zooplankton[2]}\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable (\Sexpr{collcatpers$Temperature[1]}\% less than $\gamma = 15$, \Sexpr{collcatpers$Temperature[2]}\%, less than $\gamma = 10$).
-All subset combinations for optics and organic matter parameters had $\gamma < 10$.
-All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\% less than $\gamma = 10$) and top five (\Sexpr{colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{colltoppers$top4[2]}\%, less than $\gamma = 10$) parameters.
-%' 
+<<eval = T>>=
+data(cat_ident_all)
+data(top_ident_all)
+
+# percent combos less than gamma 15, 10 by state variable, by parameter category
+# temperature category not evaluated, only one paramaeter
+collcatpers <- lapply(cat_ident_all, function(stvar){
+
+  lapply(stvar[!names(stvar) %in% 'Temperature'], function(x){
+
+    colls <- x$coll
+    l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+    l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+    c(l15, l10)
+
+  })
+
+})
+
+# percent combos less than gamma 15, 10 by state variable, by top in each category
+colltoppers <- lapply(top_ident_all, function(stvar){
+
+  lapply(stvar, function(x){
+
+    colls <- x$coll
+    l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
+    l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
+    c(l15, l10)
+
+  })
+
+})
+
+catpersO2 <- collcatpers$O2
+toppersO2 <- colltoppers$O2
+@
+
+The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
+Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
+By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\%, less than $\gamma = 10$), whereas a all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\%, less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\%, less than $\gamma = 10$) combinations were identifiable.
+Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
+Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
+The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15$ and \Sexpr{toppersO2$top1[2]}\% less than $\gamma = 10$ for the top parameters in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the fop four.
+
+An alternative view of the results in \cref{fig:identplo} to identify percent combinations that were identifiable as a function of number of parameters in each subset is show in
+
 %' <<eval = F>>=
@@
 Interestingly, no parameters from the temperature category were selected.
+
+\subsection{Observational and structural uncertainty}
 

### 2016-11-30 ident_manu.tex
first paragraph of ident results done

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Nov 29 17:13:44 2016 -0600
+  \\ Version Date:   Wed Nov 30 14:30:44 2016 -0600
 	}
@@
 Among all parameters, sensitivity values ranged from $L1 = $ $8.34\times 10^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $0.01$.
-Within categories (excluding temperature), sensitivity ranged from $4.39\times 10^{-5}$ (\textit{astarOMA}) to $7.51\times 10^{-4}$ (\textit{astar490}) for optics, $4.17\times 10^{-4}$ (\textit{KNH4}) to $0.01$ (\textit{KG1}) for organic matter, $8.34\times 10^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69\times 10^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton.
+Within categories (excluding temperature), sensitivity ranged from $4.39\times 10^{-5}$ (\textit{astarOMA}) to $7.51\times 10^{-4}$ (\textit{astar490}) for optics, $4.17\times 10^{-4}$ (\textit{KNH4}) to $0.01$ (\textit{KG1}) for organic matter, $8.34\times 10^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69\times 10^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton (\cref{tab:dosens}).
 Average sensitivity values in each category were $L1 = $ $2.81\times 10^{-4}$ for optics, $0$ for organic matter, $0.02$ for temperature, $0.01$ for phytoplankton, and $0.01$ for zooplankton.
@@
 For each variable, $L1$ ranged from $2.24\times 10^{-6}$ (\textit{QminP}) to $8.49$ (\textit{mA}) for ammonium (\cref{tab:nh4sens}), $1.38\times 10^{-6}$ (\textit{QminP}) to $13.94$ (\textit{mA}) for \ac{chla} (\cref{tab:chlsens}), $1.92\times 10^{-7}$ (\textit{QminP}) to $0.13$ (\textit{ZKa}) for irradiance (\cref{tab:irrsens}), $6.67\times 10^{-7}$ (\textit{QminP}) to $8.49$ (\textit{umax}) for nitrate (\cref{tab:no3sens}), $6.41\times 10^{-5}$ (\textit{KNH4}) to $7.22$ (\textit{mA}) for \ac{pom} (\cref{tab:om1sens}),  $7.41\times 10^{-5}$ (\textit{KNH4}) to $14.25$ (\textit{mA}) for \ac{dom} (\cref{tab:om2sens}), and $8.21\times 10^{-7}$ (\textit{QminP}) to $1.47$ (\textit{ZKa}) for phosphate (\cref{tab:po4sens}).
-For the parameter categories, ammonium was most sensitive to phytoplankton parameters (average $L1$ = $0.8$ across all parameters in the category), \ac{chla} to phytoplankton ($L1$ = ), irradiance to zooplankton ($L1$ = $0.03$), nitrate to zooplankton ($L1$ = $1.06$), \ac{pom} to temperature ($L1$ = $0.86$), \ac{dom} to temperature ($L1$ = $1.48$), and phosphate to zooplankton ($L1$ = $0.31$).
+For the parameter categories, ammonium was most sensitive to phytoplankton parameters (average $L1$ = $0.8$ across all parameters in the category), \ac{chla} to phytoplankton ($L1$ = $1.14$), irradiance to zooplankton ($L1$ = $0.03$), nitrate to zooplankton ($L1$ = $1.06$), \ac{pom} to temperature ($L1$ = $0.86$), \ac{dom} to temperature ($L1$ = $1.48$), and phosphate to zooplankton ($L1$ = $0.31$).
 Finally, average sensititivy between parameter categories independent of the state variables ranged from $0.01$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
@@
 
-%' <<eval = F>>=
-%' data(cat_ident)
-%' data(top_ident)
-%' 
-%' # percent combos less than gamma 15, 10 by category
-%' collcatpers <- lapply(cat_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' 
-%' # percent combos less than gamma 15, 10 by top in each category
-%' colltoppers <- lapply(top_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' 
-%' maxtempcoll <- scinot(max(cat_ident$Temperature$coll))
-%' @
-%' 
-%' The identifiability analyses suggested that most parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
-Parameter identifiability (as $\gamma$) increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identbox}).
-By category, identifiability was lowest for parameter subsets in the phytoplankton (collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, collcatpers$Phytoplankton[2]\% less than $\gamma = 10$)  and zooplankton categories (collcatpers$Zooplankton[1]\%, less than $\gamma = 15$, collcatpers$Zooplankton[2]\%, less than $\gamma = 10$), whereas a majority of combinations for temperature were identifiable (collcatpers$Temperature[1]\% less than $\gamma = 15$, collcatpers$Temperature[2]\%, less than $\gamma = 10$).
-All subset combinations for optics and organic matter parameters had $\gamma < 10$.
-All parameter subsets for choosing the top, top two, and top three parameters in each category were identifiable (\cref{fig:identbox}), whereas a majority were identifiable for choosing the top four (colltoppers$top4[1]\% less than $\gamma = 15$, colltoppers$top4[2]\% less than $\gamma = 10$) and top five (colltoppers$top4[1]\% less than $\gamma = 15$, colltoppers$top4[2]\%, less than $\gamma = 10$) parameters.
-%' 
+The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
+Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
+Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
+By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\%, less than $\gamma = 15$, $40$\%, less than $\gamma = 10$), whereas a all combinations were identifiable for optics ($100$\%, less than $\gamma = 15$, $100$\%, less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\%, less than $\gamma = 15$, $76.5$\%, less than $\gamma = 10$) combinations were identifiable.
+Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
+Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
+The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15$ and $100$\% less than $\gamma = 10$ for the top parameters in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the fop four.
+
+An alternative view of the results in \cref{fig:identplo} to identify percent combinations that were identifiable as a function of number of parameters in each subset is show in
+
 %' <<eval = F>>=

### 2016-11-30 R/funcs.R

@@ -42,22 +42,39 @@ form_fun <- function(x, rnd_val = 2, dig_val = 2, nsm_val = 2, ...) {
 # from https://dankelley.github.io/r/2015/03/22/scinot.html
 scinot <- function(x, pow = 3, digits = 2, showDollar = TRUE)
 {
+  
   x <- as.numeric(x)
-  sign <- ""
-  if (x < 0) {
-      sign <- "-"
-      x <- -x
-  }
-  exponent <- floor(log10(x))
-  if (exponent & abs(exponent) > pow) {
-      xx <- round(x / 10^exponent, digits=digits)
-      e <- paste("\\times 10^{", as.integer(exponent), "}", sep="")
+  
+  # only do this is x is not equal to zero
+  if(x != 0){
+    
+    sign <- ""
+    if (x < 0) {
+        sign <- "-"
+        x <- -x
+    }
+    exponent <- floor(log10(x))
+    if (exponent & abs(exponent) > pow) {
+        xx <- round(x / 10^exponent, digits=digits)
+        e <- paste("\\times 10^{", as.integer(exponent), "}", sep="")
+    } else {
+        xx <- round(x, digits=digits)
+        e <- ""
+    }
+    
+    out <- paste(sign, xx, e, sep="")
+    
   } else {
-      xx <- round(x, digits=digits)
-      e <- ""
+    
+    out <- x
+    
   }
-  if (showDollar) paste("$", sign, xx, e, "$", sep="")
-  else paste(sign, xx, e, sep="")
+  
+  # add dollars if true
+  if (showDollar) out <- paste("$", out, "$", sep="")
+  
+  return(out)
+  
 }
 
 # alternative list structure for parameter categories

### 2016-12-01 ident_manu.Rnw
percthresh fig added

@@
 Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
-Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\%, less than $\gamma = 10$), whereas a all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\%, less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\%, less than $\gamma = 10$) combinations were identifiable.
+Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
+By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas a all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\% less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$) combinations were identifiable.
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
@@
 The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15$ and \Sexpr{toppersO2$top1[2]}\% less than $\gamma = 10$ for the top parameters in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the fop four.
+Results for the remaining state variables had similar patterns in identifability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
+Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.
 
@@
 To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
-Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (\Sexpr{p1z1collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$ for Phytoplankton; \Sexpr{p1z1collcatpers$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Zooplankton[2]}\%, less than $\gamma = 10$ for zooplankton).
+Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (\Sexpr{p1z1collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$ for Phytoplankton; \Sexpr{p1z1collcatpers$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Zooplankton[2]}\% less than $\gamma = 10$ for zooplankton).
 Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.
@@
 
+@
+
+% percent below gamma thresholds
+<<percthresh, eval = T, fig.cap = 'Percent of identifiable parameter sets for \\ac{do} at different $\\gamma$ thresholds, selection criteria, and total number of parameters in the set.
+Thresholds varied from $\\gamma = 2$ to $20$ such that sets with $\\gamma$ below a threshold were considered identifiable relative to the value.
+Plots in (a) show percent of identifiable sets by selecting parameters within categories and (b) shows percent identifiable by selecting from the top 1 through 4 parameters in all categories.
+Percent identifiable was based on all sets in \\cref{fig:identplo}.', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=
+data(cat_ident_all)
+data(top_ident_all)
+
+# state variable, categories (no temp ident because only one parameter)
+catnms <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Zooplankton')
+toplevs <- paste0('top', 1:4)
+toplabs <- paste('Top', 1:4)
+stts_lev <- c('O2')
+stts_lab <- c('Dissolved Oxygen')
+
+thresh <- seq(2, 20, by = 2)
+
+# percent combos less than gamma 15, 10 by state variable, by parameter category
+# temperature category not evaluated, only one paramaeter
+collcatpers <- lapply(cat_ident_all[stts_lev], function(stvar){
+
+  bystvar <- lapply(stvar[!names(stvar) %in% 'Temperature'], function(x){
+
+    bysets <- split(x, x$N) %>% 
+      lapply(function(sets){
+        colls <- sets$coll
+        sapply(thresh, function(x) 100 * sum(colls < x)/length(colls))
+
+      }) %>% 
+      do.call('rbind', .) %>% 
+      data.frame(
+        nparms = row.names(.), 
+        .
+      ) %>% 
+      mutate(
+        nparms = as.numeric(as.character(nparms))
+      ) %>% 
+      gather('lval', 'perc', -nparms) %>% 
+      mutate(lval = factor(lval, 
+        levels = paste0('X', 1:length(thresh)), 
+        labels = paste0('l', thresh)
+      ))
+    bysets
+
+  }) %>% 
+  reshape2::melt(., id.vars = names(.[[1]])) %>% 
+  rename(Category = L1)
+
+  return(bystvar)
+
+  }) %>% 
+  reshape2::melt(., id.vars = names(.[[1]])) %>% 
+  rename(`State variable` = L1) %>% 
+  mutate(
+    `State variable` = factor(`State variable`, levels = stts_lev, labels = stts_lab),
+    Category = factor(Category, levels = catnms), 
+    Threshold = gsub('^l', '', lval),
+    Threshold = as.numeric(Threshold)
+    )
+
+colltoppers <- lapply(top_ident_all[stts_lev], function(stvar){
+
+  bystvar <- lapply(stvar, function(x){
+
+    bysets <- split(x, x$N) %>% 
+      lapply(function(sets){
+        colls <- sets$coll
+        sapply(thresh, function(x) 100 * sum(colls < x)/length(colls))
+
+      }) %>% 
+      do.call('rbind', .) %>% 
+      data.frame(
+        nparms = row.names(.), 
+        .
+      ) %>% 
+      mutate(
+        nparms = as.numeric(as.character(nparms))
+      ) %>% 
+      gather('lval', 'perc', -nparms) %>% 
+      mutate(lval = factor(lval, 
+        levels = paste0('X', 1:length(thresh)), 
+        labels = paste0('l', thresh)
+      ))
+    bysets
+
+  }) %>% 
+  reshape2::melt(., id.vars = names(.[[1]])) %>% 
+  rename(Category = L1) %>% 
+  filter(!Category %in% 'top5')
+
+  return(bystvar)
+
+  }) %>% 
+  reshape2::melt(., id.vars = names(.[[1]])) %>% 
+  rename(`State variable` = L1) %>% 
+  mutate(
+    `State variable` = factor(`State variable`, levels = stts_lev, labels = stts_lab),
+    Category = factor(Category, levels = toplevs, labels = toplabs), 
+    Threshold = gsub('^l', '', lval),
+    Threshold = as.numeric(Threshold)
+    )
+
+toplo1 <- collcatpers
+toplo2 <- colltoppers
+
+# default theme
+mytheme <- theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.x = element_blank(), 
+    axis.title.y = element_blank(),
+    axis.ticks.x = element_line(),
+    axis.ticks.y = element_line(),
+    axis.ticks.length = unit(.1, "cm"), 
+    legend.position = 'none'
+  )
+
+lncol <- 'darkgrey'
+sz <- 3
+
+p1 <- ggplot(toplo1, aes(x = nparms, group = lval)) + 
+  geom_line(aes(y = perc), colour = lncol) + 
+  geom_point(aes(y = perc, fill = Threshold), shape = 21, colour = lncol, 
+    size = sz
+    ) + 
+  scale_fill_distiller(palette = "Spectral") +
+  facet_wrap(~ Category, ncol = 1) +
+  mytheme +
+  ggtitle('(a) By parameter category')
+
+p2 <- ggplot(toplo2, aes(x = nparms, group = lval)) + 
+  geom_line(aes(y = perc), colour = lncol) + 
+  geom_point(aes(y = perc, fill = Threshold), shape = 21, colour = lncol, 
+    size = sz
+    ) + 
+  scale_fill_distiller(palette = "Spectral") +
+  facet_wrap(~ Category, ncol = 1) +
+  mytheme +
+  ggtitle('(b) By top parameters, all categories')
+
+pleg <- ggplot(toplo2, aes(x = nparms, group = lval)) + 
+  geom_point(aes(y = perc, fill = Threshold)) + 
+  scale_fill_distiller(palette = "Spectral")
+pleg <- g_legend(pleg)
+
+grid.arrange(
+  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
+  left = 'Percent identifiable sets',
+  pleg, ncol = 2, widths = c(1, 0.2)
+)
 @

### 2016-12-01 ident_manu.tex
percthresh fig added

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Nov 30 14:30:44 2016 -0600
+  \\ Version Date:   Wed Nov 30 17:02:50 2016 -0600
 	}
@@
 Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
-Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\%, less than $\gamma = 15$, $40$\%, less than $\gamma = 10$), whereas a all combinations were identifiable for optics ($100$\%, less than $\gamma = 15$, $100$\%, less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\%, less than $\gamma = 15$, $76.5$\%, less than $\gamma = 10$) combinations were identifiable.
+Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
+By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas a all combinations were identifiable for optics ($100$\% less than $\gamma = 15$, $100$\% less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$) combinations were identifiable.
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
@@
 The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15$ and $100$\% less than $\gamma = 10$ for the top parameters in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the fop four.
+Results for the remaining state variables had similar patterns in identifability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
+Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.
 
@@
 To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
-Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (p1z1collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Phytoplankton[2]\% less than $\gamma = 10$ for Phytoplankton; p1z1collcatpers$Zooplankton[1]\%, less than $\gamma = 15$, p1z1collcatpers$Zooplankton[2]\%, less than $\gamma = 10$ for zooplankton).
+Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (p1z1collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Phytoplankton[2]\% less than $\gamma = 10$ for Phytoplankton; p1z1collcatpers$Zooplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Zooplankton[2]\% less than $\gamma = 10$ for zooplankton).
 Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.
@@
 
+% percent below gamma thresholds
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\maxwidth]{figs/percthresh-1}
+
+}
+
+\caption{Percent of identifiable parameter sets for \ac{do} at different $\gamma$ thresholds, selection criteria, and total number of parameters in the set.
+Thresholds varied from $\gamma = 2$ to $20$ such that sets with $\gamma$ below a threshold were considered identifiable relative to the value.
+Plots in (a) show percent of identifiable sets by selecting parameters within categories and (b) shows percent identifiable by selecting from the top 1 through 4 parameters in all categories.
+Percent identifiable was based on all sets in \cref{fig:identplo}.}\label{fig:percthresh}
+\end{figure}
+
 % parameter exclusion temp

### 2016-12-01 ident_manu.Rnw
identifiability results section done

@@
 
-An alternative view of the results in \cref{fig:identplo} to identify percent combinations that were identifiable as a function of number of parameters in each subset is show in
-
-%' <<eval = F>>=
-%' temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
-%' @
-%' 
-%' A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
-For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.
-Further evaluation showed that identifiability was greatly affected by the inclusion of one or two specific parameters in a subset combination.
-\Cref{fig:excltemp} shows the temperature collinearity ($\gamma$) ranges in detail for the parameter subsets in \cref{fig:identbox} before and after excluding individual parameters.
-Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.
-Exclusion of the parameters \Sexpr{temp_coll[2]} and \Sexpr{temp_coll[5]} showed that $\gamma$ remained well below the 10, 15 threshold for all parameter combinations.
-Morever, inclusion of \Sexpr{temp_coll[1]}, \Sexpr{temp_coll[4]}, \Sexpr{temp_coll[7]}, and \Sexpr{temp_coll[8]} generally reduced collinearity relative to when the parameters were excluded.
-Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).
-%' 
-%' <<eval = F>>=
-%' data(p1z1cat_ident)
-%' data(p1z1top_ident)
-%' 
-%' # percent combos less than gamma 15, 10 by category
-%' p1z1collcatpers <- lapply(p1z1cat_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' 
-%' # percent combos less than gamma 15, 10 by top in each category
-%' p1z1colltoppers <- lapply(p1z1top_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' @
-%' 
-%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
-As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.
-However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs.
-fast-growing plankton.
-To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
-Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (\Sexpr{p1z1collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$ for Phytoplankton; \Sexpr{p1z1collcatpers$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Zooplankton[2]}\% less than $\gamma = 10$ for zooplankton).
-Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.
-Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (\Sexpr{p1z1colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top4[2]}\% less than $\gamma = 10$) and a decrease (\Sexpr{p1z1colltoppers$top5[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top5[2]}\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).
-%' 
-%' \subsection{Parameter selection}
-%' 
+An alternative view of the results in \cref{fig:identplo} can be used to demonstrate the effects of parameter selection criteria and number of parameters in the selection pool on identifiability.
+\Cref{fig:percthresh} shows the percentage of identifiable parameter sets for \ac{do} using the same selection criteria in \cref{fig:identplo}, i.e., selection of parameters only within parameter categories and selection of the top sensitive parameters regardless of category.
+\Cref{fig:percthresh} is conceptually similar to \cref{fig:identplo}, with the added effect of a chosen $\gamma$ threshold on identifability.
+Previous studies have provided general rules for $\gamma$ thresholds, such that exact values beyond which model calibration fails could vary for the given model and optimization method.
+The selected $\gamma$ thresholds are somewhat arbitrary, although the results show differences that have implications for parameter selection for model calibration.
+In general, identifiability decreases with the addition of parameters, although the rate of decrease depends on the selected threshold for $\gamma$.
+Notable differences in identifiability are also observed by selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
+
+<<eval = T>>=
+om_coll <- par_txt(paste0(c('KG1', 'KG2', 'KGcdom', 'KNH4', 'KNO3', 'KO2', 'KstarO2', 'nitmax'), '_1'))
+@
+
+An evaluation of the effects of individual parameters on $\gamma$ further suggested that some parameters have disproportionate effects on identifiability.
+Based on $\gamma = 15$, \cref{fig:identplo} suggests that most parameter sets for organic matter were identifiable, regardless of how many parameters were selected (i.e., two through eight).
+Because identifiability of the organic matter parameters was generally acceptable, identification of one or more redundant parameters that are inflating $\gamma$ values could provide useful information.
+\Cref{fig:exclex} shows an alternative view of identifiability of \ac{do} with exclusion and inclusion of individual parameters in different sets for the organic matter category.
+Collinearity increases with more parameters included in a subset, although the increase varies depending on which parameter was included or excluded from the set.
+For example, inclusion of \Sexpr{om_coll[5]} in a parameter set almost always inflated $\gamma$.
+All parameter subsets that did not include \Sexpr{om_coll[5]} were well below $\gamma = 15$, suggesting that removal of this parameter improves identifiability.
+Interestingly, the inclusion of some parameters caused a reduction in $\gamma$, which contradicts the general rule that more parameters caused reduced identifiablity.
+For example, parameter sets that included \Sexpr{om_coll[3]} generally had lower $\gamma$ values relative to those that excluded the parameter.
+
+\subsection{Parameter selection}
+
 %' <<eval = F>>=
@@
   mutate(numparms = as.numeric(gsub('^X', '', numparms))) %>% 
-  filter(combs > 0) %>% 
-  mutate(combs = log(combs))
+  filter(combs > 0)# %>% 
+  # mutate(combs = log(combs))
 
@@
   scale_fill_distiller(palette = pal, 
-    guide = guide_legend(title = 'Number of unique parameter\ncombinations, log-scale')) + 
+    guide = guide_legend(title = 'Number of unique parameter\ncombinations'),
+    trans = 'log10'
+    ) + 
   scale_x_continuous('Total number of parameters in set', expand = c(0, 0)) + 

### 2016-12-01 ident_manu.tex
identifiability results section done

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Nov 30 17:02:50 2016 -0600
+  \\ Version Date:   Thu Dec 1 12:24:21 2016 -0600
 	}
@@
 
-An alternative view of the results in \cref{fig:identplo} to identify percent combinations that were identifiable as a function of number of parameters in each subset is show in
-
-%' <<eval = F>>=
-%' temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
-%' @
-%' 
-%' A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).
-For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.
-Further evaluation showed that identifiability was greatly affected by the inclusion of one or two specific parameters in a subset combination.
-\Cref{fig:excltemp} shows the temperature collinearity ($\gamma$) ranges in detail for the parameter subsets in \cref{fig:identbox} before and after excluding individual parameters.
-Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.
-Exclusion of the parameters temp_coll[2] and temp_coll[5] showed that $\gamma$ remained well below the 10, 15 threshold for all parameter combinations.
-Morever, inclusion of temp_coll[1], temp_coll[4], temp_coll[7], and temp_coll[8] generally reduced collinearity relative to when the parameters were excluded.
-Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).
-%' 
-%' <<eval = F>>=
-%' data(p1z1cat_ident)
-%' data(p1z1top_ident)
-%' 
-%' # percent combos less than gamma 15, 10 by category
-%' p1z1collcatpers <- lapply(p1z1cat_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' 
-%' # percent combos less than gamma 15, 10 by top in each category
-%' p1z1colltoppers <- lapply(p1z1top_ident, function(x){
-%'   
-%'   colls <- x$coll
-%'   l15 <- scinot(100 * sum(colls < 15)/length(colls), digits = 1)
-%'   l10 <- scinot(100 * sum(colls < 10)/length(colls), digits = 1)
-%'   c(l15, l10)
-%'   
-%'   })
-%' @
-%' 
-%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.
-As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.
-However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs.
-fast-growing plankton.
-To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}).
-Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (p1z1collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Phytoplankton[2]\% less than $\gamma = 10$ for Phytoplankton; p1z1collcatpers$Zooplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Zooplankton[2]\% less than $\gamma = 10$ for zooplankton).
-Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.
-Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (p1z1colltoppers$top4[1]\% less than $\gamma = 15$, p1z1colltoppers$top4[2]\% less than $\gamma = 10$) and a decrease (p1z1colltoppers$top5[1]\% less than $\gamma = 15$, p1z1colltoppers$top5[2]\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).
-%' 
-%' \subsection{Parameter selection}
-%' 
+An alternative view of the results in \cref{fig:identplo} can be used to demonstrate the effects of parameter selection criteria and number of parameters in the selection pool on identifiability.
+\Cref{fig:percthresh} shows the percentage of identifiable parameter sets for \ac{do} using the same selection criteria in \cref{fig:identplo}, i.e., selection of parameters only within parameter categories and selection of the top sensitive parameters regardless of category.
+\Cref{fig:percthresh} is conceptually similar to \cref{fig:identplo}, with the added effect of a chosen $\gamma$ threshold on identifability.
+Previous studies have provided general rules for $\gamma$ thresholds, such that exact values beyond which model calibration fails could vary for the given model and optimization method.
+The selected $\gamma$ thresholds are somewhat arbitrary, although the results show differences that have implications for parameter selection for model calibration.
+In general, identifiability decreases with the addition of parameters, although the rate of decrease depends on the selected threshold for $\gamma$.
+Notable differences in identifiability are also observed by selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
+
+An evaluation of the effects of individual parameters on $\gamma$ further suggested that some parameters have disproportionate effects on identifiability.
+Based on $\gamma = 15$, \cref{fig:identplo} suggests that most parameter sets for organic matter were identifiable, regardless of how many parameters were selected (i.e., two through eight).
+Because identifiability of the organic matter parameters was generally acceptable, identification of one or more redundant parameters that are inflating $\gamma$ values could provide useful information.
+\Cref{fig:exclex} shows an alternative view of identifiability of \ac{do} with exclusion and inclusion of individual parameters in different sets for the organic matter category.
+Collinearity increases with more parameters included in a subset, although the increase varies depending on which parameter was included or excluded from the set.
+For example, inclusion of \textit{KNO3} in a parameter set almost always inflated $\gamma$.
+All parameter subsets that did not include \textit{KNO3} were well below $\gamma = 15$, suggesting that removal of this parameter improves identifiability.
+Interestingly, the inclusion of some parameters caused a reduction in $\gamma$, which contradicts the general rule that more parameters caused reduced identifiablity.
+For example, parameter sets that included \textit{KGcdom} generally had lower $\gamma$ values relative to those that excluded the parameter.
+
+\subsection{Parameter selection}
+
 %' <<eval = F>>=

### 2016-12-02 ident_manu.Rnw
results draft done

@@
 Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas a all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\% less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$) combinations were identifiable.
+By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\% less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$) combinations were identifiable.
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
@@
 \Cref{fig:percthresh} is conceptually similar to \cref{fig:identplo}, with the added effect of a chosen $\gamma$ threshold on identifability.
-Previous studies have provided general rules for $\gamma$ thresholds, such that exact values beyond which model calibration fails could vary for the given model and optimization method.
+Previous studies have provided general rules for $\gamma$ thresholds \citep{Brun01,Omlin01}, such that exact values beyond which model calibration fails could vary for the given model and optimization method.
 The selected $\gamma$ thresholds are somewhat arbitrary, although the results show differences that have implications for parameter selection for model calibration.
 In general, identifiability decreases with the addition of parameters, although the rate of decrease depends on the selected threshold for $\gamma$.
-Notable differences in identifiability are also observed by selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
+More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset.
+Notable differences in identifiability were also observed by selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
 
@@
 
-%' <<eval = F>>=
-%' data(tocal)
-%' 
-%' # n parms and ident for each selection heuristic
-%' h1_id <- tocal$cat %>% 
-%'   split(., .$Category) %>% 
-%'   lapply(function(x){
-%'     x <- x[x$coll < 15, ]
-%'     list(nrow(x), scinot(max(x$coll), digits = 1))
-%'   }) 
-%' h2_id <- filter(tocal$top, coll < 15) %>%
-%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
-%'   .[c(2, 3)]
-%' h3_id <- filter(tocal$cattop, coll < 15) %>%
-%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
-%'   .[c(2, 3)]
-%' 
-%' # which parameter broke selection for h2, h3
-%' h2_brk <- tocal$top
-%' sel <- which(h2_brk$coll < 15)
-%' h2_brk <- h2_brk[c(sel, rev(sel)[1] + 1), ] %>% 
-%'   arrange(-coll) %>% 
-%'   .[1:2, ] %>% 
-%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
-%'   .[[2]]
-%' # which parameter broke selection for h2, h3
-%' h3_brk <- tocal$cattop
-%' sel <- which(h3_brk$coll < 15)
-%' h3_brk <- h3_brk[c(sel, rev(sel)[1] + 1), ] %>% 
-%'   arrange(-coll) %>% 
-%'   .[1:2, ] %>% 
-%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
-%'   .[[2]]
-%' @
-%' 
-%' Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
-For the first selection heuristic, all sensitive parameters from the optics ($n = $ \Sexpr{scinot(h1_id$Optics[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$Optics[[2]]}) and organic matter ($n = $ \Sexpr{scinot(h1_id$`Organic Matter`[[1]], digits = 0)}, $\gamma =$  \Sexpr{h1_id$`Organic Matter`[[2]]}) categories were selected, whereas \Sexpr{toeng(h1_id$Phytoplankton[[1]])[[1]]} were selected for phytoplankton ($\gamma = $ \Sexpr{h1_id$Phytoplankton[[2]]}), \Sexpr{toeng(h1_id$Temperature[[1]])[[1]]} for temperature ($\gamma = $ \Sexpr{h1_id$Temperature[[2]]}), and \Sexpr{toeng(h1_id$Zooplankton[[1]])[[1]]} for zooplankton ($\gamma = $ \Sexpr{h1_id$Zooplankton[[2]]}).
-For the second selection heuristic, \Sexpr{toeng(h2_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h2_id[[2]]}, with a majority from the phytoplankton category, \cref{tab:identall1}).
-For the third heuristic, \Sexpr{toeng(h3_id[[1]])[[1]]} parameters were selected ($\gamma = $ \Sexpr{h3_id[[2]]}) with equal representation between categories.
-For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.
-Selection independent of category showed that including \Sexpr{par_txt(h2_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h2_brk[3], digits = 1)} to \Sexpr{scinot(h2_brk[2], digits = 1)} and equal selection within cateogies showed that including \Sexpr{par_txt(h3_brk[1])} caused in increase in $\gamma$ from \Sexpr{scinot(h3_brk[3], digits = 1)} to \Sexpr{scinot(h3_brk[2], digits = 1)}.
-Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, \ac{pom}, \ac{dom}, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
-Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
-Interestingly, no parameters from the temperature category were selected.
+<<eval = T>>=
+data(tocal_all)
+
+# average number of parmaeters in each category for first heurist
+# independent of state variable
+catave <- lapply(tocal_all, 
+  function(x){
+
+    x$cat %>% 
+    group_by(Category) %>% 
+    summarise(cnt = sum(coll < 15))
+
+  }) %>% 
+  reshape2::melt(., id.var = names(.[[1]])) %>% 
+  group_by(Category) %>% 
+  summarise(cnt = mean(cnt)) %>% 
+  arrange(cnt) %>% 
+  mutate(
+    Category = tolower(Category),
+    cnt = round(cnt, 2)
+    ) %>% 
+  arrange(cnt)
+
+@
+
+The above results demonstrated that each state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by identifiability thresholds and parameter selection criteria.
+These results further underscore the need for explicit selection heuristics for parameters to calibrate for improving model performance.
+Results for each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) applied to each state variable differed in the number of selected parameters and distribution of parameters within each category (\cref{tab:heurist1,tab:heurist2,tab:heurist3}).
+In general, a corresponendence was observed between the number of parameters that were selected given the threhold of $\gamma = 15$ and relative identifiability between the state variables.
+As noted above, nitrate was the least identifiable variable (\cref{fig:identploall}), whereas other variables (e.g., \ac{do}, irradiance) were more identifiable.
+The constraints on relative identifiability between variables were demonstrated with the selection heuristics.
+For example, heuristics for nitrate typically selected only one or two parameters that met the criteria as compared to more identifiable variables that included several parameters that were identifiable.
+Overall, the first selection heuristic demonstrated that the number of parameters chosen by parameter category differed independently of the state variables (\cref{tab:heurist1}).
+The number of selected parameters averaged across state variable in decreasing order was \Sexpr{catave[4, 2]} parameters (\Sexpr{catave[4, 1]}), \Sexpr{catave[3, 2]} (\Sexpr{catave[3, 1]}), \Sexpr{catave[2, 2]} (\Sexpr{catave[2, 1]}), and \Sexpr{catave[1, 2]} (\Sexpr{catave[1, 1]}).
+These rankings were independent of parameter sensitivity and identifiability in each category.
+The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic.
+
+\Cref{fig:heurist_stts} demonstrates parameter selection for all state variables following the second heuristic where parameters were chosen by decreasing sensitivity independent of parameter categories (exact values are shown in \cref{tab:heurist2}).
+The y-axis on the plot shows the relative identifiability values with the addition of parameters from one to many on the x-axis (from left to right).
+The second to last parameter for each variable is the last parameter selected within the potential threshold of $\gamma = 15$.
+Interestingly, the last parameter shown for most of the state variables caused a relatively large increase in $\gamma$ that was disproportionate to the combined identifiability of the preceding parameter set.
+For most variables, the phytoplankton edibility vector for zooplankton, \Sexpr{par_txt('ediblevector(Z1)_1')}, caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
+In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative approach to identifying parameters that are disporportionately redundant within a given parameter set.
+This infomation is useful if additional parameter selection rules are developed ndependently of those proposed herein.
 
 \subsection{Observational and structural uncertainty}
+
+Both the relative $L1$ estimates and number of parameters that affected state variables were sensitive to variation in the initial conditions (observation effects) and structural changes in the model.
+Visual comparison of sensitivity values ($L1$) for the default model setup showed that all state variables were sensitive to \Sexpr{par_txt('vmaxSi_1')} after changing the initial conditions to April or September conditions (\cref{fig:sensalltile}).
+State variables were also sensitive to \Sexpr{par_txt('Ksi_1')} for only the September conditions.
+Changing the model structure from the default (simple) to the complex setup showed state variables were also sensitive to \Sexpr{par_txt('KQn_1')} and \Sexpr{par_txt('Tref(nospA+nospZ)_7')}.
+Changes in the sensitivity of individual parameters were also observed, most notably as a disproportionate increase in $L1$ for ammonium, \ac{chla}, \ac{pom}, and \ac{dom} to \Sexpr{par_txt('mA_1')} and \Sexpr{par_txt('Tref(nospA+nospZ)_1')} using the complex model setup.
+Summaries by parameter categories of the effects of initial conditions and structural changes are shown in \cref{tab:inistrchg,fig:inistrsumm}.
+Changes in average sensitivity using April and September initial conditions showed most variables were less sensitive to parameters in the optics, temperature, and zooplankton categories, whereas increased sensitivity was generally observed for parameters in the organic matter and phytoplankton categories.
+Some exceptions were observed, such as a decrease in nitrogen sensitivity to phytoplankton parameters.
+Effects of structural complexity were most apparent as an increase in sensitivity of state variables to phytoplankton and temperature parameters, as noted for the individual variables in \cref{fig:sensalltile}.
 
@@
     coll = sapply(coll, scinot), 
-    Rank = sapply(rnk_incat, scinot), 
-    Rank = paste0(Rank)
+    Rank = rnk_incat
     ) %>%
@@
 Selections followed the first heuristic where parameters were selected within categories from most to least sensitive until $\\gamma > 15$.
-Rank describes the relative parameter sensitivity in each category for each state variable.'
+Rank describes the relative parameter sensitivity in each category for each state variable.
+Duplicate parameters and ranks in the first two columns apply only to $\\gamma$ values in the same row (i.e., the top-ranked parameter could vary for each variable).'
 colnms <- c('Rank', 'Ammonium', 'Chl-\\textit{a}', 'O$_2$', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
@@
     mean_def = mean(Default, na.rm = TRUE),
-    iniapr_dif = mean_def - mean(`Initial: April`, na.rm = TRUE),
+    iniapr_dif = mean(`Initial: April`, na.rm = TRUE) - mean_def,
     iniapr_sgn = sign(iniapr_dif),
@@
     iniapr_dif = ifelse(iniapr_sgn == -1, iniapr_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', iniapr_dif))),
-    inisep_dif = mean_def - mean(`Initial: September`, na.rm = TRUE),
+    inisep_dif = mean(`Initial: September`, na.rm = TRUE) - mean_def,
     inisep_sgn = sign(inisep_dif),
@@
     inisep_dif = ifelse(inisep_sgn == -1, inisep_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', inisep_dif))),
-    strcom_dif = mean_def - mean(`Structure: complex`, na.rm = TRUE),
+    strcom_dif = mean(`Structure: complex`, na.rm = TRUE) - mean_def,
     strcom_sgn = sign(strcom_dif),
@@
 Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
-The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\\gamma = 1$, see \\cref{fig:inistreval}).', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=
+The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=
 

### 2016-12-02 ident_manu.tex
results draft done

@@
   \vspace{1in} 
-  \\ Version Date:   Thu Dec 1 12:24:21 2016 -0600
+  \\ Version Date:   Thu Dec 1 15:17:07 2016 -0600
 	}
@@
 Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas a all combinations were identifiable for optics ($100$\% less than $\gamma = 15$, $100$\% less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$) combinations were identifiable.
+By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas all combinations were identifiable for optics ($100$\% less than $\gamma = 15$, $100$\% less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$) combinations were identifiable.
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
@@
 
-%' <<eval = F>>=
-%' data(tocal)
-%' 
-%' # n parms and ident for each selection heuristic
-%' h1_id <- tocal$cat %>% 
-%'   split(., .$Category) %>% 
-%'   lapply(function(x){
-%'     x <- x[x$coll < 15, ]
-%'     list(nrow(x), scinot(max(x$coll), digits = 1))
-%'   }) 
-%' h2_id <- filter(tocal$top, coll < 15) %>%
-%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
-%'   .[c(2, 3)]
-%' h3_id <- filter(tocal$cattop, coll < 15) %>%
-%'   list(nrow(.), scinot(max(.$coll), digits = 1)) %>% 
-%'   .[c(2, 3)]
-%' 
-%' # which parameter broke selection for h2, h3
-%' h2_brk <- tocal$top
-%' sel <- which(h2_brk$coll < 15)
-%' h2_brk <- h2_brk[c(sel, rev(sel)[1] + 1), ] %>% 
-%'   arrange(-coll) %>% 
-%'   .[1:2, ] %>% 
-%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
-%'   .[[2]]
-%' # which parameter broke selection for h2, h3
-%' h3_brk <- tocal$cattop
-%' sel <- which(h3_brk$coll < 15)
-%' h3_brk <- h3_brk[c(sel, rev(sel)[1] + 1), ] %>% 
-%'   arrange(-coll) %>% 
-%'   .[1:2, ] %>% 
-%'   list(c(as.character(.$Parameter[1]), .$coll)) %>% 
-%'   .[[2]]
-%' @
-%' 
-%' Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).
-For the first selection heuristic, all sensitive parameters from the optics ($n = $ scinot(h1_id$Optics[[1]], digits = 0), $\gamma =$  h1_id$Optics[[2]]) and organic matter ($n = $ scinot(h1_id$`Organic Matter`[[1]], digits = 0), $\gamma =$  h1_id$`Organic Matter`[[2]]) categories were selected, whereas toeng(h1_id$Phytoplankton[[1]])[[1]] were selected for phytoplankton ($\gamma = $ h1_id$Phytoplankton[[2]]), toeng(h1_id$Temperature[[1]])[[1]] for temperature ($\gamma = $ h1_id$Temperature[[2]]), and toeng(h1_id$Zooplankton[[1]])[[1]] for zooplankton ($\gamma = $ h1_id$Zooplankton[[2]]).
-For the second selection heuristic, toeng(h2_id[[1]])[[1]] parameters were selected ($\gamma = $ h2_id[[2]], with a majority from the phytoplankton category, \cref{tab:identall1}).
-For the third heuristic, toeng(h3_id[[1]])[[1]] parameters were selected ($\gamma = $ h3_id[[2]]) with equal representation between categories.
-For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.
-Selection independent of category showed that including par_txt(h2_brk[1]) caused in increase in $\gamma$ from scinot(h2_brk[3], digits = 1) to scinot(h2_brk[2], digits = 1) and equal selection within cateogies showed that including par_txt(h3_brk[1]) caused in increase in $\gamma$ from scinot(h3_brk[3], digits = 1) to scinot(h3_brk[2], digits = 1).
-Finally, parameter selection for other state variables (\ac{chla}, irradiance, nitrate, ammonium, \ac{pom}, \ac{dom}, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).
-Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.
-Interestingly, no parameters from the temperature category were selected.
+The above results demonstrated that each state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by identifiability thresholds and parameter selection criteria.
+These results further underscore the need for explicit selection heuristics for parameters to calibrate for improving model performance.
+Results for each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) applied to each state variable differed in the number of selected parameters and distribution of parameters within each category (\cref{tab:heurist1,tab:heurist2,tab:heurist3}).
+In general, a corresponendence was observed between the number of parameters that were selected given the threhold of $\gamma = 15$ and relative identifiability between the state variables.
+As noted above, nitrate was the least identifiable variable (\cref{fig:identploall}), whereas other variables (e.g., \ac{do}, irradiance) were more identifiable.
+The constraints on relative identifiability between variables were demonstrated with the selection heuristics.
+For example, heuristics for nitrate typically selected only one or two parameters that met the criteria as compared to more identifiable variables that included several parameters that were identifiable.
+Overall, the first selection heuristic demonstrated that the number of parameters chosen by parameter category differed independently of the state variables (\cref{tab:heurist1}).
+The number of selected parameters averaged across state variable in decreasing order was 4.25 parameters (phytoplankton), 3.5 (organic matter), 2.75 (optics), and 2.38 (zooplankton).
+These rankings were independent of parameter sensitivity and identifiability in each category.
+The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic.
+
+\Cref{fig:heurist_stts} demonstrates parameter selection for all state variables following the second heuristic where parameters were chosen by decreasing sensitivity independent of parameter categories (exact values are shown in \cref{tab:heurist2}).
+The y-axis on the plot shows the relative identifiability values with the addition of parameters from one to many on the x-axis (from left to right).
+The second to last parameter for each variable is the last parameter selected within the potential threshold of $\gamma = 15$.
+Interestingly, the last parameter shown for most of the state variables caused a relatively large increase in $\gamma$ that was disproportionate to the combined identifiability of the preceding parameter set.
+For most variables, the phytoplankton edibility vector for zooplankton, \textit{ediblevector(Z1)}, caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
+In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative approach to identifying parameters that are disporportionately redundant within a given parameter set.
+This infomation is useful if additional parameter selection rules are developed ndependently of those proposed herein.
 
 \subsection{Observational and structural uncertainty}
+
+Both the relative $L1$ estimates and number of parameters that affected state variables were sensitive to variation in the initial conditions (observation effects) and structural changes in the model.
+Visual comparison of sensitivity values ($L1$) for the default model setup showed that all state variables were sensitive to \textit{vmaxSi} after changing the initial conditions to April or September conditions (\cref{fig:sensalltile}).
+State variables were also sensitive to \textit{Ksi} for only the September conditions.
+Changing the model structure from the default (simple) to the complex setup showed state variables were also sensitive to \textit{KQn} and \textit{Tref(nospA+nospZ)$_{z1}$}.
+Changes in the sensitivity of individual parameters were also observed, most notably as a disproportionate increase in $L1$ for ammonium, \ac{chla}, \ac{pom}, and \ac{dom} to \textit{mA} and \textit{Tref(nospA+nospZ)$_{p1}$} using the complex model setup.
+Summaries by parameter categories of the effects of initial conditions and structural changes are shown in \cref{tab:inistrchg,fig:inistrsumm}.
+Changes in average sensitivity using April and September initial conditions showed most variables were less sensitive to parameters in the optics, temperature, and zooplankton categories, whereas increased sensitivity was generally observed for parameters in the organic matter and phytoplankton categories.
+Some exceptions were observed, such as a decrease in nitrogen sensitivity to phytoplankton parameters.
+Effects of structural complexity were most apparent as an increase in sensitivity of state variables to phytoplankton and temperature parameters, as noted for the individual variables in \cref{fig:sensalltile}.
 
@@
 Selections followed the first heuristic where parameters were selected within categories from most to least sensitive until $\gamma > 15$.
-Rank describes the relative parameter sensitivity in each category for each state variable.\label{tab:heurist1}}
+Rank describes the relative parameter sensitivity in each category for each state variable.
+Duplicate parameters and ranks in the first two columns apply only to $\gamma$ values in the same row (i.e., the top-ranked parameter could vary for each variable).\label{tab:heurist1}}
 \begin{center}
-\begin{tabular}{llllllllll}
+\begin{tabular}{lrllllllll}
 \hline\hline
@@
 {\bfseries Optics}&&&&&\tabularnewline
-~~Ammonium&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Chlorophyll&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Dissolved Oxygen&$2.81\times 10^{-4}$&&$\bm{2.11\times 10^{-4}}$&$\bm{1.46\times 10^{-4}}$&$\bm{1.93\times 10^{-4}}$\tabularnewline
-~~Irradiance&$0.01$&&$-0$&$-0$&$-0$\tabularnewline
-~~Nitrate&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~OM1&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~OM2&$0.02$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Phosphate&$0$&&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline
+~~Ammonium&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~Chlorophyll&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~Dissolved Oxygen&$2.81\times 10^{-4}$&&$-2.11\times 10^{-4}$&$-1.46\times 10^{-4}$&$-1.93\times 10^{-4}$\tabularnewline
+~~Irradiance&$0.01$&&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline
+~~Nitrate&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~OM1&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~OM2&$0.02$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~Phosphate&$0$&&$-0$&$-0$&$-0$\tabularnewline
 \hline
 {\bfseries Organic Matter}&&&&&\tabularnewline
-~~Ammonium&$0.31$&&$-0.08$&$-0.04$&$\bm{2.22\times 10^{-4}}$\tabularnewline
-~~Chlorophyll&$0.02$&&$-0.12$&$-0.14$&$\bm{0.01}$\tabularnewline
-~~Dissolved Oxygen&$0$&&$\bm{6.75\times 10^{-4}}$&$-2.32\times 10^{-4}$&$\bm{0}$\tabularnewline
-~~Irradiance&$0.01$&&$-0.01$&$-0.01$&$\bm{2.99\times 10^{-4}}$\tabularnewline
-~~Nitrate&$0.12$&&$-0.06$&$-0.09$&$\bm{0.1}$\tabularnewline
-~~OM1&$0.13$&&$-0.15$&$-0.12$&$-0.04$\tabularnewline
-~~OM2&$0.14$&&$-0.07$&$-0.17$&$-0.05$\tabularnewline
-~~Phosphate&$0.03$&&$-0.04$&$-0.06$&$\bm{0.02}$\tabularnewline
+~~Ammonium&$0.31$&&$\bm{0.08}$&$\bm{0.04}$&$-2.22\times 10^{-4}$\tabularnewline
+~~Chlorophyll&$0.02$&&$\bm{0.12}$&$\bm{0.14}$&$-0.01$\tabularnewline
+~~Dissolved Oxygen&$0$&&$-6.75\times 10^{-4}$&$\bm{2.32\times 10^{-4}}$&$-0$\tabularnewline
+~~Irradiance&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$-2.99\times 10^{-4}$\tabularnewline
+~~Nitrate&$0.12$&&$\bm{0.06}$&$\bm{0.09}$&$-0.1$\tabularnewline
+~~OM1&$0.13$&&$\bm{0.15}$&$\bm{0.12}$&$\bm{0.04}$\tabularnewline
+~~OM2&$0.14$&&$\bm{0.07}$&$\bm{0.17}$&$\bm{0.05}$\tabularnewline
+~~Phosphate&$0.03$&&$\bm{0.04}$&$\bm{0.06}$&$-0.02$\tabularnewline
 \hline
 {\bfseries Phytoplankton}&&&&&\tabularnewline
-~~Ammonium&$0.8$&&$\bm{0.02}$&$-0.3$&$-65.98$\tabularnewline
-~~Chlorophyll&$1.14$&&$-1.23$&$-4.38$&$-104.24$\tabularnewline
-~~Dissolved Oxygen&$0.01$&&$\bm{4.58\times 10^{-4}}$&$-0$&$-3.44\times 10^{-4}$\tabularnewline
-~~Irradiance&$0.02$&&$\bm{0}$&$-0$&$-0.01$\tabularnewline
-~~Nitrate&$0.74$&&$\bm{0.43}$&$\bm{0.45}$&$\bm{0.64}$\tabularnewline
-~~OM1&$0.76$&&$-0.17$&$-0.46$&$-55.11$\tabularnewline
-~~OM2&$1.28$&&$-0.34$&$-1.15$&$-128.93$\tabularnewline
-~~Phosphate&$0.17$&&$-0.03$&$-0.05$&$\bm{0.14}$\tabularnewline
+~~Ammonium&$0.8$&&$-0.02$&$\bm{0.3}$&$\bm{65.98}$\tabularnewline
+~~Chlorophyll&$1.14$&&$\bm{1.23}$&$\bm{4.38}$&$\bm{104.24}$\tabularnewline
+~~Dissolved Oxygen&$0.01$&&$-4.58\times 10^{-4}$&$\bm{0}$&$\bm{3.44\times 10^{-4}}$\tabularnewline
+~~Irradiance&$0.02$&&$-0$&$\bm{0}$&$\bm{0.01}$\tabularnewline
+~~Nitrate&$0.74$&&$-0.43$&$-0.45$&$-0.64$\tabularnewline
+~~OM1&$0.76$&&$\bm{0.17}$&$\bm{0.46}$&$\bm{55.11}$\tabularnewline
+~~OM2&$1.28$&&$\bm{0.34}$&$\bm{1.15}$&$\bm{128.93}$\tabularnewline
+~~Phosphate&$0.17$&&$\bm{0.03}$&$\bm{0.05}$&$-0.14$\tabularnewline
 \hline
 {\bfseries Temperature}&&&&&\tabularnewline
-~~Ammonium&$0.79$&&$\bm{0.69}$&$\bm{0.69}$&$-272.31$\tabularnewline
-~~Chlorophyll&$0.6$&&$\bm{0.47}$&$\bm{0.45}$&$-114.51$\tabularnewline
-~~Dissolved Oxygen&$0.02$&&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
-~~Irradiance&$0.03$&&$\bm{0.02}$&$\bm{0.02}$&$-0.01$\tabularnewline
-~~Nitrate&$0.3$&&$\bm{0.15}$&$\bm{0.16}$&$\bm{0.19}$\tabularnewline
-~~OM1&$0.86$&&$\bm{0.68}$&$\bm{0.69}$&$-215.17$\tabularnewline
-~~OM2&$1.48$&&$\bm{1.21}$&$\bm{1.2}$&$-900.26$\tabularnewline
-~~Phosphate&$0.16$&&$\bm{0.11}$&$\bm{0.09}$&$\bm{0.11}$\tabularnewline
+~~Ammonium&$0.79$&&$-0.69$&$-0.69$&$\bm{272.31}$\tabularnewline
+~~Chlorophyll&$0.6$&&$-0.47$&$-0.45$&$\bm{114.51}$\tabularnewline
+~~Dissolved Oxygen&$0.02$&&$-0.02$&$-0.02$&$-0.01$\tabularnewline
+~~Irradiance&$0.03$&&$-0.02$&$-0.02$&$\bm{0.01}$\tabularnewline
+~~Nitrate&$0.3$&&$-0.15$&$-0.16$&$-0.19$\tabularnewline
+~~OM1&$0.86$&&$-0.68$&$-0.69$&$\bm{215.17}$\tabularnewline
+~~OM2&$1.48$&&$-1.21$&$-1.2$&$\bm{900.26}$\tabularnewline
+~~Phosphate&$0.16$&&$-0.11$&$-0.09$&$-0.11$\tabularnewline
 \hline
 {\bfseries Zooplankton}&&&&&\tabularnewline
-~~Ammonium&$0.47$&&$\bm{0.45}$&$\bm{0.44}$&$\bm{0.16}$\tabularnewline
-~~Chlorophyll&$0.39$&&$\bm{0.26}$&$\bm{0.23}$&$\bm{0.2}$\tabularnewline
-~~Dissolved Oxygen&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$\bm{0.01}$\tabularnewline
-~~Irradiance&$0.03$&&$\bm{0.02}$&$\bm{0.02}$&$\bm{0.01}$\tabularnewline
-~~Nitrate&$1.06$&&$\bm{1.02}$&$\bm{1.02}$&$\bm{0.98}$\tabularnewline
-~~OM1&$0.37$&&$\bm{0.27}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
-~~OM2&$0.39$&&$\bm{0.3}$&$\bm{0.28}$&$\bm{0.18}$\tabularnewline
-~~Phosphate&$0.31$&&$\bm{0.19}$&$\bm{0.17}$&$\bm{0.27}$\tabularnewline
+~~Ammonium&$0.47$&&$-0.45$&$-0.44$&$-0.16$\tabularnewline
+~~Chlorophyll&$0.39$&&$-0.26$&$-0.23$&$-0.2$\tabularnewline
+~~Dissolved Oxygen&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~Irradiance&$0.03$&&$-0.02$&$-0.02$&$-0.01$\tabularnewline
+~~Nitrate&$1.06$&&$-1.02$&$-1.02$&$-0.98$\tabularnewline
+~~OM1&$0.37$&&$-0.27$&$-0.28$&$-0.18$\tabularnewline
+~~OM2&$0.39$&&$-0.3$&$-0.28$&$-0.18$\tabularnewline
+~~Phosphate&$0.31$&&$-0.19$&$-0.17$&$-0.27$\tabularnewline
 \hline
@@
 
-\caption{Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables.
+\caption[Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables]{Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables.
 Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
 Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
-The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\gamma = 1$, see \cref{fig:inistreval}).}\label{fig:identploall}
+The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identploall}
 \end{figure}

### 2016-12-05 ident_manu.Rnw
first two pages of discussion

@@
 We argue that quantitative and ecological certainty in model calibration are often at odds and practitioners must choose explicit model components to optimize given tradeoffs between the two.
-We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of paramater perturbations on model output.
+We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of parameter perturbations on model output.
 As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in hypoxic condition can be potentially misguided in the absence of quantitative descriptions of identifiability.
@@
 An understanding of the biological, physical, and chemical processes that contribute to the growth of hypoxic areas is a critical concern for mitigating and preventing these negative impacts.
-Numerical ecosystem models have been important tools for describing current knowledge of ecosystem processes that contribute to hypoxia formation and for predicting the effects of proposed management activities or future scenarios \citep{Scavia04,Hagy07,Pauer16}.
-Unlike statistical models that have more generic structures, simulation and process-based models include explicit descriptions of relevant processes that are constrained by empirical or observational data relevant to the system of interest \citep[e.g.][]{Omlin01b,Eldridge10}.
+Numerical ecosystem models are important tools that synthesize knowledge of ecosystem processes that contribute to hypoxia formation and for predicting the effects of proposed management activities or future scenarios \citep{Scavia04,Hagy07,Pauer16}.
+Unlike statistical models with more generic structures, simulation and process-based models include explicit descriptions of relevant processes that are constrained by empirical or observational data relevant to the system of interest \citep[e.g.][]{Omlin01b,Eldridge10}.
 These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions \citep{Warner05,Zhao10,Ganju16}.
@@
 Standard approaches for uncertainty analysis can be used to begin addressing model complexity issues.
-In the most general sense, uncertainty is evaluated relative to the effects of input conditions or the observed data used to calibrate a model, changes in parameter values, or variation in the structural components \citep{Beck87}.
+In the most general sense, uncertainty is evaluated relative to the effects of input conditions or the observed data used to calibrate a model, changes in parameter values, or variation in the structural components (i.e., observational, parameter, or structural uncertainty) \citep{Beck87}.
 Evaluating parameter uncertainty is by far the most common and simplest means of evaluating model behavior.
@@
 Redundancies in parameter effects lead to unidentifiable models where optimal solutions may be empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
+An unidentifiable parameter or parameter set has effects on model output that can be undone or compensated for by alteration of other parameters.
 The concept of identifiable parameter subsets is not foreign to hypoxia or eutrophication models  \citep{Omlin01,Estrada10,Mateus15}, although there is a clear need for greater integration of these concepts in model development \citep{Fasham06}.
-Moreover, the inclusion of sensitivity and identifiability analyses in model tuning will require the adoption of selection rules that are context-dependent given the subsets that are possible with large parameter sets \citep[e.g.,][]{Wagener01, Wagener01b}.
+Moreover, the inclusion of sensitivity and identifiability analyses in model tuning will require the adoption of conservative selection rules for parameters to calibrate given the number of unique combinations of parameter subsets for most models \citep[e.g.,][]{Wagener01, Wagener01b}.
 
@@
 \item quantify the identifiability of subsets of the total parameter space based on sensitivity,
-\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories, including extension to other state variables provided by the model.
+\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories.
 \end{inparaenum}
-A final analysis evaluates identifiability relative to structural uncertainty to provide an example of extending these methods to more complex uncertainty assessments.
-The optimum parameter space is defined as the chosen subset that represents the maximum number of identifiable parameters.
-Here, `optimum' is both a qualitative description based on a research question or management goal and a quantitative objective based on numerical optimization criteria for fitting model output to a calibration dataset.
+These principles were also applied to other state variables predicted by the model (ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus).
+A final analysis evaluated identifiability relative to structural uncertainty to provide an example of extending these methods to more complex uncertainty assessments.
+Throughout, the optimum parameter set is defined as the chosen subset that represents the maximum number of identifiable parameters.
+`Optimum' is both a qualitative description based on a research question or management goal and a quantitative objective based on numerical optimization criteria for fitting model output to a calibration dataset.
 These results can be used to refine existing models or guide application of models to novel contexts, such as downscaling or application to new environments.
@@
 This study evaluated the core unit of a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.
-The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describes hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
+The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
 The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
@@
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
-Accordingly, the sensitivity and identifiability analyses described below focused exclusively on FishTank and are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
+Accordingly, the sensitivity and identifiability analyses described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
 The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
@@
 The analyses relied exclusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10,RDCT16}.
-Parameters were individually perturbed by 50\% of the original values and the model was executed to obtain an estimate \ac{do} sensitivity.
+Parameters were individually perturbed by 50\% of the original values and the model was executed to obtain an estimate of \ac{do} sensitivity.
 For each perturbation, a sensitivity value $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
@@
 
+The $L1$ value for each parameter was used as the primary measure of sensitivity for the state variables.
 All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ (suggesting sensitivity) were retained for identifiability analysis.
@@
 The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that described deviations of predicted \ac{do} from the default parameter values.
-The matrix $\hat{S}$ was first normalized by dividing by the square root of the summed residuals \citep{Omlin01,Soetaert10}.
-
-The collinearity index $\gamma$ provides a measure of the linear dependence between sensitivity functions described above for subsets of parameters.
-Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms given similar effects of the selected parameters on \ac{do}.
-Greater sensitivity of a state variable to a subset of parameters does not always imply better identifiability if the individual effects are similar.
+Thus, $\gamma$ can be estimated for any subset of parameter combinations using the change in model output for perturbations of individual parameters.
+Sensitivity matrices were first normalized by dividing by the square root of the summed residuals \citep{Omlin01,Soetaert10}.
+
+The collinearity index $\gamma$ provides a measure of the linear dependence between sensitivity functions (i.e., $S_i$ for $j$ parameters) described above for subsets of parameters.
+Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms given similar effects of the selected parameters on the estimated state variable.
+Greater sensitivity of a state variable to a subset of parameters does not always imply better identifiability if the effects of individual parameters are similar.
 An intuitive interpretation of $\gamma$ is provided by \citet{Brun01} such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
@@
 Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
-An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practicioners may only be interested in optics parameters).
+An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practitioners may only be interested in optics parameters).
 For example, \cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., based on $n$ choose $k$ combinations equal to $n!/\left(k!\left(n-k\right)!\right)$).
@@
 Conversely, the complex scenario used switches that modelled relationships between phytoplankton growth with temperature using the Arrhenius model \citep{Geider97}, nutrient uptake as proposed by \citet{Lehman75} and modified in \citet{Geider98}, internal cell quotas following \citet{Flynn03}, \ac{chla} to carbon ratios following \citet{Cloern95}, light-dependence of photosynthesis that is nutrient dependent \citep{Flynn03}, and a specific growth rate that is nutrient dependent.
-Complete details are provided as supplementary material to \citetalias{LehrterIR}.
+Complete details of model switches are provided as supplementary material to \citetalias{LehrterIR}.
 
@@
 Local sensitivity analyses for the additional state variables (ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus) had similar results as \ac{do} with some exceptions (\cref{fig:sensalltile,tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens}).
-All additional variables were sensitive to the same parameters (\Sexpr{locO2$tot} of \Sexpr{length(p1z1pars)} evaluated), although average sensitivity differed between variables.
+All variables were sensitive to the same parameters as \ac{do} (\Sexpr{locO2$tot} of \Sexpr{length(p1z1pars)} evaluated), although average sensitivity differed between variables.
 Average $L1$ ranged from \Sexpr{scinot(aveall[2])} for \Sexpr{names(aveall)[2]} (\cref{tab:irrsens}) to \Sexpr{scinot(aveall[length(aveall)])} for \Sexpr{names(aveall)[length(aveall)]} (\cref{tab:om2sens}).
@@
 For the parameter categories, ammonium was most sensitive to \Sexpr{names(maxcat$NH4)} parameters (average $L1$ = \Sexpr{maxcat$NH4} across all parameters in the category), \ac{chla} to \Sexpr{names(maxcat$Chla_mg_tot)} ($L1$ = \Sexpr{maxcat$Chla_mg_tot}), irradiance to \Sexpr{names(maxcat$irradiance)} ($L1$ = \Sexpr{maxcat$irradiance}), nitrate to \Sexpr{names(maxcat$NO3)} ($L1$ = \Sexpr{maxcat$NO3}), \ac{pom} to \Sexpr{names(maxcat$OM1)} ($L1$ = \Sexpr{maxcat$OM1}), \ac{dom} to \Sexpr{names(maxcat$OM2)} ($L1$ = \Sexpr{maxcat$OM2}), and phosphate to \Sexpr{names(maxcat$PO4)} ($L1$ = \Sexpr{maxcat$PO4}).
-Finally, average sensititivy between parameter categories independent of the state variables ranged from \Sexpr{avecat[1]} for \Sexpr{names(avecat)[1]} (average $L1$ across all variables) to \Sexpr{avecat[length(avecat)]} for \Sexpr{names(avecat)[length(avecat)]}.
+Finally, average sensitivity between parameter categories independent of the state variables ranged from \Sexpr{avecat[1]} for \Sexpr{names(avecat)[1]} (average $L1$ across all variables) to \Sexpr{avecat[length(avecat)]} for \Sexpr{names(avecat)[length(avecat)]}.
 
@@
 Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\% less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$) combinations were identifiable.
+By category, identifiability was lowest for all combinations of parameter subsets in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% of subsets less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\% less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$).
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
@@
 The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15$ and \Sexpr{toppersO2$top1[2]}\% less than $\gamma = 10$ for the top parameters in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the fop four.
-Results for the remaining state variables had similar patterns in identifability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
+Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
 Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.
@@
 The selected $\gamma$ thresholds are somewhat arbitrary, although the results show differences that have implications for parameter selection for model calibration.
-In general, identifiability decreases with the addition of parameters, although the rate of decrease depends on the selected threshold for $\gamma$.
-More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset.
+In general, identifiability decreased with the addition of parameters, although the rate of decrease depended on the selected threshold for $\gamma$.
+More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset, that is, identifiability decreased more quickly with the addition of parameters at lower $\gamma$ thresholds as compared to higher $\gamma$.
 Notable differences in identifiability were also observed by selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
@@
 
-An evaluation of the effects of individual parameters on $\gamma$ further suggested that some parameters have disproportionate effects on identifiability.
+An evaluation of the effects of individual parameters on $\gamma$ suggested that some parameters had disproportionate effects on identifiability.
 Based on $\gamma = 15$, \cref{fig:identplo} suggests that most parameter sets for organic matter were identifiable, regardless of how many parameters were selected (i.e., two through eight).
-Because identifiability of the organic matter parameters was generally acceptable, identification of one or more redundant parameters that are inflating $\gamma$ values could provide useful information.
+However, some subsets were not identifiable such that identification of one or more redundant parameters that are inflating $\gamma$ values could provide useful information.
 \Cref{fig:exclex} shows an alternative view of identifiability of \ac{do} with exclusion and inclusion of individual parameters in different sets for the organic matter category.
-Collinearity increases with more parameters included in a subset, although the increase varies depending on which parameter was included or excluded from the set.
+As before, collinearity increases with more parameters in a subset, although the increase varies depending on which parameter was included or excluded from the set.
 For example, inclusion of \Sexpr{om_coll[5]} in a parameter set almost always inflated $\gamma$.
@@
 
-The above results demonstrated that each state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by identifiability thresholds and parameter selection criteria.
+The above results demonstrated that the state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by identifiability thresholds and parameter selection criteria.
 These results further underscore the need for explicit selection heuristics for parameters to calibrate for improving model performance.
@@
 Overall, the first selection heuristic demonstrated that the number of parameters chosen by parameter category differed independently of the state variables (\cref{tab:heurist1}).
-The number of selected parameters averaged across state variable in decreasing order was \Sexpr{catave[4, 2]} parameters (\Sexpr{catave[4, 1]}), \Sexpr{catave[3, 2]} (\Sexpr{catave[3, 1]}), \Sexpr{catave[2, 2]} (\Sexpr{catave[2, 1]}), and \Sexpr{catave[1, 2]} (\Sexpr{catave[1, 1]}).
+The number of selected parameters averaged across state variables in decreasing order was \Sexpr{catave[4, 2]} parameters from the \Sexpr{catave[4, 1]} category, \Sexpr{catave[3, 2]} from \Sexpr{catave[3, 1]}, \Sexpr{catave[2, 2]} from \Sexpr{catave[2, 1]}, and \Sexpr{catave[1, 2]} from \Sexpr{catave[1, 1]}.
 These rankings were independent of parameter sensitivity and identifiability in each category.
@@
 Interestingly, the last parameter shown for most of the state variables caused a relatively large increase in $\gamma$ that was disproportionate to the combined identifiability of the preceding parameter set.
-For most variables, the phytoplankton edibility vector for zooplankton, \Sexpr{par_txt('ediblevector(Z1)_1')}, caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
-In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative approach to identifying parameters that are disporportionately redundant within a given parameter set.
-This infomation is useful if additional parameter selection rules are developed ndependently of those proposed herein.
+For most variables, the phytoplankton edibility vector for zooplankton (\Sexpr{par_txt('ediblevector(Z1)_1')}) caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
+In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disporportionately redundant within a given parameter set.
+This infomation is useful if additional parameter selection rules are developed independently of those proposed herein.
 
@@
 \section{Discussion}
-%' 
-%' % back of envelop calcs for number of relevant parms, all state variables
-%' <<echo = F>>=
-%' 
-%' @
+
+Common goals in the application of biogeochemical models of ecosystem processes are to \begin{inparaenum}[1\upshape)]
+\item accurately describe the system with historical data, and 
+\item provide a means of forecasting ecosystem condition with hypothesized management or environmental scenarios. 
+\end{inparaenum}
+Although these objectives are the focus of most model applications, the structural components of process-based models should secondarily provide inference into which ecosystem processes and functions are driving observed or hypothesized changes.
+This latter objective represents a more general scientific outcome of biogeochemical models that extends beyond the applied benefits of describing and predicting change in a particular system.
+Modelers often hope to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting these principles.
+Extension of these principles to test the effects of structural changes and observation uncertainty on model predictions provideds further evidence to validate model components.
+This study provided a simple approach to use the effects of parameter perturbations on model state variables to characterize identifiable parameter subsets that vary by parameter selection criteria.
+By doing so, we demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiabilty thresholds described in the literature.
+The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
+We further demonstrated that changes in the model structure and variation in the initial conditions had an effect on sensitivity which has direct implications for identifiability.
+In general, these results provide justification for the use of explicit parameter selection heuristics that practitioners should adopt for model calibration.
+
+Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analsyes.
+State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\Sexpr{par_txt('umax_1')} for phytoplankton, \Sexpr{par_txt('Zumax_1')} for zooplankton), mortality coefficient for phytoplankton (\Sexpr{par_txt('mA_1')}), and the zooplankton half saturation coefficent for grazing (\Sexpr{par_txt('ZKa_1')}).
+An increase in growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} concentration in the water column.
+Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pool of organic matter.
+Most variables were also sensitive to variation in the half-saturation grazing coefficient which is linked to the concentration of nutrients that support half the maximum grazing rate.
+Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs}.
+The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance to biological relationships.
+State variables were sensitive to changes in light and temperature parameters, although to a lesser extent than phytoplankton and zooplankton parameters.
+As such, the differing sensitivities of state variables to parameters in each of the categories was not unexpected given general ecological relationships that are well understood and described by the model.
+
+The overwhelming conclusion from the identifiablity analyses is that only limited subsets of parameters are identifiable within the constraints of local sensitivity analyses.
+Although we have not attempted actual model calibration (see recommendations below), these results support previous studies that have suggested similarly small subsets of parameters can be identified using traditional calibration schemes \citep[e.g.,][]{Wheater86,Ye97,Omlin01}.
+In addition to \ac{cgem}, these conclusions have relevance for many biogeochemical models that include numerous parameters and structural equations to characterize processes in the model domain.
+A general conclusion is that perhaps a trend towards less complex models could be beneficial given that only a small subset of parameters is identifiable and that ecosystem processes may in fact be sufficiently characterized with few parameters \citep{Ye97}.
+Conversely, others have argued that model complexity is not in itself a disadvantage when parsimony is not the sole arbitrator of model structure \citep{Reichert97}.
+Over-parameterization can be useful if processes have importance that were not evaluated during model identification.
+Our results demonstrated that approximately 75\% of the evaluated parameters had an effect on the eight state variables, whereas \ac{cgem} includes a total of 36 variables and multiple plankton groups, not all of which have immediate concern for understanding hypoxia.
+The redundancies identified with the sensitivity analyses are only problematic if the primary interest is, for example, \ac{do} dynamics.
+Moreover, the proposed parameter selection heuristics provide flexibility for selecting different parameters based on parameter categories with the assumption that the chosen parameters depends on the research or management question.
+
+% Commonalities in idenfitiability that emerged were 1) potentially driven by a single parameter, 2) nto related to sensitivity, 3) not always related to sheer number of aprmaters
+
+%The \ac{cgem} model also has the ability to model multiple phytoplankton and zooplankton groups, whereas the FishTank model evaluated herein only evaluated one group each for simplicity.
+The use of simple sensitivity analyses is insufficient to
+
+% id of single-most redundant parameters - inclusion/exclusion or fig. 7
+
 %' We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
@@
 Rank describes the relative parameter sensitivity in each category for each state variable.
-Duplicate parameters and ranks in the first two columns apply only to $\\gamma$ values in the same row (i.e., the top-ranked parameter could vary for each variable).'
+Duplicate parameters and ranks in the first two columns apply only to $\\gamma$ values in the same row (i.e., parameter ranks vary for each variable).'
 colnms <- c('Rank', 'Ammonium', 'Chl-\\textit{a}', 'O$_2$', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')

### 2016-12-05 ident_manu.tex
first two pages of discussion

@@
   \vspace{1in} 
-  \\ Version Date:   Thu Dec 1 15:17:07 2016 -0600
+  \\ Version Date:   Fri Dec 2 14:10:33 2016 -0600
 	}
@@
 Local sensitivity analyses for the additional state variables (ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus) had similar results as \ac{do} with some exceptions (\cref{fig:sensalltile,tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens}).
-All additional variables were sensitive to the same parameters (38 of 51 evaluated), although average sensitivity differed between variables.
+All variables were sensitive to the same parameters as \ac{do} (38 of 51 evaluated), although average sensitivity differed between variables.
 Average $L1$ ranged from $0.02$ for irradiance (\cref{tab:irrsens}) to $0.71$ for \ac{dom} (\cref{tab:om2sens}).
@@
 For the parameter categories, ammonium was most sensitive to phytoplankton parameters (average $L1$ = $0.8$ across all parameters in the category), \ac{chla} to phytoplankton ($L1$ = $1.14$), irradiance to zooplankton ($L1$ = $0.03$), nitrate to zooplankton ($L1$ = $1.06$), \ac{pom} to temperature ($L1$ = $0.86$), \ac{dom} to temperature ($L1$ = $1.48$), and phosphate to zooplankton ($L1$ = $0.31$).
-Finally, average sensititivy between parameter categories independent of the state variables ranged from $0.01$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
+Finally, average sensitivity between parameter categories independent of the state variables ranged from $0.01$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
 
@@
 Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas all combinations were identifiable for optics ($100$\% less than $\gamma = 15$, $100$\% less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$) combinations were identifiable.
+By category, identifiability was lowest for all combinations of parameter subsets in the phytoplankton ($60$\% of subsets less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas all combinations were identifiable for optics ($100$\% less than $\gamma = 15$, $100$\% less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$).
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
@@
 The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15$ and $100$\% less than $\gamma = 10$ for the top parameters in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the fop four.
-Results for the remaining state variables had similar patterns in identifability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
+Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
 Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.
@@
 The selected $\gamma$ thresholds are somewhat arbitrary, although the results show differences that have implications for parameter selection for model calibration.
-In general, identifiability decreases with the addition of parameters, although the rate of decrease depends on the selected threshold for $\gamma$.
-More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset.
+In general, identifiability decreased with the addition of parameters, although the rate of decrease depended on the selected threshold for $\gamma$.
+More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset, that is, identifiability decreased more quickly with the addition of parameters at lower $\gamma$ thresholds as compared to higher $\gamma$.
 Notable differences in identifiability were also observed by selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
 
-An evaluation of the effects of individual parameters on $\gamma$ further suggested that some parameters have disproportionate effects on identifiability.
+An evaluation of the effects of individual parameters on $\gamma$ suggested that some parameters had disproportionate effects on identifiability.
 Based on $\gamma = 15$, \cref{fig:identplo} suggests that most parameter sets for organic matter were identifiable, regardless of how many parameters were selected (i.e., two through eight).
-Because identifiability of the organic matter parameters was generally acceptable, identification of one or more redundant parameters that are inflating $\gamma$ values could provide useful information.
+However, some subsets were not identifiable such that identification of one or more redundant parameters that are inflating $\gamma$ values could provide useful information.
 \Cref{fig:exclex} shows an alternative view of identifiability of \ac{do} with exclusion and inclusion of individual parameters in different sets for the organic matter category.
-Collinearity increases with more parameters included in a subset, although the increase varies depending on which parameter was included or excluded from the set.
+As before, collinearity increases with more parameters in a subset, although the increase varies depending on which parameter was included or excluded from the set.
 For example, inclusion of \textit{KNO3} in a parameter set almost always inflated $\gamma$.
@@
 Overall, the first selection heuristic demonstrated that the number of parameters chosen by parameter category differed independently of the state variables (\cref{tab:heurist1}).
-The number of selected parameters averaged across state variable in decreasing order was 4.25 parameters (phytoplankton), 3.5 (organic matter), 2.75 (optics), and 2.38 (zooplankton).
+The number of selected parameters averaged across state variables in decreasing order was 4.25 parameters from the phytoplankton category, 3.5 from organic matter, 2.75 from optics, and 2.38 from zooplankton.
 These rankings were independent of parameter sensitivity and identifiability in each category.
@@
 Interestingly, the last parameter shown for most of the state variables caused a relatively large increase in $\gamma$ that was disproportionate to the combined identifiability of the preceding parameter set.
-For most variables, the phytoplankton edibility vector for zooplankton, \textit{ediblevector(Z1)}, caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
-In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative approach to identifying parameters that are disporportionately redundant within a given parameter set.
-This infomation is useful if additional parameter selection rules are developed ndependently of those proposed herein.
+For most variables, the phytoplankton edibility vector for zooplankton (\textit{ediblevector(Z1)}) caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
+In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disporportionately redundant within a given parameter set.
+This infomation is useful if additional parameter selection rules are developed independently of those proposed herein.
 
@@
 \section{Discussion}
-%' 
-%' % back of envelop calcs for number of relevant parms, all state variables
-%' <<echo = F>>=
-%' 
-%' @
+
+Common goals in the application of biogeochemical models of ecosystem processes are to \begin{inparaenum}[1\upshape)]
+\item accurately describe the system with historical data, and 
+\item provide a means of forecasting ecosystem condition with hypothesized management or environmental scenarios. 
+\end{inparaenum}
+Although these objectives are the focus of most model applications, the structural components of process-based models should secondarily provide inference into which ecosystem processes and functions are driving observed or hypothesized changes.
+This latter objective represents a more general scientific outcome of biogeochemical models that extends beyond the applied benefits of describing and predicting change in a particular system.
+Modelers often hope to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting these principles.
+Extension of these principles to test the effects of structural changes and observation uncertainty on model predictions provideds further evidence to validate model components.
+This study provided a simple approach to use the effects of parameter perturbations on model state variables to characterize identifiable parameter subsets that vary by parameter selection criteria.
+By doing so, we demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiabilty thresholds described in the literature.
+The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
+We further demonstrated that changes in the model structure and variation in the initial conditions had an effect on sensitivity which has direct implications for identifiability.
+In general, these results provide justification for the use of explicit parameter selection heuristics that practitioners should adopt for model calibration.
+
+Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analsyes.
+State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\textit{umax} for phytoplankton, \textit{Zumax} for zooplankton), mortality coefficient for phytoplankton (\textit{mA}), and the zooplankton half saturation coefficent for grazing (\textit{ZKa}).
+An increase in growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} concentration in the water column.
+Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pool of organic matter.
+Most variables were also sensitive to variation in the half-saturation grazing coefficient which is linked to the concentration of nutrients that support half the maximum grazing rate.
+Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs}.
+The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance to biological relationships.
+State variables were sensitive to changes in light and temperature parameters, although to a lesser extent than phytoplankton and zooplankton parameters.
+As such, the differing sensitivities of state variables to parameters in each of the categories was not unexpected given general ecological relationships that are well understood and described by the model.
+
+The overwhelming conclusion from the identifiablity analyses is that only limited subsets of parameters are identifiable within the constraints of local sensitivity analyses.
+Although we have not attempted actual model calibration (see recommendations below), these results support previous studies that have suggested similarly small subsets of parameters can be identified using traditional calibration schemes \citep[e.g.,][]{Wheater86,Ye97,Omlin01}.
+In addition to \ac{cgem}, these conclusions have relevance for many biogeochemical models that include numerous parameters and structural equations to characterize processes in the model domain.
+A general conclusion is that perhaps a trend towards less complex models could be beneficial given that only a small subset of parameters is identifiable and that ecosystem processes may in fact be sufficiently characterized with few parameters \citep{Ye97}.
+Conversely, others have argued that model complexity is not in itself a disadvantage when parsimony is not the sole arbitrator of model structure \citep{Reichert97}.
+Over-parameterization can be useful if processes have importance that were not evaluated during model identification.
+Our results demonstrated that approximately 75\% of the evaluated parameters had an effect on the eight state variables, whereas \ac{cgem} includes a total of 36 variables and multiple plankton groups, not all of which have immediate concern for understanding hypoxia.
+The redundancies identified with the sensitivity analyses are only problematic if the primary interest is, for example, \ac{do} dynamics.
+Moreover, the proposed parameter selection heuristics provide flexibility for selecting different parameters based on parameter categories with the assumption that the chosen parameters depends on the research or management question.
+
+% Commonalities in idenfitiability that emerged were 1) potentially driven by a single parameter, 2) nto related to sensitivity, 3) not always related to sheer number of aprmaters
+
+%The \ac{cgem} model also has the ability to model multiple phytoplankton and zooplankton groups, whereas the FishTank model evaluated herein only evaluated one group each for simplicity.
+The use of simple sensitivity analyses is insufficient to
+
+% id of single-most redundant parameters - inclusion/exclusion or fig. 7
+
 %' We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
@@
 Rank describes the relative parameter sensitivity in each category for each state variable.
-Duplicate parameters and ranks in the first two columns apply only to $\gamma$ values in the same row (i.e., the top-ranked parameter could vary for each variable).\label{tab:heurist1}}
+Duplicate parameters and ranks in the first two columns apply only to $\gamma$ values in the same row (i.e., parameter ranks vary for each variable).\label{tab:heurist1}}
 \begin{center}

### 2016-12-06 ident_manu.Rnw
four pages done in discussion

@@
 
+\subsection{Implications of sensitivity and identifiability analyses}
+
 Common goals in the application of biogeochemical models of ecosystem processes are to \begin{inparaenum}[1\upshape)]
-\item accurately describe the system with historical data, and 
-\item provide a means of forecasting ecosystem condition with hypothesized management or environmental scenarios. 
+\item accurately describe the system my matching predictions with observed data \citep{Reckhow90}, and 
+\item provide a means of forecasting ecosystem condition with hypothesized management or environmental scenarios \citep{Clark01}. 
 \end{inparaenum}
@@
 This latter objective represents a more general scientific outcome of biogeochemical models that extends beyond the applied benefits of describing and predicting change in a particular system.
-Modelers often hope to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting these principles.
-Extension of these principles to test the effects of structural changes and observation uncertainty on model predictions provideds further evidence to validate model components.
+Modelers often hope to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting hypotheses \citep{Kirchner06}.
+Extension of these principles to test the effects of structural changes and observation uncertainty on model predictions provides further evidence to validate model components.
 This study provided a simple approach to use the effects of parameter perturbations on model state variables to characterize identifiable parameter subsets that vary by parameter selection criteria.
@@
 
-Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analsyes.
+Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analyses.
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\Sexpr{par_txt('umax_1')} for phytoplankton, \Sexpr{par_txt('Zumax_1')} for zooplankton), mortality coefficient for phytoplankton (\Sexpr{par_txt('mA_1')}), and the zooplankton half saturation coefficent for grazing (\Sexpr{par_txt('ZKa_1')}).
 An increase in growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} concentration in the water column.
-Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pool of organic matter.
-Most variables were also sensitive to variation in the half-saturation grazing coefficient which is linked to the concentration of nutrients that support half the maximum grazing rate.
-Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs}.
+Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter.
+Most variables were also sensitive to variation in the half-saturation grazing coefficient which moderates the concentration of nutrients that support half the maximum grazing rate.
+Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs} \citep{Fahnenstiel95,Roelke00,Eldridge10}.
 The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance to biological relationships.
@@
 Over-parameterization can be useful if processes have importance that were not evaluated during model identification.
+Single objective functions that maximize model precision with identifiable parameters may also provide an incomplete characterization of model worth, which has prompted the development of probability-based models of hypoxia that explicitly include uncertainty in model components \citep[e.g.][]{Obenour15}.
 Our results demonstrated that approximately 75\% of the evaluated parameters had an effect on the eight state variables, whereas \ac{cgem} includes a total of 36 variables and multiple plankton groups, not all of which have immediate concern for understanding hypoxia.
@@
 
-% Commonalities in idenfitiability that emerged were 1) potentially driven by a single parameter, 2) nto related to sensitivity, 3) not always related to sheer number of aprmaters
+Results from the identifiability analyses provided additional insight into the interactions of parameters in large biogeochemical models.
+First, identifiability of parameter subsets was not related to the sensitivity of individual variables.
+As noted above, an identifiable parameter is one that has a unique effect on model predictions that cannot be compensated for or undone by changing values of other parameters.
+The magnitude of the effect has no bearing on identifiability, which further complicates the selection of parameters for calibration.
+Although identifiability is the primary limiting factor in choosing a given set, the relative sensitivities are more important for the decision to include or exclude indvidual parameters.
+Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
+Similarly, identifability was not always related to the number of parameters in a set.
+Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
+For example, \cref{fig:exclex} shows that including \Sexpr{par_txt('KGcdom_1')}, \Sexpr{par_txt('KO2_1')}, or \Sexpr{par_txt('nitmax_1')} in parameters sets more often reduced $\gamma$ relative to sets that excluded the parameters.
+Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parame ters often caused a disporportionate increase in $\gamma$ (e.g., \Sexpr{par_txt('ediblevector(Z1)_1')}).
+These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
+The selection criteria proposed in our above analyses can facilitate parameter selection and also provide diagnostic tools to identify parameters with disproportionate effects on $\gamma$.
+
+\subsection{Recommendations and conclusions}
+
+An evaluation of parameter uncertainty and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
+In general, uncertainty analyses that lead to improved models are ultimately expected to increase our understanding of properties that define ecosystems using relationships described by the model.
+The extension of simple parameter sensitivity analyses to the generalization of ecosystem properties requires additional analysis and potential model refinement, at the core of which is the balance between generality and precision.
+We emphasize that the utility of a specific model depends on the question and objective for application to a specific system.
+For the above analysis, the FishTank model as part of the larger \ac{cgem} application was evaluated in the context of hypoxia effects on ecosystem condition and function.
+At the core of the simple model is a set of biogeochemical equations that characterize the system in relation to planktonic groups, nutrient requirements, and water-column metabolism.
+Our results have shown that relatively small subsets of parameters are identifiable given the complexity of the model, and as a result, we have provided a general approach to select parameter subsets depending on the ecological context (i.e., selection by parameter category, selection for specific state variables).
+Thus, the results described above have relevance for further model refinement with the specific goal of better understanding ecological dynamics that moderate hypoxia on the northern \ac{gom}.
+However, the general principles of sensitivity and parameter identifiability have broad applicability beyond this context and we argue that such methods should be more universally applied as an initial approach to quantify numerical constraints of biogeochemical models.
+
+Specific approaches can be used to improve and build on the results presented herein, in addition to the more general considerations noted above.
+A logical next step is an evaluation of model precision following calibration with relevant parameter subsets.
+For simplicity, our analysis did not calibrate model parameters and an explicit assumption was that parameter subsets with $\gamma$ below 10 or 15 were identifiable.
+To our knowledge, this threshold has not been rigorously evaluated and a logical expectation is that this threshold is likely to vary between parameter subsets and the chosen method of model calibration.
+Variation in parameter estimates given differences in the calibration method and identifiability thresholds has meaningful implications for intrerpreting model output.
+Further, the extent to which the results for the simple \ac{zerod} extrapolate to the larger three-dimensional model should be evaluated.
+Although the simple model
 
@@
 The use of simple sensitivity analyses is insufficient to
-
-% id of single-most redundant parameters - inclusion/exclusion or fig. 7
-
-%' We showed only small subsets are identifiable, similar conclusions have been described by citations in \citep{Wagener01}, p.
-14 for models that follow traditional calibration schemes (e.g., objective function minimization).
 %' 
@@
 The example in teh results highlights how redundant variables can be identified as a necessary part of the model calibration process.
-%' 
-%' Why did identifiability decrease for top five parameters in each category after removing redundant phyto/zoop groups?
-%' 
-%' \citep{Denman03} describes over-parameterization for multiple phyto groups, use this to emphasize collinearity issues with the phyto groups despite differing sensitivity values between groups
-%' 
-%' Identifiability by category - varies with number of parameters in the category but some were more redundant than others (phytoplankton).  
 %' 

### 2016-12-06 ident_manu.tex
four pages done in discussion

@@
   \vspace{1in} 
-  \\ Version Date:   Fri Dec 2 14:10:33 2016 -0600
+  \\ Version Date:   Mon Dec 5 14:51:33 2016 -0600
 	}
@@
 
-Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analsyes.
+Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analyses.
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\textit{umax} for phytoplankton, \textit{Zumax} for zooplankton), mortality coefficient for phytoplankton (\textit{mA}), and the zooplankton half saturation coefficent for grazing (\textit{ZKa}).
 An increase in growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} concentration in the water column.
-Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pool of organic matter.
-Most variables were also sensitive to variation in the half-saturation grazing coefficient which is linked to the concentration of nutrients that support half the maximum grazing rate.
-Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs}.
+Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter.
+Most variables were also sensitive to variation in the half-saturation grazing coefficient which moderates the concentration of nutrients that support half the maximum grazing rate.
+Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs} \citep{Fahnenstiel95,Roelke00,Eldridge10}.
 The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance to biological relationships.
@@
 
-% Commonalities in idenfitiability that emerged were 1) potentially driven by a single parameter, 2) nto related to sensitivity, 3) not always related to sheer number of aprmaters
+Results from the identifiability analyses provided additional insight into the interactions of parameters in large biogeochemical models.
+First, identifiability of parameter subsets was not related to the sensitivity of individual variables.
+As noted above, an identifiable parameter is one that has a unique effect on model predictions that cannot be compensated for or undone by changing values of other parameters.
+The magnitude of the effect has no bearing on identifiability, which further complicates the selection of parameters for calibration.
+Although identifiability is the primary limiting factor in choosing a given set, the relative sensitivities are more important for the decision to include or exclude indvidual parameters.
+Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
+Similarly, identifability was not always related to the number of parameters in a set.
+Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
+For example, \cref{fig:exclex} shows that including \textit{KGcdom}, \textit{KO2}, or \textit{nitmax} in parameters sets more often reduced $\gamma$ relative to sets that excluded the parameters.
+Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parame ters often caused a disporportionate increase in $\gamma$ (e.g., \textit{ediblevector(Z1)}).
+These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
+The selection criteria proposed in our above analyses can facilitate parameter selection and also provide diagnostic tools to identify parameters with disproportionate effects on $\gamma$.
+
+\subsection{Recommendations and conclusions}
+
+An evaluation of parameter uncertainty and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
+In general, uncertainty analyses that lead to improved models are ultimately expected to increase our understanding of properties that define ecosystems using relationships described by the model.
+The extension of simple parameter sensitivity analyses to the generalization of ecosystem properties requires additional analysis and potential model refinement, at the core of which is the balance between generality and precision.
+We emphasize that the utility of a specific model depends on the question and objective for application to a specific system.
+For the above analysis, the FishTank model as part of the larger \ac{cgem} application was evaluated in the context of hypoxia effects on ecosystem condition and function.
+At the core of the simple model is a set of biogeochemical equations that characterize the system in relation to planktonic groups, nutrient requirements, and water-column metabolism.
+Our results have shown that relatively small subsets of parameters are identifiable given the complexity of the model, and as a result, we have provided a general approach to select parameter subsets depending on the ecological context (i.e., selection by parameter category, selection for specific state variables).
+Thus, the results described above have relevance for further model refinement with the specific goal of better understanding ecological dynamics that moderate hypoxia on the northern \ac{gom}.
+However, the general principles of sensitivity and parameter identifiability have broad applicability beyond this context and we argue that such methods should be more universally applied as an initial approach to quantify numerical constraints of biogeochemical models.
+
+Specific approaches can be used to improve and build on the results presented herein, in addition to the more general considerations noted above.
+A logical next step is an evaluation of model precision following calibration with relevant parameter subsets.
+For simplicity, our analysis did not calibrate model parameters and an explicit assumption was that parameter subsets with $\gamma$ below 10 or 15 were identifiable.
+To our knowledge, this threshold has not been rigorously evaluated and a logical expectation is that this threshold is likely to vary between parameter subsets and the chosen method of model calibration.
+Variation in parameter estimates given differences in the calibration method and identifiability thresholds has meaningful implications for intrerpreting model output.
+Further, the extent to which the results for the simple \ac{zerod} extrapolate to the larger three-dimensional model should be evaluated.
+Although the simple model
 

### 2016-12-07 ident_manu.Rnw
draft done

@@
 In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
-We argue that quantitative and ecological certainty in model calibration are often at odds and practitioners must choose explicit model components to optimize given tradeoffs between the two.
-We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of parameter perturbations on model output.
-As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in hypoxic condition can be potentially misguided in the absence of quantitative descriptions of identifiability.
-Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.
+The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates.
+Variation in sensitivity had a direct correspendence wtih identifiability, such that only small subsets of the complete parameter set were characterized as having unique effects on the model output.
+As a result, we provide a set of parameter selection heuristics that can be used to identify parameters for model calibration that depend on relative sensitivity and ecological categories within the biogeochemical equations.
+Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in evaluations of water quality models.
 In addition to immediate implications for regional models, we provide a framework for describing the effects of parameter uncertainty and identifiability that can be applied to similar models to better inform environmental management.
@@
 Specific approaches can be used to improve and build on the results presented herein, in addition to the more general considerations noted above.
-A logical next step is an evaluation of model precision following calibration with relevant parameter subsets.
+An evaluation of model precision following calibration with relevant parameter subsets could provide additional information that supports results from the sensitivity analyses.
 For simplicity, our analysis did not calibrate model parameters and an explicit assumption was that parameter subsets with $\gamma$ below 10 or 15 were identifiable.
-To our knowledge, this threshold has not been rigorously evaluated and a logical expectation is that this threshold is likely to vary between parameter subsets and the chosen method of model calibration.
-Variation in parameter estimates given differences in the calibration method and identifiability thresholds has meaningful implications for intrerpreting model output.
-Further, the extent to which the results for the simple \ac{zerod} extrapolate to the larger three-dimensional model should be evaluated.
-Although the simple model
-
-%The \ac{cgem} model also has the ability to model multiple phytoplankton and zooplankton groups, whereas the FishTank model evaluated herein only evaluated one group each for simplicity.
-The use of simple sensitivity analyses is insufficient to
-%' 
-%' Emphasize that parameters that have the greatest effect on collinearity are not those that have the highest sensitivity (contrast the identifiability by category vs identifiability by top parameters)  , also note that groups of parameters together can have large effects on collinearity, maybe some kind of bootstrap analysis could be done looking at doubletons, etc.
-The example in teh results highlights how redundant variables can be identified as a necessary part of the model calibration process.
-%' 
-%' Questions specific to GOM - what initial conditions are important? How many phytoplankton groups do we need (e.g., related to structural uncertainty)?
-%' 
-%' How does the assimilation of additional parameters (e.g., other state variables) during calibration influence the conclusions?
-\citet{Wagener01} describes this as a potential approach to improving model performance by improving the availability of information for model calibration (p.
-14).
-%' 
-%' How does uncertainty translate to what a model should provide (generality v precision)?  The first step - find out what can be optimized but then do not overfit....
-%' 
-%' What about structural uncertainty - does sensitivity of a model to variation in a parameter imply parameter uncertainty and/or structural uncertainty?
-%' 
-%' A final point about optimization with identifiable parameter sets - optimization to fit the data still does not ensure a correct model.
-Failing in one way can be over-compensated by another feature, e.g., the parameter set that is optimized (see \cite{Flynn05}, p.
-1207, third paragraph), also \citep{Durand02,Arhonditsis08}, also note that over-parameterized models are not necessarily bad, see \citep{Omlin01}, models must be validated for the uses which they were intended where a comparison of observed and predicted is the simplest approach and other methods should be used depending on analysis needs \citep{Rykiel96}
-%' 
-%' \cite{Omlin01} state that the sensitivity, identifiability, estimation process is iterative (p. 113), need to rinse and repeat for proper calibration. 
-%' 
-%' How to improve identifiability - get more/better observed data, include obs from other state variables in RSS minimization (eqn q in \cite{Omlin01})
-%' 
-%' Alternative methods for uncertainty analysis - bayesian, MCMC, nonlinear calibration-constrained optimization \citep{Gallagher07}, \citep{Arhonditsis08}
-%' 
-%' Our heuristic products are partially analogous to the Rainfall-Runoff Modelling Toolbox (RRMT) presented by \citep{Wagener01b}2001 (cited on page 15, in \citealt{Wagener01}), although ours is simple in comparison
+To our knowledge, this threshold has not been rigorously evaluated and an expectation is that this threshold is likely to vary between parameter subsets and the chosen calibration method.
+Variation in parameter estimates given the calibration method and different identifiability thresholds could affect the interpration of model output.
+Further, the extent to which results for the \ac{zerod} extrapolate to the larger three-dimensional model should be evaluated.
+Although the above analyses were facilitated using the \ac{zerod} model (i.e, quick execution times, ease of changing model parameters), lack of physical transport or spatial components potentially limits extrapolation of the results to the larger model.
+Uncertainy in parameter estimates at lower dimensions could be magnified as errors propagate to larger scales or site-specific observations for model calibration are not appropriate across a hydrodynamic grid \citep{Harvey00,Lehrter10}.
+The effects of structural or observational uncertainty should also be evaluated in the context of the larger model.
+Our simple approach to examine changes in the initial conditions and switches used in the model showed that sensitivity estimates of individual parameters were affected, having further implications for characterizing identifiability.
 

### 2016-12-07 ident_manu.tex
draft done

@@
   \vspace{1in} 
-  \\ Version Date:   Mon Dec 5 14:51:33 2016 -0600
+  \\ Version Date:   Tue Dec 6 13:56:23 2016 -0600
 	}

### 2016-12-07 ident_manu.Rnw
personal edits to results, discussion

@@
 
+% invisible section anchor
+\newcommand\invisiblesection[1]{%
+  \refstepcounter{section}%
+  \addcontentsline{toc}{section}{\protect\numberline{\thesection}#1}%
+  \sectionmark{#1}}
+
 %knitr options
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{locO2$tot} of the \Sexpr{length(p1z1pars)} (\Sexpr{round(100 * locO2$tot/length(p1z1pars), 0)}\% of total) evaluated parameters in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{locO2$tot} of the \Sexpr{length(p1z1pars)} (\Sexpr{round(100 * locO2$tot/length(p1z1pars), 0)}\% of total) parameters that were evaluated in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
 Within each parameter category, \ac{do} was sensitive to \Sexpr{locO2$bycat$Optics} parameters for optics (\Sexpr{locO2$lncat$Optics} of all optic parameters), \Sexpr{locO2$bycat$`Organic Matter`} for organic matter (\Sexpr{locO2$lncat$`Organic Matter`}), \Sexpr{locO2$bycat$Phytoplankton} for phytoplankton (\Sexpr{locO2$lncat$Phytoplankton}), \Sexpr{locO2$bycat$Temperature} for temperature (\Sexpr{locO2$lncat$Temperature}), and \Sexpr{locO2$bycat$Zooplankton} for zooplankton (\Sexpr{locO2$lncat$Zooplankton}).
@@
 Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{locO2$sensrng$error[1]} for \Sexpr{locO2$sensrng$Parameter[1]} (\Sexpr{tolower(locO2$sensrng$Category[1])}) to \Sexpr{locO2$sensrng$error[2]} for \Sexpr{locO2$sensrng$Parameter[2]} (\Sexpr{tolower(locO2$sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{locO2$sensave}.
-Within categories (excluding temperature), sensitivity ranged from \Sexpr{locO2$sensrngcat$Optics$error[1]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Optics$error[2]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{locO2$sensrngcat$`Organic Matter`$error[1]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{locO2$sensrngcat$`Organic Matter`$error[2]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{locO2$sensrngcat$Phytoplankton$error[1]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Phytoplankton$error[2]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[2]}) for phytoplankton, and \Sexpr{locO2$sensrngcat$Zooplankton$error[1]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Zooplankton$error[2]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{tab:dosens}).
+Within categories (excluding temperature with one sensitive parameter), sensitivity ranged from \Sexpr{locO2$sensrngcat$Optics$error[1]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Optics$error[2]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{locO2$sensrngcat$`Organic Matter`$error[1]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{locO2$sensrngcat$`Organic Matter`$error[2]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{locO2$sensrngcat$Phytoplankton$error[1]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Phytoplankton$error[2]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[2]}) for phytoplankton, and \Sexpr{locO2$sensrngcat$Zooplankton$error[1]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Zooplankton$error[2]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{tab:dosens}).
 Average sensitivity values in each category were $L1 = $ \Sexpr{locO2$sensavecat$Optics} for optics, \Sexpr{locO2$sensavecat$`Organic Matter`} for organic matter, \Sexpr{locO2$sensavecat$Temperature} for temperature, \Sexpr{locO2$sensavecat$Phytoplankton} for phytoplankton, and \Sexpr{locO2$sensavecat$Zooplankton} for zooplankton.
@@
 Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
-Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% of subsets less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\% less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$).
+Parameter identifiability for \ac{do} decreased (increasing $\gamma$) at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
+By category, identifiability was lowest for all combinations of parameter subsets in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% of subsets less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15, 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$).
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
 Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
-The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15$ and \Sexpr{toppersO2$top1[2]}\% less than $\gamma = 10$ for the top parameters in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the fop four.
+The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15, 10$ for the top parameter in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the top four.
 Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
-Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.
+Most notably, nitrate was consistently the least identifiable variable (highest overall $\gamma$), whereas \ac{do} was most identifiable.
 
@@
 \Cref{fig:percthresh} shows the percentage of identifiable parameter sets for \ac{do} using the same selection criteria in \cref{fig:identplo}, i.e., selection of parameters only within parameter categories and selection of the top sensitive parameters regardless of category.
-\Cref{fig:percthresh} is conceptually similar to \cref{fig:identplo}, with the added effect of a chosen $\gamma$ threshold on identifability.
-Previous studies have provided general rules for $\gamma$ thresholds \citep{Brun01,Omlin01}, such that exact values beyond which model calibration fails could vary for the given model and optimization method.
-The selected $\gamma$ thresholds are somewhat arbitrary, although the results show differences that have implications for parameter selection for model calibration.
+\Cref{fig:percthresh} is similar to \cref{fig:identplo}, with the added effect of a chosen $\gamma$ threshold on identifability.
+Previous studies have provided only general rules for $\gamma$ thresholds \citep{Brun01,Omlin01}, such that exact values for which parameter sets are inestimable likely vary between models and optimization methods.
+As such, multiple values are shown in \cref{fig:percthresh}  given that actual thresholds could vary in practice.
 In general, identifiability decreased with the addition of parameters, although the rate of decrease depended on the selected threshold for $\gamma$.
 More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset, that is, identifiability decreased more quickly with the addition of parameters at lower $\gamma$ thresholds as compared to higher $\gamma$.
-Notable differences in identifiability were also observed by selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
+Notable differences in identifiability were also observed by parameter selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
 
@@
 
-The above results demonstrated that the state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by identifiability thresholds and parameter selection criteria.
-These results further underscore the need for explicit selection heuristics for parameters to calibrate for improving model performance.
+The above results demonstrated that state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by $\gamma$ thresholds and parameter selection criteria.
 Results for each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) applied to each state variable differed in the number of selected parameters and distribution of parameters within each category (\cref{tab:heurist1,tab:heurist2,tab:heurist3}).
@@
 As noted above, nitrate was the least identifiable variable (\cref{fig:identploall}), whereas other variables (e.g., \ac{do}, irradiance) were more identifiable.
-The constraints on relative identifiability between variables were demonstrated with the selection heuristics.
-For example, heuristics for nitrate typically selected only one or two parameters that met the criteria as compared to more identifiable variables that included several parameters that were identifiable.
+The constraints on identifiability between variables were demonstrated with the selection heuristics.
+For example, heuristics for nitrate typically selected only one or two parameters that met the criteria as compared to more identifiable variables that included several parameters.
 Overall, the first selection heuristic demonstrated that the number of parameters chosen by parameter category differed independently of the state variables (\cref{tab:heurist1}).
 The number of selected parameters averaged across state variables in decreasing order was \Sexpr{catave[4, 2]} parameters from the \Sexpr{catave[4, 1]} category, \Sexpr{catave[3, 2]} from \Sexpr{catave[3, 1]}, \Sexpr{catave[2, 2]} from \Sexpr{catave[2, 1]}, and \Sexpr{catave[1, 2]} from \Sexpr{catave[1, 1]}.
-These rankings were independent of parameter sensitivity and identifiability in each category.
-The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic.
+The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic given equal importance between categories.
 
 \Cref{fig:heurist_stts} demonstrates parameter selection for all state variables following the second heuristic where parameters were chosen by decreasing sensitivity independent of parameter categories (exact values are shown in \cref{tab:heurist2}).
-The y-axis on the plot shows the relative identifiability values with the addition of parameters from one to many on the x-axis (from left to right).
+The y-axis shows the relative identifiability with the addition of parameters from one to many on the x-axis (from left to right).
 The second to last parameter for each variable is the last parameter selected within the potential threshold of $\gamma = 15$.
@@
 For most variables, the phytoplankton edibility vector for zooplankton (\Sexpr{par_txt('ediblevector(Z1)_1')}) caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
-In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disporportionately redundant within a given parameter set.
+In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disproportionately redundant within a given parameter set (i.e., large contribution to $\gamma$).
 This infomation is useful if additional parameter selection rules are developed independently of those proposed herein.
@@
 Changes in average sensitivity using April and September initial conditions showed most variables were less sensitive to parameters in the optics, temperature, and zooplankton categories, whereas increased sensitivity was generally observed for parameters in the organic matter and phytoplankton categories.
-Some exceptions were observed, such as a decrease in nitrogen sensitivity to phytoplankton parameters.
+Some exceptions were observed, such as a decrease in nitrogen sensitivity to phytoplankton parameters (\cref{tab:inistrchg}).
 Effects of structural complexity were most apparent as an increase in sensitivity of state variables to phytoplankton and temperature parameters, as noted for the individual variables in \cref{fig:sensalltile}.
@@
 Common goals in the application of biogeochemical models of ecosystem processes are to \begin{inparaenum}[1\upshape)]
-\item accurately describe the system my matching predictions with observed data \citep{Reckhow90}, and 
+\item accurately describe the system by matching predictions with observed data \citep{Reckhow90}, and 
 \item provide a means of forecasting ecosystem condition with hypothesized management or environmental scenarios \citep{Clark01}. 
 \end{inparaenum}
-Although these objectives are the focus of most model applications, the structural components of process-based models should secondarily provide inference into which ecosystem processes and functions are driving observed or hypothesized changes.
-This latter objective represents a more general scientific outcome of biogeochemical models that extends beyond the applied benefits of describing and predicting change in a particular system.
+Although these objectives are the focus of most applications, the structural components of process-based models should secondarily provide inference into which ecosystem processes and functions are driving observed changes.
+This latter objective represents a more generic scientific purpose of biogeochemical models that extends beyond the applied benefits of describing and predicting change in a particular system.
 Modelers often hope to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting hypotheses \citep{Kirchner06}.
-Extension of these principles to test the effects of structural changes and observation uncertainty on model predictions provides further evidence to validate model components.
+Extension of these principles to test the effects of structural changes and observation uncertainty on model predictions provides further information to support validation of model components.
 This study provided a simple approach to use the effects of parameter perturbations on model state variables to characterize identifiable parameter subsets that vary by parameter selection criteria.
@@
 We further demonstrated that changes in the model structure and variation in the initial conditions had an effect on sensitivity which has direct implications for identifiability.
-In general, these results provide justification for the use of explicit parameter selection heuristics that practitioners should adopt for model calibration.
+In general, these results provide justification for the use of explicit parameter selection heuristics that practitioners should adopt to facilitate model calibration.
 
@@
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\Sexpr{par_txt('umax_1')} for phytoplankton, \Sexpr{par_txt('Zumax_1')} for zooplankton), mortality coefficient for phytoplankton (\Sexpr{par_txt('mA_1')}), and the zooplankton half saturation coefficent for grazing (\Sexpr{par_txt('ZKa_1')}).
-An increase in growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} concentration in the water column.
+An increase in the growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} in the water column.
 Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter.
@@
 The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance to biological relationships.
-State variables were sensitive to changes in light and temperature parameters, although to a lesser extent than phytoplankton and zooplankton parameters.
+That is, state variables were sensitive to changes in light and temperature parameters, although to a lesser extent than phytoplankton and zooplankton parameters.
 As such, the differing sensitivities of state variables to parameters in each of the categories was not unexpected given general ecological relationships that are well understood and described by the model.
@@
 The redundancies identified with the sensitivity analyses are only problematic if the primary interest is, for example, \ac{do} dynamics.
-Moreover, the proposed parameter selection heuristics provide flexibility for selecting different parameters based on parameter categories with the assumption that the chosen parameters depends on the research or management question.
+Moreover, the proposed selection heuristics provide flexibility for choosing different parameters with the assumption that those chosen depend on the research or management question.
 
@@
 First, identifiability of parameter subsets was not related to the sensitivity of individual variables.
-As noted above, an identifiable parameter is one that has a unique effect on model predictions that cannot be compensated for or undone by changing values of other parameters.
-The magnitude of the effect has no bearing on identifiability, which further complicates the selection of parameters for calibration.
-Although identifiability is the primary limiting factor in choosing a given set, the relative sensitivities are more important for the decision to include or exclude indvidual parameters.
+As noted above, an identifiable parameter is one that has a unique effect on model predictions that cannot be compensated for or undone by changing other parameters.
+The magnitude of the effect of a parameter has no bearing on identifiability, which further complicates the selection of parameters for calibration.
+Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude indvidual parameters.
 Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
@@
 Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
-For example, \cref{fig:exclex} shows that including \Sexpr{par_txt('KGcdom_1')}, \Sexpr{par_txt('KO2_1')}, or \Sexpr{par_txt('nitmax_1')} in parameters sets more often reduced $\gamma$ relative to sets that excluded the parameters.
-Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parame ters often caused a disporportionate increase in $\gamma$ (e.g., \Sexpr{par_txt('ediblevector(Z1)_1')}).
+For example, \cref{fig:exclex} shows that including \Sexpr{par_txt('KGcdom_1')}, \Sexpr{par_txt('KO2_1')}, or \Sexpr{par_txt('nitmax_1')} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
+Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parameters often caused a disproportionate increase in $\gamma$ (e.g., \Sexpr{par_txt('ediblevector(Z1)_1')}).
 These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
@@
 An evaluation of parameter uncertainty and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
-In general, uncertainty analyses that lead to improved models are ultimately expected to increase our understanding of properties that define ecosystems using relationships described by the model.
+In general, uncertainty analyses that lead to improved models are ultimately expected to increase our understanding of properties defining ecological relationships.
 The extension of simple parameter sensitivity analyses to the generalization of ecosystem properties requires additional analysis and potential model refinement, at the core of which is the balance between generality and precision.
 We emphasize that the utility of a specific model depends on the question and objective for application to a specific system.
-For the above analysis, the FishTank model as part of the larger \ac{cgem} application was evaluated in the context of hypoxia effects on ecosystem condition and function.
+For the above analysis, the FishTank model, as part of the larger \ac{cgem} application, was evaluated in the context of hypoxia effects on ecosystem condition and function.
 At the core of the simple model is a set of biogeochemical equations that characterize the system in relation to planktonic groups, nutrient requirements, and water-column metabolism.
@@
 For simplicity, our analysis did not calibrate model parameters and an explicit assumption was that parameter subsets with $\gamma$ below 10 or 15 were identifiable.
-To our knowledge, this threshold has not been rigorously evaluated and an expectation is that this threshold is likely to vary between parameter subsets and the chosen calibration method.
+To our knowledge, this threshold has not been rigorously evaluated and it is likely to vary between parameter subsets and the chosen calibration method.
 Variation in parameter estimates given the calibration method and different identifiability thresholds could affect the interpration of model output.
 Further, the extent to which results for the \ac{zerod} extrapolate to the larger three-dimensional model should be evaluated.
-Although the above analyses were facilitated using the \ac{zerod} model (i.e, quick execution times, ease of changing model parameters), lack of physical transport or spatial components potentially limits extrapolation of the results to the larger model.
+Although the above analyses were facilitated using the \ac{zerod} model (i.e, quick execution times, ease of changing model parameters), lack of physical transport or spatial components potentially limits extrapolation of the results.
 Uncertainy in parameter estimates at lower dimensions could be magnified as errors propagate to larger scales or site-specific observations for model calibration are not appropriate across a hydrodynamic grid \citep{Harvey00,Lehrter10}.
@@
 \end{singlespace}
-\clearpage
 
@@
 % tables
+
+\invisiblesection{Tables}
 
@@
 stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
-stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'POM', 'DOM', 'Phosphate'))
 
@@
 Duplicate parameters and ranks in the first two columns apply only to $\\gamma$ values in the same row (i.e., parameter ranks vary for each variable).'
-colnms <- c('Rank', 'Ammonium', 'Chl-\\textit{a}', 'O$_2$', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
+colnms <- c('Rank', 'Ammonium', 'Chl-\\textit{a}', 'O$_2$', 'Irradiance', 'Nitrate', 'POM', 'DOM', 'Phosphate')
 
@@
   stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
-  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))
+  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'POM', 'DOM', 'Phosphate'))
 
@@
 
+\invisiblesection{Figure}
+
 % combination example
@@
 stts_lev <- c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4')
-stts_lab <- c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')
+stts_lab <- c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'POM', 'DOM', 'Phosphate')
 

### 2016-12-07 ident_manu.tex
personal edits to results, discussion

@@
   \vspace{1in} 
-  \\ Version Date:   Tue Dec 6 13:56:23 2016 -0600
+  \\ Version Date:   Wed Dec 7 11:57:48 2016 -0600
 	}
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 38 of the 51 (75\% of total) evaluated parameters in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 38 of the 51 (75\% of total) parameters that were evaluated in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
 Within each parameter category, \ac{do} was sensitive to three parameters for optics (75\% of all optic parameters), eight for organic matter (67\%), 16 for phytoplankton (73\%), one for temperature (50\%), and 10 for zooplankton (91\%).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ $8.34\times 10^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $0.01$.
-Within categories (excluding temperature), sensitivity ranged from $4.39\times 10^{-5}$ (\textit{astarOMA}) to $7.51\times 10^{-4}$ (\textit{astar490}) for optics, $4.17\times 10^{-4}$ (\textit{KNH4}) to $0.01$ (\textit{KG1}) for organic matter, $8.34\times 10^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69\times 10^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton (\cref{tab:dosens}).
-Average sensitivity values in each category were $L1 = $ $2.81\times 10^{-4}$ for optics, $0$ for organic matter, $0.02$ for temperature, $0.01$ for phytoplankton, and $0.01$ for zooplankton.
+Among all parameters, sensitivity values ranged from $L1 = $ $8.34\times 10^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $9.2\times 10^{-3}$.
+Within categories (excluding temperature with one sensitive parameter), sensitivity ranged from $4.39\times 10^{-5}$ (\textit{astarOMA}) to $7.51\times 10^{-4}$ (\textit{astar490}) for optics, $4.17\times 10^{-4}$ (\textit{KNH4}) to $6.15\times 10^{-3}$ (\textit{KG1}) for organic matter, $8.34\times 10^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69\times 10^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton (\cref{tab:dosens}).
+Average sensitivity values in each category were $L1 = $ $2.81\times 10^{-4}$ for optics, $2.17\times 10^{-3}$ for organic matter, $0.02$ for temperature, $0.01$ for phytoplankton, and $0.01$ for zooplankton.
 
@@
 Average $L1$ ranged from $0.02$ for irradiance (\cref{tab:irrsens}) to $0.71$ for \ac{dom} (\cref{tab:om2sens}).
-All average sensitivity values for the state variables were higher than the average for \ac{do} ($L1$ = $0.01$).
+All average sensitivity values for the state variables were higher than the average for \ac{do} ($L1$ = $9.2\times 10^{-3}$).
 For each variable, $L1$ ranged from $2.24\times 10^{-6}$ (\textit{QminP}) to $8.49$ (\textit{mA}) for ammonium (\cref{tab:nh4sens}), $1.38\times 10^{-6}$ (\textit{QminP}) to $13.94$ (\textit{mA}) for \ac{chla} (\cref{tab:chlsens}), $1.92\times 10^{-7}$ (\textit{QminP}) to $0.13$ (\textit{ZKa}) for irradiance (\cref{tab:irrsens}), $6.67\times 10^{-7}$ (\textit{QminP}) to $8.49$ (\textit{umax}) for nitrate (\cref{tab:no3sens}), $6.41\times 10^{-5}$ (\textit{KNH4}) to $7.22$ (\textit{mA}) for \ac{pom} (\cref{tab:om1sens}),  $7.41\times 10^{-5}$ (\textit{KNH4}) to $14.25$ (\textit{mA}) for \ac{dom} (\cref{tab:om2sens}), and $8.21\times 10^{-7}$ (\textit{QminP}) to $1.47$ (\textit{ZKa}) for phosphate (\cref{tab:po4sens}).
 For the parameter categories, ammonium was most sensitive to phytoplankton parameters (average $L1$ = $0.8$ across all parameters in the category), \ac{chla} to phytoplankton ($L1$ = $1.14$), irradiance to zooplankton ($L1$ = $0.03$), nitrate to zooplankton ($L1$ = $1.06$), \ac{pom} to temperature ($L1$ = $0.86$), \ac{dom} to temperature ($L1$ = $1.48$), and phosphate to zooplankton ($L1$ = $0.31$).
-Finally, average sensitivity between parameter categories independent of the state variables ranged from $0.01$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
+Finally, average sensitivity between parameter categories independent of the state variables ranged from $8.38\times 10^{-3}$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
 
@@
 Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
-Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
-By category, identifiability was lowest for all combinations of parameter subsets in the phytoplankton ($60$\% of subsets less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas all combinations were identifiable for optics ($100$\% less than $\gamma = 15$, $100$\% less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$).
+Parameter identifiability for \ac{do} decreased (increasing $\gamma$) at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
+By category, identifiability was lowest for all combinations of parameter subsets in the phytoplankton ($60$\% of subsets less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas all combinations were identifiable for optics ($100$\% less than $\gamma = 15, 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$).
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
 Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
-The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15$ and $100$\% less than $\gamma = 10$ for the top parameters in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the fop four.
+The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15, 10$ for the top parameter in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the top four.
 Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
-Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.
+Most notably, nitrate was consistently the least identifiable variable (highest overall $\gamma$), whereas \ac{do} was most identifiable.
 
@@
 As noted above, nitrate was the least identifiable variable (\cref{fig:identploall}), whereas other variables (e.g., \ac{do}, irradiance) were more identifiable.
-The constraints on relative identifiability between variables were demonstrated with the selection heuristics.
-For example, heuristics for nitrate typically selected only one or two parameters that met the criteria as compared to more identifiable variables that included several parameters that were identifiable.
+The constraints on identifiability between variables were demonstrated with the selection heuristics.
+For example, heuristics for nitrate typically selected only one or two parameters that met the criteria as compared to more identifiable variables that included several parameters.
 Overall, the first selection heuristic demonstrated that the number of parameters chosen by parameter category differed independently of the state variables (\cref{tab:heurist1}).
 The number of selected parameters averaged across state variables in decreasing order was 4.25 parameters from the phytoplankton category, 3.5 from organic matter, 2.75 from optics, and 2.38 from zooplankton.
-These rankings were independent of parameter sensitivity and identifiability in each category.
-The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic.
+The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic given equal importance between categories.
 
 \Cref{fig:heurist_stts} demonstrates parameter selection for all state variables following the second heuristic where parameters were chosen by decreasing sensitivity independent of parameter categories (exact values are shown in \cref{tab:heurist2}).
-The y-axis on the plot shows the relative identifiability values with the addition of parameters from one to many on the x-axis (from left to right).
+The y-axis shows the relative identifiability with the addition of parameters from one to many on the x-axis (from left to right).
 The second to last parameter for each variable is the last parameter selected within the potential threshold of $\gamma = 15$.
@@
 For most variables, the phytoplankton edibility vector for zooplankton (\textit{ediblevector(Z1)}) caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
-In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disporportionately redundant within a given parameter set.
+In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disproportionately redundant within a given parameter set (i.e., large contribution to $\gamma$).
 This infomation is useful if additional parameter selection rules are developed independently of those proposed herein.
@@
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\textit{umax} for phytoplankton, \textit{Zumax} for zooplankton), mortality coefficient for phytoplankton (\textit{mA}), and the zooplankton half saturation coefficent for grazing (\textit{ZKa}).
-An increase in growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} concentration in the water column.
+An increase in the growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} in the water column.
 Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter.
@@
 Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
-For example, \cref{fig:exclex} shows that including \textit{KGcdom}, \textit{KO2}, or \textit{nitmax} in parameters sets more often reduced $\gamma$ relative to sets that excluded the parameters.
-Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parame ters often caused a disporportionate increase in $\gamma$ (e.g., \textit{ediblevector(Z1)}).
+For example, \cref{fig:exclex} shows that including \textit{KGcdom}, \textit{KO2}, or \textit{nitmax} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
+Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parameters often caused a disproportionate increase in $\gamma$ (e.g., \textit{ediblevector(Z1)}).
 These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
@@
 \hline
-Dissolved Inorganic Carbon&$2134$&$2096.5$&$2133.37$\tabularnewline
+Dissolved Inorganic Carbon&$2.13\times 10^{3}$&$2.1\times 10^{3}$&$2.13\times 10^{3}$\tabularnewline
 Ammonium&$1.09$&$1.79$&$0.35$\tabularnewline
@@
 \hline\hline
-\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Ammonium}&\multicolumn{1}{c}{Chl-\textit{a}}&\multicolumn{1}{c}{O$_2$}&\multicolumn{1}{c}{Irradiance}&\multicolumn{1}{c}{Nitrate}&\multicolumn{1}{c}{OM1}&\multicolumn{1}{c}{OM2}&\multicolumn{1}{c}{Phosphate}\tabularnewline
+\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{Ammonium}&\multicolumn{1}{c}{Chl-\textit{a}}&\multicolumn{1}{c}{O$_2$}&\multicolumn{1}{c}{Irradiance}&\multicolumn{1}{c}{Nitrate}&\multicolumn{1}{c}{POM}&\multicolumn{1}{c}{DOM}&\multicolumn{1}{c}{Phosphate}\tabularnewline
 \hline
@@
 ~~\scriptsize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
-~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$5.36$&-&$7.78$&$7.87$&-\tabularnewline
-~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.73$\tabularnewline
-~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&-&$10.04$\tabularnewline
-~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$6.02$&-&$7.91$&$7.87$&-\tabularnewline
+~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$7.87$&$5.36$&-&-&$7.78$\tabularnewline
+~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&$4.73$&-\tabularnewline
+~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&$10.04$&-\tabularnewline
+~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$7.87$&$6.02$&-&-&$7.91$\tabularnewline
 \hline
 {\bfseries Organic Matter}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
-~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&-&$1$&$1$\tabularnewline
+~~\scriptsize{\textit{KG2}}&$1$&-&-&-&$1$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&-&$1$&-&-&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&-&$1$&-&-\tabularnewline
 ~~\scriptsize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&-&$1.93$&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&$13.43$&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&$1.39$&-&-&-&$1.47$\tabularnewline
 ~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
-~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$3$&-&-&-&-&$8.19$&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&$13.75$&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$3$&-&-&-&$11.96$&-&-&-&$14.07$\tabularnewline
 ~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
+~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&$14.68$&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&-&$10.65$&-&-&$14.08$\tabularnewline
 ~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline
@@
 {\bfseries Phytoplankton}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
-~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$2$&-&-&-&-&-&-&$1.21$&-\tabularnewline
-~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$7.45$\tabularnewline
-~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
+~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&$1$&-&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&-&$1$&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&-&-&$1.15$\tabularnewline
+~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&-&$1.29$&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&-&$11.57$&-&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$2$&-&-&-&$1.21$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&$7.45$&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&-&$1.98$&-&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&$2.9$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&-&-&$3.26$\tabularnewline
 ~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
-~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
-~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&-&$4.09$&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&-&-&$4.98$\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&$4.9$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&-&-&$10.11$\tabularnewline
 ~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
@@
 {\bfseries Zooplankton}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
-~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
-~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&-&-&$7.3$&$5.43$&-\tabularnewline
-~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
+~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&-&$1$&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&$1$&-&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&$5.43$&-&-&-&$7.3$\tabularnewline
+~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&-&$6.32$&$9.76$&$8.54$&-\tabularnewline
 ~~\scriptsize{\textit{Zm}}&$3$&-&-&$4.57$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&$6.93$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Zm}}&$4$&-&-&-&$11.86$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&-&$6.93$&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zm}}&$4$&-&-&-&-&$11.86$&-&-&-\tabularnewline
 ~~\scriptsize{\textit{Zumax}}&$4$&-&-&$5.2$&-&-&-&-&-\tabularnewline
@@
 \hline
+{\bfseries DOM}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
+~~3&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$2.46$\tabularnewline
+~~4&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.91$\tabularnewline
+\hline
 {\bfseries Irradiance}&&&&\tabularnewline
@@
 \hline
-{\bfseries OM1}&&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$7.22$&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Zumax}}&$0.96$&$1$\textsubscript{Z}&$1.15$\tabularnewline
-~~3&\scriptsize{\textit{KG1}}&$0.92$&$1$\textsubscript{OM}&$3.87$\tabularnewline
-\hline
-{\bfseries OM2}&&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
-~~3&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$2.46$\tabularnewline
-~~4&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.91$\tabularnewline
-\hline
 {\bfseries Phosphate}&&&&\tabularnewline
@@
 ~~4&\scriptsize{\textit{ZQn}}&$0.5$&$2$\textsubscript{Z}&$13.74$\tabularnewline
+\hline
+{\bfseries POM}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$7.22$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Zumax}}&$0.96$&$1$\textsubscript{Z}&$1.15$\tabularnewline
+~~3&\scriptsize{\textit{KG1}}&$0.92$&$1$\textsubscript{OM}&$3.87$\tabularnewline
 \hline
@@
 ~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.02$&$1$\textsubscript{T}&$2.29$\tabularnewline
-~~4&\scriptsize{\textit{KG1}}&$0.01$&$1$\textsubscript{OM}&$3.85$\tabularnewline
+~~4&\scriptsize{\textit{KG1}}&$6.15\times 10^{-3}$&$1$\textsubscript{OM}&$3.85$\tabularnewline
 ~~5&\scriptsize{\textit{astar490}}&$7.51\times 10^{-4}$&$1$\textsubscript{O}&$3.89$\tabularnewline
@@
 ~~7&\scriptsize{\textit{ZQn}}&$0.02$&$2$\textsubscript{Z}&$5.22$\tabularnewline
+\hline
+{\bfseries DOM}&&&&\tabularnewline
+~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
+~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
+~~3&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.61$\tabularnewline
+~~4&\scriptsize{\textit{KG2}}&$0.94$&$1$\textsubscript{OM}&$3.39$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$0.04$&$1$\textsubscript{O}&$4.46$\tabularnewline
+~~6&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$6.02$\tabularnewline
+~~7&\scriptsize{\textit{ZKa}}&$0.88$&$2$\textsubscript{Z}&$9.21$\tabularnewline
 \hline
@@
 ~~7&\scriptsize{\textit{mA}}&$0.05$&$2$\textsubscript{P}&$11.21$\tabularnewline
-~~8&\scriptsize{\textit{KG1}}&$0$&$2$\textsubscript{OM}&$14.65$\tabularnewline
-~~9&\scriptsize{\textit{astarOMA}}&$0$&$2$\textsubscript{O}&$14.72$\tabularnewline
+~~8&\scriptsize{\textit{KG1}}&$3.96\times 10^{-3}$&$2$\textsubscript{OM}&$14.65$\tabularnewline
+~~9&\scriptsize{\textit{astarOMA}}&$1.47\times 10^{-3}$&$2$\textsubscript{O}&$14.72$\tabularnewline
 \hline
@@
 \hline
-{\bfseries OM1}&&&&\tabularnewline
+{\bfseries Phosphate}&&&&\tabularnewline
+~~1&\scriptsize{\textit{ZKa}}&$1.47$&$1$\textsubscript{Z}&$1$\tabularnewline
+~~2&\scriptsize{\textit{umax}}&$0.78$&$1$\textsubscript{P}&$11.45$\tabularnewline
+~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.16$&$1$\textsubscript{T}&$13.71$\tabularnewline
+~~4&\scriptsize{\textit{KG1}}&$0.14$&$1$\textsubscript{OM}&$14.64$\tabularnewline
+\hline
+{\bfseries POM}&&&&\tabularnewline
 ~~1&\scriptsize{\textit{mA}}&$7.22$&$1$\textsubscript{P}&$1$\tabularnewline
@@
 ~~5&\scriptsize{\textit{astar490}}&$0.03$&$1$\textsubscript{O}&$5.81$\tabularnewline
-\hline
-{\bfseries OM2}&&&&\tabularnewline
-~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
-~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
-~~3&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.61$\tabularnewline
-~~4&\scriptsize{\textit{KG2}}&$0.94$&$1$\textsubscript{OM}&$3.39$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$0.04$&$1$\textsubscript{O}&$4.46$\tabularnewline
-~~6&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$6.02$\tabularnewline
-~~7&\scriptsize{\textit{ZKa}}&$0.88$&$2$\textsubscript{Z}&$9.21$\tabularnewline
-\hline
-{\bfseries Phosphate}&&&&\tabularnewline
-~~1&\scriptsize{\textit{ZKa}}&$1.47$&$1$\textsubscript{Z}&$1$\tabularnewline
-~~2&\scriptsize{\textit{umax}}&$0.78$&$1$\textsubscript{P}&$11.45$\tabularnewline
-~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.16$&$1$\textsubscript{T}&$13.71$\tabularnewline
-~~4&\scriptsize{\textit{KG1}}&$0.14$&$1$\textsubscript{OM}&$14.64$\tabularnewline
 \hline
@@
 {\bfseries Optics}&&&&&\tabularnewline
-~~Ammonium&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
-~~Chlorophyll&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~Ammonium&$0.01$&&$-9.13\times 10^{-3}$&$-8.37\times 10^{-3}$&$-7.7\times 10^{-3}$\tabularnewline
+~~Chlorophyll&$8.77\times 10^{-3}$&&$-6.79\times 10^{-3}$&$-6.3\times 10^{-3}$&$-7.33\times 10^{-3}$\tabularnewline
 ~~Dissolved Oxygen&$2.81\times 10^{-4}$&&$-2.11\times 10^{-4}$&$-1.46\times 10^{-4}$&$-1.93\times 10^{-4}$\tabularnewline
-~~Irradiance&$0.01$&&$\bm{0}$&$\bm{0}$&$\bm{0}$\tabularnewline
-~~Nitrate&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
-~~OM1&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
-~~OM2&$0.02$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
-~~Phosphate&$0$&&$-0$&$-0$&$-0$\tabularnewline
+~~Irradiance&$9.1\times 10^{-3}$&&$\bm{2.56\times 10^{-3}}$&$\bm{3.1\times 10^{-3}}$&$\bm{1.57\times 10^{-3}}$\tabularnewline
+~~Nitrate&$7.72\times 10^{-3}$&&$-6.46\times 10^{-3}$&$-6.2\times 10^{-3}$&$-6.8\times 10^{-3}$\tabularnewline
+~~POM&$0.01$&&$-9.06\times 10^{-3}$&$-8.49\times 10^{-3}$&$-8.56\times 10^{-3}$\tabularnewline
+~~DOM&$0.02$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~Phosphate&$3.35\times 10^{-3}$&&$-2.53\times 10^{-3}$&$-2.15\times 10^{-3}$&$-3.04\times 10^{-3}$\tabularnewline
 \hline
@@
 ~~Chlorophyll&$0.02$&&$\bm{0.12}$&$\bm{0.14}$&$-0.01$\tabularnewline
-~~Dissolved Oxygen&$0$&&$-6.75\times 10^{-4}$&$\bm{2.32\times 10^{-4}}$&$-0$\tabularnewline
-~~Irradiance&$0.01$&&$\bm{0.01}$&$\bm{0.01}$&$-2.99\times 10^{-4}$\tabularnewline
+~~Dissolved Oxygen&$2.17\times 10^{-3}$&&$-6.75\times 10^{-4}$&$\bm{2.32\times 10^{-4}}$&$-1.05\times 10^{-3}$\tabularnewline
+~~Irradiance&$6.63\times 10^{-3}$&&$\bm{5.34\times 10^{-3}}$&$\bm{6.79\times 10^{-3}}$&$-2.99\times 10^{-4}$\tabularnewline
 ~~Nitrate&$0.12$&&$\bm{0.06}$&$\bm{0.09}$&$-0.1$\tabularnewline
-~~OM1&$0.13$&&$\bm{0.15}$&$\bm{0.12}$&$\bm{0.04}$\tabularnewline
-~~OM2&$0.14$&&$\bm{0.07}$&$\bm{0.17}$&$\bm{0.05}$\tabularnewline
+~~POM&$0.13$&&$\bm{0.15}$&$\bm{0.12}$&$\bm{0.04}$\tabularnewline
+~~DOM&$0.14$&&$\bm{0.07}$&$\bm{0.17}$&$\bm{0.05}$\tabularnewline
 ~~Phosphate&$0.03$&&$\bm{0.04}$&$\bm{0.06}$&$-0.02$\tabularnewline
@@
 ~~Chlorophyll&$1.14$&&$\bm{1.23}$&$\bm{4.38}$&$\bm{104.24}$\tabularnewline
-~~Dissolved Oxygen&$0.01$&&$-4.58\times 10^{-4}$&$\bm{0}$&$\bm{3.44\times 10^{-4}}$\tabularnewline
-~~Irradiance&$0.02$&&$-0$&$\bm{0}$&$\bm{0.01}$\tabularnewline
+~~Dissolved Oxygen&$0.01$&&$-4.58\times 10^{-4}$&$\bm{2.31\times 10^{-3}}$&$\bm{3.44\times 10^{-4}}$\tabularnewline
+~~Irradiance&$0.02$&&$-2.04\times 10^{-3}$&$\bm{1.83\times 10^{-3}}$&$\bm{7.53\times 10^{-3}}$\tabularnewline
 ~~Nitrate&$0.74$&&$-0.43$&$-0.45$&$-0.64$\tabularnewline
-~~OM1&$0.76$&&$\bm{0.17}$&$\bm{0.46}$&$\bm{55.11}$\tabularnewline
-~~OM2&$1.28$&&$\bm{0.34}$&$\bm{1.15}$&$\bm{128.93}$\tabularnewline
+~~POM&$0.76$&&$\bm{0.17}$&$\bm{0.46}$&$\bm{55.11}$\tabularnewline
+~~DOM&$1.28$&&$\bm{0.34}$&$\bm{1.15}$&$\bm{128.93}$\tabularnewline
 ~~Phosphate&$0.17$&&$\bm{0.03}$&$\bm{0.05}$&$-0.14$\tabularnewline
@@
 ~~Nitrate&$0.3$&&$-0.15$&$-0.16$&$-0.19$\tabularnewline
-~~OM1&$0.86$&&$-0.68$&$-0.69$&$\bm{215.17}$\tabularnewline
-~~OM2&$1.48$&&$-1.21$&$-1.2$&$\bm{900.26}$\tabularnewline
+~~POM&$0.86$&&$-0.68$&$-0.69$&$\bm{215.17}$\tabularnewline
+~~DOM&$1.48$&&$-1.21$&$-1.2$&$\bm{900.26}$\tabularnewline
 ~~Phosphate&$0.16$&&$-0.11$&$-0.09$&$-0.11$\tabularnewline
@@
 ~~Chlorophyll&$0.39$&&$-0.26$&$-0.23$&$-0.2$\tabularnewline
-~~Dissolved Oxygen&$0.01$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
+~~Dissolved Oxygen&$0.01$&&$-0.01$&$-8.68\times 10^{-3}$&$-6.96\times 10^{-3}$\tabularnewline
 ~~Irradiance&$0.03$&&$-0.02$&$-0.02$&$-0.01$\tabularnewline
 ~~Nitrate&$1.06$&&$-1.02$&$-1.02$&$-0.98$\tabularnewline
-~~OM1&$0.37$&&$-0.27$&$-0.28$&$-0.18$\tabularnewline
-~~OM2&$0.39$&&$-0.3$&$-0.28$&$-0.18$\tabularnewline
+~~POM&$0.37$&&$-0.27$&$-0.28$&$-0.18$\tabularnewline
+~~DOM&$0.39$&&$-0.3$&$-0.28$&$-0.18$\tabularnewline
 ~~Phosphate&$0.31$&&$-0.19$&$-0.17$&$-0.27$\tabularnewline
@@
 % figures
+
+\invisiblesection{Figure}
 
@@
 
-\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for all state variables.
+\caption[Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for all state variables]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for all state variables.
 Parameters are selected by decreasing sensitivity independent of parameter categories.

### 2016-12-07 R/funcs.R

@@ -40,7 +40,7 @@ form_fun <- function(x, rnd_val = 2, dig_val = 2, nsm_val = 2, ...) {
 # digits numeric for rounding
 # showdollar logical if output is enclosed in dollar for latex
 # from https://dankelley.github.io/r/2015/03/22/scinot.html
-scinot <- function(x, pow = 3, digits = 2, showDollar = TRUE)
+scinot <- function(x, pow = 2, digits = 2, showDollar = TRUE)
 {
   
   x <- as.numeric(x)

### 2016-12-14 ident_manu.Rnw
minor edits to discussion

@@
 % aliased citations
-\defcitealias{LehrterIR}{Lehrter et al. in review}
+\defcitealias{LehrterIP}{Lehrter et al. in press}
 
@@
 These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions \citep{Warner05,Zhao10,Ganju16}.
-Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} (\citealt{Fennel13,Obenour15,Pauer16}, \citetalias{LehrterIR}).
+Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} (\citealt{Fennel13,Obenour15,Pauer16}, \citetalias{LehrterIP}).
 This area drains a significant portion of the continental United States through the \ac{marb} and is the second largest hypoxic area in the world \citep{Rabalais02}.
@@
 
-Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).
+Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIP}).
 A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
@@
 The final parameter set that was evaluated included \Sexpr{length(p1z1pars)} parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
-A full description of the model parameters is available as an appendix in \citetalias{LehrterIR}.
+A full description of the model parameters is available as an appendix in \citetalias{LehrterIP}.
 
@@
 Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).
-Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIR}.
+Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIP}.
 
@@
 Conversely, the complex scenario used switches that modelled relationships between phytoplankton growth with temperature using the Arrhenius model \citep{Geider97}, nutrient uptake as proposed by \citet{Lehman75} and modified in \citet{Geider98}, internal cell quotas following \citet{Flynn03}, \ac{chla} to carbon ratios following \citet{Cloern95}, light-dependence of photosynthesis that is nutrient dependent \citep{Flynn03}, and a specific growth rate that is nutrient dependent.
-Complete details of model switches are provided as supplementary material to \citetalias{LehrterIR}.
+Complete details of model switches are provided as supplementary material to \citetalias{LehrterIP}.
 
@@
 In addition to \ac{do}, other state variables that were evaluated were ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.
-Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIR}).
+Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIP}).
 
@@
 
-Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analyses.
+Although the results were specific to individual variables, some generalities about hypoxia dynamics can be inferred from the sensitivity analyses.
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\Sexpr{par_txt('umax_1')} for phytoplankton, \Sexpr{par_txt('Zumax_1')} for zooplankton), mortality coefficient for phytoplankton (\Sexpr{par_txt('mA_1')}), and the zooplankton half saturation coefficent for grazing (\Sexpr{par_txt('ZKa_1')}).
@@
 
-The overwhelming conclusion from the identifiablity analyses is that only limited subsets of parameters are identifiable within the constraints of local sensitivity analyses.
+The overwhelming conclusion from the identifiability analyses is that only limited subsets of parameters were identifiable within the constraints of local sensitivity analyses.
 Although we have not attempted actual model calibration (see recommendations below), these results support previous studies that have suggested similarly small subsets of parameters can be identified using traditional calibration schemes \citep[e.g.,][]{Wheater86,Ye97,Omlin01}.
@@
 The magnitude of the effect of a parameter has no bearing on identifiability, which further complicates the selection of parameters for calibration.
-Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude indvidual parameters.
+Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude individual parameters.
 Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
@@
 Variation in parameter estimates given the calibration method and different identifiability thresholds could affect the interpration of model output.
-Further, the extent to which results for the \ac{zerod} extrapolate to the larger three-dimensional model should be evaluated.
+Further, the extent to which results for the \ac{zerod} model extrapolate to the larger three-dimensional model should be evaluated.
 Although the above analyses were facilitated using the \ac{zerod} model (i.e, quick execution times, ease of changing model parameters), lack of physical transport or spatial components potentially limits extrapolation of the results.
@@
 The effects of structural or observational uncertainty should also be evaluated in the context of the larger model.
-Our simple approach to examine changes in the initial conditions and switches used in the model showed that sensitivity estimates of individual parameters were affected, having further implications for characterizing identifiability.
+Our simple approach to examine changes in the initial conditions and switches used in the model showed that sensitivity estimates of individual parameters differed relative to the original model configuration, having further implications for characterizing identifiability.
 
@@
 cap_val <- 'Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.
-Complete details and equations are provided as supplementary material to \\citetalias{LehrterIR}.'
+Complete details and equations are provided as supplementary material to \\citetalias{LehrterIP}.'
 

### 2016-12-14 ident_manu.tex
minor edits to discussion

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Dec 7 11:57:48 2016 -0600
+  \\ Version Date:   Wed Dec 7 14:54:11 2016 -0600
 	}
@@
 The final parameter set that was evaluated included 51 parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (22), temperature (2), and zooplankton (11).
-A full description of the model parameters is available as an appendix in \citetalias{LehrterIR}.
+A full description of the model parameters is available as an appendix in \citetalias{LehrterIP}.
 
@@
 
-Although the results were specific to individual variables, some generalities can be inferred from the sensitivity analyses.
+Although the results were specific to individual variables, some generalities about hypoxia dynamics can be inferred from the sensitivity analyses.
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\textit{umax} for phytoplankton, \textit{Zumax} for zooplankton), mortality coefficient for phytoplankton (\textit{mA}), and the zooplankton half saturation coefficent for grazing (\textit{ZKa}).
@@
 \caption{Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.
-Complete details and equations are provided as supplementary material to \citetalias{LehrterIR}.\label{tab:strcs}}
+Complete details and equations are provided as supplementary material to \citetalias{LehrterIP}.\label{tab:strcs}}
 \begin{center}

### 2016-12-15 ident_manu.Rnw
added keywords

@@
 \usepackage{fixltx2e}
-\usepackage[inline]{showlabels}
+% \usepackage[inline]{showlabels}
 \bibpunct{(}{)}{,}{a}{}{,}
@@
 The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates.
-Variation in sensitivity had a direct correspendence wtih identifiability, such that only small subsets of the complete parameter set were characterized as having unique effects on the model output.
+Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set were characterized as having unique effects on the model output.
 As a result, we provide a set of parameter selection heuristics that can be used to identify parameters for model calibration that depend on relative sensitivity and ecological categories within the biogeochemical equations.
@@
 \end{abstract}
+Keywords: \ac{cgem}, \ac{gom}, Hypoxia, Identifiability, Sensitivity
 \acresetall

### 2016-12-15 ident_manu.tex
added keywords

@@
   \vspace{1in} 
-  \\ Version Date:   Wed Dec 7 14:54:11 2016 -0600
+  \\ Version Date:   Wed Dec 14 07:59:53 2016 -0600
 	}

### 2016-12-16 ident_manu.Rnw
elsarticle class

@@
-\documentclass[letterpaper,12pt,oneside]{article}
+\documentclass[preprint]{elsarticle}
 \usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
-\usepackage{setspace}
 \usepackage[colorlinks=true,allcolors=Blue]{hyperref}
-\usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{indentfirst}
-\usepackage{titlesec}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{graphicx}
-\usepackage{verbatim}
-\usepackage{rotating}
-\usepackage{tabularx}
-\usepackage{outlines}
 \usepackage{lineno}
-\usepackage{array}
-\usepackage{times}
 \usepackage{cleveref}
 \usepackage{acronym}
-\usepackage[position=t]{subfig}
 \usepackage{paralist}
-\usepackage[noae]{Sweave}
-\usepackage{natbib}
-\usepackage{array}
-\usepackage{pdflscape}
 \usepackage{bm}
@@
 % \usepackage[inline]{showlabels}
-\bibpunct{(}{)}{,}{a}{}{,}
-
-% page margins and section title formatting
-\linespread{1.5}
-\setlength{\footskip}{0.5in}
-\titleformat*{\section}{\Large\bf\em}
-\titleformat*{\subsection}{\singlespace\large\bf}
-\titleformat*{\subsubsection}{\singlespace\normalsize\bf\em}
-\titlespacing{\section}{0in}{0in}{0in}
-\titlespacing{\subsection}{0in}{0in}{0in}
-\titlespacing{\subsubsection}{0in}{0in}{0in}
+
+% biblio options
+\bibliographystyle{elsarticle-harv}
+\biboptions{authoryear}
 
@@
   \sectionmark{#1}}
+
+% macro fix for multiple asterisks for corr author
+\makeatletter
+\def\@author#1{\g@addto@macro\elsauthors{\normalsize%
+    \def\baselinestretch{1}%
+    \upshape\authorsep#1\unskip\textsuperscript{%
+      \ifx\@fnmark\@empty\else\unskip\sep\@fnmark\let\sep=,\fi
+      \ifx\@corref\@empty\else\unskip\sep\@corref\let\sep=,\fi
+      }%
+    \def\authorsep{\unskip,\space}%
+    \global\let\@fnmark\@empty
+    \global\let\@corref\@empty  %% Added
+    \global\let\sep\@empty}%
+    \@eadauthor={#1}
+}
+\makeatother
 
@@
 
-% get the version based on commit date
+% get the version from git log
 <<echo = FALSE, cache = FALSE>>=
 raw <- system('git log -1', intern = TRUE)
-raw <- raw[grep('^Date', raw)]
-raw <- paste('Version', raw)
+date <- raw[grep('^Date', raw)]
+date <- gsub('^Date:\\s*', '', date)
+commit <- raw[grep('^commit', raw)]
+commit <- gsub('^commit ', '', commit)
+commit <- paste0('\\href{https://github.com/fawda123/identifiability/commit/', commit, '}{', commit, '}')
+vers <- paste0('Version: ', date, ', ', commit)
 @
@@
 
-\raggedbottom
-\linenumbers
-\raggedright
-\urlstyle{same}
-\setlength{\parindent}{0.5in}
-\renewcommand\refname{References \vspace{12pt}}
-
-\begin{singlespace}
-\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
-\author{
-  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
-  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
-  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
-	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
-	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
-	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
-  \\{\textit {\normalsize Dauphin Island, AL 36528}}
-	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
-	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
-	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
-	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
-	\\{\textit {\normalsize Phone: 919-541-3985,}}
-	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
-  \vspace{1in} 
-  \\ \Sexpr{raw}
-	}
+\begin{frontmatter}
+
+\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
+\tnotetext[mytitlenote]{\Sexpr{vers}}
+
 \date{}
-\maketitle
-\end{singlespace}
-\clearpage
+
+\author{Marcus W. Beck\corref{mycorrespondingauthor}}
+\address{USEPA National Health and Environmental Effects Research Laboratory, Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}
+\cortext[mycorrespondingauthor]{Corresponding author}
+\ead{beck.marcus@epa.gov}
+
+\author{John C. Lehrter}
+\address{Dauphin Island Sea Lab, University of South Alabama, Dauphin Island, AL 36528}
+\ead{jlehrter@disl.org}
+
+\author{Lisa L. Lowe}
+\address{Lockheed Martin IS \& GS - Civil supporting the USEPA, Research Triangle Park, NC 27709}
+\ead{lowe.lisa@epa.gov}
 
@@
 \end{abstract}
-Keywords: \ac{cgem}, \ac{gom}, Hypoxia, Identifiability, Sensitivity
+
+\begin{keyword}
+\ac{cgem}, \ac{gom}, Hypoxia, Identifiability, Sensitivity
+\end{keyword}
+
+\end{frontmatter}
+
 \acresetall
+\linenumbers
 
@@
 
+\bibliography{refs}
 \clearpage
-\begin{singlespace}
-\bibliographystyle{apalike_mine}
-\bibliography{refs}
-\end{singlespace}
 
@@
 Identifiability of including all eight parameters is in \\cref{fig:identplo}.
-Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "\\textwidth">>=
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "0.8\\textwidth">>=
 data(cat_ident_all)

### 2016-12-16 ident_manu.tex
elsarticle class

@@
-\documentclass[letterpaper,12pt,oneside]{article}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[preprint]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth
@@
 \usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
-\usepackage{setspace}
 \usepackage[colorlinks=true,allcolors=Blue]{hyperref}
-\usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{indentfirst}
-\usepackage{titlesec}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{graphicx}
-\usepackage{verbatim}
-\usepackage{rotating}
-\usepackage{tabularx}
-\usepackage{outlines}
 \usepackage{lineno}
-\usepackage{array}
-\usepackage{times}
 \usepackage{cleveref}
 \usepackage{acronym}
-\usepackage[position=t]{subfig}
 \usepackage{paralist}
-\usepackage[noae]{Sweave}
-\usepackage{natbib}
-\usepackage{array}
-\usepackage{pdflscape}
 \usepackage{bm}
@@
 
+% macro fix for multiple asterisks for corr author
+\makeatletter
+\def\@author#1{\g@addto@macro\elsauthors{\normalsize%
+    \def\baselinestretch{1}%
+    \upshape\authorsep#1\unskip\textsuperscript{%
+      \ifx\@fnmark\@empty\else\unskip\sep\@fnmark\let\sep=,\fi
+      \ifx\@corref\@empty\else\unskip\sep\@corref\let\sep=,\fi
+      }%
+    \def\authorsep{\unskip,\space}%
+    \global\let\@fnmark\@empty
+    \global\let\@corref\@empty  %% Added
+    \global\let\sep\@empty}%
+    \@eadauthor={#1}
+}
+\makeatother
+
 %knitr options
@@
 
-\raggedbottom
-\linenumbers
-\raggedright
-\urlstyle{same}
-\setlength{\parindent}{0.5in}
-\renewcommand\refname{References \vspace{12pt}}
-
-\begin{singlespace}
-\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
-\author{
-  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
-  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
-  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
-	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
-	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
-	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
-  \\{\textit {\normalsize Dauphin Island, AL 36528}}
-	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
-	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
-	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
-	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
-	\\{\textit {\normalsize Phone: 919-541-3985,}}
-	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
-  \vspace{1in} 
-  \\ Version Date:   Wed Dec 14 07:59:53 2016 -0600
-	}
+\begin{frontmatter}
+
+\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
+\tnotetext[mytitlenote]{Version: Thu Dec 15 15:47:19 2016 -0600, \href{https://github.com/fawda123/identifiability/commit/f47752c773b8b0d1c90abe57d41f57038201ea42}{f47752c773b8b0d1c90abe57d41f57038201ea42}}
+
 \date{}
-\maketitle
-\end{singlespace}
-\clearpage
+
+\author{Marcus W. Beck\corref{mycorrespondingauthor}}
+\address{USEPA National Health and Environmental Effects Research Laboratory, Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}
+\cortext[mycorrespondingauthor]{Corresponding author}
+\ead{beck.marcus@epa.gov}
+
+\author{John C. Lehrter}
+\address{Dauphin Island Sea Lab, University of South Alabama, Dauphin Island, AL 36528}
+\ead{jlehrter@disl.org}
+
+\author{Lisa L. Lowe}
+\address{Lockheed Martin IS \& GS - Civil supporting the USEPA, Research Triangle Park, NC 27709}
+\ead{lowe.lisa@epa.gov}
 
@@
 
-{\centering \includegraphics[width=\textwidth]{figs/exclex-1}
+{\centering \includegraphics[width=0.8\textwidth]{figs/exclex-1}
 

### 2016-12-21 ident_manu.Rnw
bib journals now abbreviated

@@
 % \usepackage[inline]{showlabels}
+
+\journal{Ecological Modelling}
 
@@
 writeLines(refs, con = file('refs.bib'))
+
+# library(Jabbrev)
+# bbl_ext('ident_manu.bbl', 'refs.bib', 'ident_manu.bib')
+# bib_shr('ident_manu.bib', 'refsshr.bib')
 @
@@
 \begin{abstract}
-\noindent Bio-geo-chemical models are useful tools in environmental sciences that can guide management and policy-making.
-Consequently, significant time and resources are spent developing these models in system-specific contexts.
-The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools.
+\noindent The optimization of parameters and transferability to different systems are fundamental concerns in the application of biogeochemical models.
 This study provides a context for understanding quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.
@@
 
-\bibliography{refs}
+\bibliography{refsshr}
 \clearpage

### 2016-12-21 ident_manu.tex
bib journals now abbreviated

@@
 
+\journal{Ecological Modelling}
+
 % biblio options
@@
 
-% get the version based on commit date
+% get the version from git log
 
@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Thu Dec 15 15:47:19 2016 -0600, \href{https://github.com/fawda123/identifiability/commit/f47752c773b8b0d1c90abe57d41f57038201ea42}{f47752c773b8b0d1c90abe57d41f57038201ea42}}
+\tnotetext[mytitlenote]{Version: Fri Dec 16 10:08:47 2016 -0600, \href{https://github.com/fawda123/identifiability/commit/5e43ad8aba3a34ec8163993b8c3ffa785e1f0fcd}{5e43ad8aba3a34ec8163993b8c3ffa785e1f0fcd}}
 

### 2017-03-06 ident_manu.Rnw
commence hacking

@@
 \usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
+\usepackage{setspace}
 \usepackage[colorlinks=true,allcolors=Blue]{hyperref}
@@
 
+\linespread{1.5}
+
 %knitr options
@@
 
+\author{Brandon M. Jarvis}
+\address{USEPA National Health and Environmental Effects Research Laboratory, Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}
+\ead{jarvis.brandon@epa.gov}
+
 \begin{abstract}
@@
 This approach is sometimes called inverse modelling where results from sensitivity analyses are used to guide calibration or fit of the developed model to observations (\citealt{Soetaert10}, or confronting models with data, \textit{sensu} \citealt{Hilborn97}).
-Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability', where only a subset of parameters can be numerically constrained to the data as compared to the entire parameter set.
+Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability', where only a subset of identifiable parameters can be numerically constrained to the data as compared to the entire set.
 Redundancies in parameter effects lead to unidentifiable models where optimal solutions may be empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
@@
 The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.
-Atmospheric and hydrological boundary conditions described in \citet{Hodur97} and \citet{Lehrter13} are also included in \ac{cgem}.
+Atmospheric and hydrologic boundary conditions described in \citet{Hodur97} and \citet{Lehrter13} are also included in \ac{cgem}.
 
@@
 Our simple approach to examine changes in the initial conditions and switches used in the model showed that sensitivity estimates of individual parameters differed relative to the original model configuration, having further implications for characterizing identifiability.
+\clearpage
 

### 2017-03-06 ident_manu.tex
commence hacking

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Fri Dec 16 10:08:47 2016 -0600, \href{https://github.com/fawda123/identifiability/commit/5e43ad8aba3a34ec8163993b8c3ffa785e1f0fcd}{5e43ad8aba3a34ec8163993b8c3ffa785e1f0fcd}}
+\tnotetext[mytitlenote]{Version: Wed Dec 21 10:59:02 2016 -0600, \href{https://github.com/fawda123/identifiability/commit/d3eb2370a7cc79abbb571fc9216ed07baa4c881b}{d3eb2370a7cc79abbb571fc9216ed07baa4c881b}}
 
@@
 \ead{lowe.lisa@epa.gov}
+
+\author{Brandon M. Jarvis}
+\address{USEPA National Health and Environmental Effects Research Laboratory, Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}
+\ead{jarvis.brandon@epa.gov}
 
@@
 \end{tabular}\end{center}
-
 \end{table}
@@
 \end{tabular}\end{center}}
-
 \footnotesize *Temperature parameters apply separately to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts\end{table}
@@
 \end{tabular}\end{center}}
-
 \end{table}

### 2017-03-07 ident_manu.Rnw
fixed column orders in table 2

@@
 
+% fix warning if acronyms are reset after abstract
+\makeatletter
+\renewcommand*\@verridelabel[1]{%
+  \@bsphack
+  \protected@write\@auxout{}{\string\undonewlabel{#1}}%
+  \protected@write\@auxout{}{\string\undonewlabel{#1@cref}}%Added for cleverref
+  \label{#1}%
+  \@overriddenmessage rs{#1}%
+  \@esphack
+}%
+\makeatother
+
 \linespread{1.5}
@@
 
+\linenumbers
 \acresetall
-\linenumbers
 
@@
 
-\subsection{Observational and structural uncertainty}
-
-In addition to parameter uncertainty, the effects of observational and structural uncertainty on the sensitivity analyses were evaluated by changing the initial conditions and structural components, respectively, from the default model setup.
-First, observational uncertainty (i.e., effects of observed data on model output) was evaluated by varying the initial conditions that were based on observational data from research cruises in the northern \ac{gom} \citep{Murrell14}.
-Uncertainty in these data translates directly to uncertainty that can influence results of the sensitivity analysis.
-For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplankton (the concentration supporting half the maximum uptake rate of nutrients) will vary given the initial nutrient concentrations \citep{Eppley69}.
-Further, changes in the ratio between nitrogen and phosphorus could affect sensitivity depending on the limiting nutrient.
-Parameter sensitivity was re-evaluated by varying all initial conditions that were non-zero by different seasonal means based on averages of water quality data across stations and years.
-April and September seasonal averages of the observed data were used to evaluate the effects of conditions that were typical of spring and late summer on the \ac{lcs} (\cref{tab:inits}).
-
-The effects of model structure on parameter sensitivity (i.e., structural uncertainty) were evaluated by changing specific components of the model.
-The FishTank model includes several ecosystem processes or characteristics that can be included based on expected conditions, available data, or desired complexity.
-These `switches' are conceptually different from model parameters as they allow the inclusion or exclusion of explicit equations or processes.
-Switches in FishTank include different structural equations for the vertical attenuation of light through the water column (inherent or apparent optical properties, \citealt{Penta09,Eldridge10}) and chlorophyll to carbon ratio models (fixed or dynamic given light and nutrients, \citealt{Cloern95}).
-Several switches also affect phytoplankton growth including different models for specific growth and effects of temperature, light dependence, nutrient uptake, and internal cell quotas \citepalias[][references therein]{LehrterIP}.
-
-Parameter sensitivity was evaluated by comparing the results from the default model setup to a more complex setup with alternative switches (\cref{tab:strcs}).
-The scenarios used switches for different equations to represent structural relationships of phytoplankton growth patterns with temperature, nutrient uptake, cell quotas, \ac{chla} to carbon ratios, photosynthesis dynamics, and specific growth limits.
-The default scenario modelled phytoplankton growth with temperature as a sigmoidal function \citep{Eldridge10}, nutrient uptake as Michaelis-Menten kinetics \citep{Dugdale67}, internal cell quotas following \citet{Droop73}, \ac{chla} to carbon ratios as a simple regression \citep{Murrell14}, light-dependence of photosynthesis with photoinhibition \citep{Platt80}, and a specific growth rate following Leibig's law of the minimum.
-Conversely, the complex scenario used switches that modelled relationships between phytoplankton growth with temperature using the Arrhenius model \citep{Geider97}, nutrient uptake as proposed by \citet{Lehman75} and modified in \citet{Geider98}, internal cell quotas following \citet{Flynn03}, \ac{chla} to carbon ratios following \citet{Cloern95}, light-dependence of photosynthesis that is nutrient dependent \citep{Flynn03}, and a specific growth rate that is nutrient dependent.
-Complete details of model switches are provided as supplementary material to \citetalias{LehrterIP}.
-
 \subsection{Extension to other state variables}
@@
 Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIP}).
+
+\subsection{Model calibration with parameter subsets}
+
+% we want to show that the results have relevance for the larger three-dimensional model and that model output for calibration to different parameters sets will have differing precision given 1) differences in sensitivity to included ina  subsets and 2) differences given proportion of parameters selected from different categories.
+
+% we use a time series from Weeks Bay NERRS because data are continuous, initial conditions were modified to match weeks bay conditions.
+DO time series was filtered to remove tidal advection component and air/sea gas exhange was used.
+This is not a perfect example but works for our purposes to demonstrate differeing precision as directly related to identifiability of subsets and paramter types in a subset.
+% note that we are not concerned with the magnitude of the error but the differences in error between parameter subsets and number of runs to convergence.
 
@@
 
-\subsection{Observational and structural uncertainty}
-
-Both the relative $L1$ estimates and number of parameters that affected state variables were sensitive to variation in the initial conditions (observation effects) and structural changes in the model.
-Visual comparison of sensitivity values ($L1$) for the default model setup showed that all state variables were sensitive to \Sexpr{par_txt('vmaxSi_1')} after changing the initial conditions to April or September conditions (\cref{fig:sensalltile}).
-State variables were also sensitive to \Sexpr{par_txt('Ksi_1')} for only the September conditions.
-Changing the model structure from the default (simple) to the complex setup showed state variables were also sensitive to \Sexpr{par_txt('KQn_1')} and \Sexpr{par_txt('Tref(nospA+nospZ)_7')}.
-Changes in the sensitivity of individual parameters were also observed, most notably as a disproportionate increase in $L1$ for ammonium, \ac{chla}, \ac{pom}, and \ac{dom} to \Sexpr{par_txt('mA_1')} and \Sexpr{par_txt('Tref(nospA+nospZ)_1')} using the complex model setup.
-Summaries by parameter categories of the effects of initial conditions and structural changes are shown in \cref{tab:inistrchg,fig:inistrsumm}.
-Changes in average sensitivity using April and September initial conditions showed most variables were less sensitive to parameters in the optics, temperature, and zooplankton categories, whereas increased sensitivity was generally observed for parameters in the organic matter and phytoplankton categories.
-Some exceptions were observed, such as a decrease in nitrogen sensitivity to phytoplankton parameters (\cref{tab:inistrchg}).
-Effects of structural complexity were most apparent as an increase in sensitivity of state variables to phytoplankton and temperature parameters, as noted for the individual variables in \cref{fig:sensalltile}.
-
 \section{Discussion}
@@
 
-% initial conditions evaluated 
-<<inits, eval = T, cache = F>>=
-data(ini_eval)
-
-inits <- lapply(ini_eval, function(x) unlist(x[[1]])) %>% 
-  do.call('rbind', .) %>% 
-  t %>% 
-  data.frame(vars = row.names(.), .) %>% 
-  mutate(
-    Default = sapply(def, scinot),
-    April = sapply(apr, scinot), 
-    September = sapply(sep, scinot)
-  ) %>% 
-  select(-def, -apr, -sep) %>% 
-  mutate(
-    vars = factor(vars, 
-      labels = c('Ammonium', 'Dissolved Inorganic Carbon', 'Dissolved Oygen','Nitrate', 'Phosphate', 'Silica'),
-      levels = c('NH4', 'DIC', 'O2', 'NO3', 'PO4', 'Si')
-    ), 
-    vars = as.character(vars)
-  )
-
-cap_val <- 'Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
-April and September values are based on seasonal averages from water quality samples of the \\ac{lcs}.
-All units are $\\mu$mol L$^{-1}$.'
-
-latex( 
-  inits[, -1],
-  file = '',
-  rowlabel = 'Variables',
-  caption = cap_val,
-  caption.loc = 'top',
-  label = 'tab:inits',
-  rowname = inits[, 1]
-  )  
-@
-
-% structural conditions
-<<strcs, eval = T, cache = F>>=
-swtch <- data.frame(
-  lab = c('Temperature', 'Uptake', 'Quota', 'Chla:C', 'Photosynthesis', 'Specific growth rate'),
-  sim = c('sigmoidal {\\scriptsize \\citep{Eldridge10}}', 'Michaelis-Menten {\\scriptsize \\citep{Dugdale67}}', 'Droop {\\scriptsize \\citep{Droop73}}', 'regression {\\scriptsize \\citep{Murrell14}}', 'photoinhibition {\\scriptsize \\citep{Platt80}}', "Leibig's minimum"),
-  com = c('Arrenhius {\\scriptsize \\citep{Geider97}}', 'Geider {\\scriptsize \\citep{Lehman75,Geider98}}', 'Flynn {\\scriptsize \\citep{Flynn03}}', 'Cloern {\\scriptsize \\citep{Cloern95}}', 'nutrient dependent', 'nutrient dependent'),
-  stringsAsFactors = F
-  ) %>% 
-  rename(
-    `Switch type` = lab, 
-    Default = sim, 
-    Complex = com
-  )
-
-cap_val <- 'Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.
-Complete details and equations are provided as supplementary material to \\citetalias{LehrterIP}.'
-
-latex( 
-  swtch[, -1],
-  file = '',
-  rowlabel = 'Switch type',
-  caption = cap_val,
-  caption.loc = 'top',
-  label = 'tab:strcs',
-  rowname = swtch[, 1]
-  )
-
-@
-
 % do sensitivity all categories
@@
   arrange(Category, Rank)
+totab <- totab[, c('Category', 'Parameter', 'Rank', rev(stts_lab))]
 
@@
 
-% change in sensitivity for different initial, structural conditions
-<<inistrchg, eval = T, cache = F>>=
-# initial conditions
-data(ini_eval)
-data(struct_eval)
-
-to_eval <- lapply(ini_eval, function(x) x[[2]]) %>% 
-  c(., struct = list(struct_eval))
-
-eval_levs <- c('def', 'apr', 'sep', 'struct')
-eval_labs <- c('Default', 'Initial: April', 'Initial: September', 'Structure: complex')
-
-totab_all <- sapply(1:length(to_eval), function(x) {
-
-  tmp <- reshape2::melt(to_eval[[x]], id.var = c('Parameter', 'error', 'Category'))
-  nms <- names(to_eval)[x]
-
-  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
-  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'POM', 'DOM', 'Phosphate'))
-
-  toplo <- mutate(tmp,
-      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
-      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
-      nms = nms
-    ) %>% 
-    rename(Sensitivity = error)
-
-  return(toplo)
-
-  }, simplify = F)
-totab_all <- do.call('rbind', totab_all)
-totab_all <- mutate(totab_all, nms = factor(nms, levels = eval_levs, labels = eval_labs))
-
-# summarize
-totab_all <- spread(totab_all, nms, Sensitivity) %>% 
-  group_by(Category, L1) %>% 
-  summarise(
-    mean_def = mean(Default, na.rm = TRUE),
-    iniapr_dif = mean(`Initial: April`, na.rm = TRUE) - mean_def,
-    iniapr_sgn = sign(iniapr_dif),
-    iniapr_dif = sapply(iniapr_dif, scinot),
-    iniapr_dif = ifelse(iniapr_sgn == -1, iniapr_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', iniapr_dif))),
-    inisep_dif = mean(`Initial: September`, na.rm = TRUE) - mean_def,
-    inisep_sgn = sign(inisep_dif),
-    inisep_dif = sapply(inisep_dif, scinot),
-    inisep_dif = ifelse(inisep_sgn == -1, inisep_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', inisep_dif))),
-    strcom_dif = mean(`Structure: complex`, na.rm = TRUE) - mean_def,
-    strcom_sgn = sign(strcom_dif),
-    strcom_dif = sapply(strcom_dif, scinot),
-    strcom_dif = ifelse(strcom_sgn == -1, strcom_dif, gsub('\\$$', '}$', gsub('^\\$', '$\\\\bm{', strcom_dif))),
-    mean_def = sapply(mean_def, scinot)
-  ) %>% 
-  select(-iniapr_sgn, -inisep_sgn, -strcom_sgn)
-
-# final table formatting
-cats <- as.character(totab_all$Category)
-stts<- totab_all$L1
-cap_val<- 'Changes in mean sensitivity of state variables by parameter categories to different initial conditions and structural components of the model.
-Changes show the difference in average sensitivity from results using the default model setup.
-Sensitivities are based on average $L1$ (see \\cref{l1}) values of the state variables to changes in parameters in each parameter category.
-Increases in average sensitivity are in bold.
-Medians and ranges of sensitivity values for the different conditions are shown in \\cref{fig:inistrsumm}.'
-colnms <- c('Default sensitivity', 'Initial: April', 'Initial: September', 'Structure: complex')
-
-latex( 
-  totab_all[, -c(1, 2)],
-  file = '',
-  rowlabel = 'State variables by parameter category',
-  caption = cap_val,
-  caption.loc = 'top',
-  size = 'scriptsize',
-  label = 'tab:inistrchg',
-  rowname = stts,
-  rgroup = unique(cats),
-  n.rgroup = as.numeric(table(cats)),
-  colheads = colnms,
-  cgroup = c('', 'Change'),
-  n.cgroup = c(1, 3)
-  )
-
-@
-
 \clearpage
@@
 % effects of changing initial and structural conditions
-<<sensalltile, fig.cap = 'Sensitivity values (L1, \\cref{l1}) of all state variables to changes in parameter values using default conditions, changes in initial conditions (April, September seasonal means, \\cref{tab:inits}), and changes in structural complexity (\\cref{tab:strcs}).
+<<sensalltile, fig.cap = 'Sensitivity values (L1, \\cref{l1}) of all state variables to changes in a 50\\% increase in parameter values.
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
-See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 7, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
+See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 6, fig.width = 4, out.width = '0.7\\textwidth', eval = T, echo = F, warning = F, message = F>>=
 # initial conditions
@@
 
+# get only the default results
+toplo_all <- filter(toplo_all, nms %in% 'Default')
+
 pbase <- theme(
@@
   axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8), 
-  axis.text.y = element_text(size = 6),
+  axis.text.y = element_text(size = 8),
   legend.position = 'top', 
@@
   scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
-  facet_grid(Category~nms, scales = 'free_y', space = 'free') + 
+  facet_grid(Category~., scales = 'free_y', space = 'free') + 
   guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
@@
 
-% summary of initial/structural changes on parameter sensitivity
-<<inistrsumm, eval = T, fig.cap = 'Summaries of changes in parameter sensitivity values (L1, \\cref{l1}) from the default model conditions.
-Sensitivity was re-evaluated using initial conditions as seasonal means for April and September, and added structural complexity.
-Sensitivity is summarized as the minimum, median, and maximum for each state variable separated by parameter categories.
-Changes in average sensitivity from the default model conditions are in \\cref{tab:inistrchg}.', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
-
-# initial conditions
-data(ini_eval)
-data(struct_eval)
-
-to_eval <- lapply(ini_eval, function(x) x[[2]]) %>% 
-  c(., struct = list(struct_eval))
-
-eval_levs <- c('def', 'apr', 'sep', 'struct')
-eval_labs <- c('Default', 'Initial: April', 'Initial: September', 'Structure: complex')
-
-toplo_all <- sapply(1:length(to_eval), function(x) {
-
-  tmp <- reshape2::melt(to_eval[[x]], id.var = c('Parameter', 'error', 'Category'))
-  nms <- names(to_eval)[x]
-
-  stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
-  stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'POM', 'DOM', 'Phosphate'))
-
-  toplo <- mutate(tmp,
-      L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab)),
-      Parameter = as.character(par_txt(Parameter, frm = 'exp')), 
-      nms = nms
-    ) %>% 
-    rename(Sensitivity = error)
-
-  return(toplo)
-
-  }, simplify = F)
-toplo_all <- do.call('rbind', toplo_all)
-toplo_all <- mutate(toplo_all, nms = factor(nms, levels = eval_levs, labels = eval_labs))
-
-# summarize
-toplo_all <- group_by(toplo_all, Category, L1, nms) %>% 
-  summarise(
-    med_val = median(Sensitivity, na.rm = TRUE),
-    ave_val = mean(Sensitivity, na.rm = TRUE), 
-    min_val = quantile(Sensitivity, 0, na.rm = TRUE), 
-    max_val = quantile(Sensitivity, 1, na.rm = TRUE)
-  )
-
-pbase <- theme_minimal() + 
-  theme(
-    legend.position = 'top',
-    axis.text.x = element_text(size = 8), 
-    axis.line.x = element_line(),
-    axis.line.y = element_line(), 
-    # panel.grid.minor =   element_blank(), 
-    # panel.grid.major = element_blank(),
-    axis.ticks.x = element_line(),
-    axis.ticks.y = element_line(),
-    axis.ticks.length = unit(.1, "cm")
-    )
-
-mycols <- RColorBrewer::brewer.pal(5, 'Spectral')
-names(mycols) <- cats
-fils<- scale_fill_manual(name = 'Category', values = mycols)
-cols <- scale_colour_manual(name = 'Category', values = mycols)
-
-ddge_wd <- 0.7
-ggplot(toplo_all, aes(x = L1)) + 
-  geom_errorbar(aes(ymin = min_val, ymax = max_val, group = Category), colour = 'black', width = 0, position = position_dodge(width = ddge_wd)) +
-  geom_point(aes(y = med_val, fill = Category), colour = 'black', pch = 21, position = position_dodge(width = ddge_wd), size = 3) + 
-  scale_y_continuous('Sensitivity', trans = 'log10') + 
-  scale_x_discrete('State variable') + 
-  facet_wrap( ~ nms, ncol = 1) +
-  cols +
-  fils + 
-  pbase
-@
-
 \clearpage

### 2017-03-07 ident_manu.tex
fixed column orders in table 2

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Wed Dec 21 10:59:02 2016 -0600, \href{https://github.com/fawda123/identifiability/commit/d3eb2370a7cc79abbb571fc9216ed07baa4c881b}{d3eb2370a7cc79abbb571fc9216ed07baa4c881b}}
+\tnotetext[mytitlenote]{Version: Mon Mar 6 11:12:53 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/4a06dbf55054203e59978de8be41053a6c7b9ba1}{4a06dbf55054203e59978de8be41053a6c7b9ba1}}
 
@@
 This infomation is useful if additional parameter selection rules are developed independently of those proposed herein.
-
-\subsection{Observational and structural uncertainty}
-
-Both the relative $L1$ estimates and number of parameters that affected state variables were sensitive to variation in the initial conditions (observation effects) and structural changes in the model.
-Visual comparison of sensitivity values ($L1$) for the default model setup showed that all state variables were sensitive to \textit{vmaxSi} after changing the initial conditions to April or September conditions (\cref{fig:sensalltile}).
-State variables were also sensitive to \textit{Ksi} for only the September conditions.
-Changing the model structure from the default (simple) to the complex setup showed state variables were also sensitive to \textit{KQn} and \textit{Tref(nospA+nospZ)$_{z1}$}.
-Changes in the sensitivity of individual parameters were also observed, most notably as a disproportionate increase in $L1$ for ammonium, \ac{chla}, \ac{pom}, and \ac{dom} to \textit{mA} and \textit{Tref(nospA+nospZ)$_{p1}$} using the complex model setup.
-Summaries by parameter categories of the effects of initial conditions and structural changes are shown in \cref{tab:inistrchg,fig:inistrsumm}.
-Changes in average sensitivity using April and September initial conditions showed most variables were less sensitive to parameters in the optics, temperature, and zooplankton categories, whereas increased sensitivity was generally observed for parameters in the organic matter and phytoplankton categories.
-Some exceptions were observed, such as a decrease in nitrogen sensitivity to phytoplankton parameters (\cref{tab:inistrchg}).
-Effects of structural complexity were most apparent as an increase in sensitivity of state variables to phytoplankton and temperature parameters, as noted for the individual variables in \cref{fig:sensalltile}.
 
@@
 \invisiblesection{Tables}
-
-% initial conditions evaluated 
-%latex.default(inits[, -1], file = "", rowlabel = "Variables",     caption = cap_val, caption.loc = "top", label = "tab:inits",     rowname = inits[, 1])%
-\begin{table}[!tbp]
-\caption{Initial conditions that were varied to evaluate effects of observational uncertainty on parameter sensitivity.
-April and September values are based on seasonal averages from water quality samples of the \ac{lcs}.
-All units are $\mu$mol L$^{-1}$.\label{tab:inits}}
-\begin{center}
-\begin{tabular}{llll}
-\hline\hline
-\multicolumn{1}{l}{Variables}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{April}&\multicolumn{1}{c}{September}\tabularnewline
-\hline
-Dissolved Inorganic Carbon&$2.13\times 10^{3}$&$2.1\times 10^{3}$&$2.13\times 10^{3}$\tabularnewline
-Ammonium&$1.09$&$1.79$&$0.35$\tabularnewline
-Nitrate&$71.4$&$3.75$&$2.04$\tabularnewline
-Dissolved Oygen&$172$&$194.47$&$152.57$\tabularnewline
-Phosphate&$1.81$&$0.23$&$0.42$\tabularnewline
-Silica&$71.4$&$5.84$&$9.77$\tabularnewline
-\hline
-\end{tabular}\end{center}
-\end{table}
-
-% structural conditions
-%latex.default(swtch[, -1], file = "", rowlabel = "Switch type",     caption = cap_val, caption.loc = "top", label = "tab:strcs",     rowname = swtch[, 1])%
-\begin{table}[!tbp]
-\caption{Model switches that were used to evaluate effects of structural uncertainty on parameter sensitivity.
-Complete details and equations are provided as supplementary material to \citetalias{LehrterIP}.\label{tab:strcs}}
-\begin{center}
-\begin{tabular}{lll}
-\hline\hline
-\multicolumn{1}{l}{Switch type}&\multicolumn{1}{c}{Default}&\multicolumn{1}{c}{Complex}\tabularnewline
-\hline
-Temperature&sigmoidal {\scriptsize \citep{Eldridge10}}&Arrenhius {\scriptsize \citep{Geider97}}\tabularnewline
-Uptake&Michaelis-Menten {\scriptsize \citep{Dugdale67}}&Geider {\scriptsize \citep{Lehman75,Geider98}}\tabularnewline
-Quota&Droop {\scriptsize \citep{Droop73}}&Flynn {\scriptsize \citep{Flynn03}}\tabularnewline
-Chla:C&regression {\scriptsize \citep{Murrell14}}&Cloern {\scriptsize \citep{Cloern95}}\tabularnewline
-Photosynthesis&photoinhibition {\scriptsize \citep{Platt80}}&nutrient dependent\tabularnewline
-Specific growth rate&Leibig's minimum&nutrient dependent\tabularnewline
-\hline
-\end{tabular}\end{center}
-\end{table}
 
@@
 ~~\scriptsize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
-~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$7.87$&$5.36$&-&-&$7.78$\tabularnewline
-~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&$4.73$&-\tabularnewline
-~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&$10.04$&-\tabularnewline
-~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$7.87$&$6.02$&-&-&$7.91$\tabularnewline
+~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$5.36$&-&$7.78$&$7.87$&-\tabularnewline
+~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.73$\tabularnewline
+~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&-&$10.04$\tabularnewline
+~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$6.02$&-&$7.91$&$7.87$&-\tabularnewline
 \hline
 {\bfseries Organic Matter}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&-&$1$&$1$\tabularnewline
-~~\scriptsize{\textit{KG2}}&$1$&-&-&-&$1$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&-&$1$&-&-&-\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&-&$1$&-&-\tabularnewline
+~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
+~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
 ~~\scriptsize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&-&$1.93$&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&$13.43$&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&$1.39$&-&-&-&$1.47$\tabularnewline
+~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
 ~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KG2}}&$3$&-&-&-&-&$8.19$&-&-&-\tabularnewline
-~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&$13.75$&-\tabularnewline
-~~\scriptsize{\textit{KO2}}&$3$&-&-&-&$11.96$&-&-&-&$14.07$\tabularnewline
+~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
+~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
 ~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&$14.68$&-\tabularnewline
-~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&-&$10.65$&-&-&$14.08$\tabularnewline
+~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
+~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
 ~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline
@@
 {\bfseries Phytoplankton}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&$1$&-&-&-&$1$\tabularnewline
-~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&-&$1$&$1$&$1$&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&-&-&$1.15$\tabularnewline
-~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&-&$1.29$&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&-&$11.57$&-&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$2$&-&-&-&$1.21$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&$7.45$&-\tabularnewline
-~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&-&$1.98$&-&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&$2.9$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&-&-&$3.26$\tabularnewline
+~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
+~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$2$&-&-&-&-&-&-&$1.21$&-\tabularnewline
+~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$7.45$\tabularnewline
+~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
+~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
 ~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&-&$4.09$&-&-&-\tabularnewline
-~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&-&-&$4.98$\tabularnewline
-~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&$4.9$&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&-&-&$10.11$\tabularnewline
+~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
+~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
+~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
 ~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
@@
 {\bfseries Zooplankton}&&&&&&&&&\tabularnewline
-~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&-&$1$&$1$&$1$&-\tabularnewline
-~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&$1$&-&-&-&$1$\tabularnewline
-~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&$5.43$&-&-&-&$7.3$\tabularnewline
-~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&-&$6.32$&$9.76$&$8.54$&-\tabularnewline
+~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
+~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&-&-&$7.3$&$5.43$&-\tabularnewline
+~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
 ~~\scriptsize{\textit{Zm}}&$3$&-&-&$4.57$&-&-&-&-&-\tabularnewline
-~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&-&$6.93$&-&-&-\tabularnewline
-~~\scriptsize{\textit{Zm}}&$4$&-&-&-&-&$11.86$&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&$6.93$&-&-&-&-\tabularnewline
+~~\scriptsize{\textit{Zm}}&$4$&-&-&-&$11.86$&-&-&-&-\tabularnewline
 ~~\scriptsize{\textit{Zumax}}&$4$&-&-&$5.2$&-&-&-&-&-\tabularnewline
@@
 
-% change in sensitivity for different initial, structural conditions
-%latex.default(totab_all[, -c(1, 2)], file = "", rowlabel = "State variables by parameter category",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:inistrchg", rowname = stts, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, cgroup = c("",         "Change"), n.cgroup = c(1, 3))%
-\begin{table}[!tbp]
-{\scriptsize
-\caption{Changes in mean sensitivity of state variables by parameter categories to different initial conditions and structural components of the model.
-Changes show the difference in average sensitivity from results using the default model setup.
-Sensitivities are based on average $L1$ (see \cref{l1}) values of the state variables to changes in parameters in each parameter category.
-Increases in average sensitivity are in bold.
-Medians and ranges of sensitivity values for the different conditions are shown in \cref{fig:inistrsumm}.\label{tab:inistrchg}}
-\begin{center}
-\begin{tabular}{llclll}
-\hline\hline
-\multicolumn{1}{l}{\bfseries State variables by parameter category}&\multicolumn{1}{c}{\bfseries }&\multicolumn{1}{c}{\bfseries }&\multicolumn{3}{c}{\bfseries Change}\tabularnewline
-\cline{4-6}
-\multicolumn{1}{l}{}&\multicolumn{1}{c}{Default sensitivity}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Initial: April}&\multicolumn{1}{c}{Initial: September}&\multicolumn{1}{c}{Structure: complex}\tabularnewline
-\hline
-{\bfseries Optics}&&&&&\tabularnewline
-~~Ammonium&$0.01$&&$-9.13\times 10^{-3}$&$-8.37\times 10^{-3}$&$-7.7\times 10^{-3}$\tabularnewline
-~~Chlorophyll&$8.77\times 10^{-3}$&&$-6.79\times 10^{-3}$&$-6.3\times 10^{-3}$&$-7.33\times 10^{-3}$\tabularnewline
-~~Dissolved Oxygen&$2.81\times 10^{-4}$&&$-2.11\times 10^{-4}$&$-1.46\times 10^{-4}$&$-1.93\times 10^{-4}$\tabularnewline
-~~Irradiance&$9.1\times 10^{-3}$&&$\bm{2.56\times 10^{-3}}$&$\bm{3.1\times 10^{-3}}$&$\bm{1.57\times 10^{-3}}$\tabularnewline
-~~Nitrate&$7.72\times 10^{-3}$&&$-6.46\times 10^{-3}$&$-6.2\times 10^{-3}$&$-6.8\times 10^{-3}$\tabularnewline
-~~POM&$0.01$&&$-9.06\times 10^{-3}$&$-8.49\times 10^{-3}$&$-8.56\times 10^{-3}$\tabularnewline
-~~DOM&$0.02$&&$-0.01$&$-0.01$&$-0.01$\tabularnewline
-~~Phosphate&$3.35\times 10^{-3}$&&$-2.53\times 10^{-3}$&$-2.15\times 10^{-3}$&$-3.04\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&&&&\tabularnewline
-~~Ammonium&$0.31$&&$\bm{0.08}$&$\bm{0.04}$&$-2.22\times 10^{-4}$\tabularnewline
-~~Chlorophyll&$0.02$&&$\bm{0.12}$&$\bm{0.14}$&$-0.01$\tabularnewline
-~~Dissolved Oxygen&$2.17\times 10^{-3}$&&$-6.75\times 10^{-4}$&$\bm{2.32\times 10^{-4}}$&$-1.05\times 10^{-3}$\tabularnewline
-~~Irradiance&$6.63\times 10^{-3}$&&$\bm{5.34\times 10^{-3}}$&$\bm{6.79\times 10^{-3}}$&$-2.99\times 10^{-4}$\tabularnewline
-~~Nitrate&$0.12$&&$\bm{0.06}$&$\bm{0.09}$&$-0.1$\tabularnewline
-~~POM&$0.13$&&$\bm{0.15}$&$\bm{0.12}$&$\bm{0.04}$\tabularnewline
-~~DOM&$0.14$&&$\bm{0.07}$&$\bm{0.17}$&$\bm{0.05}$\tabularnewline
-~~Phosphate&$0.03$&&$\bm{0.04}$&$\bm{0.06}$&$-0.02$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&&&&\tabularnewline
-~~Ammonium&$0.8$&&$-0.02$&$\bm{0.3}$&$\bm{65.98}$\tabularnewline
-~~Chlorophyll&$1.14$&&$\bm{1.23}$&$\bm{4.38}$&$\bm{104.24}$\tabularnewline
-~~Dissolved Oxygen&$0.01$&&$-4.58\times 10^{-4}$&$\bm{2.31\times 10^{-3}}$&$\bm{3.44\times 10^{-4}}$\tabularnewline
-~~Irradiance&$0.02$&&$-2.04\times 10^{-3}$&$\bm{1.83\times 10^{-3}}$&$\bm{7.53\times 10^{-3}}$\tabularnewline
-~~Nitrate&$0.74$&&$-0.43$&$-0.45$&$-0.64$\tabularnewline
-~~POM&$0.76$&&$\bm{0.17}$&$\bm{0.46}$&$\bm{55.11}$\tabularnewline
-~~DOM&$1.28$&&$\bm{0.34}$&$\bm{1.15}$&$\bm{128.93}$\tabularnewline
-~~Phosphate&$0.17$&&$\bm{0.03}$&$\bm{0.05}$&$-0.14$\tabularnewline
-\hline
-{\bfseries Temperature}&&&&&\tabularnewline
-~~Ammonium&$0.79$&&$-0.69$&$-0.69$&$\bm{272.31}$\tabularnewline
-~~Chlorophyll&$0.6$&&$-0.47$&$-0.45$&$\bm{114.51}$\tabularnewline
-~~Dissolved Oxygen&$0.02$&&$-0.02$&$-0.02$&$-0.01$\tabularnewline
-~~Irradiance&$0.03$&&$-0.02$&$-0.02$&$\bm{0.01}$\tabularnewline
-~~Nitrate&$0.3$&&$-0.15$&$-0.16$&$-0.19$\tabularnewline
-~~POM&$0.86$&&$-0.68$&$-0.69$&$\bm{215.17}$\tabularnewline
-~~DOM&$1.48$&&$-1.21$&$-1.2$&$\bm{900.26}$\tabularnewline
-~~Phosphate&$0.16$&&$-0.11$&$-0.09$&$-0.11$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&&&&\tabularnewline
-~~Ammonium&$0.47$&&$-0.45$&$-0.44$&$-0.16$\tabularnewline
-~~Chlorophyll&$0.39$&&$-0.26$&$-0.23$&$-0.2$\tabularnewline
-~~Dissolved Oxygen&$0.01$&&$-0.01$&$-8.68\times 10^{-3}$&$-6.96\times 10^{-3}$\tabularnewline
-~~Irradiance&$0.03$&&$-0.02$&$-0.02$&$-0.01$\tabularnewline
-~~Nitrate&$1.06$&&$-1.02$&$-1.02$&$-0.98$\tabularnewline
-~~POM&$0.37$&&$-0.27$&$-0.28$&$-0.18$\tabularnewline
-~~DOM&$0.39$&&$-0.3$&$-0.28$&$-0.18$\tabularnewline
-~~Phosphate&$0.31$&&$-0.19$&$-0.17$&$-0.27$\tabularnewline
-\hline
-\end{tabular}\end{center}}
-\end{table}
-
 \clearpage
@@
 
-\caption{Sensitivity values (L1, \cref{l1}) of all state variables to changes in parameter values using default conditions, changes in initial conditions (April, September seasonal means, \cref{tab:inits}), and changes in structural complexity (\cref{tab:strcs}).
+\caption{Sensitivity values (L1, \cref{l1}) of all state variables to changes in a 50\% increase in parameter values.
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
@@
 Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
-\end{figure}
-
-% summary of initial/structural changes on parameter sensitivity
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/inistrsumm-1}
-
-}
-
-\caption{Summaries of changes in parameter sensitivity values (L1, \cref{l1}) from the default model conditions.
-Sensitivity was re-evaluated using initial conditions as seasonal means for April and September, and added structural complexity.
-Sensitivity is summarized as the minimum, median, and maximum for each state variable separated by parameter categories.
-Changes in average sensitivity from the default model conditions are in \cref{tab:inistrchg}.}\label{fig:inistrsumm}
 \end{figure}

### 2017-03-08 ident_manu.Rnw
fixed theme issues in figures

@@
   facet_grid(Category~., scales = 'free_y', space = 'free') + 
-  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))
+  guides(fill = guide_colourbar(barheight = 0.25, barwidth = 5, label.theme = element_text(size = 6, angle = 0)))
 
@@
 lncol <- 'darkgrey'
-sz <- 2
+sz <- 3
 
@@
   facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
-  mytheme +
+  mytheme %+replace%
   theme(legend.position = 'none') + 
@@
   facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +
-  mytheme + 
+  mytheme %+replace%
   theme(legend.title = element_blank()) + 
@@
 pleg <- g_legend(p2)
-p2 <- p2 + theme(legend.position = 'none')
+p2 <- p2 + 
+  mytheme %+replace%
+  theme(legend.position = 'none')
 
@@
   facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
-  mytheme +
+  mytheme %+replace%
+  theme(legend.position = 'none') + 
   scale_y_continuous(trans = 'log10') + 
-  theme(legend.position = 'none') + 
   ggtitle('(a) By parameter category')
@@
 pleg <- g_legend(p2)
-p2 <- p2 + theme(legend.position = 'none')
+p2 <- p2 +
+  mytheme %+replace%
+  theme(legend.position = 'none')
 
@@
   cols +
-  pthm +
+  pthm %+replace%
   theme(legend.position = 'top')

### 2017-03-08 ident_manu.tex
fixed theme issues in figures

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Mon Mar 6 11:12:53 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/4a06dbf55054203e59978de8be41053a6c7b9ba1}{4a06dbf55054203e59978de8be41053a6c7b9ba1}}
+\tnotetext[mytitlenote]{Version: Tue Mar 7 16:55:36 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/8f38d5a2d17442eb0f3f3d4db61d379b841c8830}{8f38d5a2d17442eb0f3f3d4db61d379b841c8830}}
 

### 2017-03-09 ident_manu.Rnw
much shortening

@@
 \begin{abstract}
-\noindent The optimization of parameters and transferability to different systems are fundamental concerns in the application of biogeochemical models.
-This study provides a context for understanding quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.
-The analysis provides a contrast of numeric and ecological certainty in parameter subsets using a systematic framework to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
+\noindent This study addresses quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.
+A systematic framework is used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
 In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
-The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates.
+The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates and less sensitive to physical or chemical parameters.
 Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set were characterized as having unique effects on the model output.
@@
 Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in evaluations of water quality models.
-In addition to immediate implications for regional models, we provide a framework for describing the effects of parameter uncertainty and identifiability that can be applied to similar models to better inform environmental management.
 \end{abstract}
@@
 This area drains a significant portion of the continental United States through the \ac{marb} and is the second largest hypoxic area in the world \citep{Rabalais02}.
-Understanding processes that contribute to the frequency and duration of hypoxic events remains a critical research goal for the region, including the application of process-based models to characterize the current knowledge domain.
+Understanding processes that contribute to the frequency and duration of hypoxic events remains a critical research goal for the region.
 
@@
 Process-based models are more commonly imbalanced between reality and theory, such that most are over-parameterized in an attempt to completely describe reality \citep{Denman03,Nossent12,Petrucci14}.
-Such over-parameterization, including use of many  structural equations, can have serious implications for practical applications.
 Quantitative limitations of over-parameterization are analagous to degrees of freedom in standard statistical models as free parameters cannot be numerically estimated when constrained to an observed dataset \citep{Kirchner06}.
 More importantly, over-parameterization can limit use across systems outside of the data domain and impose uncertainty in model predictions as realistic values for every variable may not be known or inaccurately applied from existing studies \citep{Durand02,Refsgaard07,Wade08}.
-The application of process-based models to describe hypoxia dynamics has not been immune to these challenges and comprehensive approaches are needed to develop models that more carefully balance theory with reality \citep[e.g.,][]{Snowling01}.
-
-Standard approaches for uncertainty analysis can be used to begin addressing model complexity issues.
-In the most general sense, uncertainty is evaluated relative to the effects of input conditions or the observed data used to calibrate a model, changes in parameter values, or variation in the structural components (i.e., observational, parameter, or structural uncertainty) \citep{Beck87}.
-Evaluating parameter uncertainty is by far the most common and simplest means of evaluating model behavior.
-Although uncertainty analyses should be integrated throughout model development and application, parameters are more often evaluated post-hoc as a form of `damage control' for further calibration.
+
+Model precision can be evaluated relative to the effects of initial conditions or the observed data used for calibration, changes in parameter values, or variation in the structural components (i.e., observational, parameter, or structural uncertainty) \citep{Beck87}.
+Evaluating effects of parameter changes is by far the most common and simplest approach.
+Although sensitivity analyses should be integrated with model development, parameters are often evaluated post-hoc as a form of `damage control' for further calibration.
 This approach is sometimes called inverse modelling where results from sensitivity analyses are used to guide calibration or fit of the developed model to observations (\citealt{Soetaert10}, or confronting models with data, \textit{sensu} \citealt{Hilborn97}).
-Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability', where only a subset of identifiable parameters can be numerically constrained to the data as compared to the entire set.
-Redundancies in parameter effects lead to unidentifiable models where optimal solutions may be empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
-An unidentifiable parameter or parameter set has effects on model output that can be undone or compensated for by alteration of other parameters.
-The concept of identifiable parameter subsets is not foreign to hypoxia or eutrophication models  \citep{Omlin01,Estrada10,Mateus15}, although there is a clear need for greater integration of these concepts in model development \citep{Fasham06}.
-Moreover, the inclusion of sensitivity and identifiability analyses in model tuning will require the adoption of conservative selection rules for parameters to calibrate given the number of unique combinations of parameter subsets for most models \citep[e.g.,][]{Wagener01, Wagener01b}.
-
-This study describes a parameter sensitivity analysis to evaluate identifiability of parameter subsets for a bio-geo-chemical model of hypoxia for the northern \ac{gom}.
-We evaluate a simple \ac{zerod} unit of a larger spatial-temporal model to explore relationships between multiple parameter sets and hypoxia dynamics on the \ac{lcs}.
-Specifically, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the larger parameter set can be optimized for a given research question or dataset.
-We provide explicit guidance for choosing such subsets of the parameter space given constraints on identifiability as directly related to sensitivity analyses.
-The objectives are to \begin{inparaenum}[1\upshape)]
-\item identify the parameters that have the greatest influence on \ac{do} using local sensitivity analysis,
+Parameter sensitivity analysis combined with inverse modelling necessarily involves questions of parameter `identifiability'.
+Redundancies in parameter effects lead to unidentifiable models where calibration is empirically impossible (i.e., standard algorithms will not converge) or parameter values may be non-unique leading to the right answer for the wrong reason \citep{Kirchner06}.
+Unidentifiable parameter sets have effects on model output that can be undone or compensated for by alteration of other parameters.
+Identifiability issues are not foreign to hypoxia or eutrophication models  \citep{Omlin01,Estrada10,Mateus15}, although there is a clear need for greater integration of these concepts in practice \citep{Fasham06}.
+
+This study describes a parameter sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.
+The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifability constraints.
+The specific goals were to \begin{inparaenum}[1\upshape)]
+\item identify the parameters that have the greatest influence on state variables using local sensitivity analysis,
 \item quantify the identifiability of subsets of the total parameter space based on sensitivity,
@@
 \end{inparaenum}
-These principles were also applied to other state variables predicted by the model (ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus).
-A final analysis evaluated identifiability relative to structural uncertainty to provide an example of extending these methods to more complex uncertainty assessments.
-Throughout, the optimum parameter set is defined as the chosen subset that represents the maximum number of identifiable parameters.
-`Optimum' is both a qualitative description based on a research question or management goal and a quantitative objective based on numerical optimization criteria for fitting model output to a calibration dataset.
-These results can be used to refine existing models or guide application of models to novel contexts, such as downscaling or application to new environments.
-We conclude with a discussion of the implications for hypoxia formation in coastal regions, including management strategies for nutrient reduction and use of mechanistic models to inform decision-making.
+In addition to \ac{do}, other state variables that were evaluated included ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.
+In general, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the complete parameter set can be optimized.
+Although concerns of identifiability constraints have been shown in the literature, rulesets are not readily available that define how parameters should be selected given tradeoffs betwen precision, sensitivity, and identifiability, especially for biogeochemical models of ecosystem processes.
 
@@
 Hypoxic events, defined  as $<$2 mg L$^{-1}$ of \ac{do} ($<$ 64 mmol m$^{-3}$), occur seasonally in bottom waters in the northern \ac{gom}.
-The \ac{lcs} receives high nutrient loads from the \ac{marb} that drains a significant portion of the continental United States.
-Nutrient-stimulated primary production in surface waters increases biological oxygen demand in bottom waters as sinking organic matter is decomposed \citep{Bierman94,Murrell13}.
 The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.
 Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97,Paerl98,Obenour15}.
-
-This study evaluated the core unit of a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.
-The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
-The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).
+The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
+The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf.
 The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.
-Atmospheric and hydrologic boundary conditions described in \citet{Hodur97} and \citet{Lehrter13} are also included in \ac{cgem}.
 
@@
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
-Accordingly, the sensitivity and identifiability analyses described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.
-The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.
-A set of initial conditions is provided on execution of the model that is based on observations of relevant variables obtained from research cruises in the northern \ac{gom} during April, June, and September of 2006 \citep[Table 1 in][]{Murrell14}.
-
-Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIP}).
-A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.
+Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIP}).
+A total of 108 equations are estimated at each time step to return values for each of the 36 state variables described by the model.
 In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution.
-These parameters define relationships among fixed effects in the equations and represent ecological properties described by the model that influence hypoxia formation.
 Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.
@@
 
-The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep of FishTank simulations from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
+The sensitivity of state variables to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
 Irrelevant parameters were removed for several reasons; parameters were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
-Additionally, FishTank includes six phytoplankton and two zooplankton groups to describe complexity in community structure and foodweb dynamics.
-However, structural equations for each group are identical such that chosen parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
-Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
-To remove obvious redundancies in the model, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
-The final parameter set that was evaluated included \Sexpr{length(p1z1pars)} parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
+Additionally, FishTank includes six phytoplankton and two zooplankton groups to add complexity in community structure and foodweb dynamics.
+To remove obvious redundancies, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
+The final set that was evaluated included \Sexpr{length(p1z1pars)} parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
 A full description of the model parameters is available as an appendix in \citetalias{LehrterIP}.
@@
 
-The analysis focused on sensitivity of \ac{do} and other state variables (noted below) in the \ac{zerod} FishTank model to identify parameters that may affect spatial and temporal variation of hypoxia in the larger model.
-A local sensitivity analysis was performed by evaluating the change in \ac{do} following perturbation of each parameter from its original value.
-The analyses relied exclusively on concepts used in the FME package developed for the R statistical programming language \citep{Soetaert10,RDCT16}.
-Parameters were individually perturbed by 50\% of the original values and the model was executed to obtain an estimate of \ac{do} sensitivity.
-For each perturbation, a sensitivity value $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
+A local sensitivity analysis was performed by evaluating the change in state variables following perturbation of each parameter from its original value \citep{Soetaert10,RDCT16}.
+Parameters were individually perturbed by 50\% of the original values and sensitivity $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
 
@@
 
-\noindent where the estimate depended on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
+\noindent where the estimate is based on the change in the predicted value for response variable $y$ divided by the change in the parameter $\Theta_j$ multiplied by the quotient of scaling factors $w$ for each.
 The scaling factors, $w_{\Theta_j}$ for the parameter $\Theta_j$ and $w_{y_i}$ for response variable $y_i$, were set as the default value of the unperturbed parameter and the predicted value of $y_i$ after perturbation \citep{Soetaert10}.
-The scaling ensures the estimates are unitless such that the relative magnitudes allow comparisons of model sensitivity to parameters and state variables that differ in scale.
-Sensitivity values for all $j$ parameters were summarized across the time series from $i = 1$ to $n$ as $L1$:
+Scaling makes the estimates unitless to compare model sensitivity to parameters and state variables that differ in relative magnitude.
+Sensitivity values for all $j$ parameters were summarized as a single value across the time series from $i = 1$ to $n$ as $L1$:
 
@@
 
-The $L1$ value for each parameter was used as the primary measure of sensitivity for the state variables.
-All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ (suggesting sensitivity) were retained for identifiability analysis.
+All parameters for each of the six equation categories (optics, organic matter, phytoplankton, temperature, and zooplankton) that had non-zero $L1$ were retained for identifiability analysis.
 
@@
 
-Identifiability of parameter subsets was estimated from the minimum eigenvector of the cross-product of a selected sensitivity matrix \citep{Brun01,Omlin01}:
+The collinearity index $\gamma$ provides a measure of potential redundancies in the response of a state variable to changes in parameter values.
+The index measures the linear dependence between sensitivity functions (i.e., $S_i$ for $j$ parameters) described above for parameter subsets and was estimated from the minimum eigenvector of the cross-product of a selected sensitivity matrix \citep{Brun01,Omlin01}:
 
@@
 
-\noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for parameters in a sensitivity matrix $S$.
-The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that described deviations of predicted \ac{do} from the default parameter values.
-Thus, $\gamma$ can be estimated for any subset of parameter combinations using the change in model output for perturbations of individual parameters.
+\noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) parameter sets.
+The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that described deviations of predicted \ac{do} following perturbations of each parameter.
+Thus, $\gamma$ can be estimated from results for any subset of parameter combinations.
 Sensitivity matrices were first normalized by dividing by the square root of the summed residuals \citep{Omlin01,Soetaert10}.
-
-The collinearity index $\gamma$ provides a measure of the linear dependence between sensitivity functions (i.e., $S_i$ for $j$ parameters) described above for subsets of parameters.
-Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms given similar effects of the selected parameters on the estimated state variable.
-Greater sensitivity of a state variable to a subset of parameters does not always imply better identifiability if the effects of individual parameters are similar.
-An intuitive interpretation of $\gamma$ is provided by \citet{Brun01} such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
+Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms.
+An intuitive interpretation of $\gamma$ is provided by \citet{Brun01}, such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
 That is, $\gamma = 10$ suggests the relative change in \ac{do} for an arbitrary parameter in the selected set can be compensated for by 90\% with changes in the other parameters.
 
-Initial analyses suggested that considerably limited subsets of parameters were identifiable of the \Sexpr{length(p1z1pars)} evaluated for the FishTank model.
-Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
-An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practitioners may only be interested in optics parameters).
-For example, \cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., based on $n$ choose $k$ combinations equal to $n!/\left(k!\left(n-k\right)!\right)$).
+Parameter selection for model calibration must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
+An additional challenge is a large number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practitioners may only be interested in optics parameters).
+\cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., $n$ choose $k$ combinations, $n!/\left(k!\left(n-k\right)!\right)$).
 The number of unique combinations increases with the total parameters in the set and is also maximized for moderate selections (e.g., selecting half the total).
 For example, over 10$^{14}$ combinations are possible by selecting 25 parameters from a set of 50.
-Accordingly, parameter selection is complicated by differing sensitivity, identifiability limits for parameter subsets, and the difficulty of choosing from many combinations.
-
-A set of heuristics was developed that address the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
-These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability).
+
+A set of heuristics was developed that addresses the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
+These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
 Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences by model users given questions of interest.
@@
 \end{inparaenum} The selection rules produced seven subsets of parameters that could further be used to optimize model calibration.
-
-\subsection{Extension to other state variables}
-
-The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
-In addition to \ac{do}, other state variables that were evaluated were ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.
-Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIP}).
 
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{locO2$tot} of the \Sexpr{length(p1z1pars)} (\Sexpr{round(100 * locO2$tot/length(p1z1pars), 0)}\% of total) parameters that were evaluated in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in \Sexpr{locO2$tot} of the \Sexpr{length(p1z1pars)} (\Sexpr{round(100 * locO2$tot/length(p1z1pars), 0)}\% of total) parameters that were evaluated in FishTank (\cref{fig:sensalltile}, \cref{tab:dosens}).
 Within each parameter category, \ac{do} was sensitive to \Sexpr{locO2$bycat$Optics} parameters for optics (\Sexpr{locO2$lncat$Optics} of all optic parameters), \Sexpr{locO2$bycat$`Organic Matter`} for organic matter (\Sexpr{locO2$lncat$`Organic Matter`}), \Sexpr{locO2$bycat$Phytoplankton} for phytoplankton (\Sexpr{locO2$lncat$Phytoplankton}), \Sexpr{locO2$bycat$Temperature} for temperature (\Sexpr{locO2$lncat$Temperature}), and \Sexpr{locO2$bycat$Zooplankton} for zooplankton (\Sexpr{locO2$lncat$Zooplankton}).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ \Sexpr{locO2$sensrng$error[1]} for \Sexpr{locO2$sensrng$Parameter[1]} (\Sexpr{tolower(locO2$sensrng$Category[1])}) to \Sexpr{locO2$sensrng$error[2]} for \Sexpr{locO2$sensrng$Parameter[2]} (\Sexpr{tolower(locO2$sensrng$Category[2])}), whereas average sensitivity among all parameters was $L1 = $ \Sexpr{locO2$sensave}.
+Among all parameters, average sensitivity was $L1 = $ \Sexpr{locO2$sensave} with values ranging from $L1 = $ \Sexpr{locO2$sensrng$error[1]} for \Sexpr{locO2$sensrng$Parameter[1]} (\Sexpr{tolower(locO2$sensrng$Category[1])}) to \Sexpr{locO2$sensrng$error[2]} for \Sexpr{locO2$sensrng$Parameter[2]} (\Sexpr{tolower(locO2$sensrng$Category[2])}).
 Within categories (excluding temperature with one sensitive parameter), sensitivity ranged from \Sexpr{locO2$sensrngcat$Optics$error[1]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Optics$error[2]} (\Sexpr{locO2$sensrngcat$Optics$Parameter[2]}) for optics, \Sexpr{locO2$sensrngcat$`Organic Matter`$error[1]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[1]}) to \Sexpr{locO2$sensrngcat$`Organic Matter`$error[2]} (\Sexpr{locO2$sensrngcat$`Organic Matter`$Parameter[2]}) for organic matter, \Sexpr{locO2$sensrngcat$Phytoplankton$error[1]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Phytoplankton$error[2]} (\Sexpr{locO2$sensrngcat$Phytoplankton$Parameter[2]}) for phytoplankton, and \Sexpr{locO2$sensrngcat$Zooplankton$error[1]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[1]}) to \Sexpr{locO2$sensrngcat$Zooplankton$error[2]} (\Sexpr{locO2$sensrngcat$Zooplankton$Parameter[2]}) for zooplankton (\cref{tab:dosens}).
@@
 
-\subsection{Subset identifiability}
+\subsection{Identifiability of parameter subsets and selection rules}
 
@@
 
-The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
-Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
+The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$.
 Parameter identifiability for \ac{do} decreased (increasing $\gamma$) at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
@@
 For example, inclusion of \Sexpr{om_coll[5]} in a parameter set almost always inflated $\gamma$.
-All parameter subsets that did not include \Sexpr{om_coll[5]} were well below $\gamma = 15$, suggesting that removal of this parameter improves identifiability.
+All parameter subsets that did not include \Sexpr{om_coll[5]} were well below $\gamma = 15$, suggesting that exclusion of this parameter improves identifiability.
 Interestingly, the inclusion of some parameters caused a reduction in $\gamma$, which contradicts the general rule that more parameters caused reduced identifiablity.
 For example, parameter sets that included \Sexpr{om_coll[3]} generally had lower $\gamma$ values relative to those that excluded the parameter.
-
-\subsection{Parameter selection}
 
@@
 @
-
-The above results demonstrated that state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by $\gamma$ thresholds and parameter selection criteria.
 Results for each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) applied to each state variable differed in the number of selected parameters and distribution of parameters within each category (\cref{tab:heurist1,tab:heurist2,tab:heurist3}).
@@
 The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic given equal importance between categories.
-
-\Cref{fig:heurist_stts} demonstrates parameter selection for all state variables following the second heuristic where parameters were chosen by decreasing sensitivity independent of parameter categories (exact values are shown in \cref{tab:heurist2}).
-The y-axis shows the relative identifiability with the addition of parameters from one to many on the x-axis (from left to right).
-The second to last parameter for each variable is the last parameter selected within the potential threshold of $\gamma = 15$.
-Interestingly, the last parameter shown for most of the state variables caused a relatively large increase in $\gamma$ that was disproportionate to the combined identifiability of the preceding parameter set.
-For most variables, the phytoplankton edibility vector for zooplankton (\Sexpr{par_txt('ediblevector(Z1)_1')}) caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
-In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disproportionately redundant within a given parameter set (i.e., large contribution to $\gamma$).
-This infomation is useful if additional parameter selection rules are developed independently of those proposed herein.
 
@@
 This study provided a simple approach to use the effects of parameter perturbations on model state variables to characterize identifiable parameter subsets that vary by parameter selection criteria.
-By doing so, we demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiabilty thresholds described in the literature.
+By doing so, we demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiability thresholds described in the literature.
 The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
-We further demonstrated that changes in the model structure and variation in the initial conditions had an effect on sensitivity which has direct implications for identifiability.
 In general, these results provide justification for the use of explicit parameter selection heuristics that practitioners should adopt to facilitate model calibration.
 
-Although the results were specific to individual variables, some generalities about hypoxia dynamics can be inferred from the sensitivity analyses.
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\Sexpr{par_txt('umax_1')} for phytoplankton, \Sexpr{par_txt('Zumax_1')} for zooplankton), mortality coefficient for phytoplankton (\Sexpr{par_txt('mA_1')}), and the zooplankton half saturation coefficent for grazing (\Sexpr{par_txt('ZKa_1')}).
@@
 
-The overwhelming conclusion from the identifiability analyses is that only limited subsets of parameters were identifiable within the constraints of local sensitivity analyses.
-Although we have not attempted actual model calibration (see recommendations below), these results support previous studies that have suggested similarly small subsets of parameters can be identified using traditional calibration schemes \citep[e.g.,][]{Wheater86,Ye97,Omlin01}.
+A general conclusion from the identifiability analyses is that only limited subsets of parameters were identifiable within the constraints of local sensitivity analyses.
+These results support previous studies that have suggested similarly small subsets of parameters can be identified using traditional calibration schemes \citep[e.g.,][]{Wheater86,Ye97,Omlin01}.
 In addition to \ac{cgem}, these conclusions have relevance for many biogeochemical models that include numerous parameters and structural equations to characterize processes in the model domain.
@@
 For example, \cref{fig:exclex} shows that including \Sexpr{par_txt('KGcdom_1')}, \Sexpr{par_txt('KO2_1')}, or \Sexpr{par_txt('nitmax_1')} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
-Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parameters often caused a disproportionate increase in $\gamma$ (e.g., \Sexpr{par_txt('ediblevector(Z1)_1')}).
 These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
@@
 
-An evaluation of parameter uncertainty and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
+An evaluation of sensitivity and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
 In general, uncertainty analyses that lead to improved models are ultimately expected to increase our understanding of properties defining ecological relationships.
 The extension of simple parameter sensitivity analyses to the generalization of ecosystem properties requires additional analysis and potential model refinement, at the core of which is the balance between generality and precision.
-We emphasize that the utility of a specific model depends on the question and objective for application to a specific system.
+The utility of a specific model depends on the question and objective for application to a specific system.
 For the above analysis, the FishTank model, as part of the larger \ac{cgem} application, was evaluated in the context of hypoxia effects on ecosystem condition and function.
@@
 
-Specific approaches can be used to improve and build on the results presented herein, in addition to the more general considerations noted above.
+Specific approaches can be used to improve and build on the results presented herein, in addition to the more general considerations above.
 An evaluation of model precision following calibration with relevant parameter subsets could provide additional information that supports results from the sensitivity analyses.
@@
 Variation in parameter estimates given the calibration method and different identifiability thresholds could affect the interpration of model output.
-Further, the extent to which results for the \ac{zerod} model extrapolate to the larger three-dimensional model should be evaluated.
+Further, how results for the \ac{zerod} model extrapolate to the larger three-dimensional model should be evaluated.
 Although the above analyses were facilitated using the \ac{zerod} model (i.e, quick execution times, ease of changing model parameters), lack of physical transport or spatial components potentially limits extrapolation of the results.
-Uncertainy in parameter estimates at lower dimensions could be magnified as errors propagate to larger scales or site-specific observations for model calibration are not appropriate across a hydrodynamic grid \citep{Harvey00,Lehrter10}.
+Variation in parameter estimates at lower dimensions could be magnified as errors propagate to larger scales or site-specific observations for model calibration are not appropriate across a hydrodynamic grid \citep{Harvey00,Lehrter10}.
 The effects of structural or observational uncertainty should also be evaluated in the context of the larger model.
@@
 Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive (L1, \\cref{l1}), until $\\gamma > 15$.
-Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).
-See \\cref{fig:heurist_stts} for a graphical illustration.'
+Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).'
 colnms <- c('Parameter', 'L1', 'Rank', '$\\gamma$')
@@
 
-% heuristic plots, all state
-<<heurist_stts, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for all state variables.
-Parameters are selected by decreasing sensitivity independent of parameter categories.
-Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\\gamma > 15$.', fig.height = 6, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
-data(tocal_all)
-
-# factor levels
-cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
-stts_lev <- c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4')
-stts_lab <- c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'POM', 'DOM', 'Phosphate')
-
-# custom col scale
-mycols <- RColorBrewer::brewer.pal(5, 'Spectral')
-names(mycols) <- cats
-cols <- scale_fill_manual(name = 'Category', values = mycols)
-
-# ggplot theme
-pthm <- theme_minimal() + 
-  theme(
-    axis.text.x = element_text(size = 8), 
-    axis.line.x = element_line(),
-    axis.line.y = element_line(), 
-    panel.grid.minor = element_blank(), 
-    panel.grid.major = element_blank(),
-    axis.ticks.x = element_line(),
-    axis.ticks.y = element_line(),
-    axis.ticks.length = unit(.1, "cm")
-    )
-
-# get all parameters for each state variable where coll < 15 plus one
-toplo <- lapply(tocal_all, function(x) x$top) %>% 
-  reshape2::melt(., id.var = names(.[[1]])) %>% 
-  mutate(
-    L1 = factor(L1, levels = stts_lev, labels = stts_lab),
-    Category = factor(Category, levels = cats, labels = cats)
-  ) %>% 
-  split(., .$L1) %>% 
-  lapply(function(x){
-    # browser()
-    sel <- which(x$coll < 15)
-    x <- x[c(sel, max(sel) + 1), ] %>% 
-      na.omit
-    x
-
-  }) %>% 
-  do.call('rbind', .) %>% 
-  data.frame %>% 
-  mutate(Parameter = as.character(par_txt(Parameter, frm = 'exp')))
-
-ggplot(toplo, aes(x = Selected, y = coll)) + 
-  geom_line() + 
-  geom_text_repel(aes(label = Parameter), size = 3,
-    parse = TRUE,
-    point.padding = unit(0, "lines"),
-    box.padding = unit(1, "lines"), 
-    force = 3
-    ) +
-  geom_point(aes(fill = Category), shape = 21, size = 4) +
-  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
-  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
-  facet_wrap(~L1, scales= 'free', ncol = 4) + 
-  scale_y_continuous('Identifiability') + 
-  scale_x_continuous(
-    'Parameters selected by sensitivity',
-    breaks = toplo$Selected, 
-    expand = c(.1, .1)
-    ) + 
-  cols +
-  pthm %+replace%
-  theme(legend.position = 'top')
-
-@
-
 \clearpage

### 2017-03-09 ident_manu.tex
much shortening

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue Mar 7 16:55:36 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/8f38d5a2d17442eb0f3f3d4db61d379b841c8830}{8f38d5a2d17442eb0f3f3d4db61d379b841c8830}}
+\tnotetext[mytitlenote]{Version: Wed Mar 8 10:38:46 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/f654ac2857b352ca61eae17b12e5450b982e6825}{f654ac2857b352ca61eae17b12e5450b982e6825}}
 
@@
 
-The sensitivity of \ac{do} to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep of FishTank simulations from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
+The sensitivity of state variables to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
 Irrelevant parameters were removed for several reasons; parameters were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
-Additionally, FishTank includes six phytoplankton and two zooplankton groups to describe complexity in community structure and foodweb dynamics.
-However, structural equations for each group are identical such that chosen parameter values primarily control differences between the groups, e.g., large-bodied or small-bodied plankton, slow-growing or fast-growing plankton, etc.
-Initial analyses indicated that parameter sensitivity of dissolved oxygen was identical within the six phytoplankton and zooplankton groups.
-To remove obvious redundancies in the model, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
-The final parameter set that was evaluated included 51 parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (22), temperature (2), and zooplankton (11).
+Additionally, FishTank includes six phytoplankton and two zooplankton groups to add complexity in community structure and foodweb dynamics.
+To remove obvious redundancies, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
+The final set that was evaluated included 51 parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (22), temperature (2), and zooplankton (11).
 A full description of the model parameters is available as an appendix in \citetalias{LehrterIP}.
@@
 
-\noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) results for parameters in a sensitivity matrix $S$.
-The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that described deviations of predicted \ac{do} from the default parameter values.
-Thus, $\gamma$ can be estimated for any subset of parameter combinations using the change in model output for perturbations of individual parameters.
+\noindent where $\gamma$ ranges from one to infinity for perfectly identifiable (orthogonal) or unidentifiable (perfectly collinear) parameter sets.
+The sensitivity functions were supplied as a matrix $\hat{S}$ with rows $i$ and columns $j$ (\cref{sijeqn}) that described deviations of predicted \ac{do} following perturbations of each parameter.
+Thus, $\gamma$ can be estimated from results for any subset of parameter combinations.
 Sensitivity matrices were first normalized by dividing by the square root of the summed residuals \citep{Omlin01,Soetaert10}.
-
-The collinearity index $\gamma$ provides a measure of the linear dependence between sensitivity functions (i.e., $S_i$ for $j$ parameters) described above for subsets of parameters.
-Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms given similar effects of the selected parameters on the estimated state variable.
-Greater sensitivity of a state variable to a subset of parameters does not always imply better identifiability if the effects of individual parameters are similar.
-An intuitive interpretation of $\gamma$ is provided by \citet{Brun01} such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
+Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms.
+An intuitive interpretation of $\gamma$ is provided by \citet{Brun01}, such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
 That is, $\gamma = 10$ suggests the relative change in \ac{do} for an arbitrary parameter in the selected set can be compensated for by 90\% with changes in the other parameters.
 
-Initial analyses suggested that considerably limited subsets of parameters were identifiable of the 51 evaluated for the FishTank model.
-Given this limitation, parameter selection must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
-An additional challenge is the excessively high number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practitioners may only be interested in optics parameters).
-For example, \cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., based on $n$ choose $k$ combinations equal to $n!/\left(k!\left(n-k\right)!\right)$).
+Parameter selection for model calibration must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
+An additional challenge is a large number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practitioners may only be interested in optics parameters).
+\cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., $n$ choose $k$ combinations, $n!/\left(k!\left(n-k\right)!\right)$).
 The number of unique combinations increases with the total parameters in the set and is also maximized for moderate selections (e.g., selecting half the total).
 For example, over 10$^{14}$ combinations are possible by selecting 25 parameters from a set of 50.
-Accordingly, parameter selection is complicated by differing sensitivity, identifiability limits for parameter subsets, and the difficulty of choosing from many combinations.
-
-A set of heuristics was developed that address the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
-These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability).
+
+A set of heuristics was developed that addresses the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
+These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
 Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences by model users given questions of interest.
@@
 
-\subsection{Extension to other state variables}
-
-The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.
-In addition to \ac{do}, other state variables that were evaluated were ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.
-Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIP}).
-
 \subsection{Model calibration with parameter subsets}
@@
 
-Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 38 of the 51 (75\% of total) parameters that were evaluated in FishTank (default panel \cref{fig:sensalltile}, \cref{tab:dosens}).
+Local sensitivity analyses showed that \ac{do} was sensitive to perturbations in 38 of the 51 (75\% of total) parameters that were evaluated in FishTank (\cref{fig:sensalltile}, \cref{tab:dosens}).
 Within each parameter category, \ac{do} was sensitive to three parameters for optics (75\% of all optic parameters), eight for organic matter (67\%), 16 for phytoplankton (73\%), one for temperature (50\%), and 10 for zooplankton (91\%).
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, sensitivity values ranged from $L1 = $ $8.34\times 10^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton), whereas average sensitivity among all parameters was $L1 = $ $9.2\times 10^{-3}$.
+Among all parameters, average sensitivity was $L1 = $ $9.2\times 10^{-3}$ with values ranging from $L1 = $ $8.34\times 10^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton).
 Within categories (excluding temperature with one sensitive parameter), sensitivity ranged from $4.39\times 10^{-5}$ (\textit{astarOMA}) to $7.51\times 10^{-4}$ (\textit{astar490}) for optics, $4.17\times 10^{-4}$ (\textit{KNH4}) to $6.15\times 10^{-3}$ (\textit{KG1}) for organic matter, $8.34\times 10^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69\times 10^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton (\cref{tab:dosens}).
@@
 
-\subsection{Subset identifiability}
-
-The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.
-Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.
+\subsection{Identifiability of parameter subsets and selection rules}
+
+The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$.
 Parameter identifiability for \ac{do} decreased (increasing $\gamma$) at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}).
@@
 For example, inclusion of \textit{KNO3} in a parameter set almost always inflated $\gamma$.
-All parameter subsets that did not include \textit{KNO3} were well below $\gamma = 15$, suggesting that removal of this parameter improves identifiability.
+All parameter subsets that did not include \textit{KNO3} were well below $\gamma = 15$, suggesting that exclusion of this parameter improves identifiability.
 Interestingly, the inclusion of some parameters caused a reduction in $\gamma$, which contradicts the general rule that more parameters caused reduced identifiablity.
@@
 
-\subsection{Parameter selection}
-
-The above results demonstrated that state variables differed in the magnitudes of sensitivity for each parameter and the number of identifiable subsets, where the latter varied by $\gamma$ thresholds and parameter selection criteria.
 Results for each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) applied to each state variable differed in the number of selected parameters and distribution of parameters within each category (\cref{tab:heurist1,tab:heurist2,tab:heurist3}).
@@
 The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic given equal importance between categories.
-
-\Cref{fig:heurist_stts} demonstrates parameter selection for all state variables following the second heuristic where parameters were chosen by decreasing sensitivity independent of parameter categories (exact values are shown in \cref{tab:heurist2}).
-The y-axis shows the relative identifiability with the addition of parameters from one to many on the x-axis (from left to right).
-The second to last parameter for each variable is the last parameter selected within the potential threshold of $\gamma = 15$.
-Interestingly, the last parameter shown for most of the state variables caused a relatively large increase in $\gamma$ that was disproportionate to the combined identifiability of the preceding parameter set.
-For most variables, the phytoplankton edibility vector for zooplankton (\textit{ediblevector(Z1)}) caused a dramatic increase in $\gamma$ with inclusion in the parameter set.
-In addition to demonstrating the approach for selection with the second heuristic, \cref{fig:heurist_stts} provides an alternative method of identifying parameters that are disproportionately redundant within a given parameter set (i.e., large contribution to $\gamma$).
-This infomation is useful if additional parameter selection rules are developed independently of those proposed herein.
 
@@
 This study provided a simple approach to use the effects of parameter perturbations on model state variables to characterize identifiable parameter subsets that vary by parameter selection criteria.
-By doing so, we demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiabilty thresholds described in the literature.
+By doing so, we demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiability thresholds described in the literature.
 The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
-We further demonstrated that changes in the model structure and variation in the initial conditions had an effect on sensitivity which has direct implications for identifiability.
 In general, these results provide justification for the use of explicit parameter selection heuristics that practitioners should adopt to facilitate model calibration.
 
-Although the results were specific to individual variables, some generalities about hypoxia dynamics can be inferred from the sensitivity analyses.
 State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\textit{umax} for phytoplankton, \textit{Zumax} for zooplankton), mortality coefficient for phytoplankton (\textit{mA}), and the zooplankton half saturation coefficent for grazing (\textit{ZKa}).
@@
 For example, \cref{fig:exclex} shows that including \textit{KGcdom}, \textit{KO2}, or \textit{nitmax} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
-Conversely, \cref{fig:heurist_stts} showed that the inclusion of a specific parameters often caused a disproportionate increase in $\gamma$ (e.g., \textit{ediblevector(Z1)}).
 These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
@@
 Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive (L1, \cref{l1}), until $\gamma > 15$.
-Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).
-See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}}
+Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:heurist2}}
 \begin{center}
@@
 Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:exclex}
-\end{figure}
-
-% heuristic plots, all state
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\textwidth]{figs/heurist_stts-1}
-
-}
-
-\caption[Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for all state variables]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for all state variables.
-Parameters are selected by decreasing sensitivity independent of parameter categories.
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.
-Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
 \end{figure}

### 2017-03-12 ident_manu.Rnw
sens evaluation did use surface flux

@@
 
-The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux) nor sediment diagenesis.
+The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any advection, mixing, or sediment diagenesis.
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
@@
 This is not a perfect example but works for our purposes to demonstrate differeing precision as directly related to identifiability of subsets and paramter types in a subset.
+Thus we were primarily concerned with showing differences in calibration results between paramters sets and not an absolute description of the time series.
 % note that we are not concerned with the magnitude of the error but the differences in error between parameter subsets and number of runs to convergence.

### 2017-03-12 ident_manu.tex
sens evaluation did use surface flux

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Wed Mar 8 10:38:46 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/f654ac2857b352ca61eae17b12e5450b982e6825}{f654ac2857b352ca61eae17b12e5450b982e6825}}
+\tnotetext[mytitlenote]{Version: Thu Mar 9 13:12:38 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/70c8da3c6d4aa0e50231198ae90027a250ce2ae5}{70c8da3c6d4aa0e50231198ae90027a250ce2ae5}}
 

### 2017-03-17 ident_manu.Rnw
areal views to plot

@@
 library(purrr)
+library(grid)
+library(lubridate)
+# library(raster)
+library(rgeos)
+library(ggpolypath)
+library(readxl)
+library(ggmap)
 @
@@
 
+<<areachg, eval = T, fig.cap = 'Estimated hypoxic area and monthly averages (km$^2 \\times$ 1000) using the default parameter settings (a, b) and the differences using a 50\\% increase in each parameter (c, d).
+The selected parameters were the top sensitive in each parameter category for \\ac{do} in \\cref{fig:sensalltile,tab:dosens}.
+Error bars are 95\\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.
+Areal extent of estimated hypoxia on August 29\\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = "\\textwidth">>=
+# ##
+# # area time series
+# areats <- read_excel('ignore/runcompare.xlsx', sheet = 'area')
+# 
+# ##
+# # get all arrays of hypox area for each parameter
+# shts <- excel_sheets('ignore/runcompare.xlsx') %>% 
+#   grep('array', ., value = T)
+# latlon <- read_excel('ignore/runcompare.xlsx', sheet = 'Latlon') %>% 
+#   list(
+#     lat = c(.[,1])[[1]], 
+#     lon = as.numeric(names(.)[-1])
+#     ) %>% 
+#   .[c('lat', 'lon')]
+# 
+# ls <- vector('list', length = length(shts))
+# names(ls) <- shts
+# for(sht in shts){
+#  
+#   cat(sht, '\t')
+#   
+#   # read the sheet, interpolate for higher res
+#   tmp <- read_excel('ignore/runcompare.xlsx', sheet = sht, na = '-9999', col_names = F) 
+#   tmp <- tmp[1:176,1:320] %>% 
+#     as.matrix
+#   obs <- list(x = latlon$lat, y = latlon$lon, z = tmp)
+#   newgrd <- expand.grid(
+#       x = approx(latlon$lat, n = 4 * ncol(tmp))$y,
+#       y = approx(latlon$lon, n = 4 * nrow(tmp))$y
+#       )
+#   int_val <- fields::interp.surface(
+#     obj = obs,
+#     loc = newgrd
+#     )
+#   tmp <- data.frame(newgrd, tmp = int_val) %>%
+#     spread(x, tmp) %>%
+#     dplyr::select(-y) %>%
+#     as.matrix %>% 
+#     .[, ncol(.):1] %>% 
+#     t
+#   
+#   # subset hypoxic areas, make polygon
+#   # get only the large areas
+#   tmp[tmp >= 64] <- NA
+#   tmp[!is.na(tmp)] <- 1
+#   tmp <- raster(tmp, 
+#     xmn = min(latlon$lon), 
+#     xmx = max(latlon$lon),   
+#     ymn = min(latlon$lat), 
+#     ymx = max(latlon$lat)
+#     )
+#   tmp <- rasterToPolygons(tmp, dissolve = T) %>% 
+#     disaggregate
+#   areas <- transform(data.frame(tmp), area = gArea(tmp, byid = T))
+#   filt <- with(areas, which(area > 0.12)) #quantile(area, 0.99)))
+#   tmp <- tmp[filt, ] %>% 
+#     fortify
+#   
+#   ls[[sht]] <- data.frame(parm = sht, tmp)
+#    
+# }
+# 
+# # combine output from each sheet
+# arrs <- do.call('rbind', ls) %>% 
+#   mutate(
+#     parm = gsub('_array$', '', parm)
+#     ) %>% 
+#   # filter(lat > 28) %>% 
+#   tibble::remove_rownames(.) %>% 
+#   unite('grp', parm, group, remove = F)
+# 
+# # save
+# save(areats, arrs, file = 'data/area.RData', compress = 'xz')
+
+# area time series and 2d arrays (areats, arrs)
+data(area)
+
+# theme
+mytheme <- theme_minimal() + 
+  theme(
+    axis.line.x = element_line(), 
+    axis.line.y = element_line(), 
+    axis.title.y = element_blank(),
+    axis.title.x = element_blank(), 
+    axis.ticks.x = element_line(),
+    axis.ticks.y = element_line(),
+    axis.ticks.length = unit(.1, "cm"),
+    legend.title = element_blank(),
+    legend.position = 'top', 
+    legend.text.align = 0
+  )
+
+# colors
+cols <- RColorBrewer::brewer.pal(5, 'Spectral')
+
+# format area time series 
+areats <- areats %>% 
+  dplyr::select(dts = 1, everything()) %>% 
+  mutate(
+    dts = as.Date(dts), 
+    mo = month(dts, label = T)
+  ) %>% 
+  gather('var', 'val', -dts, -mo) %>% 
+  mutate(
+    var = gsub('\\+50%$', '', var),
+    val = val / 1000
+    ) %>% 
+  spread(var, val) %>% 
+  filter(mo %in% c('May', 'Jun', 'Jul', 'Aug', 'Sep', 'Oct'))
+
+# formatted levels in order
+levs <- c('umax', 'ZKa', 'astar490', 'KG1', 'Tref')
+labs <- paste0(c('umax', 'ZKa', 'astar490', 'KG1', 'Tref(nospA+nospZ)'), '_1')
+labs <- par_txt(labs, frm = 'exp')
+
+##
+# data for each plot
+
+toplo1 <- areats
+
+toplo2 <- gather(areats, 'var', 'val', -dts, -Original, -mo) %>% 
+  mutate(
+    valper = val - Original,
+    var = factor(var, levels = levs, labels = labs)
+  )
+
+toplo3 <- areats %>%
+  group_by(mo) %>% 
+  summarise(
+    valup = t.test(Original)$conf.int[2],
+    valdn = t.test(Original)$conf.int[1],
+    val = mean(Original)
+  )
+
+toplo4 <- gather(areats, 'var', 'val', -dts, -mo, -Original) %>% 
+  group_by(mo, var) %>% 
+  summarise(
+    valup = t.test(val, Original)$conf.int[2],
+    valdn = t.test(val, Original)$conf.int[1],
+    val = mean(val) - mean(Original)
+  ) %>% 
+  ungroup %>% 
+  mutate(
+    var = factor(var, levels = levs, labels = labs)
+  )
+
+toplo5 <- filter(arrs, parm %in% 'original')
+
+toplo6 <- filter(arrs, !parm %in% 'original') %>% 
+  mutate(
+    parm = factor(parm, levels = levs, labels = labs)
+  )
+
+##
+# subplots
+
+p1 <- ggplot(toplo1, aes(x = dts, y = Original)) + 
+  geom_polygon() + 
+  mytheme + 
+  scale_x_date(date_labels = '%b', date_breaks = '1 month') +
+  ggtitle(label = NULL, subtitle = '(a) Area with default parameters')
+
+p2 <- ggplot(toplo2, aes(x = dts, y = valper, fill = var)) + 
+  geom_ribbon(aes(ymin = 0, ymax = valper), colour = 'darkgrey', size = 0.35) + 
+  mytheme %+replace%
+  theme(legend.position = 'none') +
+  scale_x_date(date_labels = '%b', date_breaks = '1 month') +
+  scale_fill_manual(values = cols, labels = labs) +
+  ggtitle(label = NULL, subtitle = '(c) Area differences with parameter perturbations')
+
+p3 <- ggplot(toplo3, aes(x = mo, y = val)) + 
+  geom_bar(stat = 'identity') + 
+  geom_errorbar(aes(ymin = valdn, ymax = valup), width = 0.25, lwd = 0.35) + 
+  mytheme +
+  ggtitle(label = NULL, subtitle = '(b) Averages with default parameters')
+
+pd <- position_dodge(0.75)
+p4 <- ggplot(toplo4, aes(x = mo, y = val, fill = var)) + 
+  geom_bar(stat = 'identity', position = pd, width = 0.75, colour = 'darkgrey', lwd = 0.35) + 
+  geom_errorbar(aes(ymin = valdn, ymax = valup), position = pd, width = 0.25, size = 0.35) + 
+  scale_fill_manual(values = cols, labels = labs) +
+  mytheme +
+  ggtitle(label = NULL, subtitle = '(d) Average differences with parameter perturbations')
+
+pleg <- g_legend(p4)
+p4 <- p4 + 
+  mytheme  %+replace%
+  theme(legend.position = 'none')
+
+# basemap for area ts
+ext <- make_bbox(arrs$long, arrs$lat, f = 0.01)
+map <- get_stamenmap(ext, zoom = 9, maptype = "toner-lite")
+
+p5 <- ggmap(map) + 
+  geom_polypath(data = toplo5, aes(x = long, y = lat, group = grp), alpha = 0.5) +
+  geom_path(data = toplo6, aes(x = long, y = lat, group = grp, colour = parm), alpha = 0.9, size = 1) + 
+  scale_y_continuous(expand = c(0, 0)) + 
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_colour_manual(values = cols, labels = labs) +
+  coord_equal() + 
+  mytheme %+replace%
+  theme(legend.position = 'none') +
+  ggtitle(label = NULL, subtitle = '(e) Estimated areal extents on August 29')
+
+pA <- ggplot_gtable(ggplot_build(p1))
+pB <- ggplot_gtable(ggplot_build(p2))
+pC <- ggplot_gtable(ggplot_build(p3))
+pD <- ggplot_gtable(ggplot_build(p4))
+pE <- ggplot_gtable(ggplot_build(p5))
+maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3])
+pA$widths[2:3] <- maxWidth
+pC$widths[2:3] <- maxWidth
+pE$widths[2:3] <- maxWidth
+maxWidth = unit.pmax(pC$widths[2:3], pD$widths[2:3], pE$widths[2:3])
+pB$widths[2:3] <- maxWidth
+pD$widths[2:3] <- maxWidth
+
+ylab <- expression(paste('Hypoxic area ( ', km^2, ' x 1000)'))
+grid.arrange(
+  left = textGrob(ylab, rot = 90),
+  arrangeGrob(
+    arrangeGrob(pA, pC, ncol = 2),
+    pleg, 
+    arrangeGrob(pB, pD, ncol = 2), 
+    pE,
+    ncol = 1, 
+    heights = c(1, 0.1, 1, 1.4)
+  )
+)
+
+@
+
 \clearpage

### 2017-03-17 ident_manu.tex
areal views to plot

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Thu Mar 9 13:12:38 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/70c8da3c6d4aa0e50231198ae90027a250ce2ae5}{70c8da3c6d4aa0e50231198ae90027a250ce2ae5}}
+\tnotetext[mytitlenote]{Version: Sun Mar 12 12:53:46 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/39a5c73735c94c696b2422eddee88342245006dd}{39a5c73735c94c696b2422eddee88342245006dd}}
 
@@
 
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/areachg-1}
+
+}
+
+\caption{Estimated hypoxic area and monthly averages (km$^2 \times$ 1000) using the default parameter settings (a, b) and the differences using a 50\% increase in each parameter (c, d).
+The selected parameters were the top sensitive in each parameter category for \ac{do} in \cref{fig:sensalltile,tab:dosens}.
+Error bars are 95\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.
+Areal extent of estimated hypoxia on August 29\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).}\label{fig:areachg}
+\end{figure}
+
 \clearpage

### 2017-03-26 ident_manu.Rnw
methods for calibration/extrapolation written

@@
 library(ggmap)
+library(ggsn)
 @
@@
 
-A local sensitivity analysis was performed by evaluating the change in state variables following perturbation of each parameter from its original value \citep{Soetaert10,RDCT16}.
+A local sensitivity analysis was performed by evaluating the change in state variables following perturbation of each parameter from its original value \citep{Soetaert10,RDCT17}.
 Parameters were individually perturbed by 50\% of the original values and sensitivity $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
@@
 Parameter selection for model calibration must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
-An additional challenge is a large number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., practitioners may only be interested in optics parameters).
+An additional challenge is a large number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., parameters for a group of related structural equations could be of interest).
 \cref{fig:combnex} provides a simple graphic of the unique number of combinations that are possible for different subsets of `complete' parameter sets of different sizes (i.e., $n$ choose $k$ combinations, $n!/\left(k!\left(n-k\right)!\right)$).
@@
 
-\subsection{Model calibration with parameter subsets}
-
-% we want to show that the results have relevance for the larger three-dimensional model and that model output for calibration to different parameters sets will have differing precision given 1) differences in sensitivity to included ina  subsets and 2) differences given proportion of parameters selected from different categories.
-
-% we use a time series from Weeks Bay NERRS because data are continuous, initial conditions were modified to match weeks bay conditions.
-DO time series was filtered to remove tidal advection component and air/sea gas exhange was used.
-This is not a perfect example but works for our purposes to demonstrate differeing precision as directly related to identifiability of subsets and paramter types in a subset.
-Thus we were primarily concerned with showing differences in calibration results between paramters sets and not an absolute description of the time series.
-% note that we are not concerned with the magnitude of the error but the differences in error between parameter subsets and number of runs to convergence.
+\subsection{Model calibration and extrapolation}
+
+Selected parameter subsets from the seven heuristics were used to calibrate the \ac{zerod} model.
+This analysis demonstrated that different parameter sets can produce model output with differing precision and calibration effort given 1) differences in variable sensitivity to parameters in each subset, 2) differences in the parameters selected from different categories (heuristic difference), and 3) differences in identifiability values.
+Generally, this analysis was a proof of concept that the selection heuristics can lead to an `optimal' model by maximizing the balance between sensitivity and identifiability.
+
+A time series of \ac{do} from Weeks Bay, Alabama was used for model calibration.
+Daily observations from January 1\textsuperscript{st},  2006 to January 1\textsuperscript{st}, 2007 at the Weeks Bay station of the Weeks Bay National Estuarine Reserve were used \citep{Wenner04}.
+We chose this location because of the availability of data for model calibration compared to bottom waters in the northern \ac{gom} and the system exhibits hypoxia from eutrophication.
+This application also provided a practical example of how the FishTank model could be calibrated using data from alternative locations.
+Initial conditions for model input were modified to match conditions in Weeks Bay using observed water quality and nutrient data (all data from \url{http://cdmo.baruch.sc.edu/}).
+The \ac{do} time series was filtered to reduce physical effects of the tidal advection component on the observed data (\textit{sensu} \citealt{Beck15b}).
+As such, the filtered data were comparable to a time series with no physical advection to match conditions of the \ac{zerod} FishTank model with no hydrodynamic component.
+
+Each parameter subset was calibrated to most closely match the model output to the observed time series.
+Parameter values were searched using the optim function in R that implemented the limited memory modification of the BFGS quasi-Newton method \citep{Byrd95,Nocedal06,RDCT17}.
+This opimization scheme searches for values within the user-defined lower and upper bounds of each parameter.
+We set the algorithm to search within +/- 50\% of the default parameter values.
+While we recognize that `actual' parameter values could possibly be outside of this range, constraining the values to those tested herein was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
+Moreover, precise limits on each parameter were less of a concern for the current analysis as our primary goal was to demonstrate differences in precision as a function of sensitivity and identifiability.
+The optimal values for each parameter were identified based on convergence of the model results as a minimization of the root-mean squared error between the observed and modelled data.
+
+As a final analysis, effects of parameter changes on the larger 3-dimensional model were evaluated to demonstrate that results from the \ac{zerod} FishTank model can be extrapolated.
+For simplicity, only the most sensitive parameter in each category was selected.
+The \ac{cgem} model was run for one year using the default parameter conditions and by increasing each of the selected parameters by 50\%.
+This produced six spatially-referenced time series from which the changes in the daily hypoxic area (number of cells $<$ 64 mmol \ac{do}) were estimated in the nothern \ac{gom}.
 
@@
 
+\subsection{Model calibration and extrapolation}
+
+Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values.
+The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
+The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of category and equally within each category were also evaluated.
+<<>>=
+NULL
+@
+
+% starting rmse of model without calibration
+\cref{fig:areachg}
+% does overall area change correlate with degree of sensitivity?
+
 \section{Discussion}
@@
 
-\bibliography{refsshr}
+\bibliography{refs}
+% \bibliography{refsshr}
 \clearpage
@@
   geom_polypath(data = toplo5, aes(x = long, y = lat, group = grp), alpha = 0.5) +
-  geom_path(data = toplo6, aes(x = long, y = lat, group = grp, colour = parm), alpha = 0.9, size = 1) + 
+  geom_path(data = toplo6, aes(x = long, y = lat, group = grp, colour = parm), alpha = 0.8, size = 0.8) + 
   scale_y_continuous(expand = c(0, 0)) + 
@@
   theme(legend.position = 'none') +
-  ggtitle(label = NULL, subtitle = '(e) Estimated areal extents on August 29')
+  ggtitle(label = NULL, subtitle = '(e) Estimated areal extents on August 29, default extent in grey') + 
+  scalebar(location = 'bottomleft', y.min = 28.35, y.max = 28.8, x.min = -93.3, x.max = -92, 
+    dist = 20, dd2km= TRUE, model='WGS84', st.dist=.1, st.size = 2, height = 0.08)
 
@@
 
-ylab <- expression(paste('Hypoxic area ( ', km^2, ' x 1000)'))
+ylab <- expression(paste('                                               Hypoxic area ( ', km^2, ' x 1000)'))
 grid.arrange(
-  left = textGrob(ylab, rot = 90),
   arrangeGrob(
@@
     ncol = 1, 
+      left = textGrob(ylab, rot = 90),
     heights = c(1, 0.1, 1, 1.4)

### 2017-03-26 ident_manu.tex
methods for calibration/extrapolation written

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Mar 12 12:53:46 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/39a5c73735c94c696b2422eddee88342245006dd}{39a5c73735c94c696b2422eddee88342245006dd}}
+\tnotetext[mytitlenote]{Version: Fri Mar 17 14:00:58 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/4e88d0837d798238902ff4eb6348b72e9143c557}{4e88d0837d798238902ff4eb6348b72e9143c557}}
 
@@
 The second and third selection heuristics (\cref{tab:heurist2,tab:heurist3}) were similar, although more parameters were generally selected for the third heuristic given equal importance between categories.
+
+\subsection{Model calibration and extrapolation}
+
+Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values.
+The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
+The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of category and equally within each category were also evaluated.
+NULL
+
+% starting rmse of model without calibration
+\cref{fig:areachg}
+% does overall area change correlate with degree of sensitivity?
 

### 2017-03-26 R/funcs.R

@@ -1186,3 +1186,225 @@ loc_summ <- function(scatall){
   return(out_ls)
   
 }
+
+######
+# get list of parameter combinations to calibrate from tocal_all data object
+#
+# tocal_all input data object created in dat_proc.R
+# out_var chr string of state variable to eval
+# thrsh numeric for collinearity thresholds
+# coll logical if gamma is returned as an additional element for each heuristic
+#
+# temperature is manually added as a category in the first heuristic
+# only one parameter so wasn't included in tocal_all output
+#
+# min/max values for ediblevector and tref were added, 
+# former form Eldridge and Roelke, latter from reasonable temp ranges
+get_cmbs <- function(tocal_all, out_var = 'O2', thrsh = 15, coll = TRUE, errs = TRUE, pert = 0.5){
+  
+  # expected parameter values and ranges
+  allp <- get(load(file = 'ignore/GEM_InputFile.RData'))
+  rngs <- formpars('ignore/var_ranges.txt')
+  
+  # get out_var results, melt, create heurist column, filter by thresh, 
+  # add temp category (one parameter), combine with input file to get values
+  idpars <- tocal_all[[out_var]] %>% 
+    reshape2::melt(id.vars = names(.[[1]])) %>% 
+    mutate(
+      Category = ifelse(!L1 %in% 'cat', '', Category),
+      L1 = ifelse(Category %in% '', L1, ''), 
+      parm = as.character(Parameter)
+      ) %>% 
+    unite('heurist', L1, Category, sep = '') %>% 
+    filter(coll < thrsh) %>%
+    group_by(heurist) %>% 
+    mutate(coll = max(coll, na.rm = TRUE)) %>% 
+    ungroup %>% 
+    select(parm, error, heurist, coll) %>% 
+    rbind(
+      data.frame(parm = 'Tref(nospA+nospZ)_1', error = 0.02, heurist = 'Temperature', coll = NA)
+      ) %>% 
+    left_join(., allp, by = 'parm') %>% 
+    rename(vals = value)
+  
+  # get expected ranges
+  # add missing values
+  rngs <- filter(rngs, parm %in% idpars$parm) %>% 
+    separate(value, c('est', 'minv', 'maxv'), sep = '/') %>% 
+    mutate(
+      minv = ifelse(parm %in% 'Tref(nospA+nospZ)_1', 0, 
+        ifelse(parm %in% 'ediblevector(Z1)_1', 0.05, 
+          minv)),
[…]

### 2017-03-26 ident_manu.Rnw
table 5 added

@@
   )
+
+@
+
+% calibration table, do
+<<calib, eval = T, cache = F>>=
+
+library(tidyverse)
+library(lubridate)
+source("R/funcs.R")
+
+load(file = 'data/tocal_all.RData')
+load(file = 'data/cals.RData')
+
+# starting rmse
+strt <- cals[[1]]$mat[1,] %>% 
+  .[length(.)]
+# 72.13955
+
+idpars <- get_cmbs(tocal_all, 'O2', coll = T, errs = T, pert = 0.5)
+
+colerr <- get_cmbs(tocal_all, 'O2') %>% 
+  lapply(function(x) c(x$coll, mean(x$errs), length(x$errs))) %>% 
+  do.call('rbind', .) %>% 
+  data.frame %>% 
+  rownames_to_column %>% 
+  rename(
+    heurist = rowname, 
+    coll = X1,
+    avee = X2,
+    nprm = X3
+  )
+
+levs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'top', 'cattop')
+labs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'Independent of category', 'Equally within category')
+caldat <- lapply(cals, function(x) c(x$value, nrow(x$mat))) %>% 
+  do.call('rbind', .) %>% 
+  data.frame %>% 
+  rownames_to_column %>% 
+  rename(
+    heurist = rowname, 
+    rmse = X1, 
+    its = X2
+  ) %>% 
+  left_join(colerr, by = 'heurist') %>% 
+  select(heurist, coll, nprm, avee, its, rmse) %>% 
+  mutate(
+    heurist = factor(heurist, levels = levs, labels = labs),
+    coll = ifelse(is.na(coll), 1, coll),
+    coll = sapply(coll, scinot),
+    nprm = sapply(nprm, scinot),
+    its = sapply(its, scinot),
+    rmse = sapply(rmse, scinot), 
+    avee = sapply(avee, scinot)
+    ) %>% 
+  arrange(heurist)
+
+# pairs(caldat[, -1])
+totab <- caldat
+cap_val <- 'Results of model calibration to observed \\ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third).
+The collinearity values ($\\gamma$) and parameters of each subset are from \\cref{tab:heurist1,tab:heurist2,tab:heurist3}.
+Mean L1 is the average of sensitivity values (\\cref{l1}) for the subset.
+$RMSE$ shows the final error comparing observed and model output after the specified number of iterations for optimization.'
+colnms <- c('$\\gamma$', '$n$ parameters', 'mean L1', 'Iterations', '$RMSE$')
+
+latex( 
+  totab[, -1],
+  file = '',
+  rowlabel = 'Selection heuristic',
+  caption = cap_val,
+  caption.loc = 'top',
+  size = 'scriptsize',
+  label = 'tab:calib',
+  rowname = totab$heurist,
+  rgroup = c('1', '2', '3'),
+  n.rgroup = c(5, 1, 1),
+  colheads = colnms
+  )
+
 @

### 2017-03-26 ident_manu.tex
table 5 added

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Fri Mar 17 14:00:58 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/4e88d0837d798238902ff4eb6348b72e9143c557}{4e88d0837d798238902ff4eb6348b72e9143c557}}
+\tnotetext[mytitlenote]{Version: Sun Mar 26 14:18:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}{4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}}
 
@@
 
+% calibration table, do
+%latex.default(totab[, -1], file = "", rowlabel = "Selection heuristic",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:calib", rowname = totab$heurist, rgroup = c("1",         "2", "3"), n.rgroup = c(5, 1, 1), colheads = colnms)%
+\begin{table}[!tbp]
+{\scriptsize
+\caption{Results of model calibration to observed \ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third).
+The collinearity values ($\gamma$) and parameters of each subset are from \cref{tab:heurist1,tab:heurist2,tab:heurist3}.
+Mean L1 is the average of sensitivity values (\cref{l1}) for the subset.
+$RMSE$ shows the final error comparing observed and model output after the specified number of iterations for optimization.\label{tab:calib}}
+\begin{center}
+\begin{tabular}{llllll}
+\hline\hline
+\multicolumn{1}{l}{Selection heuristic}&\multicolumn{1}{c}{$\gamma$}&\multicolumn{1}{c}{$n$ parameters}&\multicolumn{1}{c}{mean L1}&\multicolumn{1}{c}{Iterations}&\multicolumn{1}{c}{$RMSE$}\tabularnewline
+\hline
+{\bfseries 1}&&&&&\tabularnewline
+~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$14$&$72.14$\tabularnewline
+~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$154$&$68.7$\tabularnewline
+~~Phytoplankton&$3.97$&$7$&$0.02$&$270$&$68.72$\tabularnewline
+~~Temperature&$1$&$1$&$0.02$&$6$&$71.76$\tabularnewline
+~~Zooplankton&$5.2$&$4$&$0.03$&$99$&$71.22$\tabularnewline
+\hline
+{\bfseries 2}&&&&&\tabularnewline
+~~Independent of category&$6.81$&$8$&$0.03$&$850$&$67.05$\tabularnewline
+\hline
+{\bfseries 3}&&&&&\tabularnewline
+~~Equally within category&$5.22$&$7$&$0.03$&$690$&$67.67$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+\end{table}
+
 \clearpage

### 2017-03-26 ident_manu.Rnw
figures say collinearity instead of identifiability

@@
 % identifiability plot
-<<identplo, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.
-Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
+<<identplo, eval = T, fig.cap = 'Collinearity ($\\gamma$ as a measure of identifiability, \\cref{gameq}) of parameter subsets for \\ac{do}.
+Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.
+Lines represent collinearity ranges for the possible combinations given the number of parameters in the set.
 The temperature category is not shown because \\ac{do} was sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 7, fig.width = 8, echo = F, cache = TRUE>>=
@@
 
+leftlab <- expression(paste('Collinearity, ', italic(gamma)))
 grid.arrange(
   arrangeGrob(p1, p2, ncol = 2),
-  left = 'Identifiability', 
+  left = textGrob(leftlab, rot = 90),
   bottom = 'Parameters in set',
@@
 % identifiability plot, all state variables
-<<identploall, eval = T, fig.cap = 'Average identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for all state variables.
-Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
-Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
+<<identploall, eval = T, fig.cap = 'Average collinearity ($\\gamma$ as a measure of identifiability, \\cref{gameq}) of parameter subsets for all state variables.
+Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.
+Collinearity was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
 The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=
@@
 
+leftlab <- expression(paste('Collinearity, ', italic(gamma)))
 grid.arrange(
   arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
-  left = 'Identifiability',
+  left = textGrob(leftlab, rot = 90),
   pleg, ncol = 2, widths = c(1, 0.2)
@@
 % parameter exclusion temp
-<<exclex, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) for \\ac{do} of organic matter parameters for subset combinations in \\cref{fig:identplo}.
-Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
-Identifiability of including all eight parameters is in \\cref{fig:identplo}.
-Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "0.8\\textwidth">>=
+<<exclex, eval = T, fig.cap = 'Collinearity ($\\gamma$ as a measure of identifiability, \\cref{gameq}) for \\ac{do} of organic matter parameters for subset combinations in \\cref{fig:identplo}.
+Collinearity is evaluated for subsets that excluded and included the parameters at the top of each plot.
+Collinearity of including all eight parameters is in \\cref{fig:identplo}.
+Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable collinearity.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "0.8\\textwidth">>=
 data(cat_ident_all)
@@
 
+leftlab <- expression(paste('Collinearity, ', italic(gamma)))
 ggplot(toplo, aes(x = N, y = coll, fill = inc)) + 
@@
   scale_fill_brewer(palette = 'Spectral') + 
-  scale_y_continuous('Identifiability', trans = 'log', breaks = c(0.1, 1, 10, 100, 1000)) +
+  scale_y_continuous(leftlab, trans = 'log', breaks = c(0.1, 1, 10, 100, 1000)) +
   scale_x_discrete('Parameters in set') + 

### 2017-03-26 ident_manu.tex
figures say collinearity instead of identifiability

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Mar 26 14:18:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}{4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}}
+\tnotetext[mytitlenote]{Version: Sun Mar 26 15:18:56 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/bf9e2162ec0d9ba7edf4ddc5b7ba5c1019142186}{bf9e2162ec0d9ba7edf4ddc5b7ba5c1019142186}}
 
@@
 
-\caption{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.
-Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
-Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.
+\caption{Collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) of parameter subsets for \ac{do}.
+Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.
+Lines represent collinearity ranges for the possible combinations given the number of parameters in the set.
 The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identplo}
@@
 
-\caption[Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables]{Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables.
-Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.
-Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
+\caption[Average collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) of parameter subsets for all state variables]{Average collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) of parameter subsets for all state variables.
+Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.
+Collinearity was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.
 The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identploall}
@@
 
-\caption{Identifiability (as $\gamma$, \cref{gameq}) for \ac{do} of organic matter parameters for subset combinations in \cref{fig:identplo}.
-Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot.
-Identifiability of including all eight parameters is in \cref{fig:identplo}.
-Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:exclex}
+\caption{Collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) for \ac{do} of organic matter parameters for subset combinations in \cref{fig:identplo}.
+Collinearity is evaluated for subsets that excluded and included the parameters at the top of each plot.
+Collinearity of including all eight parameters is in \cref{fig:identplo}.
+Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable collinearity.}\label{fig:exclex}
 \end{figure}

### 2017-03-26 ident_manu.Rnw
calib results text done

@@
 \acrodef{pom}[POM]{particulate organic matter}
+\acrodef{rmse}[\textit{RMSE}]{root mean squared error}
 \acrodef{zerod}[0-D]{zero-dimensional}
@@
 library(ggsn)
+library(tibble)
 @
@@
 Selected parameter subsets from the seven heuristics were used to calibrate the \ac{zerod} model.
-This analysis demonstrated that different parameter sets can produce model output with differing precision and calibration effort given 1) differences in variable sensitivity to parameters in each subset, 2) differences in the parameters selected from different categories (heuristic difference), and 3) differences in identifiability values.
+This analysis demonstrated that different parameter sets can produce model output with differing precision and calibration effort given
+\begin{inparaenum}[1\upshape)]
+\item differences in variable sensitivity to parameters in each subset, 
+\item differences in the parameters selected from different categories (heuristic difference), and 
+\item differences in identifiability values.
+\end{inparaenum}
 Generally, this analysis was a proof of concept that the selection heuristics can lead to an `optimal' model by maximizing the balance between sensitivity and identifiability.
@@
 Moreover, precise limits on each parameter were less of a concern for the current analysis as our primary goal was to demonstrate differences in precision as a function of sensitivity and identifiability.
-The optimal values for each parameter were identified based on convergence of the model results as a minimization of the root-mean squared error between the observed and modelled data.
+The optimal values for each parameter were identified based on convergence of the model results as a minimization of the \ac{rmse} between the observed and modelled data.
 
@@
 
-Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values.
+<<>>=
+load(file = 'data/tocal_all.RData')
+load(file = 'data/cals.RData')
+
+# starting rmse
+# 72.13955
+
+idpars <- get_cmbs(tocal_all, 'O2', coll = T, errs = T, pert = 0.5)
+
+colerr <- get_cmbs(tocal_all, 'O2') %>% 
+  lapply(function(x) c(x$coll, mean(x$errs), length(x$errs))) %>% 
+  do.call('rbind', .) %>% 
+  data.frame %>% 
+  rownames_to_column %>% 
+  rename(
+    heurist = rowname, 
+    coll = X1,
+    avee = X2,
+    nprm = X3
+  )
+
+levs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'top', 'cattop')
+labs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'Independent of category', 'Equally within category')
+caldat <- lapply(cals, function(x) c(x$value, nrow(x$mat))) %>% 
+  do.call('rbind', .) %>% 
+  data.frame %>% 
+  rownames_to_column %>% 
+  rename(
+    heurist = rowname, 
+    rmse = X1, 
+    its = X2
+  ) %>% 
+  left_join(colerr, by = 'heurist') %>% 
+  select(heurist, coll, nprm, avee, its, rmse) %>% 
+  mutate(
+    heurist = factor(heurist, levels = levs, labels = labs)
+  )
+
+# pairs(caldat[, -1])
+temp <- filter(caldat, heurist %in% 'Temperature')
+optics <- filter(caldat, heurist %in% 'Optics')
+top <- filter(caldat, heurist %in% 'Independent of category')
+cattop <- filter(caldat, heurist %in% 'Equally within category')
+@
+
+Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values (\cref{tab:calib}).
 The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
 The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of category and equally within each category were also evaluated.
-<<>>=
-NULL
-@
+As expected, the number of required iterations to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
+For example, only \Sexpr{toeng(temp$its)[[1]]} iterations were required to optimize the single parameter selected for the temperature category, whereas \Sexpr{top$its} iterations were required for the \Sexpr{toeng(top$nprm)[[1]]} parameters selected independent of category.
+A slight positive assocation between collinearity and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set inreased with lower identifiability (higher $\gamma$).
+Of the seven paramter subsets, selection independent of category and equally within each category produced the lowest \ac{rmse} values (\Sexpr{scinot(top$rmse)}, \Sexpr{scinot(cattop$rmse)}, respectively), whereas the optimal values for paramters in the Optics category had the lowest reduction in \ac{rmse} (\Sexpr{scinot(optics$rmse)}).
+Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
+Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 (\Sexpr{scinot(optics$avee)}), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 (\Sexpr{scinot(top$avee)}, \cref{tab:calib}).
 
@@
 
-library(tidyverse)
-library(lubridate)
-source("R/funcs.R")
-
-load(file = 'data/tocal_all.RData')
-load(file = 'data/cals.RData')
-
-# starting rmse
 strt <- cals[[1]]$mat[1,] %>% 
-  .[length(.)]
-# 72.13955
-
-idpars <- get_cmbs(tocal_all, 'O2', coll = T, errs = T, pert = 0.5)
-
-colerr <- get_cmbs(tocal_all, 'O2') %>% 
-  lapply(function(x) c(x$coll, mean(x$errs), length(x$errs))) %>% 
-  do.call('rbind', .) %>% 
-  data.frame %>% 
-  rownames_to_column %>% 
-  rename(
-    heurist = rowname, 
-    coll = X1,
-    avee = X2,
-    nprm = X3
-  )
-
-levs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'top', 'cattop')
-labs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'Independent of category', 'Equally within category')
-caldat <- lapply(cals, function(x) c(x$value, nrow(x$mat))) %>% 
-  do.call('rbind', .) %>% 
-  data.frame %>% 
-  rownames_to_column %>% 
-  rename(
-    heurist = rowname, 
-    rmse = X1, 
-    its = X2
-  ) %>% 
-  left_join(colerr, by = 'heurist') %>% 
-  select(heurist, coll, nprm, avee, its, rmse) %>% 
-  mutate(
-    heurist = factor(heurist, levels = levs, labels = labs),
+  .[length(.)] %>% 
+  scinot
+
+totab <- caldat %>% 
+  mutate(
     coll = ifelse(is.na(coll), 1, coll),
@@
 
-# pairs(caldat[, -1])
-totab <- caldat
 cap_val <- 'Results of model calibration to observed \\ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third).
@@
 $RMSE$ shows the final error comparing observed and model output after the specified number of iterations for optimization.'
-colnms <- c('$\\gamma$', '$n$ parameters', 'mean L1', 'Iterations', '$RMSE$')
+foot.val <- '\\footnotesize *Starting \\ac{rmse} $= 72.14$'
+colnms <- c('$\\gamma$', '$n$ parameters', 'mean L1', 'Iterations', '$RMSE$*')
 
@@
   rgroup = c('1', '2', '3'),
+  insert.bottom = foot.val, 
   n.rgroup = c(5, 1, 1),

### 2017-03-26 ident_manu.tex
calib results text done

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Mar 26 15:18:56 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/bf9e2162ec0d9ba7edf4ddc5b7ba5c1019142186}{bf9e2162ec0d9ba7edf4ddc5b7ba5c1019142186}}
+\tnotetext[mytitlenote]{Version: Sun Mar 26 15:32:37 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/b41a6df79d21b187457db88f058313b9b430416a}{b41a6df79d21b187457db88f058313b9b430416a}}
 
@@
 
-Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values.
+Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values (\cref{tab:calib}).
 The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
 The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of category and equally within each category were also evaluated.
-NULL
+As expected, the number of required iterations to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
+For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 850 iterations were required for the eight parameters selected independent of category.
+A slight positive assocation between collinearity and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set inreased with lower identifiability (higher $\gamma$).
+Of the seven paramter subsets, selection independent of category and equally within each category produced the lowest \ac{rmse} values ($67.05$, $67.67$, respectively), whereas the optimal values for paramters in the Optics category had the lowest reduction in \ac{rmse} ($72.14$).
+Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
+Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 ($2.81\times 10^{-4}$), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 ($0.03$, \cref{tab:calib}).
 
@@
 % calibration table, do
-%latex.default(totab[, -1], file = "", rowlabel = "Selection heuristic",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:calib", rowname = totab$heurist, rgroup = c("1",         "2", "3"), n.rgroup = c(5, 1, 1), colheads = colnms)%
+%latex.default(totab[, -1], file = "", rowlabel = "Selection heuristic",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:calib", rowname = totab$heurist, rgroup = c("1",         "2", "3"), insert.bottom = foot.val, n.rgroup = c(5,         1, 1), colheads = colnms)%
 \begin{table}[!tbp]
@@
 \hline\hline
-\multicolumn{1}{l}{Selection heuristic}&\multicolumn{1}{c}{$\gamma$}&\multicolumn{1}{c}{$n$ parameters}&\multicolumn{1}{c}{mean L1}&\multicolumn{1}{c}{Iterations}&\multicolumn{1}{c}{$RMSE$}\tabularnewline
+\multicolumn{1}{l}{Selection heuristic}&\multicolumn{1}{c}{$\gamma$}&\multicolumn{1}{c}{$n$ parameters}&\multicolumn{1}{c}{mean L1}&\multicolumn{1}{c}{Iterations}&\multicolumn{1}{c}{$RMSE$*}\tabularnewline
 \hline
@@
 \end{tabular}\end{center}}
-\end{table}
+\footnotesize *Starting \ac{rmse} $= 72.14$\end{table}
 

### 2017-03-27 ident_manu.Rnw
results done for calibration exrapolation

@@
 \usepackage{fixltx2e}
-% \usepackage[inline]{showlabels}
+\usepackage[inline]{showlabels}
 
@@
 # starting rmse
+strt <- cals[[1]]$mat[1,] %>% 
+  .[length(.)] %>% 
+  scinot(., digits = 3)
 # 72.13955
@@
 The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
-The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of category and equally within each category were also evaluated.
-As expected, the number of required iterations to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
+The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of parameter category and equally within each category were also evaluated.
+As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
 For example, only \Sexpr{toeng(temp$its)[[1]]} iterations were required to optimize the single parameter selected for the temperature category, whereas \Sexpr{top$its} iterations were required for the \Sexpr{toeng(top$nprm)[[1]]} parameters selected independent of category.
-A slight positive assocation between collinearity and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set inreased with lower identifiability (higher $\gamma$).
-Of the seven paramter subsets, selection independent of category and equally within each category produced the lowest \ac{rmse} values (\Sexpr{scinot(top$rmse)}, \Sexpr{scinot(cattop$rmse)}, respectively), whereas the optimal values for paramters in the Optics category had the lowest reduction in \ac{rmse} (\Sexpr{scinot(optics$rmse)}).
+A slight positive assocation between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
+Of the seven parameter subsets, selection independent of category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt}, reduction to \Sexpr{scinot(top$rmse, digits = 3)}, \Sexpr{scinot(cattop$rmse, digits = 3)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse, digits = 3)}).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
-Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 (\Sexpr{scinot(optics$avee)}), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 (\Sexpr{scinot(top$avee)}, \cref{tab:calib}).
-
-% starting rmse of model without calibration
-\cref{fig:areachg}
-% does overall area change correlate with degree of sensitivity?
+Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 (\Sexpr{scinot(optics$avee)}, \Sexpr{toeng(optics$nprm)} parameters), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 (\Sexpr{scinot(top$avee)}, \Sexpr{toeng(top$nprm)} parameters, \cref{tab:calib}).
+
+<<>>=
+data(area)
+
+# areats
+maxdef <- areats[which.max(areats$Original), ]
+
+# areas with  months
+areatxt<- areats %>% 
+  dplyr::select(dts = 1, everything()) %>% 
+  mutate(
+    dts = as.Date(dts), 
+    mo = month(dts, label = T)
+  )
+
+# default august area mean +- se
+deftxt <- filter(areatxt, mo %in% 'Aug') %>% 
+  .$Original %>% 
+  t.test
+deftxt <- with(deftxt, c(estimate, diff(conf.int)/2)) %>% 
+  round
+
+# mean difference and se from default
+levs <- c('umax', 'ZKa', 'astar490', 'KG1', 'Tref')
+labs <- paste0(c('umax', 'ZKa', 'astar490', 'KG1', 'Tref(nospA+nospZ)'), '_1')
+labs <- par_txt(labs, frm = 'tex')
+modiffs <- gather(areatxt, 'var', 'val', -dts, -mo, -Original) %>% 
+  group_by(mo, var) %>% 
+  summarise(
+    se = diff(t.test(val, Original)$conf.int)/2,
+    est = mean(val) - mean(Original)
+  ) %>% 
+  ungroup %>% 
+  mutate(
+    var = gsub('\\+50%', '', var), 
+    var = factor(var, levels = levs, labels = labs)
+  )
+
+# umax July area mean inrease +- se
+umaxtxt <- filter(modiffs, mo %in% 'Jul') %>% 
+  filter(grepl('umax', var)) %>% 
+  select(est, se) %>% 
+  round
+
+# tref July area mean decrease +- se
+treftxt <- filter(modiffs, mo %in% 'Jul') %>% 
+  filter(grepl('Tref', var)) %>% 
+  select(est, se) %>% 
+  round
+
+load(file = 'data/sens_ests_cat_all.RData')
+senstop <- sens_ests_cat_all[['O2']] %>% 
+  group_by(Category) %>% 
+  filter(error %in% max(error)) %>% 
+  ungroup %>% 
+  arrange(error) %>% 
+  mutate(
+    Parameter = par_txt(Parameter), 
+    error = sapply(error, scinot)
+  )
+@
+
+The estimated areal extent of bottom-water hypoxia using default parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at \Sexpr{scinot(maxdef$Original)} km$^2$ (\cref{fig:areachg}a, August mean area \Sexpr{deftxt[1]} $\pm$ \Sexpr{deftxt[2]} km$^2$, \cref{fig:areachg}b).
+Increases in the top sensitive parameters for \ac{do} in each category (\cref{tab:dosens}) increased the estimated areal extent of hypoxia (Figs.
+\ref{fig:areachg}c, \ref{fig:areachg}e), with the exception of the parameter for optimum temperature of growth (\Sexpr{par_txt('Tref(nospA+nospZ)_1')}), which caused a decrease (mean difference from July default area \Sexpr{treftxt$est} $\pm$ \Sexpr{treftxt$se} km$^2$, \cref{fig:areachg}d).
+The largest increase in area was caused by an increase in the maximum growth rate of phytoplankton (\Sexpr{par_txt('umax_1')}), with the greatest increase occurring in July (monthly mean increase of \Sexpr{umaxtxt$est} $\pm$ \Sexpr{umaxtxt$se} km$^2$, \cref{fig:areachg}d).
+Overall, changes in hypoxia extent were largest for parameters with large sensitivity values (i.e., L1 = \Sexpr{senstop[4, 2]} for \Sexpr{senstop[4, 1]}, L1 = \Sexpr{senstop[5, 2]} for \Sexpr{senstop[5, 1]}).
 
 \section{Discussion}
-
-\subsection{Implications of sensitivity and identifiability analyses}
 
@@
 
-strt <- cals[[1]]$mat[1,] %>% 
-  .[length(.)] %>% 
-  scinot
-
 totab <- caldat %>% 
@@
     its = sapply(its, scinot),
-    rmse = sapply(rmse, scinot), 
+    rmse = sapply(rmse, scinot, digits = 3), 
     avee = sapply(avee, scinot)
@@
 $RMSE$ shows the final error comparing observed and model output after the specified number of iterations for optimization.'
-foot.val <- '\\footnotesize *Starting \\ac{rmse} $= 72.14$'
+foot.val <- '\\footnotesize *Starting \\ac{rmse} $= 72.140$'
 colnms <- c('$\\gamma$', '$n$ parameters', 'mean L1', 'Iterations', '$RMSE$*')
@@
 Error bars are 95\\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.
-Areal extent of estimated hypoxia on August 29\\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = "\\textwidth">>=
+Areal extent of estimated hypoxia on August 28\\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = "\\textwidth">>=
 # ##
@@
   theme(legend.position = 'none') +
-  ggtitle(label = NULL, subtitle = '(e) Estimated areal extents on August 29, default extent in grey') + 
+  ggtitle(label = NULL, subtitle = '(e) Estimated areal extents on August 28, default extent in grey') + 
   scalebar(location = 'bottomleft', y.min = 28.35, y.max = 28.8, x.min = -93.3, x.max = -92, 

### 2017-03-27 ident_manu.tex
results done for calibration exrapolation

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Mar 26 15:32:37 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/b41a6df79d21b187457db88f058313b9b430416a}{b41a6df79d21b187457db88f058313b9b430416a}}
+\tnotetext[mytitlenote]{Version: Sun Mar 26 16:14:21 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/ad5c4632bfb7084298ee0ce337870bbac1db811c}{ad5c4632bfb7084298ee0ce337870bbac1db811c}}
 
@@
 The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
-The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of category and equally within each category were also evaluated.
-As expected, the number of required iterations to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
+The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of parameter category and equally within each category were also evaluated.
+As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
 For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 850 iterations were required for the eight parameters selected independent of category.
-A slight positive assocation between collinearity and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set inreased with lower identifiability (higher $\gamma$).
-Of the seven paramter subsets, selection independent of category and equally within each category produced the lowest \ac{rmse} values ($67.05$, $67.67$, respectively), whereas the optimal values for paramters in the Optics category had the lowest reduction in \ac{rmse} ($72.14$).
+A slight positive assocation between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
+Of the seven parameter subsets, selection independent of category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$, reduction to $67.052$, $67.665$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.139$).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
-Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 ($2.81\times 10^{-4}$), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 ($0.03$, \cref{tab:calib}).
-
-% starting rmse of model without calibration
-\cref{fig:areachg}
-% does overall area change correlate with degree of sensitivity?
+Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 ($2.81\times 10^{-4}$, three parameters), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 ($0.03$, eight parameters, \cref{tab:calib}).
+
+The estimated areal extent of bottom-water hypoxia using default parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at $1.19\times 10^{4}$ km$^2$ (\cref{fig:areachg}a, August mean area 8988 $\pm$ 551 km$^2$, \cref{fig:areachg}b).
+Increases in the top sensitive parameters for \ac{do} in each category (\cref{tab:dosens}) increased the estimated areal extent of hypoxia (Figs.
+\ref{fig:areachg}c, \ref{fig:areachg}e), with the exception of the parameter for optimum temperature of growth (\textit{Tref(nospA+nospZ)$_{p1}$}), which caused a decrease (mean difference from July default area -1070 $\pm$ 1161 km$^2$, \cref{fig:areachg}d).
+The largest increase in area was caused by an increase in the maximum growth rate of phytoplankton (\textit{umax}), with the greatest increase occurring in July (monthly mean increase of 4109 $\pm$ 1085 km$^2$, \cref{fig:areachg}d).
+Overall, changes in hypoxia extent were largest for parameters with large sensitivity values (i.e., L1 = $0.05$ for \textit{ZKa}, L1 = $0.05$ for \textit{umax}).
 
 \section{Discussion}
-
-\subsection{Implications of sensitivity and identifiability analyses}
 
@@
 {\bfseries 1}&&&&&\tabularnewline
-~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$14$&$72.14$\tabularnewline
-~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$154$&$68.7$\tabularnewline
-~~Phytoplankton&$3.97$&$7$&$0.02$&$270$&$68.72$\tabularnewline
-~~Temperature&$1$&$1$&$0.02$&$6$&$71.76$\tabularnewline
-~~Zooplankton&$5.2$&$4$&$0.03$&$99$&$71.22$\tabularnewline
+~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$14$&$72.139$\tabularnewline
+~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$154$&$68.701$\tabularnewline
+~~Phytoplankton&$3.97$&$7$&$0.02$&$270$&$68.722$\tabularnewline
+~~Temperature&$1$&$1$&$0.02$&$6$&$71.759$\tabularnewline
+~~Zooplankton&$5.2$&$4$&$0.03$&$99$&$71.223$\tabularnewline
 \hline
 {\bfseries 2}&&&&&\tabularnewline
-~~Independent of category&$6.81$&$8$&$0.03$&$850$&$67.05$\tabularnewline
+~~Independent of category&$6.81$&$8$&$0.03$&$850$&$67.052$\tabularnewline
 \hline
 {\bfseries 3}&&&&&\tabularnewline
-~~Equally within category&$5.22$&$7$&$0.03$&$690$&$67.67$\tabularnewline
+~~Equally within category&$5.22$&$7$&$0.03$&$690$&$67.665$\tabularnewline
 \hline
 \end{tabular}\end{center}}
-\footnotesize *Starting \ac{rmse} $= 72.14$\end{table}
+\footnotesize *Starting \ac{rmse} $= 72.140$\end{table}
 
@@
 Error bars are 95\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.
-Areal extent of estimated hypoxia on August 29\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).}\label{fig:areachg}
+Areal extent of estimated hypoxia on August 28\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).}\label{fig:areachg}
 \end{figure}

### 2017-03-27 ident_manu.Rnw
ident threshold figure gone

@@
 \usepackage{fixltx2e}
-\usepackage[inline]{showlabels}
+% \usepackage[inline]{showlabels}
 
@@
 
-An alternative view of the results in \cref{fig:identplo} can be used to demonstrate the effects of parameter selection criteria and number of parameters in the selection pool on identifiability.
-\Cref{fig:percthresh} shows the percentage of identifiable parameter sets for \ac{do} using the same selection criteria in \cref{fig:identplo}, i.e., selection of parameters only within parameter categories and selection of the top sensitive parameters regardless of category.
-\Cref{fig:percthresh} is similar to \cref{fig:identplo}, with the added effect of a chosen $\gamma$ threshold on identifability.
-Previous studies have provided only general rules for $\gamma$ thresholds \citep{Brun01,Omlin01}, such that exact values for which parameter sets are inestimable likely vary between models and optimization methods.
-As such, multiple values are shown in \cref{fig:percthresh}  given that actual thresholds could vary in practice.
-In general, identifiability decreased with the addition of parameters, although the rate of decrease depended on the selected threshold for $\gamma$.
-More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset, that is, identifiability decreased more quickly with the addition of parameters at lower $\gamma$ thresholds as compared to higher $\gamma$.
-Notable differences in identifiability were also observed by parameter selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
-
 <<eval = T>>=
@@
 
-% percent below gamma thresholds
-<<percthresh, eval = T, fig.cap = 'Percent of identifiable parameter sets for \\ac{do} at different $\\gamma$ thresholds, selection criteria, and total number of parameters in the set.
-Thresholds varied from $\\gamma = 2$ to $20$ such that sets with $\\gamma$ below a threshold were considered identifiable relative to the value.
-Plots in (a) show percent of identifiable sets by selecting parameters within categories and (b) shows percent identifiable by selecting from the top 1 through 4 parameters in all categories.
-Percent identifiable was based on all sets in \\cref{fig:identplo}.', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=
-data(cat_ident_all)
-data(top_ident_all)
-
-# state variable, categories (no temp ident because only one parameter)
-catnms <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Zooplankton')
-toplevs <- paste0('top', 1:4)
-toplabs <- paste('Top', 1:4)
-stts_lev <- c('O2')
-stts_lab <- c('Dissolved Oxygen')
-
-thresh <- seq(2, 20, by = 2)
-
-# percent combos less than gamma 15, 10 by state variable, by parameter category
-# temperature category not evaluated, only one paramaeter
-collcatpers <- lapply(cat_ident_all[stts_lev], function(stvar){
-
-  bystvar <- lapply(stvar[!names(stvar) %in% 'Temperature'], function(x){
-
-    bysets <- split(x, x$N) %>% 
-      lapply(function(sets){
-        colls <- sets$coll
-        sapply(thresh, function(x) 100 * sum(colls < x)/length(colls))
-
-      }) %>% 
-      do.call('rbind', .) %>% 
-      data.frame(
-        nparms = row.names(.), 
-        .
-      ) %>% 
-      mutate(
-        nparms = as.numeric(as.character(nparms))
-      ) %>% 
-      gather('lval', 'perc', -nparms) %>% 
-      mutate(lval = factor(lval, 
-        levels = paste0('X', 1:length(thresh)), 
-        labels = paste0('l', thresh)
-      ))
-    bysets
-
-  }) %>% 
-  reshape2::melt(., id.vars = names(.[[1]])) %>% 
-  rename(Category = L1)
-
-  return(bystvar)
-
-  }) %>% 
-  reshape2::melt(., id.vars = names(.[[1]])) %>% 
-  rename(`State variable` = L1) %>% 
-  mutate(
-    `State variable` = factor(`State variable`, levels = stts_lev, labels = stts_lab),
-    Category = factor(Category, levels = catnms), 
-    Threshold = gsub('^l', '', lval),
-    Threshold = as.numeric(Threshold)
-    )
-
-colltoppers <- lapply(top_ident_all[stts_lev], function(stvar){
-
-  bystvar <- lapply(stvar, function(x){
-
-    bysets <- split(x, x$N) %>% 
-      lapply(function(sets){
-        colls <- sets$coll
-        sapply(thresh, function(x) 100 * sum(colls < x)/length(colls))
-
-      }) %>% 
-      do.call('rbind', .) %>% 
-      data.frame(
-        nparms = row.names(.), 
-        .
-      ) %>% 
-      mutate(
-        nparms = as.numeric(as.character(nparms))
-      ) %>% 
-      gather('lval', 'perc', -nparms) %>% 
-      mutate(lval = factor(lval, 
-        levels = paste0('X', 1:length(thresh)), 
-        labels = paste0('l', thresh)
-      ))
-    bysets
-
-  }) %>% 
-  reshape2::melt(., id.vars = names(.[[1]])) %>% 
-  rename(Category = L1) %>% 
-  filter(!Category %in% 'top5')
-
-  return(bystvar)
-
-  }) %>% 
-  reshape2::melt(., id.vars = names(.[[1]])) %>% 
-  rename(`State variable` = L1) %>% 
-  mutate(
-    `State variable` = factor(`State variable`, levels = stts_lev, labels = stts_lab),
-    Category = factor(Category, levels = toplevs, labels = toplabs), 
-    Threshold = gsub('^l', '', lval),
-    Threshold = as.numeric(Threshold)
-    )
-
-toplo1 <- collcatpers
-toplo2 <- colltoppers
-
-# default theme
-mytheme <- theme_minimal() + 
-  theme(
-    axis.line.x = element_line(), 
-    axis.line.y = element_line(), 
-    axis.title.x = element_blank(), 
-    axis.title.y = element_blank(),
-    axis.ticks.x = element_line(),
-    axis.ticks.y = element_line(),
-    axis.ticks.length = unit(.1, "cm"), 
-    legend.position = 'none'
-  )
-
-lncol <- 'darkgrey'
-sz <- 3
-
-p1 <- ggplot(toplo1, aes(x = nparms, group = lval)) + 
-  geom_line(aes(y = perc), colour = lncol) + 
-  geom_point(aes(y = perc, fill = Threshold), shape = 21, colour = lncol, 
-    size = sz
-    ) + 
-  scale_fill_distiller(palette = "Spectral") +
-  facet_wrap(~ Category, ncol = 1) +
-  mytheme +
-  ggtitle('(a) By parameter category')
-
-p2 <- ggplot(toplo2, aes(x = nparms, group = lval)) + 
-  geom_line(aes(y = perc), colour = lncol) + 
-  geom_point(aes(y = perc, fill = Threshold), shape = 21, colour = lncol, 
-    size = sz
-    ) + 
-  scale_fill_distiller(palette = "Spectral") +
-  facet_wrap(~ Category, ncol = 1) +
-  mytheme +
-  ggtitle('(b) By top parameters, all categories')
-
-pleg <- ggplot(toplo2, aes(x = nparms, group = lval)) + 
-  geom_point(aes(y = perc, fill = Threshold)) + 
-  scale_fill_distiller(palette = "Spectral")
-pleg <- g_legend(pleg)
-
-grid.arrange(
-  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
-  left = 'Percent identifiable sets',
-  pleg, ncol = 2, widths = c(1, 0.2)
-)
-@
-
 % parameter exclusion temp
@@
   geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
-  geom_boxplot(outlier.size = 0.5, size = 0.5) + 
+  geom_boxplot(outlier.size = 0.5, size = 0.4) + 
   facet_wrap(~parm, label = label_parsed, ncol = 2) + 

### 2017-03-27 ident_manu.tex
ident threshold figure gone

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Mar 26 16:14:21 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/ad5c4632bfb7084298ee0ce337870bbac1db811c}{ad5c4632bfb7084298ee0ce337870bbac1db811c}}
+\tnotetext[mytitlenote]{Version: Mon Mar 27 13:44:31 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/52c5bbb2da21e0ecce154b9907a01aab993c8937}{52c5bbb2da21e0ecce154b9907a01aab993c8937}}
 
@@
 Most notably, nitrate was consistently the least identifiable variable (highest overall $\gamma$), whereas \ac{do} was most identifiable.
-
-An alternative view of the results in \cref{fig:identplo} can be used to demonstrate the effects of parameter selection criteria and number of parameters in the selection pool on identifiability.
-\Cref{fig:percthresh} shows the percentage of identifiable parameter sets for \ac{do} using the same selection criteria in \cref{fig:identplo}, i.e., selection of parameters only within parameter categories and selection of the top sensitive parameters regardless of category.
-\Cref{fig:percthresh} is similar to \cref{fig:identplo}, with the added effect of a chosen $\gamma$ threshold on identifability.
-Previous studies have provided only general rules for $\gamma$ thresholds \citep{Brun01,Omlin01}, such that exact values for which parameter sets are inestimable likely vary between models and optimization methods.
-As such, multiple values are shown in \cref{fig:percthresh}  given that actual thresholds could vary in practice.
-In general, identifiability decreased with the addition of parameters, although the rate of decrease depended on the selected threshold for $\gamma$.
-More conservative values for $\gamma$ (e.g., $\gamma = 5$) were more sensitive to the number of parameters in a subset, that is, identifiability decreased more quickly with the addition of parameters at lower $\gamma$ thresholds as compared to higher $\gamma$.
-Notable differences in identifiability were also observed by parameter selection criteria (within categories or top parameters only), which further supports results in \cref{fig:identplo,fig:identploall}.
 
@@
 
-% percent below gamma thresholds
-\begin{figure}[!ht]
-
-{\centering \includegraphics[width=\maxwidth]{figs/percthresh-1}
-
-}
-
-\caption{Percent of identifiable parameter sets for \ac{do} at different $\gamma$ thresholds, selection criteria, and total number of parameters in the set.
-Thresholds varied from $\gamma = 2$ to $20$ such that sets with $\gamma$ below a threshold were considered identifiable relative to the value.
-Plots in (a) show percent of identifiable sets by selecting parameters within categories and (b) shows percent identifiable by selecting from the top 1 through 4 parameters in all categories.
-Percent identifiable was based on all sets in \cref{fig:identplo}.}\label{fig:percthresh}
-\end{figure}
-
 % parameter exclusion temp

### 2017-03-28 ident_manu.Rnw
better draft done

@@
 
+% number of parameters evaluated, total and by category
+<<echo = FALSE>>=
+p1z1pars <- par_tst()
+
+# number of parameters in each category
+nparms <- parcats2(as_df = TRUE) %>% 
+  filter(shrt %in% p1z1pars) %>% 
+  .$cats %>% 
+  table %>% 
+  as.list  
+@
+
 \begin{abstract}
-\noindent This study addresses quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.
-A systematic framework is used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
-In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
+\noindent Local sensitivity analyses and identifiability of parameter subsets were used to describe numerical constraints of a hypoxia model for bottom waters of the northern Gulf of Mexico.
 The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates and less sensitive to physical or chemical parameters.
-Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set were characterized as having unique effects on the model output.
-As a result, we provide a set of parameter selection heuristics that can be used to identify parameters for model calibration that depend on relative sensitivity and ecological categories within the biogeochemical equations.
-Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in evaluations of water quality models.
+Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
+Selecting parameters by decreasing sensitivity demonstrated that only eight of \Sexpr{sum(unlist(nparms))} total parameters had a sufficiently unique effect on model output for accurate calibration.
+As a result, parameter selection heuristics were used to identify parameters for model calibration that depended on combined effects on output, relative sensitivity of each parameter, and ecological categories for the biogeochemical equations.
+The calibrated \ac{zerod} unit of the hypoxia model had improved precision if sensitive parameters were included in an identifiable subset.
+Extension of results to a three-dimensional grid of the Gulf of Mexico showed that sensitive parameters for the \ac{zerod} model translated to non-trivial changes in the areal estimates of hypoxia.
 \end{abstract}
@@
 
-The development and application of a model represents a tradeoff between characteristics expected from the output or provided by the structural components.
-An idealized model is sufficiently generalizable across systems, provides results that are precise given the inputs, and includes components that are realistic descriptions of actual processes \citep{Levins66}.
+The development of a model represents a tradeoff between characteristics expected from the output and information represented by the structural components.
+An ideal model is sufficiently generalizable across systems, provides results that are precise given the inputs, and includes components that are realistic descriptions of actual processes \citep{Levins66}.
 Given that these characteristics cannot be simultaneously achieved, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99,Ganju16}.
@@
 This study describes a parameter sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.
-The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifability constraints.
+The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifiability constraints.
 The specific goals were to \begin{inparaenum}[1\upshape)]
@@
 \end{inparaenum}
+The \ac{zero} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model precision.
+Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability the results.
 In addition to \ac{do}, other state variables that were evaluated included ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.
 In general, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the complete parameter set can be optimized.
-Although concerns of identifiability constraints have been shown in the literature, rulesets are not readily available that define how parameters should be selected given tradeoffs betwen precision, sensitivity, and identifiability, especially for biogeochemical models of ecosystem processes.
 
@@
 The hypoxic area averages 15,540 km$^2$ annually (1993-2015) with minimum concentrations observed from late spring to early fall.
-Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to the formation of hypoxia \citep{Wiseman97,Paerl98,Obenour15}.
+Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to hypoxia formation \citep{Wiseman97,Paerl98,Obenour15}.
 The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
@@
 
-% number of parameters evaluated, total and by category
-<<echo = FALSE>>=
-p1z1pars <- par_tst()
-
-# number of parameters in each category
-nparms <- parcats2(as_df = TRUE) %>% 
-  filter(shrt %in% p1z1pars) %>% 
-  .$cats %>% 
-  table %>% 
-  as.list  
-@
-
-The sensitivity of state variables to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
+The sensitivity of state variables to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep with daily output from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
 Irrelevant parameters were removed for several reasons; parameters were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
@@
 A local sensitivity analysis was performed by evaluating the change in state variables following perturbation of each parameter from its original value \citep{Soetaert10,RDCT17}.
-Parameters were individually perturbed by 50\% of the original values and sensitivity $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
+Parameters were individually perturbed by a 50\% increase of the original values and sensitivity $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
 
@@
 
-Parameter selection for model calibration must consider the competing objectives of increased precision with parameter inclusion and reduced identifability as it relates to optimization.
+Parameter selection for model calibration must consider the competing objectives of increased precision with parameter inclusion and reduced identifiability as it relates to optimization.
 An additional challenge is a large number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., parameters for a group of related structural equations could be of interest).
@@
 A set of heuristics was developed that addresses the tradeoff in model complexity and identifiability given the challenges described above \citep[see also][]{Wagener01}.
-These rulesets were developed with the assumption that parameters will be selected with preference for those with high sensitivity and identifability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
-Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences by model users given questions of interest.
-In all selection scenarios, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
-\item blocked within parameter category,
+These rulesets were developed to select parameters with preference for those with high sensitivity and identifiability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
+Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences by users given desired application of the model.
+For all selection heuristics, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
+\item blocked within each of five parameter categories,
 \item independent of parameter category,
 \item or considering all categories equally.
-\end{inparaenum} The selection rules produced seven subsets of parameters that could further be used to optimize model calibration.
-
-\subsection{Model calibration and extrapolation}
+\end{inparaenum}
+
+\subsection{Model calibration and scalability}
 
@@
 We set the algorithm to search within +/- 50\% of the default parameter values.
-While we recognize that `actual' parameter values could possibly be outside of this range, constraining the values to those tested herein was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
+While we recognize that `actual' parameter values could possibly extend beyond this range, constraining the values to the range tested herein was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
 Moreover, precise limits on each parameter were less of a concern for the current analysis as our primary goal was to demonstrate differences in precision as a function of sensitivity and identifiability.
@@
 
-As a final analysis, effects of parameter changes on the larger 3-dimensional model were evaluated to demonstrate that results from the \ac{zerod} FishTank model can be extrapolated.
+As a final analysis, effects of parameter changes on the larger 3-dimensional model were evaluated to demonstrate that results from the \ac{zerod} FishTank model are scalable.
 For simplicity, only the most sensitive parameter in each category was selected.
 The \ac{cgem} model was run for one year using the default parameter conditions and by increasing each of the selected parameters by 50\%.
-This produced six spatially-referenced time series from which the changes in the daily hypoxic area (number of cells $<$ 64 mmol \ac{do}) were estimated in the nothern \ac{gom}.
+This produced six spatially-referenced time series (one default, five for each parameter change) from which changes in the daily hypoxic area (number of cells $<$ 64 mmol \ac{do}) were estimated.
 
@@
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
-Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
-The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15, 10$ for the top parameter in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the top four.
-Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
+Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifiability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
+The percentage of parameter subsets that were below the acceptable thresholds for identifiability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15, 10$ for the top parameter in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the top four.
+Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiability between state variables was observed (\cref{fig:identploall}).
 Most notably, nitrate was consistently the least identifiable variable (highest overall $\gamma$), whereas \ac{do} was most identifiable.
@@
 
-\subsection{Model calibration and extrapolation}
+\subsection{Model calibration and scalability}
 
@@
 
-Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values (\cref{tab:calib}).
-The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
-The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of parameter category and equally within each category were also evaluated.
+Calibration of parameter values for each of the seven selection heuristics (\cref{tab:heurist1,tab:heurist2,tab:heurist3})  produced model output that varied in precision and computational effort required to identify optimal values (\cref{tab:calib}).
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
 For example, only \Sexpr{toeng(temp$its)[[1]]} iterations were required to optimize the single parameter selected for the temperature category, whereas \Sexpr{top$its} iterations were required for the \Sexpr{toeng(top$nprm)[[1]]} parameters selected independent of category.
-A slight positive assocation between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
-Of the seven parameter subsets, selection independent of category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt}, reduction to \Sexpr{scinot(top$rmse, digits = 3)}, \Sexpr{scinot(cattop$rmse, digits = 3)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse, digits = 3)}).
+A slight positive association between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt}, reduction to \Sexpr{scinot(top$rmse, digits = 3)}, \Sexpr{scinot(cattop$rmse, digits = 3)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse, digits = 3)}).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 
-Common goals in the application of biogeochemical models of ecosystem processes are to \begin{inparaenum}[1\upshape)]
+Common goals in the application of biogeochemical models are to \begin{inparaenum}[1\upshape)]
 \item accurately describe the system by matching predictions with observed data \citep{Reckhow90}, and 
@@
 \end{inparaenum}
-Although these objectives are the focus of most applications, the structural components of process-based models should secondarily provide inference into which ecosystem processes and functions are driving observed changes.
-This latter objective represents a more generic scientific purpose of biogeochemical models that extends beyond the applied benefits of describing and predicting change in a particular system.
-Modelers often hope to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting hypotheses \citep{Kirchner06}.
-Extension of these principles to test the effects of structural changes and observation uncertainty on model predictions provides further information to support validation of model components.
-This study provided a simple approach to use the effects of parameter perturbations on model state variables to characterize identifiable parameter subsets that vary by parameter selection criteria.
-By doing so, we demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiability thresholds described in the literature.
+Although these objectives are the focus of most applications, the structural components and associated parameters of process-based models should secondarily provide insight of ecosystem processes that are driving observed changes.
+This latter objective represents a more generic scientific purpose of modelling that extends beyond the benefits of describing and predicting change.
+Modelers aim to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting hypotheses \citep{Hilborn97,Kirchner06}.
+Accordingly, this study provided a simple approach to use the effects of parameter perturbations on state variables to characterize identifiable parameter subsets that varied by selection criteria.
+By doing so, we provided a simple and preliminary approach towards improved model refinement that begins to address more general purposes of model applications.
+Our specific results demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiability thresholds described in the literature.
 The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
-In general, these results provide justification for the use of explicit parameter selection heuristics that practitioners should adopt to facilitate model calibration.
+Use of identifiable parameter subsets with sensitive parameters improved model precision and results for the smaller model were scalable to the 3-dimensional model.
+In general, these results provide justification for the use of explicit parameter selection heuristics to improve model precision.
 
@@
 These results support previous studies that have suggested similarly small subsets of parameters can be identified using traditional calibration schemes \citep[e.g.,][]{Wheater86,Ye97,Omlin01}.
-In addition to \ac{cgem}, these conclusions have relevance for many biogeochemical models that include numerous parameters and structural equations to characterize processes in the model domain.
-A general conclusion is that perhaps a trend towards less complex models could be beneficial given that only a small subset of parameters is identifiable and that ecosystem processes may in fact be sufficiently characterized with few parameters \citep{Ye97}.
+In addition to \ac{cgem}, these conclusions have relevance for other biogeochemical models that include numerous parameters and structural equations to characterize processes in the model domain.
+A general conclusion is that less complex models could potentially be beneficial given that only a small subset of parameters is identifiable and that ecosystem processes may in fact be sufficiently characterized with few parameters \citep{Ye97}.
 Conversely, others have argued that model complexity is not in itself a disadvantage when parsimony is not the sole arbitrator of model structure \citep{Reichert97}.
@@
 Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude individual parameters.
+For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model precision and that these parameters had affects that translated to the larger model.
 Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
-Similarly, identifability was not always related to the number of parameters in a set.
+Similarly, identifiability was not always related to the number of parameters in a set.
 Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
-For example, \cref{fig:exclex} shows that including \Sexpr{par_txt('KGcdom_1')}, \Sexpr{par_txt('KO2_1')}, or \Sexpr{par_txt('nitmax_1')} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
+For example, \cref{fig:exclex} showed that including \Sexpr{par_txt('KGcdom_1')}, \Sexpr{par_txt('KO2_1')}, or \Sexpr{par_txt('nitmax_1')} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
 These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
@@
 In general, uncertainty analyses that lead to improved models are ultimately expected to increase our understanding of properties defining ecological relationships.
-The extension of simple parameter sensitivity analyses to the generalization of ecosystem properties requires additional analysis and potential model refinement, at the core of which is the balance between generality and precision.
-The utility of a specific model depends on the question and objective for application to a specific system.
+The extension of simple parameter sensitivity analyses to the generalization of ecosystem properties requires additional analysis and model refinement.
+Further, the utility of a specific model depends on the question and objective for application to a specific system.
 For the above analysis, the FishTank model, as part of the larger \ac{cgem} application, was evaluated in the context of hypoxia effects on ecosystem condition and function.
-At the core of the simple model is a set of biogeochemical equations that characterize the system in relation to planktonic groups, nutrient requirements, and water-column metabolism.
 Our results have shown that relatively small subsets of parameters are identifiable given the complexity of the model, and as a result, we have provided a general approach to select parameter subsets depending on the ecological context (i.e., selection by parameter category, selection for specific state variables).
+We further demonstrated the effects of selected subsets on model precision and the potential for scalability to larger spatial-temporal models.
 Thus, the results described above have relevance for further model refinement with the specific goal of better understanding ecological dynamics that moderate hypoxia on the northern \ac{gom}.
@@
 Specific approaches can be used to improve and build on the results presented herein, in addition to the more general considerations above.
-An evaluation of model precision following calibration with relevant parameter subsets could provide additional information that supports results from the sensitivity analyses.
-For simplicity, our analysis did not calibrate model parameters and an explicit assumption was that parameter subsets with $\gamma$ below 10 or 15 were identifiable.
-To our knowledge, this threshold has not been rigorously evaluated and it is likely to vary between parameter subsets and the chosen calibration method.
-Variation in parameter estimates given the calibration method and different identifiability thresholds could affect the interpration of model output.
-Further, how results for the \ac{zerod} model extrapolate to the larger three-dimensional model should be evaluated.
-Although the above analyses were facilitated using the \ac{zerod} model (i.e, quick execution times, ease of changing model parameters), lack of physical transport or spatial components potentially limits extrapolation of the results.
-Variation in parameter estimates at lower dimensions could be magnified as errors propagate to larger scales or site-specific observations for model calibration are not appropriate across a hydrodynamic grid \citep{Harvey00,Lehrter10}.
-The effects of structural or observational uncertainty should also be evaluated in the context of the larger model.
-Our simple approach to examine changes in the initial conditions and switches used in the model showed that sensitivity estimates of individual parameters differed relative to the original model configuration, having further implications for characterizing identifiability.
+The effects of structural or observational uncertainty could be evaluated as an extension of the analyses presented above.
+For example, the sensitivity of \ac{do} to variation in the half-saturation constants for phytoplankton (the concentration supporting half the maximum uptake rate of nutrients) could vary given the initial nutrient concentrations \citep{Eppley69}.
+Further, changes in the ratio between nitrogen and phosphorus could affect the sensitivity of state variables to parameter changes depending on the limiting nutrient.
+A more challenging analysis is an evaluation of the effects of structural components on model output, which requires exclusion or inclusion of explicit biogeochemical equations.
+Fortunately, the FishTank model includes several `switches' that allow users to change the governing equations that estimate state variables, such as switches that `turn on' different structural equations for light attenuation in the water column.
+This design is uncommon in biogeochemical models and could be leveraged for an evaluation of structural uncertainty.
+As such, our analysis of parameter sensitivity and identifiabilty could be combined with an evaluation of observational and structural uncertainty for a more complete characterization of the model, having implications for understanding drivers of hypoxia in coastal waters.
+
 \clearpage

### 2017-03-28 ident_manu.tex
better draft done

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Mon Mar 27 13:44:31 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/52c5bbb2da21e0ecce154b9907a01aab993c8937}{52c5bbb2da21e0ecce154b9907a01aab993c8937}}
+\tnotetext[mytitlenote]{Version: Mon Mar 27 15:12:15 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/2fbaaefe9317f286aa11b3f3fe425ff27a551ad5}{2fbaaefe9317f286aa11b3f3fe425ff27a551ad5}}
 
@@
 
+% number of parameters evaluated, total and by category
+
 \begin{abstract}
-\noindent This study addresses quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.
-A systematic framework is used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.
-In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.
+\noindent Local sensitivity analyses and identifiability of parameter subsets were used to describe numerical constraints of a hypoxia model for bottom waters of the northern Gulf of Mexico.
 The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates and less sensitive to physical or chemical parameters.
-Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set were characterized as having unique effects on the model output.
-As a result, we provide a set of parameter selection heuristics that can be used to identify parameters for model calibration that depend on relative sensitivity and ecological categories within the biogeochemical equations.
-Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in evaluations of water quality models.
+Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
+Selecting parameters by decreasing sensitivity demonstrated that only eight of 51 total parameters had a sufficiently unique effect on model output for accurate calibration.
+As a result, parameter selection heuristics were used to identify parameters for model calibration that depended on combined effects on output, relative sensitivity of each parameter, and ecological categories for the biogeochemical equations.
+The calibrated \ac{zerod} unit of the hypoxia model had improved precision if sensitive parameters were included in an identifiable subset.
+Extension of results to a three-dimensional grid of the Gulf of Mexico showed that sensitive parameters for the \ac{zerod} model translated to non-trivial changes in the areal estimates of hypoxia.
 \end{abstract}
@@
 
-% number of parameters evaluated, total and by category
-
-The sensitivity of state variables to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
+The sensitivity of state variables to perturbations of all relevant parameters for the 108 equations was estimated using a five minute timestep with daily output from January 1\textsuperscript{st} to December 31\textsuperscript{st}, 2006.
 Irrelevant parameters were removed for several reasons; parameters were not relevant for the \ac{zerod} model (i.e., hydrodynamic parameters), were considered physical constants, or had no effect given initial conditions.
@@
 Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).
-Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
-The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15, 10$ for the top parameter in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the top four.
-Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).
+Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifiability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).
+The percentage of parameter subsets that were below the acceptable thresholds for identifiability was $100$\% less than $\gamma = 15, 10$ for the top parameter in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the top four.
+Results for the remaining state variables had similar patterns in identifiability with increasing size of parameter subsets and selection categories, although differences in identifiability between state variables was observed (\cref{fig:identploall}).
 Most notably, nitrate was consistently the least identifiable variable (highest overall $\gamma$), whereas \ac{do} was most identifiable.
@@
 
-\subsection{Model calibration and extrapolation}
-
-Calibration of parameter values for each of the seven selection heuristics produced model output that varied in precision and computational effort to identify optimal values (\cref{tab:calib}).
-The seven evaluated subsets were those for \ac{do} in each of the four categories of parameters in \cref{tab:heurist1}, including the single parameter for temperature.
-The subsets in \cref{tab:heurist2,tab:heurist3} for the parameters selected independent of parameter category and equally within each category were also evaluated.
+\subsection{Model calibration and scalability}
+
+Calibration of parameter values for each of the seven selection heuristics (\cref{tab:heurist1,tab:heurist2,tab:heurist3})  produced model output that varied in precision and computational effort required to identify optimal values (\cref{tab:calib}).
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
 For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 850 iterations were required for the eight parameters selected independent of category.
-A slight positive assocation between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
-Of the seven parameter subsets, selection independent of category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$, reduction to $67.052$, $67.665$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.139$).
+A slight positive association between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$, reduction to $67.052$, $67.665$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.139$).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude individual parameters.
+For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model precision and that these parameters had affects that translated to the larger model.
 Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
-Similarly, identifability was not always related to the number of parameters in a set.
+Similarly, identifiability was not always related to the number of parameters in a set.
 Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
-For example, \cref{fig:exclex} shows that including \textit{KGcdom}, \textit{KO2}, or \textit{nitmax} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
+For example, \cref{fig:exclex} showed that including \textit{KGcdom}, \textit{KO2}, or \textit{nitmax} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
 These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.

### 2017-03-28 ident_manu.Rnw
updated bib with shrt journal names

@@
 \begin{abstract}
-\noindent Local sensitivity analyses and identifiability of parameter subsets were used to describe numerical constraints of a hypoxia model for bottom waters of the northern Gulf of Mexico.
+\noindent Local sensitivity analyses and identifiable parameter subsets were used to describe numerical constraints of a hypoxia model for bottom waters of the northern Gulf of Mexico.
 The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates and less sensitive to physical or chemical parameters.
 Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
-Selecting parameters by decreasing sensitivity demonstrated that only eight of \Sexpr{sum(unlist(nparms))} total parameters had a sufficiently unique effect on model output for accurate calibration.
+Selecting parameters by decreasing sensitivity demonstrated that only eight of \Sexpr{sum(unlist(nparms))} total parameters had a sufficiently unique effect on model output for precise calibration.
 As a result, parameter selection heuristics were used to identify parameters for model calibration that depended on combined effects on output, relative sensitivity of each parameter, and ecological categories for the biogeochemical equations.
@@
 \end{inparaenum}
-The \ac{zero} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model precision.
+The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model precision.
 Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability the results.
@@
   .[length(.)] %>% 
-  scinot(., digits = 3)
+  scinot(.)
 # 72.13955
@@
 For example, only \Sexpr{toeng(temp$its)[[1]]} iterations were required to optimize the single parameter selected for the temperature category, whereas \Sexpr{top$its} iterations were required for the \Sexpr{toeng(top$nprm)[[1]]} parameters selected independent of category.
-A slight positive association between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt}, reduction to \Sexpr{scinot(top$rmse, digits = 3)}, \Sexpr{scinot(cattop$rmse, digits = 3)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse, digits = 3)}).
+No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt}, reduction to \Sexpr{scinot(top$rmse)}, \Sexpr{scinot(cattop$rmse)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse)}).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 
-\bibliography{refs}
-% \bibliography{refsshr}
+% \bibliography{refs}
+\bibliography{refsshr}
 \clearpage
@@
     nprm = sapply(nprm, scinot),
-    its = sapply(its, scinot),
-    rmse = sapply(rmse, scinot, digits = 3), 
+    its = paste0('$', its, '$'),
+    rmse = sapply(rmse, scinot), 
     avee = sapply(avee, scinot)

### 2017-03-28 ident_manu.tex
updated bib with shrt journal names

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Mon Mar 27 15:12:15 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/2fbaaefe9317f286aa11b3f3fe425ff27a551ad5}{2fbaaefe9317f286aa11b3f3fe425ff27a551ad5}}
+\tnotetext[mytitlenote]{Version: Tue Mar 28 09:22:53 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/2cadbba32f41563b26f352a0842ad2eea3b78910}{2cadbba32f41563b26f352a0842ad2eea3b78910}}
 
@@
 \begin{abstract}
-\noindent Local sensitivity analyses and identifiability of parameter subsets were used to describe numerical constraints of a hypoxia model for bottom waters of the northern Gulf of Mexico.
+\noindent Local sensitivity analyses and identifiable parameter subsets were used to describe numerical constraints of a hypoxia model for bottom waters of the northern Gulf of Mexico.
 The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates and less sensitive to physical or chemical parameters.
 Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
-Selecting parameters by decreasing sensitivity demonstrated that only eight of 51 total parameters had a sufficiently unique effect on model output for accurate calibration.
+Selecting parameters by decreasing sensitivity demonstrated that only eight of 51 total parameters had a sufficiently unique effect on model output for precise calibration.
 As a result, parameter selection heuristics were used to identify parameters for model calibration that depended on combined effects on output, relative sensitivity of each parameter, and ecological categories for the biogeochemical equations.
@@
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
-For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 850 iterations were required for the eight parameters selected independent of category.
-A slight positive association between collinearity ($\gamma$) and number of iterations was also observed, such that computational effort  to identify optimal values for a parameter set increased with lower identifiability (higher $\gamma$).
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$, reduction to $67.052$, $67.665$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.139$).
+For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 1530 iterations were required for the eight parameters selected independent of category.
+No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$, reduction to $66.77$, $67.44$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.12$).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 {\bfseries 1}&&&&&\tabularnewline
-~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$14$&$72.139$\tabularnewline
-~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$154$&$68.701$\tabularnewline
-~~Phytoplankton&$3.97$&$7$&$0.02$&$270$&$68.722$\tabularnewline
-~~Temperature&$1$&$1$&$0.02$&$6$&$71.759$\tabularnewline
-~~Zooplankton&$5.2$&$4$&$0.03$&$99$&$71.223$\tabularnewline
+~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$49$&$72.12$\tabularnewline
+~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$154$&$68.7$\tabularnewline
+~~Phytoplankton&$3.97$&$7$&$0.02$&$1725$&$68.3$\tabularnewline
+~~Temperature&$1$&$1$&$0.02$&$6$&$71.76$\tabularnewline
+~~Zooplankton&$5.2$&$4$&$0.03$&$279$&$71.22$\tabularnewline
 \hline
 {\bfseries 2}&&&&&\tabularnewline
-~~Independent of category&$6.81$&$8$&$0.03$&$850$&$67.052$\tabularnewline
+~~Independent of category&$6.81$&$8$&$0.03$&$1530$&$66.77$\tabularnewline
 \hline
 {\bfseries 3}&&&&&\tabularnewline
-~~Equally within category&$5.22$&$7$&$0.03$&$690$&$67.665$\tabularnewline
+~~Equally within category&$5.22$&$7$&$0.03$&$1005$&$67.44$\tabularnewline
 \hline

### 2017-03-28 ident_manu.Rnw
fig 1 schematic added

@@
 The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates and less sensitive to physical or chemical parameters.
-Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
+Variation in sensitivity had a direct correspondence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
 Selecting parameters by decreasing sensitivity demonstrated that only eight of \Sexpr{sum(unlist(nparms))} total parameters had a sufficiently unique effect on model output for precise calibration.
@@
 These events are detrimental to aquatic organisms and have significant negative effects on economic resources derived from coastal ecosystems \citep{Lipton03,Diaz11}.
-An understanding of the biological, physical, and chemical processes that contribute to the growth of hypoxic areas is a critical concern for mitigating and preventing these negative impacts.
+An understanding of the biological, physical, and chemical processes that influence hypoxic areas is a critical concern for mitigating and preventing these negative impacts.
 Numerical ecosystem models are important tools that synthesize knowledge of ecosystem processes that contribute to hypoxia formation and for predicting the effects of proposed management activities or future scenarios \citep{Scavia04,Hagy07,Pauer16}.
@@
 Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to hypoxia formation \citep{Wiseman97,Paerl98,Obenour15}.
-The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
+The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep[\cref{fig:mod_schem},][]{Eldridge10}.
 The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf.
@@
 \invisiblesection{Figure}
+
+% model schematic
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{figs/mod_schem.png}
+\caption{Conceptual representation of biogeochemical components for \ac{do} and carbon dioxide modelled in \ac{cgem} (complete equations \citealt{Eldridge10}).
+FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
+\label{fig:mod_schem}
+\end{figure}
 

### 2017-03-28 ident_manu.tex
fig 1 schematic added

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue Mar 28 09:22:53 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/2cadbba32f41563b26f352a0842ad2eea3b78910}{2cadbba32f41563b26f352a0842ad2eea3b78910}}
+\tnotetext[mytitlenote]{Version: Tue Mar 28 14:41:10 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/e933435a9f4d7e068be7e4cc2ed6c72de4df0fb7}{e933435a9f4d7e068be7e4cc2ed6c72de4df0fb7}}
 
@@
 The sensitivity of state variables differed considerably with parameter changes, although most variables were responsive to changes in parameters that influenced planktonic growth rates and less sensitive to physical or chemical parameters.
-Variation in sensitivity had a direct correspendence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
+Variation in sensitivity had a direct correspondence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
 Selecting parameters by decreasing sensitivity demonstrated that only eight of 51 total parameters had a sufficiently unique effect on model output for precise calibration.
@@
 
+% model schematic
+\begin{figure}
+\centering
+\includegraphics[width=0.7\textwidth]{figs/mod_schem.png}
+\caption{Conceptual representation of biogeochemical components for \ac{do} and carbon dioxide modelled in \ac{cgem} (complete equations \citealt{Eldridge10}).
+FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
+\label{fig:mod_schem}
+\end{figure}
+
 % combination example

### 2017-03-29 ident_manu.tex
better schematic added

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue Mar 28 14:41:10 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/e933435a9f4d7e068be7e4cc2ed6c72de4df0fb7}{e933435a9f4d7e068be7e4cc2ed6c72de4df0fb7}}
+\tnotetext[mytitlenote]{Version: Tue Mar 28 17:29:18 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/55035672775b152721843109c2926082eceeba21}{55035672775b152721843109c2926082eceeba21}}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{figs/mod_schem.png}
-\caption{Conceptual representation of biogeochemical components for \ac{do} and carbon dioxide modelled in \ac{cgem} (complete equations \citealt{Eldridge10}).
+\includegraphics[width=0.7\textwidth]{figs/mod_schem.pdf}
+\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations \citealt{Eldridge10}).
 FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}

### 2017-04-09 ident_manu.Rnw
better schematic added
cover letter added

@@
-\documentclass[preprint]{elsarticle}
+\documentclass[review]{elsarticle}
 \usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
@@
 
-\linespread{1.5}
+\linespread{2}
 
@@
 \begin{document}
+\large
 
@@
 
-This study describes a parameter sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.
+This study describes a sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.
 The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifiability constraints.

### 2017-04-09 ident_manu.tex
cover letter added

@@
-\documentclass[preprint]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[review]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth
@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue Mar 28 17:29:18 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/55035672775b152721843109c2926082eceeba21}{55035672775b152721843109c2926082eceeba21}}
+\tnotetext[mytitlenote]{Version: Wed Mar 29 18:01:37 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/82b584d191ce9aa05d1adeff4e6db4a8a38db9e2}{82b584d191ce9aa05d1adeff4e6db4a8a38db9e2}}
 

### 2017-04-10 ident_manu.Rnw
minor edits from LL

@@
 Parameter values were searched using the optim function in R that implemented the limited memory modification of the BFGS quasi-Newton method \citep{Byrd95,Nocedal06,RDCT17}.
-This opimization scheme searches for values within the user-defined lower and upper bounds of each parameter.
+This optimization scheme searches for values within the user-defined lower and upper bounds of each parameter.
 We set the algorithm to search within +/- 50\% of the default parameter values.
@@
 An increase in the growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} in the water column.
-Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter.
+Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter from algal sources.
 Most variables were also sensitive to variation in the half-saturation grazing coefficient which moderates the concentration of nutrients that support half the maximum grazing rate.

### 2017-04-10 ident_manu.tex
minor edits from LL

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Wed Mar 29 18:01:37 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/82b584d191ce9aa05d1adeff4e6db4a8a38db9e2}{82b584d191ce9aa05d1adeff4e6db4a8a38db9e2}}
+\tnotetext[mytitlenote]{Version: Sun Apr 9 11:59:44 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/452af951d19edb6129949898f5923b6e48c0ff26}{452af951d19edb6129949898f5923b6e48c0ff26}}
 

### 2017-04-10 ident_manu.Rnw
submitted to ecomod

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{\Sexpr{vers}}
+\tnotetext[mytitlenote]{\Sexpr{vers}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 
-\linenumbers
+% \linenumbers
 \acresetall
@@
 
-\section{Methods}
+\section{Materials and Methods}
 
@@
 
+\section*{Acknowledgments}
+
+We thank the research staff of the USEPA Gulf Ecology Division, Environmental Modeling and Visualization Laboratory, and Naval Research Laboratory for their efforts developing the hydrodynamic and biogeochemical components of \ac{cgem}.
+
+\section*{Role of Funding Sources}
+
+This study was funded, reviewed, and approved for publication by the US EPA, National Health and Environmental Effects Research Laboratory.
+However, the views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the US EPA.
+
 \clearpage
@@
 \includegraphics[width=0.7\textwidth]{figs/mod_schem.pdf}
-\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations \citealt{Eldridge10}).
+\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations in \citealt{Eldridge10}).
 FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
@@
 Error bars are 95\\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.
-Areal extent of estimated hypoxia on August 28\\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = "\\textwidth">>=
+Areal extent of estimated hypoxia on August 28\\textsuperscript{th} using the default parameters (grey) and estimated changes with parameter perturbations is shown in (e).', fig.height = 7, fig.width = 7, echo = F, cache = TRUE, out.width = "\\textwidth">>=
 # ##

### 2017-04-10 ident_manu.tex
submitted to ecomod

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Apr 9 11:59:44 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/452af951d19edb6129949898f5923b6e48c0ff26}{452af951d19edb6129949898f5923b6e48c0ff26}}
+\tnotetext[mytitlenote]{Version: Mon Apr 10 12:57:29 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/cb605034ebf62786fb3f412f99538ccdf606ffa4}{cb605034ebf62786fb3f412f99538ccdf606ffa4}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 As such, our analysis of parameter sensitivity and identifiabilty could be combined with an evaluation of observational and structural uncertainty for a more complete characterization of the model, having implications for understanding drivers of hypoxia in coastal waters.
+
+\section*{Acknowledgments}
+
+We thank the research staff of the USEPA Gulf Ecology Division, Environmental Modeling and Visualization Laboratory, and Naval Research Laboratory for their efforts developing the hydrodynamic and biogeochemical components of \ac{cgem}.
+
+\section*{Role of Funding Sources}
+
+This study was funded, reviewed, and approved for publication by the US EPA, National Health and Environmental Effects Research Laboratory.
+However, the views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the US EPA.
 
@@
 Error bars are 95\% confidence intervals for the monthly averages in (b) and the difference in monthly averages (d) from the perturbed and default results.
-Areal extent of estimated hypoxia on August 28\textsuperscript{th} using the defaulat parameters (grey) and estimated changes with parameter perturbations is shown in (e).}\label{fig:areachg}
+Areal extent of estimated hypoxia on August 28\textsuperscript{th} using the default parameters (grey) and estimated changes with parameter perturbations is shown in (e).}\label{fig:areachg}
 \end{figure}

### 2017-05-02 ident_manu.Rnw
beth comments

@@
 We thank the research staff of the USEPA Gulf Ecology Division, Environmental Modeling and Visualization Laboratory, and Naval Research Laboratory for their efforts developing the hydrodynamic and biogeochemical components of \ac{cgem}.
+We thank James Pauer, Yonghsan Wan, and Susan Elizabeth George for providing helpful comments on an earlier draft.
 
@@
 
-% effects of changing initial and structural conditions
+% sensitivity heat map
 <<sensalltile, fig.cap = 'Sensitivity values (L1, \\cref{l1}) of all state variables to changes in a 50\\% increase in parameter values.
@@
   geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = lncol) + 
-  geom_point(aes(y = ave, shape = 'Ave', fill = 'Ave'), colour = lncol, size = sz) + 
-  geom_point(aes(y = med, shape = 'Med', fill = 'Med'), colour = lncol, size = sz) + 
-  scale_shape_manual(name = '', labels = c('Ave', 'Med'), values = c(21, 24)) + 
-  scale_fill_manual(name = '', labels = c('Ave', 'Med'), values = cols[c(5, 3)]) +
+  geom_point(aes(y = ave, shape = 'Average', fill = 'Average'), colour = lncol, size = sz) + 
+  geom_point(aes(y = med, shape = 'Median', fill = 'Median'), colour = lncol, size = sz) + 
+  scale_shape_manual(name = '', labels = c('Average', 'Median'), values = c(21, 24)) + 
+  scale_fill_manual(name = '', labels = c('Average', 'Median'), values = cols[c(5, 3)]) +
   facet_wrap(~ npercat, ncol = 1, scales = 'free_y') +

### 2017-05-02 ident_manu.tex
beth comments

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Mon Apr 10 12:57:29 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/cb605034ebf62786fb3f412f99538ccdf606ffa4}{cb605034ebf62786fb3f412f99538ccdf606ffa4}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Mon Apr 10 15:30:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/0f86dadf816bb11046b5ad72f427002e17bf4cef}{0f86dadf816bb11046b5ad72f427002e17bf4cef}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 
-% effects of changing initial and structural conditions
+% sensitivity heat map
 \begin{figure}[!ht]

### 2017-07-31 revision/review_response.Rnw
review response template

\documentclass[letterpaper,12pt]{article}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{indentfirst}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[final]{animate}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{array}
\usepackage{subfig} 
\usepackage[noae]{Sweave}
\usepackage{cleveref}
\usepackage[figureposition=bottom]{caption}
\usepackage{paralist}
\usepackage{acronym}
\usepackage{outlines}
\usepackage{amsmath}

%acronyms
% \acrodef{}{}

%knitr options
<<setup, cache = F, echo = F>>=
# set global chunk options
opts_chunk$set(fig.align = 'center', message = F, dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F, echo = F)
options(replace.assign=TRUE,width=90,digits=1)
@

\setlength{\parskip}{5mm}
\setlength{\parindent}{0in}

\newcommand{\Bigtxt}[1]{\textbf{\textit{#1}}}

\begin{document}
\raggedright

% \title{}
% \author{}
% \maketitle

{\it Response to reviewer comments ``Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in teh northern Gulf of Mexico'', Beck, MW, Lehrter, JC, Lowe, LL, Jarvis BM.}

{\it We thank the editor and review for providing thoughtful comments on our manuscript.  Responses to these comments are shown in italics.  Page and paragraph numbers refer to the revised manuscript.}

\Bigtxt{Editor's comments:}

The authors executed the work on parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern Gulf of Mexico. The authors did not provide proper conceptual diagram of the model.  The model is not presented in detail, it is necessary to give more details on original model. Discussion part is unnecessary long, lot of introduction in the discussion. This part needs major revisions and complete restructure. The sensitivity analysis was adequately implemented but further clarification is needed for how the water quality model was applied in Weeks Bay. In view of the above comments and reports of reviewers, your manuscript has been evaluated and you are informed to resubmit the manuscript after proper and thorough revisions in accordance with the comments of editor/reviewers. Review reports are appended below. Thank you for your submission in Ecological Modelling.

\Bigtxt{Reviewer 1:}

The authors present the sensitivity analysis of a 0-Dimensional biochemical model implemented in Weeks Bay Alabama. The authors evaluated the sensitivity of the model predictions of DO, ammonium, nitrate, chl-a and irradiance to perturbations in several model parameters. In general, the theoretical basis of the sensitivity analysis is very interesting and mathematically sound and the use of the collinearity index (Eq. 3) to explore linear correlations between parameters seems to be very useful to help identify the most important parameters controlling the model performance (in terms of goodness of fit to observed datasets). The paper can be accepted pending major revisions.

My main concern with the manuscript is that while the application of the sensitivity analysis to the FishTank model seems ok, the application of the FishTank model to Weeks Bay, AL is weak and not convincing. First of all, a correct representation of the advective and dispersive transport is critical to be able to capture the fate and transport of water quality in an estuary. Without a correct representation of transport it is almost impossible to be able to obtain a predictive water quality model. The FishTank model in this case neglects all modes of transport in Weeks Bay, AL and therefore assume the estuary is like a bathtub. This is obviously incorrect and represents a clear limitation of the paper.

For the sensitivity analysis the authors manipulated the observations of DO in the estuary filtering the tidal impacts to be able to implement the FishTank model. However, there is no evidence of the resulting time series of DO or of the other variables analyzed. I am concerned that while removing the DO variations due to tidal cycles, the authors could have also removed the daily variation of DO which can be associated to diurnal cycles of sunlight and temperature. If this is the case, then the DO calibration is based almost on synthetic and unrealistic DO data. The authors must include a section showing the data that was used for the calibration analysis. This section should include a location figure showing Weeks Bay, AL, the stations used to extract the original datasets, plots of the unprocessed and processed time series of DO, ammonium, nitrate, chl-a and irradiance as well as plots showing the processed data against the calibrated model outputs for each variable. The authors must also include a table with the calibrated parameter values. This information is standard in all modeling studies.

Please also describe what are the forcing conditions of the FishTank model. There are two tributary rivers in Weeks Bay and one outlet condition. How is each one simulated in your FishTank model?.

Other comments:

Introduction. I suggest the authors to include also references of couple hydrodynamic and water quality studies available in the region. For example, the work of Camacho et al. (2014a) in St. Louis Bay, MS and part of Mississippi Sound is a relevant citation that is missing in this investigation. The work of Dortch et al. (2007) in Mississippi Sound should also be cited. Sensitivity analyses have also been conducted in the past in the region. For example, Camacho et al (2014b) conducted an uncertainty and sensitivity analysis of a hydrodynamic model of Weeks Bay Alabama. I suggest the authors to include these references. The sensitivity estimates provided by Camacho et al. (2014b) seem to be based on the same equation Eq. (1) included in this manuscript. Can the authors briefly indicate (perhaps one or two sentences) if both methods are the same?

lines 24 - 39 page 3. This part of the text is full of vague statements. Please be more explicit. What are the ``characteristics expected from the output'' and the ``information represented by the structural components''. What do you mean with ``Given that these characteristics cannot be simultaneously achieved, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other''.

lines 24 - 39 page 3. I think the reference Levins (1966) is extremely old and must be removed.

It is interesting to see that the authors constantly use the term ``precision'' to denote goodness of fit. In general, precision is used to denote the number of digits of a number. Note that a number can be precise but inaccurate. I suggest the authors to revise the text and replace ``precision'' with a better term to denote goodness of fit. e.g. level of agreement between observations and simulations.

Line 9 page 10. Selection or Selected?

Line 4 page 12. what are the default parameter conditions?. You should include a table with the default parameter values and parameter values under 50\% modified conditions.

Lines 29-30 page 16. Please include the units in the reported RMSEs. mmol O2?

References

Camacho, R. A., Martin, J. L., Watson, B., Paul, M. J., Zheng, L., \& Stribling, J. B. (2014a). Modeling the factors controlling phytoplankton in the St. Louis Bay estuary, Mississippi and evaluating estuarine responses to nutrient load modifications. Journal of Environmental Engineering, 141(3), 04014067.

Camacho, R. A., Martin, J. L., Diaz-Ramirez, J., McAnally, W., Rodriguez, H., Suscy, P., \& Zhang, S. (2014b). Uncertainty analysis of estuarine hydrodynamic models: an evaluation of input data uncertainty in the weeks bay estuary, alabama. Applied Ocean Research, 47, 138-153.

Dortch M. S., Zakikhani M, Noel M.R, and Kim S. C (2007). Application of a Water Quality Model to Mississippi Sound to Evaluate Impacts of Freshwater Diversions.

\end{document}

### 2017-07-31 revision/review_response.tex
review response template

--- 2017-07-31 revision/review_response.Rnw
@@
-\documentclass[letterpaper,12pt]{article}
+\documentclass[letterpaper,12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
@@
 %knitr options
-<<setup, cache = F, echo = F>>=
-# set global chunk options
-opts_chunk$set(fig.align = 'center', message = F, dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F, echo = F)
-options(replace.assign=TRUE,width=90,digits=1)
-@
 
@@
 \newcommand{\Bigtxt}[1]{\textbf{\textit{#1}}}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}

### 2017-07-31 ident_manu.tex
review response template

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Mon Apr 10 15:30:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/0f86dadf816bb11046b5ad72f427002e17bf4cef}{0f86dadf816bb11046b5ad72f427002e17bf4cef}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Tue May 2 09:04:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/eedd4b1c3c2a4bd984b414a5b3fc28e9845d2d88}{eedd4b1c3c2a4bd984b414a5b3fc28e9845d2d88}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 

### 2017-08-01 revision/review_response.Rnw
revisions half way done

@@
 
-{\it Response to reviewer comments ``Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in teh northern Gulf of Mexico'', Beck, MW, Lehrter, JC, Lowe, LL, Jarvis BM.}
+{\it Response to reviewer comments ``Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern Gulf of Mexico'', Beck MW, Lehrter JC, Lowe LL, Jarvis BM.}
 
-{\it We thank the editor and review for providing thoughtful comments on our manuscript.
+{\it We thank the editor and reviewer for providing thoughtful comments on our manuscript.
 Responses to these comments are shown in italics.
@@
 The authors did not provide proper conceptual diagram of the model.
+
+{\it }
+
 The model is not presented in detail, it is necessary to give more details on original model.
-Discussion part is unnecessary long, lot of introduction in the discussion.
-This part needs major revisions and complete restructure.
+
+{\it }
+
+Discussion part is unnecessary long, lot of introduction in the discussion. This part needs major revisions and complete restructure.
+
+{\it The discussion was shortened and introductory material was removed.
+Specifically, the first paragraph of the discusison was removed and the first paragraph of sec.
+4.1 was shortened.
+This reduced the length by over a page.}
+
 The sensitivity analysis was adequately implemented but further clarification is needed for how the water quality model was applied in Weeks Bay.
+
+{\it }
+
 In view of the above comments and reports of reviewers, your manuscript has been evaluated and you are informed to resubmit the manuscript after proper and thorough revisions in accordance with the comments of editor/reviewers.
@@
 (2007) in Mississippi Sound should also be cited.
+
+{\it Citations for Dortch et al. 2007 and Camacho et al. 2014a were added to the first paragraph.}
+
 Sensitivity analyses have also been conducted in the past in the region.
@@
 
+{\it Yes, this approach is similarly described by Camacho et al.
+2014b.
+The following text was added to paragraph one in sec.
+2.2: `This approach is described as a First Order Variance Analysis that linearly propagates changes from model parameters to model predictions (Camacho et al.
+2014b).'}
+
 lines 24 - 39 page 3.
@@
 
+{\it This section was revised as follows:
+
+`The development of a model represents a tradeoff between achieving predictive accuracy and a realistic representation of environmental processes....
+Given that these characteristics cannot be simultaneously achieved, models are developed that balance predictive accuracy with environmental realism, often favoring one at the expense of the other.'
+
+}
+
 lines 24 - 39 page 3. I think the reference Levins (1966) is extremely old and must be removed.
+
+{\it This citation was referenced in Ganju et al.
+2016, from which this information was obtained.
+We have not removed the citation because we feel that age does not make a publication inadequate.
+However, we have added the citation to Ganju et al.
+2016 as a more current reference.}
 
@@
 
+{\it We have found that precision is commonly used in the literature to describe goodness of fit, although we appreciate the distinction made by the reviewer.
+Considering an example where observed data represent a biased sample of an environmental process (e.g., infrequent or unevent sampling of an event that varies over time), model calibration to these data can only possibly achieve precision.
+Although practitioners would not knowingly use observed data that are biased for model calibration, we are certain that many ecological datasets are incomplete representations of actual processes.
+We argue then that model calibration in many cases is better described as seeking precision, although in practice it is stated as predictive accuracy given an incomplete knowledge of the observed data relative to the true environmental process.
+Regardless, we have replaced precision with ``goodness of fit'' or ``fit'' as a more generic term.}
+
 Line 9 page 10. Selection or Selected?
+
+{\it Changed to: `Heurestics for parameter selection also recognized...'}
 
@@
 
-References
-
-Camacho, R.
-A., Martin, J.
-L., Watson, B., Paul, M.
-J., Zheng, L., \& Stribling, J.
-B.
-(2014a).
-Modeling the factors controlling phytoplankton in the St.
-Louis Bay estuary, Mississippi and evaluating estuarine responses to nutrient load modifications.
-Journal of Environmental Engineering, 141(3), 04014067.
-
-Camacho, R.
-A., Martin, J.
-L., Diaz-Ramirez, J., McAnally, W., Rodriguez, H., Suscy, P., \& Zhang, S.
-(2014b).
-Uncertainty analysis of estuarine hydrodynamic models: an evaluation of input data uncertainty in the weeks bay estuary, alabama.
-Applied Ocean Research, 47, 138-153.
-
-Dortch M. S., Zakikhani M, Noel M.R, and Kim S. C (2007). Application of a Water Quality Model to Mississippi Sound to Evaluate Impacts of Freshwater Diversions.
+{\it RMSE units are reported as mmol o2 m-3 and was added to the text.}
 

### 2017-08-01 ident_manu.Rnw
revisions half way done

@@
 
-# library(Jabbrev)
+# # library(Jabbrev)
 # bbl_ext('ident_manu.bbl', 'refs.bib', 'ident_manu.bib')
@@
 Variation in sensitivity had a direct correspondence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
-Selecting parameters by decreasing sensitivity demonstrated that only eight of \Sexpr{sum(unlist(nparms))} total parameters had a sufficiently unique effect on model output for precise calibration.
+Selecting parameters by decreasing sensitivity demonstrated that only eight of \Sexpr{sum(unlist(nparms))} total parameters had a sufficiently unique effect on model output for accurate calibration.
 As a result, parameter selection heuristics were used to identify parameters for model calibration that depended on combined effects on output, relative sensitivity of each parameter, and ecological categories for the biogeochemical equations.
-The calibrated \ac{zerod} unit of the hypoxia model had improved precision if sensitive parameters were included in an identifiable subset.
+The calibrated \ac{zerod} unit of the hypoxia model had improved fit to the observed data if sensitive parameters were included in an identifiable subset.
 Extension of results to a three-dimensional grid of the Gulf of Mexico showed that sensitive parameters for the \ac{zerod} model translated to non-trivial changes in the areal estimates of hypoxia.
@@
 An understanding of the biological, physical, and chemical processes that influence hypoxic areas is a critical concern for mitigating and preventing these negative impacts.
-Numerical ecosystem models are important tools that synthesize knowledge of ecosystem processes that contribute to hypoxia formation and for predicting the effects of proposed management activities or future scenarios \citep{Scavia04,Hagy07,Pauer16}.
+Numerical ecosystem models are important tools that synthesize knowledge of ecosystem processes that contribute to hypoxia formation and for predicting the effects of proposed management activities or future scenarios \citep{Scavia04,Hagy07,Camacho14a,Pauer16}.
 Unlike statistical models with more generic structures, simulation and process-based models include explicit descriptions of relevant processes that are constrained by empirical or observational data relevant to the system of interest \citep[e.g.][]{Omlin01b,Eldridge10}.
-These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions \citep{Warner05,Zhao10,Ganju16}.
+These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions \citep{Warner05,Dortch07,Zhao10,Ganju16}.
 Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} (\citealt{Fennel13,Obenour15,Pauer16}, \citetalias{LehrterIP}).
@@
 
-The development of a model represents a tradeoff between characteristics expected from the output and information represented by the structural components.
-An ideal model is sufficiently generalizable across systems, provides results that are precise given the inputs, and includes components that are realistic descriptions of actual processes \citep{Levins66}.
-Given that these characteristics cannot be simultaneously achieved, models are developed in partial dependence of reality and theoretical constructs, completely separate from both, or dependent on one or the other \citep{Morrison99,Ganju16}.
+The development of a model represents a tradeoff between achieving predictive accuracy and a realistic representation of environmental processes.
+An ideal model is sufficiently generalizable across systems, provides results that are accurate given the inputs, and includes components that are valid descriptions of actual processes \citep{Levins66, Ganju16}.
+Given that these characteristics cannot be simultaneously achieved, models are developed that balance predictive accuracy with environmental realism, often favoring one at the expense of the other \citep{Morrison99,Ganju16}.
 These challenges are analagous to the well-known bias-variance tradeoff in statistical models that balances the competing objectives of over- and under-fitting to an observed dataset.
@@
 
-Model precision can be evaluated relative to the effects of initial conditions or the observed data used for calibration, changes in parameter values, or variation in the structural components (i.e., observational, parameter, or structural uncertainty) \citep{Beck87}.
+Model fit can be evaluated relative to the effects of initial conditions or the observed data used for calibration, changes in parameter values, or variation in the structural components (i.e., observational, parameter, or structural uncertainty) \citep{Beck87}.
 Evaluating effects of parameter changes is by far the most common and simplest approach.
@@
 \end{inparaenum}
-The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model precision.
+The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model fit.
 Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability the results.
@@
 
-A local sensitivity analysis was performed by evaluating the change in state variables following perturbation of each parameter from its original value \citep{Soetaert10,RDCT17}.
+A local sensitivity analysis was performed by evaluating the change in state variables following perturbation of each parameter from its original value \citep{Soetaert10,Camacho14b,RDCT17}.
+This approach is described as a First Order Variance Analysis that linearly propagates changes from model parameters to model predictions \citep{Camacho14b}.
 Parameters were individually perturbed by a 50\% increase of the original values and sensitivity $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
@@
 Sensitivity matrices were first normalized by dividing by the square root of the summed residuals \citep{Omlin01,Soetaert10}.
-Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize precision on a calibration dataset are inestimable by conventional optimization algorithms.
+Estimates of $\gamma$ greater than 10-15 suggest parameter sets are poorly identifiable \citep{Brun01,Omlin01}, meaning parameter values that maximize fit on a calibration dataset are inestimable by conventional optimization algorithms.
 An intuitive interpretation of $\gamma$ is provided by \citet{Brun01}, such that a change in a state variable caused by a change in one parameter can be offset by the fraction $1 - 1/\gamma$ by the remaining parameters.
@@
 
-Parameter selection for model calibration must consider the competing objectives of increased precision with parameter inclusion and reduced identifiability as it relates to optimization.
+Parameter selection for model calibration must consider the competing objectives of increased goodness of fit with parameter inclusion and reduced identifiability as it relates to optimization.
 An additional challenge is a large number of combinations of parameter sets, which complicates selection given sensitivity differences and desired ecological categories of each parameter (e.g., parameters for a group of related structural equations could be of interest).
@@
 These rulesets were developed to select parameters with preference for those with high sensitivity and identifiability based on $\gamma < 15$ as an acceptable threshold for subsets (e.g., 93\% accountability between parameters).
-Selection heurestics also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences by users given desired application of the model.
+Heurestics for parameter selection also recognized that parameter categories (i.e., optics, organic matter, phytoplankton, temperature, zooplankton) may have unequal preferences by users given desired application of the model.
 For all selection heuristics, parameters were selected by decreasing sensitivity starting with the most sensitive until identifiability did not exceed $\gamma = 15$ where selections were \begin{inparaenum}[1\upshape)]
@@
 Selected parameter subsets from the seven heuristics were used to calibrate the \ac{zerod} model.
-This analysis demonstrated that different parameter sets can produce model output with differing precision and calibration effort given
+This analysis demonstrated that different parameter sets can produce model output with differing goodness and fit and calibration effort given
 \begin{inparaenum}[1\upshape)]
@@
 While we recognize that `actual' parameter values could possibly extend beyond this range, constraining the values to the range tested herein was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
-Moreover, precise limits on each parameter were less of a concern for the current analysis as our primary goal was to demonstrate differences in precision as a function of sensitivity and identifiability.
+Moreover, precise limits on each parameter were less of a concern for the current analysis as our primary goal was to demonstrate differences in fit as a function of sensitivity and identifiability.
 The optimal values for each parameter were identified based on convergence of the model results as a minimization of the \ac{rmse} between the observed and modelled data.
@@
 
-Calibration of parameter values for each of the seven selection heuristics (\cref{tab:heurist1,tab:heurist2,tab:heurist3})  produced model output that varied in precision and computational effort required to identify optimal values (\cref{tab:calib}).
+Calibration of parameter values for each of the seven selection heuristics (\cref{tab:heurist1,tab:heurist2,tab:heurist3})  produced model output that varied in goodness of fit and computational effort required to identify optimal values (\cref{tab:calib}).
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
@@
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt}, reduction to \Sexpr{scinot(top$rmse)}, \Sexpr{scinot(cattop$rmse)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse)}).
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt} mmol O$_2$ m$^{-3}$, reduction to \Sexpr{scinot(top$rmse)}, \Sexpr{scinot(cattop$rmse)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse)}).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 
-Common goals in the application of biogeochemical models are to \begin{inparaenum}[1\upshape)]
-\item accurately describe the system by matching predictions with observed data \citep{Reckhow90}, and 
-\item provide a means of forecasting ecosystem condition with hypothesized management or environmental scenarios \citep{Clark01}. 
-\end{inparaenum}
-Although these objectives are the focus of most applications, the structural components and associated parameters of process-based models should secondarily provide insight of ecosystem processes that are driving observed changes.
-This latter objective represents a more generic scientific purpose of modelling that extends beyond the benefits of describing and predicting change.
-Modelers aim to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting hypotheses \citep{Hilborn97,Kirchner06}.
-Accordingly, this study provided a simple approach to use the effects of parameter perturbations on state variables to characterize identifiable parameter subsets that varied by selection criteria.
-By doing so, we provided a simple and preliminary approach towards improved model refinement that begins to address more general purposes of model applications.
-Our specific results demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiability thresholds described in the literature.
-The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
-Use of identifiable parameter subsets with sensitive parameters improved model precision and results for the smaller model were scalable to the 3-dimensional model.
-In general, these results provide justification for the use of explicit parameter selection heuristics to improve model precision.
-
-State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\Sexpr{par_txt('umax_1')} for phytoplankton, \Sexpr{par_txt('Zumax_1')} for zooplankton), mortality coefficient for phytoplankton (\Sexpr{par_txt('mA_1')}), and the zooplankton half saturation coefficent for grazing (\Sexpr{par_txt('ZKa_1')}).
-An increase in the growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} in the water column.
-Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter from algal sources.
-Most variables were also sensitive to variation in the half-saturation grazing coefficient which moderates the concentration of nutrients that support half the maximum grazing rate.
+State variables were most sensitive to phytoplankton and zooplankton parameters, particularly the maximum growth rates (\Sexpr{par_txt('umax_1')} for phytoplankton, \Sexpr{par_txt('Zumax_1')} for zooplankton), mortality coefficient for phytoplankton (\Sexpr{par_txt('mA_1')}), and the zooplankton half saturation coefficent for grazing (\Sexpr{par_txt('ZKa_1')}).
+An increase in the growth rate of primary producers can increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} in the water column.
+Similarly, increases in zooplankton abundance with increased growth rates can reduce phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter from algal sources.
+Most variables were also sensitive to variation in the half-saturation grazing coefficient which moderates nutrient concentrations that support half the maximum grazing rate.
 Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs} \citep{Fahnenstiel95,Roelke00,Eldridge10}.
-The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance to biological relationships.
-That is, state variables were sensitive to changes in light and temperature parameters, although to a lesser extent than phytoplankton and zooplankton parameters.
-As such, the differing sensitivities of state variables to parameters in each of the categories was not unexpected given general ecological relationships that are well understood and described by the model.
+The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance.
+That is, state variables were sensitive to changes in light and temperature parameters, although to a lesser extent than biological parameters.
+As such, the differing sensitivities of state variables to parameters in each of the categories was not unexpected given ecological relationships that are well understood and described by the model.
 
@@
 In addition to \ac{cgem}, these conclusions have relevance for other biogeochemical models that include numerous parameters and structural equations to characterize processes in the model domain.
-A general conclusion is that less complex models could potentially be beneficial given that only a small subset of parameters is identifiable and that ecosystem processes may in fact be sufficiently characterized with few parameters \citep{Ye97}.
-Conversely, others have argued that model complexity is not in itself a disadvantage when parsimony is not the sole arbitrator of model structure \citep{Reichert97}.
+A general conclusion is that less complex models are potentially beneficial given that only a small subset of parameters is identifiable and that ecosystem processes may in fact be sufficiently characterized with few parameters \citep{Ye97}.
+Conversely, others have argued that model complexity is not in itself a disadvantage when parsimony is not the only determinant of model structure \citep{Reichert97}.
 Over-parameterization can be useful if processes have importance that were not evaluated during model identification.
-Single objective functions that maximize model precision with identifiable parameters may also provide an incomplete characterization of model worth, which has prompted the development of probability-based models of hypoxia that explicitly include uncertainty in model components \citep[e.g.][]{Obenour15}.
+Single objective functions that maximize model fit with identifiable parameters may also provide an incomplete characterization of model worth, which has prompted the development of probability-based models of hypoxia that explicitly include uncertainty in model components \citep[e.g.][]{Obenour15}.
 Our results demonstrated that approximately 75\% of the evaluated parameters had an effect on the eight state variables, whereas \ac{cgem} includes a total of 36 variables and multiple plankton groups, not all of which have immediate concern for understanding hypoxia.
-The redundancies identified with the sensitivity analyses are only problematic if the primary interest is, for example, \ac{do} dynamics.
+The redundancies identified with the sensitivity analyses are challenging only if the primary interest is, for example, \ac{do} dynamics.
 Moreover, the proposed selection heuristics provide flexibility for choosing different parameters with the assumption that those chosen depend on the research or management question.
@@
 Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude individual parameters.
-For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model precision and that these parameters had affects that translated to the larger model.
+For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model fit and that these parameters had affects that translated to the larger model.
 Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
 Similarly, identifiability was not always related to the number of parameters in a set.
-Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
+Although the general trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
 For example, \cref{fig:exclex} showed that including \Sexpr{par_txt('KGcdom_1')}, \Sexpr{par_txt('KO2_1')}, or \Sexpr{par_txt('nitmax_1')} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
-These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
-The selection criteria proposed in our above analyses can facilitate parameter selection and also provide diagnostic tools to identify parameters with disproportionate effects on $\gamma$.
+The selection criteria proposed above can facilitate parameter selection and also provide diagnostic tools to identify parameters with disproportionate effects on $\gamma$.
 
@@
 
-An evaluation of sensitivity and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
-In general, uncertainty analyses that lead to improved models are ultimately expected to increase our understanding of properties defining ecological relationships.
-The extension of simple parameter sensitivity analyses to the generalization of ecosystem properties requires additional analysis and model refinement.
-Further, the utility of a specific model depends on the question and objective for application to a specific system.
-For the above analysis, the FishTank model, as part of the larger \ac{cgem} application, was evaluated in the context of hypoxia effects on ecosystem condition and function.
-Our results have shown that relatively small subsets of parameters are identifiable given the complexity of the model, and as a result, we have provided a general approach to select parameter subsets depending on the ecological context (i.e., selection by parameter category, selection for specific state variables).
-We further demonstrated the effects of selected subsets on model precision and the potential for scalability to larger spatial-temporal models.
-Thus, the results described above have relevance for further model refinement with the specific goal of better understanding ecological dynamics that moderate hypoxia on the northern \ac{gom}.
-However, the general principles of sensitivity and parameter identifiability have broad applicability beyond this context and we argue that such methods should be more universally applied as an initial approach to quantify numerical constraints of biogeochemical models.
-
-Specific approaches can be used to improve and build on the results presented herein, in addition to the more general considerations above.
+Our results demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiability thresholds described in the literature.
+The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
+Use of identifiable parameter subsets with sensitive parameters improved model fit and results for the smaller model were scalable to the 3-dimensional model.
+However, an evaluation of sensitivity and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
+We have provided a general approach to select parameter subsets for further model development depending on the ecological context (i.e., selection by parameter category, selection for specific state variables).
+Thus, the results described above have relevance for model refinement with the specific goal of better understanding ecological dynamics that moderate hypoxia on the northern \ac{gom}.
+The general principles of sensitivity and parameter identifiability have broad applicability beyond this context and we argue that such methods should be more universally applied as an initial approach to quantify numerical constraints of biogeochemical models.
+
 The effects of structural or observational uncertainty could be evaluated as an extension of the analyses presented above.
@@
 A more challenging analysis is an evaluation of the effects of structural components on model output, which requires exclusion or inclusion of explicit biogeochemical equations.
-Fortunately, the FishTank model includes several `switches' that allow users to change the governing equations that estimate state variables, such as switches that `turn on' different structural equations for light attenuation in the water column.
+The FishTank model includes several `switches' that allow users to change the governing equations that estimate state variables, such as switches that `turn on' different structural equations for light attenuation in the water column.
 This design is uncommon in biogeochemical models and could be leveraged for an evaluation of structural uncertainty.

### 2017-08-01 ident_manu.tex
revisions half way done

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue May 2 09:04:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/eedd4b1c3c2a4bd984b414a5b3fc28e9845d2d88}{eedd4b1c3c2a4bd984b414a5b3fc28e9845d2d88}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Mon Jul 31 17:43:04 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/03ef21c36dd48fe1a6afd2f825a9bd6aaa19f078}{03ef21c36dd48fe1a6afd2f825a9bd6aaa19f078}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 Variation in sensitivity had a direct correspondence with identifiability, such that only small subsets of the complete parameter set had unique effects on the model output.
-Selecting parameters by decreasing sensitivity demonstrated that only eight of 51 total parameters had a sufficiently unique effect on model output for precise calibration.
+Selecting parameters by decreasing sensitivity demonstrated that only eight of 51 total parameters had a sufficiently unique effect on model output for accurate calibration.
 As a result, parameter selection heuristics were used to identify parameters for model calibration that depended on combined effects on output, relative sensitivity of each parameter, and ecological categories for the biogeochemical equations.
-The calibrated \ac{zerod} unit of the hypoxia model had improved precision if sensitive parameters were included in an identifiable subset.
+The calibrated \ac{zerod} unit of the hypoxia model had improved fit to the observed data if sensitive parameters were included in an identifiable subset.
 Extension of results to a three-dimensional grid of the Gulf of Mexico showed that sensitive parameters for the \ac{zerod} model translated to non-trivial changes in the areal estimates of hypoxia.
@@
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$, reduction to $66.77$, $67.44$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.12$).
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$ mmol O$_2$ m$^{-3}$, reduction to $66.77$, $67.44$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.12$).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 
-Common goals in the application of biogeochemical models are to \begin{inparaenum}[1\upshape)]
-\item accurately describe the system by matching predictions with observed data \citep{Reckhow90}, and 
-\item provide a means of forecasting ecosystem condition with hypothesized management or environmental scenarios \citep{Clark01}. 
-\end{inparaenum}
-Although these objectives are the focus of most applications, the structural components and associated parameters of process-based models should secondarily provide insight of ecosystem processes that are driving observed changes.
-This latter objective represents a more generic scientific purpose of modelling that extends beyond the benefits of describing and predicting change.
-Modelers aim to identify universal principles that govern dynamics across systems and the constraint of model parameters to observations provides a means of supporting or refuting hypotheses \citep{Hilborn97,Kirchner06}.
-Accordingly, this study provided a simple approach to use the effects of parameter perturbations on state variables to characterize identifiable parameter subsets that varied by selection criteria.
-By doing so, we provided a simple and preliminary approach towards improved model refinement that begins to address more general purposes of model applications.
-Our specific results demonstrated that small parameter subsets relative to all sensitive parameters were within the identifiability thresholds described in the literature.
-The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
-Use of identifiable parameter subsets with sensitive parameters improved model precision and results for the smaller model were scalable to the 3-dimensional model.
-In general, these results provide justification for the use of explicit parameter selection heuristics to improve model precision.
-
-State variables were most sensitive to parameters in the phytoplankton and zooplankton categories, particularly the maximum growth rates (\textit{umax} for phytoplankton, \textit{Zumax} for zooplankton), mortality coefficient for phytoplankton (\textit{mA}), and the zooplankton half saturation coefficent for grazing (\textit{ZKa}).
-An increase in the growth rate of primary producers has the potential to increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} in the water column.
-Similarly, increases in zooplankton abundance with increased growth rates causes a reduction in phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter from algal sources.
-Most variables were also sensitive to variation in the half-saturation grazing coefficient which moderates the concentration of nutrients that support half the maximum grazing rate.
+State variables were most sensitive to phytoplankton and zooplankton parameters, particularly the maximum growth rates (\textit{umax} for phytoplankton, \textit{Zumax} for zooplankton), mortality coefficient for phytoplankton (\textit{mA}), and the zooplankton half saturation coefficent for grazing (\textit{ZKa}).
+An increase in the growth rate of primary producers can increase oxygen concentration through photosynthetic processes, although increased production of organic matter is balanced with respiration and bacterial decomposition that reduce \ac{do} in the water column.
+Similarly, increases in zooplankton abundance with increased growth rates can reduce phytoplankton biomass through grazing, which is expected to further deplete pools of organic matter from algal sources.
+Most variables were also sensitive to variation in the half-saturation grazing coefficient which moderates nutrient concentrations that support half the maximum grazing rate.
 Although the tradeoff between abundance, grazing, and decomposition is complex, the sensitivity of model state variables to parameters that directly control the abundance of primary producers is in agreement with empirical observations of factors that influence hypoxia dynamics on the \ac{lcs} \citep{Fahnenstiel95,Roelke00,Eldridge10}.
-The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance to biological relationships.
-That is, state variables were sensitive to changes in light and temperature parameters, although to a lesser extent than phytoplankton and zooplankton parameters.
-As such, the differing sensitivities of state variables to parameters in each of the categories was not unexpected given general ecological relationships that are well understood and described by the model.
+The sensitivity of the model output to variation in other parameters that relate to physical and chemical properties of the system was of secondary importance.
+That is, state variables were sensitive to changes in light and temperature parameters, although to a lesser extent than biological parameters.
+As such, the differing sensitivities of state variables to parameters in each of the categories was not unexpected given ecological relationships that are well understood and described by the model.
 
@@
 Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude individual parameters.
-For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model precision and that these parameters had affects that translated to the larger model.
+For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model fit and that these parameters had affects that translated to the larger model.
 Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
 Similarly, identifiability was not always related to the number of parameters in a set.
-Although the overwhelming trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
+Although the general trend was decreasing identifiability with more parameters, the unique effects of including an individual parameter with an existing set often reduced the $\gamma$ estimate.
 For example, \cref{fig:exclex} showed that including \textit{KGcdom}, \textit{KO2}, or \textit{nitmax} in parameter sets more often reduced $\gamma$ relative to sets that excluded the parameters.
-These examples demonstrate the complex interactions of parameter changes on variable response, highlighting the need to consider the combined and individual effects of parameters on identifiability.
-The selection criteria proposed in our above analyses can facilitate parameter selection and also provide diagnostic tools to identify parameters with disproportionate effects on $\gamma$.
+The selection criteria proposed above can facilitate parameter selection and also provide diagnostic tools to identify parameters with disproportionate effects on $\gamma$.
 

### 2017-08-01 ident_manu.Rnw
new model fig

@@
 \author{John C. Lehrter}
-\address{Dauphin Island Sea Lab, University of South Alabama, Dauphin Island, AL 36528}
+\address{University of South Alabama, Dauphin Island Sea Lab, Dauphin Island, AL 36528}
 \ead{jlehrter@disl.org}
@@
 Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to hypoxia formation \citep{Wiseman97,Paerl98,Obenour15}.
-The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep[\cref{fig:mod_schem},][]{Eldridge10}.
+The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep[\cref{fig:fishmod},][]{Eldridge10}.
 The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{figs/mod_schem.pdf}
-\caption{Conceptual representation of biogeochemical components modelled in \ac{cgem} (complete equations in \citealt{Eldridge10}).
-FishTank implements a \ac{zerod} version of the model that does not include any advection, mixing, or sediment diagenesis.}
+\includegraphics[width=0.7\textwidth]{figs/fishmod.pdf}
+\caption{Conceptual representation of biogeochemical components included in FishTank (complete equations in \citealt{Eldridge10}).
+The \acl{cgem} couples FishTank with a hydrodynamic model that includes advection, mixing, and dispersion.}
 \label{fig:mod_schem}

### 2017-08-01 ident_manu.tex
new model fig

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Mon Jul 31 17:43:04 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/03ef21c36dd48fe1a6afd2f825a9bd6aaa19f078}{03ef21c36dd48fe1a6afd2f825a9bd6aaa19f078}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Tue Aug 1 13:06:48 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/8169e808436dd5e6f70a58cb58addf7a41d98b7b}{8169e808436dd5e6f70a58cb58addf7a41d98b7b}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 

### 2017-08-02 revision/review_response.Rnw
new model fig
parameter values to tables

@@
 
-{\it }
+{\it The previous conceptual diagram was for CGEM that included both the biogeochemical components of FishTank and hydrodynamic components.
+A new figure was created that inludes only the FishTank components.
+}
 
@@
 
-{\it We have found that precision is commonly used in the literature to describe goodness of fit, although we appreciate the distinction made by the reviewer.
+{\it We have found that precision is commonly used in the literature to describe goodness of fit, although we understand the distinction made by the reviewer.
 Considering an example where observed data represent a biased sample of an environmental process (e.g., infrequent or unevent sampling of an event that varies over time), model calibration to these data can only possibly achieve precision.
@@
 
+{\it The starting parameter values were added to Tables 1, S1-S7.  We have not added the 50\% increase in each parameter as this is a simple calculation and it clutters the tabular information.}
+
 Lines 29-30 page 16. Please include the units in the reported RMSEs. mmol O2?

### 2017-08-02 ident_manu.Rnw
parameter values to tables

@@
 \renewcommand{\figurename}{Fig.}
-
-% aliased citations
-\defcitealias{LehrterIP}{Lehrter et al. in press}
 
@@
 \author{Lisa L. Lowe}
-\address{Lockheed Martin IS \& GS - Civil supporting the USEPA, Research Triangle Park, NC 27709}
+\address{CSRA, Inc. supporting the USEPA, Research Triangle Park, NC 27709}
 \ead{lowe.lisa@epa.gov}
@@
 These models are often coupled with hydrodynamic grids to provide spatially-explicit representations of patterns in three dimensions \citep{Warner05,Dortch07,Zhao10,Ganju16}.
-Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} (\citealt{Fennel13,Obenour15,Pauer16}, \citetalias{LehrterIP}).
+Combined hydrodynamic and bio-geo-chemical models have been developed specifically to describe hypoxic conditions on the \ac{lcs} in the northern \ac{gom} \citep{Fennel13,Obenour15,Pauer16,Lehrter17}.
 This area drains a significant portion of the continental United States through the \ac{marb} and is the second largest hypoxic area in the world \citep{Rabalais02}.
@@
 Seasonal variation is strongly related to carbon and nutrient export from the \ac{marb} \citep{Lohrenz08,Bianchi10}, whereas hydrologic variation, currents, and wind patterns can affect vertical salinity gradients that contribute to hypoxia formation \citep{Wiseman97,Paerl98,Obenour15}.
-The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep[\cref{fig:fishmod},][]{Eldridge10}.
+The \ac{cgem} was developed to describe hypoxia dynamics on the \ac{lcs} and includes elements from the Navy Coastal Ocean Model \citep{Martin00} for hydrodynamics and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.
 The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf.
@@
 
-The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any advection, mixing, or sediment diagenesis.
+The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any advection, mixing, or sediment diagenesis (\cref{fig:fishmod}).
+A full description of the model structure, equations, and parameters is described in \citet{Lehrter17}.
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
-Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIP}).
+Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citealt{Lehrter17}).
 A total of 108 equations are estimated at each time step to return values for each of the 36 state variables described by the model.
@@
 The final set that was evaluated included \Sexpr{length(p1z1pars)} parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
-A full description of the model parameters is available as an appendix in \citetalias{LehrterIP}.
+A full description of the model parameters is available as an appendix in \citet{Lehrter17}.
 

### 2017-08-02 ident_manu.tex
parameter values to tables

@@
 
-% aliased citations
-\defcitealias{LehrterIP}{Lehrter et al. in press}
-
 %acronyms
@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue Aug 1 13:06:48 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/8169e808436dd5e6f70a58cb58addf7a41d98b7b}{8169e808436dd5e6f70a58cb58addf7a41d98b7b}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Tue Aug 1 16:09:48 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/c8fc63e4d9d637ede500474a4806a69c13b5c16a}{c8fc63e4d9d637ede500474a4806a69c13b5c16a}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 The final set that was evaluated included 51 parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (22), temperature (2), and zooplankton (11).
-A full description of the model parameters is available as an appendix in \citetalias{LehrterIP}.
+A full description of the model parameters is available as an appendix in \citet{Lehrter17}.
 
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$7.51\times 10^{-4}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.92\times 10^{-5}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.39\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.05$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.02$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.02$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.02$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.01$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$8.36\times 10^{-3}$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$8.12\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$6.94\times 10^{-3}$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$4.32\times 10^{-3}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$4.27\times 10^{-3}$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$4.23\times 10^{-3}$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$4.13\times 10^{-3}$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.9\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$2.77\times 10^{-4}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$8.34\times 10^{-8}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.05$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.02$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.02$\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$0.02$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.01$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$9.38\times 10^{-5}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.69\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$4.99\times 10^{-4}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$4.17\times 10^{-4}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$7.51\times 10^{-4}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$4.92\times 10^{-5}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$4.39\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.02$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$0.05$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$0.02$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.02$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$0.02$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.01$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$8.36\times 10^{-3}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$8.12\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$6.94\times 10^{-3}$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$4.57\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$4.32\times 10^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$4.27\times 10^{-3}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$4.23\times 10^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$4.13\times 10^{-3}$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$2.9\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$2.77\times 10^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$8.34\times 10^{-8}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$0.05$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.02$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.02$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$0.02$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.01$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$7.78\times 10^{-3}$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$5.32\times 10^{-3}$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$2.96\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$9.38\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$3.69\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$6.15\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$3.14\times 10^{-3}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$3.04\times 10^{-3}$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$2.98\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$5.85\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$5.8\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$4.99\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$4.17\times 10^{-4}$\tabularnewline
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.63\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.5\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~mortality coefficient&\textit{mA}&$8.49$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$1.32$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.65$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.6$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.46$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.29$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.16$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.15$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.14$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.14$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$0.1$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.1$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.03$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$2.24\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$1.42$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.76$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.74$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.62$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.5$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.3$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.22$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.16$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.07\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$1.44\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.54$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$0.66$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.07$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.06$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.05$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.03$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.03$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$1.63\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$1.5\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.79$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$8.49$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$1.32$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$0.65$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.6$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.46$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$0.29$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.17$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.16$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.15$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.14$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$0.14$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.1$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$0.1$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.03$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.01$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$2.24\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$1.42$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.76$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$0.74$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.62$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.5$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$0.3$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$0.22$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.16$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.07\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.44\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$1.54$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$0.66$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$0.07$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.07$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.06$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.05$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$0.03$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$7.55\times 10^{-3}$\tabularnewline
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.45\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.13\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~mortality coefficient&\textit{mA}&$13.94$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.95$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.85$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.62$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.53$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.26$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.25$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.24$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.14$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.12$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$0.07$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.02$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$1.38\times 10^{-6}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$1.02$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.85$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.57$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.52$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.23$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.14$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.29\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$7.55\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.03$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.01$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.35\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$3.4\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$2.97\times 10^{-5}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$1.45\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$1.13\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.6$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$13.94$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$0.95$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$0.85$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.62$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.53$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.26$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$0.25$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.24$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.17$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.14$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$0.12$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$0.1$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.07$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.02$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.01$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.38\times 10^{-6}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$1.02$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$0.85$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.57$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.52$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.41$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$0.23$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$0.17$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.14$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.29\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$7.55\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.07$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$0.03$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$0.01$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.01$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$3.35\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.19\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$3.4\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.97\times 10^{-5}$\tabularnewline
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.47\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.34\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.09$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.05$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.04$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.04$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.03$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.02$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.01$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.01$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.01$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$9.48\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$9.38\times 10^{-3}$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$8.1\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$5.75\times 10^{-3}$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$3.78\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$9.81\times 10^{-4}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$1.92\times 10^{-7}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.13$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.06$\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$0.04$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.04$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.03$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.02$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$9.34\times 10^{-5}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$1.99\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.2\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.54\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.72\times 10^{-6}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1.48\times 10^{-6}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$1.47\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$1.34\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.03$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$0.09$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$0.05$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.04$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$0.04$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.03$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$0.02$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.01$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.01$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.01$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$9.48\times 10^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$9.38\times 10^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$8.1\times 10^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$5.75\times 10^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$3.78\times 10^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$9.81\times 10^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.92\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$0.13$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.06$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$0.04$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.04$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.03$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$0.02$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$0.01$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$9.67\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$9.34\times 10^{-5}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$1.99\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.05$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$3.96\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$9.88\times 10^{-4}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$7.2\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$3.54\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$6.18\times 10^{-5}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$1.72\times 10^{-6}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$1.48\times 10^{-6}$\tabularnewline
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.27\times 10^{-3}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.19\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$8.49$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.89$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.7$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.33$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.27$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.2$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.19$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.13$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.11$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.1$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.09$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$0.09$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.07$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$7.06\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.67\times 10^{-7}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$7.59$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$1.17$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.7$\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$0.34$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.26$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.25$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.8\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$8.59\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.78$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$0.07$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.04$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.03$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.02$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$9.96\times 10^{-3}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$9.87\times 10^{-3}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.02$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$1.27\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$1.19\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.3$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$8.49$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.89$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.7$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$0.33$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$0.27$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$0.2$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.19$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.13$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.11$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$0.1$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$0.1$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.09$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.09$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.07$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$7.06\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$6.67\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$7.59$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$1.17$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.7$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$0.34$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$0.26$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.25$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$0.17$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.1$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$3.8\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$8.59\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.78$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$0.07$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.04$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.03$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$0.02$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$0.01$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$9.96\times 10^{-3}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$9.87\times 10^{-3}$\tabularnewline
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.73\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.49\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~mortality coefficient&\textit{mA}&$7.22$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.9$\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.89$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.67$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.67$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.45$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.29$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.24$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.22$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$0.21$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.14$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.11$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.09$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$7.35\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$0.96$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.79$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.54$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.49$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.39$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.27$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.16$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$9.64\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.06\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.92$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.02$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$6.98\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$6.41\times 10^{-5}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.03$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$1.73\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$1.49\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.86$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$7.22$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$0.9$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$0.89$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.67$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.67$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.45$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.29$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.24$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$0.22$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.21$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.14$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.11$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$0.1$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$0.09$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.01$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$7.35\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$0.96$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$0.79$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.54$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.49$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.39$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$0.27$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$0.16$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.12$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$9.64\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.06\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$0.92$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.07$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.04$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.02$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$0.01$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$3.72\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$6.98\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$6.41\times 10^{-5}$\tabularnewline
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$2.48\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$2.04\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~mortality coefficient&\textit{mA}&$14.25$\tabularnewline
-~~maximum growth rate&\textit{umax}&$1.11$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.94$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.86$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.85$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$0.67$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.36$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.29$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.25$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$0.24$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.22$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.2$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.14$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.1$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$0.02$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$4.37\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$1.01$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$0.88$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.58$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.54$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.13$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.12$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$0.04$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.69\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.94$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.1$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.04$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$8.44\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$7.41\times 10^{-5}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$0.04$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$2.48\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$2.04\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$1.48$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$14.25$\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$1.11$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$0.94$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.86$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.85$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.67$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.36$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.29$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.25$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.24$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$0.22$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.2$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$0.14$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$0.1$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$0.02$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$4.37\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$1.01$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$0.88$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.58$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.54$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.41$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$0.17$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.13$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$0.12$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$0.04$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$1.69\times 10^{-3}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$0.94$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.1$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.04$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$0.04$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.03$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$3.16\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$8.44\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$7.41\times 10^{-5}$\tabularnewline
 \hline
@@
 \begin{center}
-\begin{tabular}{lll}
+\begin{tabular}{llll}
 \hline\hline
-\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline
-\hline
-{\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$9.01\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$5.21\times 10^{-4}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$5.13\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline
-\hline
-{\bfseries Phytoplankton}&&\tabularnewline
-~~maximum growth rate&\textit{umax}&$0.78$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$0.59$\tabularnewline
-~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.23$\tabularnewline
-~~mortality coefficient&\textit{mA}&$0.2$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$0.18$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.13$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$0.11$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$0.09$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$0.06$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$0.06$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$0.04$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$0.03$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$6.97\times 10^{-3}$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$6.68\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$8.21\times 10^{-7}$\tabularnewline
-\hline
-{\bfseries Zooplankton}&&\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$1.47$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&$0.5$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.35$\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$0.26$\tabularnewline
-~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.19$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.15$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.1$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$6.43\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.38\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.14$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.06$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.02$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.01$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.29\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$2.7\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$2.64\times 10^{-5}$\tabularnewline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline
+\hline
+{\bfseries Optics}&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$9.01\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.21\times 10^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$5.13\times 10^{-4}$\tabularnewline
+\hline
+{\bfseries Temperature}&&&\tabularnewline
+~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$22$&$0.16$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&\tabularnewline
+~~maximum growth rate&\textit{umax}&$0.41$&$0.78$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$0.59$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$&$0.25$\tabularnewline
+~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.23$\tabularnewline
+~~mortality coefficient&\textit{mA}&$0.1$&$0.2$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.18$\tabularnewline
+~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$1.72\times 10^{8}$&$0.13$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.11$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$0.09$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$3.37\times 10^{4}$&$0.06$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.06$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$0.04$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.03$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$4.51$&$6.97\times 10^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$6.68\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$8.21\times 10^{-7}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$1.12\times 10^{12}$&$1.47$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$0.5$\tabularnewline
+~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$0.35$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$9.45\times 10^{7}$&$0.26$\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.4$&$0.19$\tabularnewline
+~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.25$&$0.15$\tabularnewline
+~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.2$&$0.1$\tabularnewline
+~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$0.06$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$6.43\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$3.38\times 10^{-5}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$50$&$0.14$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$50$&$0.06$\tabularnewline
+~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.02$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.01$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$7.29\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.19\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$2.7\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.64\times 10^{-5}$\tabularnewline
 \hline

### 2017-08-02 R/funcs.R

@@ -1030,16 +1030,18 @@ senstab <- function(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', tabs
     mutate(Parameter = as.character(Parameter)) %>% 
     left_join(., tmpest, by = 'Parameter') %>% 
     left_join(., labs, by = 'Parameter') %>% 
-    select(cats, lngs, Parameter, L1) %>% 
+    select(cats, lngs, Parameter, vals, L1) %>% 
     arrange(cats, -L1) %>% 
     mutate(
       Parameter = par_txt(Parameter),
       lngs = gsub('^.*:\\s', '', lngs), 
       lngs = gsub('_', '', lngs),
+      vals = sapply(vals, scinot, digits = digits, pow = pow),
       L1 = sapply(L1, scinot, digits = digits, pow = pow)
     ) %>% 
     rename(
-      Description = lngs
+      Description = lngs, 
+      Value = vals
     )
   
   # final table formatting

### 2017-08-02 R/funcs.R
added parunis function

@@ -159,14 +159,14 @@ parcats2 <- function(as_df = FALSE){
       'Ea_R(nospA+nospZ)_8'
       ),
     lngs = c(
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
-      'Tref(nospA+nospZ): Optimum temperature for growth(C)',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
+      'Tref(nospA+nospZ): Optimum temperature for growth',
       'KTg1(nospA+nospZ): Effect of T below Topt(C^2)',
       'KTg1(nospA+nospZ): Effect of T below Topt(C^2)',
       'KTg1(nospA+nospZ): Effect of T below Topt(C^2)',
@@ -407,12 +407,12 @@ parcats2 <- function(as_df = FALSE){
       "umax: maximum growth rate", 
       "umax: maximum growth rate", 
       "umax: maximum growth rate", 
-      "alpha: initial slope of the photosynthesis-irradiance relationship", 
-      "alpha: initial slope of the photosynthesis-irradiance relationship", 
-      "alpha: initial slope of the photosynthesis-irradiance relationship", 
-      "alpha: initial slope of the photosynthesis-irradiance relationship", 
-      "alpha: initial slope of the photosynthesis-irradiance relationship", 
-      "alpha: initial slope of the photosynthesis-irradiance relationship", 
+      "alpha: initial slope of photosynthesis v irradiance", 
+      "alpha: initial slope of photosynthesis v irradiance", 
[…]

### 2017-08-02 ident_manu.tex
working on parmtab function

--- 2017-08-01 ident_manu.tex
@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue Aug 1 13:06:48 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/8169e808436dd5e6f70a58cb58addf7a41d98b7b}{8169e808436dd5e6f70a58cb58addf7a41d98b7b}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Wed Aug 2 13:16:06 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/5cd8b68899d08c2c8f96177fe72e018bd764f96a}{5cd8b68899d08c2c8f96177fe72e018bd764f96a}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 \caption{Sensitivity of \ac{do} to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect \ac{do} are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline
 \hline
@@
 ~~mortality coefficient&\textit{mA}&$0.02$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.02$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.02$\tabularnewline
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.02$\tabularnewline
@@
 ~~phytoplankton basal respiration coefficient&\textit{respb}&$6.94\times 10^{-3}$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline
 ~~minimum N cell-quota&\textit{QminN}&$4.32\times 10^{-3}$\tabularnewline
@@
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$0.02$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.02$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.02$\tabularnewline
 ~~maximum growth rate of zooplankton&\textit{Zumax}&$0.02$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.01$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline
 ~~zooplankton carbon/individual&\textit{ZQc}&$9.38\times 10^{-5}$\tabularnewline
@@
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
 ~~maximum rate of nitrification per day&\textit{nitmax}&$4.99\times 10^{-4}$\tabularnewline
@@
 \caption{Sensitivity of ammonium to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect ammonium are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline
 \hline
@@
 ~~maximum growth rate&\textit{umax}&$0.65$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.6$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.6$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.46$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.29$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$0.29$\tabularnewline
 ~~coefficient for non-limiting nutrient&\textit{aN}&$0.17$\tabularnewline
@@
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$0.62$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.5$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.3$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.22$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.16$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.5$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.3$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.22$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.16$\tabularnewline
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$1.07\times 10^{-3}$\tabularnewline
@@
 ~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.07$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.06$\tabularnewline
@@
 ~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.03$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
 \hline
@@
 \caption{Sensitivity of \ac{chla} to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect \ac{chla} are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline
 \hline
@@
 ~~maximum growth rate&\textit{umax}&$0.85$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.62$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.62$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.53$\tabularnewline
 ~~phytoplankton growth respiration coefficient&\textit{respg}&$0.26$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.25$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$0.25$\tabularnewline
 ~~phytoplankton basal respiration coefficient&\textit{respb}&$0.24$\tabularnewline
@@
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$0.52$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.23$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.14$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.41$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.23$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.14$\tabularnewline
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$1.29\times 10^{-3}$\tabularnewline
@@
 {\bfseries Organic Matter}&&\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
 ~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.03$\tabularnewline
@@
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.35\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
 ~~maximum rate of nitrification per day&\textit{nitmax}&$3.4\times 10^{-5}$\tabularnewline
@@
 \caption{Sensitivity of irradiance to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect irradiance are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline
 \hline
@@
 ~~mortality coefficient&\textit{mA}&$0.05$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.04$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.04$\tabularnewline
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.04$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.03$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.02$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$0.02$\tabularnewline
 ~~coefficient for non-limiting nutrient&\textit{aN}&$0.01$\tabularnewline
@@
 ~~maximum growth rate of zooplankton&\textit{Zumax}&$0.04$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.04$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.04$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.03$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.02$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67\times 10^{-3}$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.02$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67\times 10^{-3}$\tabularnewline
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$9.34\times 10^{-5}$\tabularnewline
@@
 {\bfseries Organic Matter}&&\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.05$\tabularnewline
 ~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
@@
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.54\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline
 ~~maximum rate of nitrification per day&\textit{nitmax}&$1.72\times 10^{-6}$\tabularnewline
@@
 \caption{Sensitivity of nitrate to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect nitrate are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline
 \hline
@@
 ~~phytoplankton carbon/cell&\textit{Qc}&$0.89$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.7$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.7$\tabularnewline
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.33$\tabularnewline
 ~~mortality coefficient&\textit{mA}&$0.27$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.2$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$0.2$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.19$\tabularnewline
@@
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$1.17$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.7$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.7$\tabularnewline
 ~~maximum growth rate of zooplankton&\textit{Zumax}&$0.34$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.26$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.26$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.25$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$\tabularnewline
 ~~zooplankton carbon/individual&\textit{ZQc}&$3.8\times 10^{-3}$\tabularnewline
@@
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.78$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$0.07$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.04$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$0.07$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.04$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.03$\tabularnewline
@@
 \caption{Sensitivity of \ac{pom} to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect \ac{pom} are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline
 \hline
@@
 ~~phytoplankton carbon/cell&\textit{Qc}&$0.67$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.67$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.67$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.45$\tabularnewline
@@
 ~~phytoplankton basal respiration coefficient&\textit{respb}&$0.24$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.22$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$0.22$\tabularnewline
 ~~minimum N cell-quota&\textit{QminN}&$0.21$\tabularnewline
@@
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$0.49$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.39$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.27$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.16$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.39$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.27$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.16$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline
 ~~zooplankton carbon/individual&\textit{ZQc}&$9.64\times 10^{-3}$\tabularnewline
@@
 ~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.92$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
@@
 ~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
 ~~maximum rate of nitrification per day&\textit{nitmax}&$6.98\times 10^{-5}$\tabularnewline
@@
 \caption{Sensitivity of \acl{dom} to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect \acl{dom} are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline
 \hline
@@
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.86$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.85$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.85$\tabularnewline
 ~~phytoplankton carbon/cell&\textit{Qc}&$0.67$\tabularnewline
@@
 ~~minimum N cell-quota&\textit{QminN}&$0.24$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.22$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$0.22$\tabularnewline
 ~~half-saturation constant for P&\textit{Kp}&$0.2$\tabularnewline
@@
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$0.54$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.13$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.12$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.41$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.13$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.12$\tabularnewline
 ~~zooplankton carbon/individual&\textit{ZQc}&$0.04$\tabularnewline
@@
 ~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.94$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.1$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.1$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
@@
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline
 ~~maximum rate of nitrification per day&\textit{nitmax}&$8.44\times 10^{-5}$\tabularnewline
@@
 \caption{Sensitivity of phosphate to perturbations of individual parameters.
-Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).
+Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).
 Parameters that did not affect phosphate are not shown.
@@
 {\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline
 \hline
@@
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.25$\tabularnewline
-~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.23$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.23$\tabularnewline
 ~~mortality coefficient&\textit{mA}&$0.2$\tabularnewline
 ~~N-uptake rate measured at umax&\textit{vmaxN}&$0.18$\tabularnewline
-~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.13$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$0.13$\tabularnewline
 ~~coefficient for non-limiting nutrient&\textit{aN}&$0.11$\tabularnewline
@@
 ~~zooplankton nitrogen/individual&\textit{ZQn}&$0.5$\tabularnewline
-~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.35$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&$0.35$\tabularnewline
 ~~maximum growth rate of zooplankton&\textit{Zumax}&$0.26$\tabularnewline
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.19$\tabularnewline
-~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.15$\tabularnewline
-~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.1$\tabularnewline
-~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.15$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.1$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$6.43\times 10^{-3}$\tabularnewline
@@
 ~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.06$\tabularnewline
-~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.02$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.02$\tabularnewline
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.01$\tabularnewline
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.29\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
 ~~maximum rate of nitrification per day&\textit{nitmax}&$2.7\times 10^{-5}$\tabularnewline

### 2017-08-02 R/funcs.R

@@ -473,18 +473,18 @@ parcats2 <- function(as_df = FALSE){
       "Ksi: half-saturation constant for Si uptake", 
       "Ksi: half-saturation constant for Si uptake", 
       "Ksi: half-saturation constant for Si uptake", 
-      "KQn: Qn constant for Flynn nutrient dependent growth model", 
-      "KQn: Qn constant for Flynn nutrient dependent growth model", 
-      "KQn: Qn constant for Flynn nutrient dependent growth model", 
-      "KQn: Qn constant for Flynn nutrient dependent growth model", 
-      "KQn: Qn constant for Flynn nutrient dependent growth model", 
-      "KQn: Qn constant for Flynn nutrient dependent growth model", 
-      "KQp: Qp constant for Flynn nutrient dependent growth model", 
-      "KQp: Qp constant for Flynn nutrient dependent growth model", 
-      "KQp: Qp constant for Flynn nutrient dependent growth model", 
-      "KQp: Qp constant for Flynn nutrient dependent growth model", 
-      "KQp: Qp constant for Flynn nutrient dependent growth model", 
-      "KQp: Qp constant for Flynn nutrient dependent growth model", 
+      "KQn: Qn constant for Flynn growth model", 
+      "KQn: Qn constant for Flynn growth model", 
+      "KQn: Qn constant for Flynn growth model", 
+      "KQn: Qn constant for Flynn growth model", 
+      "KQn: Qn constant for Flynn growth model", 
+      "KQn: Qn constant for Flynn growth model", 
+      "KQp: Qp constant for Flynn growth model", 
+      "KQp: Qp constant for Flynn growth model", 
+      "KQp: Qp constant for Flynn growth model", 
+      "KQp: Qp constant for Flynn growth model", 
+      "KQp: Qp constant for Flynn growth model", 
+      "KQp: Qp constant for Flynn growth model", 
       "nfQs: exponent for Geider nutrient uptake model",
       "nfQs: exponent for Geider nutrient uptake model", 
       "nfQs: exponent for Geider nutrient uptake model",
@@ -829,23 +829,23 @@ parcats2 <- function(as_df = FALSE){
       'KstarO2: O2 concentration that inhibits denitrification',
       'KNO3: half-saturation concentration for denitrification',
       'pCO2: atmospheric CO2',
[…]

### 2017-08-03 revision/review_response.Rnw
parameter table added

@@
 
-{\it }
+{\it We have added Table 1 that inlcudes a full list and description of parameters that were evaluated for the sensitivity analysis.}
 
@@
 
-{\it The starting parameter values were added to Tables 1, S1-S7.  We have not added the 50\% increase in each parameter as this is a simple calculation and it clutters the tabular information.}
+{\it A new table (Table 1) was added for the full parameter set including names, long description, units, values, and the 50\% increase in values for the sensitivity analyses.}
 

### 2017-08-03 ident_manu.Rnw
parameter table added

@@
 To remove obvious redundancies, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
-The final set that was evaluated included \Sexpr{length(p1z1pars)} parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}).
+The final set that was evaluated included \Sexpr{length(p1z1pars)} parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ \Sexpr{nparms$Optics} parameters), organic matter (\Sexpr{nparms$`Organic Matter`}), phytoplankton (\Sexpr{nparms$Phytoplankton}), temperature (\Sexpr{nparms$Temperature}), and zooplankton (\Sexpr{nparms$Zooplankton}) (\cref{tab:parmtab}).
 A full description of the model parameters is available as an appendix in \citet{Lehrter17}.
@@
 This approach is described as a First Order Variance Analysis that linearly propagates changes from model parameters to model predictions \citep{Camacho14b}.
-Parameters were individually perturbed by a 50\% increase of the original values and sensitivity $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
+Parameters were individually perturbed by a 50\% increase of the original values (\cref{tab:parmtab}) and sensitivity $S$ was estimated for each time step $i$ given a change for parameter $j$ as:
 
@@
 
+% parameter info
+<<parmtab, eval = T, cache = F>>=
+parmtab(tabsize = 'tiny')
+@
+
 % do sensitivity all categories
@@
 The \acl{cgem} couples FishTank with a hydrodynamic model that includes advection, mixing, and dispersion.}
-\label{fig:mod_schem}
+\label{fig:fishmod}
 \end{figure}
@@
 The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 50 parameter sets are shown each with one through 50 total parameters.
-Note that the number of unique combinations is shown as the natural-log.', fig.height = 5, fig.width = 5, out.width = '0.6\\textwidth'>>=
+Note that the number of unique combinations is shown as the natural-log.', cache = TRUE, fig.height = 5, fig.width = 5, out.width = '0.6\\textwidth'>>=
 
@@
 Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.
-See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 6, fig.width = 4, out.width = '0.7\\textwidth', eval = T, echo = F, warning = F, message = F>>=
+See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 6, fig.width = 4, out.width = '0.7\\textwidth', eval = T, cache = TRUE, echo = F, warning = F, message = F>>=
 # initial conditions

### 2017-08-03 ident_manu.tex
parameter table added

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Wed Aug 2 13:16:06 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/5cd8b68899d08c2c8f96177fe72e018bd764f96a}{5cd8b68899d08c2c8f96177fe72e018bd764f96a}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Wed Aug 2 17:20:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/a49e333c59176457f6c598684d90ef37895bdafb}{a49e333c59176457f6c598684d90ef37895bdafb}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 To remove obvious redundancies, the sensitivity analyses were conducted using only one phytoplankton and one zooplankton group.
-The final set that was evaluated included 51 parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (22), temperature (2), and zooplankton (11).
+The final set that was evaluated included 51 parameters that were further grouped into one of six categories based on applicable biogeochemical components of the model: optics ($n = $ 4 parameters), organic matter (12), phytoplankton (22), temperature (2), and zooplankton (11) (\cref{tab:parmtab}).
 A full description of the model parameters is available as an appendix in \citet{Lehrter17}.
@@
 \invisiblesection{Tables}
+
+% parameter info
+%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%
+\begin{table}[!tbp]
+{\tiny
+\caption{FishTank parameters evaluated for sensitivity and identifiability.
+Sensitivitity analyses were based on a 50\% increase (Value $\cdot$ 1.5) from the initial value of each parameter.
+Dashed units are dimensionless.
+Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.
+A full description of the model structure, equations, and parameters is described in \citet{Lehrter17}.\label{tab:parmtab}}
+\begin{center}
+\begin{tabular}{lllll}
+\hline\hline
+\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Units}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{Value $\cdot$ 1.5}\tabularnewline
+\hline
+{\bfseries Optics}&&&&\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&m$^{-1}$ (mg Chla m$^{-3}$)$^{-1}$&$0.04$&$0.06$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&m$^{-1}$ (mg OMA m$^{-3}$)$^{-1}$&$0.1$&$0.15$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&m$^{-1}$ (mg OMZ m$^{-3}$)$^{-1}$&$0.1$&$0.15$\tabularnewline
+~~sinking rate&\textit{sink CDOM}&m d$^{-1}$&$0$&$0$\tabularnewline
+\hline
+{\bfseries Temperature}&&&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&C&$22$&$33$\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&C&$22$&$33$\tabularnewline
+\hline
+{\bfseries Phytoplankton}&&&&\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&10$^{-16}$ cm$^2$ s quanta$^{-1}$ d$^{-1}$&$8.42\times 10^{-17}$&$1.26\times 10^{-16}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&-&$1$&$1.5$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&10$^7$ cells m$^{-3}$&$1.72\times 10^{8}$&$2.58\times 10^{8}$\tabularnewline
+~~edibility vector for Z1&\textit{ediblevector(Z1)}&-&$0.25$&$0.38$\tabularnewline
+~~edibility vector for Z2&\textit{ediblevector(Z2)}&-&$0.25$&$0.38$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&mmol m$^{-3}$&$4.51$&$6.76$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&mmol m$^{-3}$&$2.86$&$4.29$\tabularnewline
+~~Qn constant for Flynn growth model&\textit{KQn}&-&$5$&$7.5$\tabularnewline
+~~Qp constant for Flynn growth model&\textit{KQp}&-&$0.2$&$0.3$\tabularnewline
+~~half-saturation constant for Si uptake&\textit{Ksi}&mmol m$^{-3}$&$4.51$&$6.76$\tabularnewline
+~~mortality coefficient&\textit{mA}&d$^{-1}$&$0.1$&$0.15$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&10$^{-7}$ mmol C cell$^{-1}$&$1.35\times 10^{-6}$&$2.03\times 10^{-6}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&10$^{-9}$ mmol N cell$^{-1}$&$6.08\times 10^{-9}$&$9.12\times 10^{-9}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&10$^{-9}$ mmol P cell$^{-1}$&$6.19\times 10^{-10}$&$9.29\times 10^{-10}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&d$^{-1}$&$0.02$&$0.03$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&-&$0.1$&$0.15$\tabularnewline
+~~sinking rate of phytoplankton cells&\textit{sink A}&m d$^{-1}$&$1.49$&$2.23$\tabularnewline
+~~maximum growth rate&\textit{umax}&d$^{-1}$&$0.41$&$0.62$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$4.1\times 10^{-8}$&$6.15\times 10^{-8}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$2.68\times 10^{-8}$&$4.02\times 10^{-8}$\tabularnewline
+~~Si-uptake rate measured at umax&\textit{vmaxSi}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$4.1\times 10^{-8}$&$6.15\times 10^{-8}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$\mu$m$^3$&$3.37\times 10^{4}$&$5.05\times 10^{4}$\tabularnewline
+\hline
+{\bfseries Zooplankton}&&&&\tabularnewline
+~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&-&$0.4$&$0.6$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$\mu$m$^3$ m$^{-3}$&$1.12\times 10^{12}$&$1.68\times 10^{12}$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&m$^6$ ind$^{-2}$ d$^{-1}$&$7.2\times 10^{-4}$&$0$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&mmol C ind$^{-1}$&$3.13\times 10^{-4}$&$4.7\times 10^{-4}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&mmol N ind$^{-1}$&$6.95\times 10^{-5}$&$1.04\times 10^{-4}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&mmol P ind$^{-1}$&$3.77\times 10^{-6}$&$5.66\times 10^{-6}$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&d$^{-1}$&$0.1$&$0.15$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&-&$0.2$&$0.3$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&-&$0.25$&$0.38$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$\mu$m$^3$ ind$^{-1}$ d$^{-1}$&$9.45\times 10^{7}$&$1.42\times 10^{8}$\tabularnewline
+~~zooplankton volume/individual&\textit{Zvolcell}&$\mu$m$^3$ ind$^{-1}$&$2.98\times 10^{7}$&$4.47\times 10^{7}$\tabularnewline
+\hline
+{\bfseries Organic Matter}&&&&\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&y$^{-1}$&$50$&$75$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&y$^{-1}$&$50$&$75$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&d$^{-1}$&$0.01$&$0.02$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&mmol m$^{-3}$&$1$&$1.5$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&mmol m$^{-3}$&$10$&$15$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&mmol m$^{-3}$&$10$&$15$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&mmol m$^{-3}$&$10$&$15$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&mmol m$^{-3}$ d$^{-1}$&$0.52$&$0.78$\tabularnewline
+~~phytoplankton sinking rate&\textit{sink OM1\_A}&m d$^{-1}$&$10$&$15$\tabularnewline
+~~zooplankton sinking rate&\textit{sink OM1\_Z}&m d$^{-1}$&$10$&$15$\tabularnewline
+~~phytoplankton sinking rate&\textit{sink OM2\_A}&m d$^{-1}$&$0$&$0$\tabularnewline
+~~zooplankton sinking rate&\textit{sink OM2\_Z}&m d$^{-1}$&$0$&$0$\tabularnewline
+\hline
+\end{tabular}\end{center}}
+\end{table}
 
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$4.99\times 10^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$4.17\times 10^{-4}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$3.69\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$4.99\times 10^{-4}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$4.17\times 10^{-4}$\tabularnewline
 \hline
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.54$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$0.66$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.07$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.06$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.05$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.03$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 ~~zooplankton carbon/individual&\textit{ZQc}&$1.44\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.54$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$0.66$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.07$\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.06$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.05$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.03$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
 \hline
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.03$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.01$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.35\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$3.4\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$2.97\times 10^{-5}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 ~~zooplankton carbon/individual&\textit{ZQc}&$7.55\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.03$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.01$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.35\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$3.4\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$2.97\times 10^{-5}$\tabularnewline
 \hline
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.05$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.2\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.54\times 10^{-4}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.72\times 10^{-6}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1.48\times 10^{-6}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 ~~zooplankton carbon/individual&\textit{ZQc}&$1.99\times 10^{-5}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$0.05$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.2\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.54\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.72\times 10^{-6}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1.48\times 10^{-6}$\tabularnewline
 \hline
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.78$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$0.07$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.04$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.03$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.02$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$9.96\times 10^{-3}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$9.87\times 10^{-3}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$8.59\times 10^{-4}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.78$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$0.07$\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$0.04$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.03$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.02$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$9.96\times 10^{-3}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$9.87\times 10^{-3}$\tabularnewline
 \hline
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.92$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.02$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$6.98\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$6.41\times 10^{-5}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$1.06\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.92$\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.02$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$6.98\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$6.41\times 10^{-5}$\tabularnewline
 \hline
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.94$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.1$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.04$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$8.44\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$7.41\times 10^{-5}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 ~~zooplankton phosphorus/individual&\textit{ZQp}&$1.69\times 10^{-3}$\tabularnewline
-\hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.94$\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$0.1$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.04$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.04$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$8.44\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$7.41\times 10^{-5}$\tabularnewline
 \hline
@@
 \hline
-{\bfseries Temperature}&&\tabularnewline
-~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline
+{\bfseries Organic Matter}&&\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.14$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.06$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$0.02$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.01$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.29\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$2.7\times 10^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$2.64\times 10^{-5}$\tabularnewline
 \hline
@@
 \hline
+{\bfseries Temperature}&&\tabularnewline
+~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline
+\hline
 {\bfseries Zooplankton}&&\tabularnewline
@@
 \hline
-{\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.14$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.06$\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$0.02$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.01$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.29\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$2.7\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$2.64\times 10^{-5}$\tabularnewline
-\hline
 \end{tabular}\end{center}}

### 2017-08-03 R/funcs.R

@@ -1109,29 +1109,29 @@ parmtab <- function(tablab = 'parmtab', tabsize = 'normalsize', pow = 3, digits 
       `Value $\\cdot$ 1.5` = valsp50
     )
   
-  return(totab)
+  if(dfout) return(totab)
   
-  # # final table formatting
-  # Description <- totab$Description
-  # cats <- totab$cats
-  # totab <- totab[,-c(1:2)]
-  # 
-  # cap.val<- paste('Sensitivity of', captxt, 'to perturbations of individual parameters.  Sensitivities are based on a 50\\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \\cref{l1}).  Parameters that did not affect', captxt, 'are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.')
-  # 
-  # latex( 
-  #   totab,
-  #   file = '',
-  #   rowlabel = 'Description',
-  #   caption = cap.val,
-  #   caption.loc = 'top',
-  #   rowname = Description,
-  #   rgroup = unique(cats),
-  #   n.rgroup = as.numeric(table(cats)),
-  #   size = tabsize,
-  #   label = paste0('tab:', tablab), 
-  #   insert.bottom = foot.val
-  #   )
-    
+  # final table formatting
+  Description <- totab$Description
+  cats <- totab$cats
+  totab <- totab[,-c(1:2)]
+
[…]

### 2017-08-04 revision/review_response.Rnw
nearly twenty pages, the best, let me tell you

@@
 
-{\it We have added Table 1 that inlcudes a full list and description of parameters that were evaluated for the sensitivity analysis.}
+{\it We have added Table 1 that inccudes a full list and description of parameters that were evaluated for the sensitivity analysis.
+This table includes short and long descriptions, units, and starting values.
+
+Full details of the model are provided as an appendix in Lehrter et al.
+2017.
+We have not included the content here because it includes nearly twenty pages which we do not wish to duplicate.
+We refer the reader to the appendix twice in section 2.1, which includes a new sentence in the first paragraph: `A full description of the model structure, equations, and parameters is described in appendices A-F in Lehrter et al.
+(2017).'
+}
 
@@
 {\it The discussion was shortened and introductory material was removed.
-Specifically, the first paragraph of the discusison was removed and the first paragraph of sec.
+Specifically, the first paragraph of the discussion was removed and the first paragraph of sec.
 4.1 was shortened.
-This reduced the length by over a page.}
+This reduced the length by over one page.}
 

### 2017-08-04 ident_manu.Rnw
nearly twenty pages, the best, let me tell you

@@
 The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model fit.
-Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability the results.
+Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability of the results.
 In addition to \ac{do}, other state variables that were evaluated included ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus.
@@
 The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any advection, mixing, or sediment diagenesis (\cref{fig:fishmod}).
-A full description of the model structure, equations, and parameters is described in \citet{Lehrter17}.
+A full description of the model structure, equations, and parameters is described in appendices A-F in \citet{Lehrter17}.
 Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids.
-Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citealt{Lehrter17}).
+Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendices in \citealt{Lehrter17}).
 A total of 108 equations are estimated at each time step to return values for each of the 36 state variables described by the model.

### 2017-08-04 ident_manu.tex
nearly twenty pages, the best, let me tell you

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Wed Aug 2 17:20:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/a49e333c59176457f6c598684d90ef37895bdafb}{a49e333c59176457f6c598684d90ef37895bdafb}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Thu Aug 3 12:09:09 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/0895cb42311eb3eb06b254be874f61997b2288d5}{0895cb42311eb3eb06b254be874f61997b2288d5}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 

### 2017-08-06 ident_manu.tex
new table with flask calibration, not final

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Thu Aug 3 12:09:09 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/0895cb42311eb3eb06b254be874f61997b2288d5}{0895cb42311eb3eb06b254be874f61997b2288d5}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Fri Aug 4 17:59:08 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/84e94b5eb0aca29df79344221e5651a5af428017}{84e94b5eb0aca29df79344221e5651a5af428017}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
-For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 1530 iterations were required for the eight parameters selected independent of category.
+For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 136 iterations were required for the eight parameters selected independent of category.
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $72.14$ mmol O$_2$ m$^{-3}$, reduction to $66.77$, $67.44$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($72.12$).
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $33.47$ mmol O$_2$ m$^{-3}$, reduction to $26.56$, $28.36$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($33.3$).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 {\bfseries 1}&&&&&\tabularnewline
-~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$49$&$72.12$\tabularnewline
-~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$154$&$68.7$\tabularnewline
-~~Phytoplankton&$3.97$&$7$&$0.02$&$1725$&$68.3$\tabularnewline
-~~Temperature&$1$&$1$&$0.02$&$6$&$71.76$\tabularnewline
-~~Zooplankton&$5.2$&$4$&$0.03$&$279$&$71.22$\tabularnewline
+~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$49$&$33.3$\tabularnewline
+~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$44$&$31.48$\tabularnewline
+~~Phytoplankton&$3.97$&$7$&$0.02$&$300$&$25.84$\tabularnewline
+~~Temperature&$1$&$1$&$0.02$&$6$&$31.23$\tabularnewline
+~~Zooplankton&$5.2$&$4$&$0.03$&$72$&$32.99$\tabularnewline
 \hline
 {\bfseries 2}&&&&&\tabularnewline
-~~Independent of category&$6.81$&$8$&$0.03$&$1530$&$66.77$\tabularnewline
+~~Independent of category&$6.81$&$8$&$0.03$&$136$&$26.56$\tabularnewline
 \hline
 {\bfseries 3}&&&&&\tabularnewline
-~~Equally within category&$5.22$&$7$&$0.03$&$1005$&$67.44$\tabularnewline
+~~Equally within category&$5.22$&$7$&$0.03$&$45$&$28.36$\tabularnewline
 \hline

### 2017-08-15 ident_manu.Rnw
added calex figure from new flask calibration data

@@
 
+load(file = 'data/cals.RData')
+
+# starting rmse
+strt <- cals[[1]]$mat[1,] %>% 
+  .[length(.)] %>% 
+  scinot(.)
+
 totab <- caldat %>% 
@@
 $RMSE$ shows the final error comparing observed and model output after the specified number of iterations for optimization.'
-foot.val <- '\\footnotesize *Starting \\ac{rmse} $= 72.140$'
+foot.val <- paste0('\\footnotesize *Starting \\ac{rmse} ', strt)
 colnms <- c('$\\gamma$', '$n$ parameters', 'mean L1', 'Iterations', '$RMSE$*')
@@
 
+% calibration example
+<<calex, eval = T, fig.cap = 'Example of calibration steps for the phytoplankton parameter subset.
+The FishTank model was calibrated using data from an approximate 12-hour flask experiment of oxygen production.
+Model calibration adjusted parameters (left plots) to minimize the \\ac{rmse} between experimental and modelled dissolved oxygen (top left).
+The phytoplankton parameters were those identifiable for dissolved oxygen (\\cref{tab:heurist1}), arranged from most (top plot) to least sensitive (bottom plot) (\\cref{tab:dosens}).
+The relative parameter changes in the right plots show the initial parameter values (black) and the the selected parameter values (blue) after calibration.', fig.height = 7, fig.width = 6, echo = F, cache = T, out.width = '\\textwidth'>>=
+data(cals)
+data(tocal_all)
+plo_cal(cals, tocal_all, whichsub = 'Phytoplankton', widths = c(1, 0.4), heights = c(0.125, 1))
+@
+
+% CGEM area change plots
 <<areachg, eval = T, fig.cap = 'Estimated hypoxic area and monthly averages (km$^2 \\times$ 1000) using the default parameter settings (a, b) and the differences using a 50\\% increase in each parameter (c, d).

### 2017-08-15 ident_manu.tex
added calex figure from new flask calibration data

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Fri Aug 4 17:59:08 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/84e94b5eb0aca29df79344221e5651a5af428017}{84e94b5eb0aca29df79344221e5651a5af428017}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Sun Aug 6 08:21:57 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/c03d0df749cea19daced8a68105265cf1ed2a63e}{c03d0df749cea19daced8a68105265cf1ed2a63e}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
-For example, only six iterations were required to optimize the single parameter selected for the temperature category, whereas 136 iterations were required for the eight parameters selected independent of category.
+For example, only three iterations were required to optimize the single parameter selected for the temperature category, whereas 136 iterations were required for the eight parameters selected independent of category.
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $33.47$ mmol O$_2$ m$^{-3}$, reduction to $26.56$, $28.36$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($33.3$).
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $35.17$ mmol O$_2$ m$^{-3}$, reduction to $35.15$, $35.16$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($35.17$).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 {\bfseries 1}&&&&&\tabularnewline
-~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$49$&$33.3$\tabularnewline
-~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$44$&$31.48$\tabularnewline
-~~Phytoplankton&$3.97$&$7$&$0.02$&$300$&$25.84$\tabularnewline
-~~Temperature&$1$&$1$&$0.02$&$6$&$31.23$\tabularnewline
-~~Zooplankton&$5.2$&$4$&$0.03$&$72$&$32.99$\tabularnewline
+~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$7$&$35.17$\tabularnewline
+~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$286$&$35.05$\tabularnewline
+~~Phytoplankton&$3.97$&$7$&$0.02$&$255$&$35.03$\tabularnewline
+~~Temperature&$1$&$1$&$0.02$&$3$&$35.17$\tabularnewline
+~~Zooplankton&$5.2$&$4$&$0.03$&$9$&$35.17$\tabularnewline
 \hline
 {\bfseries 2}&&&&&\tabularnewline
-~~Independent of category&$6.81$&$8$&$0.03$&$136$&$26.56$\tabularnewline
+~~Independent of category&$6.81$&$8$&$0.03$&$136$&$35.15$\tabularnewline
 \hline
 {\bfseries 3}&&&&&\tabularnewline
-~~Equally within category&$5.22$&$7$&$0.03$&$45$&$28.36$\tabularnewline
+~~Equally within category&$5.22$&$7$&$0.03$&$105$&$35.16$\tabularnewline
 \hline
 \end{tabular}\end{center}}
-\footnotesize *Starting \ac{rmse} $= 72.140$\end{table}
+\footnotesize *Starting \ac{rmse} $35.17$\end{table}
 
@@
 
+% calibration example
+\begin{figure}[!ht]
+
+{\centering \includegraphics[width=\textwidth]{figs/calex-1}
+
+}
+
+\caption{Example of calibration steps for the phytoplankton parameter subset.
+The FishTank model was calibrated using data from an approximate 12-hour flask experiment of oxygen production.
+Model calibration adjusted parameters (left plots) to minimize the \ac{rmse} between experimental and modelled dissolved oxygen (top left).
+The phytoplankton parameters were those identifiable for dissolved oxygen (\cref{tab:heurist1}), arranged from most (top plot) to least sensitive (bottom plot) (\cref{tab:dosens}).
+The relative parameter changes in the right plots show the initial parameter values (black) and the the selected parameter values (blue) after calibration.}\label{fig:calex}
+\end{figure}
+
+% CGEM area change plots
 \begin{figure}[!ht]

### 2017-08-15 R/funcs.R

@@ -1556,3 +1556,155 @@ parunis <- function(as_df = TRUE){
   return(out)
   
 }
+
+# Plot calibration results for parameter subsets
+#
+# cals is input dataset
+# tocal_all is input dataset
+# whichsub chr string of subset to plot, must be one of names in tocal_all
+# pert NULL or numeric indicating range of parameter values that were tested to create cals
+# heights vector of length two for plot spacing
+# widths vector of length two for plot spacing
+#
+plo_cal <- function(cals, tocal_all, whichsub = names(cals), pert = NULL, heights = c(0.1, 1), widths = c(1, 1)){
+
+  library(tibble)
+  library(tidyverse)
+    
+  # get calibration results for a given parameter subsets
+  whichsub <- match.arg(whichsub)
+  selsub <- cals[[whichsub]]
+  
+  # get min/max values that were used to create cals, make sure pert is ok
+  rngs <- get_cmbs(tocal_all, out_var = 'O2', thrsh = 15, coll = T, errs = TRUE, pert = pert)
+  
+  # get parameter levels, ordered by sensitivity
+  ords <- rngs[[whichsub]] %>% 
+    .$errs %>% 
+    names
+  ordlabs <- as.character(par_txt(ords, frm = 'exp'))
+
+  # calibration steps, parameters and error
+  toplo <- selsub$mat %>% 
+    data.frame
+  names(toplo) <- c(names(selsub$par), 'rmse')
+  toplo <- toplo %>% 
+    mutate(iter = 1:nrow(.)) %>% 
+    gather('var', 'val', -iter) 
+  
+  # err data to plot
+  toploerr <- toplo %>% 
+    filter(var %in% 'rmse')
+    
+  # calibration steps to plot
+  toplo <- toplo %>% 
+    filter(!var %in% 'rmse') %>% 
+    mutate(
+      var = factor(var, levels = ords, labels = ordlabs)
+    )
+  
+  # error plot (top left)
+  perr <- ggplot(toploerr, aes(x = iter, y = val)) + 
+    geom_line() + 
+    theme_bw() + 
+    theme(
+      strip.background = element_blank(), 
+      # axis.text.y = element_text(size = 6), 
+      axis.title.x = element_blank(), 
+      axis.ticks.x = element_blank(), 
+      axis.text.x = element_blank(), 
[…]

### 2017-08-15 ident_manu.Rnw
added calibration table 2

@@
 strt <- cals[[1]]$mat[1,] %>% 
-  .[length(.)] %>% 
-  scinot(.)
+  .[length(.)]
 
@@
   arrange(heurist)
+strt <- scinot(strt)
 
@@
   n.rgroup = c(5, 1, 1),
+  colheads = colnms
+  )
+
+@
+
+% do ending parameter values
+<<calibprm, eval = T, cache = F, warning = F>>=
+
+load(file = 'data/cals.RData')
+load(file = 'data/tocal_all.RData')
+
+ests <- map(cals, 'par') %>%
+  map(enframe, name = 'parm', value = 'val') %>% 
+  enframe(name = 'heurist') %>%
+  unnest %>% 
+  mutate(var = 'calib') %>% 
+  select(heurist, var, parm, val)
+
+rngs <- get_cmbs(tocal_all, out_var = 'O2', thrsh = 15, coll = T, errs = TRUE, pert = NULL) %>% 
+  lapply(function(x){
+    x[c('error', 'vals', 'minv', 'maxv')] %>% 
+      bind_rows(.id = 'var') %>% 
+      gather('parm', 'val', -var)
+  }) %>% 
+  enframe(name = 'heurist') %>% 
+  unnest
+
+levs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'top', 'cattop')
+labs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'Independent of category', 'Equally within category')
+
+totab <- rbind(ests, rngs) %>% 
+  spread('var', 'val') %>% 
+  mutate(
+    pchg = 100 * (calib - vals)/vals,
+    pchg = ifelse(pchg > 0, paste0('+', round(pchg, 0)), 
+      ifelse(pchg < 0, paste0('-', round(pchg, 0)), 'nc')
+    ),
+    minv = sapply(minv, scinot), 
+    maxv = sapply(maxv, scinot), 
+    vals = sapply(vals, scinot),
+    calib = sapply(calib, scinot),
+    rgrp = ifelse(heurist == 'top', '2', ifelse(heurist == 'cattop', '3', '1')), 
+    heurist = factor(heurist, levels = levs, labels = labs), 
+    parm = par_txt(parm)
+  ) %>% 
+  select(rgrp, heurist, parm, error, minv, maxv, vals, calib, pchg) %>% 
+  arrange(heurist, -error) %>% 
+  mutate(
+    error = sapply(error, scinot),
+    heurist = as.character(heurist), 
+    heurist = ifelse(duplicated(heurist), '', heurist)
+    )
+
+cap_val <- 'Results of parameter changes from model calibration to observed \\ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third).
+The parameters of each subset are from \\cref{tab:heurist1,tab:heurist2,tab:heurist3}.
+The L1 values are relative sensitivity of \\ac{do} to a paramter change.
+Starting and final parameter values after calibration are shown, including the percent change.
+The calibration routing was bounded by minimum and maximum values appropriate for each parameter.'
+colnms <- c('Parameter', 'L1', 'Min', 'Max', 'Initial', 'Final', '\\% change')
+
+latex(
+  totab[, -c(1,2)],
+  file = '',
+  rowlabel = 'Selection heuristic',
+  caption = cap_val,
+  caption.loc = 'top',
+  size = 'scriptsize',
+  label = 'tab:calibprm',
+  rowname = totab$heurist,
+  rgroup = names(table(totab$rgrp)),
+  n.rgroup = as.numeric(table(totab$rgrp)),
   colheads = colnms

### 2017-08-15 ident_manu.tex
added calibration table 2

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Aug 6 08:21:57 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/c03d0df749cea19daced8a68105265cf1ed2a63e}{c03d0df749cea19daced8a68105265cf1ed2a63e}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Tue Aug 15 15:08:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/c0ce23e253cb1532614d91ec7a60ed5b8e91e26f}{c0ce23e253cb1532614d91ec7a60ed5b8e91e26f}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 
+% do ending parameter values
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selection heuristic",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:calibprm", rowname = totab$heurist, rgroup = names(table(totab$rgrp)),     n.rgroup = as.numeric(table(totab$rgrp)), colheads = colnms)%
+\begin{table}[!tbp]
+{\scriptsize
+\caption{Results of parameter changes from model calibration to observed \ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third).
+The parameters of each subset are from \cref{tab:heurist1,tab:heurist2,tab:heurist3}.
+The L1 values are relative sensitivity of \ac{do} to a paramter change.
+Starting and final parameter values after calibration are shown, including the percent change.
+The calibration routing was bounded by minimum and maximum values appropriate for each parameter.\label{tab:calibprm}}
+\begin{center}
+\begin{tabular}{llllllll}
+\hline\hline
+\multicolumn{1}{l}{Selection heuristic}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{Initial}&\multicolumn{1}{c}{Final}&\multicolumn{1}{c}{\% change}\tabularnewline
+\hline
+{\bfseries 1}&&&&&&&\tabularnewline
+~~Optics&\textit{astar490}&$7.51\times 10^{-4}$&$0.02$&$0.12$&$0.04$&$0.04$&nc\tabularnewline
+~~&\textit{astarOMZ}&$4.92\times 10^{-5}$&$0.01$&$0.15$&$0.01$&$0.01$&nc\tabularnewline
+~~&\textit{astarOMA}&$4.39\times 10^{-5}$&$0.01$&$0.15$&$0.01$&$0.01$&nc\tabularnewline
+~~Organic Matter&\textit{KG1}&$6.15\times 10^{-3}$&$5$&$100$&$30$&$48.04$&+60\tabularnewline
+~~&\textit{KG2}&$3.14\times 10^{-3}$&$5$&$100$&$30$&$33.21$&+11\tabularnewline
+~~&\textit{KstarO2}&$3.04\times 10^{-3}$&$1$&$100$&$10$&$10$&nc\tabularnewline
+~~&\textit{KGcdom}&$2.98\times 10^{-3}$&$0$&$1$&$0.01$&$0.01$&nc\tabularnewline
+~~&\textit{KO2}&$5.85\times 10^{-4}$&$1$&$100$&$10$&$100$&+900\tabularnewline
+~~Phytoplankton&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$2.5$&+123\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$&$0.5$&$0.11$&$0.01$&--91\tabularnewline
+~~&\textit{alpha}&$0.02$&$1\times 10^{-17}$&$6\times 10^{-16}$&$3.96\times 10^{-16}$&$6\times 10^{-16}$&+52\tabularnewline
+~~&\textit{ediblevector(Z1)}&$0.02$&$0.05$&$1$&$0.5$&$0.5$&nc\tabularnewline
+~~&\textit{Qc}&$0.01$&$1\times 10^{-9}$&$5\times 10^{-7}$&$4.54\times 10^{-8}$&$5\times 10^{-7}$&+1001\tabularnewline
+~~&\textit{respg}&$8.36\times 10^{-3}$&$0.01$&$0.5$&$0.1$&$0.1$&nc\tabularnewline
+~~&\textit{vmaxN}&$8.12\times 10^{-3}$&$1\times 10^{-11}$&$1\times 10^{-8}$&$1.33\times 10^{-9}$&$1.33\times 10^{-9}$&nc\tabularnewline
+~~Temperature&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$&$40$&$17$&$17$&nc\tabularnewline
+~~Zooplankton&\textit{ZKa}&$0.05$&$1\times 10^{11}$&$2.5\times 10^{12}$&$1.12\times 10^{12}$&$1.12\times 10^{12}$&nc\tabularnewline
+~~&\textit{ZQn}&$0.02$&$1\times 10^{-6}$&$2.04\times 10^{-4}$&$6.95\times 10^{-5}$&$6.95\times 10^{-5}$&nc\tabularnewline
+~~&\textit{Zm}&$0.02$&$1\times 10^{-4}$&$10$&$7.2\times 10^{-4}$&$7.2\times 10^{-4}$&nc\tabularnewline
+~~&\textit{Zumax}&$0.02$&$5\times 10^{8}$&$2\times 10^{9}$&$9.45\times 10^{8}$&$9.45\times 10^{8}$&nc\tabularnewline
+\hline
+{\bfseries 2}&&&&&&&\tabularnewline
+~~Independent of category&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$1.12$&nc\tabularnewline
+~~&\textit{ZKa}&$0.05$&$1\times 10^{11}$&$2.5\times 10^{12}$&$1.12\times 10^{12}$&$1.12\times 10^{12}$&nc\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$&$0.5$&$0.11$&$0.09$&--21\tabularnewline
+~~&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$&$40$&$17$&$17$&nc\tabularnewline
+~~&\textit{ZQn}&$0.02$&$1\times 10^{-6}$&$2.04\times 10^{-4}$&$6.95\times 10^{-5}$&$6.95\times 10^{-5}$&nc\tabularnewline
+~~&\textit{alpha}&$0.02$&$1\times 10^{-17}$&$6\times 10^{-16}$&$3.96\times 10^{-16}$&$6\times 10^{-16}$&+52\tabularnewline
+~~&\textit{Zm}&$0.02$&$1\times 10^{-4}$&$10$&$7.2\times 10^{-4}$&$7.2\times 10^{-4}$&nc\tabularnewline
+~~&\textit{Zumax}&$0.02$&$5\times 10^{8}$&$2\times 10^{9}$&$9.45\times 10^{8}$&$9.45\times 10^{8}$&nc\tabularnewline
+\hline
+{\bfseries 3}&&&&&&&\tabularnewline
+~~Equally within category&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$1.47$&+32\tabularnewline
+~~&\textit{ZKa}&$0.05$&$1\times 10^{11}$&$2.5\times 10^{12}$&$1.12\times 10^{12}$&$1.12\times 10^{12}$&nc\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$&$0.5$&$0.11$&$0.1$&--11\tabularnewline
+~~&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$&$40$&$17$&$17$&nc\tabularnewline
+~~&\textit{ZQn}&$0.02$&$1\times 10^{-6}$&$2.04\times 10^{-4}$&$6.95\times 10^{-5}$&$6.95\times 10^{-5}$&nc\tabularnewline
+~~&\textit{KG1}&$6.15\times 10^{-3}$&$5$&$100$&$30$&$5$&--83\tabularnewline
+~~&\textit{astar490}&$7.51\times 10^{-4}$&$0.02$&$0.12$&$0.04$&$0.04$&nc\tabularnewline
+\hline
+\end{tabular}\end{center}}
+\end{table}
+
 \clearpage

### 2017-08-16 ident_manu.Rnw
adding new text for bottles

@@
 Selected parameter subsets from the seven heuristics were used to calibrate the \ac{zerod} model.
-This analysis demonstrated that different parameter sets can produce model output with differing goodness and fit and calibration effort given
+This analysis demonstrated that different parameter sets can produce model output with differing goodness of fit and calibration effort given
 \begin{inparaenum}[1\upshape)]
@@
 
-A time series of \ac{do} from Weeks Bay, Alabama was used for model calibration.
-Daily observations from January 1\textsuperscript{st},  2006 to January 1\textsuperscript{st}, 2007 at the Weeks Bay station of the Weeks Bay National Estuarine Reserve were used \citep{Wenner04}.
-We chose this location because of the availability of data for model calibration compared to bottom waters in the northern \ac{gom} and the system exhibits hypoxia from eutrophication.
-This application also provided a practical example of how the FishTank model could be calibrated using data from alternative locations.
-Initial conditions for model input were modified to match conditions in Weeks Bay using observed water quality and nutrient data (all data from \url{http://cdmo.baruch.sc.edu/}).
-The \ac{do} time series was filtered to reduce physical effects of the tidal advection component on the observed data (\textit{sensu} \citealt{Beck15b}).
-As such, the filtered data were comparable to a time series with no physical advection to match conditions of the \ac{zerod} FishTank model with no hydrodynamic component.
-
-Each parameter subset was calibrated to most closely match the model output to the observed time series.
+Estimates of oxygen production from closed bottle experiments were used to calibrate the \ac{zerod} model.
+Surface water was collected from a fixed location in Pensacola Bay, Florida () on September 25\textsuperscript{th}, 2013.
+Water samples were placed into closed 100 mL glass bottles at the time of collection and transported back to the lab for treatments.
+Concentrations of \ac{do} and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection.
+Oxygen concentrations were established using Winkler reagents (Parsons et al.
+1985) and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.
+Ammonium was analyzed using a fluorometric method (Holmes et al.
+1999); other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods (APHA 2005).
+
+Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using three treatments: light, dark, and light plus nutrients.
+All treatments were exposed to ambient outdoor conditions in a water bath with continuous flow at the laboratory.
+The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
+The nutrient treatments were supplemented with an equal mix of 25 mmol m$^{-3}$ of ammonium and nitrate and 1.7 mmol m$^{-3}$, approximately two orders of magnitude above ambient concentrations.
+The exposure experiments began at 7am and were concluded at 7pm, after which the concentrations of \ac{do} in each bottle were measured.
+Four replicates of each treatment were used.
+HOBO\textsuperscript{\textregistered} pendants were used to measure continous temperature and light for each treatment.
+
+Each parameter subset was calibrated to the ending \ac{do} concentration for each of the four replicates of each treatment.
+The intial concentrations and treatments were used as starting conditions for FishTank.
+The corresponding continous temperature and light measurements were also used as forcing conditions for the model.
 Parameter values were searched using the optim function in R that implemented the limited memory modification of the BFGS quasi-Newton method \citep{Byrd95,Nocedal06,RDCT17}.
 This optimization scheme searches for values within the user-defined lower and upper bounds of each parameter.
-We set the algorithm to search within +/- 50\% of the default parameter values.
-While we recognize that `actual' parameter values could possibly extend beyond this range, constraining the values to the range tested herein was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
+We set the algorithm to search within a range of values for a subset that was chosen to best reflect expections given professional judgment and reasonable bounds from the literature.
+While we recognize that `actual' parameter values could possibly extend beyond these ranges, constraining the values was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
 Moreover, precise limits on each parameter were less of a concern for the current analysis as our primary goal was to demonstrate differences in fit as a function of sensitivity and identifiability.

### 2017-08-16 ident_manu.tex
adding new text for bottles

@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Tue Aug 15 15:08:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/c0ce23e253cb1532614d91ec7a60ed5b8e91e26f}{c0ce23e253cb1532614d91ec7a60ed5b8e91e26f}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Tue Aug 15 18:37:33 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/b9430cdc1b195b992ae6ea786f8e485723cf540c}{b9430cdc1b195b992ae6ea786f8e485723cf540c}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 
-A time series of \ac{do} from Weeks Bay, Alabama was used for model calibration.
-Daily observations from January 1\textsuperscript{st},  2006 to January 1\textsuperscript{st}, 2007 at the Weeks Bay station of the Weeks Bay National Estuarine Reserve were used \citep{Wenner04}.
-We chose this location because of the availability of data for model calibration compared to bottom waters in the northern \ac{gom} and the system exhibits hypoxia from eutrophication.
-This application also provided a practical example of how the FishTank model could be calibrated using data from alternative locations.
-Initial conditions for model input were modified to match conditions in Weeks Bay using observed water quality and nutrient data (all data from \url{http://cdmo.baruch.sc.edu/}).
-The \ac{do} time series was filtered to reduce physical effects of the tidal advection component on the observed data (\textit{sensu} \citealt{Beck15b}).
-As such, the filtered data were comparable to a time series with no physical advection to match conditions of the \ac{zerod} FishTank model with no hydrodynamic component.
-
-Each parameter subset was calibrated to most closely match the model output to the observed time series.
-Parameter values were searched using the optim function in R that implemented the limited memory modification of the BFGS quasi-Newton method \citep{Byrd95,Nocedal06,RDCT17}.
+Estimates of oxygen production from closed bottle experiments were used to calibrate the \ac{zerod} model.
+Surface water was collected from a fixed location in Pensacola Bay, Florida () on September 25\textsuperscript{th}, 2013.
+Water samples were placed into closed 100 mL glass bottles at the time of collection and transported back to the lab for treatments.
+Concentrations of \ac{do} and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection.
+Oxygen concentrations were established using Winkler reagents (Parsons et al.
+1985) and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.
+Ammonium was analyzed using a fluorometric method (Holmes et al.
+1999); other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods (APHA 2005).
+
+Oxygen production after an approximate 12 hour period was estimated within the bottles using three treatments: light, dark, and light plus nutrients.
+All treatments were allowed to sit under ambient outdoor conditions in a water bath with continuous flow at the laboratory.
+The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
+The nutrient treatments were supplemented with an equal mix of 25 mmol m$^{-3}$ of ammonium and nitrate and 1.7 mmol m$^{-3}$, approximately two order of magnitude above ambient concentrations.
+The exposure experiments began at 7am and were concluded at 7pm, after which the concentrations of \ac{do} in each bottle were measured.
+Four replicates of each treatment were used.
+HOBO\textsuperscript{\textregistered} pendants were used to measure continous temperature and light for each treatment.
+
+Each parameter subset was calibrated to the ending \ac{do} concentration for each of the four replicates per treatment.
+The intial values Parameter values were searched using the optim function in R that implemented the limited memory modification of the BFGS quasi-Newton method \citep{Byrd95,Nocedal06,RDCT17}.
 This optimization scheme searches for values within the user-defined lower and upper bounds of each parameter.
-We set the algorithm to search within +/- 50\% of the default parameter values.
+We set the algorithm to search within an expected range chosen by the authors to best reflect...
 While we recognize that `actual' parameter values could possibly extend beyond this range, constraining the values to the range tested herein was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
@@
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
-For example, only three iterations were required to optimize the single parameter selected for the temperature category, whereas 136 iterations were required for the eight parameters selected independent of category.
+For example, only three iterations were required to optimize the single parameter selected for the temperature category, whereas 289 iterations were required for the eight parameters selected independent of category.
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $35.17$ mmol O$_2$ m$^{-3}$, reduction to $35.15$, $35.16$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($35.17$).
+Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $35.33$ mmol O$_2$ m$^{-3}$, reduction to $35.29$, $35.32$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($35.33$).
 Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
@@
 {\bfseries 1}&&&&&\tabularnewline
-~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$7$&$35.17$\tabularnewline
-~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$286$&$35.05$\tabularnewline
-~~Phytoplankton&$3.97$&$7$&$0.02$&$255$&$35.03$\tabularnewline
-~~Temperature&$1$&$1$&$0.02$&$3$&$35.17$\tabularnewline
-~~Zooplankton&$5.2$&$4$&$0.03$&$9$&$35.17$\tabularnewline
+~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$133$&$35.33$\tabularnewline
+~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$231$&$35.33$\tabularnewline
+~~Phytoplankton&$3.97$&$7$&$0.02$&$180$&$34.63$\tabularnewline
+~~Temperature&$1$&$1$&$0.02$&$3$&$35.33$\tabularnewline
+~~Zooplankton&$5.2$&$4$&$0.03$&$117$&$35.32$\tabularnewline
 \hline
 {\bfseries 2}&&&&&\tabularnewline
-~~Independent of category&$6.81$&$8$&$0.03$&$136$&$35.15$\tabularnewline
+~~Independent of category&$6.81$&$8$&$0.03$&$289$&$35.29$\tabularnewline
 \hline
 {\bfseries 3}&&&&&\tabularnewline
-~~Equally within category&$5.22$&$7$&$0.03$&$105$&$35.16$\tabularnewline
+~~Equally within category&$5.22$&$7$&$0.03$&$180$&$35.32$\tabularnewline
 \hline
 \end{tabular}\end{center}}
-\footnotesize *Starting \ac{rmse} $35.17$\end{table}
+\footnotesize *Starting \ac{rmse} $35.33$\end{table}
 
@@
 {\bfseries 1}&&&&&&&\tabularnewline
-~~Optics&\textit{astar490}&$7.51\times 10^{-4}$&$0.02$&$0.12$&$0.04$&$0.04$&nc\tabularnewline
+~~Optics&\textit{astar490}&$7.51\times 10^{-4}$&$0.02$&$0.12$&$0.04$&$0.04$&-0\tabularnewline
 ~~&\textit{astarOMZ}&$4.92\times 10^{-5}$&$0.01$&$0.15$&$0.01$&$0.01$&nc\tabularnewline
 ~~&\textit{astarOMA}&$4.39\times 10^{-5}$&$0.01$&$0.15$&$0.01$&$0.01$&nc\tabularnewline
-~~Organic Matter&\textit{KG1}&$6.15\times 10^{-3}$&$5$&$100$&$30$&$48.04$&+60\tabularnewline
-~~&\textit{KG2}&$3.14\times 10^{-3}$&$5$&$100$&$30$&$33.21$&+11\tabularnewline
+~~Organic Matter&\textit{KG1}&$6.15\times 10^{-3}$&$5$&$100$&$30$&$30.02$&+0\tabularnewline
+~~&\textit{KG2}&$3.14\times 10^{-3}$&$5$&$100$&$30$&$30.06$&+0\tabularnewline
 ~~&\textit{KstarO2}&$3.04\times 10^{-3}$&$1$&$100$&$10$&$10$&nc\tabularnewline
 ~~&\textit{KGcdom}&$2.98\times 10^{-3}$&$0$&$1$&$0.01$&$0.01$&nc\tabularnewline
-~~&\textit{KO2}&$5.85\times 10^{-4}$&$1$&$100$&$10$&$100$&+900\tabularnewline
+~~&\textit{KO2}&$5.85\times 10^{-4}$&$1$&$100$&$10$&$10.18$&+2\tabularnewline
 ~~Phytoplankton&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$2.5$&+123\tabularnewline
@@
 ~~&\textit{ZQn}&$0.02$&$1\times 10^{-6}$&$2.04\times 10^{-4}$&$6.95\times 10^{-5}$&$6.95\times 10^{-5}$&nc\tabularnewline
-~~&\textit{Zm}&$0.02$&$1\times 10^{-4}$&$10$&$7.2\times 10^{-4}$&$7.2\times 10^{-4}$&nc\tabularnewline
+~~&\textit{Zm}&$0.02$&$1\times 10^{-4}$&$10$&$7.2\times 10^{-4}$&$6.96\times 10^{-3}$&+867\tabularnewline
 ~~&\textit{Zumax}&$0.02$&$5\times 10^{8}$&$2\times 10^{9}$&$9.45\times 10^{8}$&$9.45\times 10^{8}$&nc\tabularnewline
@@
 {\bfseries 2}&&&&&&&\tabularnewline
-~~Independent of category&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$1.12$&nc\tabularnewline
+~~Independent of category&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$2.5$&+123\tabularnewline
 ~~&\textit{ZKa}&$0.05$&$1\times 10^{11}$&$2.5\times 10^{12}$&$1.12\times 10^{12}$&$1.12\times 10^{12}$&nc\tabularnewline
-~~&\textit{mA}&$0.02$&$0.01$&$0.5$&$0.11$&$0.09$&--21\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$&$0.5$&$0.11$&$0.01$&--91\tabularnewline
 ~~&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$&$40$&$17$&$17$&nc\tabularnewline
@@
 ~~&\textit{alpha}&$0.02$&$1\times 10^{-17}$&$6\times 10^{-16}$&$3.96\times 10^{-16}$&$6\times 10^{-16}$&+52\tabularnewline
-~~&\textit{Zm}&$0.02$&$1\times 10^{-4}$&$10$&$7.2\times 10^{-4}$&$7.2\times 10^{-4}$&nc\tabularnewline
+~~&\textit{Zm}&$0.02$&$1\times 10^{-4}$&$10$&$7.2\times 10^{-4}$&$5.47\times 10^{-3}$&+660\tabularnewline
 ~~&\textit{Zumax}&$0.02$&$5\times 10^{8}$&$2\times 10^{9}$&$9.45\times 10^{8}$&$9.45\times 10^{8}$&nc\tabularnewline
@@
 {\bfseries 3}&&&&&&&\tabularnewline
-~~Equally within category&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$1.47$&+32\tabularnewline
+~~Equally within category&\textit{umax}&$0.05$&$0.1$&$2.5$&$1.12$&$2.5$&+123\tabularnewline
 ~~&\textit{ZKa}&$0.05$&$1\times 10^{11}$&$2.5\times 10^{12}$&$1.12\times 10^{12}$&$1.12\times 10^{12}$&nc\tabularnewline
-~~&\textit{mA}&$0.02$&$0.01$&$0.5$&$0.11$&$0.1$&--11\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$&$0.5$&$0.11$&$0.01$&--91\tabularnewline
 ~~&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$&$40$&$17$&$17$&nc\tabularnewline
 ~~&\textit{ZQn}&$0.02$&$1\times 10^{-6}$&$2.04\times 10^{-4}$&$6.95\times 10^{-5}$&$6.95\times 10^{-5}$&nc\tabularnewline
-~~&\textit{KG1}&$6.15\times 10^{-3}$&$5$&$100$&$30$&$5$&--83\tabularnewline
-~~&\textit{astar490}&$7.51\times 10^{-4}$&$0.02$&$0.12$&$0.04$&$0.04$&nc\tabularnewline
+~~&\textit{KG1}&$6.15\times 10^{-3}$&$5$&$100$&$30$&$28.11$&--6\tabularnewline
+~~&\textit{astar490}&$7.51\times 10^{-4}$&$0.02$&$0.12$&$0.04$&$0.03$&--12\tabularnewline
 \hline

### 2017-08-17 revision/review_response.Rnw
almost done with revision

@@
 
-{\it }
+{\it We present a thorough recalibration of the model }
 
@@
 This is obviously incorrect and represents a clear limitation of the paper.
+
+{\it
+
+Calibration the model to the Weeks Bay data was meant to demonstrate application of the parameter selection heuristics to improve insight into model behavior.
+We agree with the reviewer that this application is not entirely appropriate given the potential hydrodynamic influences on the observed data.
+However, we still argue that unit-testing is an efficient means of improving larger models that are computationally intensive.
+To address the concern of the reviewer and to maintain our emphasis on unit-testing, we have chosen a a more appropriate dataset, described below.
+In addition, we have added this sentence to the the final paragraph of the introduction to emphasize the benefits of our zero-dimensional model.
+
+'In general, the analysis makes a case for unit-testing with lower-dimensional models, particularly when computional limitations preclude the use of conventional optimization algorithms with larger three-dimensional models.'
+
+The new dataset was
+
+For the discussion:
+
+'However, calibration to most parameter sets showed little improvement in model fit despite relatively large changes in parameter values.
+This result underscores the challenge of model optimization when conidering many parameters.
+Although we demonstrated model sensitivity to individual parameters, the interactive effects are also important.
+For example, optimization to zooplankton parameters showed almost no change in model \ac{rmse} despite a relatively large sensitivity of the model to individual parameters.
+A more comprehensive approach that considers the interaction of zooplankton parameters with others, such as phytoplankton, is warranted given the structural dependencies betwen parameter cateogires.
+Indeed, the reduction in \ac{rmse} for selection heuristics that weighted the parameter categories equally showed the scond largest reduction in model error.'
+}
 

### 2017-08-17 ident_manu.Rnw
almost done with revision

@@
 \renewcommand{\figurename}{Fig.}
+
+% aliased citations
+\defcitealias{APHA05}{APHA 2005}
+\defcitealias{MurrellIR}{Murrell et al. in revision}
 
@@
 As a result, parameter selection heuristics were used to identify parameters for model calibration that depended on combined effects on output, relative sensitivity of each parameter, and ecological categories for the biogeochemical equations.
-The calibrated \ac{zerod} unit of the hypoxia model had improved fit to the observed data if sensitive parameters were included in an identifiable subset.
+The calibrated \ac{zerod} unit of the hypoxia model had improved fit to the observed data if sensitive phytoplankton parameters were included in an identifiable subset.
 Extension of results to a three-dimensional grid of the Gulf of Mexico showed that sensitive parameters for the \ac{zerod} model translated to non-trivial changes in the areal estimates of hypoxia.
@@
 This study describes a sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.
+In general, the analysis makes a case for unit-testing with lower-dimensional models, particularly when computional limitations preclude the use of conventional optimization algorithms with larger three-dimensional models.
 The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifiability constraints.
@@
 \end{inparaenum}
-The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model fit.
+The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics for optimization.
 Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability of the results.
@@
 Estimates of oxygen production from closed bottle experiments were used to calibrate the \ac{zerod} model.
-Surface water was collected from a fixed location in Pensacola Bay, Florida () on September 25\textsuperscript{th}, 2013.
+Surface water was collected from a fixed location in Pensacola Bay, Florida (30.35$^{\circ}$ N, 87.20$^{\circ}$ W) on September 25\textsuperscript{th}, 2013 (full details in \citetalias{MurrellIR}).
 Water samples were placed into closed 100 mL glass bottles at the time of collection and transported back to the lab for treatments.
 Concentrations of \ac{do} and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection.
-Oxygen concentrations were established using Winkler reagents (Parsons et al.
-1985) and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.
-Ammonium was analyzed using a fluorometric method (Holmes et al.
-1999); other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods (APHA 2005).
-
-Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using three treatments: light, dark, and light plus nutrients.
+Oxygen concentrations were established using Winkler reagents \citep{Parsons85} and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.
+Ammonium was analyzed using a fluorometric method \citep{Holmes99}; other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods \citepalias{APHA05}.
+
+Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using light and dark treaments.
 All treatments were exposed to ambient outdoor conditions in a water bath with continuous flow at the laboratory.
 The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
-The nutrient treatments were supplemented with an equal mix of 25 mmol m$^{-3}$ of ammonium and nitrate and 1.7 mmol m$^{-3}$, approximately two orders of magnitude above ambient concentrations.
 The exposure experiments began at 7am and were concluded at 7pm, after which the concentrations of \ac{do} in each bottle were measured.
-Four replicates of each treatment were used.
-HOBO\textsuperscript{\textregistered} pendants were used to measure continous temperature and light for each treatment.
-
-Each parameter subset was calibrated to the ending \ac{do} concentration for each of the four replicates of each treatment.
-The intial concentrations and treatments were used as starting conditions for FishTank.
-The corresponding continous temperature and light measurements were also used as forcing conditions for the model.
+Each treatment had four replicates and HOBO\textsuperscript{\textregistered} pendants were used to measure continuous temperature and light.
+
+Each parameter subset in \cref{tab:heurist1,tab:heurist2,tab:heurist3} for \ac{do} was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
+The intial nutrient and oxygen concentrations were used as starting conditions for FishTank.
+The corresponding continuous temperature and light measurements were also used as forcing conditions.
 Parameter values were searched using the optim function in R that implemented the limited memory modification of the BFGS quasi-Newton method \citep{Byrd95,Nocedal06,RDCT17}.
 This optimization scheme searches for values within the user-defined lower and upper bounds of each parameter.
-We set the algorithm to search within a range of values for a subset that was chosen to best reflect expections given professional judgment and reasonable bounds from the literature.
+We set the algorithm to search within a range of values for a subset that was chosen to best reflect expectations given professional judgment and reasonable bounds from the literature.
 While we recognize that `actual' parameter values could possibly extend beyond these ranges, constraining the values was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
@@
   scinot(.)
-# 72.13955
 
@@
 cattop <- filter(caldat, heurist %in% 'Equally within category')
+phyto <- filter(caldat, heurist %in% 'Phytoplankton')
+
+# for individual parameters
+
+ests <- map(cals, 'par') %>%
+  map(enframe, name = 'parm', value = 'val') %>% 
+  enframe(name = 'heurist') %>%
+  unnest %>% 
+  mutate(var = 'calib') %>% 
+  select(heurist, var, parm, val)
+
+rngs <- get_cmbs(tocal_all, out_var = 'O2', thrsh = 15, coll = T, errs = TRUE, pert = NULL) %>% 
+  lapply(function(x){
+    x[c('error', 'vals', 'minv', 'maxv')] %>% 
+      bind_rows(.id = 'var') %>% 
+      gather('parm', 'val', -var)
+  }) %>% 
+  enframe(name = 'heurist') %>% 
+  unnest
+
+prch <- rbind(ests, rngs) %>% 
+  spread('var', 'val') %>% 
+  mutate(
+    pchg = 100 * (calib - vals) / vals,
+    pchg = ifelse(pchg > 0, round(pchg, 1), 
+      ifelse(pchg < 0, round(pchg, 1), NA)
+    ),
+    minv = sapply(minv, scinot), 
+    maxv = sapply(maxv, scinot), 
+    vals = vals,
+    calib = sapply(calib, scinot),
+    rgrp = ifelse(heurist == 'top', '2', ifelse(heurist == 'cattop', '3', '1')), 
+    heurist = factor(heurist, levels = levs, labels = labs), 
+    parm = par_txt(parm)
+  ) %>% 
+  unite('minmax', minv, maxv, sep = '/') %>% 
+  select(rgrp, heurist, parm, error, minmax, vals, calib, pchg) %>% 
+  arrange(heurist, -error) %>% 
+  mutate(
+    heurist = as.character(heurist), 
+    heurist = ifelse(duplicated(heurist), '', heurist)
+    ) 
+nc <- prch %>% 
+  filter(is.na(pchg))
+ncmax <- prch[which.max(prch$pchg), ]
 @
@@
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
-For example, only \Sexpr{toeng(temp$its)[[1]]} iterations were required to optimize the single parameter selected for the temperature category, whereas \Sexpr{top$its} iterations were required for the \Sexpr{toeng(top$nprm)[[1]]} parameters selected independent of category.
+For example, only \Sexpr{toeng(temp$its)[[1]]} iterations were required to optimize the single parameter selected for the temperature category, whereas \Sexpr{phyto$its} iterations were required for the \Sexpr{toeng(phyto$nprm)[[1]]} parameters selected for phytoplankton (\cref{fig:calex}).
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt} mmol O$_2$ m$^{-3}$, reduction to \Sexpr{scinot(top$rmse)}, \Sexpr{scinot(cattop$rmse)}, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction (\Sexpr{scinot(optics$rmse)}).
-Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
-Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 (\Sexpr{scinot(optics$avee)}, \Sexpr{toeng(optics$nprm)} parameters), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 (\Sexpr{scinot(top$avee)}, \Sexpr{toeng(top$nprm)} parameters, \cref{tab:calib}).
+Of the seven parameter subsets, the optimal phytoplankton parameters had the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt} mmol O$_2$ m$^{-3}$, reduction to \Sexpr{scinot(phyto$rmse)}).
+The identifiable parameters selected equally within categories (third heuristic) and independent of category (second heuristic) produced the second and third greatest reduction in \ac{rmse} (\Sexpr{scinot(cattop$rmse)}, and \Sexpr{scinot(top$rmse)}, respectively), although much less than that observed for phytoplankton parametrs.
+Overall, calibration to most of the parameter subsets had a small effect on \ac{rmse}.
+However, the magnitude of parameter changes for calibration varied up to several orders of magnitude from the initial values (\cref{tab:calibprm}).
+The percent change in parameters from the intial values varied from no change (Optics parameters \Sexpr{nc$parm[1]} and \Sexpr{nc$prm[2]}) to 900\% (\Sexpr{ncmax$parm}).
+Many calibrated parameter values included those at the lower or upper bounds used for the optimization routine (as for phytoplankton, \cref{fig:calex}).
+There was no relationship between magnitude of parameter changes within a subset and overall reduction of \ac{rmse}.
 
@@
 The identifiable parameter subsets varied considerably between state variables and the method for parameter selection.
-Use of identifiable parameter subsets with sensitive parameters improved model fit and results for the smaller model were scalable to the 3-dimensional model.
-However, an evaluation of sensitivity and identifiability of relevant parameter sets is a preliminary and simplistic approach to improving model predictions.
-We have provided a general approach to select parameter subsets for further model development depending on the ecological context (i.e., selection by parameter category, selection for specific state variables).
-Thus, the results described above have relevance for model refinement with the specific goal of better understanding ecological dynamics that moderate hypoxia on the northern \ac{gom}.
-The general principles of sensitivity and parameter identifiability have broad applicability beyond this context and we argue that such methods should be more universally applied as an initial approach to quantify numerical constraints of biogeochemical models.
+Use of identifiable parameter subsets with sensitive parameters improved model fit, particularly for phytoplankton parameters.
+However, calibration to most parameter sets showed little improvement in model fit despite relatively large changes in parameter values.
+This result underscores the challenge of model optimization when conidering many parameters.
+Although we demonstrated model sensitivity to individual parameters, the interactive effects are also important.
+For example, optimization to zooplankton parameters showed almost no change in model \ac{rmse} despite a relatively large sensitivity of the model to individual parameters.
+A more comprehensive approach that considers the interaction of zooplankton parameters with others, such as phytoplankton, is warranted given the structural dependencies betwen parameter cateogires.
+Indeed, the reduction in \ac{rmse} for selection heuristics that weighted the parameter categories equally showed the second largest reduction in model error.
 
@@
 We thank the research staff of the USEPA Gulf Ecology Division, Environmental Modeling and Visualization Laboratory, and Naval Research Laboratory for their efforts developing the hydrodynamic and biogeochemical components of \ac{cgem}.
-We thank James Pauer, Yonghsan Wan, and Susan Elizabeth George for providing helpful comments on an earlier draft.
+We thank James Pauer, Yonghsan Wan, Susan Elizabeth George, and an anonymous reviewer for providing helpful comments on an earlier draft.
+We thank Michael Murrell for assistance with the bottle dataset.
 
@@
 
+% for abbreviated journal names
+<<eval = F, echo = F>>=
+library(Jabbrev)
+bbl_ext('ident_manu.bbl', 'refs.bib')
+bib_shr('refs_kp.bib')
+file.copy('refs_kp_new.bib', 'refsshr.bib', overwrite = TRUE)
+file.remove(c('refs_kp.bib', 'refs_kp_new.bib'))
+@
 % \bibliography{refs}
@@
 <<parmtab, eval = T, cache = F>>=
-parmtab(tabsize = 'tiny')
+parmtab(tabsize = 'scriptsize')
 @
@@
   mutate(
-    pchg = 100 * (calib - vals)/vals,
-    pchg = ifelse(pchg > 0, paste0('+', round(pchg, 0)), 
-      ifelse(pchg < 0, paste0('-', round(pchg, 0)), 'nc')
+    pchg = 100 * (calib - vals) / vals,
+    pchg = ifelse(pchg > 0, paste0('+', round(pchg, 1)), 
+      ifelse(pchg < 0, paste0('-', round(pchg, 1)), 'nc')
     ),
@@
   ) %>% 
-  select(rgrp, heurist, parm, error, minv, maxv, vals, calib, pchg) %>% 
+  unite('minmax', minv, maxv, sep = '/') %>% 
+  select(rgrp, heurist, parm, error, minmax, vals, calib, pchg) %>% 
   arrange(heurist, -error) %>% 
@@
 The calibration routing was bounded by minimum and maximum values appropriate for each parameter.'
-colnms <- c('Parameter', 'L1', 'Min', 'Max', 'Initial', 'Final', '\\% change')
+colnms <- c('Parameter', 'L1', 'Min/Max', 'Initial', 'Final', '\\% change')
 

### 2017-08-17 ident_manu.tex
almost done with revision

--- 2017-08-15 ident_manu.tex
@@
 
+% aliased citations
+\defcitealias{APHA05}{APHA 2005}
+\defcitealias{MurrellIR}{Murrell et al. in revision}
+
 %acronyms
@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Sun Aug 6 08:21:57 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/c03d0df749cea19daced8a68105265cf1ed2a63e}{c03d0df749cea19daced8a68105265cf1ed2a63e}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Wed Aug 16 18:18:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/b081f900ad818adbbf496e0b8888820e38bda065}{b081f900ad818adbbf496e0b8888820e38bda065}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 
-A time series of \ac{do} from Weeks Bay, Alabama was used for model calibration.
-Daily observations from January 1\textsuperscript{st},  2006 to January 1\textsuperscript{st}, 2007 at the Weeks Bay station of the Weeks Bay National Estuarine Reserve were used \citep{Wenner04}.
-We chose this location because of the availability of data for model calibration compared to bottom waters in the northern \ac{gom} and the system exhibits hypoxia from eutrophication.
-This application also provided a practical example of how the FishTank model could be calibrated using data from alternative locations.
-Initial conditions for model input were modified to match conditions in Weeks Bay using observed water quality and nutrient data (all data from \url{http://cdmo.baruch.sc.edu/}).
-The \ac{do} time series was filtered to reduce physical effects of the tidal advection component on the observed data (\textit{sensu} \citealt{Beck15b}).
-As such, the filtered data were comparable to a time series with no physical advection to match conditions of the \ac{zerod} FishTank model with no hydrodynamic component.
-
-Each parameter subset was calibrated to most closely match the model output to the observed time series.
+Estimates of oxygen production from closed bottle experiments were used to calibrate the \ac{zerod} model.
+Surface water was collected from a fixed location in Pensacola Bay, Florida (30.35$^{\circ}$ N, 87.20$^{\circ}$ W) on September 25\textsuperscript{th}, 2013 (full details in \citetalias{MurrellIR}).
+Water samples were placed into closed 100 mL glass bottles at the time of collection and transported back to the lab for treatments.
+Concentrations of \ac{do} and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection.
+Oxygen concentrations were established using Winkler reagents \citep{Parsons85} and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.
+Ammonium was analyzed using a fluorometric method \citep{Holmes99}; other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods \citepalias{APHA05}.
+
+Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using light and dark treaments.
+All treatments were exposed to ambient outdoor conditions in a water bath with continuous flow at the laboratory.
+The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
+The exposure experiments began at 7am and were concluded at 7pm, after which the concentrations of \ac{do} in each bottle were measured.
+Each treatment had four replicates and HOBO\textsuperscript{\textregistered} pendants were used to measure continuous temperature and light.
+
+Each parameter subset in \cref{tab:heurist1,tab:heurist2,tab:heurist3} for \ac{do} was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
+The intial nutrient and oxygen concentrations were used as starting conditions for FishTank.
+The corresponding continuous temperature and light measurements were also used as forcing conditions.
 Parameter values were searched using the optim function in R that implemented the limited memory modification of the BFGS quasi-Newton method \citep{Byrd95,Nocedal06,RDCT17}.
 This optimization scheme searches for values within the user-defined lower and upper bounds of each parameter.
-We set the algorithm to search within +/- 50\% of the default parameter values.
-While we recognize that `actual' parameter values could possibly extend beyond this range, constraining the values to the range tested herein was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
+We set the algorithm to search within a range of values for a subset that was chosen to best reflect expectations given professional judgment and reasonable bounds from the literature.
+While we recognize that `actual' parameter values could possibly extend beyond these ranges, constraining the values was expected to produce output that was more interpretable within the context of the sensitivity functions defined above.
 Moreover, precise limits on each parameter were less of a concern for the current analysis as our primary goal was to demonstrate differences in fit as a function of sensitivity and identifiability.
@@
 Although \ac{do} had the greatest sensitivity to parameters in the zooplankton category (as percentage of total), the relative effects varied.
-Among all parameters, average sensitivity was $L1 = $ $9.2\times 10^{-3}$ with values ranging from $L1 = $ $8.34\times 10^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton).
-Within categories (excluding temperature with one sensitive parameter), sensitivity ranged from $4.39\times 10^{-5}$ (\textit{astarOMA}) to $7.51\times 10^{-4}$ (\textit{astar490}) for optics, $4.17\times 10^{-4}$ (\textit{KNH4}) to $6.15\times 10^{-3}$ (\textit{KG1}) for organic matter, $8.34\times 10^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69\times 10^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton (\cref{tab:dosens}).
-Average sensitivity values in each category were $L1 = $ $2.81\times 10^{-4}$ for optics, $2.17\times 10^{-3}$ for organic matter, $0.02$ for temperature, $0.01$ for phytoplankton, and $0.01$ for zooplankton.
+Among all parameters, average sensitivity was $L1 = $ $9.2e^{-3}$ with values ranging from $L1 = $ $8.34e^{-8}$ for \textit{QminP} (phytoplankton) to $0.05$ for \textit{umax} (phytoplankton).
+Within categories (excluding temperature with one sensitive parameter), sensitivity ranged from $4.39e^{-5}$ (\textit{astarOMA}) to $7.51e^{-4}$ (\textit{astar490}) for optics, $4.17e^{-4}$ (\textit{KNH4}) to $6.15e^{-3}$ (\textit{KG1}) for organic matter, $8.34e^{-8}$ (\textit{QminP}) to $0.05$ (\textit{umax}) for phytoplankton, and $3.69e^{-5}$ (\textit{ZQp}) to $0.05$ (\textit{ZKa}) for zooplankton (\cref{tab:dosens}).
+Average sensitivity values in each category were $L1 = $ $2.81e^{-4}$ for optics, $2.17e^{-3}$ for organic matter, $0.02$ for temperature, $0.01$ for phytoplankton, and $0.01$ for zooplankton.
 
@@
 Average $L1$ ranged from $0.02$ for irradiance (\cref{tab:irrsens}) to $0.71$ for \ac{dom} (\cref{tab:om2sens}).
-All average sensitivity values for the state variables were higher than the average for \ac{do} ($L1$ = $9.2\times 10^{-3}$).
-For each variable, $L1$ ranged from $2.24\times 10^{-6}$ (\textit{QminP}) to $8.49$ (\textit{mA}) for ammonium (\cref{tab:nh4sens}), $1.38\times 10^{-6}$ (\textit{QminP}) to $13.94$ (\textit{mA}) for \ac{chla} (\cref{tab:chlsens}), $1.92\times 10^{-7}$ (\textit{QminP}) to $0.13$ (\textit{ZKa}) for irradiance (\cref{tab:irrsens}), $6.67\times 10^{-7}$ (\textit{QminP}) to $8.49$ (\textit{umax}) for nitrate (\cref{tab:no3sens}), $6.41\times 10^{-5}$ (\textit{KNH4}) to $7.22$ (\textit{mA}) for \ac{pom} (\cref{tab:om1sens}),  $7.41\times 10^{-5}$ (\textit{KNH4}) to $14.25$ (\textit{mA}) for \ac{dom} (\cref{tab:om2sens}), and $8.21\times 10^{-7}$ (\textit{QminP}) to $1.47$ (\textit{ZKa}) for phosphate (\cref{tab:po4sens}).
+All average sensitivity values for the state variables were higher than the average for \ac{do} ($L1$ = $9.2e^{-3}$).
+For each variable, $L1$ ranged from $2.24e^{-6}$ (\textit{QminP}) to $8.49$ (\textit{mA}) for ammonium (\cref{tab:nh4sens}), $1.38e^{-6}$ (\textit{QminP}) to $13.94$ (\textit{mA}) for \ac{chla} (\cref{tab:chlsens}), $1.92e^{-7}$ (\textit{QminP}) to $0.13$ (\textit{ZKa}) for irradiance (\cref{tab:irrsens}), $6.67e^{-7}$ (\textit{QminP}) to $8.49$ (\textit{umax}) for nitrate (\cref{tab:no3sens}), $6.41e^{-5}$ (\textit{KNH4}) to $7.22$ (\textit{mA}) for \ac{pom} (\cref{tab:om1sens}),  $7.41e^{-5}$ (\textit{KNH4}) to $14.25$ (\textit{mA}) for \ac{dom} (\cref{tab:om2sens}), and $8.21e^{-7}$ (\textit{QminP}) to $1.47$ (\textit{ZKa}) for phosphate (\cref{tab:po4sens}).
 For the parameter categories, ammonium was most sensitive to phytoplankton parameters (average $L1$ = $0.8$ across all parameters in the category), \ac{chla} to phytoplankton ($L1$ = $1.14$), irradiance to zooplankton ($L1$ = $0.03$), nitrate to zooplankton ($L1$ = $1.06$), \ac{pom} to temperature ($L1$ = $0.86$), \ac{dom} to temperature ($L1$ = $1.48$), and phosphate to zooplankton ($L1$ = $0.31$).
-Finally, average sensitivity between parameter categories independent of the state variables ranged from $8.38\times 10^{-3}$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
+Finally, average sensitivity between parameter categories independent of the state variables ranged from $8.38e^{-3}$ for optics (average $L1$ across all variables) to $0.62$ for phytoplankton.
 
@@
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
-For example, only three iterations were required to optimize the single parameter selected for the temperature category, whereas 136 iterations were required for the eight parameters selected independent of category.
+For example, only 12 iterations were required to optimize the single parameter selected for the temperature category, whereas 615 iterations were required for the seven parameters selected for phytoplankton (\cref{fig:calex}).
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, selection independent of parameter category and equally within each category produced the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $35.17$ mmol O$_2$ m$^{-3}$, reduction to $35.15$, $35.16$, respectively), whereas the optimal values for parameters in the Optics category had the smallest reduction ($35.17$).
-Lower \ac{rmse} was associated with higher average sensitivity of a parameter subset.
-Parameters selected only in the optics category had the highest \ac{rmse} and lowest average L1 ($2.81\times 10^{-4}$, three parameters), whereas parameters selected independent of category had the lowest \ac{rmse} and highest average L1 ($0.03$, eight parameters, \cref{tab:calib}).
-
-The estimated areal extent of bottom-water hypoxia using default parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at $1.19\times 10^{4}$ km$^2$ (\cref{fig:areachg}a, August mean area 8988 $\pm$ 551 km$^2$, \cref{fig:areachg}b).
+Of the seven parameter subsets, the optimal phytoplankton parameters had the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $21.14$ mmol O$_2$ m$^{-3}$, reduction to $5.81$).
+The identifiable parameters selected equally within categories (third heuristic) and independent of category (second heuristic) produced the second and third greatest reduction in \ac{rmse} ($19.09$, and $19.45$, respectively), although much less than that observed for phytoplankton parametrs.
+Overall, calibration to most of the parameter subsets had a small effect on \ac{rmse}.
+However, the magnitude of parameter changes for calibration varied up to several orders of magnitude from the initial values (\cref{tab:calibprm}).
+The percent change in parameters from the intial values varied from no change (Optics parameters \textit{astarOMZ} and ) to 900\% (\textit{KO2}).
+Many calibrated parameter values included those at the lower or upper bounds used for the optimization routine (as for phytoplankton, \cref{fig:calex}).
+There was no relationship between magnitude of parameter changes within a subset and overall reduction of \ac{rmse}.
+
+The estimated areal extent of bottom-water hypoxia using default parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at $1.19e^{4}$ km$^2$ (\cref{fig:areachg}a, August mean area 8988 $\pm$ 551 km$^2$, \cref{fig:areachg}b).
 Increases in the top sensitive parameters for \ac{do} in each category (\cref{tab:dosens}) increased the estimated areal extent of hypoxia (Figs.
@@
 \clearpage
+
+% for abbreviated journal names
 
@@
 \begin{table}[!tbp]
-{\tiny
+{\scriptsize
 \caption{FishTank parameters evaluated for sensitivity and identifiability.
@@
 {\bfseries Phytoplankton}&&&&\tabularnewline
-~~initial slope of photosynthesis v irradiance&\textit{alpha}&10$^{-16}$ cm$^2$ s quanta$^{-1}$ d$^{-1}$&$8.42\times 10^{-17}$&$1.26\times 10^{-16}$\tabularnewline
+~~initial slope of photosynthesis v irradiance&\textit{alpha}&10$^{-16}$ cm$^2$ s quanta$^{-1}$ d$^{-1}$&$8.42e^{-17}$&$1.26e^{-16}$\tabularnewline
 ~~coefficient for non-limiting nutrient&\textit{aN}&-&$1$&$1.5$\tabularnewline
-~~phytoplankton threshold for grazing&\textit{Athresh}&10$^7$ cells m$^{-3}$&$1.72\times 10^{8}$&$2.58\times 10^{8}$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&10$^7$ cells m$^{-3}$&$1.72e^{8}$&$2.58e^{8}$\tabularnewline
 ~~edibility vector for Z1&\textit{ediblevector(Z1)}&-&$0.25$&$0.38$\tabularnewline
@@
 ~~mortality coefficient&\textit{mA}&d$^{-1}$&$0.1$&$0.15$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&10$^{-7}$ mmol C cell$^{-1}$&$1.35\times 10^{-6}$&$2.03\times 10^{-6}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&10$^{-9}$ mmol N cell$^{-1}$&$6.08\times 10^{-9}$&$9.12\times 10^{-9}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&10$^{-9}$ mmol P cell$^{-1}$&$6.19\times 10^{-10}$&$9.29\times 10^{-10}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&10$^{-7}$ mmol C cell$^{-1}$&$1.35e^{-6}$&$2.03e^{-6}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&10$^{-9}$ mmol N cell$^{-1}$&$6.08e^{-9}$&$9.12e^{-9}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&10$^{-9}$ mmol P cell$^{-1}$&$6.19e^{-10}$&$9.29e^{-10}$\tabularnewline
 ~~phytoplankton basal respiration coefficient&\textit{respb}&d$^{-1}$&$0.02$&$0.03$\tabularnewline
@@
 ~~maximum growth rate&\textit{umax}&d$^{-1}$&$0.41$&$0.62$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$4.1\times 10^{-8}$&$6.15\times 10^{-8}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$2.68\times 10^{-8}$&$4.02\times 10^{-8}$\tabularnewline
-~~Si-uptake rate measured at umax&\textit{vmaxSi}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$4.1\times 10^{-8}$&$6.15\times 10^{-8}$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$\mu$m$^3$&$3.37\times 10^{4}$&$5.05\times 10^{4}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$4.1e^{-8}$&$6.15e^{-8}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$2.68e^{-8}$&$4.02e^{-8}$\tabularnewline
+~~Si-uptake rate measured at umax&\textit{vmaxSi}&10$^{-8}$ mmol cell$^{-1}$ d$^{-1}$&$4.1e^{-8}$&$6.15e^{-8}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$\mu$m$^3$&$3.37e^{4}$&$5.05e^{4}$\tabularnewline
 \hline
@@
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&-&$0.4$&$0.6$\tabularnewline
-~~half saturation coefficient for grazing&\textit{ZKa}&$\mu$m$^3$ m$^{-3}$&$1.12\times 10^{12}$&$1.68\times 10^{12}$\tabularnewline
-~~quadratic mortality constant&\textit{Zm}&m$^6$ ind$^{-2}$ d$^{-1}$&$7.2\times 10^{-4}$&$0$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&mmol C ind$^{-1}$&$3.13\times 10^{-4}$&$4.7\times 10^{-4}$\tabularnewline
-~~zooplankton nitrogen/individual&\textit{ZQn}&mmol N ind$^{-1}$&$6.95\times 10^{-5}$&$1.04\times 10^{-4}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&mmol P ind$^{-1}$&$3.77\times 10^{-6}$&$5.66\times 10^{-6}$\tabularnewline
+~~half saturation coefficient for grazing&\textit{ZKa}&$\mu$m$^3$ m$^{-3}$&$1.12e^{12}$&$1.68e^{12}$\tabularnewline
+~~quadratic mortality constant&\textit{Zm}&m$^6$ ind$^{-2}$ d$^{-1}$&$7.2e^{-4}$&$0$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&mmol C ind$^{-1}$&$3.13e^{-4}$&$4.7e^{-4}$\tabularnewline
+~~zooplankton nitrogen/individual&\textit{ZQn}&mmol N ind$^{-1}$&$6.95e^{-5}$&$1.04e^{-4}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&mmol P ind$^{-1}$&$3.77e^{-6}$&$5.66e^{-6}$\tabularnewline
 ~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&d$^{-1}$&$0.1$&$0.15$\tabularnewline
@@
 ~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&-&$0.25$&$0.38$\tabularnewline
-~~maximum growth rate of zooplankton&\textit{Zumax}&$\mu$m$^3$ ind$^{-1}$ d$^{-1}$&$9.45\times 10^{7}$&$1.42\times 10^{8}$\tabularnewline
-~~zooplankton volume/individual&\textit{Zvolcell}&$\mu$m$^3$ ind$^{-1}$&$2.98\times 10^{7}$&$4.47\times 10^{7}$\tabularnewline
+~~maximum growth rate of zooplankton&\textit{Zumax}&$\mu$m$^3$ ind$^{-1}$ d$^{-1}$&$9.45e^{7}$&$1.42e^{8}$\tabularnewline
+~~zooplankton volume/individual&\textit{Zvolcell}&$\mu$m$^3$ ind$^{-1}$&$2.98e^{7}$&$4.47e^{7}$\tabularnewline
 \hline
@@
 {\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$7.51\times 10^{-4}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.92\times 10^{-5}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.39\times 10^{-5}$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$7.51e^{-4}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.92e^{-5}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.39e^{-5}$\tabularnewline
 \hline
 {\bfseries Organic Matter}&&\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
-~~decay rate of CDOM&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$4.99\times 10^{-4}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$4.17\times 10^{-4}$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$6.15e^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$3.14e^{-3}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04e^{-3}$\tabularnewline
+~~decay rate of CDOM&\textit{KGcdom}&$2.98e^{-3}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85e^{-4}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$5.8e^{-4}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$4.99e^{-4}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$4.17e^{-4}$\tabularnewline
 \hline
@@
 ~~phytoplankton carbon/cell&\textit{Qc}&$0.01$\tabularnewline
-~~phytoplankton growth respiration coefficient&\textit{respg}&$8.36\times 10^{-3}$\tabularnewline
-~~N-uptake rate measured at umax&\textit{vmaxN}&$8.12\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$6.94\times 10^{-3}$\tabularnewline
-~~phytoplankton threshold for grazing&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$4.32\times 10^{-3}$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$4.27\times 10^{-3}$\tabularnewline
-~~coefficient for non-limiting nutrient&\textit{aN}&$4.23\times 10^{-3}$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$4.13\times 10^{-3}$\tabularnewline
-~~half-saturation constant for P&\textit{Kp}&$2.9\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$2.77\times 10^{-4}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$8.34\times 10^{-8}$\tabularnewline
+~~phytoplankton growth respiration coefficient&\textit{respg}&$8.36e^{-3}$\tabularnewline
+~~N-uptake rate measured at umax&\textit{vmaxN}&$8.12e^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$6.94e^{-3}$\tabularnewline
+~~phytoplankton threshold for grazing&\textit{Athresh}&$4.57e^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$4.32e^{-3}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$4.27e^{-3}$\tabularnewline
+~~coefficient for non-limiting nutrient&\textit{aN}&$4.23e^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$4.13e^{-3}$\tabularnewline
+~~half-saturation constant for P&\textit{Kp}&$2.9e^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$2.77e^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$8.34e^{-8}$\tabularnewline
 \hline
@@
 ~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.01$\tabularnewline
-~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
-~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
-~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$9.38\times 10^{-5}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$3.69\times 10^{-5}$\tabularnewline
+~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78e^{-3}$\tabularnewline
+~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32e^{-3}$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96e^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$9.38e^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$3.69e^{-5}$\tabularnewline
 \hline
@@
 ~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.02$&$1$\textsubscript{T}&$2.29$\tabularnewline
-~~4&\scriptsize{\textit{KG1}}&$6.15\times 10^{-3}$&$1$\textsubscript{OM}&$3.85$\tabularnewline
-~~5&\scriptsize{\textit{astar490}}&$7.51\times 10^{-4}$&$1$\textsubscript{O}&$3.89$\tabularnewline
+~~4&\scriptsize{\textit{KG1}}&$6.15e^{-3}$&$1$\textsubscript{OM}&$3.85$\tabularnewline
+~~5&\scriptsize{\textit{astar490}}&$7.51e^{-4}$&$1$\textsubscript{O}&$3.89$\tabularnewline
 ~~6&\scriptsize{\textit{mA}}&$0.02$&$2$\textsubscript{P}&$4.42$\tabularnewline
@@
 ~~7&\scriptsize{\textit{mA}}&$0.05$&$2$\textsubscript{P}&$11.21$\tabularnewline
-~~8&\scriptsize{\textit{KG1}}&$3.96\times 10^{-3}$&$2$\textsubscript{OM}&$14.65$\tabularnewline
-~~9&\scriptsize{\textit{astarOMA}}&$1.47\times 10^{-3}$&$2$\textsubscript{O}&$14.72$\tabularnewline
+~~8&\scriptsize{\textit{KG1}}&$3.96e^{-3}$&$2$\textsubscript{OM}&$14.65$\tabularnewline
+~~9&\scriptsize{\textit{astarOMA}}&$1.47e^{-3}$&$2$\textsubscript{O}&$14.72$\tabularnewline
 \hline
@@
 {\bfseries 1}&&&&&\tabularnewline
-~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$7$&$35.17$\tabularnewline
-~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$286$&$35.05$\tabularnewline
-~~Phytoplankton&$3.97$&$7$&$0.02$&$255$&$35.03$\tabularnewline
-~~Temperature&$1$&$1$&$0.02$&$3$&$35.17$\tabularnewline
-~~Zooplankton&$5.2$&$4$&$0.03$&$9$&$35.17$\tabularnewline
+~~Optics&$3.87$&$3$&$2.81e^{-4}$&$14$&$21.14$\tabularnewline
+~~Organic Matter&$8.61$&$5$&$3.18e^{-3}$&$132$&$20.6$\tabularnewline
+~~Phytoplankton&$3.97$&$7$&$0.02$&$615$&$5.81$\tabularnewline
+~~Temperature&$1$&$1$&$0.02$&$12$&$21.14$\tabularnewline
+~~Zooplankton&$5.2$&$4$&$0.03$&$54$&$21.14$\tabularnewline
 \hline
 {\bfseries 2}&&&&&\tabularnewline
-~~Independent of category&$6.81$&$8$&$0.03$&$136$&$35.15$\tabularnewline
+~~Independent of category&$6.81$&$8$&$0.03$&$221$&$19.45$\tabularnewline
 \hline
 {\bfseries 3}&&&&&\tabularnewline
-~~Equally within category&$5.22$&$7$&$0.03$&$105$&$35.16$\tabularnewline
+~~Equally within category&$5.22$&$7$&$0.03$&$435$&$19.09$\tabularnewline
 \hline
 \end{tabular}\end{center}}
-\footnotesize *Starting \ac{rmse} $35.17$\end{table}
+\footnotesize *Starting \ac{rmse} $21.14$\end{table}
+
+% do ending parameter values
+%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selection heuristic",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:calibprm", rowname = totab$heurist, rgroup = names(table(totab$rgrp)),     n.rgroup = as.numeric(table(totab$rgrp)), colheads = colnms)%
+\begin{table}[!tbp]
+{\scriptsize
+\caption{Results of parameter changes from model calibration to observed \ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third).
+The parameters of each subset are from \cref{tab:heurist1,tab:heurist2,tab:heurist3}.
+The L1 values are relative sensitivity of \ac{do} to a paramter change.
+Starting and final parameter values after calibration are shown, including the percent change.
+The calibration routing was bounded by minimum and maximum values appropriate for each parameter.\label{tab:calibprm}}
+\begin{center}
+\begin{tabular}{lllllll}
+\hline\hline
+\multicolumn{1}{l}{Selection heuristic}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{Min/Max}&\multicolumn{1}{c}{Initial}&\multicolumn{1}{c}{Final}&\multicolumn{1}{c}{\% change}\tabularnewline
+\hline
+{\bfseries 1}&&&&&&\tabularnewline
+~~Optics&\textit{astar490}&$7.51e^{-4}$&$0.02$/$0.12$&$0.04$&$0.04$&--0.3\tabularnewline
+~~&\textit{astarOMZ}&$4.92e^{-5}$&$0.01$/$0.15$&$0.01$&$0.01$&nc\tabularnewline
+~~&\textit{astarOMA}&$4.39e^{-5}$&$0.01$/$0.15$&$0.01$&$0.01$&nc\tabularnewline
+~~Organic Matter&\textit{KG1}&$6.15e^{-3}$&$5$/$100$&$30$&$5$&--83.3\tabularnewline
+~~&\textit{KG2}&$3.14e^{-3}$&$5$/$100$&$30$&$52.31$&+74.4\tabularnewline
+~~&\textit{KstarO2}&$3.04e^{-3}$&$1$/$100$&$10$&$10.01$&+0.1\tabularnewline
+~~&\textit{KGcdom}&$2.98e^{-3}$&$0$/$1$&$0.01$&$0.01$&+0.1\tabularnewline
+~~&\textit{KO2}&$5.85e^{-4}$&$1$/$100$&$10$&$100$&+900\tabularnewline
+~~Phytoplankton&\textit{umax}&$0.05$&$0.1$/$2.5$&$1.12$&$2.49$&+121.9\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$/$0.5$&$0.11$&$0.07$&--38.9\tabularnewline
+~~&\textit{alpha}&$0.02$&$1e^{-17}$/$6e^{-16}$&$3.96e^{-16}$&$6e^{-16}$&+51.5\tabularnewline
+~~&\textit{ediblevector(Z1)}&$0.02$&$0.05$/$1$&$0.5$&$0.37$&--26.5\tabularnewline
+~~&\textit{Qc}&$0.01$&$1e^{-9}$/$5e^{-7}$&$4.54e^{-8}$&$3.21e^{-7}$&+606.3\tabularnewline
+~~&\textit{respg}&$8.36e^{-3}$&$0.01$/$0.5$&$0.1$&$0.01$&--89.6\tabularnewline
+~~&\textit{vmaxN}&$8.12e^{-3}$&$1e^{-11}$/$1e^{-8}$&$1.33e^{-9}$&$1.35e^{-9}$&+1.8\tabularnewline
+~~Temperature&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$/$40$&$17$&$16.5$&--2.9\tabularnewline
+~~Zooplankton&\textit{ZKa}&$0.05$&$1e^{11}$/$2.5e^{12}$&$1.12e^{12}$&$1.61e^{12}$&+43.6\tabularnewline
+~~&\textit{ZQn}&$0.02$&$1e^{-6}$/$2.04e^{-4}$&$6.95e^{-5}$&$7.53e^{-5}$&+8.3\tabularnewline
+~~&\textit{Zm}&$0.02$&$1e^{-4}$/$10$&$7.2e^{-4}$&$8.9e^{-4}$&+23.6\tabularnewline
+~~&\textit{Zumax}&$0.02$&$5e^{8}$/$2e^{9}$&$9.45e^{8}$&$5.33e^{8}$&--43.6\tabularnewline
+\hline
+{\bfseries 2}&&&&&&\tabularnewline
+~~Independent of category&\textit{umax}&$0.05$&$0.1$/$2.5$&$1.12$&$2.5$&+123.2\tabularnewline
+~~&\textit{ZKa}&$0.05$&$1e^{11}$/$2.5e^{12}$&$1.12e^{12}$&$2.5e^{12}$&+123.2\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$/$0.5$&$0.11$&$0.01$&--90.9\tabularnewline
+~~&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$/$40$&$17$&$5.82$&--65.7\tabularnewline
+~~&\textit{ZQn}&$0.02$&$1e^{-6}$/$2.04e^{-4}$&$6.95e^{-5}$&$7.04e^{-5}$&+1.2\tabularnewline
+~~&\textit{alpha}&$0.02$&$1e^{-17}$/$6e^{-16}$&$3.96e^{-16}$&$6e^{-16}$&+51.5\tabularnewline
+~~&\textit{Zm}&$0.02$&$1e^{-4}$/$10$&$7.2e^{-4}$&$1.07e^{-3}$&+48.9\tabularnewline
+~~&\textit{Zumax}&$0.02$&$5e^{8}$/$2e^{9}$&$9.45e^{8}$&$5e^{8}$&--47.1\tabularnewline
+\hline
+{\bfseries 3}&&&&&&\tabularnewline
+~~Equally within category&\textit{umax}&$0.05$&$0.1$/$2.5$&$1.12$&$2.5$&+123.2\tabularnewline
+~~&\textit{ZKa}&$0.05$&$1e^{11}$/$2.5e^{12}$&$1.12e^{12}$&$2.5e^{12}$&+123.2\tabularnewline
+~~&\textit{mA}&$0.02$&$0.01$/$0.5$&$0.11$&$0.01$&--90.9\tabularnewline
+~~&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$&$0$/$40$&$17$&$12.2$&--28.2\tabularnewline
+~~&\textit{ZQn}&$0.02$&$1e^{-6}$/$2.04e^{-4}$&$6.95e^{-5}$&$8.87e^{-5}$&+27.6\tabularnewline
+~~&\textit{KG1}&$6.15e^{-3}$&$5$/$100$&$30$&$5$&--83.3\tabularnewline
+~~&\textit{astar490}&$7.51e^{-4}$&$0.02$/$0.12$&$0.04$&$0.02$&--46.7\tabularnewline
+\hline
+\end{tabular}\end{center}}
+\end{table}
 
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.63\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.5\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.63e^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.5e^{-3}$\tabularnewline
 \hline
@@
 ~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.03$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$7.55e^{-3}$\tabularnewline
 \hline
@@
 ~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$2.24\times 10^{-6}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$2.24e^{-6}$\tabularnewline
 \hline
@@
 ~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.16$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.07\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$1.44\times 10^{-4}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.07e^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$1.44e^{-4}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.45\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.13\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.45e^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.13e^{-3}$\tabularnewline
 \hline
@@
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.01$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.35\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$3.4\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$2.97\times 10^{-5}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.35e^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19e^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$3.4e^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$2.97e^{-5}$\tabularnewline
 \hline
@@
 ~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$1.38\times 10^{-6}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$1.38e^{-6}$\tabularnewline
 \hline
@@
 ~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.14$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.29\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$7.55\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.29e^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$7.55e^{-5}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.47\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.34\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.47e^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.34e^{-3}$\tabularnewline
 \hline
@@
 ~~decay rate of CDOM&\textit{KGcdom}&$0.05$\tabularnewline
-~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
-~~turnover rate for OM2A and OM2Z&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.2\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.54\times 10^{-4}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$1.72\times 10^{-6}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$1.48\times 10^{-6}$\tabularnewline
+~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96e^{-3}$\tabularnewline
+~~turnover rate for OM2A and OM2Z&\textit{KG2}&$9.88e^{-4}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.2e^{-4}$\tabularnewline
+~~half-saturation concentration for O2 utilization&\textit{KO2}&$3.54e^{-4}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$6.18e^{-5}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$1.72e^{-6}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$1.48e^{-6}$\tabularnewline
 \hline
@@
 ~~half-saturation constant for P&\textit{Kp}&$0.01$\tabularnewline
-~~P-uptake rate measured at umax&\textit{vmaxP}&$9.48\times 10^{-3}$\tabularnewline
-~~phytoplankton basal respiration coefficient&\textit{respb}&$9.38\times 10^{-3}$\tabularnewline
-~~phytoplankton volume/cell&\textit{volcell}&$8.1\times 10^{-3}$\tabularnewline
-~~minimum N cell-quota&\textit{QminN}&$5.75\times 10^{-3}$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$3.78\times 10^{-3}$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$9.81\times 10^{-4}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$1.92\times 10^{-7}$\tabularnewline
+~~P-uptake rate measured at umax&\textit{vmaxP}&$9.48e^{-3}$\tabularnewline
+~~phytoplankton basal respiration coefficient&\textit{respb}&$9.38e^{-3}$\tabularnewline
+~~phytoplankton volume/cell&\textit{volcell}&$8.1e^{-3}$\tabularnewline
+~~minimum N cell-quota&\textit{QminN}&$5.75e^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$3.78e^{-3}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$9.81e^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$1.92e^{-7}$\tabularnewline
 \hline
@@
 ~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
-~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$9.34\times 10^{-5}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$1.99\times 10^{-5}$\tabularnewline
+~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67e^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$9.34e^{-5}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$1.99e^{-5}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.27\times 10^{-3}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.19\times 10^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.27e^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.19e^{-3}$\tabularnewline
 \hline
@@
 ~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$9.96\times 10^{-3}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$9.87\times 10^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$9.96e^{-3}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$9.87e^{-3}$\tabularnewline
 \hline
@@
 ~~phytoplankton basal respiration coefficient&\textit{respb}&$0.07$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$7.06\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$6.67\times 10^{-7}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$7.06e^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$6.67e^{-7}$\tabularnewline
 \hline
@@
 ~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.8\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$8.59\times 10^{-4}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.8e^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$8.59e^{-4}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.03$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.73\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.49\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.73e^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$1.49e^{-3}$\tabularnewline
 \hline
@@
 ~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$6.98\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$6.41\times 10^{-5}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$3.72e^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$6.98e^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$6.41e^{-5}$\tabularnewline
 \hline
@@
 ~~half-saturation constant for N&\textit{Kn}&$0.01$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$7.35\times 10^{-4}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$7.35e^{-4}$\tabularnewline
 \hline
@@
 ~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$9.64\times 10^{-3}$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.06\times 10^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$9.64e^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.06e^{-3}$\tabularnewline
 \hline
@@
 ~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$2.48\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$2.04\times 10^{-3}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$2.48e^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$2.04e^{-3}$\tabularnewline
 \hline
@@
 ~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$0.03$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$8.44\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$7.41\times 10^{-5}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$3.16e^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$8.44e^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$7.41e^{-5}$\tabularnewline
 \hline
@@
 ~~half-saturation constant for N&\textit{Kn}&$0.02$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$4.37\times 10^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$4.37e^{-3}$\tabularnewline
 \hline
@@
 ~~zooplankton carbon/individual&\textit{ZQc}&$0.04$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$1.69\times 10^{-3}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$1.69e^{-3}$\tabularnewline
 \hline
@@
 {\bfseries Optics}&&\tabularnewline
-~~Chla specific absorption at 490 nm&\textit{astar490}&$9.01\times 10^{-3}$\tabularnewline
-~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$5.21\times 10^{-4}$\tabularnewline
-~~OMA specific absorption at 490 nm&\textit{astarOMA}&$5.13\times 10^{-4}$\tabularnewline
+~~Chla specific absorption at 490 nm&\textit{astar490}&$9.01e^{-3}$\tabularnewline
+~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$5.21e^{-4}$\tabularnewline
+~~OMA specific absorption at 490 nm&\textit{astarOMA}&$5.13e^{-4}$\tabularnewline
 \hline
@@
 ~~half-saturation concentration for O2 utilization&\textit{KO2}&$0.01$\tabularnewline
-~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.29\times 10^{-3}$\tabularnewline
-~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline
-~~maximum rate of nitrification per day&\textit{nitmax}&$2.7\times 10^{-5}$\tabularnewline
-~~NH4 rate constant for nitrification&\textit{KNH4}&$2.64\times 10^{-5}$\tabularnewline
+~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$7.29e^{-3}$\tabularnewline
+~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19e^{-3}$\tabularnewline
+~~maximum rate of nitrification per day&\textit{nitmax}&$2.7e^{-5}$\tabularnewline
+~~NH4 rate constant for nitrification&\textit{KNH4}&$2.64e^{-5}$\tabularnewline
 \hline
@@
 ~~half-saturation constant for P&\textit{Kp}&$0.03$\tabularnewline
-~~half-saturation constant for N&\textit{Kn}&$6.97\times 10^{-3}$\tabularnewline
-~~phytoplankton carbon/cell&\textit{Qc}&$6.68\times 10^{-3}$\tabularnewline
-~~minimum P cell-quota&\textit{QminP}&$8.21\times 10^{-7}$\tabularnewline
+~~half-saturation constant for N&\textit{Kn}&$6.97e^{-3}$\tabularnewline
+~~phytoplankton carbon/cell&\textit{Qc}&$6.68e^{-3}$\tabularnewline
+~~minimum P cell-quota&\textit{QminP}&$8.21e^{-7}$\tabularnewline
 \hline
@@
 ~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline
-~~zooplankton phosphorus/individual&\textit{ZQp}&$6.43\times 10^{-3}$\tabularnewline
-~~zooplankton carbon/individual&\textit{ZQc}&$3.38\times 10^{-5}$\tabularnewline
+~~zooplankton phosphorus/individual&\textit{ZQp}&$6.43e^{-3}$\tabularnewline
+~~zooplankton carbon/individual&\textit{ZQc}&$3.38e^{-5}$\tabularnewline
 \hline

### 2017-08-17 R/funcs.R

@@ -56,7 +56,7 @@ scinot <- function(x, pow = 2, digits = 2, showDollar = TRUE)
     exponent <- floor(log10(x))
     if (exponent & abs(exponent) > pow) {
         xx <- round(x / 10^exponent, digits=digits)
-        e <- paste("\\times 10^{", as.integer(exponent), "}", sep="")
+        e <- paste("e^{", as.integer(exponent), "}", sep="")
     } else {
         xx <- round(x, digits=digits)
         e <- ""

### 2017-08-18 revision/review_response.Rnw
revision resubmitted

--- 2017-08-04 revision/review_response.Rnw
@@
 \documentclass[letterpaper,12pt]{article}
-\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
+\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
 \usepackage{setspace}
-\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{indentfirst}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage[final]{animate}
-\usepackage{graphicx}
-\usepackage{verbatim}
-\usepackage{rotating}
-\usepackage{tabularx}
-\usepackage{array}
-\usepackage{subfig} 
-\usepackage[noae]{Sweave}
+\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
+\usepackage{lineno}
 \usepackage{cleveref}
-\usepackage[figureposition=bottom]{caption}
+\usepackage{acronym}
 \usepackage{paralist}
-\usepackage{acronym}
-\usepackage{outlines}
-\usepackage{amsmath}
+\usepackage{bm}
+\usepackage{fixltx2e}
 
@@
 options(replace.assign=TRUE,width=90,digits=1)
+@
+
+%setup
+<<message = F, warning = F>>=
+library(tidyverse)
 @
@@
 
-{\it We thank the editor and reviewer for providing thoughtful comments on our manuscript.
-Responses to these comments are shown in italics.
-Page and paragraph numbers refer to the revised manuscript.}
+{\it We thank the editor and reviewer for providing helpful comments on our manuscript.  Responses to these comments are shown in italics.}
 
@@
 
-{\it We have added Table 1 that inccudes a full list and description of parameters that were evaluated for the sensitivity analysis.
+{\it We have added Table 1 that includes a full list and description of parameters that were evaluated for the sensitivity analysis.
 This table includes short and long descriptions, units, and starting values.
@@
 
-{\it }
+{\it We present a thorough recalibration of the model with an alternative dataset described below.  Please see our responses to the reviewer.}
 
@@
 
+{\it
+
+We agree with the reviewer that this application is not entirely appropriate given the hydrodynamic influences on the observed data.
+However, our objective was to demonstrate that unit-testing of the zero-dimensional is an efficient means of improving larger models that are computationally intensive.
+Our intent was not to present a complete predictive model with hydrodynamic forcing to Weeks Bay.
+To address the concern of the reviewer and to maintain our emphasis on unit-testing, we have chosen a a more appropriate dataset, described below.
+A sentence added to the final paragraph of the introduction emphasizes our intent of the analysis:
+
+'In general, the analysis makes a case for unit-testing with lower-dimensional models, particularly when computional limitations preclude the use of conventional optimization algorithms with larger three-dimensional models.'
+
+An alternative dataset was used that included flask experiments of oxygen production from Pensacola Bay, Florida.
+This dataset included light and dark treatments of water samples in closed bottles for an approximate 12-hour period, including before and after measurements of DO concentrations with initial nutrient values for each treatment and replicate.
+The dataset is described in detail in Murrell et al.
+in revision (Murrell, M.
+C., Caffrey, J.
+C., Marcovich, D.
+T., Beck, M.
+W., Jarvis, B.
+M., III, J.
+D.
+H., in revision.
+Seasonal oxygen dynamics in a warm temperate estuary: Effects of hydrologic variability on measurements of primary production, respiration, and net metabolism.
+Estuaries Coasts - (-), –.).
+Methods were added to the manuscript, Sec.
+2.4:
+
+`Estimates of oxygen production from closed bottle experiments were used to calibrate the 0-D model.
+Surface water was collected from a fixed location in Pensacola Bay, Florida (30.35$^{\circ}$ N, 87.20$^{\circ}$ W) on September 25\textsuperscript{th}, 2013 (full details in Murrell et al.
+in revision).
+Water samples were placed into closed 300 mL glass bottles and transported back to the lab for treatments.
+Concentrations of O$_2$ and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection.
+Oxygen concentrations were established using Winkler reagents (Parsons et al.
+1985) and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.
+Ammonium was analyzed using a fluorometric method (Holmes et al.
+1999); other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods (APHA 2005).
+
+<<echo = F>>=
+load(file = '../data/flaskdo.RData')
+source('../R/funcs.R')
+
+flsk <- flaskdo %>% 
+  select(-rep, -tmt_rep, -stt, -end) %>% 
+  gather('var', 'val', -tmt) %>% 
+  group_by(tmt, var) %>%
+  summarise(
+    se = sapply(sd(val)/sqrt(length(val)), scinot),
+    val = sapply(mean(val), scinot)
+    )
+
+ltstt <- flsk %>% 
+  filter(tmt %in% 'lt' & var %in% 'sttO2')
+ltend <- flsk %>% 
+  filter(tmt %in% 'lt' & var %in% 'endO2')
+dkstt <- flsk %>% 
+  filter(tmt %in% 'dk' & var %in% 'sttO2')
+dkend <- flsk %>% 
+  filter(tmt %in% 'dk' & var %in% 'endO2')
+initam <- flsk %>% 
+  filter(var %in% 'NH4')
+initno <- flsk %>% 
+  filter(var %in% 'NO3')
+initsi <- flsk %>% 
+  filter(var %in% 'Si')
+initpo <- flsk %>% 
+  filter(var %in% 'PO4')
+@
+
+Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using light and dark treaments.
+All treatments were exposed to ambient outdoor conditions in a water bath at the laboratory.
+The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
+The exposure experiments began at 7am and were concluded at 7pm, after which the concentrations of O$_2$ in each bottle were measured.
+Each treatment had four replicates and HOBO\textsuperscript{\textregistered} pendants were used to measure continuous temperature and light.
+Starting O$_2$ concentrations for the experiments were \Sexpr{ltstt$val} ($\pm$ \Sexpr{ltstt$se}) mmol O$_2$ m$^{-3}$ and ending concentrations were \Sexpr{ltend$val} ($\pm$ \Sexpr{ltend$se}) mmol O$_2$ m$^{-3}$ for the light treatments and \Sexpr{dkend$val} ($\pm$ \Sexpr{dkend$se}) mmol O$_2$ m$^{-3}$ for the dark treatments.
+Initial nutrient concentrations were \Sexpr{initam$val[1]} mmol m$^{-3}$ for NH$_4^+$ (single sample), \Sexpr{initpo$val[1]} mmol m$^{-3}$ for PO$_4^{3-}$, and \Sexpr{initsi$val[1]} mmol m$^{-3}$ for SiO$_3^{2-}$.
+Concentrations for NO$_2^-$ and NO$_3^-$ were below detection limit.
+
+Each parameter subset for O$_2$ from the selection heuristics was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
+The intial nutrient and oxygen concentrations were used as starting conditions for FishTank.
+The corresponding continuous temperature and light measurements were also used as forcing conditions.
+Parameter values were searched using the optim function...
+'
+}
+
 For the sensitivity analysis the authors manipulated the observations of DO in the estuary filtering the tidal impacts to be able to implement the FishTank model.
@@
 
+{\it
+
+Our use of the flask experimental data addresses these concerns.
+The initial and ending DO concentrations for the experimental data, including intial nutrient concentrations, were reported in our revision to the methods.
+We have also added Table 7 for more details on the calibration results for each parameter subset.
+In addition, Figure 7 was added (old Figure 7 is now Figure 8) to demonstrate the opimization routine using the phytoplankton parameter set in Table 3 for dissolved oxygen.
+
+The new results for the experimental data present some interesting challenges that demonstrated how unit-testing can inform model understanding.
+The implications of the analysis were described in an addition to the discussion, sec.
+4.1:
+
+`..However, calibration to most parameter sets showed little improvement in model fit despite relatively large changes in parameter values.
+This result underscores the challenge of model optimization when conidering many parameters.
+Although we demonstrated model sensitivity to individual parameters, the interactive effects are also important.
+For example, optimization to zooplankton parameters showed almost no change in model \it{RMSE} despite a relatively large sensitivity of the model to individual parameters.
+A more comprehensive approach that considers the interaction of zooplankton parameters with others, such as phytoplankton, is warranted given the structural dependencies betwen parameter categories.
+Indeed, the reduction in \it{RMSE} for selection heuristics that equally considered the parameter categories (third heuristic) showed the second largest reduction in model error.
+This subset included both phytoplankton and zooplankton parameters, suggesting more careful consideration of these sensitive parameters could further improve model calibration.'
+
+}
+
 Please also describe what are the forcing conditions of the FishTank model. There are two tributary rivers in Weeks Bay and one outlet condition. How is each one simulated in your FishTank model?.
+
+{\it Please see the description above justifying our use of the new dataset.}
 
@@
 
-`The development of a model represents a tradeoff between achieving predictive accuracy and a realistic representation of environmental processes....
-Given that these characteristics cannot be simultaneously achieved, models are developed that balance predictive accuracy with environmental realism, often favoring one at the expense of the other.'
+`The development of a model represents a tradeoff between achieving predictive accuracy and a realistic representation of environmental processes [...] Given that these characteristics cannot be simultaneously achieved, models are developed to balance predictive accuracy with environmental realism or often favor one at the expense of the other.'
 
@@
 {\it We have found that precision is commonly used in the literature to describe goodness of fit, although we understand the distinction made by the reviewer.
-Considering an example where observed data represent a biased sample of an environmental process (e.g., infrequent or unevent sampling of an event that varies over time), model calibration to these data can only possibly achieve precision.
+Considering an example where observed data represent a biased sample of an environmental process (e.g., infrequent or uneven sampling of an event that varies over time), model calibration to these data can only ever achieve precision.
 Although practitioners would not knowingly use observed data that are biased for model calibration, we are certain that many ecological datasets are incomplete representations of actual processes.
@@
 
-{\it RMSE units are reported as mmol o2 m-3 and was added to the text.}
+{\it RMSE units are reported as mmol o2 m-3, which was added to the text.}
 

### 2017-08-18 revision/review_response.tex
revision resubmitted

--- 2017-08-04 revision/review_response.tex
@@
 \usepackage{alltt}
-\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
+\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
 \usepackage{setspace}
-\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{indentfirst}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage[final]{animate}
-\usepackage{graphicx}
-\usepackage{verbatim}
-\usepackage{rotating}
-\usepackage{tabularx}
-\usepackage{array}
-\usepackage{subfig} 
-\usepackage[noae]{Sweave}
+\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
+\usepackage{lineno}
 \usepackage{cleveref}
-\usepackage[figureposition=bottom]{caption}
+\usepackage{acronym}
 \usepackage{paralist}
-\usepackage{acronym}
-\usepackage{outlines}
-\usepackage{amsmath}
+\usepackage{bm}
+\usepackage{fixltx2e}
 
@@
 %knitr options
+
+%setup
 
@@
 
+{\it
+
+We agree with the reviewer that this application is not entirely appropriate given the hydrodynamic influences on the observed data.
+However, our objective was to demonstrate that unit-testing of the zero-dimensional is an efficient means of improving larger models that are computationally intensive.
+Our intent was not to present a complete predictive model with hydrodynamic forcing to Weeks Bay.
+To address the concern of the reviewer and to maintain our emphasis on unit-testing, we have chosen a a more appropriate dataset, described below.
+A sentence added to the final paragraph of the introduction emphasizes our intent of the analysis:
+
+'In general, the analysis makes a case for unit-testing with lower-dimensional models, particularly when computional limitations preclude the use of conventional optimization algorithms with larger three-dimensional models.'
+
+An alternative dataset was used that included flask experiments of oxygen production from Pensacola Bay, Florida.
+This dataset included light and dark treatments of water samples in closed bottles for an approximate 12-hour period, including before and after measurements of DO concentrations with initial nutrient values for each treatment and replicate.
+The dataset is described in detail in Murrell et al.
+in revision (Murrell, M.
+C., Caffrey, J.
+C., Marcovich, D.
+T., Beck, M.
+W., Jarvis, B.
+M., III, J.
+D.
+H., in revision.
+Seasonal oxygen dynamics in a warm temperate estuary: Effects of hydrologic variability on measurements of primary production, respiration, and net metabolism.
+Estuaries Coasts - (-), –.).
+Methods were added to the manuscript, Sec.
+2.4:
+
+`Estimates of oxygen production from closed bottle experiments were used to calibrate the 0-D model.
+Surface water was collected from a fixed location in Pensacola Bay, Florida (30.35$^{\circ}$ N, 87.20$^{\circ}$ W) on September 25\textsuperscript{th}, 2013 (full details in Murrell et al.
+in revision).
+Water samples were placed into closed 300 mL glass bottles and transported back to the lab for treatments.
+Concentrations of O$_2$ and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection.
+Oxygen concentrations were established using Winkler reagents (Parsons et al.
+1985) and titration using a MetrOhm Titrando with thiosulfate titrant calibrated against an iodate standard and electrochemical endpoint detection.
+Ammonium was analyzed using a fluorometric method (Holmes et al.
+1999); other nutrients were analyzed using either a Thermo Fisher Aquakem 200 discrete analyzer or an Astoria-Pacific continuous flow analyzer using standard colorimetric methods (APHA 2005).
+
+Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using light and dark treaments.
+All treatments were exposed to ambient outdoor conditions in a water bath at the laboratory.
+The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
+The exposure experiments began at 7am and were concluded at 7pm, after which the concentrations of O$_2$ in each bottle were measured.
+Each treatment had four replicates and HOBO\textsuperscript{\textregistered} pendants were used to measure continuous temperature and light.
+Starting O$_2$ concentrations for the experiments were $200.78$ ($\pm$ $4.47$) mmol O$_2$ m$^{-3}$ and ending concentrations were $229.57$ ($\pm$ $2.66$) mmol O$_2$ m$^{-3}$ for the light treatments and $195.51$ ($\pm$ $1.9$) mmol O$_2$ m$^{-3}$ for the dark treatments.
+Initial nutrient concentrations were $0.71$ mmol m$^{-3}$ for NH$_4^+$ (single sample), $0.13$ mmol m$^{-3}$ for PO$_4^{3-}$, and $38.4$ mmol m$^{-3}$ for SiO$_3^{2-}$.
+Concentrations for NO$_2^-$ and NO$_3^-$ were below detection limit.
+
+Each parameter subset for O$_2$ from the selection heuristics was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
+The intial nutrient and oxygen concentrations were used as starting conditions for FishTank.
+The corresponding continuous temperature and light measurements were also used as forcing conditions.
+Parameter values were searched using the optim function...
+'
+}
+
 For the sensitivity analysis the authors manipulated the observations of DO in the estuary filtering the tidal impacts to be able to implement the FishTank model.

### 2017-08-18 ident_manu.Rnw
revision resubmitted

@@
 An ideal model is sufficiently generalizable across systems, provides results that are accurate given the inputs, and includes components that are valid descriptions of actual processes \citep{Levins66, Ganju16}.
-Given that these characteristics cannot be simultaneously achieved, models are developed that balance predictive accuracy with environmental realism, often favoring one at the expense of the other \citep{Morrison99,Ganju16}.
+Given that these characteristics cannot be simultaneously achieved, models are developed to balance predictive accuracy with environmental realism or often favor one at the expense of the other \citep{Morrison99,Ganju16}.
 These challenges are analagous to the well-known bias-variance tradeoff in statistical models that balances the competing objectives of over- and under-fitting to an observed dataset.
@@
 \item identify the parameters that have the greatest influence on state variables using local sensitivity analysis,
-\item quantify the identifiability of subsets of the total parameter space based on sensitivity,
-\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories.
+\item quantify the identifiability of subsets of the total parameter space based on sensitivity, and
+\item provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories.
 \end{inparaenum}
@@
 Surface water was collected from a fixed location in Pensacola Bay, Florida (30.35$^{\circ}$ N, 87.20$^{\circ}$ W) on September 25\textsuperscript{th}, 2013 (full details in \citetalias{MurrellIR}).
-Water samples were placed into closed 100 mL glass bottles at the time of collection and transported back to the lab for treatments.
+Water samples were placed into closed 300 mL glass bottles and transported back to the lab for treatments.
 Concentrations of \ac{do} and nutrients (NH$_4^+$, NO$_2^-$, NO$_3^-$, PO$_4^{3-}$, and SiO$_3^{2-}$) were extracted from the samples within one hour of collection.
@@
 
+<<echo = F>>=
+data(flaskdo)
+
+flsk <- flaskdo %>% 
+  select(-rep, -tmt_rep, -stt, -end) %>% 
+  gather('var', 'val', -tmt) %>% 
+  group_by(tmt, var) %>%
+  summarise(
+    se = sapply(sd(val)/sqrt(length(val)), scinot),
+    val = sapply(mean(val), scinot)
+    )
+
+ltstt <- flsk %>% 
+  filter(tmt %in% 'lt' & var %in% 'sttO2')
+ltend <- flsk %>% 
+  filter(tmt %in% 'lt' & var %in% 'endO2')
+dkstt <- flsk %>% 
+  filter(tmt %in% 'dk' & var %in% 'sttO2')
+dkend <- flsk %>% 
+  filter(tmt %in% 'dk' & var %in% 'endO2')
+initam <- flsk %>% 
+  filter(var %in% 'NH4')
+initno <- flsk %>% 
+  filter(var %in% 'NO3')
+initsi <- flsk %>% 
+  filter(var %in% 'Si')
+initpo <- flsk %>% 
+  filter(var %in% 'PO4')
+@
+
 Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using light and dark treaments.
-All treatments were exposed to ambient outdoor conditions in a water bath with continuous flow at the laboratory.
+All treatments were exposed to ambient outdoor conditions in a water bath at the laboratory.
 The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
@@
 Each treatment had four replicates and HOBO\textsuperscript{\textregistered} pendants were used to measure continuous temperature and light.
-
-Each parameter subset in \cref{tab:heurist1,tab:heurist2,tab:heurist3} for \ac{do} was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
+Starting \ac{do} concentrations for the experiments were \Sexpr{ltstt$val} ($\pm$ \Sexpr{ltstt$se}) mmol O$_2$ m$^{-3}$ and ending concentrations were \Sexpr{ltend$val} ($\pm$ \Sexpr{ltend$se}) mmol O$_2$ m$^{-3}$ for the light treatments and \Sexpr{dkend$val} ($\pm$ \Sexpr{dkend$se}) mmol O$_2$ m$^{-3}$ for the dark treatments.
+Initial nutrient concentrations were \Sexpr{initam$val[1]} mmol m$^{-3}$ for NH$_4^+$ (single sample), \Sexpr{initpo$val[1]} mmol m$^{-3}$ for PO$_4^{3-}$, and \Sexpr{initsi$val[1]} mmol m$^{-3}$ for SiO$_3^{2-}$.
+Concentrations for NO$_2^-$ and NO$_3^-$ were below detection limit.
+
+Each parameter subset for O$_2$ from the selection heuristics was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
 The intial nutrient and oxygen concentrations were used as starting conditions for FishTank.
@@
 An evaluation of the effects of individual parameters on $\gamma$ suggested that some parameters had disproportionate effects on identifiability.
-Based on $\gamma = 15$, \cref{fig:identplo} suggests that most parameter sets for organic matter were identifiable, regardless of how many parameters were selected (i.e., two through eight).
+For example, \cref{fig:identplo} suggests that most parameter sets for organic matter were identifiable ($\gamma <$ 15 for most), regardless of how many parameters were selected (i.e., two through eight).
 However, some subsets were not identifiable such that identification of one or more redundant parameters that are inflating $\gamma$ values could provide useful information.
@@
 
-Calibration of parameter values for each of the seven selection heuristics (\cref{tab:heurist1,tab:heurist2,tab:heurist3}) produced model output that varied in goodness of fit and computational effort required to identify optimal values (\cref{tab:calib}).
+Calibration of parameter values for \ac{do} for each of the seven selection heuristics (\cref{tab:heurist1,tab:heurist2,tab:heurist3}) produced model output that varied in goodness of fit and computational effort required to identify optimal values (\cref{tab:calib}).
 As expected, the number of required iterations of the optimization algorithm to minimize \ac{rmse} of observed \ac{do} and model output varied in proportion to the number of parameters in a subset.
@@
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, the optimal phytoplankton parameters had the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} \Sexpr{strt} mmol O$_2$ m$^{-3}$, reduction to \Sexpr{scinot(phyto$rmse)}).
-The identifiable parameters selected equally within categories (third heuristic) and independent of category (second heuristic) produced the second and third greatest reduction in \ac{rmse} (\Sexpr{scinot(cattop$rmse)}, and \Sexpr{scinot(top$rmse)}, respectively), although much less than that observed for phytoplankton parametrs.
+Of the seven parameter subsets, the optimal phytoplankton parameters had the largest reduction in \ac{rmse} values from the initial output (starting \ac{rmse} \Sexpr{strt} mmol O$_2$ m$^{-3}$, reduction to \Sexpr{scinot(phyto$rmse)}).
+The identifiable parameters selected equally within categories (third heuristic) and independent of category (second heuristic) produced the second and third greatest reduction in \ac{rmse} (\Sexpr{scinot(cattop$rmse)}, and \Sexpr{scinot(top$rmse)}, respectively), although much less than that observed for phytoplankton parameters.
 Overall, calibration to most of the parameter subsets had a small effect on \ac{rmse}.
-However, the magnitude of parameter changes for calibration varied up to several orders of magnitude from the initial values (\cref{tab:calibprm}).
-The percent change in parameters from the intial values varied from no change (Optics parameters \Sexpr{nc$parm[1]} and \Sexpr{nc$prm[2]}) to 900\% (\Sexpr{ncmax$parm}).
+However, the magnitude of parameter changes for calibration varied up to several orders from the initial values (\cref{tab:calibprm}).
+The percent change in parameters from the intial values varied from no change (optics parameters \Sexpr{nc$parm[1]} and \Sexpr{nc$parm[2]}) to 900\% (organic matter parameter \Sexpr{ncmax$parm}).
 Many calibrated parameter values included those at the lower or upper bounds used for the optimization routine (as for phytoplankton, \cref{fig:calex}).
@@
 
-The estimated areal extent of bottom-water hypoxia using default parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at \Sexpr{scinot(maxdef$Original)} km$^2$ (\cref{fig:areachg}a, August mean area \Sexpr{deftxt[1]} $\pm$ \Sexpr{deftxt[2]} km$^2$, \cref{fig:areachg}b).
+The estimated areal extent of bottom-water hypoxia using initial parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at \Sexpr{scinot(maxdef$Original)} km$^2$ (\cref{fig:areachg}a, August mean area \Sexpr{deftxt[1]} $\pm$ \Sexpr{deftxt[2]} km$^2$, \cref{fig:areachg}b).
 Increases in the top sensitive parameters for \ac{do} in each category (\cref{tab:dosens}) increased the estimated areal extent of hypoxia (Figs.
@@
 Although identifiability is the primary limiting factor in choosing a set, the relative sensitivities are more important for the decision to include or exclude individual parameters.
-For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model fit and that these parameters had affects that translated to the larger model.
+For example, \cref{tab:calib,fig:areachg} demonstrated that parameter sets with sensitive parameters had improved model fit and that these parameters had effects that translated to the larger model.
 Our analysis addressed this challenge by presenting multiple selection criteria for identifiable parameter sets that prioritized the most sensitive parameters during the selection process.
@@
 For example, optimization to zooplankton parameters showed almost no change in model \ac{rmse} despite a relatively large sensitivity of the model to individual parameters.
-A more comprehensive approach that considers the interaction of zooplankton parameters with others, such as phytoplankton, is warranted given the structural dependencies betwen parameter cateogires.
-Indeed, the reduction in \ac{rmse} for selection heuristics that weighted the parameter categories equally showed the second largest reduction in model error.
+A more comprehensive approach that considers the interaction of zooplankton parameters with others, such as phytoplankton, is warranted given the structural dependencies betwen parameter categories.
+Indeed, the reduction in \ac{rmse} for selection heuristics that equally considered the parameter categories (third heuristic) showed the second largest reduction in model error.
+This subset included both phytoplankton and zooplankton parameters, suggesting more careful consideration of these sensitive parameters could further improve model calibration.
 
@@
 This design is uncommon in biogeochemical models and could be leveraged for an evaluation of structural uncertainty.
-As such, our analysis of parameter sensitivity and identifiabilty could be combined with an evaluation of observational and structural uncertainty for a more complete characterization of the model, having implications for understanding drivers of hypoxia in coastal waters.
+As such, our analysis of parameter sensitivity and identifiability could be combined with an evaluation of observational and structural uncertainty for a more complete characterization of the model, having further implications for understanding drivers of hypoxia in coastal waters.
 
@@
 However, the views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the US EPA.
+Mention of trade names or commercial products does not constitute endorsement by the authors or the US EPA.
 
@@
 The parameters of each subset are from \\cref{tab:heurist1,tab:heurist2,tab:heurist3}.
-The L1 values are relative sensitivity of \\ac{do} to a paramter change.
-Starting and final parameter values after calibration are shown, including the percent change.
-The calibration routing was bounded by minimum and maximum values appropriate for each parameter.'
+The L1 values are relative sensitivity of \\ac{do} to a parameter change.
+Initial and final parameter values after calibration are shown, including the percent change.
+The calibration routine was bounded by minimum and maximum values for each parameter.'
 colnms <- c('Parameter', 'L1', 'Min/Max', 'Initial', 'Final', '\\% change')
@@
 \includegraphics[width=0.7\textwidth]{figs/fishmod.pdf}
-\caption{Conceptual representation of biogeochemical components included in FishTank (complete equations in \citealt{Eldridge10}).
+\caption{Conceptual representation of biogeochemical components included in FishTank (complete equations in \citealt{Eldridge10}, appendices A-F in \citealt{Lehrter17}).
 The \acl{cgem} couples FishTank with a hydrodynamic model that includes advection, mixing, and dispersion.}
@@
 The phytoplankton parameters were those identifiable for dissolved oxygen (\\cref{tab:heurist1}), arranged from most (top plot) to least sensitive (bottom plot) (\\cref{tab:dosens}).
-The relative parameter changes in the right plots show the initial parameter values (black) and the the selected parameter values (blue) after calibration.', fig.height = 7, fig.width = 6, echo = F, cache = T, out.width = '\\textwidth'>>=
+The relative parameter changes in the right plots show the initial parameter values (black) and the selected parameter values (blue) after calibration.', fig.height = 7, fig.width = 6, echo = F, cache = T, out.width = '\\textwidth'>>=
 data(cals)

### 2017-08-18 revision/source/ident_manu.tex
revision resubmitted

--- 2017-08-17 ident_manu.tex
@@
 \title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
-\tnotetext[mytitlenote]{Version: Wed Aug 16 18:18:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/b081f900ad818adbbf496e0b8888820e38bda065}{b081f900ad818adbbf496e0b8888820e38bda065}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
+\tnotetext[mytitlenote]{Version: Thu Aug 17 18:08:14 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/7e3894b946e67efce7a075d46c2169be58729981}{7e3894b946e67efce7a075d46c2169be58729981}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
 
@@
 Oxygen production after an approximate 12 hour period (morning to evening) was estimated within the bottles using light and dark treaments.
-All treatments were exposed to ambient outdoor conditions in a water bath with continuous flow at the laboratory.
+All treatments were exposed to ambient outdoor conditions in a water bath at the laboratory.
 The dark treatments used opaque black bottles to ensure no exposure of ambient light to the samples.
@@
 Each treatment had four replicates and HOBO\textsuperscript{\textregistered} pendants were used to measure continuous temperature and light.
-
-Each parameter subset in \cref{tab:heurist1,tab:heurist2,tab:heurist3} for \ac{do} was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
+Starting \ac{do} concentrations for the experiments were $200.78$ ($\pm$ $4.47$) mmol O$_2$ m$^{-3}$ and ending concentrations were $229.57$ ($\pm$ $2.66$) mmol O$_2$ m$^{-3}$ for the light treatments and $195.51$ ($\pm$ $1.9$) mmol O$_2$ m$^{-3}$ for the dark treatments.
+Initial nutrient concentrations were $0.71$ mmol m$^{-3}$ for NH$_4^+$ (single sample), $0.13$ mmol m$^{-3}$ for PO$_4^{3-}$, and $38.4$ mmol m$^{-3}$ for SiO$_3^{2-}$.
+Concentrations for NO$_2^-$ and NO$_3^-$ were below detection limit.
+
+Each parameter subset for O$_2$ from the selection heuristics was calibrated to the ending oxygen concentration for each of the four replicates of each treatment.
 The intial nutrient and oxygen concentrations were used as starting conditions for FishTank.
@@
 No association was observed between collinearity ($\gamma$) and number of iterations or calibration.
-Of the seven parameter subsets, the optimal phytoplankton parameters had the largest reduction in \ac{rmse} values from the default output (starting \ac{rmse} $21.14$ mmol O$_2$ m$^{-3}$, reduction to $5.81$).
-The identifiable parameters selected equally within categories (third heuristic) and independent of category (second heuristic) produced the second and third greatest reduction in \ac{rmse} ($19.09$, and $19.45$, respectively), although much less than that observed for phytoplankton parametrs.
+Of the seven parameter subsets, the optimal phytoplankton parameters had the largest reduction in \ac{rmse} values from the initial output (starting \ac{rmse} $21.14$ mmol O$_2$ m$^{-3}$, reduction to $5.81$).
+The identifiable parameters selected equally within categories (third heuristic) and independent of category (second heuristic) produced the second and third greatest reduction in \ac{rmse} ($19.09$, and $19.45$, respectively), although much less than that observed for phytoplankton parameters.
 Overall, calibration to most of the parameter subsets had a small effect on \ac{rmse}.
-However, the magnitude of parameter changes for calibration varied up to several orders of magnitude from the initial values (\cref{tab:calibprm}).
-The percent change in parameters from the intial values varied from no change (Optics parameters \textit{astarOMZ} and ) to 900\% (\textit{KO2}).
+However, the magnitude of parameter changes for calibration varied up to several orders from the initial values (\cref{tab:calibprm}).
+The percent change in parameters from the intial values varied from no change (optics parameters \textit{astarOMZ} and \textit{astarOMA}) to 900\% (organic matter parameter \textit{KO2}).
 Many calibrated parameter values included those at the lower or upper bounds used for the optimization routine (as for phytoplankton, \cref{fig:calex}).
@@
 
-The estimated areal extent of bottom-water hypoxia using default parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at $1.19e^{4}$ km$^2$ (\cref{fig:areachg}a, August mean area 8988 $\pm$ 551 km$^2$, \cref{fig:areachg}b).
+The estimated areal extent of bottom-water hypoxia using initial parameter values for the 3-dimensional model peaked on August, 28\textsuperscript{th} at $1.19e^{4}$ km$^2$ (\cref{fig:areachg}a, August mean area 8988 $\pm$ 551 km$^2$, \cref{fig:areachg}b).
 Increases in the top sensitive parameters for \ac{do} in each category (\cref{tab:dosens}) increased the estimated areal extent of hypoxia (Figs.
@@
 The parameters of each subset are from \cref{tab:heurist1,tab:heurist2,tab:heurist3}.
-The L1 values are relative sensitivity of \ac{do} to a paramter change.
-Starting and final parameter values after calibration are shown, including the percent change.
-The calibration routing was bounded by minimum and maximum values appropriate for each parameter.\label{tab:calibprm}}
+The L1 values are relative sensitivity of \ac{do} to a parameter change.
+Initial and final parameter values after calibration are shown, including the percent change.
+The calibration routine was bounded by minimum and maximum values for each parameter.\label{tab:calibprm}}
 \begin{center}
@@
 The phytoplankton parameters were those identifiable for dissolved oxygen (\cref{tab:heurist1}), arranged from most (top plot) to least sensitive (bottom plot) (\cref{tab:dosens}).
-The relative parameter changes in the right plots show the initial parameter values (black) and the the selected parameter values (blue) after calibration.}\label{fig:calex}
+The relative parameter changes in the right plots show the initial parameter values (black) and the selected parameter values (blue) after calibration.}\label{fig:calex}
 \end{figure}
